### 2013-03-13 text/opencv-test.tex
Added a writeup for march 14th

\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}

\begin{document}

\title{Preliminary test on OpenCV feature implementations}
\author{Jonas Arnfred}

\maketitle

\begin{abstract}
% TODO!
\end{abstract}

\section{Project Description} 
In controlled settings existing face recognition
algorithms have achieved good results in both classifying and clustering faces,
but often these approaches break down when we consider images from real life 
application such as cell phone photo albums. Here we encounter non-aligned 
faces under different lighting conditions that might be partially obscured and 
turning in different directions. Even recent approaches to recognize 
non-aligned faces such as \cite[pp 9.]{liao2011} don't achieve more than 60\% 
geniune accept rate at 1\% false accept rate when comparing faces from 
LFW\footnote{Labeled Faces in the Wild} database. When we consider face patches 
not revealing the entire face the performance drops further to around 40\% 
genuine accept rate at 1\% false accept rate.

If we relax the problem of classification to the more general problem of 
clustering it might turn out that this accuracity is sufficient to accurately 
separate a set of face patches into partitions each ideally only containing 
pictures belonging to one person.

\subsection{A modest proposal}
%
% Consider a graph $G = (V, E)$ where $v_i$ is a vertix if $v_i \in V$ and 
% $e_i$ is an edge if $(v_i, v_j) \in E$ for $v_i, v_j \in V$ and a class 
% function $C (V \rightarrow c (c \in C)$ it is often possible to obtain a 
% partitioning $P$ such that for each partition $p \in P$ we have that $\forall 
% v_i, v_j \in c, C(v_i) = C(v_j)$ \emph{even} when the graph contains 
% interclass edges, that is an $\exists e \in E$ for which $
%
If we consider a graph it is often possible to succesfully obtain a 
partitioning that adheres to a classification of the graph even if the graph 
has intercluster edges. This is of course only possible as long as the 
intercluster edges outnumber or outweigh the intracluster edges, but if we can 
create a link between two nodes around 40\% of the time and only have 1\% of 
them be incorrect, we are looking at a very well behaved graph.

To apply graph clustering to image clustering, consider the set of image 
patches as the set of nodes and the edges between the nodes as the similarity 
between two image patches. The ideal partitioning of the graph is then one 
where all the nodes representing image patches belonging to a particular person 
are clustered together in their own partition.

Intuitively this is an easier problem than classification. Even if two 
images-patches might not resemble each other, they could both happen to 
resemble a common neighbor and consequently be clustered together.

\subsection{How can this be done?}
Because images in real world conditions are often taken under changing light 
and containing partially obscured or half turned faces, we can't require images 
to be aligned and homogenious in lighting and position in order to use them.

An alternative approach would be to sample characteristics from the face-patch 
in the form of feature points and compare how well these samples match feature 
points from other face-patches. If we can descripe the feature points in a 
light and affine transformation agnostic way, ideally we would be able to match 
them to corresponding feature points on other face-patches.

By comparing feature points we can construct a similarity graph linking the 
face-patches to each other and use a graph clustering algorithm to obtain the 
final clusterings.

\section{So is it done yet?}
Before I present the finished algorithm there are a few practical and 
theoretical problems that need to be solved first.

\subsection{Theoretical shenanigans}

Given two sets of feature points and trying to match them, it's important to 
realize that these two sets might be obtained from face-patches that contain 
some overlapping characteristics but both might also contain features that are 
not present in the other patch at all. If one patch contain the face from the 
eyes and down (the person might be wearing a cap) and the other patch contain 
everything from the nose and up (the same person might cover their mouth with 
their hand) we will have feature points from the cap, the hair, the mouth and 
the hand that will not match at all. This means that when we try to match two 
face-patches, we need to match them in a way that highlights the points that 
match well and ignores the points that don't.

I see two ways to possibly approach the problem. One is to find a mathematical 
method like sub-tree matching or similar approaches to match the two sets of 
feature points against each other for each image\footnote{I would be interested 
in hearing your input on this subject, or be put in contact with someone who 
might answer it}. A different (and in my opinion promising) approach is to 
forego the matching of two images entirely:

If we consider the entire set of face-patches and the even bigger set of all 
the feature points, we could potentially match each feature point against the 
set of all possible feature points. Instead of basing the edges in the graph on 
the similarity of two image patches, we base the edge on the feature points 
that happen to be linked between any two given face-patches when matched 
against all possible points. A na\"ive approach is obviously of quadratic 
complexity in the amount of feature points, which very fast would become 
unfeasible to compute, but since points that can be compared both euclidean 
distances and hamming distances form a metric space, a much faster solution 
might be possible using metric trees like VP and BK trees\footnote{See: 
\href{http://stackoverflow.com/questions/6389841/efficiently-find-binary-strings-with-low-hamming-distance-in-large-set}{This 
answe on stackoverflow.com} and 
\href{http://en.wikipedia.org/wiki/Metric_tree}{Wikipedia} (I promise and swear 
I won't use wikipedia as a source for the thesis!)
}. In the case of hamming distance I could potentially further Huffman encode 
the library of feature points to reduce their length without reducing 
dimensionality.

Here is the text of your introduction.

\begin{equation}
    \label{simple_equation}
    \alpha = \sqrt{ \beta }
\end{equation}

\subsection{Subsection Heading Here}
Write your subsection text here.

\begin{figure}
    \centering
    \includegraphics[width=3.0in]{myfigure}
    \caption{Simulation Results}
    \label{simulationfigure}
\end{figure}

\section{Conclusion}
Write your conclusion here.

\end{document}

### 2013-03-13 text/opencv-test.tex
Added some youtube links to report

@@
 in the form of feature points and compare how well these samples match feature 
-points from other face-patches. If we can descripe the feature points in a 
+points from other face-patches. If we can describe the feature points in a 
 light and affine transformation agnostic way, ideally we would be able to match 
@@
 
-\subsection{Theoretical shenanigans}
+\subsection{Theoretical shenanigans\footnote{%
+\href{http://www.youtube.com/watch?v=MFZG8KQJni8}{Relevant YouTube Clip}}}
 
@@
 feature points against each other for each image\footnote{I would be interested 
-in hearing your input on this subject, or be put in contact with someone who 
-might answer it}. A different (and in my opinion promising) approach is to 
-forego the matching of two images entirely:
+in hearing your input on this subject}.  A different (and in my opinion 
+promising) approach is to forego the matching of two images entirely:
 
@@
 dimensionality.
+
+\subsection{Practical considerations}
+
+The success of this approach is dependent on feature points being able to 
+describe image keypoints in a light and affine transformation agnostic way. In 
+the paper using an alignment free approach to match images I mentioned 
+before\footnote{\cite{liao2011}} they whip up their own feature descriptor, an 
+approach I'm not personally very convinced of since they never show their own 
+descriptor to be superior to anything else than sift. Given that many new 
+feature descriptors have come out in recent years, it seems to me much more 
+sensible to use an already tested and confirmed approach than to cook up a new 
+method, before I can show that coming up with a new feature descriptor is the 
+only way to solve the problem\footnote{And in this case I'll most likely spend 
+my thesis trying to come up with a feature descriptor instead of solving the 
+original problem}.
+
+Fortunately OpenCV implements a range of feature descriptors\footnote{To be 
+precise they include an interface for: SIFT, SURF, ORB, BRISK, BRIEF and FREAK.  
+I have however not been able to get FREAK to work}. So in order to see if any 
+of these feature detectors might be usable and if yes, which ones, I decided to 
+put them to the test.
+
+\section{Getting some data\footnote{%
+\href{http://www.youtube.com/watch?v=FQ3UrLQP2ok}{Relevant YouTube clip}}}
 

### 2013-03-13 text/opencv-test.tex
Finished the opencv-test writeup

@@
 \usepackage{hyperref}
+\usepackage[stable]{footmisc}
+\usepackage{caption}
+\usepackage{adjustbox}
+\usepackage{subcaption}
 
@@
 If we relax the problem of classification to the more general problem of 
-clustering it might turn out that this accuracity is sufficient to accurately 
+clustering it might turn out that this accuracy is sufficient to accurately 
 separate a set of face patches into partitions each ideally only containing 
@@
 %
-If we consider a graph it is often possible to succesfully obtain a 
+If we consider a graph it is often possible to successfully obtain a 
 partitioning that adheres to a classification of the graph even if the graph 
-has intercluster edges. This is of course only possible as long as the 
-intercluster edges outnumber or outweigh the intracluster edges, but if we can 
-create a link between two nodes around 40\% of the time and only have 1\% of 
-them be incorrect, we are looking at a very well behaved graph.
+has \emph{inter}-cluster edges. This is of course only possible as long as the 
+\emph{inter}-cluster edges outnumber or outweigh the \emph{intra}-cluster 
+edges, but if we can create a link between two nodes around 40\% of the time 
+and only have 1\% of them be incorrect, we are looking at a very well behaved 
+graph.
 
@@
 \subsection{Theoretical shenanigans\footnote{%
-\href{http://www.youtube.com/watch?v=MFZG8KQJni8}{Relevant YouTube Clip}}}
+\href{http://www.youtube.com/watch?v=MFZG8KQJni8}{http://www.youtube.com/watch?v=MFZG8KQJni8}}}
 
@@
 
-\section{Getting some data\footnote{%
-\href{http://www.youtube.com/watch?v=FQ3UrLQP2ok}{Relevant YouTube clip}}}
+\section{Experiments}
+The goal of these experiment is to see if different feature descriptors given 
+real life images would score the similarities between images showing the same 
+face significantly higher than images showing the faces of different people.
 
-Here is the text of your introduction.
+\subsection{Getting some data\footnote{%
+\href{http://www.youtube.com/watch?v=FQ3UrLQP2ok}{http://www.youtube.com/watch?v=FQ3UrLQP2ok}}}
+In order to test this I used the LFW dataset\footnote{Labeled Faces in the 
+Wild}.  This is a dataset consisting of labeled photos of famous people taken 
+by photographers under different circumstances and in different quality. The 
+faces vary between looking straight at the camera and turning their head to 
+either side, but not to the extend of being full profile. The lighting is 
+usually relatively good but very inconsistent as most photos are from different 
+events, sometimes years apart.
 
-\begin{equation}
-    \label{simple_equation}
-    \alpha = \sqrt{ \beta }
-\end{equation}
+This dataset is not a perfect match since the ideal application for this 
+algorithm would be people's own photo albums, where the camera used is 
+consistent and the faces often might be in profile. However it does pose 
+similar challenges in the form of lightning and non-aligned faces that it 
+serves well to give a rough idea of the general performance of different 
+feature descriptors.
 
-\subsection{Subsection Heading Here}
-Write your subsection text here.
+\subsection{Experiment Setup}
+
+In general there are two measures to consider when we compare keypoints in an 
+image; the distance measure and how unique the match is. The distance measure 
+for the keypoint descriptors I have reviewed are either based on euclidean 
+distance or on hamming distance. Once we have matched keypoints of one image to 
+their highest matching counterpart in another image, we can filter these 
+matches either by only including matches that symmetric, i.e. if we swap the 
+two images and run the same matching algorithm we get the same match. Another 
+method proposed in \cite{lowe2004sift} is to look at the ratio between the best 
+and second best match. If the distances are too similar, the keypoint match is 
+not unique enough and hence discarded.
+
+Since I don't have a solution yet for how best to compare two face-patches, I 
+have created four na\"ive methods that gives a score for a match of two 
+face-patches given their keypoint descriptors. These methods might not be 
+ideal, but it's my hope that they serve the purpose of rating the similarities 
+between images well enough to evaluate the different types of descriptors.  
+Notice that since a better matching function would be able to discard more bad 
+matches and keep more good matches, the results obtained using my na\"ive 
+methods sets a lower bound on how well the different descriptors perform.  
+Hopefully this lower bound is equally tight for all of them, but this is by no 
+means a given and my comparison can therefore not be seen as a general 
+evaluation of their performance.
+
+The four matching functions are given as parameters the distance for each 
+keypoint to it's closest match and the ratio for each keypoint between the 
+distance of the closest and second closest match. They work as follows:
+\begin{itemize}
+	\item{\emph{Simple Mean}: Take the mean of all distances}
+	\item{\emph{Better half}: Take the mean of the best half of the distances}
+	\item{\emph{Treshold}: Take the mean of only the points that are both in the 
+	better half of distances and ratios}
+	\item{\emph{Limit to 10}: As above but take only the 10 points with the 
+best distance}
+\end{itemize}
+I also created another four similarly functions, the only difference being that 
+the mean was over the \emph{ratio} and not the \emph{distance}.
+
+To quickly weed out bad performers I designed a small test-set including three 
+people from the LFW testset\footnote{Anna Kournikova, Ann Veneman and Bill 
+Gates}. For each person 10 images were picked at random and all pairs of images 
+compared using the eight functions mentioned above.
+
+\begin{table}[t]
+\begin{center}
+	\begin{tabular}{l l|l l}
+		\multicolumn{2}{c}{Preliminary Test} & \multicolumn{2}{c}{Full Test} \\
+		\hline
+		Locator & Descriptor & Locator & Descriptor \\
+		\hline
+		Sift & Sift & &\\
+		Surf & Surf & &\\
+		Orb & Orb & Orb & Orb \\
+		Fast & Orb & Fast & Orb \\
+		Orb & Brief & Orb & Brief \\
+		Fast & Brief & Fast & Brief \\
+		Orb & Brisk & & \\
+		Brisk & Brisk & & \\
+	\end{tabular}
+	\label{table:features}
+	\caption{Keypoints and descriptors used in preliminary and full testing 
+round}
+\end{center}
+\end{table}
+
+Since I have several different methods for selecting keypoints and several 
+different algorithms for creating descriptors based on the keypoints 
+available in OpenCV. The pairings I tested can be seen in table 1.  
+Generally I used the keypoint locator that was available for the 
+descriptor I was testing, and when this wasn't possible paired the 
+descriptor with a keypoint locator of a similar method.
+
+Upon finding the best performing keypoint locator and descriptor pairs I went 
+on to test them on an imageset containing $60$ people with ten images per 
+person, that is $600$ images in total.
+
+\section{Results\footnote{%
+\href{http://www.youtube.com/watch?v=tKT-eWMWXOE}{http://www.youtube.com/watch?v=tKT-eWMWXOE}}}
+
+The results from the preliminary testing can be seen in table 2.  The 
+difference displayed is the percentage wise difference between the score 
+of pairs of faces belonging to the same person as opposed to pairs of 
+faces belonging to two different people. The score is calculated using 
+either the ratio or the distance with one of the four functions 
+described above.
+
+It is immediately obvious that the distance based measures fare much better 
+than the ratio based measures. In particular the `treshold' and `limit10' 
+methods work well. However our main concern is not with how well the different 
+functions perform but rather the performance of different descriptors. Here we 
+see a clear advantage of Orb, Brief and Brisk. Brisk however shows some strange 
+fluctuations and would be surprised if these results were a true indicator of 
+the performance of the descriptor. Brisk is also significantly slower than the 
+others, usually taking around 9-10 seconds to calculate similarities between 30 
+images, something than can be calculated by the other methods in around 0.3 
+seconds.
+
+\begin{table}[t]
+\begin{adjustbox}{center}
+	\label{table:preliminary}
+	\begin{tabular}{l c c c c c c c c}
+		& \multicolumn{4}{c}{Ratio} & \multicolumn{4}{c}{Distance} \\
+		& Mean & Best Half & Treshold & Limit10 & Mean & Best Half & Treshold &
+Limit10 \\
+		\hline
+		Sift-Sift	& 0.4 & 0.7 & 0.8  & 0.4  & 0.7 & -0.4 & 1.0 & 1.5 \\
+		Surf-Surf	& 0.4 & 0.7 & 0.8  & 1.4  & 0.9 & 0.9  & 0.7 & 0.9 \\
+		Orb-Orb		& 0.6 & 1.1 & 1.3  & 1.1  & 2.0 & 0.6  & 3.8 & 3.5 \\
+		Fast-Orb	& 0.8 & 1.5 & 1.7  & 1.6  & 2.7 & 13.2 & 4.3 & 4.7 \\
+		Orb-Brief	& 0.4 & 0.9 & 1.0  & 0.6  & 5.8 & 2.3  & 8.9 & 8.8 \\
+		Fast-Brief	& 1.1 & 2.0 & 2.2  & 2.0  & 4.8 & 11.0 & 8.3 & 10.6 \\
+		Orb-Brisk	& 1.1 & 2.0 & 2.2  & 2.3  & 4.8 & 7.3  & 6.7 & 6.8 \\
+		Brisk-Brisk	& 0.0 & 0.0 & -0.1 & -0.1 & 0.9 & -6.2 & 1.7 & 1.7 \\
+	\end{tabular}
+\end{adjustbox}
+	\caption{Percentage difference in preliminary testing round}
+\end{table}
+
+The difference in mean doesn't tell us much if we don't know the variance of 
+the individual classifier, since a high variance would mean that we would need 
+an equally big difference to use the similarity score for anything. To 
+illustrate the behavior of the distributions I've made a few plots. In 
+figure \ref{fig:smallset-all-methods} eight histograms are shown, each 
+displaying the behavior of a particular keypoint locator-descriptor 
+combination using the same score function (Treshold).  When taking the 
+distributions into account it's apparent that the descriptors Orb and 
+Brief are performing about equally well given Orb's lower variance.
 
@@
         \centering
-    \includegraphics[width=3.0in]{myfigure}
-    \caption{Simulation Results}
-    \label{simulationfigure}
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/sift-sift-treshold}
+				\caption{Sift-Sift Treshold: 1.0\% diff.}
+				\label{fig:smallset-sift-sift-treshold}
+        \end{subfigure}%
+		\quad %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/surf-surf-treshold}
+				\caption{Surf-Surf Treshold: 0.6\% diff.}
+				\label{fig:smallset-surf-surf-treshold}
+        \end{subfigure}%
+
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/orb-orb-treshold}
+				\caption{Orb-Orb Treshold: 3.8\% diff.}
+				\label{fig:smallset-orb-orb-treshold}
+        \end{subfigure}%
+		\quad%
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/fast-orb-treshold}
+				\caption{Fast-Orb Treshold: 4.3\% diff.}
+				\label{fig:smallset-fast-orb-treshold}
+        \end{subfigure}%
+
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/orb-brief-treshold}
+				\caption{Orb-Brief Treshold: 8.9\% diff.}
+				\label{fig:smallset-orb-brief-treshold}
+        \end{subfigure}%
+		\quad%
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/fast-brief-treshold}
+				\caption{Fast-Brief Treshold: 8.3\% diff.}
+				\label{fig:smallset-fast-brief-treshold}
+        \end{subfigure}%
+
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/orb-brisk-treshold}
+				\caption{Orb-Brisk Treshold: 6.7\% diff.}
+				\label{fig:smallset-orb-brisk-treshold}
+        \end{subfigure}%
+		\quad%
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/brisk-brisk-treshold}
+				\caption{Brisk-Brisk Treshold: 1.7\% diff.}
+				\label{fig:smallset-brisk-brisk-treshold}
+        \end{subfigure}%
+		\caption{Treshold results on 30 images}\label{fig:smallset-all-methods}
 \end{figure}
 
-\section{Conclusion}
-Write your conclusion here.
+I've included figure \ref{fig:smallset-orb-brief} to illustrate how Orb-Brief 
+performs over different score functions using the small testset of 30 images.  
+With only 30 images, there is no saying if the scores are just a fluke, or if 
+they will behave consistently at bigger datasets. Figure \ref{fig:bigset} is 
+included to illustrate the behavior of Orb-Brief when testing on 600 images and 
+60 people instead. The results are encouraging since they replicate and 
+usual exceeds the preliminary results using only 30 images. In table 3 
+the results from the simulation on 600 images are displayed.
+
+\begin{figure}
+        \centering
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/orb-brief-simplemean}
+				\caption{Orb-Brief Simple mean: 5.8\% diff.}
+				\label{fig:smallset-orb-brief-simplemean}
+        \end{subfigure}%
+		\quad %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[b]{0.45\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/orb-brief-besthalf}
+				\caption{Orb-Brief Best half: 2.3\% diff.}
+				\label{fig:smallset-orb-brief-besthalf}
+		\end{subfigure}
+
+		\begin{subfigure}[b]{0.45\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/orb-brief-treshold}
+				\caption{Orb-Brief Treshold: 8.7\% diff.}
+				\label{fig:smallset-orb-brief-treshold}
+		\end{subfigure}
+		\quad%
+		\begin{subfigure}[b]{0.45\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Smallset/orb-brief-limit10}
+				\caption{Orb-Brief Limit 10: 8.8\% diff.}
+				\label{fig:smallset-orb-brief-limit10}
+		\end{subfigure}
+		\caption{Orb-Brief results on 30 images}\label{fig:smallset-orb-brief}
+\end{figure}
+
+\begin{figure}
+        \centering
+		\begin{subfigure}[b]{0.45\textwidth}
+                \centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Bigset/orb-brief-simplemean}
+				\caption{Orb-Brief Simple mean: 6.3\% diff.}
+				\label{fig:bigset-orb-brief-simplemean}
+        \end{subfigure}%
+        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[b]{0.45\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Bigset/orb-brief-besthalf}
+				\caption{Orb-Brief Best half: 9.2\% diff.}
+				\label{fig:bigset-orb-brief-besthalf}
+		\end{subfigure}
+
+		\begin{subfigure}[b]{0.45\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Bigset/orb-brief-treshold}
+				\caption{Orb-Brief Treshold: 9.3\% diff.}
+				\label{fig:bigset-orb-brief-treshold}
+		\end{subfigure}
+%
+		\begin{subfigure}[b]{0.45\textwidth}
+				\centering
+				\includegraphics[width=\textwidth]{../results/OpenCV-Evaluate/Bigset/orb-brief-limit10}
+				\caption{Orb-Brief Limit 10: 9.8\% diff.}
+				\label{fig:bigset-orb-brief-limit10}
+		\end{subfigure}
+		\caption{Orb-Brief results on 600 images}\label{fig:bigset}
+\end{figure}
+
+\begin{table}[t]
+	\centering
+	\label{table:bigset}
+	\begin{tabular}{l c c c c}
+		& Mean & Best Half & Treshold & Limit10 \\
+		\hline
+		Orb-Orb		& 2.4 & 3.8 & 4.1  & 4.4 \\
+		Fast-Orb	& 3.9 & 5.7 & 6.2  & 7.1 \\
+		Orb-Brief	& 6.3 & 9.2 & 9.3  & 9.8 \\
+		Fast-Brief	& 4.7 & 7.0 & 7.3  & 8.2 \\
+	\end{tabular}
+	\caption{Percentage difference in full testing round}
+\end{table}
+
+\section{Conclusion and Questions for tomorrow}
+
+In conclusion I think that both Orb and Brief would be worth testing out for an 
+alignment free clustering approach. The important details I think we should 
+touch upon tomorrow are as follows:
+\begin{itemize}
+\item{Do these results overall show enough discriminative power to merit 
+further exploration?}
+\item{How can I best compare the keypoints of two face-patches?}
+\item{Does my proposal for using Metric trees to circumvent the problem sound 
+doable?}
+\item{Is there something super important that I've completely ignored so far?  
+(I'm mostly sitting alone with this, so I need a reality check)}
+\end{itemize}
+
+\bibliographystyle{plainnat}
+\bibliography{bibliography}
+
+% Here is the text of your introduction.
+% 
+% \begin{equation}
+%     \label{simple_equation}
+%     \alpha = \sqrt{ \beta }
+% \end{equation}
+% 
+% \subsection{Subsection Heading Here}
+% Write your subsection text here.
+% 
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=3.0in]{myfigure}
+%     \caption{Simulation Results}
+%     \label{simulationfigure}
+% \end{figure}
+% 
+% \section{Conclusion}
+% Write your conclusion here.
 

### 2013-03-15 code/descriptors/__init__.py
Preprocessing code that didn't turn out to work that well

@@ -1,0 +1,3 @@
+# Load preprocessing unit
+from pkgutil import extend_path
+__path__ = extend_path(__path__, "../preprocessing/")

### 2013-03-15 code/descriptors/evaluate.py

@@ -21,9 +21,10 @@ from itertools import combinations
 
 
 
-def imageToImage(paths, keypoint_type, descriptor_type, score_fun = lambda i,s,u : numpy.mean(s)) :
+def imageToImage(images, labels, keypoint_type, descriptor_type, score_fun = lambda i,s,u : numpy.mean(s)) :
 	""" Compare every image with every other image, generating a few different scores
-	    input: paths [List of Strings] Paths of all the images
+	    input: images [List of nparrays] all the images
+	           labels [List of Strings] labels of all the images
 		       keypoint_type [String] e.g "SURF" or "ORB" etc
 		       keypoint_descriptor [String] e.g "SURF" or "ORB" etc
 		       score_fun [(list(int), list(int/float), list(float)) -> float]
@@ -34,18 +35,12 @@ def imageToImage(paths, keypoint_type, descriptor_type, score_fun = lambda i,s,u
 		                                   where of the same person and false if not
 	"""
 
-	# Load all images
-	images = map(f.loadImage, paths)
-
 	# Get keypoints
 	keypoints = map(lambda i : f.getKeypoints(keypoint_type, i), images)
 
 	# Get descriptors
 	data = map(lambda i,k : f.getDescriptors(descriptor_type, i, k), images, keypoints)
 	keypoints, descriptors = zip(*data)
-
-	# Create a set of labels
-	labels = map(f.getLabel, paths)
 
 	# Return the scores labeled with a boolean to indicate if they are of same set
 	return matchDescriptors(descriptors, labels, descriptor_type, score_fun)

### 2013-03-15 code/preprocessing/facerec/classifier.py

@@ -1,0 +1,170 @@
+from facerec.distance import EuclideanDistance
+from facerec.util import asRowMatrix
+import logging
+import numpy as np
+import operator as op
+
+class AbstractClassifier(object):
+    def compute(self,X,y):
+        raise NotImplementedError("Every AbstractClassifier must implement the compute method.")
+    
+    def predict(self,X):
+        raise NotImplementedError("Every AbstractClassifier must implement the predict method.")
+
+class NearestNeighbor(AbstractClassifier):
+    """
+    Implements a k-Nearest Neighbor Model with a generic distance metric.
+    """
+    def __init__(self, dist_metric=EuclideanDistance(), k=1):
+        AbstractClassifier.__init__(self)
+        self.k = k
+        self.dist_metric = dist_metric
+
+    def compute(self, X, y):
+        self.X = X
+        self.y = np.asarray(y)
+    
+    def predict(self, q):
+        """
+        Predicts the k-nearest neighbor for a given query in q. 
+        
+        Args:
+        
+            q: The given query sample, which is an array.
+            
+        Returns:
+        
+            A list with the classifier output. In this framework it is
+            assumed, that the predicted class is always returned as first
+            element. Moreover, this class returns the distances for the 
+            first k-Nearest Neighbors. 
+            
+            Example:
+            
+                [ 0, 
+                   { 'labels'    : [ 0,      0,      1      ],
+                     'distances' : [ 10.132, 10.341, 13.314 ]
+                   }
+                ]
+            
+            So if you want to perform a thresholding operation, you could 
+            pick the distances in the second array of the generic classifier
+            output.    
+                    
+        """
+        distances = []
+        for xi in self.X:
+            xi = xi.reshape(-1,1)
+            d = self.dist_metric(xi, q)
+            distances.append(d)
+        if len(distances) > len(self.y):
+            raise Exception("More distances than classes. Is your distance metric correct?")
+        distances = np.asarray(distances)
+        # Get the indices in an ascending sort order:
+        idx = np.argsort(distances)
+        # Sort the labels and distances accordingly:
+        sorted_y = self.y[idx]
+        sorted_distances = distances[idx]
+        # Take only the k first items:
+        sorted_y = sorted_y[0:self.k]
+        sorted_distances = sorted_distances[0:self.k]
+        # Make a histogram of them:
[…]

### 2013-03-15 code/preprocessing/facerec/dataset.py

@@ -1,0 +1,59 @@
+import os as os
+import numpy as np
+import PIL.Image as Image
+import random
+import csv
+
+class DataSet(object):
+    def __init__(self, filename=None, sz=None):
+        self.labels = []
+        self.groups = []
+        self.names = {}
+        self.data = []
+        self.sz = sz
+        if filename is not None:
+            self.load(filename)
+
+    def shuffle(self):
+        idx = np.argsort([random.random() for i in xrange(len(self.labels))])
+        self.data = [self.data[i] for i in idx]
+        self.labels = self.labels[idx]
+        if len(self.groups) == len(self.labels):
+            self.groups = self.groups[idx]
+
+    def load(self, path):
+        c = 0
+        for dirname, dirnames, filenames in os.walk(path):
+            for subdirname in dirnames:
+                subject_path = os.path.join(dirname, subdirname)
+                for filename in os.listdir(subject_path):
+                    try:
+                        im = Image.open(os.path.join(subject_path, filename))
+                        im = im.convert("L")
+                        # resize to given size (if given)
+                        if (self.sz is not None) and isinstance(self.sz, tuple) and (len(self.sz) == 2):
+                            im = im.resize(self.sz, Image.ANTIALIAS)
+                        self.data.append(np.asarray(im, dtype=np.uint8))
+                        self.labels.append(c)
+                    except IOError:
+                        pass
+                self.names[c] = subdirname
+                c = c+1
+        self.labels = np.array(self.labels, dtype=np.int)
+        
+    def readFromCSV(self, filename):
+        # <filename>;<classId>;<groupId>
+        data = [ [str(line[0]), int(line[1]),int(line[2])] for line in csv.reader(open(filename, 'rb'), delimiter=";")]
+        self.labels = np.array([item[1] for item in data])
+        self.groups = np.array([item[2] for item in data])
+        print self.labels
+        print self.groups
+        for item in data:
+            im_filename = item[0]
+            print im_filename
+            im = Image.open(os.path.join(im_filename))
+            im = im.convert("L")
+            # resize to given size (if given)
+            if (self.sz is not None) and isinstance(self.sz, tuple) and (len(self.sz) == 2):
+                im = im.resize(self.sz, Image.ANTIALIAS)
+            self.data.append(np.asarray(im, dtype=np.uint8))

### 2013-03-15 code/preprocessing/facerec/feature.py

@@ -1,0 +1,265 @@
+import numpy as np
+
+class AbstractFeature(object):
+
+    def compute(self,X,y):
+        raise NotImplementedError("Every AbstractFeature must implement the compute method.")
+    
+    def extract(self,X):
+        raise NotImplementedError("Every AbstractFeature must implement the extract method.")
+        
+    def save(self):
+        raise NotImplementedError("Not implemented yet (TODO).")
+    
+    def load(self):
+        raise NotImplementedError("Not implemented yet (TODO).")
+        
+    def __repr__(self):
+        return "AbstractFeature"
+
+class Identity(AbstractFeature):
+    """
+    Simplest AbstractFeature you could imagine. It only forwards the data and does not operate on it, 
+    probably useful for learning a Support Vector Machine on raw data for example!
+    """
+    def __init__(self):
+        AbstractFeature.__init__(self)
+        
+    def compute(self,X,y):
+        return X
+    
+    def extract(self,X):
+        return X
+    
+    def __repr__(self):
+        return "Identity"
+
+
+from facerec.util import asColumnMatrix
+from facerec.operators import ChainOperator, CombineOperator
+        
+class PCA(AbstractFeature):
+    def __init__(self, num_components=0):
+        AbstractFeature.__init__(self)
+        self._num_components = num_components
+        
+    def compute(self,X,y):
+        # build the column matrix
+        XC = asColumnMatrix(X)
+        y = np.asarray(y)
+        # set a valid number of components
+        if self._num_components <= 0 or (self._num_components > XC.shape[1]-1):
+            self._num_components = XC.shape[1]-1
+        # center dataset
+        self._mean = XC.mean(axis=1).reshape(-1,1)
+        XC = XC - self._mean
+        # perform an economy size decomposition (may still allocate too much memory for computation)
+        self._eigenvectors, self._eigenvalues, variances = np.linalg.svd(XC, full_matrices=False)
+        # sort eigenvectors by eigenvalues in descending order
+        idx = np.argsort(-self._eigenvalues)
+        self._eigenvalues, self._eigenvectors = self._eigenvalues[idx], self._eigenvectors[:,idx]
+        # use only num_components
+        self._eigenvectors = self._eigenvectors[0:,0:self._num_components].copy()
+        self._eigenvalues = self._eigenvalues[0:self._num_components].copy()
+        # finally turn singular values into eigenvalues 
[…]

### 2013-03-15 code/preprocessing/facerec/lbp.py

@@ -1,0 +1,170 @@
+import numpy as np
+
+class LBPOperator(object):
+    def __init__(self, neighbors):
+        self._neighbors = neighbors
+
+    def __call__(self,X):
+        raise NotImplementedError("Every LBPOperator must implement the __call__ method.")
+        
+    @property
+    def neighbors(self):
+        return self._neighbors
+        
+    def __repr__(self):
+        return "LBPOperator (neighbors=%s)" % (self._neighbors)
+
+class OriginalLBP(LBPOperator):
+    def __init__(self):
+        LBPOperator.__init__(self, neighbors=8)
+    
+    def __call__(self,X):
+        X = np.asarray(X)
+        X = (1<<7) * (X[0:-2,0:-2] >= X[1:-1,1:-1]) \
+            + (1<<6) * (X[0:-2,1:-1] >= X[1:-1,1:-1]) \
+            + (1<<5) * (X[0:-2,2:] >= X[1:-1,1:-1]) \
+            + (1<<4) * (X[1:-1,2:] >= X[1:-1,1:-1]) \
+            + (1<<3) * (X[2:,2:] >= X[1:-1,1:-1]) \
+            + (1<<2) * (X[2:,1:-1] >= X[1:-1,1:-1]) \
+            + (1<<1) * (X[2:,:-2] >= X[1:-1,1:-1]) \
+            + (1<<0) * (X[1:-1,:-2] >= X[1:-1,1:-1])
+        return X
+        
+    def __repr__(self):
+        return "OriginalLBP (neighbors=%s)" % (self._neighbors)
+
+class ExtendedLBP(LBPOperator):
+    def __init__(self, radius=1, neighbors=8):
+        LBPOperator.__init__(self, neighbors=neighbors)
+        self._radius = radius
+        
+    def __call__(self,X):
+        X = np.asanyarray(X)
+        ysize, xsize = X.shape
+        # define circle
+        angles = 2*np.pi/self._neighbors
+        theta = np.arange(0,2*np.pi,angles)
+        # calculate sample points on circle with radius
+        sample_points = np.array([-np.sin(theta), np.cos(theta)]).T
+        sample_points *= self._radius
+        # find boundaries of the sample points
+        miny=min(sample_points[:,0])
+        maxy=max(sample_points[:,0])
+        minx=min(sample_points[:,1])
+        maxx=max(sample_points[:,1])
[…]

### 2013-03-15 code/preprocessing/facerec/preprocessing.py

@@ -1,0 +1,115 @@
+import numpy as np
+from facerec.feature import AbstractFeature
+from facerec.util import asColumnMatrix
+from scipy import ndimage
+    
+class HistogramEqualization(AbstractFeature):
+    def __init__(self, num_bins=256):
+        AbstractFeature.__init__(self)
+        self._num_bins = num_bins
+        
+    def compute(self,X,y):
+        Xp = []
+        for xi in X:
+            Xp.append(self.extract(xi))
+        return Xp
+        
+    def extract(self,X):
+        h, b = np.histogram(X.flatten(), self._num_bins, normed=True)
+        cdf = h.cumsum()
+        cdf = 255 * cdf / cdf[-1]
+        return np.interp(X.flatten(), b[:-1], cdf).reshape(X.shape)
+    
+    def __repr__(self):
+        return "HistogramEqualization (num_bins=%s)" % (self._num_bins)
+        
+class TanTriggsPreprocessing(AbstractFeature):
+    def __init__(self, alpha = 0.1, tau = 10.0, gamma = 0.2, sigma0 = 1.0, sigma1 = 2.0):
+        AbstractFeature.__init__(self)
+        self._alpha = float(alpha)
+        self._tau = float(tau)
+        self._gamma = float(gamma)
+        self._sigma0 = float(sigma0)
+        self._sigma1 = float(sigma1)
+    
+    def compute(self,X,y):
+        Xp = []
+        for xi in X:
+            Xp.append(self.extract(xi))
+        return Xp
+
+    def extract(self,X):
+        X = np.array(X, dtype=np.float32)
+        X = np.power(X,self._gamma)
+        X = np.asarray(ndimage.gaussian_filter(X,self._sigma1) - ndimage.gaussian_filter(X,self._sigma0))
+        X = X / np.power(np.mean(np.power(np.abs(X),self._alpha)), 1.0/self._alpha)
+        X = X / np.power(np.mean(np.power(np.minimum(np.abs(X),self._tau),self._alpha)), 1.0/self._alpha)
+        X = self._tau*np.tanh(X/self._tau)
+        return X
+
+    def __repr__(self):
+        return "TanTriggsPreprocessing (alpha=%.3f,tau=%.3f,gamma=%.3f,sigma0=%.3f,sigma1=%.3f)" % (self._alpha,self._tau,self._gamma,self._sigma0,self._sigma1)
+
+from facerec.lbp import ExtendedLBP
+
+class LBPPreprocessing(AbstractFeature):
+
[…]

### 2013-03-15 code/preprocessing/facerec/util.py

@@ -1,0 +1,81 @@
+import numpy as np
+import random
+from scipy import ndimage
+
+def read_image(filename):
+    imarr = np.array([])
+    try:
+        im = Image.open(os.path.join(filename))
+        im = im.convert("L") # convert to greyscale
+        imarr = np.array(im, dtype=np.uint8)
+    except IOError as (errno, strerror):
+        print "I/O error({0}): {1}".format(errno, strerror)
+    except:
+        print "Cannot open image."
+    return imarr
+
+def asRowMatrix(X):
+    """
+    Creates a row-matrix from multi-dimensional data items in list l.
+    
+    X [list] List with multi-dimensional data.
+    """
+    if len(X) == 0:
+        return np.array([])
+    total = 1
+    for i in range(0, np.ndim(X[0])):
+        total = total * X[0].shape[i]
+    mat = np.empty([0, total], dtype=X[0].dtype)
+    for row in X:
+        mat = np.append(mat, row.reshape(1,-1), axis=0) # same as vstack
+    return np.asmatrix(mat)
+
+def asColumnMatrix(X):
+    """
+    Creates a column-matrix from multi-dimensional data items in list l.
+    
+    X [list] List with multi-dimensional data.
+    """
+    if len(X) == 0:
+        return np.array([])
+    total = 1
+    for i in range(0, np.ndim(X[0])):
+        total = total * X[0].shape[i]
+    mat = np.empty([total, 0], dtype=X[0].dtype)
+    for col in X:
+        mat = np.append(mat, col.reshape(-1,1), axis=1) # same as hstack
+    return np.asmatrix(mat)
+
+
+def minmax_normalize(X, low, high, minX=None, maxX=None, dtype=np.float):
+    """ min-max normalize a given matrix to given range [low,high].
+    
+    Args:
+        X [rows x columns] input data
+        low [numeric] lower bound
+        high [numeric] upper bound
+    """
+    if minX is None:
+        minX = np.min(X)
+    if maxX is None:
+        maxX = np.max(X)
+    minX = float(minX)
+    maxX = float(maxX)
+    # Normalize to [0...1].    
+    X = X - minX
+    X = X / (maxX - minX)
+    # Scale to [low...high].
+    X = X * (high-low)
+    X = X + low
+    return np.asarray(X, dtype=dtype)
+
+def zscore(X):
+    X = np.asanyarray(X)
+    mean = X.mean()
+    std = X.std() 
[…]

### 2013-03-15 code/preprocessing/facerec/validation.py

@@ -1,0 +1,408 @@
+import numpy as np
+import math as math
+import random as random
+import logging
+
+from facerec.model import PredictableModel
+from facerec.classifier import AbstractClassifier
+
+def shuffle(X, y):
+    """ Shuffles two arrays by column (len(X) == len(y))
+        
+        Args:
+        
+            X [dim x num_data] input data
+            y [1 x num_data] classes
+
+        Returns:
+
+            Shuffled input arrays.
+    """
+    idx = np.argsort([random.random() for i in xrange(len(y))])
+    y = np.asarray(y)
+    X = [X[i] for i in idx]
+    y = y[idx]
+    return (X, y)
+
+def slice_2d(X,rows,cols):
+    """
+    
+    Slices a 2D list to a flat array. If you know a better approach, please correct this.
+    
+    Args:
+    
+        X [num_rows x num_cols] multi-dimensional data
+        rows [list] rows to slice
+        cols [list] cols to slice
+    
+    Example:
+    
+        >>> X=[[1,2,3,4],[5,6,7,8]]
+        >>> # slice first two rows and first column
+        >>> Commons.slice(X, range(0,2), range(0,1)) # returns [1, 5]
+        >>> Commons.slice(X, range(0,1), range(0,4)) # returns [1,2,3,4]
+    """
+    return [X[i][j] for j in cols for i in rows]
+
+class Validation(object):
+    """ Represents a generic Validation kernel for all Validation strategies.
+    
+    Attributes:
+
+        (tp,...,fns)    [int]        Validation results
+        accuracy        [float]     Accuracy over all runs.
+        std_accuracy    [float]     stddev over all runs.
+        runs            [int]         Runs performed for this validation.
+        
+    """
+    def __init__(self, model):
+        """    
+        Initialize validation with empty results.
+        """
+        # make sure we can predict on this one
+        if not isinstance(model,PredictableModel):
+            raise TypeError("Validation can only validate the type PredictableModel.")
+        self.model = model
+        self._results = np.empty((0,4), np.int)
+    
+    def add(self, result):
+        """ Adds a validation result [tp,fp,tn,fn] to this Validation object.
+        
+        Args:
+        
+            result [list] [tp, fp, tn, fn]
+        """
+        if len(result) != 4:
+            return
+        self._results = np.vstack((self._results, result))
+        
[…]

### 2013-03-15 code/preprocessing/facerec/visual.py

@@ -1,0 +1,81 @@
+from facerec.normalization import minmax
+
+import os as os
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+import PIL.Image as Image
+
+import math as math
+
+
+def create_font(fontname='Tahoma', fontsize=10):
+    return { 'fontname': fontname, 'fontsize':fontsize }
+
+def plot_gray(X,  sz=None, filename=None):
+    if not sz is None:
+        X = X.reshape(sz)
+    X = minmax(I, 0, 255)
+    fig = plt.figure()
+    implot = plt.imshow(np.asarray(Ig), cmap=cm.gray)
+    if filename is None:
+        plt.show()
+    else:
+        fig.savefig(filename, format="png", transparent=False)
+    
+def plot_eigenvectors(eigenvectors, num_components, sz, filename=None, start_component=0, rows = None, cols = None, title="Subplot", color=True):
+        if (rows is None) or (cols is None):
+            rows = cols = int(math.ceil(np.sqrt(num_components)))
+        num_components = np.min(num_components, eigenvectors.shape[1])
+        fig = plt.figure()
+        for i in range(start_component, num_components):
+            vi = eigenvectors[0:,i].copy()
+            vi = minmax(np.asarray(vi), 0, 255, dtype=np.uint8)
+            vi = vi.reshape(sz)
+            
+            ax0 = fig.add_subplot(rows,cols,(i-start_component)+1)
+            
+            plt.setp(ax0.get_xticklabels(), visible=False)
+            plt.setp(ax0.get_yticklabels(), visible=False)
+            plt.title("%s #%d" % (title, i), create_font('Tahoma',10))
+            if color:
+                implot = plt.imshow(np.asarray(vi))
+            else:
+                implot = plt.imshow(np.asarray(vi), cmap=cm.grey)
+        if filename is None:
+            fig.show()
+        else:
+            fig.savefig(filename, format="png", transparent=False)
+            
+def subplot(title, images, rows, cols, sptitle="subplot", sptitles=[], colormap=cm.gray, ticks_visible=True, filename=None):
+    fig = plt.figure()
+    # main title
+    fig.text(.5, .95, title, horizontalalignment='center') 
+    for i in xrange(len(images)):
+        ax0 = fig.add_subplot(rows,cols,(i+1))
[…]

### 2013-03-15 code/preprocessing/preprocessing.py

@@ -1,0 +1,104 @@
+"""
+Python module for preprocessing images to make them lighting invariant.
+The module is for use with experiments using descriptors such as BRIEF
+and ORB.
+
+The code is adapted from different sources. This is marked in the
+descriptions of the individual functions.
+
+Jonas Toft Arnfred, 2013-03-07
+"""
+
+####################################
+#                                  #
+#            Imports               #
+#                                  #
+####################################
+
+import numpy
+from scipy import ndimage
+from pylab import imshow
+
+
+####################################
+#                                  #
+#           Functions              #
+#                                  #
+####################################
+
+def stretch(im) :
+	""" Stretches the histogram of an image.
+	    Input: im [numpy.ndarray] Image in uint or float format
+		Output: [numpy.ndarray] Float version of the input image
+	                            normalized between 0 and 1
+	"""
+	im_float = numpy.array(im - numpy.min(im), numpy.float32)
+	return im_float / numpy.max(im_float)
+
+
+
+def toUInt(im) :
+	""" Converts a floating point image to integer image between 0 and 255
+	    Input: im [numpy.ndarray] Image in uint or float format
+	    Output: [numpy.ndarray] integer version of the image
+	"""
+	stretched = stretch(im)
+	return numpy.array(numpy.floor(stretched*255), numpy.uint8)
+
+
+
+def faceNorm(im, contrast = 0.2) :
+	""" Calculates a lighting neutral image
+	    Input: im [numpy.ndarray] Image in whatever format
+		Output: [numpy.ndarray] UINT version of image
+	"""
+	alpha = 0.1
+	tau = 10.0
+	gamma = 0.2
+	sigma1 = 1.0
+	sigma2 = 3.0
+
+	im = stretch(im)
+	c = ndimage.gaussian_filter(im, sigma1)
+	s = ndimage.gaussian_filter(im, sigma2)
+	q = numpy.asarray(c - s)
+	w = numpy.asarray(c+s+0.000001)
+	nDoG = q/w
+
+	A = contrast # The smaller the greater the enhancement
+	B = 1
+	w = nDoG*(A+B)
+	ww = numpy.abs(nDoG)+A
+	cenDoG = w/ww
+
+	return toUInt(cenDoG)
+
+
+
+def invert(im) :
[…]

### 2013-04-16 code/display.py
A lot of changes and new tests

@@ -18,10 +18,13 @@ import cv2
 import pylab
 import numpy
 import graph_tool.all as gt
-import cluster
+import math
+import louvain
+import weightMatrix
 from scipy.misc import imresize
 import Image
 from itertools import combinations, groupby, tee, product, combinations_with_replacement
+from sklearn import metrics
 
 
 ####################################
@@ -37,22 +40,13 @@ def appendimages(im1, im2) :
 
 
 
-def getPositions(keypoints) : 
-    pos = numpy.zeros([len(keypoints), 2])
-    for i in range(len(keypoints)) :
-        pos[i][0] = keypoints[i].pt[0]
-        pos[i][1] = keypoints[i].pt[1]
-    return pos
 
 
 
-def keypoints(im, locs) :
+def keypoints(im, pos) :
 	""" show image with features. input: im (image as array), 
 	    locs (row, col, scale, orientation of each feature) 
 	"""
-	# Extract positions from keypoints
-	pos = getPositions(locs)
-
 	# Plot all keypoints
 	pylab.gray()
 	pylab.imshow(im)
@@ -65,37 +59,30 @@ def compareKeypoints(im1, im2, pos1, pos2) :
 	""" Show two images next to each other with the keypoints marked
 	"""
 
-	print(pos1)
-	print(pos2)
-
 	# Construct unified image
 	im3 = appendimages(im1,im2)
 
 	# Find the offset and add it
 	offset = im1.shape[1]
-	pos2[:,1] = pos2[:,1] + offset
+	pos2_o = [(x+offset,y) for (x,y) in pos2]
 
 	# Show images
 	pylab.gray()
 	pylab.imshow(im3)
-	pylab.plot([p[1] for p in pos1], [p[0] for p in pos1], '.b')
-	pylab.plot([p[1] for p in pos2], [p[0] for p in pos2], '.b')
+	pylab.plot([x for x,y in pos1], [y for x,y in pos1], '.b')
+	pylab.plot([x for x,y in pos2_o], [y for x,y in pos2_o], '.b')
 	pylab.axis('off')
 	pylab.show()
 
 
 
-def matches(im1, im2, locs1, locs2, matchpos) :
+def matches(im1, im2, pos1, pos2, matchpos) :
 	""" show a figure with lines joining the accepted matches in im1 and im2
 	    input: im1,im2 (images as arrays), locs1,locs2 (location of features), 
[…]

### 2013-04-16 code/evaluate.py

@@ -42,11 +42,13 @@ def imageToImage(images, paths, keypoint_type, descriptor_type, score_fun = lamb
 	"""
 
 	# Get keypoints
-	keypoints = map(lambda i : f.getKeypoints(keypoint_type, i), images)
+	#keypoints = map(lambda i : f.getKeypoints(keypoint_type, i), images)
 
 	# Get descriptors
-	data = map(lambda i,k : f.getDescriptors(descriptor_type, i, k), images, keypoints)
-	keypoints, descriptors = zip(*data)
+	#data = map(lambda i,k : f.getDescriptors(descriptor_type, i, k), images, keypoints)
+	data = [f.getFeatures([p],keypoint_type, descriptor_type) for p in paths]
+	
+	indices, keypoints, descriptors = zip(*data)
 
 	# Return the scores labeled with a boolean to indicate if they are of same set
 	return matchDescriptors(descriptors, paths, descriptor_type, score_fun)
@@ -55,10 +57,21 @@ def imageToImage(images, paths, keypoint_type, descriptor_type, score_fun = lamb
 
 def matchDescriptors(descriptors, paths, descriptor_type, score_fun) :
 
+	default_map = {
+		"SIFT"   : 1,
+		"SURF"   : 1,
+		"ORB"    : 100,
+		"BRISK"  : 100,
+		"BRIEF"  : 100,
+		"FREAK"  : 100
+	}
+
 	def filterNone(l) : return [i for i in l if i != None]
 	def getScore(D1, D2, i) :
-		if (i % 100 == 0) : sys.stdout.write('#')
+		if D1 == None or D2 == None : return default_map[descriptor_type]
 		indices, scores, uniques = f.bfMatch(descriptor_type, D1, D2)
+		if indices == None : return default_map[descriptor_type]
+
 		noNones = map(filterNone, [indices, scores, uniques])
 		return score_fun(*noNones)
 

### 2013-04-16 code/features.py

@@ -39,7 +39,7 @@ supported_descriptor_types = ["SIFT","SURF","ORB","BRISK","BRIEF","FREAK"]
 ####################################
 
 
-def getFeatures(paths, size=32) :
+def getFeatures(paths, keypoint_type = "ORB", descriptor_type = "BRIEF", size=32) :
 	""" Given a list of paths to images, the function returns a list of 
 	    descriptors and keypoints
 		Input: paths [list of strings] The paths to the images we are using
@@ -50,9 +50,11 @@ def getFeatures(paths, size=32) :
 	images = map(loadImage, paths)
 
 	# Get feature descriptors
-	#keypoints = [features.getKeypoints(feature_keypoint, im) for im in images]
-	keypoints = [getORBKeypoints(im, size) for im in images]
-	data = [getDescriptors(feature_descriptor, im, k) for (im, k) in zip(images, keypoints)]
+	keypoints = [getKeypoints(keypoint_type, im) for im in images]
+	#for k in numpy.concatenate(keypoints) :
+	#	k.size = float(size)
+	#keypoints = [getORBKeypoints(im, size) for im in images]
+	data = [getDescriptors(descriptor_type, im, k) for (im, k) in zip(images, keypoints)]
 	keypoints, descriptors = zip(*data)
 
 	# Check that we could get descriptors for all images
@@ -79,11 +81,13 @@ def getKeypoints(keypoint_type, image, params = {}) :
 	return feature.detect(image)
 
 
-def getORBKeypoints(image, size=32) :
+def getORBKeypoints(image, size=[32]) :
+	if isinstance(size, (int, long)) : size = [size]
 	#o = cv2.ORB(nfeatures=2000, scaleFactor=1.06, nlevels=15, edgeThreshold=n, patchSize=n)
-	o = cv2.ORB(nfeatures=2000, scaleFactor=1.06, nlevels=12, edgeThreshold=size, patchSize=size)
+	os = [cv2.ORB(nfeatures=2000, scaleFactor=1.06, nlevels=15, edgeThreshold=s, patchSize=s) for s in size]
+	kpts = [kpt for o in os for kpt in o.detect(image)]
 	#o = cv2.ORB(nfeatures=2000, scaleFactor=1.06, nlevels=12, edgeThreshold=35, patchSize=35)
-	return o.detect(image)
+	return kpts
 
 
[…]

### 2013-04-16 code/graph.py

@@ -15,7 +15,6 @@ import pylab
 import numpy
 import display
 import features
-import weightMatrix
 import math
 import louvain
 from itertools import combinations, groupby, tee, product, combinations_with_replacement, dropwhile
@@ -71,30 +70,27 @@ def getDescriptors(paths, size=32) :
 
 	# Check that we could get descriptors for all images
 	if sum(map(lambda d : d == None, descriptors)) > 0 : return (None, None, None)
-	indices = [l for i,n in zip(range(len(labels)), map(len, descriptors)) for l in [i]*n]
-	return (indices, numpy.concatenate(keypoints), numpy.concatenate(descriptors))
+	return (numpy.concatenate(keypoints), numpy.concatenate(descriptors))
 
 
 
 def setPositions(graph, keypoints) :
 
-	positions = features.getPositions(keypoints)
+	positions = display.getPositions(keypoints)
 
-	pos_x = graph.new_vertex_property("float")
-	pos_y = graph.new_vertex_property("float")
-	for v in graph.vertices() : 
-		pos_x[v] = positions[graph.vertex_index[v]][0]
-		pos_y[v] = positions[graph.vertex_index[v]][1]
+	posMap = graph.new_vertex_property("vector<float>")
+	for v in graph.vertices() : posMap[v] = positions[graph.vertex_index[v]]
 
 	# Save weights as a graph property
-	graph.vertex_properties["x"] = pos_x
-	graph.vertex_properties["y"] = pos_y
+	graph.vertex_properties["positions"] = posMap
 
 	return graph
 
 
 
-def setFeatureIndices(graph, indices) :
+def setIndices(graph, paths) :
+
+	indices = getIndices(paths)
 
 	# Create indicemap
 	ind = graph.new_vertex_property("int")
@@ -110,7 +106,7 @@ def setFeatureIndices(graph, indices) :
 
 
 
-def getImageIndices(paths) : 
+def getIndices(paths) : 
     labels = map(features.getLabel, paths)
     i = 0
     d = {}
@@ -122,7 +118,7 @@ def getImageIndices(paths) :
 
 
 
-def init(weights) :
+def initGraph(weights) :
 
 	# This is a faster way to initialize a graph. It's not random.
 	N = weights.shape[0]
@@ -135,6 +131,23 @@ def init(weights) :
[…]

### 2013-04-16 code/louvain.py

@@ -25,42 +25,69 @@ import numpy
 
 
 def cluster(weights, verbose=False) :
-    indices = numpy.arange(0, weights.shape[0])
-    partitions = indices.copy()
-    K = numpy.sum(weights)
-    moved = 1
-    while (moved > 0) :
-        moved = sum([move(weights, i, partitions, K) for i in indices])
-        if verbose : print("Moved %i vertices" % moved)
-    return partitions
+	indices = numpy.arange(0, weights.shape[0])
+	partitions = indices.copy()
+	K = numpy.sum(weights)
+	moved = 1
+	m = 0
+	while (moved > 0) :
+		deltas = [move(weights, i, partitions, K) for i in indices]
+		moved = sum([1 if d > 0 else 0 for d in deltas])
+		if verbose : 
+			m_new = modularity(weights, partitions)
+			m_diff = m_new - m
+			m = m_new
+			print("Moved %i vertices (modularity now: %.4f, change of %.4f)" % (moved,m,m_diff))
+	return partitions
 
 
 def move(weights, index, partitions, K) :
-    # Move out of partition
-    old_partition = partitions[index]
-    partitions[index] = -1
-    # See how much we would gain from moving p back to orig_partition
-    lost_Q = deltaQ(weights, index, (old_partition == partitions), K)
-    # What is the best gain elsewhere?
-    prospects = set(partitions[numpy.nonzero(weights[index])])
-    prospect_Q = [(deltaQ(weights, index, (p == partitions), K), p) for p in prospects]
-    max_gained_Q = max(prospect_Q) if (len(prospect_Q) > 0) else (-1,-1)
-    # Is it worth moving?
-    delta = max_gained_Q[0] - lost_Q
-    if (delta > 0) : 
-        partitions[index] = max_gained_Q[1]
-        return 1
-    else : 
-        partitions[index] = old_partition
-        return 0
+	# Move out of partition
+	old_partition = partitions[index]
+	partitions[index] = -1
+	# See how much we would gain from moving p back to orig_partition
+	lost_Q = deltaQ(weights, index, (old_partition == partitions), K)
+	# What is the best gain elsewhere?
+	prospects = set(partitions[numpy.nonzero(weights[index])])
+	prospect_Q = [(deltaQ(weights, index, (p == partitions), K), p) for p in prospects]
[…]

### 2013-04-16 code/scoring.py

@@ -24,44 +24,53 @@ import math
 ####################################
 
 
-def scoreImages(paths, cluster_edges = 3, score_edges = 20, scoring = lambda m,c : m + c if c > 0 else 0.0, default_val = 0.0) :
-	""" Given paths to two images, the images are scored based on how 
-	    well their traits match
-	"""
-	# Get features
-	indices, keypoints, descriptors = features.getFeatures(paths, size=32)
-	if descriptors == None :
-		print(paths)
-		print("No descriptors found. Returning score %i" % default_val)
-		return default_val
 
-	# Get weights
-	full_weights = weightMatrix.init(descriptors)
-	score_weights = weightMatrix.pruneTreshold(full_weights, score_edges)
-	cluster_weights = weightMatrix.pruneHighest(score_weights, cluster_edges)
+def scoreWeights_2(weights, partitions, image_indices, scoring = lambda m,c : m + c if c > 0 else 0.0, verbose=False) :
 
-	# Cluster graph
-	partitions = louvain.cluster(cluster_weights)
+	def printResult(i, bipartite, isolate, w) : 
+		print("[%i]" % i + "\tbipartite: %+0.4f" % bipartite + ", isolate: %+0.4f" % isolate + ", ratio: %0.4f" % (isolate/bipartite) + ", weight: %0.2f" % w)
+	
+	def in_range(partition_mask, image_masks) :
+		return (image_masks[1].sum() > 1 and image_masks[0].sum() > 1)
 
-	# Match the traits
-	scores, cluster_indices = scoreWeights(score_weights, partitions, indices, scoring=scoring)
+	def score(index, im_masks, partition_mask, weight) :
 
-	# Get labels
-	[l1, l2] = [features.getLabel(p) for p in paths]
+		partition_weights = weights[partition_mask][:, partition_mask]
+		bipartite_weights = partition_weights[im_masks[0]][:,im_masks[1]]
+		isolated_weights_im0 = partition_weights[im_masks[0]][:,im_masks[0]]
+		isolated_weights_im1 = partition_weights[im_masks[1]][:,im_masks[1]]
+		isolated_sum = numpy.sum(isolated_weights_im0) + numpy.sum(isolated_weights_im1)
+		isolated_nb = numpy.sum(isolated_weights_im0 != 0.0) + numpy.sum(isolated_weights_im1 != 0.0)
[…]

### 2013-04-16 code/weightMatrix.py

@@ -12,6 +12,7 @@ Jonas Toft Arnfred, 2013-03-19
 ####################################
 
 import numpy
+import math
 from itertools import dropwhile
 
 
@@ -39,35 +40,59 @@ def init(descriptors) :
 
 
 
-def get_treshold(weights, edges_per_vertex) :
-	n = 300
+def get_treshold(weights, edges_per_vertex, n=300, start=0.3) :
 	nb_vertices = weights.shape[0]
-	tresholds = numpy.linspace(1,0.3,n)
+	tresholds = numpy.linspace(1,start,n)
 	w = [numpy.sum(weights > t) / (2.0*nb_vertices) for t in tresholds]
 	q = dropwhile(lambda e : e < edges_per_vertex, w)
 	index = len(list(q))
-	if (index <= 0) : return 0.3
+	if (index <= 0) : return start
 	if (index >= n) : return 1
 	return tresholds[n-index]
 
 
 
-def pruneHighest(weights, edges_per_vertex) :
+def get_fraction(weights, fraction, n=300, start=0.3) :
+	tresholds = numpy.linspace(1,start,n)
+	nb_weights = float(weights.size)
+	w = [numpy.sum(weights > t) / nb_weights for t in tresholds]
+	q = dropwhile(lambda e : e < fraction, w)
+	index = len(list(q))
+	if (index <= 0) : return start
+	if (index >= n) : return 1
+	return tresholds[n-index]
+
+
+
+def pruneFraction(weights, fraction, n=500, start=0.0) :
+	# Get treshold
+	treshold = get_fraction(weights, fraction, n=n, start=start)
+
+	# Update weight matrix
+	index = (weights <= treshold) | (weights == 1)
+	pruned_weights = weights.copy()
+	pruned_weights[index] = 0
+
+	return pruned_weights
+
+
+
+def pruneHighest(weights, edges_per_vertex,n=0,start=0) :
 	weights_triu = numpy.triu(weights)
 	new_weights = numpy.zeros(weights.shape)
-	for i,row in enumerate(weights_triu) :
+	for i,row in enumerate(weights) :
 		indices = row.argsort()[(-1*edges_per_vertex):]
 		new_weights[i,indices] = row[indices]
-	new_weights = new_weights + new_weights.T
+	new_weights[new_weights==0] += new_weights.T[new_weights==0]
 	return new_weights
[…]

### 2013-04-16 text/clustering.tex
Added a bit of info on clustering

\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[stable]{footmisc}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{subcaption}

\begin{document}

\title{Clustering feature points}
\author{Jonas Arnfred}

\maketitle

\begin{abstract}
% TODO!
\end{abstract}

\section{Project description}

Traditionally the feature points of two images have been matched by 
comparing the feature points individually and finding the best matches 
based on their distance. This approach was originally introduced with 
the SIFT features \cite{lowe2004sift} and has been used since then in 
computer vision applications such as scene recognition\footnote{See for 
example chapter 4.1.3 of \cite[pp. 226]{szeliski2010}} and image 
alignment\footnote{An example is the gold standard algorithm in \cite[p.  
114]{multipleView}}. In larger scale approaches where an image is 
compared with thousands or millions of other images, the feature points 
are usually indexed in a dictionary of visual words instead. This 
approach makes it possible to quickly retrieve matches in a large set of 
potential candidates, but the performance is restricted by how 
discriminative the individual feature points are. To agument the 
descriminative power of the feature points, \cite{wu2009bundling} 
proposes grouping the features and use the geometrical relationships 
between members of a group when matching two feature points. Similarly 
\cite{das2008event} use geometrical information about the feature points 
to cluster them before doing scene matching resulting in better matches.

Both methods suffer from two shortcomings. Firstly we have that any 
defined group in one image might not correspond to a group in another 
image.  This means that we might end up in a situation where a good 
match between two images is scored low because most of it's geometric 
neighbors are in an adjecent group. Secondly if we intent to match the 
different groups as in \cite{wu2009bundling} we might end up matching 
two mismatching groups. To improve geometric matching I propose pooling 
the keypoints from two images into one set and partitioning them into 
groups together.  The advantages of this approach is that groups are 
consistent across images, and that keypoints from one image that don't 
have equivalents in the other image will simply be grouped in their own 
group which can easily be discarded during the matching.

\subsection{Graph Clustering}

Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
{k_i, k_j for k_i \in im_1, k_j \in im_2}$ as well as a matching 
function $M(k_i, k_j) \rightarrow \mathbb{N}$ that takes two feature 
points in an image and return their matching score, we can define a 
matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
as the \emph{adjecency matrix} of the fully connected graph where each 
vertex corresponds to a keypoint and the edge between two vertices has a 
weight equal to the distance between the two corresponding keypoints.

This representation reduces the problem of partitioning the keypoints 
into groups reduces the problem to that of graph clustering or community 
structure depending on the context. In the litterature there are various 
ways of clustering a graph according to different measures of what 
constitutes an optimal partitioning. Traditionally the most used 
clustering algorithms have been K-means and spectral clustering, but in 
recent years a host of new algorithms have been proposed based on both 
Newman's concept of graph modularity\footnote{Introduced in 
\cite{girvan2002}, discussed in \cite{brandes2007} and used in 
\cite{blondel2008} as well as others} as well as information theoretical 
measures\footnote{See for example \cite{rosvall2008}} and the Potts spin 
model from physics\footnote{Used in \cite{ronhovde2009}} just to mention 
a few approaches. Many of the new algorithms differ from K-means 
clustering and Spectral clustering in that they don't require the number 
of expected to clusters to be specified beforehand\footnote{Among the 
aforementioned methods, this is true for \cite{blondel2008} and 
\cite{rosvall2008}}.  Furthermore, on tests done using randomly 
generated graphs with a known partitioning \cite{blondel2008}, 
\cite{rosvall2008} and \cite{ronhovde2009} perform markedly better than 
spectral clustering and K-means\cite{lancichinetti2009}.

The performance of clustering algorithms is a complicated issue, since 
an optimal clustering given the same graph can vary depending on the 
application. Spectral clustering for example will usually return a 
partitioning where each partition is roughly equal in size\footnote{As 
mentioned in \cite{von2007}} while the Louvain 
clustering\cite{blondel2008} might return partitions of very uneven 
size, even if the modularity measurement has been shown to penalize very 
small clusters\cite{brandes2007}. Both behaviours can be beneficial 
depending on the application, but when clustering feature points, 
maintaining clusters of an even size usually means that a few clusters 
will be '\emph{catch-all}' clusters where the feature points that don't 
fit anywhere else are grouped together. The necessity of specifying the 
amount of partitions in for example Spectral clustering or Pott's model 
clustering further exacerbates the issue since smaller partitions are 
then combined into one to achieve the right amount of partitions.

Based on these

### 2013-04-16 code/graph.py

@@ -1,302 +1,0 @@
-"""
-Python module for use with OpenCV to cluster descriptors from several images.
-
-Jonas Toft Arnfred, 2013-03-19
-"""
-
-####################################
-#                                  #
-#            Imports               #
-#                                  #
-####################################
-
-import cv2
-import pylab
-import numpy
-import display
-import features
-import math
-import louvain
-from itertools import combinations, groupby, tee, product, combinations_with_replacement, dropwhile
-import graph_tool.all as gt
-
-
-
-####################################
-#                                  #
-#           Properties             #
-#                                  #
-####################################
-
-feature_keypoint = "ORB"
-feature_descriptor = "BRIEF"
-N = 600
-
-
-####################################
-#                                  #
-#           Functions              #
-#                                  #
-####################################
-
-
-
-def cluster(graph, nb_clusters=20, iter=100, gamma=1.0, corr="erdos", verbose=False) :
-
-	# Get weights (throws an error if they don't exist)
-	weights = graph.edge_properties["weights"]
-
-	clusters = gt.community_structure(graph, iter, nb_clusters, weight=weights, gamma=gamma, corr=corr, verbose=verbose)
-	t = [(k, len(list(g))) for k,g in groupby(sorted(clusters.fa))]
-	return clusters, len(t)
-
-
-
-def getDescriptors(paths, size=32) :
-	""" Given a list of paths to images, the function returns a list of 
-	    descriptors and keypoints
-		Input: paths [list of strings] The paths to the images we are using
-		Out:   [pair of list of descriptors and list of keypoints]
-	"""
-	# Get all images and labels
-	labels = map(features.getLabel, paths)
-	images = map(features.loadImage, paths)
-
-	# Get feature descriptors
-	#keypoints = [features.getKeypoints(feature_keypoint, im) for im in images]
-	keypoints = [features.getORBKeypoints(im, size) for im in images]
-	data = [features.getDescriptors(feature_descriptor, im, k) for (im, k) in zip(images, keypoints)]
-	keypoints, descriptors = zip(*data)
[…]

### 2013-04-16 text/clustering.tex
Added a bit of information to the clustering part

@@
 \usepackage{subcaption}
+\usepackage{algpseudocode}
+\usepackage{algorithm}
+\usepackage{amsmath}
+\usepackage{amssymb}
 
@@
 have equivalents in the other image will simply be grouped in their own 
-group which can easily be discarded during the matching.
+group which can easily be discarded during the matching. This is 
+important for scene recognition where people might obscure details in 
+the picture. In addition the proposed method generalizes to three or 
+more images.  This makes it possible to easily assemble a set of 
+partially overlapping pictures without any required knowledge of their 
+position.  What's more, if one of the pictures in there is not part of 
+the set, the features of the odd image out will not form clusters with 
+the features of the other images and automatically be sorted out.
 
@@
 Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-{k_i, k_j for k_i \in im_1, k_j \in im_2}$ as well as a matching 
-function $M(k_i, k_j) \rightarrow \mathbb{N}$ that takes two feature 
+\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
+function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
 points in an image and return their matching score, we can define a 
@@
 depending on the application, but when clustering feature points, 
-maintaining clusters of an even size usually means that a few clusters 
+maintaining clusters of an even size usually means that some clusters 
 will be '\emph{catch-all}' clusters where the feature points that don't 
@@
 
-Based on these
+Based on these observations I've decided to use Louvain clustering for 
+grouping feature points since it's fast, performs well, doesn't require 
+parameters and doesn't emphasize partitions of equal sizes.
+
+\subsection{Clustering feature points using Louvain clustering}
+
+\begin{algorithm}
+\caption{Louvain-Match Algorithm}
+\label{alg-simple}
+\begin{algorithmic}
+\Require $images$ : set of images, $n$ : int $\in \mathbb{N}$
+\State $matches\gets \varnothing$
+\ForAll{$I_i \in images$} \Comment Gather features of all images
+	\State $f_i\gets getFeatures(I_i)$
+\EndFor
+\State $A\gets getAdjecencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
+\State $A_{norm}\gets 1 - normalize(A)$
+\Comment Shorter distance is higher weight
+\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
+\State $P\gets cluster(A_{pruned})$ 
+\Comment P is a set of partitions
+\ForAll{$p \in P$} \Comment p is a set of feature points
+	\State $trait\gets \left\{p \cap f_i \mid p \cap f_i \neq 
+\varnothing, f_i \in \left\{f_1, f_2,\; \ldots \;, f_n\right\}\right\}$
+	\If{$\left\vert trait \right\vert > 1$}
+		\State $matches\gets getPositions(trait)$
+		\Comment Position of trait in each image
+	\EndIf
+\EndFor \\
+\Return matches
+\end{algorithmic}
+\end{algorithm}
+
+Algorithm \ref{alg-simple} shows the basic steps taken to find matches 
+in two or more images. This algorithm is a simplified version of the 
+proposed method completely agnostic of the geometry of the feature 
+points in the picture. To better explain the algorithm here is an 
+overview over the inputs and functions mentioned and how they work:
+\begin{itemize}
+\item[]{\emph{images}: The images we are matching}
+\item[]{\emph{$n$}: The number of weights per row in the adjecency 
+matrix}
+\item[]{\emph{getFeatures}: Returns a set of feature points given an 
+image. The type of feature point is not theoretically important, but in 
+practice the BRIEF\cite{calonder2010brief} feature point detector and 
+descriptor has worked well} 
+% TODO: include a comparison of SURF, SIFT, etc
+\item[]{\emph{getAdjecencyMatrix}: Based on the distance measure used to 
+compare the similarity of the feature points a symmetric adjecency 
+matrix is returned}
+\item[]{\emph{pruneEdges}: The result of the Louvain clustering depends 
+on the density of the graph. To ensure an optimal number of partitions 
+we only keep the $n$ highest weights per row and column in the adjecency 
+matrix, making sure it's still symmetric afterwards. In practice setting 
+$n$ to around four or five usually yields good results}
+\item[]{\emph{cluster}: Cluster the graph corresponding to the adjecency 
+matrix given using the Louvain algorithm in \cite{blondel2008}}
+\item[]{\emph{getPositions}: Given a trait consisting of features in 
+several different images, find the positions of traits in each image and 
+return them. This could either be done by taking a mean of the feature 
+points in an image, or by returning the position of the highest matching 
+feature points within the trait. In practice ... TODO}
+\end{itemize}
+
+\begin{algorithm}
+\caption{Louvain-Match Algorithm With Geometry}
+\label{alg-geometry}
+\begin{algorithmic}
+\Require $images$ : set of images, $\alpha$ : float $\in \left[0, 
+1\right]$, $\beta$ : float $\in \left[0, 1\right]$
+\State $matches\gets \varnothing$
+\ForAll{$I_i \in images$} \Comment Gather features of all images
+	\State $f_i\gets getFeatures(I_i)$
+\EndFor
+\State $A\gets getAdjecencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
+\State $B\gets getGeomDistanceMatrix(f_1, f_2,\; \ldots \;, f_n)$
+\State $M\gets getInterImageMask(f_1, f_2,\; \ldots \;, f_n)$
+\State $B_{norm}\gets 1 - normalize(G)$ \State $A_{norm}\gets 1 - 
+normalize(A)$
+\State $A_{geom}\gets A_{norm}\left[ \neg M\right] + \beta \cdot 
+B_{norm}\left[M\right]$
+\State $A_{pruned}\gets pruneEdges(A_{geom},\alpha)$
+\State $P\gets cluster(A_{pruned})$ 
+\ForAll{$p \in P$}
+	\State $trait\gets \left\{p \cap f_i \mid p \cap f_i \neq 
+\varnothing, f_i \in \left\{f_1, f_2,\; \ldots \;, f_n\right\}\right\}$
+	\If{$\left\vert trait \right\vert > 1$}
+		\State $matches\gets getPositions(trait)$
+		\Comment Position of trait in each image
+	\EndIf
+\EndFor \\
+\Return matches
+\end{algorithmic}
+\end{algorithm}
+
+While clustered feature points are often geometrically close together, 
+there might be cases where several points in the same image are similar 
+enough to all be included in one cluster despite their geometrical 
+distance.  To solve this problem we can either modify the clustering 
+algorithm to take the geometric distances into account like 
+\cite{das2008event}.  Alternatively we can modify the weight matrix to 
+penalize putting distanced feature points in the same cluster. However 
+we only know the geometrical distance between two feature points as long 
+as both belong to the same image. One way to approach this problem is to 
+replace all the weights of edges between two feature points within the 
+same image with their distance. For the case of two images the original 
+adjecency matrix is defined as follows:
+%
+$$A=
+\begin{bmatrix}
+w_{1,1}   & w_{1,2}   & \ldots & w_{1,n-1}   & w_{1,n}     \\
+w_{2,1}   & w_{2,2}   & \ldots & w_{2,n-1}   & w_{2,n}     \\
+\vdots    & \vdots    & \ddots & \vdots      & \vdots      \\
+w_{n-1,1} & w_{n-1,2} & \ldots & w_{n-1,n-1} & w_{n-1,n}   \\
+w_{n,1}   & w_{n,2}   & \ldots & w_{n,n-1}   & w_{n,n}
+\end{bmatrix}=
+\begin{bmatrix}
+A_{im1} & S       \\
+T       & A_{im2} \\
+\end{bmatrix}
+$$
+%
+In a similar manner we can define an adjecency matrix based on the 
+geometrical distance. Note how for example $d_{1,n}$ doesn't contain any 
+sensible information.
+%
+$$B=
+\begin{bmatrix}
+d_{1,1}   & d_{1,2}   & \ldots & d_{1,n-1}   & d_{1,n}     \\
+d_{2,1}   & d_{2,2}   & \ldots & d_{2,n-1}   & d_{2,n}     \\
+\vdots    & \vdots    & \ddots & \vdots      & \vdots      \\
+d_{n-1,1} & d_{n-1,2} & \ldots & d_{n-1,n-1} & d_{n-1,n}   \\
+d_{n,1}   & d_{n,2}   & \ldots & d_{n,n-1}   & d_{n,n}
+\end{bmatrix}=
+\begin{bmatrix}
+B_{im1} & R       \\
+Q       & B_{im2} \\
+\end{bmatrix}
+$$
+%
+Given these two and a weight factor $\beta$ we can construct a new 
+weight matrix as follows:
+%
+$$C=
+\begin{bmatrix}
+\beta \cdot B_{im1} & S       \\
+T       & \beta \cdot B_{im2} \\
+\end{bmatrix}
+$$
+%
+Since we prune the matrix afterwards, it's important to choose a weight 
+factor that doesn't lead to all edges being either intra image edges or 
+intra image edges, since the first would create no clusters across 
+images and the latter would mean that the geometrical information would 
+be discarded and the bipartite graph constituting of edges between 
+feature points in the two images would be used instead.
+
+\bibliographystyle{abbrv}
+\bibliography{bibliography}
+\end{document}

### 2013-04-19 text/clustering.tex
Added the feature detector directory

@@
 partially overlapping pictures without any required knowledge of their 
-position.  What's more, if one of the pictures in there is not part of 
-the set, the features of the odd image out will not form clusters with 
-the features of the other images and automatically be sorted out.
+position.  What's more, if one of the pictures is not part of the set, 
+the features of the odd image out will not form clusters with the 
+features of the other images and automatically be sorted out.
+
+\section{Literature review}
+
+Since the introduction of the SIFT\cite features{lowe2004sift}, 
+collecting feature points from an image and using the descriptors to 
+match images have been used in a plethora of different applications. The 
+development of feature points have not been standing still since Lowe 
+introduced the SIFT feature back in 2004. Various modifications and 
+improments both to how features are collected and how features are best 
+described have been suggested since then. In locating feature points in 
+an image the focus
+
+To cluster similar parts in the images in to partitions we need to 
+describe these points in a way which is invariant (or close to 
+invariant) to changes in light, image quality, size, as well as 
+geometric transformations due to change in the camera position.
+
+TODO!!!! A lot more needs to be written here ...
 
@@
 \begin{algorithm}
-\caption{Louvain-Match Algorithm}
+\caption{Cluster-Match Algorithm}
 \label{alg-simple}
@@
 proposed method completely agnostic of the geometry of the feature 
-points in the picture. To better explain the algorithm here is an 
-overview over the inputs and functions mentioned and how they work:
+points in the picture. To better explain the algorithm here is a step by 
+step explication of the inputs and functions mentioned:
 \begin{itemize}
@@
 \item[]{\emph{$n$}: The number of weights per row in the adjecency 
-matrix}
+matrix.}
 \item[]{\emph{getFeatures}: Returns a set of feature points given an 
-image. The type of feature point is not theoretically important, but in 
-practice the BRIEF\cite{calonder2010brief} feature point detector and 
-descriptor has worked well} 
+image. In practice the BRIEF\cite{calonder2010brief} feature point 
+detector and descriptor has worked well, but it could easily be replaced 
+with any other feature point type.} 
 % TODO: include a comparison of SURF, SIFT, etc
@@
 compare the similarity of the feature points a symmetric adjecency 
-matrix is returned}
+matrix is returned.}
 \item[]{\emph{pruneEdges}: The result of the Louvain clustering depends 
@@
 matrix, making sure it's still symmetric afterwards. In practice setting 
-$n$ to around four or five usually yields good results}
+$n$ to around four or five yields good results.}
 \item[]{\emph{cluster}: Cluster the graph corresponding to the adjecency 
-matrix given using the Louvain algorithm in \cite{blondel2008}}
+matrix given using the Louvain algorithm in \cite{blondel2008}.}
 \item[]{\emph{getPositions}: Given a trait consisting of features in 
@@
 
+\subsubsection{On the subject of features}
+
+TODO: Show examples of the same image with feature points from different 
+detectors and explain the difference. Go in to why brief seems to work 
+best in practice and superficially explain how brief works compared with 
+SIFT.
+
 \begin{algorithm}
-\caption{Louvain-Match Algorithm With Geometry}
+\caption{Cluster-Match Algorithm With Geometry}
 \label{alg-geometry}
@@
 replace all the weights of edges between two feature points within the 
-same image with their distance. For the case of two images the original 
-adjecency matrix is defined as follows:
+same image with their distance. For the case of two images the 
+normalized adjecency matrix is defined as follows:
 %
-$$A=
+$$A_{norm}=
 \begin{bmatrix}
@@
 In a similar manner we can define an adjecency matrix based on the 
-geometrical distance. Note how for example $d_{1,n}$ doesn't contain any 
-sensible information.
+geometrical distance. Note for example how $d_{1,n}$ can take any value 
+as it denotes the geometric distance of feature points in two different 
+images and as such can be set to any value.
 %
-$$B=
+$$B_{norm}=
 \begin{bmatrix}

### 2013-04-19 code/display.py
Moved some files around

@@ -365,23 +365,6 @@ def draw_graph(g, clusters="orange", filename="graph.png") :
 	gt.graph_draw(g, pos=pos, output_size=(1000, 1000), vertex_halo=True, vertex_halo_color=class_colors, vertex_color=clusters,
 			   vertex_fill_color=clusters, vertex_size=5, edge_pen_width=weights, output=filename)
 
-def draw_graph2(g, clusters="orange", filename="graph.png") :
-	""" Show a graph with its clustering marked
-	"""
-	# Get indices
-	indices = g.vertex_properties["indices"]
-
-	# Get class colors
-	#class_colors = g.vertex_properties["class_colors"]
-
-	# Get weights and positions
-	weights = g.edge_properties["weights"]
-	pos = gt.sfdp_layout(g, eweight=weights)
-
-	# Print graph to file
-	gt.graph_draw(g, pos=pos, output_size=(1000, 1000), vertex_halo=True, vertex_color=clusters,
-			   vertex_fill_color=clusters, vertex_size=5, edge_pen_width=weights, output=filename)
-
 
 def graph_partitions(g, clusters, filename="graph_clusters.png") :
 	""" Create an image where the clusters are disconnected

### 2013-04-19 code/featureGraph.py

@@ -42,7 +42,7 @@ N = 600
 
 
 
-def cluster(graph, nb_clusters=20, iter=100, gamma=1.0, corr="erdos", verbose=False) :
+def clusterPotts(graph, nb_clusters=20, iter=100, gamma=1.0, corr="erdos", verbose=False) :
 
 	# Get weights (throws an error if they don't exist)
 	weights = graph.edge_properties["weights"]
@@ -50,29 +50,6 @@ def cluster(graph, nb_clusters=20, iter=100, gamma=1.0, corr="erdos", verbose=Fa
 	clusters = gt.community_structure(graph, iter, nb_clusters, weight=weights, gamma=gamma, corr=corr, verbose=verbose)
 	t = [(k, len(list(g))) for k,g in groupby(sorted(clusters.fa))]
 	return clusters, len(t)
-
-
-
-def getDescriptors(paths, size=32) :
-	""" Given a list of paths to images, the function returns a list of 
-	    descriptors and keypoints
-		Input: paths [list of strings] The paths to the images we are using
-		Out:   [pair of list of descriptors and list of keypoints]
-	"""
-	# Get all images and labels
-	labels = map(features.getLabel, paths)
-	images = map(features.loadImage, paths)
-
-	# Get feature descriptors
-	#keypoints = [features.getKeypoints(feature_keypoint, im) for im in images]
-	keypoints = [features.getORBKeypoints(im, size) for im in images]
-	data = [features.getDescriptors(feature_descriptor, im, k) for (im, k) in zip(images, keypoints)]
-	keypoints, descriptors = zip(*data)
-
-	# Check that we could get descriptors for all images
-	if sum(map(lambda d : d == None, descriptors)) > 0 : return (None, None, None)
-	indices = [l for i,n in zip(range(len(labels)), map(len, descriptors)) for l in [i]*n]
-	return (indices, numpy.concatenate(keypoints), numpy.concatenate(descriptors))
 
 
 
@@ -232,6 +209,7 @@ def getPartition(graph, partitioning, partition_indices) :
 def setPartition(graph, partition_array) :
 	p = graph.new_vertex_property("int")
 	p.fa = partition_array
+	graph.vp["partitions"] = p
 	return p
 
 
@@ -263,7 +241,7 @@ def getVarPos(graph) :
[…]

### 2013-04-19 code/display.py
Added some better plotting of matches

@@ -76,28 +76,35 @@ def compareKeypoints(im1, im2, pos1, pos2) :
 
 
 
-def matches(im1, im2, pos1, pos2, matchpos) :
+def matches(im1, im2, matches, filename = None) :
 	""" show a figure with lines joining the accepted matches in im1 and im2
-	    input: im1,im2 (images as arrays), locs1,locs2 (location of features), 
-	    matchscores (as output from 'match'). 
+		input: im1,im2 (images as arrays), locs1,locs2 (location of features), 
+		matchscores (as output from 'match'). 
 	"""
-
-	assert len(locs1) == len(matchpos)
 
 	# Construct unified image
 	im3 = appendimages(im1,im2)
 
+	# Create figure
+	fig = pylab.figure(frameon=False, figsize=(15.0, 7.0))
+	ax = pylab.Axes(fig, [0., 0., 1., 1.])
+
+	ax.set_axis_off()
+	fig.add_axes(ax)
+
 	# Display image
 	pylab.gray()
-	pylab.imshow(im3)
+	ax.imshow(im3, aspect='normal')
+
 
 	# Plot all lines
-	cols1 = im1.shape[1]
-	for i in range(len(matchpos)):
-		if matchpos[i] != None:
-			pylab.plot([pos1[i,1], pos2[int(matchpos[i]),1]+cols1], [pos1[i,0], pos2[int(matchpos[i]),0]], 'c')
+	offset_x = im1.shape[1]
+	for ((x1,y1),(x2,y2)) in matches:
+		pylab.plot([x1, x2+offset_x], [y1,y2], 'c', lw=0.8)
 	pylab.axis('off')
-	pylab.show()
+
+	if filename != None :
+		pylab.savefig(filename, bbox_inches=0, dpi=72)
 
 
 

### 2013-05-29 text/clustering.tex
Added stuff to clustering and new results

@@
 
-\section{Project description}
+\section{Introduction}
 
-Traditionally the feature points of two images have been matched by 
-comparing the feature points individually and finding the best matches 
-based on their distance. This approach was originally introduced with 
-the SIFT features \cite{lowe2004sift} and has been used since then in 
-computer vision applications such as scene recognition\footnote{See for 
-example chapter 4.1.3 of \cite[pp. 226]{szeliski2010}} and image 
-alignment\footnote{An example is the gold standard algorithm in \cite[p.  
-114]{multipleView}}. In larger scale approaches where an image is 
-compared with thousands or millions of other images, the feature points 
-are usually indexed in a dictionary of visual words instead. This 
-approach makes it possible to quickly retrieve matches in a large set of 
-potential candidates, but the performance is restricted by how 
-discriminative the individual feature points are. To agument the 
-descriminative power of the feature points, \cite{wu2009bundling} 
-proposes grouping the features and use the geometrical relationships 
-between members of a group when matching two feature points. Similarly 
-\cite{das2008event} use geometrical information about the feature points 
-to cluster them before doing scene matching resulting in better matches.
+Since the introduction of feature points, several methods for matching 
+them across images have been proposed in order to maximize the amount of 
+correct matches. In this part of the project I introduce two methods to 
+reliably match feature points. The word 'reliable' covers that matches 
+only are returned if they are judged as sound. That is, matches should 
+only be returned if there are objects or scenes that appear in both 
+images.
+
+When matching feature points between two images we are often faced with 
+a dilemma between making the feature descriptor more discriminative to 
+make sure only correct matches are made, and making it less 
+discriminative to increase the robustness of the descriptor over 
+different changes such as illumination, perspective and image quality.  
+Any feature type aiming for robustness will have cases where it isn't 
+possible to generate reliable matches if we only look at the pairwise 
+correspondence of the descriptors.
+
+To get around this limitation several methods have been proposed in the 
+literature. One of the most fruitful approaches have been to look at the 
+geometric configuration of the feature points and match them with 
+respect to assumptions concerning the variance between images. For 
+example an angular and distance constraint between matches as considered 
+by \cite{kim2008efficient} performs well in situations where no camera 
+rotation occurs between the two images but will likely fail in other 
+cases. Various scenarios have been proposed to improve on this simple 
+assumption, such as epipolar constraints (\cite{torr2000mlesac}, 
+\cite{chum2005matching}) and pairwise constraints 
+(\cite{choi2009robust}, \cite{leordenanu2005spectral}). The Epipolar 
+constraint carries the assumption that the two images matched are 
+related by an affine transformation. That is, there is no relative 
+movement of objects in between images and either the viewpoint is fixed 
+or the image resides entirely on a plane. In practice this assumption 
+largely holds true when all objects we are interested in matching are 
+roughly the same distance from the camera and when we don't expect to 
+match objects that aren't consistently positioned across images.  
+Pairwise constraints provide a more robust approach to this problem by 
+looking at a set of proposed correspondences and defining a pairwise 
+error between any two matches usually based on the assumption that two 
+neighboring correspondences will usually have similar angles and 
+distances. We can then convert the problem to an optimization problem 
+and return a set of correspondences that minimizes this error such as 
+proposed in \cite{choi2009robust} and \cite{leordeanu2005spectral}.  
+This approach provides more robustness because assumptions that might 
+not be true globally often still holds on a local level.
+
+A similar approach is to pick out different zones in each image and
+
+In practice there are many situations where using the geometry of the 
+image to filter correspondences is not possible. This situation most 
+often arise when the assumptions made by a geometric method turns out 
+not to hold in a particular use case. This could matchings between 
+images where the content has been scrambled or with so little 
+consistency that even the geometric assumptions break down even on a 
+local level. In addition the geometric methods all require a set of 
+correspondences to begin with. If this set of correspondences is 
+narrowed down to a smaller set with a higher ratio of inliers the result 
+of the geometric matching will be both faster and more accurate. Finally 
+some use cases might require a performance that can't be achieved by a 
+more complex geometric method where simple non geometric methods might 
+be able to provide additional matching accuracy with a smaller 
+performance penalty.
+
+There are a relatively small number of algorithms proposed to solve the 
+matching problem without involving geometric constraints. Traditionally 
+the feature points of two images have been matched by comparing the 
+every feature point of one image with all feature points of the other 
+and finding the best matches based on the similarity of the descriptors.  
+With the introduction of the SIFT features \cite{lowe2004sift}, Lowe 
+proposes an alternative measure where the uniqueness of a given match is 
+found by looking at the two nearest neighbors of each feature point and 
+calculating a match score by the ratio of similarities. By ranking the 
+scores by their uniqueness and picking the $n$ best we get a set of 
+correspondences that are distinctly matched across the two images. In 
+the book Multiple View Geometry \cite[p.  114]{multipleView}, the gold 
+standard algorithm is introduced which ranks correspondences by 
+similarity and further filters them by making sure that the map of 
+matches is reflective, i.e. that for every feature point $f_i$ matching 
+$f_j$ we also have that $f_j$ matches $f_i$.
+
+In turn the two methods proposed in this report are inspired by a simple 
+but novel idea. If we have two images and a given feature point in the 
+first image is better matched with other feature points from the 
+\emph{same} image than points in the other image, then any matches of 
+this feature point to points in the other image is deemed unreliable and 
+discarded.  This approach carries no implicit assumptions about the 
+geometric consistency of matches and can as such easily be extended with 
+other geometric solutions when appropriate.
+
+Based on this idea the two proposed methods find reliable matches as 
+follows:
+\begin{itemize}
+\item{\emph{Mirror Match}: Take any traditional way of matching feature 
+but extend it to match any given feature with the combined set of 
+features from both images, filtering out all matches that are within the 
+same image.}
+\item{\emph{Cluster Match}: Take the combined set of feature points from 
+both images and cluster these points according to their
+descriptors. Given a resulting partition of points, no matches are 
+returned if it contains only feature points from one image. If the 
+partition contains points from both images, \emph{Mirror Match} is used 
+to find the best matches within the partition.
+\end{itemize}
+The
+
+%Given two sets of feature points, $A$ and $B$ corresponding to two 
+%images $i_A$ and $i_B$, and a feature point $f_A^i$ in set $A$ is more 
+%closely related to one or more other feature points in set $A$ than 
+%feature points in set $B$ then the potential matches between $f_A^i$ 
+%and feature points in $B$ is deemed \emph{unreliable}.
+
+ This approach was originally introduced with the SIFT features and has 
+been used since then in computer vision applications such as scene 
+recognition\footnote{See for example chapter 4.1.3 of \cite[pp.  
+226]{szeliski2010}} and image alignment\footnote{An example is the gold 
+standard algorithm in \cite[p.  114]{multipleView}}.  In larger scale 
+approaches where an image is compared with thousands or millions of 
+other images, the feature points are usually indexed in a dictionary of 
+visual words instead. This approach makes it possible to quickly 
+retrieve matches in a large set of potential candidates, but the 
+performance is restricted by how discriminative the individual feature 
+points are. To agument the descriminative power of the feature points, 
+\cite{wu2009bundling} proposes grouping the features and use the 
+geometrical relationships between members of a group when matching two 
+feature points. Similarly \cite{das2008event} use geometrical 
+information about the feature points to cluster them before doing scene 
+matching resulting in better matches.
 
@@
 
-Since the introduction of the SIFT\cite features{lowe2004sift}, 
+Since the introduction of the SIFT features\cite{lowe2004sift}, 
 collecting feature points from an image and using the descriptors to 

### 2013-05-29 code/clustermatch.py

@@ -184,7 +184,7 @@ def getPartitionMatches(partitions, weights, full_weights, indices, treshold, ve
 					(p_i, p_j) = (index_both[m_i], index_both[m])
 					if verbose :
 						distance = matchDistance(ks[p_i].pt, ks[p_j].pt, homography)
-						print("%4i\tch: %.3f\tEdges: %i\tDistance: %.2f" % (p, c, nb_e, distance))
+						print("%4i\tEdges: %i\tDistance: %.2f" % (p, nb_e, distance))
 					yield (p_i, p_j)
 
 

### 2013-05-29 code/colors.py

@@ -5,7 +5,9 @@ Jonas Toft Arnfred, 2013-04-23
 """
 
 def getRedGreen(f) :
-    return '#%02x%02x11' % (int(f*255), int((1-f)*255))
+	if f > 1 : f = 1
+	c = '#%02x%02x11' % (int(f*255), int((1-f)*255))
+	return c
 
 def get() : 
 	return [

### 2013-05-29 code/display.py

@@ -24,7 +24,7 @@ import colors
 import pylab
 from scipy.misc import imresize, imread
 import Image
-from itertools import combinations, groupby, tee, product, combinations_with_replacement
+from itertools import combinations, groupby, tee, product, combinations_with_replacement, dropwhile
 from sklearn import metrics
 
 
@@ -96,7 +96,7 @@ def compareKeypoints(im1, im2, pos1, pos2) :
 	pylab.ylim(im3.shape[0],0)
 
 
-def matchPoints(im1, im2, matches, dist = None, filename = None, max_dist = 100000) :
+def matchPoints(im1, im2, matches, dist = None, filename = None, max_dist = 100) :
 	""" show a figure with lines joining the accepted matches in im1 and im2
 		input: im1,im2 (images as arrays), locs1,locs2 (location of features), 
 		matchscores (as output from 'match'). 
@@ -253,22 +253,27 @@ def accuHist(accu_list, labels, colors = ["blue", "cyan", "green", "orange", "re
 		removeDecoration()
 
 
-def accuDetail(correct, total, legend, ylim = 100, index=0) :
-	for c,t,l in zip(correct, total, legend) :
-		print("%s:\t%i of %i\t(%.2f%%)" % (l, sum(c[index]), sum(t[index]), sum(c[index])/float(sum(t[index]))))        
-	get_accu = lambda ts,cs : [1 if t == 0 else c/float(t) for t,c in zip(ts[index], cs[index])]
-	accu = [get_accu(ts, cs) for ts,cs in zip(total, correct)]
+def accuDetail(correct, total, legend, ylim = 100, treshold=1000) :
+	get_index = lambda cs : list(dropwhile(lambda (i,c) : sum(c) < treshold,enumerate(cs)))[0][0]
+	indices = [get_index(cs) for cs in correct]
+	print(indices)
+	
+	for c,t,l,i in zip(correct, total, legend, indices) :
+		print("%s:\t%i of %i\t(%.2f%%)" % (l, sum(c[i]), sum(t[i]), 100*sum(c[i])/float(sum(t[i]))))
+		
+	get_accu = lambda ts,cs,index : [1 if t == 0 else c/float(t) for t,c in zip(ts[index], cs[index])]
+	accu = [get_accu(ts, cs, index) for ts,cs,index in zip(total, correct, indices)]
[…]

### 2013-05-29 code/matching.py

@@ -37,10 +37,9 @@ import random
 ####################################
 
 
-def testMatch(paths, homography, match_fun, options = {}, verbose = False) :
+def testMatch(paths, homography, match_fun, options = {}, return_matches = False, verbose = False) :
 
 	distinct_treshold = options.get("distinct_treshold", 5)
-	distance_treshold = options.get("distance_treshold", 5)
 	tresholds = options["tresholds"]
 
 	# Get matches over tresholds
@@ -48,12 +47,13 @@ def testMatch(paths, homography, match_fun, options = {}, verbose = False) :
 
 	# Get distances
 	getDist = lambda ms : [matchDistance(m1,m2,homography) for (m1,m2) in ms]
-	match_dist_set = [getDist(ms) for ms in match_pos_set]
+	match_dist = [getDist(ms) for ms in match_pos_set]
 
 	if len(tresholds) == 1 and verbose :
-		display.distHist(match_dist_set[0], distance_treshold)
+		display.distHist(match_dist[0], tresholds[0])
 
-	return match_dist_set
+	if return_matches : return match_pos_set, match_dist
+	else : return match_dist
 
 
 # Load all files
@@ -78,7 +78,7 @@ def folderMatch(directory, dt, match_fun, tresholds, keypoint, descriptor) :
 	# Get a set of matches varied over image pairs (matrix of size N x T where N
 	# is amount of image pairs and T is the amount of tresholds. Each element in
 	# the matrix is a zipped list of matches and distances
-	match_sets = numpy.array([match_fun(dt, p, h, tresholds, keypoint, descriptor) for p, h in imagePairs]).T
+	match_sets = numpy.array([numpy.array(match_fun(dt, p, h, tresholds, keypoint, descriptor)) for p, h in imagePairs]).T
 
 	# Now collect an x axis with nb correct matches per treshold
 	get_correct_matches = lambda match_row : [nb_correct_matches(d) for d in match_row]
@@ -92,7 +92,8 @@ def folderMatch(directory, dt, match_fun, tresholds, keypoint, descriptor) :
 
 
 def getHomography(hom_path) :
-	return numpy.array([map(lambda s : float(s.strip()), line.strip().split()) for i,line in enumerate(open(hom_path)) if i < 3])
+	h = numpy.loadtxt(hom_path)
+	return h
 
 
[…]

### 2013-05-29 text/clustering.tex
A few more lines about MM and MMC

@@
 cases. Various scenarios have been proposed to improve on this simple 
-assumption, such as epipolar constraints (\cite{torr2000mlesac}, 
+assumption such as epipolar constraints (\cite{torr2000mlesac}, 
 \cite{chum2005matching}) and pairwise constraints 
@@
 
-A similar approach is to pick out different zones in each image and
+Another approach proposed in the literature is to pick out different 
+zones in each image and find a pairing of zones where feature points are 
+only matched within the same zone. \cite{das2008event} proposes 
+clustering the feature points using their geometric position and 
+matching only feature points between groups that have a certain amount 
+of matchings between them. A more sophisticated approach is introduced 
+in \cite{wu2011robust} where the zones are created by surrounding MSER 
+feature points by an ellipse and grouping the SIFT or SURF feature 
+points that fall within the ellipse together. These points can then be 
+matched according to epipolar constraints.
 
@@
 be able to provide additional matching accuracy with a smaller 
-performance penalty.
+performance penalty. This approach is inspired by \cite{wu2009bundling} 
+where bundling of feature points was used to enhance the search results 
+in large scale partial-duplicate web image search.
 
@@
 similarity and further filters them by making sure that the map of 
-matches is reflective, i.e. that for every feature point $f_i$ matching 
+matches is symmetric, i.e. that for every feature point $f_i$ matching 
 $f_j$ we also have that $f_j$ matches $f_i$.
@@
 \begin{itemize}
-\item{\emph{Mirror Match}: Take any traditional way of matching feature 
-but extend it to match any given feature with the combined set of 
-features from both images, filtering out all matches that are within the 
-same image.}
-\item{\emph{Cluster Match}: Take the combined set of feature points from 
-both images and cluster these points according to their
-descriptors. Given a resulting partition of points, no matches are 
+\item{\emph{Mirror Match}: Match features using the gold standard 
+algorithm\cite[p. 114]{multipleView} ranked by similarity and thresheld 
+by uniqueness\cite{lowe2004sift}. However instead of matching features 
+from one image with features in another, we match every feature with all 
+other features of the two images combined. Only matches from one image 
+to the other are returned.}
+\item{\emph{Mirror Match with Clustering}: Take the combined set of 
+feature points from both images and cluster these points according to 
+their descriptors. Given a resulting partition of points, no matches are 
 returned if it contains only feature points from one image. If the 
@@
 \end{itemize}
-The
 
-%Given two sets of feature points, $A$ and $B$ corresponding to two 
-%images $i_A$ and $i_B$, and a feature point $f_A^i$ in set $A$ is more 
-%closely related to one or more other feature points in set $A$ than 
-%feature points in set $B$ then the potential matches between $f_A^i$ 
-%and feature points in $B$ is deemed \emph{unreliable}.
+Matching feature points against the entire set of points from both 
+images ensures that the distinctiveness of a returned correspondence is 
+higher. In almost all cases\footnote{Exceptions would include cases 
+where we want to find all particular points in a pattern and other use 
+cases where the correspondence isn't assumed to be unique}, a good match 
+between two images is unambiguous in the sense that there are no other 
+equally (or almost equally) good potential matches to the same point.  
+This is the key insight behind the algorithm presented by Lowe in 
+\cite{lowe2004sift}. However the implication doesn't follow the other 
+way around. In the case that a feature point don't have any actual 
+correspondence in the other image, there is no guarantee that this 
+feature point might not still be uniquely matched to a feature point in 
+the other image. The issue is particularly pronounced if we compare two 
+images that don't correspond. For any proposed correspondence it is 
+entirely probable that this correspondence is unique even if it isn't 
+correct. With Mirror Match this ambiguity is avoided by incorporating 
+the feature points of both images when a match is made. When the two 
+images have nothing to do with each other, chances are that a feature 
+point will match better with another feature point from the same image 
+in which case it is easily discarded.
 
- This approach was originally introduced with the SIFT features and has 
-been used since then in computer vision applications such as scene 
-recognition\footnote{See for example chapter 4.1.3 of \cite[pp.  
-226]{szeliski2010}} and image alignment\footnote{An example is the gold 
-standard algorithm in \cite[p.  114]{multipleView}}.  In larger scale 
-approaches where an image is compared with thousands or millions of 
-other images, the feature points are usually indexed in a dictionary of 
-visual words instead. This approach makes it possible to quickly 
-retrieve matches in a large set of potential candidates, but the 
-performance is restricted by how discriminative the individual feature 
-points are. To agument the descriminative power of the feature points, 
-\cite{wu2009bundling} proposes grouping the features and use the 
-geometrical relationships between members of a group when matching two 
-feature points. Similarly \cite{das2008event} use geometrical 
-information about the feature points to cluster them before doing scene 
-matching resulting in better matches.
-
-Both methods suffer from two shortcomings. Firstly we have that any 
-defined group in one image might not correspond to a group in another 
-image.  This means that we might end up in a situation where a good 
-match between two images is scored low because most of it's geometric 
-neighbors are in an adjecent group. Secondly if we intent to match the 
-different groups as in \cite{wu2009bundling} we might end up matching 
-two mismatching groups. To improve geometric matching I propose pooling 
-the keypoints from two images into one set and partitioning them into 
-groups together.  The advantages of this approach is that groups are 
-consistent across images, and that keypoints from one image that don't 
-have equivalents in the other image will simply be grouped in their own 
-group which can easily be discarded during the matching. This is 
-important for scene recognition where people might obscure details in 
-the picture. In addition the proposed method generalizes to three or 
-more images.  This makes it possible to easily assemble a set of 
-partially overlapping pictures without any required knowledge of their 
-position.  What's more, if one of the pictures is not part of the set, 
-the features of the odd image out will not form clusters with the 
-features of the other images and automatically be sorted out.
-
-\section{Literature review}
-
-Since the introduction of the SIFT features\cite{lowe2004sift}, 
-collecting feature points from an image and using the descriptors to 
-match images have been used in a plethora of different applications. The 
-development of feature points have not been standing still since Lowe 
-introduced the SIFT feature back in 2004. Various modifications and 
-improments both to how features are collected and how features are best 
-described have been suggested since then. In locating feature points in 
-an image the focus
-
-To cluster similar parts in the images in to partitions we need to 
-describe these points in a way which is invariant (or close to 
-invariant) to changes in light, image quality, size, as well as 
-geometric transformations due to change in the camera position.
-
-TODO!!!! A lot more needs to be written here ...
+Often images will contain repetitive patterns that are difficult to 
+match\footnote{In fact this particular problem has been given attention 
+before by for example \cite{fan2011towards}} because the feature points 
+covering these patterns will look very similar. If we threshold by 
+uniqueness like in Mirror Match this means that these points will often 
+be discarded even if they might have good correspondences. To solve this 
+problem the enhanced Mirror Match with Clustering makes it possible to 
+look at groups of similar feature points one at a time and within each 
+group finding the best matches. This is done by taking the set of 
+feature points from both images and clustering. The resulting partitions 
+will each contain feature points that are similar to each other. In some 
+cases the clustering will end up grouping feature points of only one 
+image together which can then easily be discarded in the matching 
+process. In other cases partitions will contain feature points from both 
+images that can then be matched using Mirror Match but with lower 
+thresholds.
 
@@
 into groups reduces the problem to that of graph clustering or community 
-structure depending on the context. In the litterature there are various 
+structure depending on the context. In the literature there are various 
 ways of clustering a graph according to different measures of what 

### 2013-05-29 text/clustering.tex
Added the MM algorithm to the clustering.tex

@@
 \cite{chum2005matching}) and pairwise constraints 
-(\cite{choi2009robust}, \cite{leordenanu2005spectral}). The Epipolar 
+(\cite{choi2009robust}, \cite{leordeanu2005spectral}). The Epipolar 
 constraint carries the assumption that the two images matched are 
@@
 standard algorithm is introduced which ranks correspondences by 
-similarity and further filters them by making sure that the map of 
-matches is symmetric, i.e. that for every feature point $f_i$ matching 
-$f_j$ we also have that $f_j$ matches $f_i$.
+similarity and further filters them by discarding matches that aren't 
+symmetric, i.e. that for every feature point $f_i$ matching $f_j$ we 
+also have that $f_j$ matches $f_i$.
 
@@
 \begin{itemize}
-\item{\emph{Mirror Match}: Match features using the gold standard 
+\item{\emph{Mirror Match (MM)}: Match features using the gold standard 
 algorithm\cite[p. 114]{multipleView} ranked by similarity and thresheld 
@@
 to the other are returned.}
-\item{\emph{Mirror Match with Clustering}: Take the combined set of 
-feature points from both images and cluster these points according to 
+\item{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
+of feature points from both images and cluster these points according to 
 their descriptors. Given a resulting partition of points, no matches are 
@@
 partition contains points from both images, \emph{Mirror Match} is used 
-to find the best matches within the partition.
+to find the best matches within the partition.}
 \end{itemize}
@@
 process. In other cases partitions will contain feature points from both 
-images that can then be matched using Mirror Match but with lower 
+images that can then be matched using \emph{MM} but with lower 
 thresholds.
 
+The report is organized as follows. In section \ref{algorithms} I will 
+describe the two algorithms. Section \ref{experiment} will cover the 
+experimental set up and introduce the image set that is used in testing.  
+In section \ref{results} I will go through the results and conclude.
+
+\section{Algorithms}
+\label{algorithms}
+
+\begin{algorithm}
+\caption{Mirror Match Algorithm}
+\label{alg-mm}
+\begin{algorithmic}
+\Require $images$ : set of images, $t$ : float $\in \mathbb{R}$
+\State $matches_{init}\gets \varnothing$
+\State $matches_{final}\gets \varnothing$
+\State $features\gets \varnothing$
+\ForAll{$I_i \in images$} \Comment Gather features of all images
+	\State $features\gets features \cup getFeatures(I_i)$
+\EndFor
+\ForAll{$f_i \in features$} \Comment Get best match for all features
+	\State $f_m,f_n \gets getTwoNearestNeighbors(features \ {f_i})$
+	\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
+f_m)$
+	\If{$ratio < t$}
+		\State $matches_{init}\gets \left(f_i, f_m\right)$
+	\EndIf
+\EndFor
+\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
+matches
+\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
+getImg(f_j)$}
+		\State $matches_{final} \gets (f_i, f_j)$
+		\State $matches_{init} \gets matches_{init} \ (f_j, f_i)$
+	\EndIf
+\EndFor \\
+\Return $matches_{final}$
+\end{algorithmic}
+\end{algorithm}
+
+In this report I propose two algorithms for better matching feature 
+points without any geometric assumptions about the images matched. The 
+two algorithms are complementary in the sense that the first, Mirror 
+Match (\emph{MM}) is less complex but performs slightly worse than 
+Mirror Match with Clustering (\emph{MMC}). In cases where high
+
+\section{Experiments and Image Set}
+\label{experiment}
+
+\section{Results}
+\label{results}
 \subsection{Graph Clustering}

### 2013-05-30 text/clustering.tex
Added new figures to the report

@@
 
+To discuss the implementation of \emph{MM} and \emph{MMC} a few notes on 
+notation will be helpful. BLAH BLAH!
+
+\subsection{Mirror Match (\emph{MM})}
+
+The central idea behind \emph{MM} is to match features of $n$ images by 
+taking every feature from all $n$ images and matching it against every 
+other feature from the same set. We can then discard the correspondences 
+that match two points within the same image. In algorithm \ref{alg-mm} 
+the actual implementation of \emph{MM} is shown.
+
 \begin{algorithm}
-\caption{Mirror Match Algorithm}
+\caption{Mirror Match Algorithm (\emph{MM})}
 \label{alg-mm}
 \begin{algorithmic}
-\Require $images$ : set of images, $t$ : float $\in \mathbb{R}$
+\Require $images$ : set of images, $threshold$ : float $\in \mathbb{R}$
 \State $matches_{init}\gets \varnothing$
@@
 \ForAll{$f_i \in features$} \Comment Get best match for all features
-	\State $f_m,f_n \gets getTwoNearestNeighbors(features \ {f_i})$
+	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features ~ 
+\backslash ~ \left\{f_i\right\})$
 	\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
 f_m)$
-	\If{$ratio < t$}
+	\If{$ratio < threshold$}
 		\State $matches_{init}\gets \left(f_i, f_m\right)$
@@
 
-In this report I propose two algorithms for better matching feature 
-points without any geometric assumptions about the images matched. The 
-two algorithms are complementary in the sense that the first, Mirror 
-Match (\emph{MM}) is less complex but performs slightly worse than 
-Mirror Match with Clustering (\emph{MMC}). In cases where high
+This algorithm passes over three states: An acquisition state where 
+feature points are gathered, a matching state where the initial set of 
+correspondences are found and a filtering state where correspondences 
+within the same image are removed. In the acquisition state the function 
+\emph{getFeatures($I_i$)} returns a set of feature points given an 
+image.  In practice the feature used for the experiments have been 
+SIFT\cite{lowe2004sift}, but there aren't any reason why other features 
+such as SURF\cite{bay2006surf} or BRIEF\cite{calonder2010brief} couldn't 
+be used just as well. The matching state uses K-Nearest Neighbors to 
+return the two closest neighbors in the set of features for any given 
+feature $f_i$ and calculates the ratio between the correspondences as 
+proposed in \cite{lowe2004sift}.  Any correspondence with a ratio below 
+the threshold supplied will be discarded. Finally in the filter the 
+function \emph{getImg($f_i$)} returns the parent image of the feature 
+$f_i$ and discards both correspondences that aren't symmetric as well as 
+those that match two points in the same image.
 
-\section{Experiments and Image Set}
-\label{experiment}
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/mirror_match_off}
+			\caption{Baseline Result}
+			\label{fig:unique}
+		\end{subfigure}%
+		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
+			\caption{\emph{MM} with intra image matches}
+			\label{fig:within}
+		\end{subfigure}%
+		%~ %add desired spacing between images, e. g. ~, \quad, \qquad
+		  %(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/mirror_match}
+			\caption{\emph{MM}}
+			\label{fig:without}
+		\end{subfigure}%
+	}%
+	\label{fig:compare_mirror}
+	\caption{Illustration of matches filtered by \emph{MM}}
+\end{figure}
 
-\section{Results}
-\label{results}
-\subsection{Graph Clustering}
+Figure \ref{fig:compare_mirror} shows an example of the performance of 
+\emph{MM}. In sub figure \ref{fig:unique} the result of a normal 
+matching of two images is shown. The two images appear side by side and 
+for each correspondence between them, a line has been drawn from one 
+image to the other. The color of the line indicates if the 
+correspondence is accurate. Sub figure \ref{fig:within} shows the 
+correspondences found by mirror match using the same threshold before 
+the matches within the same image has been filtered out. In particular 
+the fence by the bottom of the image admits correspondences that can 
+conveniently be removed as done in sub figure \ref{fig:without} where 
+only the actual correspondences returned by the algorithm are shown.
+
+\subsection{Mirror Match with Clustering (\emph{MMC})}
+
+As opposed to \emph{MM}, \emph{MMC} diverges from traditional 
+non-geometric feature matching by clustering the feature points by 
+similarity. This process yields partitions of fairly similar feature 
+points that we can match using the same approach as \emph{MM}. Before I 
+introduce the implementation details I will go over the problem of graph 
+clustering and how it relates to feature matching.
+
+\subsubsection{Graph Clustering}
 
@@
 This representation reduces the problem of partitioning the keypoints 
-into groups reduces the problem to that of graph clustering or community 
-structure depending on the context. In the literature there are various 
-ways of clustering a graph according to different measures of what 
-constitutes an optimal partitioning. Traditionally the most used 
-clustering algorithms have been K-means and spectral clustering, but in 
-recent years a host of new algorithms have been proposed based on both 
-Newman's concept of graph modularity\footnote{Introduced in 
-\cite{girvan2002}, discussed in \cite{brandes2007} and used in 
-\cite{blondel2008} as well as others} as well as information theoretical 
-measures\footnote{See for example \cite{rosvall2008}} and the Potts spin 
-model from physics\footnote{Used in \cite{ronhovde2009}} just to mention 
-a few approaches. Many of the new algorithms differ from K-means 
-clustering and Spectral clustering in that they don't require the number 
-of expected to clusters to be specified beforehand\footnote{Among the 
-aforementioned methods, this is true for \cite{blondel2008} and 
-\cite{rosvall2008}}.  Furthermore, on tests done using randomly 
-generated graphs with a known partitioning \cite{blondel2008}, 
-\cite{rosvall2008} and \cite{ronhovde2009} perform markedly better than 
-spectral clustering and K-means\cite{lancichinetti2009}.
+into groups to that of graph clustering or community structure depending 
+on the context. In the literature there are various ways of clustering a 
+graph according to different measures of what constitutes an optimal 
+partitioning. Traditionally the most used clustering algorithms have 
+been K-means and spectral clustering, but in recent years a host of new 
+algorithms have been proposed based on both Newman's concept of graph 
+modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
+\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
+well as information theoretical measures\footnote{See for example 
+\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
+in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
+new algorithms differ from K-means clustering and Spectral clustering in 
+that they don't require the number of expected to clusters to be 
+specified beforehand\footnote{Among the aforementioned methods, this is 
+true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
+tests done using randomly generated graphs with a known partitioning 
+\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
+markedly better than spectral clustering and 
+K-means\cite{lancichinetti2009}.
 
@@
 
-\subsection{Clustering feature points using Louvain clustering}
+\subsubsection{Clustering feature points using Louvain clustering}
 
 \begin{algorithm}
-\caption{Cluster-Match Algorithm}
-\label{alg-simple}
+\caption{Mirror Match with Clustering Algorithm (\emph{MMC})}
+\label{alg-mmc}
 \begin{algorithmic}
-\Require $images$ : set of images, $n$ : int $\in \mathbb{N}$
+\Require $images$ : set of images, $threshold \in \mathbb{R}$
 \State $matches\gets \varnothing$
+\State $features\gets \varnothing$
 \ForAll{$I_i \in images$} \Comment Gather features of all images
 	\State $f_i\gets getFeatures(I_i)$
+	\State $features\gets features \cup f_i$
 \EndFor
@@
 \State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $P\gets cluster(A_{pruned})$ 
-\Comment P is a set of partitions
-\ForAll{$p \in P$} \Comment p is a set of feature points
-	\State $trait\gets \left\{p \cap f_i \mid p \cap f_i \neq 
-\varnothing, f_i \in \left\{f_1, f_2,\; \ldots \;, f_n\right\}\right\}$
-	\If{$\left\vert trait \right\vert > 1$}
-		\State $matches\gets getPositions(trait)$
-		\Comment Position of trait in each image
-	\EndIf
+\State $Partitions\gets cluster(A_{pruned})$
+\ForAll{$p \in Partitions$} \Comment p is a set of feature points
+	\State $matches\gets matches \cup getMatches(p, threshold, 
+features)$
 \EndFor \\
@@
 
-Algorithm \ref{alg-simple} shows the basic steps taken to find matches 
-in two or more images. This algorithm is a simplified version of the 
-proposed method completely agnostic of the geometry of the feature 
-points in the picture. To better explain the algorithm here is a step by 
-step explication of the inputs and functions mentioned:
+Unlike the \emph{MM} algorithm the feature points are partitioned before 
+the matching stage. While the louvain clustering algorithm doesn't 
+require any parameters in itself, it tends towards clustering all 
+feature points together in the same partition if the graph is fully 
+connected or close. To ensure that the graph is well clustered, the 
+adjacency matrix is pruned so only edges above a certain threshold is 
+kept. From empirical analysis keeping around 2.5\% of edges seems to 
+work well. Figure \ref{fig:graph} shows the result of clustering the 
+feature points displayed as a graph where each node correspond to a 
+feature point. Here the border of nodes signifies the original image 
+while the color of the node is decided by what partition it belongs to.  
+Notice that since a limited amount of colors are used disconnected 
+subgraphs of the same color can be assumed to belong to separate 
+partitions. The sub figure \ref{fig:cropped_graph} shows a detailed 
+section of the graph where the interplay between small clusters 
+consisting of two or three nodes as well as larger clusters consisting 
+of several hundred nodes can be seen.
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.60\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/MMC_graph_full}
+			\caption{Full Graph}
+			\label{fig:full_graph}
+		\end{subfigure}%
+		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.60\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/MMC_graph_cropped}
+			\caption{Cropped Section of Graph}
+			\label{fig:cropped_graph}
+		\end{subfigure}%
+	}%
+	\label{fig:graph}
+	\caption{The partitioned feature graph. Every color signifies a 
+partition while the edge color of each node signifies which image it 
+belongs to}
+\end{figure}
+
+The clusters 
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.60\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
+			\caption{Source image}
+			\label{fig:pitts_source}
+		\end{subfigure}%
+		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.60\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
+			\caption{Keypoints Displayed}
+			\label{fig:pitts_keypoints}
+		\end{subfigure}%
+	}%
+	\\
+	\makebox[\textwidth][c]{
+		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+
+		\begin{subfigure}[t]{1.16\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/MMC_partition}
+			\caption{A Partition Example}
+			\label{fig:pitts_partition}
+		\end{subfigure}%
+	}%
+	\label{fig:compare_mirror}
+	\caption{Example of partitioning of keypoints in an image}
+\end{figure}
+
+\begin{algorithm}
+\caption{Impl. of GetMatches (\emph{from MMC algorithm})}
+\label{alg-getmatches}
+\begin{algorithmic}
+\Require $p$ : set of features, $threshold \in \mathbb{R}$, $features$ : 
+Set of all features
+\State $matches \gets \varnothing$
+\State $edges \gets \left\{getSimilarity(f_i, f_j) \mid getImg(f_i) \neq 
+getImg(f_j) \wedge f_i, f_j \in p \right\}$
+\If{$\left\vert edges \right\vert = 1$} \Comment If $\exists$ one edge 
+between images
+	\State $f_i,f_j \gets getInterImageFeatures(edges_{inter}, p)$
+	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features ~ 
+\backslash ~ \left\{f_i\right\})$
+	\State $f_s,f_t \gets getTwoNearestNeighbors(f_j, features ~ 
+\backslash ~ \left\{f_j\right\})$
+	\State $ratio_i \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
+f_j)$
+	\State $ratio_j \gets getSimilarity(f_j, f_t) / getSimilarity(f_j, 
+f_i)$
+	\If{$ratio_i < threshold \wedge ratio_j < threshold$}
+		\State $matches \gets matches \cup (f_i, f_j)$
+	\EndIf
+\ElsIf{$\left\vert edges \right\vert > 1$} \Comment If $\exists$ more 
+than one edge between images
+	\ForAll{$f_i \in p$}
+		\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, p ~ \backslash 
+~ \left\{f_i\right\})$
+		\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
+f_m)$
+		\If{$getImg(f_i) \neq getImg(f_m) \wedge ratio < threshold 
+\wedge (f_m, f_i) \not\in matches$}
+			\State $matches \gets matches \cup (f_i, f_m)$
+		\EndIf
+	\EndFor
+\EndIf
+
+\Return matches
+\end{algorithmic}
+\end{algorithm}
+
+Algorithm \ref{alg-mmc} shows the basic steps taken to find matches in 
+two or more images.
+
+This algorithm is a simplified version of the proposed method completely 
+agnostic of the geometry of the feature points in the picture. To better 
+explain the algorithm here is a step by step explication of the inputs 
+and functions mentioned:
 \begin{itemize}
@@
 \end{itemize}
+
+The two algorithms introduced in this report are designed to work with 
+feature points such as ,  or similar. While the experimental results 
+have all been done with the SIFT descriptor, there aren't any 
+theoretical or practical issues with using other types of feature 
+points.
+
+In this report I propose two algorithms for better matching feature 
+points without any geometric assumptions about the images matched. The 
+two algorithms are complementary in the sense that the first, Mirror 
+Match (\emph{MM}) is less complex but performs slightly worse than 
+Mirror Match with Clustering (\emph{MMC}). In cases where high
+
+\section{Experiments and Image Set}
+\label{experiment}
+
+\section{Results}
+\label{results}
+\subsection{Graph Clustering}
 

### 2013-05-30 code/display.py

@@ -70,7 +70,7 @@ def keypoints(im, pos) :
 	pylab.show()
 
 
-def compareKeypoints(im1, im2, pos1, pos2) :
+def compareKeypoints(im1, im2, pos1, pos2, filename = None) :
 	""" Show two images next to each other with the keypoints marked
 	"""
 
@@ -95,8 +95,11 @@ def compareKeypoints(im1, im2, pos1, pos2) :
 	pylab.xlim(0,im3.shape[1])
 	pylab.ylim(im3.shape[0],0)
 
+	if filename != None :
+		fig.savefig(filename, bbox_inches='tight', dpi=72)
 
-def matchPoints(im1, im2, matches, dist = None, filename = None, max_dist = 100) :
+
+def matchPoints(im1, im2, matches, dist = None, filename = None, max_dist = 100, matches_im1 = None, dist_im1 = None, matches_im2 = None, dist_im2 = None) :
 	""" show a figure with lines joining the accepted matches in im1 and im2
 		input: im1,im2 (images as arrays), locs1,locs2 (location of features), 
 		matchscores (as output from 'match'). 
@@ -106,7 +109,7 @@ def matchPoints(im1, im2, matches, dist = None, filename = None, max_dist = 100)
 	im3 = appendimages(im1,im2)
 
 	# Create figure
-	fig = pylab.figure(frameon=False, figsize=(10.0, 7.0))
+	fig = pylab.figure(frameon=False, figsize=(5.0, 3.0))
 	ax = pylab.Axes(fig, [0., 0., 1., 1.])
 
 	ax.set_axis_off()
@@ -122,10 +125,27 @@ def matchPoints(im1, im2, matches, dist = None, filename = None, max_dist = 100)
 	else :
 		cs = ['#00aaff' for m in matches]
 
+	# Get colors for images
+	if dist_im1 != None and len(dist_im1) == len(matches_im1) :
+		cs_im1 = [colors.getRedGreen(numpy.log(d+1)/numpy.log(max_dist)) for d in dist_im1]
+	else :
+		cs_im1 = ['#00aaff' for m in matches]
+	if dist_im2 != None and len(dist_im2) == len(matches_im2) :
+		cs_im2 = [colors.getRedGreen(numpy.log(d+1)/numpy.log(max_dist)) for d in dist_im2]
+	else :
[…]

### 2013-05-31 text/clustering.tex
Added a bit of text about the test set

@@
 	\If{$ratio < threshold$}
-		\State $matches_{init}\gets \left(f_i, f_m\right)$
+		\State $matches_{init} \gets \left(f_i, f_m\right)$
 	\EndIf
@@
 \If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
-getImg(f_j)$}
+getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
 		\State $matches_{final} \gets (f_i, f_j)$
-		\State $matches_{init} \gets matches_{init} \ (f_j, f_i)$
 	\EndIf
@@
 partitions. The sub figure \ref{fig:cropped_graph} shows a detailed 
-section of the graph where the interplay between small clusters 
-consisting of two or three nodes as well as larger clusters consisting 
+section of the graph where the interplay between small partitions 
+consisting of two or three nodes as well as larger partitions consisting 
 of several hundred nodes can be seen.
@@
 
-The clusters 
+The partitions group feature points by similarity which means that 
+repetitive structures such as buildings often feature in larger 
+partitions as exemplified in figure \ref{fig:compare_mirror}. Here the 
+cluster shown in part \ref{fig:pitts_partition} contains left window 
+corners from two buildings across both images. This is an example of 
+feature points that are hard to match correctly since each point will 
+have several similar potential matches.
+
 \begin{figure}
@@
 	\label{fig:compare_mirror}
-	\caption{Example of partitioning of keypoints in an image}
+	\caption{Example of a partition of keypoints in an image}
 \end{figure}
 
+The matching algorithm for \emph{MMC} (algorithm \ref{alg-getmatches}) 
+goes through the partitions one by one and selects matches in the 
+following way: If the partition has no edges going from a feature point 
+in one image to a feature point in another image, the partition is 
+discarded. If we have more than one edge going between images then 
+$getMatches$ will behave as \emph{MM} and make sure that a 
+correspondence is symmetric, that it has a ratio above the desired 
+threshold and that it isn't matching two feature points from the same 
+image. Since feature points are all guaranteed to be fairly similar this 
+means that we can set the ratio threshold much higher than in \emph{MM} 
+and include matches that would normally have been discarded for not 
+being sufficiently unique.
+However as can be seen in the example in figure \ref{fig:cropped_graph} 
+many of the partitions contain only two feature points from different 
+images linked by one edge. This is often the case if all edges below a 
+certain similarity threshold have been removed in the graph, in which 
+case it's probable that some nodes will end up with only one outgoing 
+edge. This doesn't necessarily imply that the correspondence represented 
+by the edge is unique, but the only way to figure out if it is, is by 
+checking the similarity scores of the nearest neighbor as proposed in 
+\cite{lowe2004sift}.
+
 \begin{algorithm}
-\caption{Impl. of GetMatches (\emph{from MMC algorithm})}
+\caption{Impl. of getMatches (\emph{from MMC algorithm})}
 \label{alg-getmatches}
@@
 
-Algorithm \ref{alg-mmc} shows the basic steps taken to find matches in 
-two or more images.
-
-This algorithm is a simplified version of the proposed method completely 
-agnostic of the geometry of the feature points in the picture. To better 
-explain the algorithm here is a step by step explication of the inputs 
-and functions mentioned:
-\begin{itemize}
-\item[]{\emph{images}: The images we are matching}
-\item[]{\emph{$n$}: The number of weights per row in the adjecency 
-matrix.}
-\item[]{\emph{getFeatures}: Returns a set of feature points given an 
-image. In practice the BRIEF\cite{calonder2010brief} feature point 
-detector and descriptor has worked well, but it could easily be replaced 
-with any other feature point type.} 
-% TODO: include a comparison of SURF, SIFT, etc
-\item[]{\emph{getAdjecencyMatrix}: Based on the distance measure used to 
-compare the similarity of the feature points a symmetric adjecency 
-matrix is returned.}
-\item[]{\emph{pruneEdges}: The result of the Louvain clustering depends 
-on the density of the graph. To ensure an optimal number of partitions 
-we only keep the $n$ highest weights per row and column in the adjecency 
-matrix, making sure it's still symmetric afterwards. In practice setting 
-$n$ to around four or five yields good results.}
-\item[]{\emph{cluster}: Cluster the graph corresponding to the adjecency 
-matrix given using the Louvain algorithm in \cite{blondel2008}.}
-\item[]{\emph{getPositions}: Given a trait consisting of features in 
-several different images, find the positions of traits in each image and 
-return them. This could either be done by taking a mean of the feature 
-points in an image, or by returning the position of the highest matching 
-feature points within the trait. In practice ... TODO}
-\end{itemize}
-
 The two algorithms introduced in this report are designed to work with 
@@
 
-\section{Experiments and Image Set}
+\section{Experimental Setup}
 \label{experiment}
+
+To reliably measure the accuracity of a matching method on real images 
+we either need a set of image pairs tied by a homography or manually 
+count the number of inliers. The latter poses becomes unfeasable the 
+moment we attempt to test a non-trivial set of images, but has the 
+advantage of working with any image pair. Using a homography between 
+image pairs reduces the test cases to images where the matched areas lie 
+on a plane, or alternatively that there is no viewpoint change. This 
+greatly reduces the body of image pairs we can use to reliably test 
+matching methods. In \cite{mikolaczyk2005performance} Mikolajczyk and 
+Schmid introduces a set of images to compare the performance of feature 
+detectors. The test set looks at different feature descriptors 
+invariance faced with different lighting, blur, rotation as well as 
+viewpoint change. However in practice the image used for the view point 
+change featuring a wall of graffiti\footnote{To ensure that all points 
+lie on the same plane} has gone on to be used the most for later tests 
+given that most of the other test pairs have since become relatively 
+trivial\footnote{see \cite{wu2011robust} or \cite{delponte2006svd} for 
+examples}.
+
+Inspired by this I have collected a set of image pairs featuring murals 
+of a few famous artists\footnote{Including Banksy, Blu and Shepard 
+Fairey among others}. Each pair consist of images of the same motif 
+taken from different angles, often including repetitive patterns and 
+texture. Based on this image set the two algorithms are tested on a 
+series of image patches from each pair. In order to test if a matching 
+is reliable we of course need correct matches when the image pair we are 
+testing on indeed features the same scene, but we also need to make sure 
+that we don't get any matches when the two images have nothing in 
+common. This means that it isn't enough just testing against pairs of 
+images that we know match. We also need to test against pairs that might 
+look like they could match but in fact don't.
+
+With this in mind I have created a test suite by cropping out $300$ 
+pixel by $300$ pixel patches of the original pair with a random vertical 
+and horizontal offset. Given an image pair I can obtain $n$ pairs of 
+patches where the two patches in any pair might or might not overlap.  
+This ensures that the patch pairs where there is no overlap still retain 
+a basic similarity to each other, while the patches that do overlap 
+often only overlap on a small part of their surface.
 
@@
 \label{results}
-\subsection{Graph Clustering}
-
-\subsubsection{On the subject of features}
-
-TODO: Show examples of the same image with feature points from different 
-detectors and explain the difference. Go in to why brief seems to work 
-best in practice and superficially explain how brief works compared with 
-SIFT.
-
-\begin{algorithm}
-\caption{Cluster-Match Algorithm With Geometry}
-\label{alg-geometry}
-\begin{algorithmic}
-\Require $images$ : set of images, $\alpha$ : float $\in \left[0, 
-1\right]$, $\beta$ : float $\in \left[0, 1\right]$
-\State $matches\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather features of all images
-	\State $f_i\gets getFeatures(I_i)$
-\EndFor
-\State $A\gets getAdjecencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $B\gets getGeomDistanceMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $M\gets getInterImageMask(f_1, f_2,\; \ldots \;, f_n)$
-\State $B_{norm}\gets 1 - normalize(G)$ \State $A_{norm}\gets 1 - 
-normalize(A)$
-\State $A_{geom}\gets A_{norm}\left[ \neg M\right] + \beta \cdot 
-B_{norm}\left[M\right]$
-\State $A_{pruned}\gets pruneEdges(A_{geom},\alpha)$
-\State $P\gets cluster(A_{pruned})$ 
-\ForAll{$p \in P$}
-	\State $trait\gets \left\{p \cap f_i \mid p \cap f_i \neq 
-\varnothing, f_i \in \left\{f_1, f_2,\; \ldots \;, f_n\right\}\right\}$
-	\If{$\left\vert trait \right\vert > 1$}
-		\State $matches\gets getPositions(trait)$
-		\Comment Position of trait in each image
-	\EndIf
-\EndFor \\
-\Return matches
-\end{algorithmic}
-\end{algorithm}
-
-While clustered feature points are often geometrically close together, 
-there might be cases where several points in the same image are similar 
-enough to all be included in one cluster despite their geometrical 
-distance.  To solve this problem we can either modify the clustering 
-algorithm to take the geometric distances into account like 
-\cite{das2008event}.  Alternatively we can modify the weight matrix to 
-penalize putting distanced feature points in the same cluster. However 
-we only know the geometrical distance between two feature points as long 
-as both belong to the same image. One way to approach this problem is to 
-replace all the weights of edges between two feature points within the 
-same image with their distance. For the case of two images the 
-normalized adjecency matrix is defined as follows:
-%
-$$A_{norm}=
-\begin{bmatrix}
-w_{1,1}   & w_{1,2}   & \ldots & w_{1,n-1}   & w_{1,n}     \\
-w_{2,1}   & w_{2,2}   & \ldots & w_{2,n-1}   & w_{2,n}     \\
-\vdots    & \vdots    & \ddots & \vdots      & \vdots      \\
-w_{n-1,1} & w_{n-1,2} & \ldots & w_{n-1,n-1} & w_{n-1,n}   \\
-w_{n,1}   & w_{n,2}   & \ldots & w_{n,n-1}   & w_{n,n}
-\end{bmatrix}=
-\begin{bmatrix}
-A_{im1} & S       \\
-T       & A_{im2} \\
-\end{bmatrix}
-$$
-%
-In a similar manner we can define an adjecency matrix based on the 
-geometrical distance. Note for example how $d_{1,n}$ can take any value 
-as it denotes the geometric distance of feature points in two different 
-images and as such can be set to any value.
-%
-$$B_{norm}=
-\begin{bmatrix}
-d_{1,1}   & d_{1,2}   & \ldots & d_{1,n-1}   & d_{1,n}     \\
-d_{2,1}   & d_{2,2}   & \ldots & d_{2,n-1}   & d_{2,n}     \\
-\vdots    & \vdots    & \ddots & \vdots      & \vdots      \\
-d_{n-1,1} & d_{n-1,2} & \ldots & d_{n-1,n-1} & d_{n-1,n}   \\
-d_{n,1}   & d_{n,2}   & \ldots & d_{n,n-1}   & d_{n,n}
-\end{bmatrix}=
-\begin{bmatrix}
-B_{im1} & R       \\
-Q       & B_{im2} \\
-\end{bmatrix}
-$$
-%
-Given these two and a weight factor $\beta$ we can construct a new 
-weight matrix as follows:
-%
-$$C=
-\begin{bmatrix}
-\beta \cdot B_{im1} & S       \\
-T       & \beta \cdot B_{im2} \\
-\end{bmatrix}
-$$
-%
-Since we prune the matrix afterwards, it's important to choose a weight 
-factor that doesn't lead to all edges being either intra image edges or 
-intra image edges, since the first would create no clusters across 
-images and the latter would mean that the geometrical information would 
-be discarded and the bipartite graph constituting of edges between 
-feature points in the two images would be used instead.
 

### 2013-06-03 text/clustering.tex
Added more text and a few images

@@
+%\documentclass[12pt,journal,compsoc]{IEEEtran}
 \documentclass{article}
 \usepackage{graphicx}
+\usepackage{cite}
 \usepackage{hyperref}
@@
 
-\title{Clustering feature points}
+\title{Reliable feature point matching without the use of geometric 
+constraints}
 \author{Jonas Arnfred}
@@
 \begin{abstract}
-% TODO!
+Many algorithms have been proposed to solve the problem of matching 
+feature points in two or more images using geometric assumptions to 
+increase the robustness of the matching. However very little work 
+addresses the case where these assumptions might not hold true. In 
+particular few methods address the problem of reliable matching in cases 
+where we don't know if two images have any corresponding areas or 
+objects. In this paper we propose two algorithms for matching feature 
+points without the use of geometric constraints. The first makes use of 
+the fact that any match between two images should be better than all 
+possible matches within the image itself. The second algorithm extends 
+this idea by using the community structure in the similarity graph of 
+feature points to reliably find correspondences. To evaluate the 
+algorithms experimentally we introduce an image set of 8 image pairs all 
+containing view port changes and a simple method to generate a large 
+amount of test cases based on these 8 pairs. The experimental results 
+show that the proposed algorithm, overall, is superior to traditional 
+approaches in finding correct correspondences.
 \end{abstract}
@@
 
-\section{Experimental Setup}
+\section{Experiments}
 \label{experiment}
@@
 a basic similarity to each other, while the patches that do overlap 
-often only overlap on a small part of their surface.
+often only overlap on a small part of their surface. Figure 
+\ref{fig:fairey} shows an example of possible pairs of test images 
+(\ref{fig:fairey_crop}) produced from two source images 
+(\ref{fig:fairey1} and \ref{fig:fairey2}). Producing $n$ such pairs 
+allows us to test not just how well the matching algorithm performs on 
+corresponding images, but also how many false positives we get on 
+similar images that don't overlap.
+
+The set of source images and homographies as well as the a script to 
+generate the cropped test sets based on them have been published. The 
+actual testsets used for testing in this paper are also available 
+online\footnote{They can be found on INSERT URL HERE}.
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.50\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pair_example1}
+			\caption{Mural by Fairey (1)}
+			\label{fig:fairey1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.50\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pair_example2}
+			\caption{Mural by Fairey (2)}
+			\label{fig:fairey2}
+		\end{subfigure}%
+	}%
+	\\
+	\makebox[\textwidth][c]{
+		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+
+		\begin{subfigure}[t]{1.16\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/crop_examples}
+			\caption{Image pairs}
+			\label{fig:fairey_crop}
+		\end{subfigure}%
+	}%
+	\label{fig:fairey}
+	\caption{Example of test set produced by pair of images}
+\end{figure}
+
+\subsection{Experimental setup}
+
+Using the image test sets described above, the \emph{MM} and \emph{MMC} 
+algorithms have been tested against a baseline algorithm incorporating 
+ideas from the algorithm Lowe proposed in \cite{lowe2004sift} as well as 
+the gold standard algorithm for calculating homographies proposed in 
+\cite{multipleView}. For reference the algorithm can be seen in 
+\ref{alg:baseline}.
+
+\begin{algorithm}
+\caption{Baseline Match Algorithm (\emph{BM})}
+\label{alg:baseline}
+\begin{algorithmic}
+\Require $image_1$ : image, $image_2$ : image, $threshold$ : float $\in 
+\mathbb{R}$
+\State $matches_{init}\gets \varnothing$
+\State $matches_{final}\gets \varnothing$
+\State $features_1 \gets getFeatures(image_1)$
+\State $features_2 \gets getFeatures(image_2)$
+\ForAll{$f_i \in features_1$} \Comment Get best match for all features 
+in $image_1$
+	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features_2)$
+	\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
+	f_m)$
+	\If{$ratio < threshold$}
+		\State $matches_{init} \gets \left(f_i, f_m\right)$
+	\EndIf
+\EndFor
+%
+\ForAll{$f_i \in features_2$} \Comment Get best match for all features 
+in $image_2$
+	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features_1)$
+	\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
+	f_m)$
+	\If{$ratio < threshold$}
+		\State $matches_{init} \gets \left(f_i, f_m\right)$
+	\EndIf
+\EndFor
+%
+\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
+matches
+\If{$\left(f_j, f_i \right) \in matches_{init} \wedge \left(f_j, 
+f_i\right) \not\in matches_{final}$}
+		\State $matches_{final} \gets (f_i, f_j)$
+	\EndIf
+\EndFor \\
+\Return $matches_{final}$
+\end{algorithmic}
+\end{algorithm}
+
+For each test set of cropped image pairs the three 
+algorithms\footnote{\emph{MM}, \emph{MMC} and \emph{BM}} are applied to 
+each pair of images, and the threshold for each is varied over 50 evenly 
+spaced values. For \emph{MM} and \emph{BM} these values lie between 
+$0.4$ and $0.8$ where as the threshold for \emph{MMC} is varied between 
+$0.8$ and $1.0$. For each match returned by any of the algorithms, the 
+match is registered as an inlier if the endpoint in the second image 
+lies within $5$px of the true position calculated by the homography.  
+That is, given $H$ relating $I_1$ with $I_2$ and a match ($p_1, p_2$) 
+then the match is an inlier if $\left\vert Hp_1 - p_2 \right\vert < 5$.  
+This is a relatively lenient threshold since radial distortion from the 
+lens as well as inconsistencies to the planar assumption of the 
+background means that $H$ can not be entirely accurate. The experiments 
+are run on the $8$ image pairs in the test set, as well as the graf 
+image from \cite{mikolajczyk2005performance}.
 
@@
 
-\bibliographystyle{abbrv}
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/fairey_burma_1}
+			\caption{Burma by Fairey (1)}
+			\label{fig:burma1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/fairey_burma_2}
+			\caption{Burma by Fairey (2)}
+			\label{fig:burma2}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_fairey_burma}
+			\caption{X: Nb of correct matches. Y: Accuracity}
+			\label{fig:result_burma}
+		\end{subfigure}%
+	}%
+	\label{fig:burma}
+	\caption{results on Burma by Fairey}
+\end{figure}
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.25\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/fairey_lady_1}
+			\caption{Lady by Fairey (1)}
+			\label{fig:lady1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.25\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/fairey_lady_2}
+			\caption{Lady by Fairey (2)}
+			\label{fig:lady2}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.55\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_fairey_lady}
+			\caption{X: Nb of correct matches. Y: Accuracity}
+			\label{fig:result_lady}
+		\end{subfigure}%
+	}%
+	\label{fig:lady}
+	\caption{results on Lady by Fairey}
+\end{figure}
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/scharf_1}
+			\caption{Faces by Scharf (1)}
+			\label{fig:faces1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/scharf_2}
+			\caption{Faces by Scharf (2)}
+			\label{fig:faces2}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_scharf}
+			\caption{X: Nb of correct matches. Y: Accuracity}
+			\label{fig:result_faces}
+		\end{subfigure}%
+	}%
+	\label{fig:faces}
+	\caption{results on Faces by Scharf}
+\end{figure}
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/houston_1}
+			\caption{Houston (1)}
+			\label{fig:houston1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/houston_2}
+			\caption{Houston (2)}
+			\label{fig:houston2}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_houston}
+			\caption{X: Nb of correct matches. Y: Accuracity}
+			\label{fig:result_houston}
+		\end{subfigure}%
+	}%
+	\label{fig:houston}
+	\caption{Results on Houston}
+\end{figure}
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.25\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/blu_head_1}
+			\caption{head by blu (1)}
+			\label{fig:head1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.25\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/blu_head_2}
+			\caption{head by blu (2)}
+			\label{fig:head2}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.55\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_blu_head}
+			\caption{X: Nb of correct matches. Y: Accuracity}
+			\label{fig:result_head}
+		\end{subfigure}%
+	}%
+	\label{fig:head}
+	\caption{results on head by blu}
+\end{figure}
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.25\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/blu_pencil_1}
+			\caption{Pencil by Blu (1)}
+			\label{fig:pencil1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.25\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/blu_pencil_2}
+			\caption{Pencil by Blu (2)}
+			\label{fig:pencil2}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.55\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_blu_pencil}
+			\caption{X: Nb of correct matches. Y: Accuracity}
+			\label{fig:result_pencil}
+		\end{subfigure}%
+	}%
+	\label{fig:pencil}
+	\caption{Results on Pencil by Blu}
+\end{figure}
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/banksy_city_1}
+			\caption{City by Banksy (1)}
+			\label{fig:city1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/banksy_city_2}
+			\caption{City by Banksy (2)}
+			\label{fig:city2}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_banksy_city}
+			\caption{X: Nb of correct matches. Y: Accuracity}
+			\label{fig:result_city}
+		\end{subfigure}%
+	}%
+	\label{fig:city}
+	\caption{results on City}
+\end{figure}
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/banksy_stroller_1}
+			\caption{Stroller by Banksy (1)}
+			\label{fig:stroller1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/banksy_stroller_2}
+			\caption{Stroller by Banksy (2)}
+			\label{fig:stroller2}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_banksy_stroller}
+			\caption{X: Nb of correct matches. Y: Accuracity}
+			\label{fig:result_stroller}
+		\end{subfigure}%
+	}%
+	\label{fig:stroller}
+	\caption{Results on Stroller by Banksy}
+\end{figure}
+
+\begin{figure}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/graf_1}
+			\caption{Graf (1)}
+			\label{fig:graf1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/graf_3}
+			\caption{Graf (3)}
+			\label{fig:graf3}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.35\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_graf}
+			\caption{X: Nb of correct matches. Y: Accuracity}
+			\label{fig:result_graf}
+		\end{subfigure}%
+	}%
+	\label{fig:graf}
+	\caption{results on Graf}
+\end{figure}
+
+In figure \ref{fig:stroller} to \ref{fig:graf} the results on the images
+
+\bibliographystyle{IEEEtran}
 \bibliography{bibliography}

### 2013-06-03 code/display.py

@@ -286,14 +286,14 @@ def accuDetail(correct, total, legend, ylim = 100, treshold=1000) :
 	accuHist(accu, legend, ylim=ylim)
 
 
-def accuPlot(correct, total, legends, ylim=0.0) :
+def accuPlot(correct, total, legends, ylim=(0.0,1.01)) :
 	for ts,cs,l,color in zip(total, correct, legends, ["blue", "cyan", "green", "orange", "red"]) :
 		xs = [sum(c) for c in cs]
 		ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for (c, t) in zip(cs, ts)]
 		pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.65)
 		pylab.legend(loc="best")
 	removeDecoration()
-	pylab.ylim(ylim,1.01)
+	pylab.ylim(ylim[0],ylim[1])
 
 
 def distHist(dist, dist_treshold = 5, dist_distinct = None, accuracity = None, accu_y_lim = 100) :

### 2013-06-04 text/clustering.tex
Modified the accuPlot function a bit

@@
 \documentclass{article}
+\usepackage{footnote}
 \usepackage{graphicx}
@@
 feature points to reliably find correspondences. To evaluate the 
-algorithms experimentally we introduce an image set of 8 image pairs all 
+algorithms experimentally we introduce a set of 8 image pairs all 
 containing view port changes and a simple method to generate a large 
@@
 
-Since the introduction of feature points, several methods for matching 
-them across images have been proposed in order to maximize the amount of 
-correct matches. In this part of the project I introduce two methods to 
-reliably match feature points. The word 'reliable' covers that matches 
-only are returned if they are judged as sound. That is, matches should 
-only be returned if there are objects or scenes that appear in both 
-images.
+When matching feature points between two images we are faced with the 
+dilemma of choosing a feature descriptor. We can either choose a 
+discriminative descriptor that has a high accuracy but little 
+robustness. Alternatively a robust descriptor will better match features 
+across changes such as illumination, perspective and image quality at 
+the expense of accuracy.
 
-When matching feature points between two images we are often faced with 
-a dilemma between making the feature descriptor more discriminative to 
-make sure only correct matches are made, and making it less 
-discriminative to increase the robustness of the descriptor over 
-different changes such as illumination, perspective and image quality.  
-Any feature type aiming for robustness will have cases where it isn't 
-possible to generate reliable matches if we only look at the pairwise 
-correspondence of the descriptors.
-
-To get around this limitation several methods have been proposed in the 
-literature. One of the most fruitful approaches have been to look at the 
-geometric configuration of the feature points and match them with 
-respect to assumptions concerning the variance between images. For 
-example an angular and distance constraint between matches as considered 
-by \cite{kim2008efficient} performs well in situations where no camera 
-rotation occurs between the two images but will likely fail in other 
-cases. Various scenarios have been proposed to improve on this simple 
-assumption such as epipolar constraints (\cite{torr2000mlesac}, 
-\cite{chum2005matching}) and pairwise constraints 
-(\cite{choi2009robust}, \cite{leordeanu2005spectral}). The Epipolar 
-constraint carries the assumption that the two images matched are 
-related by an affine transformation. That is, there is no relative 
-movement of objects in between images and either the viewpoint is fixed 
-or the image resides entirely on a plane. In practice this assumption 
-largely holds true when all objects we are interested in matching are 
-roughly the same distance from the camera and when we don't expect to 
-match objects that aren't consistently positioned across images.  
-Pairwise constraints provide a more robust approach to this problem by 
-looking at a set of proposed correspondences and defining a pairwise 
-error between any two matches usually based on the assumption that two 
-neighboring correspondences will usually have similar angles and 
-distances. We can then convert the problem to an optimization problem 
-and return a set of correspondences that minimizes this error such as 
-proposed in \cite{choi2009robust} and \cite{leordeanu2005spectral}.  
-This approach provides more robustness because assumptions that might 
-not be true globally often still holds on a local level.
+To get the advantage of a robust descriptor while maintaining a high 
+accuracy, several methods have been proposed in the literature to better 
+match the resulting descriptors.  In particular many approaches look at 
+the geometric configuration of the feature points and match them with 
+according to assumptions made about the geometric relationship between 
+the images matched. A simple example is an angular and distance 
+constraint between matches as considered by \cite{kim2008efficient}.  
+This performs well in situations where no camera rotation occurs between 
+the two images, but fails when this assumption isn't met. Various 
+scenarios have been proposed to improve on this simple assumption such 
+as epipolar constraints (\cite{torr2000mlesac}, \cite{chum2005matching}) 
+and pairwise constraints (\cite{choi2009robust}, 
+\cite{leordeanu2005spectral}). The Epipolar constraint carries the 
+assumption that the two images matched are related by an affine 
+transformation. That is, there is no relative movement of objects in 
+between images and either the viewpoint is fixed or the image resides 
+entirely on a plane. In practice this assumption largely holds true when 
+all objects we are interested in matching are roughly the same distance 
+from the camera and when we don't expect to match objects that aren't 
+consistently positioned across images.  Pairwise constraints provide a 
+more robust approach by looking at a set of proposed correspondences and 
+defining a pairwise error between any two matches usually based on the 
+assumption that two neighboring correspondences will usually have 
+similar angles and distances. We can then convert the problem to an 
+optimization problem and return a set of correspondences that minimizes 
+this error such as proposed in \cite{choi2009robust} and 
+\cite{leordeanu2005spectral}. This approach provides more robustness in 
+cases where assumptions will be violated globally but might still hold 
+true on a local scale.
 
 Another approach proposed in the literature is to pick out different 
-zones in each image and find a pairing of zones where feature points are 
-only matched within the same zone. \cite{das2008event} proposes 
-clustering the feature points using their geometric position and 
-matching only feature points between groups that have a certain amount 
-of matchings between them. A more sophisticated approach is introduced 
-in \cite{wu2011robust} where the zones are created by surrounding MSER 
-feature points by an ellipse and grouping the SIFT or SURF feature 
-points that fall within the ellipse together. These points can then be 
-matched according to epipolar constraints.
+zones in each image and pair zones when correspondence pairs are mainly 
+found going from one zone to another. This allows for the filtering of 
+all correspondences that do not fall within paired zones.  
+\cite{das2008event} proposes clustering feature points by using their 
+geometric position and exclude correspondences that are geometrically 
+deviant. A more sophisticated approach is introduced in 
+\cite{wu2011robust} where the zones are created by using the MSER 
+feature detector to find areas of interest in the images. These areas 
+can be defined as an ellipse with a certain radius around the interest 
+points. The feature points that fall within this ellipse are then 
+matched according to epipolar constraints. This approach is inspired by 
+\cite{wu2009bundling} where bundling of feature points was used to 
+enhance the search results in large scale partial-duplicate web image 
+search.
 
@@
 often arise when the assumptions made by a geometric method turns out 
-not to hold in a particular use case. This could matchings between 
+not to hold in a particular use case. This could be matchings between 
 images where the content has been scrambled or with so little 
 consistency that even the geometric assumptions break down even on a 
-local level. In addition the geometric methods all require a set of 
-correspondences to begin with. If this set of correspondences is 
-narrowed down to a smaller set with a higher ratio of inliers the result 
-of the geometric matching will be both faster and more accurate. Finally 
-some use cases might require a performance that can't be achieved by a 
-more complex geometric method where simple non geometric methods might 
-be able to provide additional matching accuracy with a smaller 
-performance penalty. This approach is inspired by \cite{wu2009bundling} 
-where bundling of feature points was used to enhance the search results 
-in large scale partial-duplicate web image search.
+local level. In addition methods using geometric constraints all require 
+a set of correspondences to begin with. If this set of correspondences 
+is narrowed down to a smaller set with a higher ratio of correct matches 
+the result of the geometric matching will be both faster and more 
+accurate.  Finally some use cases might require a performance that can't 
+be achieved by a more complex geometric method where simple non 
+geometric methods might be able to provide additional matching accuracy 
+with a smaller performance penalty.
 
@@
 \begin{itemize}
-\item{\emph{Mirror Match (MM)}: Match features using the gold standard 
-algorithm\cite[p. 114]{multipleView} ranked by similarity and thresheld 
-by uniqueness\cite{lowe2004sift}. However instead of matching features 
-from one image with features in another, we match every feature with all 
-other features of the two images combined. Only matches from one image 
-to the other are returned.}
-\item{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
-of feature points from both images and cluster these points according to 
-their descriptors. Given a resulting partition of points, no matches are 
-returned if it contains only feature points from one image. If the 
-partition contains points from both images, \emph{Mirror Match} is used 
-to find the best matches within the partition.}
+\item[]{\emph{Mirror Match (MM)}: Match features using the gold standard 
+		algorithm\cite[p. 114]{multipleView} ranked by similarity and 
+		thresheld by uniqueness\cite{lowe2004sift}.  However instead of 
+		matching features from one image with features in another, we 
+	match every feature with all other features of the two images 
+combined. Only matches from one image to the other are returned.}
+\item[]{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
+		of feature points from both images and cluster these points 
+		according to their descriptors. Given a resulting partition of 
+		points, no matches are returned if it contains only feature 
+	points from one image. If the partition contains points from both 
+images, \emph{Mirror Match} is used to find the best matches within the 
+partition.}
 \end{itemize}
@@
 between two images is unambiguous in the sense that there are no other 
-equally (or almost equally) good potential matches to the same point.  
-This is the key insight behind the algorithm presented by Lowe in 
-\cite{lowe2004sift}. However the implication doesn't follow the other 
-way around. In the case that a feature point don't have any actual 
-correspondence in the other image, there is no guarantee that this 
-feature point might not still be uniquely matched to a feature point in 
-the other image. The issue is particularly pronounced if we compare two 
-images that don't correspond. For any proposed correspondence it is 
-entirely probable that this correspondence is unique even if it isn't 
-correct. With Mirror Match this ambiguity is avoided by incorporating 
-the feature points of both images when a match is made. When the two 
-images have nothing to do with each other, chances are that a feature 
-point will match better with another feature point from the same image 
-in which case it is easily discarded.
+equally good potential matches to the same point.  This is the key 
+insight behind the algorithm presented by Lowe in \cite{lowe2004sift}.  
+However the implication doesn't follow the other way around. In the case 
+that a feature point doesn't have a true correspondence there might 
+still exist point with which the feature point is uniquely matched. The 
+issue is particularly pronounced if we compare two images that don't 
+correspond. For any proposed correspondence it is entirely probable that 
+this correspondence is unique even if it isn't correct. With Mirror 
+Match this ambiguity is avoided by incorporating the feature points of 
+both images when a match is made. When the two images have no overlap or 
+objects in common, chances are that a feature point will match better 
+with another feature point from the same image in which case it is 
+easily discarded.
 
@@
 match\footnote{In fact this particular problem has been given attention 
-before by for example \cite{fan2011towards}} because the feature points 
-covering these patterns will look very similar. If we threshold by 
-uniqueness like in Mirror Match this means that these points will often 
-be discarded even if they might have good correspondences. To solve this 
-problem the enhanced Mirror Match with Clustering makes it possible to 
-look at groups of similar feature points one at a time and within each 
-group finding the best matches. This is done by taking the set of 
-feature points from both images and clustering. The resulting partitions 
-will each contain feature points that are similar to each other. In some 
-cases the clustering will end up grouping feature points of only one 
-image together which can then easily be discarded in the matching 
-process. In other cases partitions will contain feature points from both 
-images that can then be matched using \emph{MM} but with lower 
-thresholds.
-
-The report is organized as follows. In section \ref{algorithms} I will 
-describe the two algorithms. Section \ref{experiment} will cover the 
-experimental set up and introduce the image set that is used in testing.  
-In section \ref{results} I will go through the results and conclude.
+before by for example \cite{fan2011towards}} because the feature 
+descriptors covering these patterns will be similar. If we remove points 
+that aren't deemed sufficiently unique like in \emph{MM} this means that 
+these points will often be discarded even if they are correctly matched.
+\emph{MMC} makes it possible to look at groups of similar feature points 
+one at a time and within each group find the best matches. This is done 
+by taking the set of feature points from both images and cluster them by 
+their similarity. In some cases the clustering will end up grouping 
+feature points of only one image together which can then easily be 
+discarded in the matching process.  In other cases partitions will 
+contain similar feature points from both images that can then be matched 
+using \emph{MM} but with much lower thresholds.
 
@@
 \label{algorithms}
-
-To discuss the implementation of \emph{MM} and \emph{MMC} a few notes on 
-notation will be helpful. BLAH BLAH!
 
@@
 image.  In practice the feature used for the experiments have been 
-SIFT\cite{lowe2004sift}, but there aren't any reason why other features 
+SIFT\cite{lowe2004sift}, but there are no reasons why other features 
 such as SURF\cite{bay2006surf} or BRIEF\cite{calonder2010brief} couldn't 
-be used just as well. The matching state uses K-Nearest Neighbors to 
-return the two closest neighbors in the set of features for any given 
+be used just as well. The features are matched using K-Nearest Neighbors 
+to return the two closest neighbors in the set of features for any given 
 feature $f_i$ and calculates the ratio between the correspondences as 
@@
 
-Figure \ref{fig:compare_mirror} shows an example of the performance of 
-\emph{MM}. In sub figure \ref{fig:unique} the result of a normal 
-matching of two images is shown. The two images appear side by side and 
-for each correspondence between them, a line has been drawn from one 
-image to the other. The color of the line indicates if the 
-correspondence is accurate. Sub figure \ref{fig:within} shows the 
-correspondences found by mirror match using the same threshold before 
-the matches within the same image has been filtered out. In particular 
-the fence by the bottom of the image admits correspondences that can 
-conveniently be removed as done in sub figure \ref{fig:without} where 
-only the actual correspondences returned by the algorithm are shown.
+Figure \ref{fig:compare_mirror} shows an example of the result of 
+\emph{MM}. In figure \ref{fig:unique} the result of a normal matching of 
+two images is shown. The two images appear side by side and for each 
+correspondence between them, a line has been drawn from one image to the 
+other. The color of the line indicates if the correspondence is 
+accurate. Figure \ref{fig:within} shows the correspondences found by 
+mirror match using the same threshold before the matches within the same 
+image has been filtered out. In particular the fence by the bottom of 
+the image admits correspondences that can conveniently be removed as 
+done in sub figure \ref{fig:without} where only the actual 
+correspondences returned by the algorithm are shown.
 
@@
 similarity. This process yields partitions of fairly similar feature 
-points that we can match using the same approach as \emph{MM}. Before I 
-introduce the implementation details I will go over the problem of graph 
+points that we can match using the same approach as \emph{MM}. Before we 
+introduce the implementation details we will go over the problem of graph 
 clustering and how it relates to feature matching.
@@
 function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-points in an image and return their matching score, we can define a 
+points in an image and returns their matching score, we can define a 
 matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
@@
 
-Based on these observations I've decided to use Louvain clustering for 
-grouping feature points since it's fast, performs well, doesn't require 
+Based on these observations we use Louvain clustering for grouping 
+feature points since it's fast, performs well, doesn't require 
 parameters and doesn't emphasize partitions of equal sizes.
@@
 
-Unlike the \emph{MM} algorithm the feature points are partitioned before 
-the matching stage. While the louvain clustering algorithm doesn't 
-require any parameters in itself, it tends towards clustering all 
-feature points together in the same partition if the graph is fully 
-connected or close. To ensure that the graph is well clustered, the 
-adjacency matrix is pruned so only edges above a certain threshold is 
-kept. From empirical analysis keeping around 2.5\% of edges seems to 
-work well. Figure \ref{fig:graph} shows the result of clustering the 
-feature points displayed as a graph where each node correspond to a 
-feature point. Here the border of nodes signifies the original image 
-while the color of the node is decided by what partition it belongs to.  
-Notice that since a limited amount of colors are used disconnected 
-subgraphs of the same color can be assumed to belong to separate 
-partitions. The sub figure \ref{fig:cropped_graph} shows a detailed 
+While the louvain clustering algorithm doesn't require any parameters in 
+itself, it tends towards clustering all feature points together in the 
+same partition if the graph is very connected.  To ensure that the graph 
+is well clustered, the adjacency matrix is pruned so only edges above a 
+certain threshold is kept. From empirical analysis keeping around 2.5\% 
+of edges seems to work well. Figure \ref{fig:graph} shows the result of 
+clustering the feature points displayed as a graph where each node 
+correspond to a feature point. Here the border of nodes signifies the 
+original image while the color of the node is decided by what partition 
+it belongs to.  Notice that since a limited amount of colors are used 
+disconnected subgraphs of the same color can be assumed to belong to 
+separate partitions. Figure \ref{fig:cropped_graph} shows a detailed 
 section of the graph where the interplay between small partitions 
@@
 edge. This doesn't necessarily imply that the correspondence represented 
-by the edge is unique, but the only way to figure out if it is, is by 
+by the edge is unique, but the only way to discern if it is, is by 
 checking the similarity scores of the nearest neighbor as proposed in 
@@
 
-The two algorithms introduced in this report are designed to work with 
-feature points such as ,  or similar. While the experimental results 
-have all been done with the SIFT descriptor, there aren't any 
-theoretical or practical issues with using other types of feature 
-points.
-
-In this report I propose two algorithms for better matching feature 
-points without any geometric assumptions about the images matched. The 
-two algorithms are complementary in the sense that the first, Mirror 
-Match (\emph{MM}) is less complex but performs slightly worse than 
-Mirror Match with Clustering (\emph{MMC}). In cases where high
-
 \section{Experiments}
@@
 
-To reliably measure the accuracity of a matching method on real images 
-we either need a set of image pairs tied by a homography or manually 
-count the number of inliers. The latter poses becomes unfeasable the 
-moment we attempt to test a non-trivial set of images, but has the 
-advantage of working with any image pair. Using a homography between 
-image pairs reduces the test cases to images where the matched areas lie 
-on a plane, or alternatively that there is no viewpoint change. This 
-greatly reduces the body of image pairs we can use to reliably test 
-matching methods. In \cite{mikolaczyk2005performance} Mikolajczyk and 
-Schmid introduces a set of images to compare the performance of feature 
-detectors. The test set looks at different feature descriptors 
-invariance faced with different lighting, blur, rotation as well as 
-viewpoint change. However in practice the image used for the view point 
-change featuring a wall of graffiti\footnote{To ensure that all points 
-lie on the same plane} has gone on to be used the most for later tests 
-given that most of the other test pairs have since become relatively 
-trivial\footnote{see \cite{wu2011robust} or \cite{delponte2006svd} for 
-examples}.
+To reliably measure the accuracy of a matching method on real images we 
+either need a set of image pairs tied by a homography or manually count 
+the number of inliers. The latter becomes unfeasible the moment we 
+attempt to test a non-trivial set of images, but has the advantage of 
+working with any image pair. Using a homography between image pairs 
+reduces the test cases to images where the matched areas lie on a plane, 
+or alternatively that there is no viewpoint change. This greatly reduces 
+the body of image pairs we can use to reliably test matching methods. In 
+\cite{mikolaczyk2005performance} Mikolajczyk and Schmid introduces a set 
+of images to compare the performance of feature detectors. The test set 
+covers different types of image variance such as different lighting, 
+blur, rotation as well as viewpoint change.  However in practice the 
+image used for the view point change featuring a wall of 
+graffiti\footnote{To ensure that all points lie on the same plane} has 
+gone on to be used the most for later tests given that most of the other 
+test pairs have since become relatively trivial to match\footnote{see 
+\cite{wu2011robust} or \cite{delponte2006svd} for examples}.
 
-Inspired by this I have collected a set of image pairs featuring murals 
-of a few famous artists\footnote{Including Banksy, Blu and Shepard 
-Fairey among others}. Each pair consist of images of the same motif 
-taken from different angles, often including repetitive patterns and 
-texture. Based on this image set the two algorithms are tested on a 
-series of image patches from each pair. In order to test if a matching 
-is reliable we of course need correct matches when the image pair we are 
-testing on indeed features the same scene, but we also need to make sure 
-that we don't get any matches when the two images have nothing in 
-common. This means that it isn't enough just testing against pairs of 
-images that we know match. We also need to test against pairs that might 
-look like they could match but in fact don't.
+Inspired by the graffiti image we have collected a set of image pairs 
+featuring murals of a few different artists\footnote{Including Banksy, 
+Blu and Shepard Fairey among others}. Each pair consist of images of the 
+same motive taken from different angles, often including repetitive 
+patterns and texture. Based on this image set the two algorithms are 
+tested on a series of image patches from each pair. To verify that the 
+algorithms proposed are reliable we need to test that we get good 
+matches when images overlap and that we get no matches when they don't.  
+This means that it isn't enough just testing against pairs of images 
+that we know match.  We also need to test against pairs that might look 
+like they could match but in fact don't.
 
-With this in mind I have created a test suite by cropping out $300$ 
+With this in mind we have created a test suite by cropping out $300$ 
 pixel by $300$ pixel patches of the original pair with a random vertical 
-and horizontal offset. Given an image pair I can obtain $n$ pairs of 
-patches where the two patches in any pair might or might not overlap.  
-This ensures that the patch pairs where there is no overlap still retain 
-a basic similarity to each other, while the patches that do overlap 
-often only overlap on a small part of their surface. Figure 
-\ref{fig:fairey} shows an example of possible pairs of test images 
-(\ref{fig:fairey_crop}) produced from two source images 
-(\ref{fig:fairey1} and \ref{fig:fairey2}). Producing $n$ such pairs 
-allows us to test not just how well the matching algorithm performs on 
-corresponding images, but also how many false positives we get on 
-similar images that don't overlap.
+and horizontal offset. Given a source image pair we can obtain $n$ pairs 
+of patches where the two patches in any pair might or might not overlap.  
+This ensures that the patch pairs whith no overlap still retain a basic 
+similarity to each other, while the patches that do overlap often only 
+overlap on a small part of their surface. Figure \ref{fig:fairey} shows 
+an example of possible pairs of test images (\ref{fig:fairey_crop}) 
+produced from two source images (\ref{fig:fairey1} and 
+\ref{fig:fairey2}). Producing $n$ such pairs allows us to test not just 
+how well the matching algorithm performs on corresponding images, but 
+also how many false positives we get on similar images that don't 
+overlap.
 
@@
 Using the image test sets described above, the \emph{MM} and \emph{MMC} 
-algorithms have been tested against a baseline algorithm incorporating 
-ideas from the algorithm Lowe proposed in \cite{lowe2004sift} as well as 
-the gold standard algorithm for calculating homographies proposed in 
-\cite{multipleView}. For reference the algorithm can be seen in 
-\ref{alg:baseline}.
-
-\begin{algorithm}
-\caption{Baseline Match Algorithm (\emph{BM})}
-\label{alg:baseline}
-\begin{algorithmic}
-\Require $image_1$ : image, $image_2$ : image, $threshold$ : float $\in 
-\mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
-\State $features_1 \gets getFeatures(image_1)$
-\State $features_2 \gets getFeatures(image_2)$
-\ForAll{$f_i \in features_1$} \Comment Get best match for all features 
-in $image_1$
-	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features_2)$
-	\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
-	f_m)$
-	\If{$ratio < threshold$}
-		\State $matches_{init} \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-%
-\ForAll{$f_i \in features_2$} \Comment Get best match for all features 
-in $image_2$
-	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features_1)$
-	\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
-	f_m)$
-	\If{$ratio < threshold$}
-		\State $matches_{init} \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-%
-\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
-matches
-\If{$\left(f_j, f_i \right) \in matches_{init} \wedge \left(f_j, 
-f_i\right) \not\in matches_{final}$}
-		\State $matches_{final} \gets (f_i, f_j)$
-	\EndIf
-\EndFor \\
-\Return $matches_{final}$
-\end{algorithmic}
-\end{algorithm}
-
-For each test set of cropped image pairs the three 
-algorithms\footnote{\emph{MM}, \emph{MMC} and \emph{BM}} are applied to 
-each pair of images, and the threshold for each is varied over 50 evenly 
-spaced values. For \emph{MM} and \emph{BM} these values lie between 
-$0.4$ and $0.8$ where as the threshold for \emph{MMC} is varied between 
-$0.8$ and $1.0$. For each match returned by any of the algorithms, the 
-match is registered as an inlier if the endpoint in the second image 
-lies within $5$px of the true position calculated by the homography.  
-That is, given $H$ relating $I_1$ with $I_2$ and a match ($p_1, p_2$) 
-then the match is an inlier if $\left\vert Hp_1 - p_2 \right\vert < 5$.  
-This is a relatively lenient threshold since radial distortion from the 
-lens as well as inconsistencies to the planar assumption of the 
-background means that $H$ can not be entirely accurate. The experiments 
-are run on the $8$ image pairs in the test set, as well as the graf 
-image from \cite{mikolajczyk2005performance}.
+algorithms have been tested against a the algorithm Lowe proposed in 
+\cite{lowe2004sift} as well as the isodata matching algorithm proposed 
+in \cite{das2008event}.  For each test set of cropped image pairs the 
+four algorithms\footnote{\emph{MM}, \emph{MMC}, \emph{SIFT} and 
+\emph{Isodata}} are applied to each pair of images ($100$ per test set), 
+and the threshold for each algorithm is varied over 50 evenly spaced 
+values.  For \emph{MM} and \emph{SIFT} these values lie between $0.4$ 
+and $0.8$ where as the threshold for \emph{MMC} and \emph{Isodata} is 
+varied between $0.8$ and $1.0$.  For each match returned by any of the 
+algorithms, the match is registered as an inlier if the endpoint in the 
+second image lies within $5$px of the true position calculated by the 
+homography.  That is, given $H$ relating $I_1$ with $I_2$ and a match 
+($p_1, p_2$) then the match is an inlier if $\left\vert Hp_1 - p_2 
+\right\vert < 5$.  This is a relatively lenient threshold since radial 
+distortion from the lens as well as inconsistencies to the planar 
+assumption of the background means that $H$ usually isn't entirely 
+accurate. The experiments are run on the $8$ image pairs in the test 
+set, as well as the graf image from \cite{mikolajczyk2005performance}.
 
@@
 			\includegraphics[width=\textwidth]{images/result_fairey_burma}
-			\caption{X: Nb of correct matches. Y: Accuracity}
+			\caption{X: Nb of correct matches. Y: accuracy}
 			\label{fig:result_burma}
@@
 			\includegraphics[width=\textwidth]{images/result_fairey_lady}
-			\caption{X: Nb of correct matches. Y: Accuracity}
+			\caption{X: Nb of correct matches. Y: accuracy}
 			\label{fig:result_lady}
@@
 			\includegraphics[width=\textwidth]{images/result_scharf}
-			\caption{X: Nb of correct matches. Y: Accuracity}
+			\caption{X: Nb of correct matches. Y: accuracy}
 			\label{fig:result_faces}
@@
 			\includegraphics[width=\textwidth]{images/result_houston}
-			\caption{X: Nb of correct matches. Y: Accuracity}
+			\caption{X: Nb of correct matches. Y: accuracy}
 			\label{fig:result_houston}
@@
 			\includegraphics[width=\textwidth]{images/result_blu_head}
-			\caption{X: Nb of correct matches. Y: Accuracity}
+			\caption{X: Nb of correct matches. Y: accuracy}
 			\label{fig:result_head}
@@
 			\includegraphics[width=\textwidth]{images/result_blu_pencil}
-			\caption{X: Nb of correct matches. Y: Accuracity}
+			\caption{X: Nb of correct matches. Y: accuracy}
 			\label{fig:result_pencil}
@@
 			\includegraphics[width=\textwidth]{images/result_banksy_city}
-			\caption{X: Nb of correct matches. Y: Accuracity}
+			\caption{X: Nb of correct matches. Y: accuracy}
 			\label{fig:result_city}
@@
 			\includegraphics[width=\textwidth]{images/result_banksy_stroller}
-			\caption{X: Nb of correct matches. Y: Accuracity}
+			\caption{X: Nb of correct matches. Y: accuracy}
 			\label{fig:result_stroller}
@@
 			\includegraphics[width=\textwidth]{images/result_graf}
-			\caption{X: Nb of correct matches. Y: Accuracity}
+			\caption{X: Nb of correct matches. Y: accuracy}
 			\label{fig:result_graf}
@@
 
-In figure \ref{fig:stroller} to \ref{fig:graf} the results on the images
+In figure \ref{fig:stroller} to \ref{fig:graf} the results on the 
+different image pairs are shown. Keep in mind that the accuracies 
+reflect the tests done on croppings of the source images and as such 
+don't reflect the accuracies of any of the algorithms in matching the 
+two images shown. The Nb of correct matches along the x-axis reflects 
+the total amount of correct correspondences found in the $100$ cropped 
+test pairs generated from the source pair. The accuracy plot reflects 
+the accuracy for each algorithm at a given number of correct 
+correspondences. While most of the cases show a clear advantage of 
+\emph{MM} and \emph{MMC} over \emph{BM}, there are a few exceptions, 
+notably in figure \ref{fig:city} and \ref{fig:pencil}. In the case of 
+figure \ref{fig:pencil} the high general accuracy of all the algorithms 
+makes any improvement hard to obtain, however figure \ref{fig:city} 
+remains an example where the proposed algorithms don't yield any 
+significant improvement. As for the rest of the cases a clear trend 
+emerges however, with \emph{MM} performing significantly better than 
+\emph{BM} and \emph{MMC} most often improving upon that result.
+
+In terms of performance, the three methods all have a complexity of 
+$O(n^2)$ where $n$ is the amount of feature points found in the two 
+images. This complexity assumes that the number of feature points in the 
+images is about the same. However practically speaking \emph{MMC} is 
+much slower than \emph{MM} since the clustering step while having a 
+complexity of $O(nlogn)$ is very computationally intensive. In table 
+\ref{table:running_times} the running time of the algorithm is shown.  
+These numbers should however be interpreted with the knowledge that much 
+of the code behind \emph{MMC} is implemented in python while \emph{MM} 
+and \emph{BM} makes use of opencv to execute computationally intensive 
+operations in C++ which renders it much faster.
+
+\begin{savenotes}
+\begin{table}
+	\centering
+	\small
+\begin{tabular}{l*{4}{c}}
+	Algorithm: & \emph{BM} & \emph{MM} & \emph{MMC} \\
+	\noalign{\smallskip} 
+	%
+	Running time: & 20.94s & 18.23s & 883.99s \\
+\end{tabular}
+\caption{Running times\footnote{As tested on a Intel(R) Core(TM) i5-3550 
+CPU @ 3.30GHz with 8Gb memory}}
+\label{table:running_times}
+\end{table}
+\end{savenotes}
+
+\section{Summary}
+We have addressed the problem of matching feature points without using 
+geometrical constraints and proposed two algorithms \emph{Mirror Match 
+(MM)} and \emph{Mirror Match with Clustering (MMC)}. The two algorithms 
+share the same common idea that feature points should have better 
+matches in another image than in the image they came from to be 
+considered good matches and \emph{MMC} further improves on this idea by 
+using the structure of the similarity graph of the feature points. We 
+also address how to test the algorithms by constructing a image set of 
+$8$ source image pairs and a way to generate testsets based on these 
+pairs. The proposed approach shows promising results when comparing the 
+algorithms on $9$ testsets of $100$ image pairs each where many of the 
+pairs might not have any overlapping areas. In future work it will be 
+usefull to investigate how the algorithms perform when testing on sets 
+of images instead of pairs.
 

### 2013-06-04 code/display.py

@@ -286,14 +286,17 @@ def accuDetail(correct, total, legend, ylim = 100, treshold=1000) :
 	accuHist(accu, legend, ylim=ylim)
 
 
-def accuPlot(correct, total, legends, ylim=(0.0,1.01)) :
+def accuPlot(correct, total, legends, ylim=(0.0,1.01), xlim = None) :
 	for ts,cs,l,color in zip(total, correct, legends, ["blue", "cyan", "green", "orange", "red"]) :
-		xs = [sum(c) for c in cs]
+		xs = [sum(t) for t in ts]
 		ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for (c, t) in zip(cs, ts)]
 		pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.65)
 		pylab.legend(loc="best")
 	removeDecoration()
+	pylab.xlabel("# of Matches")
+	pylab.ylabel("Accuracy")
 	pylab.ylim(ylim[0],ylim[1])
+	if xlim != None : pylab.xlim(0,xlim)
 
 
 def distHist(dist, dist_treshold = 5, dist_distinct = None, accuracity = None, accu_y_lim = 100) :

### 2013-06-04 code/isomatch.py

@@ -26,7 +26,11 @@ import pylab
 ####################################
 
 
-def match(paths, options = {}) :
+def match(paths, thresholds, options = {}) :
+
+	# Get matches in usual format
+	def matchFromIndex(i,j) :
+		return (features.getPosition(ks[indices == 0][i]), features.getPosition(ks[indices == 1][j]))
 
 	# Get options
 	k_init				= options.get("k_init", 50)
@@ -35,8 +39,8 @@ def match(paths, options = {}) :
 	max_sd				= options.get("max_sd", 40)
 	min_distance		= options.get("min_distance", 25)
 	verbose				= options.get("verbose", False)
-	keypoint_type		= options.get("keypoint_type", "ORB")
-	descriptor_type		= options.get("descriptor_type", "BRIEF")
+	keypoint_type		= options.get("keypoint_type", "SIFT")
+	descriptor_type		= options.get("descriptor_type", "SIFT")
 
 	# Get images
 	images = map(features.loadImage, paths)
@@ -69,8 +73,12 @@ def match(paths, options = {}) :
 	for i,ms in enumerate(partition_links) :
 		for (j,s) in ms :
 			matches.extend(getPartitionMatches(match_points, part_1 == i, part_2 == j))
+	
+	# Filter matches by uniqueness
+	p = lambda t : [matchFromIndex(i,j) for ((i,j),u) in matches if u < t] 
+	match_set = [p(t) for t in thresholds]
 
-	return matches
+	return match_set
 
 
 
@@ -97,23 +105,20 @@ def showPartitions(part_1, part_2, indices, images, positions) :
 	pylab.show()
 
 
-def getMatchPoints(indices, ks, ds, descriptor_type = "BRIEF") :
-	# Get matches in usual format
-	def matchFromIndex(i,j) :
-		return (features.getPosition(ks[indices == 0][i]), features.getPosition(ks[indices == 1][j]))
+def getMatchPoints(indices, ks, ds, descriptor_type = "SIFT") :
 
 	# Use cv2's matcher to get matching feature points
 	bfMatches = features.bfMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
 
 	# Keep relevant data
-	match_points = [(matchFromIndex(j,i), (j, i), s) for j,(i,s,u) in enumerate(zip(*bfMatches)) if i != None]
+	match_points = [((j, i), u) for j,(i,s,u) in enumerate(zip(*bfMatches)) if i != None]
 
[…]

### 2013-06-04 code/matching.py

@@ -17,6 +17,7 @@ Jonas Toft Arnfred, 2013-04-22
 import numpy
 import isomatch
 import clustermatch
+import isomatch
 import mirrormatch
 import features
 import weightMatrix
@@ -39,18 +40,18 @@ import random
 
 def testMatch(paths, homography, match_fun, options = {}, return_matches = False, verbose = False) :
 
-	distinct_treshold = options.get("distinct_treshold", 5)
-	tresholds = options["tresholds"]
+	distinct_threshold = options.get("distinct_threshold", 5)
+	thresholds = options["thresholds"]
 
-	# Get matches over tresholds
-	match_pos_set = match_fun(paths, tresholds, options)
+	# Get matches over thresholds
+	match_pos_set = match_fun(paths, thresholds, options)
 
 	# Get distances
 	getDist = lambda ms : [matchDistance(m1,m2,homography) for (m1,m2) in ms]
 	match_dist = [getDist(ms) for ms in match_pos_set]
 
-	if len(tresholds) == 1 and verbose :
-		display.distHist(match_dist[0], tresholds[0])
+	if len(thresholds) == 1 and verbose :
+		display.distHist(match_dist[0], thresholds[0])
 
 	if return_matches : return match_pos_set, match_dist
 	else : return match_dist
@@ -64,7 +65,7 @@ def getImagePairs(directory) :
 	return [([p + "_1.jpg", p + "_2.jpg"], h) for (p,h) in zip(pairs, homographies)]
 
 
-def folderMatch(directory, dt, match_fun, tresholds, keypoint, descriptor) : 
+def folderMatch(directory, dt, match_fun, thresholds, keypoint, descriptor) : 
 
 	def flatten(l) :
 		return list(itertools.chain.from_iterable(l))
@@ -76,15 +77,15 @@ def folderMatch(directory, dt, match_fun, tresholds, keypoint, descriptor) :
 	imagePairs = getImagePairs(directory)
 
 	# Get a set of matches varied over image pairs (matrix of size N x T where N
-	# is amount of image pairs and T is the amount of tresholds. Each element in
+	# is amount of image pairs and T is the amount of thresholds. Each element in
 	# the matrix is a zipped list of matches and distances
-	match_sets = numpy.array([numpy.array(match_fun(dt, p, h, tresholds, keypoint, descriptor)) for p, h in imagePairs]).T
[…]

### 2013-06-05 code/clustermatch.py
Added new tests

@@ -35,10 +35,10 @@ dist_fun_map = {
 ####################################
 
 
-def match(paths, tresholds, options = {}) : 
+def match(paths, thresholds, options = {}) : 
 	
 	# Get parameters
-	prune_fun = options.get("prune_fun", weightMatrix.pruneTreshold)
+	prune_fun = options.get("prune_fun", weightMatrix.pruneThreshold)
 	prune_limit = options.get("prune_limit", 2.5)
 	keypoint_type = options.get("keypoint_type", "SIFT")
 	descriptor_type = options.get("descriptor_type", "SIFT")
@@ -59,9 +59,9 @@ def match(paths, tresholds, options = {}) :
 	partitions = cluster(cluster_weights, indices, split_limit = split_limit, prune_limit = cluster_prune_limit, verbose=verbose)
 	if verbose : print("%i partitions" % len(set(partitions)))
 
-	# For each treshold, get partition matches
+	# For each threshold, get partition matches
 	p = lambda t : getPartitionMatches(partitions, cluster_weights, weights, indices, t)
-	match_set = [p(t) for t in tresholds]
+	match_set = [p(t) for t in thresholds]
 
 	# Get positions
 	get_pos = lambda (m_i, m_j) : getMatchPosition(m_i, m_j, ks)
@@ -71,13 +71,13 @@ def match(paths, tresholds, options = {}) :
 
 
 
-def getMatches(m, ind, treshold) :
+def getMatches(m, ind, threshold) :
 
 	def getMaxMatch(m) :
 		for i,row in enumerate(m) :
 			s = numpy.argsort(row)
 			u = row[s[-2]] / row[s[-1]]
-			if u < treshold : yield (i,s[-1])
+			if u < threshold : yield (i,s[-1])
 	
 	# Get best matches for rows and columns
 	matches = list(getMaxMatch(m))
@@ -109,7 +109,7 @@ def cluster(weights, indices, split_limit = 10, prune_limit = 3, verbose = False
 			nb_inter_edges = numpy.sum(pij_edges > 0)
 			if (numpy.sum(partition_mask) > split_limit) :
 				# Prune weights
-				p_edges_pruned = weightMatrix.pruneTreshold(p_edges, prune_limit)
+				p_edges_pruned = weightMatrix.prunethreshold(p_edges, prune_limit)
 
 				# If there are no edges left, then skip
 				if numpy.sum(p_edges_pruned) == 0 : continue
[…]

### 2013-06-05 code/display.py

@@ -34,25 +34,27 @@ from sklearn import metrics
 #                                  #
 ####################################
 
-def appendimages(im1, im2) :
+def appendimages(im1, im2, seperator = 0) :
 	""" return a new image that appends the two images side-by-side.
 	"""
+
+	barrier = numpy.ones((im1.shape[0],seperator)) * 255
 
 	if (im1.shape[0] == im2.shape[0]) :
 		tmp = im2
 
 	elif (im1.shape[0] > im2.shape[0]) :
-		tmp = numpy.ones((im1.shape[0], im2.shape[1]))
+		tmp = numpy.ones((im1.shape[0], im2.shape[1])) * 255
 		tmp[0:im2.shape[0], :] = im2
 
 	elif (im1.shape[0] < im2.shape[0]) :
-		tmp = numpy.ones((im1.shape[0], im2.shape[1]))
+		tmp = numpy.ones((im1.shape[0], im2.shape[1])) * 255
 		tmp[0:im1.shape[0], :] = im2[0:im1.shape[0],:]
 
 	else :
 		print("Detonating thermo-nuclear devices")
 
-	return numpy.concatenate((im1,tmp), axis=1)
+	return numpy.concatenate((im1,barrier, tmp), axis=1)
 
 
 
@@ -70,16 +72,16 @@ def keypoints(im, pos) :
 	pylab.show()
 
 
-def compareKeypoints(im1, im2, pos1, pos2, filename = None) :
+def compareKeypoints(im1, im2, pos1, pos2, filename = None, separation = 0) :
 	""" Show two images next to each other with the keypoints marked
 	"""
 
 	# Construct unified image
-	im3 = appendimages(im1,im2)
+	im3 = appendimages(im1,im2, separation)
 
 	# Find the offset and add it
 	offset = im1.shape[1]
-	pos2_o = [(x+offset,y) for (x,y) in pos2]
+	pos2_o = [(x+offset + separation,y) for (x,y) in pos2]
 
 	# Create figure
 	fig = pylab.figure(frameon=False, figsize=(10.0, 7.0))
@@ -105,8 +107,10 @@ def matchPoints(im1, im2, matches, dist = None, filename = None, max_dist = 100,
 		matchscores (as output from 'match'). 
 	"""
 
+	separation = 20
+
 	# Construct unified image
[…]

### 2013-06-05 code/isodata.py

@@ -77,7 +77,7 @@ def cluster(points, k_init=None, max_iterations=100, min_partition_size=5, max_s
 	"""
 	
 	# Set a sensible k_init if it wasn't specified
-	if k_init == None:
+	if k_init == None or len(points) < k_init:
 		k_init = points.shape[0] / (min_partition_size * 2)
 	
 	# Sample nb_partitions points as initial guess

### 2013-06-05 code/isomatch.py

@@ -75,11 +75,41 @@ def match(paths, thresholds, options = {}) :
 			matches.extend(getPartitionMatches(match_points, part_1 == i, part_2 == j))
 	
 	# Filter matches by uniqueness
-	p = lambda t : [matchFromIndex(i,j) for ((i,j),u) in matches if u < t] 
+	p = lambda t : pruneMatches([matchFromIndex(i,j) for ((i,j),u) in matches if u < t])
 	match_set = [p(t) for t in thresholds]
 
 	return match_set
 
+
+
+def pruneMatches(matches) :
+	# filter matches that are deviant from average angle
+	def getLength(p1, p2) :
+		v = numpy.array([p2[0] - p1[0], p2[1] - p1[1]])
+		return numpy.linalg.norm(v)
+
+	def getAngle(p1, p2) :
+		# The + 1 is to avoid division with zero when positions overlap
+		x_dist = 500
+		return numpy.arccos((p2[0] - (p1[0] + x_dist)) / (getLength([p1[0] + x_dist, p1[1]],p2) + 0.001))
+
+	def isAcceptable(l, a) :
+		sdv = 1
+		within_length = l < (mdn_length + sdv*sdv_length) and l > (mdn_length - sdv*sdv_length)
+		within_angle = a < (mdn_angle + sdv*sdv_angle) and a > (mdn_angle - sdv*sdv_angle)
+		return within_length and within_angle
+
+	# Get the length and angle of each match
+	lengths = [ getLength(p1,p2) for p1,p2 in matches]
+	angles = [ getAngle(p1,p2) for p1,p2 in matches]
+
+	# Calculate a bit of statistics
+	mdn_length = numpy.median(lengths)
+	sdv_length = numpy.sqrt(numpy.var(lengths))
+	mdn_angle = numpy.median(angles)
+	sdv_angle = numpy.sqrt(numpy.var(angles))
+
+	return [m for m,l,a in zip(matches, lengths, angles) if isAcceptable(l, a)]
 
 
 def getLinkMat(part_1, part_2, match_points) :

### 2013-06-05 code/matching.py

@@ -233,34 +233,6 @@ def matchDistance(p1, p2, hom) :
 
 
 
-def pruneMatches(matches) :
-	# filter matches that are deviant from average angle
-	def getLength(p1, p2) :
-		v = numpy.array([p2[0] - p1[0], p2[1] - p1[1]])
-		return numpy.linalg.norm(v)
-
-	def getAngle(p1, p2) :
-		# The + 1 is to avoid division with zero when positions overlap
-		x_dist = 500
-		return numpy.arccos((p2[0] - (p1[0] + x_dist)) / (getLength([p1[0] + x_dist, p1[1]],p2) + 0.001))
-
-	def isAcceptable(l, a) :
-		sdv = 1
-		within_length = l < (mdn_length + sdv*sdv_length) and l > (mdn_length - sdv*sdv_length)
-		within_angle = a < (mdn_angle + sdv*sdv_angle) and a > (mdn_angle - sdv*sdv_angle)
-		return within_length and within_angle
-
-	# Get the length and angle of each match
-	lengths = [ getLength(p1,p2) for p1,p2 in matches]
-	angles = [ getAngle(p1,p2) for p1,p2 in matches]
-
-	# Calculate a bit of statistics
-	mdn_length = numpy.median(lengths)
-	sdv_length = numpy.sqrt(numpy.var(lengths))
-	mdn_angle = numpy.median(angles)
-	sdv_angle = numpy.sqrt(numpy.var(angles))
-
-	return [m for m,l,a in zip(matches, lengths, angles) if isAcceptable(l, a)]
 
 
 
@@ -285,26 +257,12 @@ def clusterMatch(distance_threshold, paths, homography, thresholds, keypoint, de
 		clustermatch.match,
 		verbose = False,
 		options = {
-			"prune_fun" : weightMatrix.prunethreshold, 
+			"prune_fun" : weightMatrix.pruneThreshold, 
 			"prune_limit" : 2.5,
 			"min_coherence" : 0.0,
 			"thresholds" : thresholds,
 			"split_limit" : 500,
 			"cluster_prune_limit" : 1.5,
-			"distance_threshold" : distance_threshold,
-			"keypoint_type" : keypoint,
-			"descriptor_type" : descriptor,
-		})
-
-
-def uniqueMatch(distance_threshold, paths, homography, thresholds, keypoint, descriptor) :
-	return testMatch(
-		paths,
-		homography, 
-		standardMatch,
-		verbose = False,
-		options = {
[…]

### 2013-06-05 code/mirrormatch.py

@@ -20,7 +20,7 @@ import features
 #                                  #
 ####################################
 
-def match(paths, tresholds, options = {}) :
+def match(paths, thresholds, options = {}) :
 
 	# Returns the position of a match
 	def matchPos(i,j) :
@@ -39,8 +39,8 @@ def match(paths, tresholds, options = {}) :
 	# See if matches go both ways
 	bothways = [(i,j) for i,j in enumerate(jj) if indices[i] == 0 and indices[j] == 1 and jj[j] == i]
 
-	# Now for each treshold test the uniqueness of the matches
+	# Now for each threshold test the uniqueness of the matches
 	p = lambda t : [matchPos(i,j) for i,j in bothways if uu[i] < t] 
-	match_set = [p(t) for t in tresholds]
+	match_set = [p(t) for t in thresholds]
 
 	return match_set

### 2013-06-05 code/scoring.py

@@ -122,7 +122,7 @@ def scoreImages(paths,
 		withGeometry 	= True, 
 		withCertainty 	= True, 
 		cluster_prune 	= weightMatrix.pruneHighest,
-		score_prune 	= weightMatrix.pruneTreshold,
+		score_prune 	= weightMatrix.pruneThreshold,
 		normalize		= True,
 		score_type		= scoreWeights) :
 	""" Given paths to two images, the images are scored based on how 

### 2013-06-05 code/weightMatrix.py

@@ -162,7 +162,7 @@ def pruneHighest(weights, edges_per_vertex,n=0,start=0) :
 
 
 
-def pruneTreshold(weights, edges_per_vertex, n=600, start=0.0) :
+def pruneThreshold(weights, edges_per_vertex, n=600, start=0.0) :
 	""" Removes all edges under a certain treshold
 	"""
 	# Get treshold

### 2013-06-05 code/create_testset.py
Added create_testset file

@@ -1,0 +1,221 @@
+"""
+Python module for creating a test set from source image pairs
+
+Jonas Toft Arnfred, 2013-06-05
+
+The code is released under the following license:
+
+	Copyright (C) 2013 Jonas Toft Arnfred
+
+	Permission is hereby granted, free of charge, to any person obtaining a copy of
+	this software and associated documentation files (the "Software"), to deal in
+	the Software without restriction, including without limitation the rights to
+	use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies
+	of the Software, and to permit persons to whom the Software is furnished to do
+	so, subject to the following conditions:
+
+	The above copyright notice and this permission notice shall be included in all
+	copies or substantial portions of the Software.
+
+	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
+	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
+	SOFTWARE.
+"""
+
+
+####################################
+#                                  #
+#            Imports               #
+#                                  #
+####################################
+
+import random
+from string import ascii_uppercase, digits
+from os.path import isdir, dirname, exists
+from os import makedirs
+from scipy.misc import imresize
+import pylab
+import numpy
+import sys
+import getopt
+import cv2
+
+
+####################################
+#                                  #
+#           Functions              #
+#                                  #
+####################################
+
+def loadImage(path) : 
+	""" Given a path, an image will be loaded and converted to grayscale
+		input: path [string] (path to the image)
[…]

### 2013-06-05 text/clustering.tex
Added new tests
New images and more text

--- 2013-05-31 text/clustering.tex
@@
-\documentclass{article}
+\documentclass[12pt,journal,compsoc]{IEEEtran}
+%\documentclass{article}
+\usepackage{footnote}
+\usepackage{sidecap}
 \usepackage{graphicx}
+\usepackage{cite}
 \usepackage{hyperref}
@@
 
-\title{Clustering feature points}
-\author{Jonas Arnfred}
+\title{Reliable feature point matching without the use of geometric 
+constraints}
+\author{Jonas Arnfred and what to put here exactly?}
 
 \maketitle
-
+%
 \begin{abstract}
-% TODO!
+Many algorithms have been proposed to solve the problem of matching 
+feature points in two or more images using geometric assumptions to 
+increase the robustness of the matching. However very little work 
+addresses the case where these assumptions might not hold true. In 
+particular few methods address the problem of reliable matching in cases 
+where we don't know if two images have any corresponding areas or 
+objects. In this paper we propose two algorithms for matching feature 
+points without the use of geometric constraints. The first makes use of 
+the fact that any match between two images should be better than all 
+possible matches within the image itself. The second algorithm extends 
+this idea by using the community structure in the similarity graph of 
+feature points to reliably find correspondences. To evaluate the 
+algorithms experimentally we introduce a set of 8 image pairs all 
+containing view port changes and a simple method to generate a large 
+amount of test cases based on these 8 pairs. The experimental results 
+show that the proposed algorithm, overall, is superior to traditional 
+approaches in finding correct correspondences.
 \end{abstract}
-
+%
 \section{Introduction}
-
-Since the introduction of feature points, several methods for matching 
-them across images have been proposed in order to maximize the amount of 
-correct matches. In this part of the project I introduce two methods to 
-reliably match feature points. The word 'reliable' covers that matches 
-only are returned if they are judged as sound. That is, matches should 
-only be returned if there are objects or scenes that appear in both 
-images.
-
-When matching feature points between two images we are often faced with 
-a dilemma between making the feature descriptor more discriminative to 
-make sure only correct matches are made, and making it less 
-discriminative to increase the robustness of the descriptor over 
-different changes such as illumination, perspective and image quality.  
-Any feature type aiming for robustness will have cases where it isn't 
-possible to generate reliable matches if we only look at the pairwise 
-correspondence of the descriptors.
-
-To get around this limitation several methods have been proposed in the 
-literature. One of the most fruitful approaches have been to look at the 
-geometric configuration of the feature points and match them with 
-respect to assumptions concerning the variance between images. For 
-example an angular and distance constraint between matches as considered 
-by \cite{kim2008efficient} performs well in situations where no camera 
-rotation occurs between the two images but will likely fail in other 
-cases. Various scenarios have been proposed to improve on this simple 
-assumption such as epipolar constraints (\cite{torr2000mlesac}, 
-\cite{chum2005matching}) and pairwise constraints 
-(\cite{choi2009robust}, \cite{leordeanu2005spectral}). The Epipolar 
-constraint carries the assumption that the two images matched are 
-related by an affine transformation. That is, there is no relative 
-movement of objects in between images and either the viewpoint is fixed 
-or the image resides entirely on a plane. In practice this assumption 
-largely holds true when all objects we are interested in matching are 
-roughly the same distance from the camera and when we don't expect to 
-match objects that aren't consistently positioned across images.  
-Pairwise constraints provide a more robust approach to this problem by 
-looking at a set of proposed correspondences and defining a pairwise 
-error between any two matches usually based on the assumption that two 
-neighboring correspondences will usually have similar angles and 
-distances. We can then convert the problem to an optimization problem 
-and return a set of correspondences that minimizes this error such as 
-proposed in \cite{choi2009robust} and \cite{leordeanu2005spectral}.  
-This approach provides more robustness because assumptions that might 
-not be true globally often still holds on a local level.
-
+%
+When matching feature points between two or more images we are often 
+faced with the problem of correctly identifying the actual 
+correspondences among many possible pairings. Several methods have been 
+proposed in the literature to solve this problem. In particular many 
+approaches look at the geometric configuration of the feature points and 
+match them according to assumptions made about the geometric 
+relationship between the images matched. These assumptions are then used 
+to create constraints used to evaluate the matches such as angular 
+constraints (\cite{kim2008efficient}), epipolar constraints 
+(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
+constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}).
+%
+%When matching feature points between two or more images we are often 
+%faced with the problem of correctly identifying the actual 
+%correspondences among many possible pairings. Several methods have been 
+%proposed in the literature to solve this problem. In particular many 
+%approaches look at the geometric configuration of the feature points 
+%and match them according to assumptions made about the geometric 
+%relationship between the images matched. A simple example would be to 
+%only consider matches that aren't deviating too much with respect to 
+%the average angle and distancen as considered by 
+%\cite{kim2008efficient}.  This performs well in situations where no 
+%camera rotation occurs between the two images, but fails when this 
+%assumption isn't met. Various scenarios have been proposed to improve 
+%on this simple assumption such as epipolar constraints 
+%(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
+%constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}). The 
+%Epipolar constraint carries the assumption that the two images matched 
+%are related by an affine transformation. That is, there is no relative 
+%movement of objects in between images and either the viewpoint is fixed 
+%or the image resides entirely on a plane. In practice this assumption 
+%largely holds true when all objects we are interested in matching are 
+%roughly the same distance from the camera and when we expect to match 
+%objects that are consistently positioned across images.  Pairwise 
+%constraints provide a more robust approach to the same problem by 
+%looking at a set of proposed correspondences and defining a pairwise 
+%error between any two matches for example based on the assumption that 
+%two neighboring correspondences will usually have similar angles and 
+%distances. We can then convert the problem to an optimization problem 
+%and return a set of correspondences that minimizes this error such as 
+%proposed in \cite{choi2009robust} and \cite{leordeanu2005spectral}.  
+%This approach provides more robustness in cases where assumptions that 
+%are violated globally still hold on a local scale.
+%
 Another approach proposed in the literature is to pick out different 
-zones in each image and find a pairing of zones where feature points are 
-only matched within the same zone. \cite{das2008event} proposes 
-clustering the feature points using their geometric position and 
-matching only feature points between groups that have a certain amount 
-of matchings between them. A more sophisticated approach is introduced 
-in \cite{wu2011robust} where the zones are created by surrounding MSER 
-feature points by an ellipse and grouping the SIFT or SURF feature 
-points that fall within the ellipse together. These points can then be 
+zones in each image and pair zones when correspondence pairs are mainly 
+found going from one zone to another. This allows for the filtering of 
+all correspondences that do not fall within paired zones.  
+\cite{das2008event} proposes clustering feature points by using their 
+geometric position and exclude correspondences that are geometrically 
+deviant. A more sophisticated approach is introduced in 
+\cite{wu2011robust} where the zones are created by using the MSER 
+feature detector to find areas of interest in the images. These areas 
+can be defined as an ellipse with a certain radius around the interest 
+points. The feature points that fall within this ellipse are then 
 matched according to epipolar constraints.  
-
-In practice there are many situations where using the geometry of the 
-image to filter correspondences is not possible. This situation most 
-often arise when the assumptions made by a geometric method turns out 
-not to hold in a particular use case. This could matchings between 
-images where the content has been scrambled or with so little 
-consistency that even the geometric assumptions break down even on a 
-local level. In addition the geometric methods all require a set of 
-correspondences to begin with. If this set of correspondences is 
-narrowed down to a smaller set with a higher ratio of inliers the result 
-of the geometric matching will be both faster and more accurate. Finally 
-some use cases might require a performance that can't be achieved by a 
-more complex geometric method where simple non geometric methods might 
-be able to provide additional matching accuracy with a smaller 
-performance penalty. This approach is inspired by \cite{wu2009bundling} 
-where bundling of feature points was used to enhance the search results 
-in large scale partial-duplicate web image search.
-
+%
+In practice however, there are many situations where using the geometry 
+of the image to filter correspondences is not possible. This situation 
+most often arise when the assumptions made by a geometric method aren't 
+valid. In object recognition for example, adjecent objects in one photo 
+might be separated in another. In addition methods using geometric 
+constraints all require a set of correspondences to begin with. If this 
+set of correspondences is narrowed down to a smaller set with a higher 
+ratio of correct matches the result of the geometric matching will be 
+both faster and more accurate.  Finally some use cases might require a 
+performance that can't be achieved by a more complex geometric method 
+where simple non geometric methods might be able to provide additional 
+matching accuracy with a smaller performance penalty.
+%
 There are a relatively small number of algorithms proposed to solve the 
 matching problem without involving geometric constraints. Traditionally 
-the feature points of two images have been matched by comparing the 
-every feature point of one image with all feature points of the other 
-and finding the best matches based on the similarity of the descriptors.  
+the feature points of two images have been matched by comparing every 
+feature point of one image with all feature points of the other and 
+finding the best matches based on the similarity of the descriptors.  
 With the introduction of the SIFT features \cite{lowe2004sift}, Lowe 
@@
 scores by their uniqueness and picking the $n$ best we get a set of 
-correspondences that are distinctly matched across the two images. In 
-the book Multiple View Geometry \cite[p.  114]{multipleView}, the gold 
-standard algorithm is introduced which ranks correspondences by 
-similarity and further filters them by discarding matches that aren't 
-symmetric, i.e. that for every feature point $f_i$ matching $f_j$ we 
-also have that $f_j$ matches $f_i$.
-
-In turn the two methods proposed in this report are inspired by a simple 
+correspondences that are distinctly matched across the two images.
+%
+In turn the two methods proposed in this paper are inspired by a simple 
 but novel idea. If we have two images and a given feature point in the 
@@
 other geometric solutions when appropriate.
-
-Based on this idea the two proposed methods find reliable matches as 
-follows:
-\begin{itemize}
-\item{\emph{Mirror Match (MM)}: Match features using the gold standard 
-algorithm\cite[p. 114]{multipleView} ranked by similarity and thresheld 
-by uniqueness\cite{lowe2004sift}. However instead of matching features 
-from one image with features in another, we match every feature with all 
-other features of the two images combined. Only matches from one image 
-to the other are returned.}
-\item{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
-of feature points from both images and cluster these points according to 
-their descriptors. Given a resulting partition of points, no matches are 
-returned if it contains only feature points from one image. If the 
-partition contains points from both images, \emph{Mirror Match} is used 
-to find the best matches within the partition.}
-\end{itemize}
-
-Matching feature points against the entire set of points from both 
-images ensures that the distinctiveness of a returned correspondence is 
-higher. In almost all cases\footnote{Exceptions would include cases 
-where we want to find all particular points in a pattern and other use 
-cases where the correspondence isn't assumed to be unique}, a good match 
-between two images is unambiguous in the sense that there are no other 
-equally (or almost equally) good potential matches to the same point.  
-This is the key insight behind the algorithm presented by Lowe in 
-\cite{lowe2004sift}. However the implication doesn't follow the other 
-way around. In the case that a feature point don't have any actual 
-correspondence in the other image, there is no guarantee that this 
-feature point might not still be uniquely matched to a feature point in 
-the other image. The issue is particularly pronounced if we compare two 
-images that don't correspond. For any proposed correspondence it is 
-entirely probable that this correspondence is unique even if it isn't 
-correct. With Mirror Match this ambiguity is avoided by incorporating 
-the feature points of both images when a match is made. When the two 
-images have nothing to do with each other, chances are that a feature 
-point will match better with another feature point from the same image 
-in which case it is easily discarded.
-
-Often images will contain repetitive patterns that are difficult to 
-match\footnote{In fact this particular problem has been given attention 
-before by for example \cite{fan2011towards}} because the feature points 
-covering these patterns will look very similar. If we threshold by 
-uniqueness like in Mirror Match this means that these points will often 
-be discarded even if they might have good correspondences. To solve this 
-problem the enhanced Mirror Match with Clustering makes it possible to 
-look at groups of similar feature points one at a time and within each 
-group finding the best matches. This is done by taking the set of 
-feature points from both images and clustering. The resulting partitions 
-will each contain feature points that are similar to each other. In some 
-cases the clustering will end up grouping feature points of only one 
-image together which can then easily be discarded in the matching 
-process. In other cases partitions will contain feature points from both 
-images that can then be matched using \emph{MM} but with lower 
-thresholds.
-
-The report is organized as follows. In section \ref{algorithms} I will 
-describe the two algorithms. Section \ref{experiment} will cover the 
-experimental set up and introduce the image set that is used in testing.  
-In section \ref{results} I will go through the results and conclude.
-
-\section{Algorithms}
-\label{algorithms}
-
-To discuss the implementation of \emph{MM} and \emph{MMC} a few notes on 
-notation will be helpful. BLAH BLAH!
-
+%
+%Based on this idea the two proposed methods find reliable matches as 
+%follows:
+%\begin{itemize}
+%\item[]{\emph{Mirror Match (MM)}: Match features using the gold standard 
+%		algorithm\cite[p. 114]{multipleView} ranked by similarity and 
+%		thresheld by uniqueness\cite{lowe2004sift}.  However instead of 
+%		matching features from one image with features in another, we 
+%	match every feature with all other features of the two images 
+%combined. Only matches from one image to the other are returned.}
+%\item[]{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
+%		of feature points from both images and cluster these points 
+%		according to their descriptors. Given a resulting partition of 
+%		points, no matches are returned if it contains only feature 
+%	points from one image. If the partition contains points from both 
+%images, \emph{Mirror Match} is used to find the best matches within the 
+%partition.}
+%\end{itemize}
+%%
+%Matching feature points against the entire set of points from both 
+%images ensures that the distinctiveness of a returned correspondence is 
+%higher. In almost all cases\footnote{Exceptions would include cases 
+%where we want to find all particular points in a pattern and other use 
+%cases where the correspondence isn't assumed to be unique}, a good 
+%match between two images is unambiguous in the sense that there are no 
+%other equally good potential matches to the same point.  This is the 
+%key insight behind the algorithm presented by Lowe in 
+%\cite{lowe2004sift}.  However the implication doesn't follow the other 
+%way around. In the case that a feature point doesn't have a true 
+%correspondence there might still exist point with which the feature 
+%point is uniquely matched. The issue is particularly pronounced if we 
+%compare two images that don't correspond. For any proposed 
+%correspondence it is entirely probable that this correspondence is 
+%unique even if it isn't correct. When we match against the feature 
+%points of both images this ambiguity is avoided.  When the two images 
+%have no overlap or objects in common, chances are that a feature point 
+%will match better with another feature point from the same image in 
+%which case it is easily discarded.
+%
+%Often images will contain repetitive patterns that are difficult to 
+%match\footnote{In fact this particular problem has been given attention 
+%before by for example \cite{fan2011towards}} because the feature 
+%descriptors covering these patterns will be similar. If we remove points 
+%that aren't deemed sufficiently unique like in \emph{MM} this means that 
+%these points will often be discarded even if they are correctly matched.
+%\emph{MMC} makes it possible to look at groups of similar feature points 
+%one at a time and within each group find the best matches. This is done 
+%by taking the set of feature points from both images and cluster them by 
+%their similarity. In some cases the clustering will end up grouping 
+%feature points of only one image together which can then easily be 
+%discarded in the matching process.  In other cases partitions will 
+%contain similar feature points from both images that can then be matched 
+%using \emph{MM} but with much lower thresholds.
+%
 \subsection{Mirror Match (\emph{MM})}
-
+%
 The central idea behind \emph{MM} is to match features of $n$ images by 
@@
 that match two points within the same image. In algorithm \ref{alg-mm} 
-the actual implementation of \emph{MM} is shown.
-
+the implementation of \emph{MM} is shown.
+%
 \begin{algorithm}
@@
 \begin{algorithmic}
-\Require $images$ : set of images, $threshold$ : float $\in \mathbb{R}$
+\Require $images$ : set of images, $t$ : float $\in \mathbb{R}$
 \State $matches_{init}\gets \varnothing$
@@
 \State $features\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather features of all images
+\ForAll{$I_i \in images$} \Comment Gather Stage
 	\State $features\gets features \cup getFeatures(I_i)$
 \EndFor
-\ForAll{$f_i \in features$} \Comment Get best match for all features
-	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features ~ 
-\backslash ~ \left\{f_i\right\})$
-	\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
-f_m)$
-	\If{$ratio < threshold$}
+\ForAll{$f_i \in features$} \Comment Match Stage
+	\State $f_m,f_n \gets get2NNs(f_i, features ~ \backslash ~ 
+	\left\{f_i\right\})$
+	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
+	\If{$ratio < t$}
 		\State $matches_{init} \gets \left(f_i, f_m\right)$
@@
 \ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
-matches
+Stage
 \If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
@@
 \end{algorithm}
-
-This algorithm passes over three states: An acquisition state where 
-feature points are gathered, a matching state where the initial set of 
-correspondences are found and a filtering state where correspondences 
-within the same image are removed. In the acquisition state the function 
-\emph{getFeatures($I_i$)} returns a set of feature points given an 
-image.  In practice the feature used for the experiments have been 
-SIFT\cite{lowe2004sift}, but there aren't any reason why other features 
-such as SURF\cite{bay2006surf} or BRIEF\cite{calonder2010brief} couldn't 
-be used just as well. The matching state uses K-Nearest Neighbors to 
-return the two closest neighbors in the set of features for any given 
-feature $f_i$ and calculates the ratio between the correspondences as 
-proposed in \cite{lowe2004sift}.  Any correspondence with a ratio below 
-the threshold supplied will be discarded. Finally in the filter the 
-function \emph{getImg($f_i$)} returns the parent image of the feature 
-$f_i$ and discards both correspondences that aren't symmetric as well as 
-those that match two points in the same image.
-
-\begin{figure}
+%
+In the acquisition state we gather all features in the set of images.  
+These features are then matched in the match stage using K-Nearest 
+Neighbors.  For any given feature $f_i$ the two most similar neighbors 
+are returned and we calculate the ratio between them as as proposed in 
+\cite{lowe2004sift}.  Any correspondence with a ratio above the 
+threshold supplied will be discarded. Finally in the filter stage we 
+check that matches are from different images and discard all matches 
+that are not symmetric.
+%
+\begin{figure*}
 	\makebox[\textwidth][c]{%
-		\begin{subfigure}[t]{0.45\textwidth}
+		\begin{subfigure}[t]{0.30\textwidth}
 			\centering
@@
 		\end{subfigure}%
-		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
 		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.45\textwidth}
+		\begin{subfigure}[t]{0.30\textwidth}
 			\centering
@@
 		\end{subfigure}%
-		%~ %add desired spacing between images, e. g. ~, \quad, \qquad
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad
 		  %(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.45\textwidth}
+		\begin{subfigure}[t]{0.30\textwidth}
 			\centering
@@
 			\label{fig:without}
-		\end{subfigure}%
-	}%
-	\label{fig:compare_mirror}
+		\end{subfigure}
+	}
 	\caption{Illustration of matches filtered by \emph{MM}}
-\end{figure}
-
-Figure \ref{fig:compare_mirror} shows an example of the performance of 
-\emph{MM}. In sub figure \ref{fig:unique} the result of a normal 
-matching of two images is shown. The two images appear side by side and 
-for each correspondence between them, a line has been drawn from one 
-image to the other. The color of the line indicates if the 
-correspondence is accurate. Sub figure \ref{fig:within} shows the 
-correspondences found by mirror match using the same threshold before 
-the matches within the same image has been filtered out. In particular 
-the fence by the bottom of the image admits correspondences that can 
-conveniently be removed as done in sub figure \ref{fig:without} where 
-only the actual correspondences returned by the algorithm are shown.
-
+	\label{fig:comparemirror}
+\end{figure*}
+%
+Figure \ref{fig:comparemirror} shows an example of the result of 
+\emph{MM}. In figure \ref{fig:unique} the matches between two images are 
+shown when using the \emph{SIFT} algorithm from \cite{lowe2004sift}. For 
+each match found between the two images, a line has been drawn. The 
+color of the line is green in case the match is correct and red for 
+incorrect matches. Figure \ref{fig:within} shows the correspondences 
+found by mirror match, but including all matches that are found within 
+the same image. Notice how the by the bottom of the image admits 
+correspondences that can conveniently be removed as done in sub figure 
+\ref{fig:without} where only the actual correspondences returned by the 
+algorithm are shown.
+%
 \subsection{Mirror Match with Clustering (\emph{MMC})}
-
+%
 As opposed to \emph{MM}, \emph{MMC} diverges from traditional 
@@
 similarity. This process yields partitions of fairly similar feature 
-points that we can match using the same approach as \emph{MM}. Before I 
-introduce the implementation details I will go over the problem of graph 
-clustering and how it relates to feature matching.
-
-\subsubsection{Graph Clustering}
-
-Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-points in an image and return their matching score, we can define a 
-matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-as the \emph{adjecency matrix} of the fully connected graph where each 
-vertex corresponds to a keypoint and the edge between two vertices has a 
-weight equal to the distance between the two corresponding keypoints.
-
-This representation reduces the problem of partitioning the keypoints 
-into groups to that of graph clustering or community structure depending 
-on the context. In the literature there are various ways of clustering a 
-graph according to different measures of what constitutes an optimal 
-partitioning. Traditionally the most used clustering algorithms have 
-been K-means and spectral clustering, but in recent years a host of new 
-algorithms have been proposed based on both Newman's concept of graph 
-modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-well as information theoretical measures\footnote{See for example 
-\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-new algorithms differ from K-means clustering and Spectral clustering in 
-that they don't require the number of expected to clusters to be 
-specified beforehand\footnote{Among the aforementioned methods, this is 
-true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-tests done using randomly generated graphs with a known partitioning 
-\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-markedly better than spectral clustering and 
-K-means\cite{lancichinetti2009}.
-
-The performance of clustering algorithms is a complicated issue, since 
-an optimal clustering given the same graph can vary depending on the 
-application. Spectral clustering for example will usually return a 
-partitioning where each partition is roughly equal in size\footnote{As 
-mentioned in \cite{von2007}} while the Louvain 
-clustering\cite{blondel2008} might return partitions of very uneven 
-size, even if the modularity measurement has been shown to penalize very 
-small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-depending on the application, but when clustering feature points, 
-maintaining clusters of an even size usually means that some clusters 
-will be '\emph{catch-all}' clusters where the feature points that don't 
-fit anywhere else are grouped together. The necessity of specifying the 
-amount of partitions in for example Spectral clustering or Pott's model 
-clustering further exacerbates the issue since smaller partitions are 
-then combined into one to achieve the right amount of partitions.
-
-Based on these observations I've decided to use Louvain clustering for 
-grouping feature points since it's fast, performs well, doesn't require 
-parameters and doesn't emphasize partitions of equal sizes.
-
-\subsubsection{Clustering feature points using Louvain clustering}
-
+points that we can match using the same approach as \emph{MM}. 
+%
+%Before we introduce the implementation details we will go over the 
+%problem of graph clustering and how it relates to feature matching.
+%
+%\subsubsection{Graph Clustering}
+%
+%Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
+%\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
+%function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
+%points in an image and returns their matching score, we can define a 
+%matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
+%as the \emph{adjecency matrix} of the fully connected graph where each 
+%vertex corresponds to a keypoint and the edge between two vertices has a 
+%weight equal to the distance between the two corresponding keypoints.
+%
+%This representation reduces the problem of partitioning the keypoints 
+%into groups to that of graph clustering or community structure depending 
+%on the context. In the literature there are various ways of clustering a 
+%graph according to different measures of what constitutes an optimal 
+%partitioning. Traditionally the most used clustering algorithms have 
+%been K-means and spectral clustering, but in recent years a host of new 
+%algorithms have been proposed based on both Newman's concept of graph 
+%modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
+%\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
+%well as information theoretical measures\footnote{See for example 
+%\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
+%in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
+%new algorithms differ from K-means clustering and Spectral clustering in 
+%that they don't require the number of expected to clusters to be 
+%specified beforehand\footnote{Among the aforementioned methods, this is 
+%true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
+%tests done using randomly generated graphs with a known partitioning 
+%\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
+%markedly better than spectral clustering and 
+%K-means\cite{lancichinetti2009}.
+%
+%The performance of clustering algorithms is a complicated issue, since 
+%an optimal clustering given the same graph can vary depending on the 
+%application. Spectral clustering for example will usually return a 
+%partitioning where each partition is roughly equal in size\footnote{As 
+%mentioned in \cite{von2007}} while the Louvain 
+%clustering\cite{blondel2008} might return partitions of very uneven 
+%size, even if the modularity measurement has been shown to penalize very 
+%small clusters\cite{brandes2007}. Both behaviours can be beneficial 
+%depending on the application, but when clustering feature points, 
+%maintaining clusters of an even size usually means that some clusters 
+%will be '\emph{catch-all}' clusters where the feature points that don't 
+%fit anywhere else are grouped together. The necessity of specifying the 
+%amount of partitions in for example Spectral clustering or Pott's model 
+%clustering further exacerbates the issue since smaller partitions are 
+%then combined into one to achieve the right amount of partitions.
+%
+We use the Louvain Method\cite{blondel2008} for clustering feature 
+points since it's relatively fast and performs 
+well\cite{lancichinetti2009}, doesn't require 
+parameters\cite{blondel2008} and doesn't emphasize partitions of equal 
+sizes as opposed to for example spectral clustering and 
+k-means\cite{von2007}.
+%
 \begin{algorithm}
@@
 \begin{algorithmic}
-\Require $images$ : set of images, $threshold \in \mathbb{R}$
-\State $matches\gets \varnothing$
-\State $features\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather features of all images
+\Require $images$ : set of images, $t \in \mathbb{R}$
+\State $M\gets \varnothing$
+\State $F\gets \varnothing$
+\ForAll{$I_i \in images$} \Comment Gather features
 	\State $f_i\gets getFeatures(I_i)$
-	\State $features\gets features \cup f_i$
+	\State $F\gets F \cup f_i$
 \EndFor
@@
 \State $A_{norm}\gets 1 - normalize(A)$
-\Comment Shorter distance is higher weight
 \State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $Partitions\gets cluster(A_{pruned})$
-\ForAll{$p \in Partitions$} \Comment p is a set of feature points
-	\State $matches\gets matches \cup getMatches(p, threshold, 
-features)$
+\State $P\gets cluster(A_{pruned})$
+\ForAll{$p \in P$} \Comment p is a set of feature points
+	\State $M\gets M \cup getMatches(p, t, F)$
 \EndFor \\
@@
 \end{algorithm}
-
-Unlike the \emph{MM} algorithm the feature points are partitioned before 
-the matching stage. While the louvain clustering algorithm doesn't 
-require any parameters in itself, it tends towards clustering all 
-feature points together in the same partition if the graph is fully 
-connected or close. To ensure that the graph is well clustered, the 
-adjacency matrix is pruned so only edges above a certain threshold is 
-kept. From empirical analysis keeping around 2.5\% of edges seems to 
-work well. Figure \ref{fig:graph} shows the result of clustering the 
-feature points displayed as a graph where each node correspond to a 
-feature point. Here the border of nodes signifies the original image 
-while the color of the node is decided by what partition it belongs to.  
-Notice that since a limited amount of colors are used disconnected 
-subgraphs of the same color can be assumed to belong to separate 
-partitions. The sub figure \ref{fig:cropped_graph} shows a detailed 
+%
+While the louvain clustering algorithm doesn't require any parameters in 
+itself, it tends towards clustering all feature points together in the 
+same partition if the graph is very connected.  To ensure that the graph 
+is well clustered, the adjacency matrix is pruned so only edges above a 
+certain threshold is kept. From empirical analysis keeping around 2.5\% 
+of edges seems to work well. Figure \ref{fig:graph} shows the result of 
+clustering the feature points displayed as a graph where each node 
+correspond to a feature point. Here the border of nodes signifies the 
+original image while the color of the node is decided by what partition 
+it belongs to.  Notice that since a limited amount of colors are used 
+disconnected subgraphs of the same color can be assumed to belong to 
+separate partitions. Figure \ref{fig:cropped_graph} shows a detailed 
 section of the graph where the interplay between small partitions 
@@
 of several hundred nodes can be seen.
-
-\begin{figure}
-	\makebox[\textwidth][c]{%
-		\begin{subfigure}[t]{0.60\textwidth}
+%
+\begin{SCfigure*}
+	\makebox[0.7\textwidth][c]{%
+		\begin{subfigure}[t]{0.35\textwidth}
 			\centering
@@
 		\end{subfigure}%
-		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
 		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.60\textwidth}
+		\begin{subfigure}[t]{0.3\textwidth}
 			\centering
@@
 	}%
-	\label{fig:graph}
 	\caption{The partitioned feature graph. Every color signifies a 
 	partition while the edge color of each node signifies which image it 
-belongs to}
-\end{figure}
-
+belongs to. Notice the many clusters with only two or three nodes.}
+	\label{fig:graph}
+\end{SCfigure*}
+%
 The partitions group feature points by similarity which means that 
@@
 have several similar potential matches.
-
+%
 \begin{figure}
-	\makebox[\textwidth][c]{%
-		\begin{subfigure}[t]{0.60\textwidth}
+	\makebox[0.5\textwidth][c]{%
+		\begin{subfigure}[t]{0.24\textwidth}
 			\centering
@@
 		\end{subfigure}%
-		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
 		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.60\textwidth}
+		\begin{subfigure}[t]{0.24\textwidth}
 			\centering
@@
 	\\
-	\makebox[\textwidth][c]{
+	\makebox[0.5\textwidth][c]{
 		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
@@
 
-		\begin{subfigure}[t]{1.16\textwidth}
+		\begin{subfigure}[t]{0.5\textwidth}
 			\centering
@@
 	}%
+	\caption{Example of a partition of keypoints in an image}
 	\label{fig:compare_mirror}
-	\caption{Example of a partition of keypoints in an image}
 \end{figure}
-
-The matching algorithm for \emph{MMC} (algorithm \ref{alg-getmatches}) 
-goes through the partitions one by one and selects matches in the 
-following way: If the partition has no edges going from a feature point 
-in one image to a feature point in another image, the partition is 
-discarded. If we have more than one edge going between images then 
-$getMatches$ will behave as \emph{MM} and make sure that a 
-correspondence is symmetric, that it has a ratio above the desired 
-threshold and that it isn't matching two feature points from the same 
-image. Since feature points are all guaranteed to be fairly similar this 
-means that we can set the ratio threshold much higher than in \emph{MM} 
-and include matches that would normally have been discarded for not 
-being sufficiently unique.
-However as can be seen in the example in figure \ref{fig:cropped_graph} 
-many of the partitions contain only two feature points from different 
-images linked by one edge. This is often the case if all edges below a 
-certain similarity threshold have been removed in the graph, in which 
-case it's probable that some nodes will end up with only one outgoing 
-edge. This doesn't necessarily imply that the correspondence represented 
-by the edge is unique, but the only way to figure out if it is, is by 
-checking the similarity scores of the nearest neighbor as proposed in 
-\cite{lowe2004sift}.
-
-\begin{algorithm}
-\caption{Impl. of getMatches (\emph{from MMC algorithm})}
-\label{alg-getmatches}
-\begin{algorithmic}
-\Require $p$ : set of features, $threshold \in \mathbb{R}$, $features$ : 
-Set of all features
-\State $matches \gets \varnothing$
-\State $edges \gets \left\{getSimilarity(f_i, f_j) \mid getImg(f_i) \neq 
-getImg(f_j) \wedge f_i, f_j \in p \right\}$
-\If{$\left\vert edges \right\vert = 1$} \Comment If $\exists$ one edge 
-between images
-	\State $f_i,f_j \gets getInterImageFeatures(edges_{inter}, p)$
-	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features ~ 
-\backslash ~ \left\{f_i\right\})$
-	\State $f_s,f_t \gets getTwoNearestNeighbors(f_j, features ~ 
-\backslash ~ \left\{f_j\right\})$
-	\State $ratio_i \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
-f_j)$
-	\State $ratio_j \gets getSimilarity(f_j, f_t) / getSimilarity(f_j, 
-f_i)$
-	\If{$ratio_i < threshold \wedge ratio_j < threshold$}
-		\State $matches \gets matches \cup (f_i, f_j)$
-	\EndIf
-\ElsIf{$\left\vert edges \right\vert > 1$} \Comment If $\exists$ more 
-than one edge between images
-	\ForAll{$f_i \in p$}
-		\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, p ~ \backslash 
-~ \left\{f_i\right\})$
-		\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
-f_m)$
-		\If{$getImg(f_i) \neq getImg(f_m) \wedge ratio < threshold 
-\wedge (f_m, f_i) \not\in matches$}
-			\State $matches \gets matches \cup (f_i, f_m)$
-		\EndIf
-	\EndFor
-\EndIf
-
-\Return matches
-\end{algorithmic}
-\end{algorithm}
-
-The two algorithms introduced in this report are designed to work with 
-feature points such as ,  or similar. While the experimental results 
-have all been done with the SIFT descriptor, there aren't any 
-theoretical or practical issues with using other types of feature 
-points.
-
-In this report I propose two algorithms for better matching feature 
-points without any geometric assumptions about the images matched. The 
-two algorithms are complementary in the sense that the first, Mirror 
-Match (\emph{MM}) is less complex but performs slightly worse than 
-Mirror Match with Clustering (\emph{MMC}). In cases where high
-
-\section{Experimental Setup}
+%
+%The matching algorithm for \emph{MMC} (algorithm \ref{alg-getmatches}) 
+%goes through the partitions one by one and selects matches in the 
+%following way: If the partition has no edges going from a feature point 
+%in one image to a feature point in another image, the partition is 
+%discarded. If we have more than one edge going between images then 
+%$getMatches$ will behave as \emph{MM} and make sure that a 
+%correspondence is symmetric, that it has a ratio above the desired 
+%threshold and that it isn't matching two feature points from the same 
+%image. Since feature points are all guaranteed to be fairly similar 
+%this means that we can set the ratio threshold much higher than in 
+%\emph{MM} and include matches that would normally have been discarded 
+%for not being sufficiently unique.
+The matching for \emph{MMC} \emph{getMatches} finds matches within all 
+partitions with more than two elements as done in \emph{MM}. However as 
+can be seen in the example in figure \ref{fig:cropped_graph} many of the 
+partitions contain only two feature points from different images linked 
+by one edge. In this case we compare the ratio of this match to the next 
+best match across all partitions.
+%\begin{algorithm}
+%\caption{Impl. of getMatches (\emph{from MMC algorithm})}
+%\label{alg-getmatches}
+%\begin{algorithmic}
+%\Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
+%all features
+%\State $matches \gets \varnothing$
+%\State $edges \gets \left\{getSimilarity(f_i, f_j) \mid getImg(f_i) \neq 
+%getImg(f_j) \wedge f_i, f_j \in p \right\}$
+%\If{$\left\vert edges \right\vert = 1$} \Comment If $\exists$ one edge 
+%between images
+%	\State $f_i,f_j \gets getInterImageFeatures(edges_{inter}, p)$
+%	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features ~ 
+%\backslash ~ \left\{f_i\right\})$
+%	\State $f_s,f_t \gets getTwoNearestNeighbors(f_j, features ~ 
+%\backslash ~ \left\{f_j\right\})$
+%	\State $ratio_i \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
+%f_j)$
+%	\State $ratio_j \gets getSimilarity(f_j, f_t) / getSimilarity(f_j, 
+%f_i)$
+%	\If{$ratio_i < t\wedge ratio_j < t$}
+%		\State $matches \gets matches \cup (f_i, f_j)$
+%	\EndIf
+%\ElsIf{$\left\vert edges \right\vert > 1$} \Comment If $\exists$ more 
+%than one edge between images
+%	\ForAll{$f_i \in p$}
+%		\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, p ~ \backslash 
+%~ \left\{f_i\right\})$
+%		\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
+%f_m)$
+%		\If{$getImg(f_i) \neq getImg(f_m) \wedge ratio < t
+%\wedge (f_m, f_i) \not\in matches$}
+%			\State $matches \gets matches \cup (f_i, f_m)$
+%		\EndIf
+%	\EndFor
+%\EndIf
+%
+%\Return matches
+%\end{algorithmic}
+%\end{algorithm}
+%
+\section{Experiments}
 \label{experiment}
-
-To reliably measure the accuracity of a matching method on real images 
-we either need a set of image pairs tied by a homography or manually 
-count the number of inliers. The latter poses becomes unfeasable the 
-moment we attempt to test a non-trivial set of images, but has the 
-advantage of working with any image pair. Using a homography between 
-image pairs reduces the test cases to images where the matched areas lie 
-on a plane, or alternatively that there is no viewpoint change. This 
-greatly reduces the body of image pairs we can use to reliably test 
-matching methods. In \cite{mikolaczyk2005performance} Mikolajczyk and 
-Schmid introduces a set of images to compare the performance of feature 
-detectors. The test set looks at different feature descriptors 
-invariance faced with different lighting, blur, rotation as well as 
-viewpoint change. However in practice the image used for the view point 
-change featuring a wall of graffiti\footnote{To ensure that all points 
-lie on the same plane} has gone on to be used the most for later tests 
-given that most of the other test pairs have since become relatively 
-trivial\footnote{see \cite{wu2011robust} or \cite{delponte2006svd} for 
+%
+To reliably measure the accuracy of a matching method on real images we 
+either need a set of image pairs tied by a homography or manually count 
+the number of inliers. The latter becomes unfeasible the moment we 
+attempt to test a non-trivial set of images. In 
+\cite{mikolajczyk2005performance} Mikolajczyk and Schmid introduces a 
+set of images to compare the performance of feature detectors. The test 
+set covers different types of image variance such as different lighting, 
+blur, rotation as well as viewpoint change.However in practice the view 
+point change has gone on to be used the most for later tests given that 
+most of the other test pairs have since become easy to 
+match\footnote{see \cite{wu2011robust} or \cite{delponte2006svd} for 
 examples}.
-
-Inspired by this I have collected a set of image pairs featuring murals 
-of a few famous artists\footnote{Including Banksy, Blu and Shepard 
-Fairey among others}. Each pair consist of images of the same motif 
-taken from different angles, often including repetitive patterns and 
-texture. Based on this image set the two algorithms are tested on a 
-series of image patches from each pair. In order to test if a matching 
-is reliable we of course need correct matches when the image pair we are 
-testing on indeed features the same scene, but we also need to make sure 
-that we don't get any matches when the two images have nothing in 
-common. This means that it isn't enough just testing against pairs of 
-images that we know match. We also need to test against pairs that might 
-look like they could match but in fact don't.
-
-With this in mind I have created a test suite by cropping out $300$ 
-pixel by $300$ pixel patches of the original pair with a random vertical 
-and horizontal offset. Given an image pair I can obtain $n$ pairs of 
-patches where the two patches in any pair might or might not overlap.  
-This ensures that the patch pairs where there is no overlap still retain 
-a basic similarity to each other, while the patches that do overlap 
-often only overlap on a small part of their surface.
-
+%
+%Inspired by the graffiti image we have collected a set of image pairs 
+%featuring murals of a few different artists\footnote{Including Banksy, 
+%Blu and Shepard Fairey among others}. Each pair consist of images of 
+%the same motive taken from different angles, often including repetitive 
+%patterns and texture. Based on this image set the two algorithms are 
+%tested on a series of image patches from each pair. To verify that the 
+%algorithms proposed are reliable we need to test that we get good 
+%matches when images overlap and that we get no matches when they don't.  
+%This means that it isn't enough just testing against pairs of images 
+%that we know match.  We also need to test against pairs that might look 
+%like they could match but in fact don't.
+%
+To increase the amount of images that feature view port changes we have 
+collected a set of $8$ image pairs featuring murals from different 
+angles. From these pairs we can create test suites by cropping out $250$ 
+pixel by $250$ pixel patches of the original pair with a random vertical 
+and horizontal offset. Given a source image pair we can obtain $n$ pairs 
+of patches where the two patches in any pair might or might not overlap.  
+This ensures that the patch pairs whith no overlap still retain a basic 
+similarity to each other, while the patches that do overlap often only 
+overlap on a small part of their surface. Figure \ref{fig:fairey} shows 
+an example of possible pairs of test images (\ref{fig:fairey_crop}) 
+produced from two source images (\ref{fig:fairey1} and 
+\ref{fig:fairey2}). Producing $n$ such pairs allows us to test not just 
+how well the matching algorithm performs on corresponding images, but 
+also how many false positives we get on similar images that don't 
+overlap.\footnote{The set of source images and homographies as well as 
+	the a script to generate the cropped test sets based on them have 
+	been made available online together with the exact test sets used in 
+this paper on INSERT URL HERE}.
+%
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/murals}
+	\caption{Images in the mural test set}
+	\label{fig:mural}
+\end{figure*}
+%
+\begin{figure}
+%	\makebox[0.5\textwidth][c]{%
+%		\begin{subfigure}[t]{0.12\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/pair_example1}
+%			\caption{Mural by Fairey (1)}
+%			\label{fig:fairey1}
+%		\end{subfigure}%
+%		\qquad %add desired spacing between images, e. g. ~, \quad, 
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.12\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/pair_example2}
+%			\caption{Mural by Fairey (2)}
+%			\label{fig:fairey2}
+%		\end{subfigure}%
+%	}%
+%	\\
+	%\makebox[0.5\textwidth][c]{
+	%	%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+	%	%(or a blank line to force the subfigure onto a new line)
+	%	
+	%	\begin{subfigure}[t]{0.5\textwidth}
+	%	\end{subfigure}%
+	%}%
+	\centering
+	\includegraphics[width=0.5\textwidth]{images/crop_examples}
+	\caption{Example of test set produced by a source pair of images}
+	\label{fig:fairey}
+\end{figure}
+%
+\subsection{Experimental setup}
+%
+Using the image test sets described above, the \emph{MM} and \emph{MMC} 
+algorithms have been tested against a the algorithm Lowe proposed in 
+\cite{lowe2004sift} as well as the isodata matching algorithm proposed 
+in \cite{das2008event}. For each test set of cropped image pairs the 
+four algorithms\footnote{\emph{MM}, \emph{MMC}, \emph{SIFT} and 
+\emph{Isodata}} are applied to each pair of images ($100$ per test set), 
+and the threshold for each algorithm is varied over 50 evenly spaced 
+values.  For \emph{MM} and \emph{SIFT} these values lie between $0.4$ 
+and $0.8$ where as the threshold for \emph{MMC} and \emph{Isodata} is 
+varied between $0.8$ and $1.0$.  For each match returned by any of the 
+algorithms, the match is registered as an inlier if the endpoint in the 
+second image lies within $5$px of the true position calculated by the 
+homography.  That is, given $H$ relating $I_1$ with $I_2$ and a match 
+($p_1, p_2$) then the match is an inlier if $\left\vert Hp_1 - p_2 
+\right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < 5$. The 
+experiments are run on the $8$ image pairs in the test set, as well as 
+the graf image from \cite{mikolajczyk2005performance}.
+%
 \section{Results}
 \label{results}
+%
+%\begin{figure}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/fairey_burma_1}
+%			\caption{Burma by Fairey (1)}
+%			\label{fig:burma1}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/fairey_burma_2}
+%			\caption{Burma by Fairey (2)}
+%			\label{fig:burma2}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/result_fairey_burma}
+%			\caption{X: Nb of correct matches. Y: accuracy}
+%			\label{fig:result_burma}
+%		\end{subfigure}%
+%	}%
+%	\label{fig:burma}
+%	\caption{results on Burma by Fairey}
+%\end{figure}
+%
+%\begin{figure}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.25\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/fairey_lady_1}
+%			\caption{Lady by Fairey (1)}
+%			\label{fig:lady1}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.25\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/fairey_lady_2}
+%			\caption{Lady by Fairey (2)}
+%			\label{fig:lady2}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.55\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/result_fairey_lady}
+%			\caption{X: Nb of correct matches. Y: accuracy}
+%			\label{fig:result_lady}
+%		\end{subfigure}%
+%	}%
+%	\label{fig:lady}
+%	\caption{results on Lady by Fairey}
+%\end{figure}
+%
+%
+\begin{figure}
+	\makebox[0.5\textwidth][c]{%
+		\begin{subfigure}[t]{.13\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/graf}
+			\caption{Graf \cite{mikolajczyk2005performance}}
+			\label{fig:result_graf}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{.27\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_graf}
+			%\caption{Performance on Scharf}
+		\end{subfigure}%
+	}%
 
-\bibliographystyle{abbrv}
+	\makebox[0.5\textwidth][c]{%
+		\begin{subfigure}[t]{.15\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/scharf}
+			\caption{Faces (Scharf)}
+			\label{fig:result_faces}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{.27\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_scharf}
+			%\caption{Performance on Scharf}
+		\end{subfigure}%
+	}%
+	\label{fig:accuracy}
+	\caption{Accuracy Examples: Each plot pictures the result of $100$ 
+	image pairs generated from the source images shown to the left.  The 
+number of matches is the total number of matches for all $100$ image 
+pairs.}
+\end{figure}
+%
+\begin{figure}
+	\centering
+	\includegraphics[width=0.45\textwidth]{images/result_viewport}
+	\caption{Results on viewport changes. S is image 1 and 2 of the 
+	graffiti set in\cite{mikolajczyk2005performance}. M is 1 and 3, L is 
+1 and 4 while XL is 1 and 5. Solid line is result by \emph{MMC} while 
+dashed line is result by \emph{SIFT}}
+	\label{fig:result_viewport}
+\end{figure}
+%\begin{figure}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/houston_1}
+%			\caption{Houston (1)}
+%			\label{fig:houston1}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/houston_2}
+%			\caption{Houston (2)}
+%			\label{fig:houston2}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/result_houston}
+%			\caption{X: Nb of correct matches. Y: accuracy}
+%			\label{fig:result_houston}
+%		\end{subfigure}%
+%	}%
+%	\label{fig:houston}
+%	\caption{Results on Houston}
+%\end{figure}
+%
+%\begin{figure}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.25\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/blu_head_1}
+%			\caption{head by blu (1)}
+%			\label{fig:head1}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.25\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/blu_head_2}
+%			\caption{head by blu (2)}
+%			\label{fig:head2}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.55\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/result_blu_head}
+%			\caption{X: Nb of correct matches. Y: accuracy}
+%			\label{fig:result_head}
+%		\end{subfigure}%
+%	}%
+%	\label{fig:head}
+%	\caption{results on head by blu}
+%\end{figure}
+%
+%\begin{figure}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.25\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/blu_pencil_1}
+%			\caption{Pencil by Blu (1)}
+%			\label{fig:pencil1}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.25\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/blu_pencil_2}
+%			\caption{Pencil by Blu (2)}
+%			\label{fig:pencil2}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.55\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/result_blu_pencil}
+%			\caption{X: Nb of correct matches. Y: accuracy}
+%			\label{fig:result_pencil}
+%		\end{subfigure}%
+%	}%
+%	\label{fig:pencil}
+%	\caption{Results on Pencil by Blu}
+%\end{figure}
+%
+%\begin{figure}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/banksy_city_1}
+%			\caption{City by Banksy (1)}
+%			\label{fig:city1}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/banksy_city_2}
+%			\caption{City by Banksy (2)}
+%			\label{fig:city2}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/result_banksy_city}
+%			\caption{X: Nb of correct matches. Y: accuracy}
+%			\label{fig:result_city}
+%		\end{subfigure}%
+%	}%
+%	\label{fig:city}
+%	\caption{results on City}
+%\end{figure}
+%
+%\begin{figure}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/banksy_stroller_1}
+%			\caption{Stroller by Banksy (1)}
+%			\label{fig:stroller1}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/banksy_stroller_2}
+%			\caption{Stroller by Banksy (2)}
+%			\label{fig:stroller2}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/result_banksy_stroller}
+%			\caption{X: Nb of correct matches. Y: accuracy}
+%			\label{fig:result_stroller}
+%		\end{subfigure}%
+%	}%
+%	\label{fig:stroller}
+%	\caption{Results on Stroller by Banksy}
+%\end{figure}
+%
+%
+%\begin{figure}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/graf_1}
+%			\caption{Graf (1)}
+%			\label{fig:graf1}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/graf_3}
+%			\caption{Graf (3)}
+%			\label{fig:graf3}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.35\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/result_graf}
+%			\caption{X: Nb of correct matches. Y: accuracy}
+%			\label{fig:result_graf}
+%		\end{subfigure}%
+%	}%
+%	\label{fig:graf}
+%	\caption{results on Graf}
+%\end{figure}
+%
+Figure \ref{fig:accumulated} shows the results on the test set proposed 
+earlier\footnote{Illustrated in Figure \ref{mural}}. The performance of 
+the proposed algorithm is shown to be [FILL IN ONCE THE DATA IS READY] 
+to \emph{SIFT} and \emph{Isodata} when testing on image pairs that might 
+not overlap. This result is repeated (TODO: is it?) when testing on the 
+graf image as demonstrated in Figure \ref{fig:result_graf}. To 
+illustrate that this performance improvement isn't limited to street 
+art, figure \ref{fig:gallagher} shows the performance on an image from 
+the Gallagher data set \cite{gallagher2008} where images featuring 
+occlusion and change of perspective are matched. While performance is of 
+course affected by the magnitude of for example view port change, figure 
+\ref{fig:result_viewport} shows that \emph{MMC} consistently outperforms 
+the \emph{SIFT} algorithm over different magnitudes of change in 
+perspective. TODO: include note on plot for different descriptors.
+
+In terms of performance, table \ref{table:running_times} shows the 
+running time of the four algorithms over $100$ image pairs of $250$px by 
+$250$px. These numbers should be interpreted with the knowledge that 
+much of the code behind \emph{MMC} and \emph{Isodata} is implemented in 
+python while \emph{MM} and \emph{SIFT} makes use of opencv to execute 
+computationally intensive operations in C++ which renders it much 
+faster.
+%
+\begin{savenotes}
+\begin{table}
+	\centering
+	\small
+\begin{tabular}{l*{4}{c}}
+	Algorithm: & \emph{SIFT} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
+	\\
+	\noalign{\smallskip} 
+	%
+	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
+\end{tabular}
+\caption{Running times\footnote{As tested on a Intel(R) Core(TM) i5-3550 
+CPU @ 3.30GHz with 8Gb memory}}
+\label{table:running_times}
+\end{table}
+\end{savenotes}
+%
+\section{Summary}
+We have addressed the problem of matching feature points without using 
+geometrical constraints and proposed two algorithms \emph{Mirror Match 
+(MM)} and \emph{Mirror Match with Clustering (MMC)}. The two algorithms 
+share the same common idea that feature points should have better 
+matches in another image than in the image they came from to be 
+considered good matches and \emph{MMC} further improves on this idea by 
+using the structure of the similarity graph of the feature points. We 
+also address how to test the algorithms by constructing a image set of 
+$8$ source image pairs and a way to generate testsets based on these 
+pairs. The proposed approach shows promising results when comparing the 
+algorithms on $9$ testsets of $100$ image pairs each where many of the 
+pairs might not have any overlapping areas. In future work it will be 
+usefull to investigate how the algorithms perform when testing on sets 
+of images instead of pairs.
+%
+\bibliographystyle{IEEEtran}
 \bibliography{bibliography}

### 2013-06-05 code/display.py

@@ -289,17 +289,33 @@ def accuDetail(correct, total, legend, ylim = 100, treshold=1000) :
 	accuHist(accu, legend, ylim=ylim)
 
 
-def accuPlot(correct, total, legends, ylim=(0.0,1.01), xlim = None) :
-	pylab.figure(figsize=(3, 3))
+def accuPlot(correct, total, legends, ylim=(0.0,1.01), xlim = None, size = (4,6), compareCorrect = None, compareTotal = None, compareLabel = None, outside = False) :
+	fig = pylab.figure(figsize=size)
+	ax = pylab.subplot(111)
 	for ts,cs,l,color in zip(total, correct, legends, ["blue", "cyan", "green", "orange", "red"]) :
 		xs = [sum(t) for t in ts]
 		ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for (c, t) in zip(cs, ts)]
-		pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.65)
+		pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.75)
 		pylab.legend(loc="best")
+	if compareCorrect != None and compareTotal != None and compareLabel != None :
+		for ts,cs,l,color in zip(compareTotal, compareCorrect, legends, ["blue", "cyan", "green", "orange", "red"]) :
+			xs = [sum(t) for t in ts]
+			ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for (c, t) in zip(cs, ts)]
+			pylab.plot(xs, ys, '--', label="%s - %s" % (l, compareLabel), color=color, alpha=0.95)
+			pylab.legend(loc="best")
 	removeDecoration()
 	pylab.xlabel("# of Matches")
 	pylab.ylabel("Accuracy")
 	pylab.ylim(ylim[0],ylim[1])
+
+	if outside == True :
+		# Shink current axis by 20%
+		box = ax.get_position()
+		ax.set_position([box.x0, box.y0, box.width * 0.75, box.height])
+
+		# Put a legend to the right of the current axis
+		ax.legend(loc='center left', bbox_to_anchor=(1, 0.5))
+
 	if xlim != None : pylab.xlim(0,xlim)
 
 
@@ -541,7 +557,7 @@ def graph_partitions(g, clusters, filename="graph_clusters.png") :
 
 
 
-def graph_on_images(graph, images, clusters = "orange", path="graph_on_images.png", vertex_size=5, edge_color=[0.0, 0.0, 0.0, 0.8]) :
[…]

### 2013-06-05 code/isodata.py

@@ -77,11 +77,16 @@ def cluster(points, k_init=None, max_iterations=100, min_partition_size=5, max_s
 	"""
 	
 	# Set a sensible k_init if it wasn't specified
-	if k_init == None or len(points) < k_init:
+	if k_init == None:
 		k_init = points.shape[0] / (min_partition_size * 2)
+
+	if k_init > points.shape[0] :
+		k_init = points.shape[0] / 2
+
 	
 	# Sample nb_partitions points as initial guess
 	random.seed(seed)
+	print("Amount of points: %i, k_init: %i" % (len(points), k_init))
 	centers = numpy.array(random.sample(points, k_init))
 	
 	# Iterate

### 2013-06-05 code/isomatch.py

@@ -54,6 +54,8 @@ def match(paths, thresholds, options = {}) :
 	# Get matches
 	match_points = getMatchPoints(indices, ks, ds, descriptor_type = descriptor_type)
 
+	if len(match_points) == 0 : return [[] for _ in thresholds]
+
 	# Partition with isodata
 	part_1 = isodata.cluster(positions[indices==0], k_init=k_init, max_iterations=max_iterations, min_partition_size=min_partition_size, max_sd=max_sd, min_distance=min_distance)
 	part_2 = isodata.cluster(positions[indices==1], k_init=k_init, max_iterations=max_iterations, min_partition_size=min_partition_size, max_sd=max_sd, min_distance=min_distance)

### 2013-06-06 text/clustering.tex
V. 2.0

@@
 \usepackage{footnote}
+\usepackage[font={small}]{caption}
 \usepackage{sidecap}
@@
 collected a set of $8$ image pairs featuring murals from different 
-angles. From these pairs we can create test suites by cropping out $250$ 
-pixel by $250$ pixel patches of the original pair with a random vertical 
-and horizontal offset. Given a source image pair we can obtain $n$ pairs 
-of patches where the two patches in any pair might or might not overlap.  
-This ensures that the patch pairs whith no overlap still retain a basic 
-similarity to each other, while the patches that do overlap often only 
-overlap on a small part of their surface. Figure \ref{fig:fairey} shows 
-an example of possible pairs of test images (\ref{fig:fairey_crop}) 
-produced from two source images (\ref{fig:fairey1} and 
-\ref{fig:fairey2}). Producing $n$ such pairs allows us to test not just 
-how well the matching algorithm performs on corresponding images, but 
-also how many false positives we get on similar images that don't 
-overlap.\footnote{The set of source images and homographies as well as 
-	the a script to generate the cropped test sets based on them have 
-	been made available online together with the exact test sets used in 
-this paper on INSERT URL HERE}.
+angles.  From these pairs we can create test suites by cropping out 
+$250$ pixel by $250$ pixel patches of the original pair with a random 
+vertical and horizontal offset. Given a source image pair we can obtain 
+$n$ pairs of patches where the two patches in any pair might or might 
+not overlap.  This ensures that the patch pairs whith no overlap still 
+retain a basic similarity to each other, while the patches that do 
+overlap often only overlap on a small part of their surface. This 
+dataset will from here on be referred to as the \emph{Murals} dataset.  
+Figure \ref{fig:fairey} shows an example of possible pairs of test 
+images produced from two source images to the left.  Producing $n$ such 
+pairs allows us to test not just how well the matching algorithm 
+performs on corresponding images, but also how many false positives we 
+get on similar images that don't overlap.\footnote{The set of source 
+	images and homographies as well as the script to generate the 
+cropped test sets based on them have been made available online together 
+with the exact test sets used in this paper on 
+\href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.
 %
@@
 \begin{figure}
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{0.12\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pair_example1}
-%			\caption{Mural by Fairey (1)}
-%			\label{fig:fairey1}
-%		\end{subfigure}%
-%		\qquad %add desired spacing between images, e. g. ~, \quad, 
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.12\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pair_example2}
-%			\caption{Mural by Fairey (2)}
-%			\label{fig:fairey2}
-%		\end{subfigure}%
-%	}%
-%	\\
-	%\makebox[0.5\textwidth][c]{
-	%	%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-	%	%(or a blank line to force the subfigure onto a new line)
-	%	
-	%	\begin{subfigure}[t]{0.5\textwidth}
-	%	\end{subfigure}%
-	%}%
+	\makebox[0.5\textwidth][c]{%
+		\begin{subfigure}[t]{0.044\textwidth}
 			\centering
-	\includegraphics[width=0.5\textwidth]{images/crop_examples}
+			\includegraphics[width=\textwidth]{images/pair_example1}
+			\label{fig:fairey1}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, (or a 
+		%blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.044\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pair_example2}
+			\label{fig:fairey2}
+		\end{subfigure}%
+		~ %
+		\begin{subfigure}[t]{0.37\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/crop_examples}
+		\end{subfigure}%
+	}%
 	\caption{Example of test set produced by a source pair of images}
@@
 %
-\subsection{Experimental setup}
+%\subsection{Experimental setup}
 %
 Using the image test sets described above, the \emph{MM} and \emph{MMC} 
-algorithms have been tested against a the algorithm Lowe proposed in 
-\cite{lowe2004sift} as well as the isodata matching algorithm proposed 
-in \cite{das2008event}. For each test set of cropped image pairs the 
-four algorithms\footnote{\emph{MM}, \emph{MMC}, \emph{SIFT} and 
-\emph{Isodata}} are applied to each pair of images ($100$ per test set), 
-and the threshold for each algorithm is varied over 50 evenly spaced 
-values.  For \emph{MM} and \emph{SIFT} these values lie between $0.4$ 
-and $0.8$ where as the threshold for \emph{MMC} and \emph{Isodata} is 
-varied between $0.8$ and $1.0$.  For each match returned by any of the 
-algorithms, the match is registered as an inlier if the endpoint in the 
-second image lies within $5$px of the true position calculated by the 
-homography.  That is, given $H$ relating $I_1$ with $I_2$ and a match 
-($p_1, p_2$) then the match is an inlier if $\left\vert Hp_1 - p_2 
-\right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < 5$. The 
+algorithms have been tested against \emph{SIFT}, the algorithm Lowe 
+proposed in \cite{lowe2004sift} as well as the \emph{Isodata} matching 
+algorithm proposed in \cite{das2008event} which uses geometric 
+information to improve the matching. For each test set of cropped image 
+pairs the four algorithms\footnote{\emph{MM}, \emph{MMC}, \emph{SIFT} 
+and \emph{Isodata}} are applied to each pair of images ($100$ per test 
+set), and the threshold for each algorithm is varied over 50 evenly 
+spaced values. For each match returned by any of the algorithms, the 
+match is registered as an inlier if given $H$ relating $I_1$ with $I_2$ 
+and a match ($p_1, p_2$) the match is an inlier if $\left\vert Hp_1 - 
+p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < 5$. The 
 experiments are run on the $8$ image pairs in the test set, as well as 
@@
 	}%
+
+	\makebox[0.5\textwidth][c]{%
+		\begin{subfigure}[t]{.15\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pitts}
+			\caption{Pittsburg \cite{gallagher2008}}
+			\label{fig:result_pitts}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{.27\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_pitts}
+			%\caption{Performance on Scharf}
+		\end{subfigure}%
+	}%
 	\label{fig:accuracy}
@@
 	\label{fig:result_viewport}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.45\textwidth]{images/result_accumulated}
+	\caption{Results on the mural dataset. For each of the 8 source 
+		image pairs, 100 test pairs have been created. The x-axis 
+		illustrates the accumulated returned matches for all pairs.
+		changes.}
+	\label{fig:result_accumulated}
 \end{figure}
@@
 %
-Figure \ref{fig:accumulated} shows the results on the test set proposed 
-earlier\footnote{Illustrated in Figure \ref{mural}}. The performance of 
-the proposed algorithm is shown to be [FILL IN ONCE THE DATA IS READY] 
-to \emph{SIFT} and \emph{Isodata} when testing on image pairs that might 
-not overlap. This result is repeated (TODO: is it?) when testing on the 
-graf image as demonstrated in Figure \ref{fig:result_graf}. To 
-illustrate that this performance improvement isn't limited to street 
-art, figure \ref{fig:gallagher} shows the performance on an image from 
-the Gallagher data set \cite{gallagher2008} where images featuring 
-occlusion and change of perspective are matched. While performance is of 
-course affected by the magnitude of for example view port change, figure 
-\ref{fig:result_viewport} shows that \emph{MMC} consistently outperforms 
-the \emph{SIFT} algorithm over different magnitudes of change in 
-perspective. TODO: include note on plot for different descriptors.
+Figure \ref{fig:result_accumulated} shows the accumulated results on the 
+\emph{Murals} dataset\footnote{Illustrated in Figure \ref{mural}}. It 
+shows that \emph{MMC} and \emph{MM} is overall superior to both 
+\emph{SIFT} and \emph{Isodata} which uses geometric constraints when 
+tested on image pairs with no assurance of overlap depicting simple 
+planar scenes. Figure \ref{fig:result_faces} illustrates the result on a 
+particular image pair from the \emph{Murals} dataset. For an example of 
+a real life use case \ref{fig:result_pitts} shows the results on 
+potentially overlapping image pairs generated from a typical holiday 
+scene with partial overlap and slight view port change. As can be seen 
+in figure \ref{fig:result_viewport}, \emph{MMC} consistently outperforms 
+\emph{SIFT} across different magnitudes of the viewport change. For the 
+results on image 1 and 3 from the \emph{Graf} dataset, see figure 
+\ref{fig:result_graf}.
+Generally all plots show good results by \emph{Isodata} when only the 
+best matches are returned, but when the thresholds are more lenient the 
+quality of the returned matches degrades quickly and \emph{MMC} and 
+\emph{MM} yield better results.
 
@@
 using the structure of the similarity graph of the feature points. We 
-also address how to test the algorithms by constructing a image set of 
-$8$ source image pairs and a way to generate testsets based on these 
-pairs. The proposed approach shows promising results when comparing the 
-algorithms on $9$ testsets of $100$ image pairs each where many of the 
-pairs might not have any overlapping areas. In future work it will be 
-usefull to investigate how the algorithms perform when testing on sets 
-of images instead of pairs.
+also address how to test the algorithms by constructing the 
+\emph{Murals} dataset consisting of $8$ source image pairs and a way to 
+generate testsets based on these pairs.  The proposed approach shows 
+promising results on both the \emph{Murals} dataset as well as a real 
+life example from the Gallagher dataset and the \emph{Graf} image set, 
+beating even a method using geometrical constraints when matching image 
+pairs that might not overlap.
 %

### 2013-06-06 text/clustering.tex
Fixed and compressed some introductory text

@@
 possible matches within the image itself. The second algorithm extends 
-this idea by using the community structure in the similarity graph of 
+this idea by using community structure in the similarity graph of 
 feature points to reliably find correspondences. To evaluate the 
@@
 correspondences among many possible pairings. Several methods have been 
-proposed in the literature to solve this problem. In particular many 
-approaches look at the geometric configuration of the feature points and 
-match them according to assumptions made about the geometric 
-relationship between the images matched. These assumptions are then used 
-to create constraints used to evaluate the matches such as angular 
-constraints (\cite{kim2008efficient}), epipolar constraints 
-(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
-constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}).
+proposed in the literature to solve this problem. Many approaches look 
+at the geometric configuration of the feature points and match them 
+according to assumptions made about the geometric relationship between 
+the images matched. These assumptions are then used to create 
+constraints used to evaluate the matches such as angular constraints 
+\cite{kim2008efficient}, epipolar constraints \cite{torr2000mlesac}, 
+\cite{chum2005matching} and pairwise constraints \cite{choi2009robust}, 
+\cite{leordeanu2005spectral}.
 %
@@
 %
-Another approach proposed in the literature is to pick out different 
-zones in each image and pair zones when correspondence pairs are mainly 
-found going from one zone to another. This allows for the filtering of 
-all correspondences that do not fall within paired zones.  
-\cite{das2008event} proposes clustering feature points by using their 
-geometric position and exclude correspondences that are geometrically 
-deviant. A more sophisticated approach is introduced in 
-\cite{wu2011robust} where the zones are created by using the MSER 
-feature detector to find areas of interest in the images. These areas 
-can be defined as an ellipse with a certain radius around the interest 
-points. The feature points that fall within this ellipse are then 
-matched according to epipolar constraints.  
+Alternatively we can pick out different areas in each image and pair 
+areas when correspondence pairs are mainly found going from one area to 
+another. This allows for the filtering of all correspondences that do 
+not fall within paired areas. Examples include \cite{das2008event} and 
+\cite{wu2011robust}.
+%
+%proposes clustering feature points by using their geometric position 
+%and exclude correspondences that are geometrically deviant. A more 
+%sophisticated approach is introduced in \cite{wu2011robust} where the 
+%areas are created by using the MSER feature detector to find areas of 
+%interest in the images. These areas can be defined as an ellipse with a 
+%certain radius around the interest points. The feature points that fall 
+%within this ellipse are then matched according to epipolar constraints.  
 %
 In practice however, there are many situations where using the geometry 
-of the image to filter correspondences is not possible. This situation 
-most often arise when the assumptions made by a geometric method aren't 
-valid. In object recognition for example, adjecent objects in one photo 
-might be separated in another. In addition methods using geometric 
-constraints all require a set of correspondences to begin with. If this 
-set of correspondences is narrowed down to a smaller set with a higher 
-ratio of correct matches the result of the geometric matching will be 
-both faster and more accurate.  Finally some use cases might require a 
-performance that can't be achieved by a more complex geometric method 
-where simple non geometric methods might be able to provide additional 
-matching accuracy with a smaller performance penalty.
-%
+of the image to filter correspondences is not possible, such as object 
+recognition where adjecent objects in one photo might be separated in 
+another. Another example is images that do not overlap where algorithms 
+might still find matches adhering to the imposed geometric constraints.
+In addition methods using geometric constraints all require a set of 
+correspondences to begin with. If this set of correspondences is 
+narrowed down to a smaller set with a higher ratio of correct matches 
+the result of the geometric matching will be both faster and more 
+accurate.  Finally some use cases might require a performance that can't 
+be achieved by a more complex geometric method where simple non 
+geometric methods might be able to provide sufficient matching accuracy 
+with a smaller performance penalty.
+
 There are a relatively small number of algorithms proposed to solve the 
@@
 scores by their uniqueness and picking the $n$ best we get a set of 
-correspondences that are distinctly matched across the two images.
-%
+correspondences that are distinctly matched across the two images. This 
+method will be referred to as \emph{SIFT} in this paper.
+
 In turn the two methods proposed in this paper are inspired by a simple 
@@
 			\includegraphics[width=\textwidth]{images/mirror_match_off}
-			\caption{Baseline Result}
+			\caption{SIFT}
 			\label{fig:unique}
@@
 	}
-	\caption{Illustration of matches filtered by \emph{MM}}
+	\caption{Illustration of matches filtered by \emph{MM}. For each 
+	correct match found between the two images, a green line is shown.  
+Incorrect matches are marked with a red line. Figure \ref{fig:within} 
+shows the correspondences found by mirror match, but including all 
+matches that are found within the same image. }
 	\label{fig:comparemirror}
@@
 Figure \ref{fig:comparemirror} shows an example of the result of 
-\emph{MM}. In figure \ref{fig:unique} the matches between two images are 
-shown when using the \emph{SIFT} algorithm from \cite{lowe2004sift}. For 
-each match found between the two images, a line has been drawn. The 
-color of the line is green in case the match is correct and red for 
-incorrect matches. Figure \ref{fig:within} shows the correspondences 
-found by mirror match, but including all matches that are found within 
-the same image. Notice how the by the bottom of the image admits 
+\emph{MM}. Notice how the by the bottom of the image admits 
 correspondences that can conveniently be removed as done in sub figure 
@@
 of edges seems to work well. Figure \ref{fig:graph} shows the result of 
-clustering the feature points displayed as a graph where each node 
-correspond to a feature point. Here the border of nodes signifies the 
-original image while the color of the node is decided by what partition 
-it belongs to.  Notice that since a limited amount of colors are used 
-disconnected subgraphs of the same color can be assumed to belong to 
-separate partitions. Figure \ref{fig:cropped_graph} shows a detailed 
-section of the graph where the interplay between small partitions 
-consisting of two or three nodes as well as larger partitions consisting 
-of several hundred nodes can be seen.
+clustering the feature points displayed as a graph.
 %
@@
 	}%
-	\caption{The partitioned feature graph. Every color signifies a 
-	partition while the edge color of each node signifies which image it 
-belongs to. Notice the many clusters with only two or three nodes.}
+	\caption{The partitioned feature graph. Each vertex represents a 
+		feature point while an edge represent a high similarity between 
+		points. A partition is a connected group marked by a color.  Due 
+		to a limited amount of colors some disconnected partitions have 
+		been assigned the same color. The edge color of each node 
+		signifies which image it belongs to. In the detailed crop to the 
+		right the various cluster sizes can be seen, ranging from 
+	hundreds of feature points to only two or three.}
 	\label{fig:graph}

### 2013-06-06 text/clustering.tex
V. 2.2

@@
 repetitive structures such as buildings often feature in larger 
-partitions as exemplified in figure \ref{fig:compare_mirror}. Here the 
-cluster shown in part \ref{fig:pitts_partition} contains left window 
-corners from two buildings across both images. This is an example of 
-feature points that are hard to match correctly since each point will 
-have several similar potential matches.
-%
+partitions as exemplified in figure \ref{fig:compare_mirror}. %
 \begin{figure}
@@
 	}%
-	\caption{Example of a partition of keypoints in an image}
+	\caption{Example of a partition of keypoints in an image pair. The 
+		partition shown contains window corners from a building in the 
+		left image and similar corners on the shirt in the right image.  
+	}
 	\label{fig:compare_mirror}
@@
 %
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/murals}
-	\caption{Images in the mural test set}
-	\label{fig:mural}
-\end{figure*}
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=\textwidth]{images/murals}
+%	\caption{Images in the mural test set}
+%	\label{fig:mural}
+%\end{figure*}
 %
@@
 	graffiti set in\cite{mikolajczyk2005performance}. M is 1 and 3, L is 
-1 and 4 while XL is 1 and 5. Solid line is result by \emph{MMC} while 
-dashed line is result by \emph{SIFT}}
+1 and 4 while XL is 1 and 5. \emph{MMC} is represented by a solid line 
+while \emph{SIFT} results are shown by a dashed line.}
 	\label{fig:result_viewport}
@@
 Figure \ref{fig:result_accumulated} shows the accumulated results on the 
-\emph{Murals} dataset\footnote{Illustrated in Figure \ref{mural}}. It 
-shows that \emph{MMC} and \emph{MM} is overall superior to both 
-\emph{SIFT} and \emph{Isodata} which uses geometric constraints when 
-tested on image pairs with no assurance of overlap depicting simple 
-planar scenes. Figure \ref{fig:result_faces} illustrates the result on a 
-particular image pair from the \emph{Murals} dataset. For an example of 
-a real life use case \ref{fig:result_pitts} shows the results on 
-potentially overlapping image pairs generated from a typical holiday 
-scene with partial overlap and slight view port change. As can be seen 
-in figure \ref{fig:result_viewport}, \emph{MMC} consistently outperforms 
-\emph{SIFT} across different magnitudes of the viewport change. For the 
-results on image 1 and 3 from the \emph{Graf} dataset, see figure 
-\ref{fig:result_graf}.
+\emph{Murals} dataset. It shows that \emph{MMC} and \emph{MM} is overall 
+superior to both \emph{SIFT} and \emph{Isodata} which uses geometric 
+constraints when tested on image pairs with no assurance of overlap 
+depicting simple planar scenes. Figure \ref{fig:result_faces} 
+illustrates the result on a particular image pair from the \emph{Murals} 
+dataset. For an example of a real life use case \ref{fig:result_pitts} 
+shows the results on potentially overlapping image pairs generated from 
+a typical holiday scene with partial overlap and slight view port 
+change. As can be seen in figure \ref{fig:result_viewport}, \emph{MMC} 
+consistently outperforms \emph{SIFT} across different magnitudes of the 
+viewport change. For the results on image 1 and 3 from the \emph{Graf} 
+dataset, see figure \ref{fig:result_graf}.
 Generally all plots show good results by \emph{Isodata} when only the 
@@
 \end{tabular}
-\caption{Running times\footnote{As tested on a Intel(R) Core(TM) i5-3550 
-CPU @ 3.30GHz with 8Gb memory}}
+\caption{Running times as tested on a Intel(R) Core(TM) i5-3550 CPU @ 
+3.30GHz with 8Gb memory}
 \label{table:running_times}

### 2013-06-06 text/clustering.tex
Made the paper better still

@@
-\documentclass[12pt,journal,compsoc]{IEEEtran}
+\documentclass[12pt,journal]{IEEEtran}
 %\documentclass{article}
@@
 constraints}
-\author{Jonas Arnfred and what to put here exactly?}
+%\author{Jonas Arnfred and what to put here exactly?}
 
@@
 algorithms experimentally we introduce a set of 8 image pairs all 
-containing view port changes and a simple method to generate a large 
+containing viewport changes and a simple method to generate a large 
 amount of test cases based on these 8 pairs. The experimental results 
@@
 found by looking at the two nearest neighbors of each feature point and 
-calculating a match score by the ratio of similarities. By ranking the 
-scores by their uniqueness and picking the $n$ best we get a set of 
+calculating a match score by the ratio of similarities. Ranking the 
+scores by their uniqueness and picking the $n$ best produces a set of 
 correspondences that are distinctly matched across the two images. This 
@@
 other geometric solutions when appropriate.
-%
+
 %Based on this idea the two proposed methods find reliable matches as 
@@
 %
+\section{Matching Methods}
 \subsection{Mirror Match (\emph{MM})}
@@
 \label{alg-mm}
+{\fontsize{10}{10}\selectfont
 \begin{algorithmic}
@@
 \end{algorithmic}
+}
 \end{algorithm}
@@
 	\makebox[\textwidth][c]{%
-		\begin{subfigure}[t]{0.30\textwidth}
+		\begin{subfigure}[t]{0.32\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
+			\caption{Source image}
+			\label{fig:pitts_source}
+		\end{subfigure}%
+		\enspace %
+		\begin{subfigure}[t]{0.32\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
+			\caption{Keypoints Displayed}
+			\label{fig:pitts_keypoints}
+		\end{subfigure}%
+		\enspace %add desired spacing between images, e. g. ~, \quad, 
+		%\qquad (or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.32\textwidth}
 			\centering
 			\includegraphics[width=\textwidth]{images/mirror_match_off}
-			\caption{SIFT}
+			\caption{\emph{SIFT}}
 			\label{fig:unique}
 		\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.30\textwidth}
+	}
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{0.32\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/mirror_match}
+			\caption{\emph{MM}}
+			\label{fig:without}
+		\end{subfigure}%
+		\enspace%
+		\begin{subfigure}[t]{0.32\textwidth}
 			\centering
@@
 		\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, \qquad
-		  %(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.30\textwidth}
+		\enspace %add desired spacing between images, e. g. ~, \quad, 
+		%\qquad (or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.32\textwidth}
 			\centering
-			\includegraphics[width=\textwidth]{images/mirror_match}
-			\caption{\emph{MM}}
-			\label{fig:without}
-		\end{subfigure}
-	}
+			\includegraphics[width=\textwidth]{images/MMC_partition}
+			\caption{\emph{MMC} Partition Example}
+			\label{fig:pitts_partition}
+		\end{subfigure}%
+	}%
 	\caption{Illustration of matches filtered by \emph{MM}. For each 
@@
 shows the correspondences found by mirror match, but including all 
-matches that are found within the same image. }
-	\label{fig:comparemirror}
-\end{figure*}
-%
-Figure \ref{fig:comparemirror} shows an example of the result of 
-\emph{MM}. Notice how the by the bottom of the image admits 
+matches that are found within the same image. }%
+	\label{fig:comparemirror}%
+\end{figure*}%
+
+In figure \ref{fig:comparemirror} an example of the result of \emph{MM} 
+is illustrated. Notice how the by the bottom of the image admits 
 correspondences that can conveniently be removed as done in sub figure 
@@
 algorithm are shown.
-%
+
 \subsection{Mirror Match with Clustering (\emph{MMC})}
@@
 %then combined into one to achieve the right amount of partitions.
-%
+
 We use the Louvain Method\cite{blondel2008} for clustering feature 
@@
 \label{alg-mmc}
+{\fontsize{10}{10}\selectfont
 \begin{algorithmic}
@@
 \end{algorithmic}
+}
 \end{algorithm}
-%
+
 While the louvain clustering algorithm doesn't require any parameters in 
@@
 \end{SCfigure*}
-%
+
 The partitions group feature points by similarity which means that 
 repetitive structures such as buildings often feature in larger 
-partitions as exemplified in figure \ref{fig:compare_mirror}. %
-\begin{figure}
-	\makebox[0.5\textwidth][c]{%
-		\begin{subfigure}[t]{0.24\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-			\caption{Source image}
-			\label{fig:pitts_source}
-		\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.24\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-			\caption{Keypoints Displayed}
-			\label{fig:pitts_keypoints}
-		\end{subfigure}%
-	}%
-	\\
-	\makebox[0.5\textwidth][c]{
-		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-
-		\begin{subfigure}[t]{0.5\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/MMC_partition}
-			\caption{A Partition Example}
-			\label{fig:pitts_partition}
-		\end{subfigure}%
-	}%
-	\caption{Example of a partition of keypoints in an image pair. The 
-		partition shown contains window corners from a building in the 
-		left image and similar corners on the shirt in the right image.  
-	}
-	\label{fig:compare_mirror}
-\end{figure}
+partitions as exemplified in figure \ref{fig:pitts_partition}.
+%
+%\begin{figure}
+%	\makebox[0.5\textwidth][c]{%
+%		\begin{subfigure}[t]{0.24\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
+%			\caption{Source image}
+%			\label{fig:pitts_source}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%	}%
+%	\\
+%	\makebox[0.5\textwidth][c]{
+%		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+%		%(or a blank line to force the subfigure onto a new line)
+%		
+%		\begin{subfigure}[t]{0.5\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/MMC_partition}
+%			\caption{A Partition Example}
+%			\label{fig:pitts_partition}
+%		\end{subfigure}%
+%	}%
+%	\caption{Example of a partition of keypoints in an image pair. The 
+%		partition shown contains window corners from a building in the 
+%		left image and similar corners on the shirt in the right image.  
+%	}
+%	\label{fig:compare_mirror}
+%\end{figure}
 %
@@
 %for not being sufficiently unique.
+
 The matching for \emph{MMC} \emph{getMatches} finds matches within all 
@@
 the number of inliers. The latter becomes unfeasible the moment we 
-attempt to test a non-trivial set of images. In 
-\cite{mikolajczyk2005performance} Mikolajczyk and Schmid introduces a 
+attempt to test a non-trivial set of images.
+
+In \cite{mikolajczyk2005performance} Mikolajczyk and Schmid introduces a 
 set of images to compare the performance of feature detectors. The test 
 set covers different types of image variance such as different lighting, 
-blur, rotation as well as viewpoint change.However in practice the view 
-point change has gone on to be used the most for later tests given that 
-most of the other test pairs have since become easy to 
-match\footnote{see \cite{wu2011robust} or \cite{delponte2006svd} for 
-examples}.
-%
+blur, rotation as well as viewpoint change. Inspired by this 
+dataset\footnote{In particular by the 'Graf' image set} and motivated by 
+the need for more image pairs featuring viewport changes, we have 
+compiled a set of $8$ image pairs consisting of the same subject taken 
+from two different angles. The images are collected from Flickr's 
+database of images published under a creative commons 
+licence\footnote{\href{http://creativecommons.org/}{www.creativecommons.org}, 
+a copyleft license permitting redistribution} and feature murals which 
+makes it possible to relate points in the image pairs with a homography.  
+The images have been cropped to feature the same motive and resized to 
+$900$px by $600$px. This dataset will be referred to as the 
+\emph{Murals} dataset in this paper. The images can be seen in figure 
+\ref{fig:murals}.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/murals}
+	\caption{Images in the mural test set}
+	\label{fig:murals}
+\end{figure*}
+
+%However in practice the view point change has gone on to be used the 
+%most for later tests given that most of the other test pairs have since 
+%become easy to match\footnote{see \cite{wu2011robust} or 
+%\cite{delponte2006svd} for examples}.
+
 %Inspired by the graffiti image we have collected a set of image pairs 
@@
 %like they could match but in fact don't.
-%
-To increase the amount of images that feature view port changes we have 
-collected a set of $8$ image pairs featuring murals from different 
-angles.  From these pairs we can create test suites by cropping out 
-$250$ pixel by $250$ pixel patches of the original pair with a random 
-vertical and horizontal offset. Given a source image pair we can obtain 
-$n$ pairs of patches where the two patches in any pair might or might 
-not overlap.  This ensures that the patch pairs whith no overlap still 
-retain a basic similarity to each other, while the patches that do 
-overlap often only overlap on a small part of their surface. This 
-dataset will from here on be referred to as the \emph{Murals} dataset.  
-Figure \ref{fig:fairey} shows an example of possible pairs of test 
-images produced from two source images to the left.  Producing $n$ such 
-pairs allows us to test not just how well the matching algorithm 
-performs on corresponding images, but also how many false positives we 
-get on similar images that don't overlap.\footnote{The set of source 
-	images and homographies as well as the script to generate the 
-cropped test sets based on them have been made available online together 
-with the exact test sets used in this paper on 
-\href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.
-%
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=\textwidth]{images/murals}
-%	\caption{Images in the mural test set}
-%	\label{fig:mural}
-%\end{figure*}
+
 %
@@
 	\makebox[0.5\textwidth][c]{%
-		\begin{subfigure}[t]{0.044\textwidth}
+		\begin{subfigure}[t]{0.048\textwidth}
 			\centering
@@
 		\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, (or a 
-		%blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.044\textwidth}
+		\enspace %add desired spacing between images, e. g. ~, \quad, 
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.048\textwidth}
 			\centering
@@
 		\end{subfigure}%
-		~ %
-		\begin{subfigure}[t]{0.37\textwidth}
+		\enspace %
+		\begin{subfigure}[t]{0.36\textwidth}
 			\centering
@@
 %\subsection{Experimental setup}
-%
-Using the image test sets described above, the \emph{MM} and \emph{MMC} 
-algorithms have been tested against \emph{SIFT}, the algorithm Lowe 
-proposed in \cite{lowe2004sift} as well as the \emph{Isodata} matching 
-algorithm proposed in \cite{das2008event} which uses geometric 
-information to improve the matching. For each test set of cropped image 
-pairs the four algorithms\footnote{\emph{MM}, \emph{MMC}, \emph{SIFT} 
-and \emph{Isodata}} are applied to each pair of images ($100$ per test 
-set), and the threshold for each algorithm is varied over 50 evenly 
-spaced values. For each match returned by any of the algorithms, the 
-match is registered as an inlier if given $H$ relating $I_1$ with $I_2$ 
-and a match ($p_1, p_2$) the match is an inlier if $\left\vert Hp_1 - 
-p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < 5$. The 
-experiments are run on the $8$ image pairs in the test set, as well as 
-the graf image from \cite{mikolajczyk2005performance}.
+The \emph{MM} and \emph{MMC} algorithms have been tested against 
+\emph{SIFT}, the algorithm Lowe proposed in \cite{lowe2004sift} as well 
+as the \emph{Isodata} matching algorithm proposed in \cite{das2008event} 
+which uses geometric information to improve the matching. The comparison 
+has been done using the \emph{Murals} dataset, the \emph{Graf} set from 
+\cite{mikolajczyk2005performance} and two images\footnote{100\_1942.jpg 
+and 100\_1941.jpg} from \cite{gallagher2008} illustrated in figure 
+\ref{fig:pitts_partition}.
+
+Test sets have been generated from the image pairs by cropping out 
+$250$px by $250$px patches with a random vertical and horizontal offset.  
+Given a source image pair we produce $100$ pairs of patches where the 
+two patches in any pair might or might not overlap.  This ensures that 
+the patch pairs with no overlap still retain a basic similarity to each 
+other, while the patches that do overlap often only overlap on a small 
+part of their surface. Figure \ref{fig:fairey} shows an example of 
+possible pairs of test images produced from a source image pair.  
+Producing $n$ such pairs allows us to test not just how well the 
+matching algorithm performs on a variety of overlap but also how many 
+false positives we get on similar images that don't overlap at 
+all\footnote{The set of source images and homographies as well as the 
+	script to generate the cropped test sets based on them have been 
+made available online together with the exact test sets used in this 
+paper on 
+\href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.
+
+To judge whether a possible match ($p_1, p_2$) should be counted as an 
+inlier given a homography $H$ relating two images $I_1$ and $I_2$ we 
+test if $p_1$ and $p_2$ satisfies the following criterium:
+
+$$\left\vert Hp_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 
+\right\vert < 5$$
 %
@@
 \label{results}
-%
-%\begin{figure}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/fairey_burma_1}
-%			\caption{Burma by Fairey (1)}
-%			\label{fig:burma1}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/fairey_burma_2}
-%			\caption{Burma by Fairey (2)}
-%			\label{fig:burma2}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/result_fairey_burma}
-%			\caption{X: Nb of correct matches. Y: accuracy}
-%			\label{fig:result_burma}
-%		\end{subfigure}%
-%	}%
-%	\label{fig:burma}
-%	\caption{results on Burma by Fairey}
-%\end{figure}
-%
-%\begin{figure}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.25\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/fairey_lady_1}
-%			\caption{Lady by Fairey (1)}
-%			\label{fig:lady1}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.25\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/fairey_lady_2}
-%			\caption{Lady by Fairey (2)}
-%			\label{fig:lady2}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.55\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/result_fairey_lady}
-%			\caption{X: Nb of correct matches. Y: accuracy}
-%			\label{fig:result_lady}
-%		\end{subfigure}%
-%	}%
-%	\label{fig:lady}
-%	\caption{results on Lady by Fairey}
-%\end{figure}
-%
-%
+
 \begin{figure}
@@
 			\includegraphics[width=\textwidth]{images/graf}
-			\caption{Graf \cite{mikolajczyk2005performance}}
-			\label{fig:result_graf}
 		\end{subfigure}%
@@
 	}%
+	\label{fig:results_graf}
+	\caption{Accuracy on the \emph{Graf} set from 
+		\cite{mikolajczyk2005performance} using img1 and img3. The plot 
+	shows the result of $100$ image pairs generated from the source 
+images shown to the left. The number of matches is the total number of 
+matches for all $100$ image pairs.}
+\end{figure}
 
-	\makebox[0.5\textwidth][c]{%
-		\begin{subfigure}[t]{.15\textwidth}
+\begin{figure}
 	\centering
-			\includegraphics[width=\textwidth]{images/scharf}
-			\caption{Faces (Scharf)}
-			\label{fig:result_faces}
-		\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/result_scharf}
-			%\caption{Performance on Scharf}
-		\end{subfigure}%
-	}%
+	\includegraphics[width=0.45\textwidth]{images/result_accumulated}
+	\caption{Results on the \emph{Murals} dataset and the pair of img1 
+		and img3 from the \emph{Graf} image set from 	
+		\cite{mikolajczyk2005performance}. For each of the 9 source 
+		image pairs, 100 test pairs have been created.  The x-axis 
+	illustrates the accumulated returned matches for all pairs.}
+	\label{fig:result_accumulated}
+\end{figure}
 
-	\makebox[0.5\textwidth][c]{%
-		\begin{subfigure}[t]{.15\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pitts}
-			\caption{Pittsburg \cite{gallagher2008}}
-			\label{fig:result_pitts}
-		\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-		\end{subfigure}%
-	}%
-	\label{fig:accuracy}
-	\caption{Accuracy Examples: Each plot pictures the result of $100$ 
-	image pairs generated from the source images shown to the left.  The 
-number of matches is the total number of matches for all $100$ image 
-pairs.}
-\end{figure}
-%
 \begin{figure}
@@
 	\includegraphics[width=0.45\textwidth]{images/result_viewport}
-	\caption{Results on viewport changes. S is image 1 and 2 of the 
-	graffiti set in\cite{mikolajczyk2005performance}. M is 1 and 3, L is 
-1 and 4 while XL is 1 and 5. \emph{MMC} is represented by a solid line 
-while \emph{SIFT} results are shown by a dashed line.}
+	\caption{Results on viewport changes using the \emph{Graf} set from 
+		\cite{mikolajczyk2005performance} as image pair sources. S is a 
+		testst of $100$ crops from img1 and img2. M is likewise but 
+	based on img1 and img3.  L is img1 and img4 and XL is img1 and img5.  
+To decrease clutter \emph{MM} is not shown, but it performs alike to 
+\emph{MMC}}
 	\label{fig:result_viewport}
 \end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_accumulated}
-	\caption{Results on the mural dataset. For each of the 8 source 
-		image pairs, 100 test pairs have been created. The x-axis 
-		illustrates the accumulated returned matches for all pairs.
-		changes.}
-	\label{fig:result_accumulated}
-\end{figure}
-%\begin{figure}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/houston_1}
-%			\caption{Houston (1)}
-%			\label{fig:houston1}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/houston_2}
-%			\caption{Houston (2)}
-%			\label{fig:houston2}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/result_houston}
-%			\caption{X: Nb of correct matches. Y: accuracy}
-%			\label{fig:result_houston}
-%		\end{subfigure}%
-%	}%
-%	\label{fig:houston}
-%	\caption{Results on Houston}
-%\end{figure}
-%
-%\begin{figure}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.25\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/blu_head_1}
-%			\caption{head by blu (1)}
-%			\label{fig:head1}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.25\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/blu_head_2}
-%			\caption{head by blu (2)}
-%			\label{fig:head2}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.55\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/result_blu_head}
-%			\caption{X: Nb of correct matches. Y: accuracy}
-%			\label{fig:result_head}
-%		\end{subfigure}%
-%	}%
-%	\label{fig:head}
-%	\caption{results on head by blu}
-%\end{figure}
-%
-%\begin{figure}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.25\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/blu_pencil_1}
-%			\caption{Pencil by Blu (1)}
-%			\label{fig:pencil1}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.25\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/blu_pencil_2}
-%			\caption{Pencil by Blu (2)}
-%			\label{fig:pencil2}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.55\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/result_blu_pencil}
-%			\caption{X: Nb of correct matches. Y: accuracy}
-%			\label{fig:result_pencil}
-%		\end{subfigure}%
-%	}%
-%	\label{fig:pencil}
-%	\caption{Results on Pencil by Blu}
-%\end{figure}
-%
-%\begin{figure}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/banksy_city_1}
-%			\caption{City by Banksy (1)}
-%			\label{fig:city1}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/banksy_city_2}
-%			\caption{City by Banksy (2)}
-%			\label{fig:city2}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/result_banksy_city}
-%			\caption{X: Nb of correct matches. Y: accuracy}
-%			\label{fig:result_city}
-%		\end{subfigure}%
-%	}%
-%	\label{fig:city}
-%	\caption{results on City}
-%\end{figure}
-%
-%\begin{figure}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/banksy_stroller_1}
-%			\caption{Stroller by Banksy (1)}
-%			\label{fig:stroller1}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/banksy_stroller_2}
-%			\caption{Stroller by Banksy (2)}
-%			\label{fig:stroller2}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/result_banksy_stroller}
-%			\caption{X: Nb of correct matches. Y: accuracy}
-%			\label{fig:result_stroller}
-%		\end{subfigure}%
-%	}%
-%	\label{fig:stroller}
-%	\caption{Results on Stroller by Banksy}
-%\end{figure}
-%
-%
-%\begin{figure}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf_1}
-%			\caption{Graf (1)}
-%			\label{fig:graf1}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf_3}
-%			\caption{Graf (3)}
-%			\label{fig:graf3}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.35\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/result_graf}
-%			\caption{X: Nb of correct matches. Y: accuracy}
-%			\label{fig:result_graf}
-%		\end{subfigure}%
-%	}%
-%	\label{fig:graf}
-%	\caption{results on Graf}
-%\end{figure}
-%
+
 Figure \ref{fig:result_accumulated} shows the accumulated results on the 
@@
 shows the results on potentially overlapping image pairs generated from 
-a typical holiday scene with partial overlap and slight view port 
+a typical holiday scene with partial overlap and slight viewport 
 change. As can be seen in figure \ref{fig:result_viewport}, \emph{MMC} 
@@
 %
+
+\begin{figure}
+	\makebox[0.5\textwidth][c]{%
+		\begin{subfigure}[t]{.15\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pitts}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{.27\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/result_pitts}
+			%\caption{Performance on Scharf}
+		\end{subfigure}%
+	}%
+	\label{fig:results_pitts}
+	\caption{Accuracy on an image pair from the Gallagher dataset from 
+		\cite{gallagher2008} using cropped versions of 100\_1941 and 
+		100\_1942. The plot shows the result of $100$ image pairs 
+		generated from the source images shown to the left.  The number 
+	of matches is the total number of matches for all $100$ image 
+pairs.}
+\end{figure}
+
 \section{Summary}

### 2013-06-06 code/display.py

@@ -289,19 +289,19 @@ def accuDetail(correct, total, legend, ylim = 100, treshold=1000) :
 	accuHist(accu, legend, ylim=ylim)
 
 
-def accuPlot(correct, total, legends, ylim=(0.0,1.01), xlim = None, size = (4,6), compareCorrect = None, compareTotal = None, compareLabel = None, outside = False) :
+def accuPlot(correct, total, legends, colors = ["blue", "red", "green", "orange", "cyan"], ylim=(0.0,1.01), xlim = None, size = (4,6), compareCorrect = None, compareTotal = None, compareLegend = None, outside = False) :
 	fig = pylab.figure(figsize=size)
 	ax = pylab.subplot(111)
-	for ts,cs,l,color in zip(total, correct, legends, ["blue", "cyan", "green", "orange", "red"]) :
+	for ts,cs,l,color in zip(total, correct, legends, colors) :
 		xs = [sum(t) for t in ts]
 		ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for (c, t) in zip(cs, ts)]
-		pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.75)
+		pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.95)
 		pylab.legend(loc="best")
-	if compareCorrect != None and compareTotal != None and compareLabel != None :
+	if compareCorrect != None and compareTotal != None and compareLegend != None :
 		for ts,cs,l,color in zip(compareTotal, compareCorrect, legends, ["blue", "cyan", "green", "orange", "red"]) :
 			xs = [sum(t) for t in ts]
 			ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for (c, t) in zip(cs, ts)]
-			pylab.plot(xs, ys, '--', label="%s - %s" % (l, compareLabel), color=color, alpha=0.95)
+			pylab.plot(xs, ys, '--', label="%s" % (compareLegend), color=color, alpha=1)
 			pylab.legend(loc="best")
 	removeDecoration()
 	pylab.xlabel("# of Matches")

### 2013-06-06 text/clustering.tex
Version 2.3

@@
 
-Figure \ref{fig:result_accumulated} shows the accumulated results on the 
-\emph{Murals} dataset. It shows that \emph{MMC} and \emph{MM} is overall 
-superior to both \emph{SIFT} and \emph{Isodata} which uses geometric 
-constraints when tested on image pairs with no assurance of overlap 
-depicting simple planar scenes. Figure \ref{fig:result_faces} 
-illustrates the result on a particular image pair from the \emph{Murals} 
-dataset. For an example of a real life use case \ref{fig:result_pitts} 
-shows the results on potentially overlapping image pairs generated from 
-a typical holiday scene with partial overlap and slight viewport 
-change. As can be seen in figure \ref{fig:result_viewport}, \emph{MMC} 
-consistently outperforms \emph{SIFT} across different magnitudes of the 
-viewport change. For the results on image 1 and 3 from the \emph{Graf} 
-dataset, see figure \ref{fig:result_graf}.
-Generally all plots show good results by \emph{Isodata} when only the 
-best matches are returned, but when the thresholds are more lenient the 
-quality of the returned matches degrades quickly and \emph{MMC} and 
-\emph{MM} yield better results.
+Figure \ref{fig:result_graf} shows the results for 100 image pairs 
+generated from img1 and img3 of the \emph{Graf} image set. The plot 
+illustrates how \emph{Isodata} performs well to begin with, but as we 
+permit more matches \emph{MM} and \emph{MMC} show superior results. To 
+generalize this result, figure \ref{fig:result_accumulated} displays the 
+accumulated result over the \emph{Murals} dataset as well as the 
+\emph{Graf} pair tested in fig. \ref{fig:result_graf}. In total 900 
+image pairs were generated from 9 source pairs. This plot confirms the 
+accuracy of \emph{MMC} and \emph{MM} over a bigger data set. As can be 
+seen in figure \ref{fig:result_viewport}, the results of \emph{MMC} are 
+general across different magnitudes of the viewport change.
+
+For an example of a real life use case \ref{fig:result_pitts} shows the 
+results on potentially overlapping image pairs generated from a typical 
+holiday scene with partial overlap and slight viewport change.
 
@@
 computationally intensive operations in C++ which renders it much 
-faster.
+faster. While \emph{SIFT}, \emph{MM} and \emph{Isodata} can be 
+implemented in $O(nlogn)$ where $n$ is the total amount of feature 
+points, \emph{MMC} currently has a complexity of $O(n^2)$ due to the 
+construction of a similarity matrix of the feature points. It is however 
+possible to approximate this in $O(nlogn)$, something that might be 
+pursued in future work.
 %

### 2013-06-07 text/clustering.tex
V. 2.4.

@@
 	\makebox[0.7\textwidth][c]{%
-		\begin{subfigure}[t]{0.35\textwidth}
+		\begin{subfigure}[t]{0.28\textwidth}
 			\centering
@@
 		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.3\textwidth}
+		\begin{subfigure}[t]{0.28\textwidth}
 			\centering
@@
 partitions contain only two feature points from different images linked 
-by one edge. In this case we compare the ratio of this match to the next 
-best match across all partitions.
+by one edge. In this case we compare the similarity of this match to the 
+next best match across all partitions and filter the matches based on 
+this ratio like in \emph{SIFT}.
 %\begin{algorithm}
@@
 	}%
-	\label{fig:results_graf}
 	\caption{Accuracy on the \emph{Graf} set from 
@@
 		shows the result of $100$ image pairs generated from the source 
-images shown to the left. The number of matches is the total number of 
-matches for all $100$ image pairs.}
+		images shown to the left. The number of matches is the total 
+		number of matches for all $100$ image pairs.}
+	\label{fig:result_graf}
 \end{figure}
@@
 	\caption{Results on viewport changes using the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance} as image pair sources. S is a 
-		testst of $100$ crops from img1 and img2. M is likewise but 
-	based on img1 and img3.  L is img1 and img4 and XL is img1 and img5.  
-To decrease clutter \emph{MM} is not shown, but it performs alike to 
-\emph{MMC}}
+		\cite{mikolajczyk2005performance} as image pair sources. Img 1 
+		to 6 in the \emph{Graph} set are images of the same subject but 
+		with gradually increasing view port change. Img1 and 2 are 
+		almost identical while img1 and 6 are taken from very different 
+		angles. S is a testst of $100$ crops from img1 and img2. M is 
+	likewise but based on img1 and img3.  L is img1 and img4 and XL is 
+img1 and img5.  To decrease clutter \emph{MM} is not shown, but it 
+performs alike to \emph{MMC}}
 	\label{fig:result_viewport}
@@
 generated from img1 and img3 of the \emph{Graf} image set. The plot 
-illustrates how \emph{Isodata} performs well to begin with, but as we 
-permit more matches \emph{MM} and \emph{MMC} show superior results. To 
-generalize this result, figure \ref{fig:result_accumulated} displays the 
-accumulated result over the \emph{Murals} dataset as well as the 
-\emph{Graf} pair tested in fig. \ref{fig:result_graf}. In total 900 
-image pairs were generated from 9 source pairs. This plot confirms the 
-accuracy of \emph{MMC} and \emph{MM} over a bigger data set. As can be 
-seen in figure \ref{fig:result_viewport}, the results of \emph{MMC} are 
-general across different magnitudes of the viewport change.
+illustrates the results of \emph{SIFT}, \emph{MM}, \emph{MMC} and 
+\emph{Isodata} as thresholds are varied over a range. \emph{Isodata} 
+performs well with strict thresholds, but when we require more matches 
+\emph{MM} and \emph{MMC} show superior results. To see if this results 
+generalizes over more image sets, we tested the four algorithms on the 
+\emph{Murals} dataset as well as the \emph{Graf} pair tested in fig.  
+\ref{fig:result_graf}. In total 900 image pairs were generated from 9 
+source pairs generating the plot shown in figure 
+\ref{fig:result_accumulated} displaying the accumulated amount of 
+matches on the x-axis. To verify that this performance is independent of 
+the magnitude of view port change, we tested \emph{MMC} and \emph{SIFT} 
+on the \emph{Graf} image set as shown in figure 
+\ref{fig:result_viewport}. The figure confirms that \emph{MMC} is 
+generally superior across view port changes.
 
-For an example of a real life use case \ref{fig:result_pitts} shows the 
-results on potentially overlapping image pairs generated from a typical 
-holiday scene with partial overlap and slight viewport change.
+For an example of a real life use case figure \ref{fig:result_pitts} 
+shows the results on potentially overlapping image pairs generated from 
+a typical holiday scene with partial overlap and slight view port 
+change.
 
@@
 construction of a similarity matrix of the feature points. It is however 
-possible to approximate this in $O(nlogn)$, something that might be 
-pursued in future work.
+possible to approximate this in $O(nlogn)$ using search trees, something 
+that could be pursued in future work.
 %
@@
 	}%
-	\label{fig:results_pitts}
 	\caption{Accuracy on an image pair from the Gallagher dataset from 
@@
 pairs.}
+	\label{fig:result_pitts}
 \end{figure}
@@
 life example from the Gallagher dataset and the \emph{Graf} image set, 
-beating even a method using geometrical constraints when matching image 
-pairs that might not overlap.
+surpassing even a method using geometrical constraints when matching 
+image pairs that might not overlap.
 %

### 2013-06-07 code/display.py

@@ -298,10 +298,10 @@ def accuPlot(correct, total, legends, colors = ["blue", "red", "green", "orange"
 		pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.95)
 		pylab.legend(loc="best")
 	if compareCorrect != None and compareTotal != None and compareLegend != None :
-		for ts,cs,l,color in zip(compareTotal, compareCorrect, legends, ["blue", "cyan", "green", "orange", "red"]) :
+		for ts,cs,l,color in zip(compareTotal, compareCorrect, compareLegend, ["blue", "red", "green", "orange", "red"]) :
 			xs = [sum(t) for t in ts]
 			ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for (c, t) in zip(cs, ts)]
-			pylab.plot(xs, ys, '--', label="%s" % (compareLegend), color=color, alpha=1)
+			pylab.plot(xs, ys, '--', label="%s" % (l), color=color, alpha=1)
 			pylab.legend(loc="best")
 	removeDecoration()
 	pylab.xlabel("# of Matches")

### 2013-06-07 text/clustering.tex
V 2.6

@@
-\documentclass[12pt,journal]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 %\documentclass{article}
 \usepackage{footnote}
-\usepackage[font={small}]{caption}
+%\usepackage[font={small}]{caption}
 \usepackage{sidecap}
@@
 particular few methods address the problem of reliable matching in cases 
-where we don't know if two images have any corresponding areas or 
+where we do not know if two images have any corresponding areas or 
 objects. In this paper we propose two algorithms for matching feature 
@@
 the images matched. These assumptions are then used to create 
-constraints used to evaluate the matches such as angular constraints 
+constraints on the matches such as angular constraints 
 \cite{kim2008efficient}, epipolar constraints \cite{torr2000mlesac}, 
@@
 \cite{wu2011robust}.
-%
+
 %proposes clustering feature points by using their geometric position 
@@
 %within this ellipse are then matched according to epipolar constraints.
-%
+
 In practice however, there are many situations where using the geometry 
 of the image to filter correspondences is not possible, such as object 
-recognition where adjecent objects in one photo might be separated in 
+recognition where adjacent objects in one photo might be separated in 
 another. Another example is images that do not overlap where algorithms 
 might still find matches adhering to the imposed geometric constraints.
-In addition methods using geometric constraints all require a set of 
-correspondences to begin with. If this set of correspondences is 
-narrowed down to a smaller set with a higher ratio of correct matches 
-the result of the geometric matching will be both faster and more 
-accurate.  Finally some use cases might require a performance that can't 
-be achieved by a more complex geometric method where simple non 
-geometric methods might be able to provide sufficient matching accuracy 
-with a smaller performance penalty.
+In addition methods using geometric constraints all require an initial 
+set of correspondences. If this set of correspondences is narrowed down 
+to a set with a higher ratio of correct matches the result of the 
+geometric matching will benefit in terms of speed and accuracy. Finally 
+some use cases might require a performance that can't be achieved by a 
+more complex geometric method where simple non geometric methods might 
+be able to provide sufficient matching accuracy with a smaller 
+performance penalty.
 
@@
 first image is better matched with other feature points from the 
-\emph{same} image than points in the other image, then any matches of 
+\emph{same} image than points in the other image, then any matches from 
 this feature point to points in the other image is deemed unreliable and 
@@
 %point is uniquely matched. The issue is particularly pronounced if we 
-%compare two images that don't correspond. For any proposed 
+%compare two images that do not correspond. For any proposed 
 %correspondence it is entirely probable that this correspondence is 
@@
 \ForAll{$f_i \in features$} \Comment Match Stage
-	\State $f_m,f_n \gets get2NNs(f_i, features ~ \backslash ~ 
+	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
 	\left\{f_i\right\})$
@@
 			\centering
-			\includegraphics[width=\textwidth]{images/mirror_match}
-			\caption{\emph{MM}}
-			\label{fig:without}
-		\end{subfigure}%
-		\enspace%
-		\begin{subfigure}[t]{0.32\textwidth}
-			\centering
 			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
@@
 		%\qquad (or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.32\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/mirror_match}
+			\caption{\emph{MM}}
+			\label{fig:without}
+		\end{subfigure}%
+		\enspace%
 		\begin{subfigure}[t]{0.32\textwidth}
@@
 
-In figure \ref{fig:comparemirror} an example of the result of \emph{MM} 
-is illustrated. Notice how the by the bottom of the image admits 
-correspondences that can conveniently be removed as done in sub figure 
-\ref{fig:without} where only the actual correspondences returned by the 
-algorithm are shown.
+In figure \ref{fig:within} and \ref{fig:without} an example of the 
+result of \emph{MM} is illustrated. In figure \ref{fig:unique} many of 
+the incorrect matches occur in the fence in the bottom of the image.  
+When we match all feature points together many of these incorrect 
+matches are eliminated because points in the fence match with other 
+points in the fence in the same image as shown in figure 
+\ref{fig:within} and \ref{fig:without}.
 
@@
 %in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-%new algorithms differ from K-means clustering and Spectral clustering in 
-%that they don't require the number of expected to clusters to be 
+%new algorithms differ from K-means clustering and Spectral clustering 
+%in that they do not require the number of expected to clusters to be 
 %specified beforehand\footnote{Among the aforementioned methods, this is 
@@
 %maintaining clusters of an even size usually means that some clusters 
-%will be '\emph{catch-all}' clusters where the feature points that don't 
-%fit anywhere else are grouped together. The necessity of specifying the 
-%amount of partitions in for example Spectral clustering or Pott's model 
-%clustering further exacerbates the issue since smaller partitions are 
-%then combined into one to achieve the right amount of partitions.
+%will be '\emph{catch-all}' clusters where the feature points that do 
+%not fit anywhere else are grouped together. The necessity of specifying 
+%the amount of partitions in for example Spectral clustering or Pott's 
+%model clustering further exacerbates the issue since smaller partitions 
+%are then combined into one to achieve the right amount of partitions.
 
@@
 is well clustered, the adjacency matrix is pruned so only edges above a 
-certain threshold is kept. From empirical analysis keeping around 2.5\% 
-of edges seems to work well. Figure \ref{fig:graph} shows the result of 
-clustering the feature points displayed as a graph.
+certain threshold is kept. From empirical analysis keeping the 2.5\% of 
+edges with the highest similarity seems to work well in practice. Figure 
+\ref{fig:graph} shows the result of clustering the feature points 
+displayed as a graph.
 %
@@
 	\makebox[0.7\textwidth][c]{%
-		\begin{subfigure}[t]{0.28\textwidth}
+		\begin{subfigure}[t]{0.35\textwidth}
 			\centering
@@
 		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.28\textwidth}
+		\begin{subfigure}[t]{0.32\textwidth}
 			\centering
@@
 
-The matching for \emph{MMC} \emph{getMatches} finds matches within all 
-partitions with more than two elements as done in \emph{MM}. However as 
-can be seen in the example in figure \ref{fig:cropped_graph} many of the 
-partitions contain only two feature points from different images linked 
-by one edge. In this case we compare the similarity of this match to the 
-next best match across all partitions and filter the matches based on 
-this ratio like in \emph{SIFT}.
+The matching algorithm for \emph{MMC}, \emph{getMatches}, finds matches 
+within all partitions with more than two elements as done in \emph{MM}.  
+However as can be seen in the example in figure \ref{fig:cropped_graph} 
+many of the partitions contain only two feature points from different 
+images linked by one edge. In the case of such a pair we compare the 
+similarity of the these two feature points with their second best match 
+and filters matches where this ratio falls over a certain threshold like 
+in the \emph{SIFT} algorithm.
+
 %\begin{algorithm}
@@
 %\label{alg-getmatches}
+%{\fontsize{10}{10}\selectfont
 %\begin{algorithmic}
@@
 %\State $matches \gets \varnothing$
-%\State $edges \gets \left\{getSimilarity(f_i, f_j) \mid getImg(f_i) \neq 
-%getImg(f_j) \wedge f_i, f_j \in p \right\}$
+%\State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i) \neq 
+%	getImg(f_j)$
+%\State $\wedge f_i, f_j \in p \right\}$
 %\If{$\left\vert edges \right\vert = 1$} \Comment If $\exists$ one edge 
 %between images
-%	\State $f_i,f_j \gets getInterImageFeatures(edges_{inter}, p)$
-%	\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, features ~ 
-%\backslash ~ \left\{f_i\right\})$
-%	\State $f_s,f_t \gets getTwoNearestNeighbors(f_j, features ~ 
-%\backslash ~ \left\{f_j\right\})$
-%	\State $ratio_i \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
+%	\State $f_i,f_j \gets getFeatures(edges_{inter}, p)$
+%	\State $f_m,f_n \gets get2NNs(f_i, features ~ 
+%\setminus ~ \left\{f_i\right\})$
+%	\State $f_s,f_t \gets get2NNs(f_j, features ~ 
+%\setminus ~ \left\{f_j\right\})$
+%	\State $ratio_i \gets similarity(f_i, f_n) / similarity(f_i, 
 %f_j)$
-%	\State $ratio_j \gets getSimilarity(f_j, f_t) / getSimilarity(f_j, 
+%	\State $ratio_j \gets similarity(f_j, f_t) / similarity(f_j, 
 %f_i)$
@@
 %	\ForAll{$f_i \in p$}
-%		\State $f_m,f_n \gets getTwoNearestNeighbors(f_i, p ~ \backslash 
-%~ \left\{f_i\right\})$
-%		\State $ratio \gets getSimilarity(f_i, f_n) / getSimilarity(f_i, 
+%		\State $f_m,f_n \gets get2NNs(f_i, p \setminus 
+%\left\{f_i\right\})$
+%		\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, 
 %f_m)$
@@
 %\end{algorithmic}
+%}
 %\end{algorithm}
-%
+
 \section{Experiments}
@@
 the need for more image pairs featuring viewport changes, we have 
-compiled a set of $8$ image pairs consisting of the same subject taken 
-from two different angles. The images are collected from Flickr's 
-database of images published under a creative commons 
+compiled a set of $8$ image pairs consisting of subjects taken from two 
+different angles. The images are collected from Flickr's database of 
+images published under a creative commons 
 licence\footnote{\href{http://creativecommons.org/}{www.creativecommons.org}, 
@@
 %algorithms proposed are reliable we need to test that we get good 
-%matches when images overlap and that we get no matches when they don't.  
-%This means that it isn't enough just testing against pairs of images 
-%that we know match.  We also need to test against pairs that might look 
-%like they could match but in fact don't.
+%matches when images overlap and that we get no matches when they do 
+%not.  This means that it isn't enough just testing against pairs of 
+%images that we know match.  We also need to test against pairs that 
+%might look like they could match but in fact do not.
 
@@
 and 100\_1941.jpg} from \cite{gallagher2008} illustrated in figure 
-\ref{fig:pitts_partition}.
+\ref{fig:comparemirror}.
 
@@
 matching algorithm performs on a variety of overlap but also how many 
-false positives we get on similar images that don't overlap at 
+false positives we get on similar images that do not overlap at 
 all\footnote{The set of source images and homographies as well as the 
@@
 \href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.  
+In practice the amount of overlap between pairs in a test set will 
+depend on the overlap and viewport change of the source image pair.  To 
+give a rough impression of a typical example, table \ref{table:overlap} 
+shows the overlap of image pairs created from img1 and img3 of the 
+\emph{Graf} image set from \cite{mikolajczyk2005performance}.
 
-To judge whether a possible match ($p_1, p_2$) should be counted as an 
-inlier given a homography $H$ relating two images $I_1$ and $I_2$ we 
-test if $p_1$ and $p_2$ satisfies the following criterium:
-
+Given a potential match between two images $I_1$ and $I_2$, $m = 
+\left(p_1, p_2\right)$ and a homography $H$ relating $I_1$ to $I_2$, we 
+can calculate if $m$ is an inlier by check if the positions $p_1$ and 
+$p_2$ satisfies the following criteria:
 $$\left\vert Hp_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 
 \right\vert < 5$$
+That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
+\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
+less than five pixels.
+
+\begin{table}
+	\centering
+	\small
+\begin{tabular}{l*{3}{r}}
+	Overlap: & 0\% & $< 50$\% & $> 50$\%  \\
+	\noalign{\smallskip}
 	%
+	Percent of image pairs: & 21\% & 54\% & 25\% \\
+\end{tabular}
+\caption{Overlap on the testset of 100 image pairs created from img1 and 
+img3 of the \emph{Graf} image set. 21 images had no overlap}
+\label{table:overlap}
+\end{table}
 \section{Results}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_accumulated}
+	\includegraphics[width=0.5\textwidth]{images/result_accumulated}
 	\caption{Results on the \emph{Murals} dataset and the pair of img1 
@@
 		to 6 in the \emph{Graph} set are images of the same subject but 
-		with gradually increasing view port change. Img1 and 2 are 
+		with gradually increasing viewport change. Img1 and 2 are 
 		almost identical while img1 and 6 are taken from very different 
-		angles. S is a testst of $100$ crops from img1 and img2. M is 
+		angles. S is a testset of $100$ crops from img1 and img2. M is 
 	likewise but based on img1 and img3.  L is img1 and img4 and XL is 
@@
 matches on the x-axis. To verify that this performance is independent of 
-the magnitude of view port change, we tested \emph{MMC} and \emph{SIFT} 
+the magnitude of viewport change, we tested \emph{MMC} and \emph{SIFT} 
 on the \emph{Graf} image set as shown in figure 
 \ref{fig:result_viewport}. The figure confirms that \emph{MMC} is 
-generally superior across view port changes.
+generally superior across viewport changes.
 
-For an example of a real life use case figure \ref{fig:result_pitts} 
-shows the results on potentially overlapping image pairs generated from 
-a typical holiday scene with partial overlap and slight view port 
+For an example of a real life use case, figure \ref{fig:result_pitts} 
+shows the results on 100 potentially overlapping image pairs generated 
+from a typical holiday scene featuring occlusion and a slight viewport 
 change.
@@
 %
-\begin{savenotes}
 \begin{table}
@@
 \end{table}
-\end{savenotes}
 %

### 2013-07-03 text/clustering.tex
Commited a lot of minor changes

@@
 \usepackage{hyperref}
-\usepackage[stable]{footmisc}
+%\usepackage[stable]{footmisc}
 \usepackage{caption}
@@
 algorithms experimentally we introduce a set of 8 image pairs all 
-containing viewport changes and a simple method to generate a large 
+containing viewpoint changes and a simple method to generate a large 
 amount of test cases based on these 8 pairs. The experimental results 
@@
 another. This allows for the filtering of all correspondences that do 
-not fall within paired areas. Examples include \cite{das2008event} and 
-\cite{wu2011robust}.
+not fall within paired areas. Examples include \cite{das2008event} which 
+clusters the feature points according to their position in the image
+and \cite{wu2011robust} which uses points returned by MSER feature 
+points to designate areas. In this paper the algorithm from  
+\cite{das2008event} will later be referred to as \emph{Isodata}.
 
@@
 
-In practice however, there are many situations where using the geometry 
-of the image to filter correspondences is not possible, such as object 
+In practice there are many situations where using the geometry of the 
+image to filter correspondences is not possible, such as object 
 recognition where adjacent objects in one photo might be separated in 
@@
 
-There are a relatively small number of algorithms proposed to solve the 
-matching problem without involving geometric constraints. Traditionally 
-the feature points of two images have been matched by comparing every 
-feature point of one image with all feature points of the other and 
-finding the best matches based on the similarity of the descriptors.  
-With the introduction of the SIFT features \cite{lowe2004sift}, Lowe 
-proposes an alternative measure where the uniqueness of a given match is 
-found by looking at the two nearest neighbors of each feature point and 
+Without using geometric constraints we are left with a few methods to 
+match feature points. As pointed out in \cite{szeliski2010} the simplest 
+approach to matching feature point is to return all matches within a 
+threshold of similarity.  This can be done with a fixed threshold or by 
+finding the nearest neighbors for each point, still filtering by a 
+threshold to avoid including matches for feature points that have no 
+counterpart in the other image.  In \cite{lowe2004sift}, Lowe proposes 
+an alternative measure where the uniqueness of a given match is found by 
+looking at the two nearest neighbors of each feature point and 
 calculating a match score by the ratio of similarities.  Ranking the 
@@
 correspondences that are distinctly matched across the two images. This 
-method will be referred to as \emph{SIFT} in this paper.
+method will be referred to as \emph{SIFT} in this paper. Of these three 
+methods\footnote{fixed threshold, nearest neighbors and \emph{SIFT}}, 
+\emph{SIFT} was found to perform best by a slight margin in a study in 
+\cite{mikolajczyk2005performance}.
 
@@
 
-%Based on this idea the two proposed methods find reliable matches as 
-%follows:
-%\begin{itemize}
-%\item[]{\emph{Mirror Match (MM)}: Match features using the gold standard 
-%		algorithm\cite[p. 114]{multipleView} ranked by similarity and 
-%		thresheld by uniqueness\cite{lowe2004sift}.  However instead of 
-%		matching features from one image with features in another, we 
-%	match every feature with all other features of the two images 
-%combined. Only matches from one image to the other are returned.}
-%\item[]{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
-%		of feature points from both images and cluster these points 
-%		according to their descriptors. Given a resulting partition of 
-%		points, no matches are returned if it contains only feature 
-%	points from one image. If the partition contains points from both 
-%images, \emph{Mirror Match} is used to find the best matches within the 
-%partition.}
-%\end{itemize}
-%%
+Based on this idea the two proposed methods find reliable matches as 
+follows. In \emph{Mirror Match (MM)} we match every feature from both 
+images with all other features and filter matches based on the ratio of 
+best to second best match as in \emph{SIFT}. In \emph{Mirror Match with 
+Clustering (MMC)} on the other hand we take the combined set of feature 
+points from both images and cluster these points according to their 
+descriptors.  Given a resulting partition of points, no matches are 
+returned if it contains only feature points from one image.  If the 
+partition contains points from both images, \emph{Mirror Match} is used 
+to find the best matches within the partition.
+
 %Matching feature points against the entire set of points from both 
@@
 	}%
-	\caption{Illustration of matches filtered by \emph{MM}. For each 
-	correct match found between the two images, a green line is shown.  
-Incorrect matches are marked with a red line. Figure \ref{fig:within} 
-shows the correspondences found by mirror match, but including all 
-matches that are found within the same image. }%
+	\caption{Illustration of matches filtered by \emph{MM}. a) is the 
+		source image pair. b) displays the feature points found in the 
+		two images. c) shows the result of \emph{SIFT} matching the two 
+		images. For each correct match found between the two images, a 
+		green line is shown.  Incorrect matches are marked with a red 
+		line. d) depicts all matches found by \emph{MM} including 
+	matches between points in the same image. e) shows the result from 
+d) but with the intra-image matches removed. f) shows an example of a 
+partition of feature points from the \emph{MMC} algorithm.}%
 	\label{fig:comparemirror}%
@@
 %
-\begin{SCfigure*}
-	\makebox[0.7\textwidth][c]{%
-		\begin{subfigure}[t]{0.35\textwidth}
+\begin{figure}
 	\centering
+	\begin{subfigure}[t]{0.45\textwidth}
 		\includegraphics[width=\textwidth]{images/MMC_graph_full}
@@
 	\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+
+	%add desired spacing between images, e. g. ~, \quad, \qquad		  
 	%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.32\textwidth}
-			\centering
+	\begin{subfigure}[t]{0.36\textwidth}
 		\includegraphics[width=\textwidth]{images/MMC_graph_cropped}
@@
 	\end{subfigure}%
-	}%
 	\caption{The partitioned feature graph. Each vertex represents a 
@@
 	\label{fig:graph}
-\end{SCfigure*}
+\end{figure}
 
@@
 dataset\footnote{In particular by the 'Graf' image set} and motivated by 
-the need for more image pairs featuring viewport changes, we have 
+the need for more image pairs featuring viewpoint changes, we have 
 compiled a set of $8$ image pairs consisting of subjects taken from two 
@@
 \ref{fig:murals}.
+
+\begin{figure}
+	\makebox[0.5\textwidth][c]{%
+		\begin{subfigure}[t]{0.048\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pair_example1}
+			\label{fig:fairey1}
+		\end{subfigure}%
+		\enspace %add desired spacing between images, e. g. ~, \quad, 
+		%(or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{0.048\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pair_example2}
+			\label{fig:fairey2}
+		\end{subfigure}%
+		\enspace %
+		\begin{subfigure}[t]{0.36\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/crop_examples}
+		\end{subfigure}%
+	}%
+	\caption{Example of test set produced by a source pair of images}
+	\label{fig:fairey}
+\end{figure}
 
@@
 %
-\begin{figure}
-	\makebox[0.5\textwidth][c]{%
-		\begin{subfigure}[t]{0.048\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example1}
-			\label{fig:fairey1}
-		\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.048\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example2}
-			\label{fig:fairey2}
-		\end{subfigure}%
-		\enspace %
-		\begin{subfigure}[t]{0.36\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/crop_examples}
-		\end{subfigure}%
-	}%
-	\caption{Example of test set produced by a source pair of images}
-	\label{fig:fairey}
-\end{figure}
 %
 %\subsection{Experimental setup}
-The \emph{MM} and \emph{MMC} algorithms have been tested against 
+The \emph{MM} and \emph{MMC} algorithms have been compared to 
 \emph{SIFT}, the algorithm Lowe proposed in \cite{lowe2004sift} as well 
@@
 which uses geometric information to improve the matching. The comparison 
-has been done using the \emph{Murals} dataset, the \emph{Graf} set from 
-\cite{mikolajczyk2005performance} and two images\footnote{100\_1942.jpg 
-and 100\_1941.jpg} from \cite{gallagher2008} illustrated in figure 
-\ref{fig:comparemirror}.
+with \emph{SIFT} serves to illustrate the relative performance of 
+\emph{MM} and \emph{MMC} to a state of the art algorithm not using 
+geometric constraints. \emph{Isodata} is included in the comparison to 
+illustrate the performance of an algorithm relying on geometric 
+constraints faced with image pairs that have might not have any overlap.  
+The comparison has been done using the \emph{Murals} dataset, the 
+\emph{Graf} set from \cite{mikolajczyk2005performance} and two 
+images\footnote{100\_1942.jpg and 100\_1941.jpg} from 
+\cite{gallagher2008} illustrated in figure \ref{fig:comparemirror}.
 
@@
 all\footnote{The set of source images and homographies as well as the 
-	script to generate the cropped test sets based on them have been 
-	made available online together with the exact test sets used in this 
-paper on 
-\href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.  
+script to generate the cropped test sets based on them will be made 
+available online together with the exact test sets used in this paper 
+upon acceptance}
+%\href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.  
 In practice the amount of overlap between pairs in a test set will 
-depend on the overlap and viewport change of the source image pair.  To 
+depend on the overlap and viewpoint change of the source image pair.  To 
 give a rough impression of a typical example, table \ref{table:overlap} 
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewport}
-	\caption{Results on viewport changes using the \emph{Graf} set from 
+	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
+	\caption{Results on viewpoint changes using the \emph{Graf} set from 
 		\cite{mikolajczyk2005performance} as image pair sources. Img 1 
 		to 6 in the \emph{Graph} set are images of the same subject but 
-		with gradually increasing viewport change. Img1 and 2 are 
+		with gradually increasing viewpoint change. Img1 and 2 are 
 		almost identical while img1 and 6 are taken from very different 
@@
 performs alike to \emph{MMC}}
-	\label{fig:result_viewport}
+	\label{fig:result_viewpoint}
 \end{figure}
@@
 matches on the x-axis. To verify that this performance is independent of 
-the magnitude of viewport change, we tested \emph{MMC} and \emph{SIFT} 
+the magnitude of viewpoint change, we tested \emph{MMC} and \emph{SIFT} 
 on the \emph{Graf} image set as shown in figure 
-\ref{fig:result_viewport}. The figure confirms that \emph{MMC} is 
-generally superior across viewport changes.
+\ref{fig:result_viewpoint}. The figure confirms that \emph{MMC} is 
+generally superior across viewpoint changes.
 
@@
 shows the results on 100 potentially overlapping image pairs generated 
-from a typical holiday scene featuring occlusion and a slight viewport 
+from a typical holiday scene featuring occlusion and a slight viewpoint 
 change.
@@
 considered good matches and \emph{MMC} further improves on this idea by 
-using the structure of the similarity graph of the feature points. We 
-also address how to test the algorithms by constructing the 
-\emph{Murals} dataset consisting of $8$ source image pairs and a way to 
-generate testsets based on these pairs.  The proposed approach shows 
-promising results on both the \emph{Murals} dataset as well as a real 
-life example from the Gallagher dataset and the \emph{Graf} image set, 
-surpassing even a method using geometrical constraints when matching 
-image pairs that might not overlap.
+using the structure of the similarity graph of the feature points. The 
+algorithms show promising results when tested on the \emph{Murals} data 
+set where pairs of the same object seen from different angles are 
+cropped to have different degrees of overlap ranging from full to non at 
+all. We show that this result generalizes to variations in viewpoint 
+change by comparing \emph{MMC} to \emph{SIFT} over a set of image pairs 
+with an increasing magnitude of perspective difference. We go on to 
+apply the algorithms to a real life image case featuring occlusion and a 
+slight viewpoint change and show that the performance of \emph{MM} and 
+\emph{MMC} is consistent with the results on \emph{Murals}. Given the 
+versatility of the proposed algorithms, it would be interesting to apply 
+them to problems that require high reliability faced with images that 
+might not match, such as near duplicate detection or face clustering.
 %

### 2013-07-03 code/clustermatch.py

@@ -11,22 +11,12 @@ Jonas Toft Arnfred, 2013-05-22
 ####################################
 
 import numpy
-import isodata
 import features
 import louvain
 import weightMatrix
 import scoring
 from itertools import combinations
 
-
-dist_fun_map = {
-	"SIFT"   : weightMatrix.angleDist,
-	"SURF"   : weightMatrix.angleDist,
-	"ORB"    : weightMatrix.hammingDist,
-	"BRISK"  : weightMatrix.hammingDist,
-	"BRIEF"  : weightMatrix.hammingDist,
-	"FREAK"  : weightMatrix.hammingDist
-}
 
 ####################################
 #                                  #

### 2013-07-03 code/display.py

@@ -113,7 +113,7 @@ def matchPoints(im1, im2, matches, dist = None, filename = None, max_dist = 100,
 	im3 = appendimages(im1,im2, separation)
 
 	# Create figure
-	fig = pylab.figure(frameon=False, figsize=(5.0, 3.0))
+	fig = pylab.figure(frameon=False, figsize=(12.0, 8.0))
 	ax = pylab.Axes(fig, [0., 0., 1., 1.])
 
 	ax.set_axis_off()

### 2013-07-03 code/features.py

@@ -39,7 +39,7 @@ supported_descriptor_types = ["SIFT","SURF","ORB","BRISK","BRIEF","FREAK"]
 ####################################
 
 
-def getFeatures(paths, keypoint_type = "ORB", descriptor_type = "BRIEF", size=32) :
+def getFeatures(paths, keypoint_type = "SIFT", descriptor_type = "SIFT", size=32) :
 	""" Given a list of paths to images, the function returns a list of 
 	    descriptors and keypoints
 		Input: paths [list of strings] The paths to the images we are using
@@ -146,7 +146,7 @@ def match(descriptor_type, D1, D2) :
 		# The score of the best and second best match
 		s,t = row[i], row[j]
 		# Uniqueness: The ration between the best and second best match
-		u = s / (1.0 * t)
+		u = s / float(t)
 		return (i,s,u)
 
 	T = dist_fun(D1,D2)
@@ -205,7 +205,7 @@ def bfMatch(descriptor_type, D1, D2, match_same = False) :
 	second = 2 if match_same else 1
 
 	# Convert result
-	data = [(ms[first].trainIdx, ms[first].distance, ms[first].distance*1.0/(ms[second].distance + 0.1)) 
+	data = [(ms[first].trainIdx, ms[first].distance, float(ms[first].distance)/(ms[second].distance + 0.00001)) 
 				for ms in matches_qt if len(ms) == 3]
 
 	if len(data) == 0 : return (None, None, None)

### 2013-07-03 code/matching.py

@@ -175,12 +175,11 @@ def ratioMatch(paths, thresholds, options = {}) :
 	# Check that we have keypoints:
 	if ss == None : return [[] for _ in thresholds]
 
-	# Get matches in usual format
-	def matchFromIndex(i,j) :
-		return (features.getPosition(ks[indices == 0][i]), features.getPosition(ks[indices == 1][j]))
+	# Get all positions
+	(pos_im1, pos_im2) = (features.getPositions(ks[indices == 0]), features.getPositions(ks[indices == 1]))
 
 	# Now for each threshold test the uniqueness of the matches
-	p = lambda t : [matchFromIndex(i,j) for i,j in enumerate(ii) if uu[i] < t] 
+	p = lambda t : [(pos_im1[i], pos_im2[j]) for i,j in enumerate(ii) if uu[i] < t] 
 	match_set = [p(t) for t in thresholds]
 
 	return numpy.array(match_set)
@@ -217,9 +216,6 @@ def standardMatch(paths, thresholds, options = {}) :
 
 
 
-
-
-
 def matchDistance(p1, p2, hom) :
 	""" Given a homography matrix and two points this function calculates
 	    the geometric distance between the first point transformed by the
@@ -230,9 +226,6 @@ def matchDistance(p1, p2, hom) :
 	p2_n = m1to2[0:2]/m1to2[2]
 	p1_n = m2to1[0:2]/m2to1[2]
 	return numpy.linalg.norm(p2_n - p2) + numpy.linalg.norm(p1_n - p1)
-
-
-
 
 
 

### 2013-07-03 code/mirrormatch.py

@@ -27,8 +27,8 @@ def match(paths, thresholds, options = {}) :
 		return (features.getPosition(ks[i]), features.getPosition(ks[j]))
 
 	# Get options
-	keypoint_type		= options.get("keypoint_type", "ORB")
-	descriptor_type		= options.get("descriptor_type", "BRIEF")
+	keypoint_type		= options.get("keypoint_type", "SIFT")
+	descriptor_type		= options.get("descriptor_type", "SIFT")
 
 	# Get all feature points
 	indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)

### 2013-07-03 code/spectralmatch.py
Added spectralmatch

@@ -1,0 +1,96 @@
+"""
+Python module for matching two images using spectral matching.
+
+Based on:
+Leordeanu, Marius, and Martial Hebert. "A spectral technique for correspondence problems using pairwise constraints." Computer Vision, 2005. ICCV 2005. Tenth IEEE International Conference on. Vol. 2. IEEE, 2005.
+http://repository.cmu.edu/cgi/viewcontent.cgi?article=1362&context=robotics
+
+Jonas Toft Arnfred, 2013-07-03
+"""
+
+####################################
+#                                  #
+#            Imports               #
+#                                  #
+####################################
+
+import features
+import display
+import numpy
+import itertools
+import matching
+
+
+####################################
+#                                  #
+#           Functions              #
+#                                  #
+####################################
+
+
+def match(paths, thresholds, options ={}) :
+
+	# Get parameters
+	keypoint_type = options.get("keypoint_type", "SIFT")
+	descriptor_type = options.get("descriptor_type", "SIFT")
+	verbose = options.get("verbose", False)
+	affinity_fun = options.get("affinity", affinity_simple)
+	sigma = options.get("affinity", 50)
+	nb_sources = options.get("nb_sources", 500)
+	nb_matches = options.get("nb_matches", 100)
+
+	# Get all feature points
+	indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
+	(pos_im1, pos_im2) = (features.getPositions(ks[indices == 0]), features.getPositions(ks[indices == 1]))
+
+	match_data = features.bfMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
+
+	# Get threshold for n best matches
+	threshold = numpy.sort(match_data[1])[nb_sources]
+
+	# Get matches and scores
+	matches = numpy.array([(pos_im1[i], pos_im2[j]) for (i,(j,s,r)) in enumerate(zip(*match_data)) if s < threshold])
+	scores = numpy.array([s for (j,s,r) in zip(*match_data) if r < threshold])
+
+	# Get affinity matrix
+	M = affinity_matrix(matches, scores, affinity_fun, sigma)
+
+	# Get eigenvectors
[…]

### 2013-07-30 code/matching.py
Added debug info to matching

@@ -65,7 +65,11 @@ def folderMatch(directory, dt, match_fun, thresholds, keypoint, descriptor) :
     # Get a set of matches varied over image pairs (matrix of size N x T where N
     # is amount of image pairs and T is the amount of thresholds. Each element in
     # the matrix is a zipped list of matches and distances
-    match_sets = numpy.array([numpy.array(match_fun(dt, p, h, thresholds, keypoint, descriptor)) for p, h in imagePairs]).T
+    def do_match(p,h) :
+        print("Matching pairs: %s" % features.getLabel(p[0]))
+        return numpy.array(match_fun(dt, p, h, thresholds, keypoint, descriptor))
+
+    match_sets = numpy.array([do_match(p,h) for p, h in imagePairs]).T
 
     # Now collect an x axis with nb correct matches per threshold
     get_correct_matches = lambda match_row : [nb_correct_matches(d) for d in match_row]
@@ -226,7 +230,7 @@ def spectralMatchMMC(distance_threshold, paths, homography, thresholds, keypoint
 
 
 
-def siftMatch(distance_threshold, paths, homography, thresholds, keypoint, descriptor) :
+def ratioMatch(distance_threshold, paths, homography, thresholds, keypoint, descriptor) :
     options = {
         "thresholds" : thresholds,
         "distance_threshold" : distance_threshold,

### 2013-07-30 code/ratiomatch.py

@@ -43,9 +43,6 @@ def match(paths, options = {}) :
 	# Use cv2's matcher to get matching feature points
 	ii, ss, uu = features.bfMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
 	
-	# Check that we have keypoints:
-	if ss == None : return [[] for _ in thresholds]
-
 	# Get all positions
 	(pos_im1, pos_im2) = (features.getPositions(ks[indices == 0]), features.getPositions(ks[indices == 1]))
 

### 2013-07-30 code/spectralmatch.py

@@ -38,7 +38,7 @@ def match(paths, options ={}) :
     keep_ratio = options.get("keep_ratio", 0.75)
     verbose = options.get("verbose", False)
 
-    matches, scores, ratios = matching_fun(paths, options)
+    matches, ratios, scores = matching_fun(paths, options)
     nb_matches = len(matches) * keep_ratio
     if (nb_matches < 1) : 
         return lambda t : [], [], []

### 2013-07-31 code/louvain.py
Fixing ident in louvain.py

@@ -25,72 +25,74 @@ import numpy
 
 
 def cluster(weights, verbose=False) :
-	indices = numpy.arange(0, weights.shape[0])
-	partitions = indices.copy()
-	K = numpy.sum(weights)
-	moved = 1
-	m = 0
-	while (moved > 0) :
-		deltas = [move(weights, i, partitions, K, False) for i in indices]
-		moved = sum([1 for d in deltas if d > 0])
-		delta_Q = sum(deltas)
-		if verbose : 
-			m_old = m
-			m = modularity(weights, partitions)
-			m_diff = m - m_old
-			print("Moved %i vertices (modularity now: %.4f, change of %.4f (%.4f))" % (moved,m,m_diff,delta_Q))
-	return partitions
+    indices = numpy.arange(0, weights.shape[0])
+    partitions = indices.copy()
+    K = numpy.sum(weights)
+    moved = 1
+    m = 0
+    delta_Q = 1
+    #while (moved > 0) :
+    while (delta_Q > 0) :
+        deltas = [move(weights, i, partitions, K, False) for i in indices]
+        moved = sum([1 for d in deltas if d > 0])
+        delta_Q = sum(deltas)
+        if verbose : 
+            m_old = m
+            m = modularity(weights, partitions)
+            m_diff = m - m_old
+            print("Moved %i vertices (modularity now: %.6f, change of %.6f (%.6f))" % (moved,m,m_diff,delta_Q))
+    return partitions
 
 
 def move(weights, index, partitions, K, verbose = False) :
-	# Move out of partition
-	old_partition = partitions[index]
-	#partitions[index] = -1
-	# See how much we would gain from moving p back to orig_partition
-	lost_Q = deltaQ(weights, index, (old_partition == partitions), K)
-	# What is the best gain elsewhere?
-	prospects = set(partitions[numpy.nonzero(weights[index])])
-	prospect_Q = [(deltaQ(weights, index, (p == partitions), K), p) for p in prospects]
-	max_gained_Q = max(prospect_Q) if (len(prospect_Q) > 0) else (-1,-1)
-	# Is it worth moving?
-	delta = max_gained_Q[0] - lost_Q
-	if (delta > 0.0000001) : 
-		if verbose :
-			print("Delta is %.8f, moving node from partition %i to partition %i" % (delta, old_partition, max_gained_Q[1]))
-			print(weights[partitions == old_partition][:,partitions == old_partition])
[…]

### 2013-07-31 code/matching.py

@@ -65,11 +65,11 @@ def folderMatch(directory, dt, match_fun, thresholds, keypoint, descriptor) :
     # Get a set of matches varied over image pairs (matrix of size N x T where N
     # is amount of image pairs and T is the amount of thresholds. Each element in
     # the matrix is a zipped list of matches and distances
-    def do_match(p,h) :
-        print("Matching pairs: %s" % features.getLabel(p[0]))
+    def do_match(p, h) :
+        print("%s " % features.getLabel(p[0])),
         return numpy.array(match_fun(dt, p, h, thresholds, keypoint, descriptor))
 
-    match_sets = numpy.array([do_match(p,h) for p, h in imagePairs]).T
+    match_sets = numpy.array([do_match(p, h) for p, h in imagePairs]).T
 
     # Now collect an x axis with nb correct matches per threshold
     get_correct_matches = lambda match_row : [nb_correct_matches(d) for d in match_row]
@@ -192,7 +192,7 @@ def clusterMatch(distance_threshold, paths, homography, thresholds, keypoint, de
         "prune_limit" : 2.5,
         "min_coherence" : 0.0,
         "thresholds" : thresholds,
-        "split_limit" : 500,
+        "split_limit" : 50000,
         "cluster_prune_limit" : 1.5,
         "distance_threshold" : distance_threshold,
         "keypoint_type" : keypoint,
@@ -224,6 +224,7 @@ def spectralMatchMMC(distance_threshold, paths, homography, thresholds, keypoint
         "descriptor_type" : descriptor,
         "match_fun" : clustermatch.getMatchSet,
         "threshold" : 0.94,
+        "verbose" : True,
     }
     match_fun = spectralmatch.matchAlt(paths, options)
     return evaluate(match_fun, thresholds, homography)

### 2013-07-31 code/louvain.py
Fixed issue with louvain that made it loop indefinitely

@@ -31,15 +31,16 @@ def cluster(weights, verbose=False) :
     moved = 1
     m = 0
     delta_Q = 1
+    m_diff = 1
     #while (moved > 0) :
-    while (delta_Q > 0) :
+    while (m_diff > 0 and moved > 0) :
         deltas = [move(weights, i, partitions, K, False) for i in indices]
         moved = sum([1 for d in deltas if d > 0])
         delta_Q = sum(deltas)
+        m_old = m
+        m = modularity(weights, partitions)
+        m_diff = m - m_old
         if verbose : 
-            m_old = m
-            m = modularity(weights, partitions)
-            m_diff = m - m_old
             print("Moved %i vertices (modularity now: %.6f, change of %.6f (%.6f))" % (moved,m,m_diff,delta_Q))
     return partitions
 
@@ -56,7 +57,7 @@ def move(weights, index, partitions, K, verbose = False) :
     max_gained_Q = max(prospect_Q) if (len(prospect_Q) > 0) else (-1,-1)
     # Is it worth moving?
     delta = max_gained_Q[0] - lost_Q
-    if (delta > 0.0001) : 
+    if (delta > 0.000001) : 
         if verbose :
             print("Delta is %.8f, moving node from partition %i to partition %i" % (delta, old_partition, max_gained_Q[1]))
             print(weights[partitions == old_partition][:,partitions == old_partition])
@@ -73,7 +74,7 @@ def deltaQ(weights, index, partition, K) :
     v_edges = weights[index]
     v_weight = 2.0 * v_edges[partition].sum()
     p_weight = weights[partition]
-    k_neighbours = 2.0 * p_weight.sum() - p_weight[:,partition].sum()
+    k_neighbours = 2.0 * p_weight.sum() - p_weight[:, partition].sum()
     k_v = v_edges.sum()
     Q_iv = 1.0/K * (v_weight - (k_v * k_neighbours + k_v**2) / K)
     #print("new: %.6f, old: %.6f" % (Q_iv, Q_iv_old))

### 2013-07-31 code/ratiomatch.py
changed indentation of ratiomatch from tab to spaces

@@ -34,34 +34,34 @@ import numpy
 
 def match(paths, options = {}) :
 
-	keypoint_type		= options.get("keypoint_type", "SIFT")
-	descriptor_type		= options.get("descriptor_type", "SIFT")
+    keypoint_type		= options.get("keypoint_type", "SIFT")
+    descriptor_type		= options.get("descriptor_type", "SIFT")
 
-	# Get all feature points
-	indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
+    # Get all feature points
+    indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
 
-	# Use cv2's matcher to get matching feature points
-	ii, ss, uu = features.bfMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
-	
-	# Get all positions
-	(pos_im1, pos_im2) = (features.getPositions(ks[indices == 0]), features.getPositions(ks[indices == 1]))
+    # Use cv2's matcher to get matching feature points
+    ii, ss, uu = features.bfMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
+    
+    # Get all positions
+    (pos_im1, pos_im2) = (features.getPositions(ks[indices == 0]), features.getPositions(ks[indices == 1]))
 
-	# Define a function that given a threshold returns a set of matches
-	def match_fun(threshold) :
-		match_data = [(numpy.array((pos_im1[i], pos_im2[j])), uu[i], ss[i]) for i,j in enumerate(ii) if uu[i] < threshold]
-		if len(match_data) == 0 : return [], [], []
-		matches, ratios, scores = zip(*match_data)
+    # Define a function that given a threshold returns a set of matches
+    def match_fun(threshold) :
+        match_data = [(numpy.array((pos_im1[i], pos_im2[j])), uu[i], ss[i]) for i,j in enumerate(ii) if uu[i] < threshold]
+        if len(match_data) == 0 : return [], [], []
+        matches, ratios, scores = zip(*match_data)
 
-		return matches, ratios, scores
+        return matches, ratios, scores, (pos_im1, pos_im2)
 
-	return lambda t : match_fun(t)
+    return lambda t : match_fun(t)
 
 
 def getMatchSet(paths, options = {}) :
 
-	# Get parameters
-	threshold = options.get("threshold", 1.0)
+    # Get parameters
[…]

### 2013-07-31 code/display.py
Added recallPlot to display

@@ -35,142 +35,142 @@ from sklearn import metrics
 ####################################
 
 def appendimages(im1, im2, seperator = 0) :
-	""" return a new image that appends the two images side-by-side.
-	"""
+    """ return a new image that appends the two images side-by-side.
+    """
 
-	barrier = numpy.ones((im1.shape[0],seperator)) * 255
+    barrier = numpy.ones((im1.shape[0],seperator)) * 255
 
-	if (im1.shape[0] == im2.shape[0]) :
-		tmp = im2
+    if (im1.shape[0] == im2.shape[0]) :
+        tmp = im2
 
-	elif (im1.shape[0] > im2.shape[0]) :
-		tmp = numpy.ones((im1.shape[0], im2.shape[1])) * 255
-		tmp[0:im2.shape[0], :] = im2
+    elif (im1.shape[0] > im2.shape[0]) :
+        tmp = numpy.ones((im1.shape[0], im2.shape[1])) * 255
+        tmp[0:im2.shape[0], :] = im2
 
-	elif (im1.shape[0] < im2.shape[0]) :
-		tmp = numpy.ones((im1.shape[0], im2.shape[1])) * 255
-		tmp[0:im1.shape[0], :] = im2[0:im1.shape[0],:]
+    elif (im1.shape[0] < im2.shape[0]) :
+        tmp = numpy.ones((im1.shape[0], im2.shape[1])) * 255
+        tmp[0:im1.shape[0], :] = im2[0:im1.shape[0],:]
 
-	else :
-		print("Detonating thermo-nuclear devices")
+    else :
+        print("Detonating thermo-nuclear devices")
 
-	return numpy.concatenate((im1,barrier, tmp), axis=1)
+    return numpy.concatenate((im1,barrier, tmp), axis=1)
 
 
 
 
 
 def keypoints(im, pos) :
-	""" show image with features. input: im (image as array), 
-	    locs (row, col, scale, orientation of each feature) 
-	"""
-	# Plot all keypoints
-	pylab.gray()
-	pylab.imshow(im)
-	pylab.plot([p[1] for p in pos], [p[0] for p in pos], '.b')
-	pylab.axis('off')
-	pylab.show()
+    """ show image with features. input: im (image as array), 
+        locs (row, col, scale, orientation of each feature) 
+    """
+    # Plot all keypoints
+    pylab.gray()
+    pylab.imshow(im)
[…]

### 2013-08-01 text/clustering.tex
Clustered and bibliography from submitted

--- 2013-06-07 text/clustering.tex
@@
 %\usepackage[font={small}]{caption}
-\usepackage{sidecap}
+%\usepackage{sidecap}
 \usepackage{graphicx}
@@
 \usepackage{hyperref}
-\usepackage[stable]{footmisc}
-\usepackage{caption}
-\usepackage{adjustbox}
+%\usepackage[stable]{footmisc}
+%\usepackage{caption}
+%\usepackage{adjustbox}
 \usepackage{subcaption}
@@
 
-\title{Reliable feature point matching without the use of geometric 
-constraints}
-%\author{Jonas Arnfred and what to put here exactly?}
+\title{Mirror Match: Reliable Feature Point Matching Without Geometric Constraints}
+\author{Anonymous ACPR Submission}
 
@@
 feature points in two or more images using geometric assumptions to 
-increase the robustness of the matching. However very little work 
-addresses the case where these assumptions might not hold true. In 
-particular few methods address the problem of reliable matching in cases 
-where we do not know if two images have any corresponding areas or 
-objects. In this paper we propose two algorithms for matching feature 
-points without the use of geometric constraints. The first makes use of 
-the fact that any match between two images should be better than all 
-possible matches within the image itself. The second algorithm extends 
-this idea by using community structure in the similarity graph of 
-feature points to reliably find correspondences. To evaluate the 
-algorithms experimentally we introduce a set of 8 image pairs all 
-containing viewport changes and a simple method to generate a large 
-amount of test cases based on these 8 pairs. The experimental results 
-show that the proposed algorithm, overall, is superior to traditional 
-approaches in finding correct correspondences.
+increase the robustness of the matching. However, very little work 
+addresses the case where these assumptions might not hold. In particular 
+few methods address the problem of reliable matching in cases where it 
+is unknown whether two images have any corresponding areas or objects in 
+the first place.
+
+We propose two algorithms for matching feature points without the use of 
+geometric constraints. The first relies on the fact that any match 
+between two images should be better than all possible matches within a 
+single image. The second algorithm extends this idea by using community 
+structure in the similarity graph of feature points to find reliable 
+correspondences. To evaluate the algorithms experimentally, we introduce 
+a simple method to generate a large amount of test cases based on a set 
+of image pairs with viewpoint changes. Our results show that the 
+proposed algorithm is generally superior to traditional approaches in 
+finding correct correspondences.
 \end{abstract}
@@
 proposed in the literature to solve this problem. Many approaches look 
-at the geometric configuration of the feature points and match them 
-according to assumptions made about the geometric relationship between 
-the images matched. These assumptions are then used to create 
-constraints on the matches such as angular constraints 
-\cite{kim2008efficient}, epipolar constraints \cite{torr2000mlesac}, 
-\cite{chum2005matching} and pairwise constraints \cite{choi2009robust}, 
-\cite{leordeanu2005spectral}.
+at the geometric configuration of feature points and match them based on 
+various assumptions about the geometric relationship between the images. 
+These assumptions are then used to create different constraints on the 
+matches, e.g.\ angular constraints \cite{kim2008efficient}, epipolar 
+constraints \cite{torr2000mlesac,chum2005matching}, or pairwise 
+constraints \cite{choi2009robust,leordeanu2005spectral}.
 %
@@
 %relationship between the images matched. A simple example would be to 
-%only consider matches that aren't deviating too much with respect to 
-%the average angle and distancen as considered by 
-%\cite{kim2008efficient}.  This performs well in situations where no 
-%camera rotation occurs between the two images, but fails when this 
-%assumption isn't met. Various scenarios have been proposed to improve 
-%on this simple assumption such as epipolar constraints 
-%(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
-%constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}). The 
-%Epipolar constraint carries the assumption that the two images matched 
-%are related by an affine transformation. That is, there is no relative 
+%only consider matches that aren't   too much with respect to the 
+%average angle and distancen as considered by \cite{kim2008efficient}.  
+%This performs well in situations where no camera rotation occurs 
+%between the two images, but fails when this assumption isn't met. 
+%Various scenarios have been proposed to improve on this simple 
+%assumption such as epipolar constraints (\cite{torr2000mlesac}, 
+%\cite{chum2005matching}) and pairwise constraints 
+%(\cite{choi2009robust}, \cite{leordeanu2005spectral}). The Epipolar 
+%constraint carries the assumption that the two images matched are 
+%related by an affine transformation. That is, there is no relative 
 %movement of objects in between images and either the viewpoint is fixed 
@@
 %
-Alternatively we can pick out different areas in each image and pair 
+An alternative is to pick out different areas in each image and pair 
 areas when correspondence pairs are mainly found going from one area to 
 another. This allows for the filtering of all correspondences that do 
-not fall within paired areas. Examples include \cite{das2008event} and 
-\cite{wu2011robust}.
+not fall within paired areas. Examples include \emph{Isodata} 
+\cite{das2008event}, which clusters feature points according to their 
+position in the image,
+and the method from \cite{wu2011robust}, which uses maximally stable 
+extremal regions (MSER) feature points to designate areas. %In this 
+paper the algorithm from \cite{das2008event} will later be referred to 
+as \emph{Isodata}.
 
@@
 
-In practice however, there are many situations where using the geometry 
-of the image to filter correspondences is not possible, such as object 
-recognition where adjacent objects in one photo might be separated in 
-another. Another example is images that do not overlap where algorithms 
-might still find matches adhering to the imposed geometric constraints.
-In addition methods using geometric constraints all require an initial 
-set of correspondences. If this set of correspondences is narrowed down 
-to a set with a higher ratio of correct matches the result of the 
-geometric matching will benefit in terms of speed and accuracy. Finally 
-some use cases might require a performance that can't be achieved by a 
-more complex geometric method where simple non geometric methods might 
-be able to provide sufficient matching accuracy with a smaller 
-performance penalty.
+In practice there are many situations where relying on the geometry of the 
+image to filter correspondences is not possible, for example images without overlap, or adjacent objects in one image are that are separated in 
+another.  %Another example is images that do not overlap where algorithms might still find matches adhering to the imposed geometric constraints.
+Furthermore, methods using geometric constraints all require an initial 
+set of correspondences. If this set of correspondences can be narrowed down 
+to the most probable correct matches, the geometric matching algorithm will benefit in terms of speed and accuracy. 
+Finally some use cases might require a speed that simply cannot be achieved by 
+complex geometric methods.% where simple non geometric methods might be able to provide sufficient matching accuracy with a smaller performance penalty.
 
-There are a relatively small number of algorithms proposed to solve the 
-matching problem without involving geometric constraints. Traditionally 
-the feature points of two images have been matched by comparing every 
-feature point of one image with all feature points of the other and 
-finding the best matches based on the similarity of the descriptors.  
-With the introduction of the SIFT features \cite{lowe2004sift}, Lowe 
-proposes an alternative measure where the uniqueness of a given match is 
-found by looking at the two nearest neighbors of each feature point and 
-calculating a match score by the ratio of similarities. Ranking the 
+In the absence of geometric constraints, only few methods are available. 
+As pointed out in \cite{szeliski2010}, the simplest 
+approach to matching feature points is to return all matches above a given 
+threshold of similarity.  This can be done with a fixed threshold or by 
+finding the nearest neighbors for each point (still filtering by a threshold to avoid including matches for feature points that have no counterpart in the other image).  
+Lowe \cite{lowe2004sift} proposed the scale-invariant feature transform (SIFT) together with 
+an alternative measure, where the uniqueness of a given match is found by 
+looking at the two nearest neighbors of each feature point and 
+calculating the matching score as the ratio of similarities.  Ranking the 
 scores by their uniqueness and picking the $n$ best produces a set of 
-correspondences that are distinctly matched across the two images. This 
-method will be referred to as \emph{SIFT} in this paper.
+correspondences that are distinctly matched across two images. %This method will be referred to as \emph{SIFT} in this paper. 
+Of these three methods (fixed threshold, nearest neighbors, and \emph{SIFT}), 
+\emph{SIFT} was found to perform best by a slight margin 
+\cite{mikolajczyk2005performance}.
 
-In turn the two methods proposed in this paper are inspired by a simple 
-but novel idea. If we have two images and a given feature point in the 
-first image is better matched with other feature points from the 
+The two methods we propose in this paper are inspired by a simple 
+but novel idea. If a given feature point in one image is better matched with other feature points from the 
 \emph{same} image than points in the other image, then any matches from 
-this feature point to points in the other image is deemed unreliable and 
+this feature point to points in the other image are considered unreliable and should be 
 discarded.  This approach carries no implicit assumptions about the 
-geometric consistency of matches and can as such easily be extended with 
-other geometric solutions when appropriate.
+geometric consistency of matches and as such can easily be extended with 
+other geometric solutions when appropriate or necessary.
 
-%Based on this idea the two proposed methods find reliable matches as 
-%follows:
-%\begin{itemize}
-%\item[]{\emph{Mirror Match (MM)}: Match features using the gold standard 
-%		algorithm\cite[p. 114]{multipleView} ranked by similarity and 
-%		thresheld by uniqueness\cite{lowe2004sift}.  However instead of 
-%		matching features from one image with features in another, we 
-%	match every feature with all other features of the two images 
-%combined. Only matches from one image to the other are returned.}
-%\item[]{\emph{Mirror Match with Clustering (MMC)}: Take the combined set 
-%		of feature points from both images and cluster these points 
-%		according to their descriptors. Given a resulting partition of 
-%		points, no matches are returned if it contains only feature 
-%	points from one image. If the partition contains points from both 
-%images, \emph{Mirror Match} is used to find the best matches within the 
-%partition.}
-%\end{itemize}
-%%
+Based on this idea,  we determine reliable matches as 
+follows. \emph{Mirror Match (MM)} matches every feature from both 
+images with all other features and filters matches based on the ratio of 
+best to second best match as in \emph{SIFT}. \emph{Mirror Match with 
+Clustering (MMC)} on the other hand takes the combined set of feature 
+points from both images and clusters these points according to their 
+descriptors.  If a resulting partition contains only feature points from one image, no matches are 
+returned.  If the 
+partition contains points from both images, \emph{Mirror Match} is used 
+to find the best matches within this partition.  The experimental results 
+show that both approaches generally outperform existing 
+correspondence matching methods.
+
 %Matching feature points against the entire set of points from both 
@@
 %
+
+The paper is organized as follows.
+Section~\ref{S:MatchingMethods} describes the proposed \emph{Mirror Match (MM)} and \emph{Mirror Match with Clustering (MMC)} algorithms.
+Section~\ref{S:Experiments} presents the dataset used for evaluation and the experimental setup.
+Section~\ref{S:Results} discusses the benchmarking results obtained.
+Section~\ref{S:Summary} concludes the paper.
+
 \section{Matching Methods}
+\label{S:MatchingMethods}
+
 \subsection{Mirror Match (\emph{MM})}
+
+\begin{figure}
+	\centering%
+		\begin{subfigure}[t]{\columnwidth}
+			\centering
+			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
+			\caption{Source image pair}
+			\label{fig:pitts_source}
+		\end{subfigure}%
+		\\ %
+		\begin{subfigure}[t]{\columnwidth}
+			\centering
+			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
+			\caption{Feature points}
+			\label{fig:pitts_keypoints}
+		\end{subfigure}%
+		\\ %add desired spacing between images, e. g. ~, \quad, 
+		%\qquad (or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{\columnwidth}
+			\centering
+			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
+			\caption{\emph{SIFT}}
+			\label{fig:unique}
+		\end{subfigure}%
+		\\ %add desired spacing between images, e. g. ~, \quad, 
+		\begin{subfigure}[t]{\columnwidth}
+			\centering
+			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
+			\caption{\emph{MM} intermediate result}
+			\label{fig:within}
+		\end{subfigure}%
+		\\ %add desired spacing between images, e. g. ~, \quad, 
+		%\qquad (or a blank line to force the subfigure onto a new line)
+		\begin{subfigure}[t]{\columnwidth}
+			\centering
+			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
+			\caption{\emph{MM} final result}
+			\label{fig:without}
+		\end{subfigure}%
+		\\ %add desired spacing between images, e. g. ~, \quad, 
+		\begin{subfigure}[t]{\columnwidth}
+			\centering
+			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
+			\caption{\emph{MMC} Partition Example}
+			\label{fig:pitts_partition}
+		\end{subfigure}%
+	\caption{Feature matching with \emph{MM} and \emph{MMC}.
+Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
+	(c) Result of \emph{SIFT} matching. 
+  (d) All matches found by \emph{MM}, including intra-image matches. 
+	(e) Final \emph{MM} result. 
+	(f) Example of a partition of feature points after clustering, which 
+includes similar feature points from building windows and shirt patterns.}%
+	\label{fig:comparemirror}%
+\end{figure}%
+
 %
@@
 other feature from the same set. We can then discard the correspondences 
-that match two points within the same image. In algorithm \ref{alg-mm} 
-the implementation of \emph{MM} is shown.
+that match two points within the same image. Algorithm~\ref{alg-mm} details  
+the implementation of \emph{MM}.
 %
 \begin{algorithm}
-\caption{Mirror Match Algorithm (\emph{MM})}
+\caption{Mirror Match (\emph{MM})}
 \label{alg-mm}
-{\fontsize{10}{10}\selectfont
+%{\fontsize{10}{10}\selectfont
 \begin{algorithmic}
-\Require $images$ : set of images, $t$ : float $\in \mathbb{R}$
+\Require $images$ : set of images, $t \in \mathbb{R}$
 \State $matches_{init}\gets \varnothing$
@@
 \State $features\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather Stage
+\ForAll{$I_i \in images$} \Comment Acquisition Stage
 	\State $features\gets features \cup getFeatures(I_i)$
 \EndFor
-\ForAll{$f_i \in features$} \Comment Match Stage
+\ForAll{$f_i \in features$} \Comment Matching Stage
 	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
@@
 \end{algorithmic}
-}
+%}
 \end{algorithm}
 %
-In the acquisition state we gather all features in the set of images.  
-These features are then matched in the match stage using K-Nearest 
-Neighbors.  For any given feature $f_i$ the two most similar neighbors 
-are returned and we calculate the ratio between them as as proposed in 
+In the acquisition stage we gather all features in the set of images.  
+In the matching stage these features are matched using $k$-nearest 
+neighbors.  For any given feature $f_i$ the two most similar neighbors 
+are returned, and we calculate the ratio between them as proposed in 
 \cite{lowe2004sift}.  Any correspondence with a ratio above the 
@@
 %
-\begin{figure*}
-	\makebox[\textwidth][c]{%
-		\begin{subfigure}[t]{0.32\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-			\caption{Source image}
-			\label{fig:pitts_source}
-		\end{subfigure}%
-		\enspace %
-		\begin{subfigure}[t]{0.32\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-			\caption{Keypoints Displayed}
-			\label{fig:pitts_keypoints}
-		\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.32\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/mirror_match_off}
-			\caption{\emph{SIFT}}
-			\label{fig:unique}
-		\end{subfigure}%
-	}
-	\makebox[\textwidth][c]{%
-		\begin{subfigure}[t]{0.32\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
-			\caption{\emph{MM} with intra image matches}
-			\label{fig:within}
-		\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.32\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/mirror_match}
-			\caption{\emph{MM}}
-			\label{fig:without}
-		\end{subfigure}%
-		\enspace%
-		\begin{subfigure}[t]{0.32\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/MMC_partition}
-			\caption{\emph{MMC} Partition Example}
-			\label{fig:pitts_partition}
-		\end{subfigure}%
-	}%
-	\caption{Illustration of matches filtered by \emph{MM}. For each 
-	correct match found between the two images, a green line is shown.  
-Incorrect matches are marked with a red line. Figure \ref{fig:within} 
-shows the correspondences found by mirror match, but including all 
-matches that are found within the same image. }%
-	\label{fig:comparemirror}%
-\end{figure*}%
+%\begin{figure*}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.32\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
+%			\caption{Source image pair}
+%			\label{fig:pitts_source}
+%		\end{subfigure}%
+%		\enspace %
+%		\begin{subfigure}[t]{0.32\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
+%			\caption{Feature points}
+%			\label{fig:pitts_keypoints}
+%		\end{subfigure}%
+%		\enspace %add desired spacing between images, e. g. ~, \quad, 
+%		%\qquad (or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.32\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/mirror_match_off}
+%			\caption{\emph{SIFT}}
+%			\label{fig:unique}
+%		\end{subfigure}%
+%	}
+%	\makebox[\textwidth][c]{%
+%		\begin{subfigure}[t]{0.32\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
+%			\caption{\emph{MM} intermediate result}
+%			\label{fig:within}
+%		\end{subfigure}%
+%		\enspace %add desired spacing between images, e. g. ~, \quad, 
+%		%\qquad (or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.32\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/mirror_match}
+%			\caption{\emph{MM} final result}
+%			\label{fig:without}
+%		\end{subfigure}%
+%		\enspace%
+%		\begin{subfigure}[t]{0.32\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/MMC_partition}
+%			\caption{\emph{MMC} Partition Example}
+%			\label{fig:pitts_partition}
+%		\end{subfigure}%
+%	}%
+%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}.
+Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
+%(c) Result of \emph{SIFT} matching the two images.% 
+%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
+%	(e) Final \emph{MM} result with the intra-image matches removed. 
+%	(f) Example of a partition of feature points after clustering. This partition 
+%includes similar feature points around the windows of a building and the patterns of a shirt.}%
+%	\label{fig:comparemirror}%
+%\end{figure*}%
 
-In figure \ref{fig:within} and \ref{fig:without} an example of the 
-result of \emph{MM} is illustrated. In figure \ref{fig:unique} many of 
-the incorrect matches occur in the fence in the bottom of the image.  
-When we match all feature points together many of these incorrect 
-matches are eliminated because points in the fence match with other 
-points in the fence in the same image as shown in figure 
-\ref{fig:within} and \ref{fig:without}.
+Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} using an example image pair from the Gallagher dataset \cite{gallagher2008}.
+With \emph{SIFT} (Figure~\ref{fig:unique}), many incorrect matches occur 
+in the fence towards the bottom of the image.
+When we match all feature points together, many of these incorrect 
+matches are eliminated, because points in the fence match with other 
+points in the fence in the same image (Figures~\ref{fig:within} and
+\ref{fig:without}).
 
@@
 %
-As opposed to \emph{MM}, \emph{MMC} diverges from traditional 
-non-geometric feature matching by clustering the feature points by 
+In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
+non-geometric feature matching by clustering feature points by 
 similarity. This process yields partitions of fairly similar feature 
 points that we can match using the same approach as \emph{MM}.  
+Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
 %
@@
 %are then combined into one to achieve the right amount of partitions.
+%
 
-We use the Louvain Method\cite{blondel2008} for clustering feature 
-points since it's relatively fast and performs 
-well\cite{lancichinetti2009}, doesn't require 
-parameters\cite{blondel2008} and doesn't emphasize partitions of equal 
-sizes as opposed to for example spectral clustering and 
-k-means\cite{von2007}.
 %
 \begin{algorithm}
-\caption{Mirror Match with Clustering Algorithm (\emph{MMC})}
+\caption{Mirror Match with Clustering (\emph{MMC})}
 \label{alg-mmc}
-{\fontsize{10}{10}\selectfont
+%{\fontsize{10}{10}\selectfont
 \begin{algorithmic}
@@
 \EndFor
-\State $A\gets getAdjecencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
+\State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
 \State $A_{norm}\gets 1 - normalize(A)$
@@
 \end{algorithmic}
-}
+%}
 \end{algorithm}
 
-While the louvain clustering algorithm doesn't require any parameters in 
-itself, it tends towards clustering all feature points together in the 
-same partition if the graph is very connected.  To ensure that the graph 
-is well clustered, the adjacency matrix is pruned so only edges above a 
-certain threshold is kept. From empirical analysis keeping the 2.5\% of 
-edges with the highest similarity seems to work well in practice. Figure 
-\ref{fig:graph} shows the result of clustering the feature points 
-displayed as a graph.
-%
-\begin{SCfigure*}
-	\makebox[0.7\textwidth][c]{%
-		\begin{subfigure}[t]{0.35\textwidth}
+\begin{figure}[h]
 	\centering
-			\includegraphics[width=\textwidth]{images/MMC_graph_full}
+	\begin{subfigure}{0.8\columnwidth}
+		\includegraphics[width=\columnwidth]{images/MMC_graph_full}
 		\caption{Full Graph}
@@
 	\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+
+	%add desired spacing between images, e. g. ~, \quad, \qquad		  
 	%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.32\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/MMC_graph_cropped}
+	\begin{subfigure}{0.7\columnwidth}
+		\includegraphics[width=\columnwidth]{images/MMC_graph_cropped}
 		\caption{Cropped Section of Graph}
@@
 	\end{subfigure}%
-	}%
-	\caption{The partitioned feature graph. Each vertex represents a 
-		feature point while an edge represent a high similarity between 
-		points. A partition is a connected group marked by a color.  Due 
-		to a limited amount of colors some disconnected partitions have 
-		been assigned the same color. The edge color of each node 
-		signifies which image it belongs to. In the detailed crop to the 
-		right the various cluster sizes can be seen, ranging from 
+	\caption{The partitioned feature graph (a). Each vertex represents a 
+		feature point; lines indicate high similarity between 
+		points. A partition is a connected group with the same color. The border color of each node 
+		indicates which image it belongs to.  Zooming into a section of the graph (b), the various cluster sizes can be seen, ranging from 
 	hundreds of feature points to only two or three.}
 	\label{fig:graph}
-\end{SCfigure*}
+\end{figure}
 
-The partitions group feature points by similarity which means that 
-repetitive structures such as buildings often feature in larger 
-partitions as exemplified in figure \ref{fig:pitts_partition}.
+We use the Louvain Method \cite{blondel2008} for clustering feature 
+points, since it is relatively fast and performs 
+well \cite{lancichinetti2009}, does not require 
+parameters \cite{blondel2008}, and does not emphasize partitions of equal 
+size, as opposed to spectral clustering or 
+k-means \cite{von2007}, for example.
+While the Louvain clustering algorithm does not require any parameters in 
+itself, it tends towards clustering all feature points together in the 
+same partition if the graph is very connected.  To ensure that the graph 
+is well clustered, the adjacency matrix is pruned so that only edges above a 
+certain threshold are kept. From empirical analysis, retaining the top 
+2.5\% of edges with the highest similarity seems to work well in 
+practice. Figure~\ref{fig:graph} shows the result of clustering the 
+feature points as a graph.
+%
+
+The partitions group feature points by similarity, which means that 
+repetitive structures such as buildings often appear in larger 
+partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
 %
@@
 The matching algorithm for \emph{MMC}, \emph{getMatches}, finds matches 
-within all partitions with more than two elements as done in \emph{MM}.  
-However as can be seen in the example in figure \ref{fig:cropped_graph} 
-many of the partitions contain only two feature points from different 
-images linked by one edge. In the case of such a pair we compare the 
-similarity of the these two feature points with their second best match 
-and filters matches where this ratio falls over a certain threshold like 
-in the \emph{SIFT} algorithm.
+within all partitions with more than two elements using the \emph{MM} 
+approach.  However, as can be seen in the example in 
+Figure~\ref{fig:cropped_graph}, many of the partitions contain only two 
+feature points from different images linked by one edge. In such a case, 
+we compare the similarity of the these two feature points with their 
+second best match and remove matches where this ratio lies above a 
+certain threshold, like in the \emph{SIFT} algorithm. For example in the 
+case of Figure~\ref{fig:pitts_partition}, we have feature points from a 
+building in one image grouped together with points from a shirt pattern 
+in another.  The nearest neighbor method would have returned wrong 
+matches, but since we match the partition with \emph{MM}, points in the 
+building end up matching other points in the building, and no matches 
+are returned.
 
@@
 \section{Experiments}
-\label{experiment}
+\label{S:Experiments}
 %
-To reliably measure the accuracy of a matching method on real images we 
-either need a set of image pairs tied by a homography or manually count 
-the number of inliers. The latter becomes unfeasible the moment we 
-attempt to test a non-trivial set of images.
+To reliably measure the accuracy of a matching method on real images, we 
+either need a set of image pairs tied by a homography, or we have to manually count 
+the number of inliers. The latter becomes prohibitive for large numbers of (non-trivial) images.
 
-In \cite{mikolajczyk2005performance} Mikolajczyk and Schmid introduces a 
-set of images to compare the performance of feature detectors. The test 
-set covers different types of image variance such as different lighting, 
-blur, rotation as well as viewpoint change. Inspired by this 
-dataset\footnote{In particular by the 'Graf' image set} and motivated by 
-the need for more image pairs featuring viewport changes, we have 
-compiled a set of $8$ image pairs consisting of subjects taken from two 
+Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a set of test images
+to compare the performance of feature detectors. The 
+set covers different types of image variations, such as lighting change, 
+blur, rotation, and viewpoint change. Inspired by this 
+dataset (in particular the `Graf' image set) and motivated by 
+the need for more image pairs featuring viewpoint changes, we have 
+compiled a set of 8 image pairs consisting of subjects taken from two 
 different angles. The images are collected from Flickr's database of 
 images published under a creative commons 
-licence\footnote{\href{http://creativecommons.org/}{www.creativecommons.org}, 
-a copyleft license permitting redistribution} and feature murals which 
+licence %\footnote{\href{http://creativecommons.org/}{www.creativecommons.org}, 
+%a copyleft license permitting redistribution} 
+and feature murals, which 
 makes it possible to relate points in the image pairs with a homography.  
-The images have been cropped to feature the same motive and resized to 
-$900$px by $600$px. This dataset will be referred to as the 
-\emph{Murals} dataset in this paper. The images can be seen in figure 
-\ref{fig:murals}.
+The images have been cropped to show the same motive and resized to 
+$900\times 600$ pixels.  This dataset will be referred to as the 
+\emph{Murals} dataset.  Figure~\ref{fig:murals} shows one image from each pair.
 
-\begin{figure*}
+\begin{figure}[htb]
+%	\makebox[0.5\textwidth][c]{%
+%		\begin{subfigure}[t]{0.048\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/pair_example1}
+%			\label{fig:fairey1}
+%	\end{subfigure}%
+%		\enspace %add desired spacing between images, e. g. ~, \quad, 
+%		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{0.048\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/pair_example2}
+%			\label{fig:fairey2}
+%		\end{subfigure}%
+%		\enspace %
+%		\begin{subfigure}[t]{0.36\textwidth}
+			\centering
+			\includegraphics[width=\columnwidth]{images/crop_examples}
+%		\end{subfigure}%
+%	}%
+	\caption{Sample test patches produced from an image pair.}
+	\label{fig:fairey}
+\end{figure}
+
+\begin{figure*}[t]
 	\centering
 	\includegraphics[width=\textwidth]{images/murals}
-	\caption{Images in the mural test set}
+	\caption{Images in the \emph{Murals} test set.}
 	\label{fig:murals}
 \end{figure*}
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
+	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
+	\label{fig:Graf}
+\end{figure}
 
@@
 %
-\begin{figure}
-	\makebox[0.5\textwidth][c]{%
-		\begin{subfigure}[t]{0.048\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example1}
-			\label{fig:fairey1}
-		\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{0.048\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example2}
-			\label{fig:fairey2}
-		\end{subfigure}%
-		\enspace %
-		\begin{subfigure}[t]{0.36\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/crop_examples}
-		\end{subfigure}%
-	}%
-	\caption{Example of test set produced by a source pair of images}
-	\label{fig:fairey}
-\end{figure}
 %
 %\subsection{Experimental setup}
-The \emph{MM} and \emph{MMC} algorithms have been tested against 
-\emph{SIFT}, the algorithm Lowe proposed in \cite{lowe2004sift} as well 
-as the \emph{Isodata} matching algorithm proposed in \cite{das2008event} 
-which uses geometric information to improve the matching. The comparison 
-has been done using the \emph{Murals} dataset, the \emph{Graf} set from 
-\cite{mikolajczyk2005performance} and two images\footnote{100\_1942.jpg 
-and 100\_1941.jpg} from \cite{gallagher2008} illustrated in figure 
-\ref{fig:comparemirror}.
+We compare the \emph{MM} and \emph{MMC} algorithms to 
+\emph{SIFT} \cite{lowe2004sift} as well 
+as \emph{Isodata} \cite{das2008event}. 
+\emph{Isodata} uses geometric constraints, whereas \emph{SIFT} does not.
+%, which uses geometric information to improve the matching. 
+%The comparison  with \emph{SIFT} serves to illustrate the relative performance of 
+%\emph{MM} and \emph{MMC} to a state of the art algorithm without 
+%geometric constraints. \emph{Isodata} is included to 
+%illustrate the performance of an algorithm relying on geometric 
+%constraints faced with image pairs that might not have any overlap.  
+The 
+comparison was done using the \emph{Murals} dataset (Figure~\ref{fig:murals}), the 
+\emph{Graf} set (Figure~\ref{fig:Graf}) from \cite{mikolajczyk2005performance}, and two 
+images %\footnote{100\_1942.jpg and 100\_1941.jpg} 
+from the Gallagher dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
 
-Test sets have been generated from the image pairs by cropping out 
-$250$px by $250$px patches with a random vertical and horizontal offset.  
-Given a source image pair we produce $100$ pairs of patches where the 
-two patches in any pair might or might not overlap.  This ensures that 
-the patch pairs with no overlap still retain a basic similarity to each 
-other, while the patches that do overlap often only overlap on a small 
-part of their surface. Figure \ref{fig:fairey} shows an example of 
-possible pairs of test images produced from a source image pair.  
+Test sets were generated from the image pairs by cropping square patches of
+$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
+Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
+This ensures that patch pairs with no overlap still retain a general similarity to each 
+other, while patches that do overlap often only share a small 
+part of their area. Figure~\ref{fig:fairey} shows an example of 
+possible pairs of test image patches produced from a source image pair.  
 Producing $n$ such pairs allows us to test not just how well the 
-matching algorithm performs on a variety of overlap but also how many 
+matching algorithm performs on a variety of overlaps but also how many 
 false positives we get on similar images that do not overlap at 
-all\footnote{The set of source images and homographies as well as the 
-	script to generate the cropped test sets based on them have been 
-	made available online together with the exact test sets used in this 
-paper on 
-\href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.  
+all.\footnote{~The set of source images and homographies as well as the 
+script to generate the cropped test sets based on them will be made 
+available online, together with the exact test sets used in this paper 
+upon acceptance.}
+%\href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.  
 In practice the amount of overlap between pairs in a test set will 
-depend on the overlap and viewport change of the source image pair.  To 
-give a rough impression of a typical example, table \ref{table:overlap} 
-shows the overlap of image pairs created from img1 and img3 of the 
+depend on the overlap and viewpoint change in the source image pair.  To 
+give a rough idea, Table~\ref{table:overlap} 
+shows the overlap of patch pairs created from images 1 and 3 of the 
 \emph{Graf} image set from \cite{mikolajczyk2005performance}.
 
-Given a potential match between two images $I_1$ and $I_2$, $m = 
-\left(p_1, p_2\right)$ and a homography $H$ relating $I_1$ to $I_2$, we 
-can calculate if $m$ is an inlier by check if the positions $p_1$ and 
-$p_2$ satisfies the following criteria:
-$$\left\vert Hp_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 
-\right\vert < 5$$
+\begin{table}[htb]
+\caption{Overlap in the set of 100 patch pairs created from two images of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
+\label{table:overlap}
+	\centering
+%	\small
+\begin{tabular}{r*{3}{r}}
+\hline
+	Amount of overlap: & 0\% & $< 50$\% & $> 50$\%  \\
+	\noalign{\smallskip}
+	%
+	Number of patch pairs: & 21 & 54 & 25 \\
+	\hline
+\end{tabular}
+\end{table}
+
+Given a potential match between two pixels $p_1$ and 
+$p_2$, $m = \left(p_1, p_2\right)$, and a homography $H$ relating the two images $I_1$ and $I_2$, we 
+can calculate if $m$ is an inlier by checking if the two points satisfy the following criteria:
+\begin{equation*}
+\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
+\end{equation*}
 That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
 \emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than five pixels.
+less than a certain threshold (we use $d_{\max}=5$ pixels here).
 
-\begin{table}
+\section{Results}
+\label{S:Results}
+
+Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
+generated from images 1 and 3 of the \emph{Graf} image set (cf.~Figure~\ref{fig:Graf}). The plot 
+compares the accuracy of \emph{SIFT}, \emph{MM}, \emph{MMC}, and 
+\emph{Isodata} as a function of the number of matches produced (which is achieved by varying thresholds over a certain range).
+The results show that \emph{MM} and \emph{MMC} consistently outperform \emph{SIFT}; \emph{MMC} generally lies 2-3 percentage points above \emph{MM} when both are performing at optimal accuracy.
+Although \emph{Isodata} exhibits a good performance on strict thresholds (small number of matches), that quickly diminishes when more matches are desired.
+
+\begin{figure}[htb]
+%	\makebox[0.5\textwidth][c]{%
+%		\begin{subfigure}[t]{.13\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/graf}
+%		\end{subfigure}%
+%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{.27\textwidth}
 			\centering
-	\small
-\begin{tabular}{l*{3}{r}}
-	Overlap: & 0\% & $< 50$\% & $> 50$\%  \\
-	\noalign{\smallskip}
-	%
-	Percent of image pairs: & 21\% & 54\% & 25\% \\
-\end{tabular}
-\caption{Overlap on the testset of 100 image pairs created from img1 and 
-img3 of the \emph{Graf} image set. 21 images had no overlap}
-\label{table:overlap}
-\end{table}
-\section{Results}
-\label{results}
-
-\begin{figure}
-	\makebox[0.5\textwidth][c]{%
-		\begin{subfigure}[t]{.13\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/graf}
-		\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/result_graf}
+			\includegraphics[width=0.6\columnwidth]{images/result_graf}
 			%\caption{Performance on Scharf}
-		\end{subfigure}%
-	}%
-	\caption{Accuracy on the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance} using img1 and img3. The plot 
-		shows the result of $100$ image pairs generated from the source 
+%		\end{subfigure}%
+%	}%
+	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
+		shows the result of 100 patch pairs generated from the source 
 		images shown to the left. The number of matches is the total 
-		number of matches for all $100$ image pairs.}
+		number of matches for all 100 patch pairs.}
 	\label{fig:result_graf}
@@
 
-\begin{figure}
+To validate whether these results 
+generalize to other images, we tested the four algorithms on the 
+\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
+In total 900 different patch pairs were generated from 9 
+source image pairs.  The results are shown in Figure 
+\ref{fig:result_accumulated}.
+
+\begin{figure}[htb]
 	\centering
-	\includegraphics[width=0.5\textwidth]{images/result_accumulated}
-	\caption{Results on the \emph{Murals} dataset and the pair of img1 
-		and img3 from the \emph{Graf} image set from 	
-		\cite{mikolajczyk2005performance}. For each of the 9 source 
-		image pairs, 100 test pairs have been created.  The x-axis 
-	illustrates the accumulated returned matches for all pairs.}
+	\includegraphics[width=\columnwidth]{images/result_accumulated}
+	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
 	\label{fig:result_accumulated}
@@
 
-\begin{figure}
+To further investigate the impact of viewpoint changes, we tested the 
+algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
+contains 5 images of the same mural taken with gradually increasing 
+viewpoint changes.  The first images are almost identical, while the 
+last are taken from very different angles. The results from   \emph{MMC} 
+and \emph{SIFT} as shown in Figure~\ref{fig:result_viewpoint}, 
+confirming that \emph{MMC} is generally superior to \emph{SIFT} across 
+viewpoint changes.
+The performance of \emph{MM} (not shown in the plot) is similar to 
+\emph{MMC}.
+
+\begin{figure}[htb]
 	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewport}
-	\caption{Results on viewport changes using the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance} as image pair sources. Img 1 
-		to 6 in the \emph{Graph} set are images of the same subject but 
-		with gradually increasing viewport change. Img1 and 2 are 
-		almost identical while img1 and 6 are taken from very different 
-		angles. S is a testset of $100$ crops from img1 and img2. M is 
-	likewise but based on img1 and img3.  L is img1 and img4 and XL is 
-img1 and img5.  To decrease clutter \emph{MM} is not shown, but it 
-performs alike to \emph{MMC}}
-	\label{fig:result_viewport}
+	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
+	\caption{Results for viewpoint changes using the \emph{Graf} set from 
+		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
+	\label{fig:result_viewpoint}
 \end{figure}
 
-Figure \ref{fig:result_graf} shows the results for 100 image pairs 
-generated from img1 and img3 of the \emph{Graf} image set. The plot 
-illustrates the results of \emph{SIFT}, \emph{MM}, \emph{MMC} and 
-\emph{Isodata} as thresholds are varied over a range. \emph{Isodata} 
-performs well with strict thresholds, but when we require more matches 
-\emph{MM} and \emph{MMC} show superior results. To see if this results 
-generalizes over more image sets, we tested the four algorithms on the 
-\emph{Murals} dataset as well as the \emph{Graf} pair tested in fig.  
-\ref{fig:result_graf}. In total 900 image pairs were generated from 9 
-source pairs generating the plot shown in figure 
-\ref{fig:result_accumulated} displaying the accumulated amount of 
-matches on the x-axis. To verify that this performance is independent of 
-the magnitude of viewport change, we tested \emph{MMC} and \emph{SIFT} 
-on the \emph{Graf} image set as shown in figure 
-\ref{fig:result_viewport}. The figure confirms that \emph{MMC} is 
-generally superior across viewport changes.
+Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
+shows the results on 100 patch pairs generated 
+from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
+change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.
 
-For an example of a real life use case, figure \ref{fig:result_pitts} 
-shows the results on 100 potentially overlapping image pairs generated 
-from a typical holiday scene featuring occlusion and a slight viewport 
-change.
+\begin{figure}[htb]
+%	\makebox[0.5\textwidth][c]{%
+%		\begin{subfigure}[t]{.15\textwidth}
+%			\centering
+%			\includegraphics[width=\textwidth]{images/pitts}
+%		\end{subfigure}%
+		~%add desired spacing between images, e. g. ~, \quad, \qquad
+		%(or a blank line to force the subfigure onto a new line)
+%		\begin{subfigure}[t]{.27\textwidth}
+			\centering
+			\includegraphics[width=0.6\columnwidth]{images/result_pitts}
+			%\caption{Performance on Scharf}
+%		\end{subfigure}%
+%	}%
+	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
+	\label{fig:result_pitts}
+\end{figure}
 
-In terms of performance, table \ref{table:running_times} shows the 
-running time of the four algorithms over $100$ image pairs of $250$px by 
-$250$px. These numbers should be interpreted with the knowledge that 
+In terms of computational complexity, \emph{SIFT}, \emph{MM}, and \emph{Isodata} can be 
+implemented in $O(n\log n)$, where $n$ is the total number of feature 
+points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
+construction of a similarity matrix of the feature points. However, it is 
+possible to approximate this in $O(n\log n)$ using search trees.
+
+In terms of speed, Table~\ref{table:running_times} shows the 
+running time of the four algorithms over 100 image pairs of $250\!\times\!250$ pixels. 
+These numbers should be taken with a grain of salt, given that 
 much of the code behind \emph{MMC} and \emph{Isodata} is implemented in 
-python while \emph{MM} and \emph{SIFT} makes use of opencv to execute 
-computationally intensive operations in C++ which renders it much 
-faster. While \emph{SIFT}, \emph{MM} and \emph{Isodata} can be 
-implemented in $O(nlogn)$ where $n$ is the total amount of feature 
-points, \emph{MMC} currently has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. It is however 
-possible to approximate this in $O(nlogn)$ using search trees, something 
-that could be pursued in future work.
-%
-\begin{table}
+Python, whereas \emph{MM} and \emph{SIFT} make use of OpenCV to execute 
+computationally intensive operations in C++, which makes them much 
+faster.
+
+\begin{table}[htb]
+\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
+3.30~GHz with 8~GB memory.}
+\label{table:running_times}
 	\centering
-	\small
-\begin{tabular}{l*{4}{c}}
+%	\small
+\begin{tabular}{r*{4}{c}}
+\hline
 	Algorithm: & \emph{SIFT} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
@@
 	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
+	\hline
 \end{tabular}
-\caption{Running times as tested on a Intel(R) Core(TM) i5-3550 CPU @ 
-3.30GHz with 8Gb memory}
-\label{table:running_times}
 \end{table}
@@
 
-\begin{figure}
-	\makebox[0.5\textwidth][c]{%
-		\begin{subfigure}[t]{.15\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pitts}
-		\end{subfigure}%
-		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-		\end{subfigure}%
-	}%
-	\caption{Accuracy on an image pair from the Gallagher dataset from 
-		\cite{gallagher2008} using cropped versions of 100\_1941 and 
-		100\_1942. The plot shows the result of $100$ image pairs 
-		generated from the source images shown to the left.  The number 
-	of matches is the total number of matches for all $100$ image 
-pairs.}
-	\label{fig:result_pitts}
-\end{figure}
+\section{Summary}
+\label{S:Summary}
 
-\section{Summary}
 We have addressed the problem of matching feature points without using 
-geometrical constraints and proposed two algorithms \emph{Mirror Match 
+geometrical constraints, proposing \emph{Mirror Match 
 (MM)} and \emph{Mirror Match with Clustering (MMC)}.  The two algorithms 
-share the same common idea that feature points should have better 
+share the common idea that feature points should have better 
 matches in another image than in the image they came from to be 
-considered good matches and \emph{MMC} further improves on this idea by 
-using the structure of the similarity graph of the feature points. We 
-also address how to test the algorithms by constructing the 
-\emph{Murals} dataset consisting of $8$ source image pairs and a way to 
-generate testsets based on these pairs.  The proposed approach shows 
-promising results on both the \emph{Murals} dataset as well as a real 
-life example from the Gallagher dataset and the \emph{Graf} image set, 
-surpassing even a method using geometrical constraints when matching 
-image pairs that might not overlap.
+considered good matches.  \emph{MMC} further improves on this idea by 
+using the structure of the similarity graph of the feature points.
+
+The algorithms show promising results when tested on the \emph{Murals} data 
+set. %, where pairs of the same object seen from different angles are %cropped to have different degrees of overlap ranging from full to non at all. The results on 900 patch pairs show that 
+\emph{MM} and \emph{MMC} 
+generally outperform existing matching algorithms \emph{SIFT} and \emph{Isodata}, and \emph{MMC} 
+outperforms \emph{MM}. We show that this result generalizes to 
+variations in viewpoint change as well as more realistic photos featuring occlusions. 
+% by comparing \emph{MMC} to \emph{SIFT} over a set of image pairs with an increasing magnitude of perspective difference. 
+%We go on to apply the algorithms to a real life image case 
+%featuring occlusion and a slight viewpoint change and show that the 
+%performance of \emph{MM} and \emph{MMC} is consistent with the results 
+%on \emph{Murals}.
+
+Given the versatility of the proposed algorithms, we are planning to apply them to problems that require high 
+reliability faced with images that might not match, such as near 
+duplicate detection or face recognition.
 %

### 2013-08-01 code/panorama.py
Added a scale parameter for size

@@ -37,7 +37,10 @@ from scipy.misc import imresize
 ####################################
 
 
-def match(testset, verbose = False, threshold = 0.95) :
+def match(testset, scale = 0.5, verbose = False, threshold = 0.95) :
+
+    # Save images as greyscale
+    pylab.gray()
 
     # Get a list of all images
     paths = [testset + f for (_,_,filenames) in os.walk(testset) for f in fnmatch.filter(filenames, "*.jpg")]
@@ -62,17 +65,17 @@ def match(testset, verbose = False, threshold = 0.95) :
     g = initGraph(edges, homographies, images, paths)
 
     # Run steps and return
-    return runSteps(g)
+    return runSteps(g, scale)
 
 
-def runSteps(graph) :
+def runSteps(graph, scale = 0.5) :
     nb_vertices = graph.num_vertices()
     steps = 0
     images = graph.vp["images"]
 
     # Contract all images
     while steps < nb_vertices - 1 and graph.num_edges() > 0 :
-        step(graph)
+        step(graph, scale)
 
     # Now spit out all images left
     result = [images[v] for v in graph.vertices()]
@@ -225,10 +228,10 @@ def combine(im1, im2, h_1_2, scale = 0.5) :
         im_data[k,:] = numpy.array((x_new, y_new, im1[y,x]))
 
     # Get max and min values
-    max_x = min(numpy.max(im_data[:,0])+1, 1000)
-    max_y = min(numpy.max(im_data[:,1])+1, 1000)
-    min_x = max(numpy.min(im_data[:,0]), -1000)
-    min_y = max(numpy.min(im_data[:,1]), -1000)
+    max_x = min(numpy.max(im_data[:,0])+1, 2000)
+    max_y = min(numpy.max(im_data[:,1])+1, 2000)
+    min_x = max(numpy.min(im_data[:,0]), -2000)
+    min_y = max(numpy.min(im_data[:,1]), -2000)
 
     # Calculate padding for canvas
     padding_min_x = max(min_x,0)
@@ -282,7 +285,7 @@ def combine(im1, im2, h_1_2, scale = 0.5) :
 
 
 
-def step(graph) :
+def step(graph, scale = 0.5) :
 
     def getInv(h) :
         h_inv = numpy.linalg.inv(h)
@@ -307,7 +310,7 @@ def step(graph) :
     h_1_2 = homographies[max_edge]
 
[…]

### 2013-08-01 code/display.py
Added a few new plotting methods by suggestion of Stefan

@@ -303,6 +303,20 @@ def recallPlot(correct, total, nb_correspondences, legends, colors = ["blue", "r
     pylab.ylim(ylim[0],ylim[1])
     if xlim != None : pylab.xlim(0,xlim)
 
+def recallInvPlot(correct, total, nb_correspondences, legends, colors = ["blue", "red", "green", "orange", "cyan"], ylim=(0.0,1.01), xlim = None, size = (4,6)) :
+    fig = pylab.figure(figsize=size)
+    ax = pylab.subplot(111)
+    for ts, cs, l, color in zip(total, correct, legends, colors) :
+        ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for c, t in zip(cs,ts)]
+        xs = [sum(c)/float(nb_correspondences) for c in cs]
+        pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.95)
+        pylab.legend(loc="best")
+    removeDecoration()
+    pylab.ylabel("precision")
+    pylab.xlabel("#correct / %i" % nb_correspondences)
+    pylab.ylim(ylim[0],ylim[1])
+    if xlim != None : pylab.xlim(0,xlim)
+
 def accuPlot(correct, total, legends, colors = ["blue", "red", "green", "orange", "cyan"], ylim=(0.0,1.01), xlim = None, size = (4,6), compareCorrect = None, compareTotal = None, compareLegend = None, outside = False) :
     fig = pylab.figure(figsize=size)
     ax = pylab.subplot(111)

### 2013-08-01 code/matching.py
Update to indentation

@@ -44,7 +44,7 @@ def evaluate(match_fun, thresholds, homography, return_matches = False) :
     match_set = [match_fun(t)[0] for t in thresholds]
 
     # Get distances
-    getDist = lambda ms : [matchDistance(m1,m2,homography) for (m1,m2) in ms]
+    getDist = lambda ms : [matchDistance(m1, m2, homography) for (m1, m2) in ms]
     match_dist = [getDist(ms) for ms in match_set]
 
     if return_matches : return match_set, match_dist
@@ -69,6 +69,7 @@ def folderMatch(directory, dt, match_fun, thresholds, keypoint, descriptor) :
         print("%s " % features.getLabel(p[0])),
         return numpy.array(match_fun(dt, p, h, thresholds, keypoint, descriptor))
 
+    # Get matches
     match_sets = numpy.array([do_match(p, h) for p, h in imagePairs]).T
 
     # Now collect an x axis with nb correct matches per threshold
@@ -82,18 +83,46 @@ def folderMatch(directory, dt, match_fun, thresholds, keypoint, descriptor) :
     return nb_correct_set, nb_total_set
 
 
+def folderCorrespondences(directory, dt, keypoint, descriptor) :
+
+    # Get image pairs of folder
+    imagePairs = getImagePairs(directory)
+
+    # Calculate the number of correspondences
+    correspondences = [getCorrespondences(p, h, keypoint, descriptor, dt) for p, h in imagePairs]
+
+    return correspondences
+
+
 # Load all files
 def getImagePairs(directory) :
     dir_path = "../../images/testsets/%s/" % directory
     pairs = [dir_path + p for p in os.listdir(dir_path) if len(p) <= 6]
     homographies = [getHomography(p) for p in pairs]
-    return [([p + "_1.jpg", p + "_2.jpg"], h) for (p,h) in zip(pairs, homographies)]
+    return [([p + "_1.jpg", p + "_2.jpg"], h) for (p, h) in zip(pairs, homographies)]
 
 
 
 def getHomography(hom_path) :
     h = numpy.loadtxt(hom_path)
     return h
+
+
+def getCorrespondences(paths, homography, keypoint, descriptor, distance_threshold) :
+
+    print("%s " % features.getLabel(paths[0])),
+
+    # Get all feature points
+    indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint, descriptor_type = descriptor)
+
+    # Get all positions
[…]

### 2013-08-01 code/ratiomatch.py

@@ -52,7 +52,7 @@ def match(paths, options = {}) :
         if len(match_data) == 0 : return [], [], []
         matches, ratios, scores = zip(*match_data)
 
-        return matches, ratios, scores, (pos_im1, pos_im2)
+        return matches, ratios, scores
 
     return lambda t : match_fun(t)
 

### 2013-08-01 text/clustering.tex
report is now submitted version

@@
 \cite{das2008event}, which clusters feature points according to their 
-position in the image,
-and the method from \cite{wu2011robust}, which uses maximally stable 
-extremal regions (MSER) feature points to designate areas. %In this 
-paper the algorithm from \cite{das2008event} will later be referred to 
-as \emph{Isodata}.
+position in the image, and the method from \cite{wu2011robust}, which 
+uses maximally stable extremal regions (MSER) feature points to 
+designate areas. In this paper the algorithm from \cite{das2008event} 
+will later be referred to as \emph{Isodata}.
 
@@
 
-In practice there are many situations where relying on the geometry of the 
-image to filter correspondences is not possible, for example images without overlap, or adjacent objects in one image are that are separated in 
-another.  %Another example is images that do not overlap where algorithms might still find matches adhering to the imposed geometric constraints.
-Furthermore, methods using geometric constraints all require an initial 
-set of correspondences. If this set of correspondences can be narrowed down 
-to the most probable correct matches, the geometric matching algorithm will benefit in terms of speed and accuracy. 
-Finally some use cases might require a speed that simply cannot be achieved by 
-complex geometric methods.% where simple non geometric methods might be able to provide sufficient matching accuracy with a smaller performance penalty.
+In practice there are many situations where relying on the geometry of 
+the image to filter correspondences is not possible, for example images 
+without overlap, or adjacent objects in one image are that are separated 
+in another.  Furthermore, methods using geometric constraints all 
+require an initial set of correspondences. If this set of 
+correspondences can be narrowed down to the most probable correct 
+matches, the geometric matching algorithm will benefit in terms of speed 
+and accuracy.  Finally some use cases might require a speed that simply 
+cannot be achieved by complex geometric methods.
 
 In the absence of geometric constraints, only few methods are available.  
-As pointed out in \cite{szeliski2010}, the simplest 
-approach to matching feature points is to return all matches above a given 
-threshold of similarity.  This can be done with a fixed threshold or by 
-finding the nearest neighbors for each point (still filtering by a threshold to avoid including matches for feature points that have no counterpart in the other image).  
-Lowe \cite{lowe2004sift} proposed the scale-invariant feature transform (SIFT) together with 
-an alternative measure, where the uniqueness of a given match is found by 
-looking at the two nearest neighbors of each feature point and 
-calculating the matching score as the ratio of similarities.  Ranking the 
-scores by their uniqueness and picking the $n$ best produces a set of 
-correspondences that are distinctly matched across two images. %This method will be referred to as \emph{SIFT} in this paper. 
-Of these three methods (fixed threshold, nearest neighbors, and \emph{SIFT}), 
-\emph{SIFT} was found to perform best by a slight margin 
+As pointed out in \cite{szeliski2010}, the simplest approach to matching 
+feature points is to return all matches above a given threshold of 
+similarity.  This can be done with a fixed threshold or by finding the 
+nearest neighbors for each point (still filtering by a threshold to 
+avoid including matches for feature points that have no counterpart in 
+the other image).  Lowe \cite{lowe2004sift} proposed the scale-invariant 
+feature transform (SIFT) together with an alternative measure, where the 
+uniqueness of a given match is found by looking at the two nearest 
+neighbors of each feature point and calculating the matching score as 
+the ratio of similarities.  Ranking the scores by their uniqueness and 
+picking the $n$ best produces a set of correspondences that are 
+distinctly matched across two images.
+Of these three methods (fixed threshold, nearest neighbors, and 
+\emph{SIFT}), \emph{SIFT} was found to perform best by a slight margin 
 \cite{mikolajczyk2005performance}.
 
-The two methods we propose in this paper are inspired by a simple 
-but novel idea. If a given feature point in one image is better matched with other feature points from the 
-\emph{same} image than points in the other image, then any matches from 
-this feature point to points in the other image are considered unreliable and should be 
-discarded.  This approach carries no implicit assumptions about the 
-geometric consistency of matches and as such can easily be extended with 
-other geometric solutions when appropriate or necessary.
+The two methods we propose in this paper are inspired by a simple but 
+novel idea. If a given feature point in one image is better matched with 
+other feature points from the \emph{same} image than points in the other 
+image, then any matches from this feature point to points in the other 
+image are considered unreliable and should be discarded.  This approach 
+carries no implicit assumptions about the geometric consistency of 
+matches and as such can easily be extended with other geometric 
+solutions when appropriate or necessary.
 
-Based on this idea,  we determine reliable matches as 
-follows. \emph{Mirror Match (MM)} matches every feature from both 
-images with all other features and filters matches based on the ratio of 
-best to second best match as in \emph{SIFT}. \emph{Mirror Match with 
-Clustering (MMC)} on the other hand takes the combined set of feature 
-points from both images and clusters these points according to their 
-descriptors.  If a resulting partition contains only feature points from one image, no matches are 
-returned.  If the 
-partition contains points from both images, \emph{Mirror Match} is used 
-to find the best matches within this partition.  The experimental results 
-show that both approaches generally outperform existing 
-correspondence matching methods.
+Based on this idea,  we determine reliable matches as follows. 
+\emph{Mirror Match (MM)} matches every feature from both images with all 
+other features and filters matches based on the ratio of best to second 
+best match as in \emph{SIFT}. \emph{Mirror Match with Clustering (MMC)} 
+on the other hand takes the combined set of feature points from both 
+images and clusters these points according to their descriptors.  If a 
+resulting partition contains only feature points from one image, no 
+matches are returned.  If the partition contains points from both 
+images, \emph{Mirror Match} is used to find the best matches within this 
+partition.  The experimental results show that both approaches generally 
+outperform existing correspondence matching methods.
 
@@
 
-The paper is organized as follows.
-Section~\ref{S:MatchingMethods} describes the proposed \emph{Mirror Match (MM)} and \emph{Mirror Match with Clustering (MMC)} algorithms.
-Section~\ref{S:Experiments} presents the dataset used for evaluation and the experimental setup.
+The paper is organized as follows.  Section~\ref{S:MatchingMethods} 
+describes the proposed \emph{Mirror Match (MM)} and \emph{Mirror Match 
+with Clustering (MMC)} algorithms.  Section~\ref{S:Experiments} presents 
+the dataset used for evaluation and the experimental setup.  
 Section~\ref{S:Results} discusses the benchmarking results obtained.  
@@
 
-Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} using an example image pair from the Gallagher dataset \cite{gallagher2008}.
+Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} 
+using an example image pair from the Gallagher dataset 
+\cite{gallagher2008}.
 With \emph{SIFT} (Figure~\ref{fig:unique}), many incorrect matches occur 

### 2013-08-02 text/thesis.tex
Added thesis and changes to bibliography

--- 2013-08-01 text/clustering.tex
@@
-\documentclass[conference]{IEEEtran}
-%\documentclass{article}
+%\documentclass[report]{IEEEtran}
+\documentclass{article}
 \usepackage{footnote}
 %\usepackage[font={small}]{caption}
-%\usepackage{sidecap}
+\usepackage{sidecap}
 \usepackage{graphicx}
@@
 %\usepackage[stable]{footmisc}
-%\usepackage{caption}
-%\usepackage{adjustbox}
+\usepackage{caption}
+\usepackage{adjustbox}
 \usepackage{subcaption}
@@
 
-\title{Mirror Match: Reliable Feature Point Matching Without Geometric Constraints}
-\author{Anonymous ACPR Submission}
+\title{Reliable feature point matching}
+\author{Jonas Arnfred}
 
 \maketitle
-%
-\begin{abstract}
-Many algorithms have been proposed to solve the problem of matching 
-feature points in two or more images using geometric assumptions to 
-increase the robustness of the matching. However, very little work 
-addresses the case where these assumptions might not hold. In particular 
-few methods address the problem of reliable matching in cases where it 
-is unknown whether two images have any corresponding areas or objects in 
-the first place.
 
-We propose two algorithms for matching feature points without the use of 
-geometric constraints. The first relies on the fact that any match 
-between two images should be better than all possible matches within a 
-single image. The second algorithm extends this idea by using community 
-structure in the similarity graph of feature points to find reliable 
-correspondences. To evaluate the algorithms experimentally, we introduce 
-a simple method to generate a large amount of test cases based on a set 
-of image pairs with viewpoint changes. Our results show that the 
-proposed algorithm is generally superior to traditional approaches in 
-finding correct correspondences.
-\end{abstract}
-%
 \section{Introduction}
-%
-When matching feature points between two or more images we are often 
-faced with the problem of correctly identifying the actual 
-correspondences among many possible pairings. Several methods have been 
-proposed in the literature to solve this problem. Many approaches look 
-at the geometric configuration of feature points and match them based on 
-various assumptions about the geometric relationship between the images. 
-These assumptions are then used to create different constraints on the 
-matches, e.g.\ angular constraints \cite{kim2008efficient}, epipolar 
-constraints \cite{torr2000mlesac,chum2005matching}, or pairwise 
-constraints \cite{choi2009robust,leordeanu2005spectral}.
-%
-%When matching feature points between two or more images we are often 
-%faced with the problem of correctly identifying the actual 
-%correspondences among many possible pairings. Several methods have been 
-%proposed in the literature to solve this problem. In particular many 
-%approaches look at the geometric configuration of the feature points 
-%and match them according to assumptions made about the geometric 
-%relationship between the images matched. A simple example would be to 
-%only consider matches that aren't   too much with respect to the 
-%average angle and distancen as considered by \cite{kim2008efficient}.  
-%This performs well in situations where no camera rotation occurs 
-%between the two images, but fails when this assumption isn't met. 
-%Various scenarios have been proposed to improve on this simple 
-%assumption such as epipolar constraints (\cite{torr2000mlesac}, 
-%\cite{chum2005matching}) and pairwise constraints 
-%(\cite{choi2009robust}, \cite{leordeanu2005spectral}). The Epipolar 
-%constraint carries the assumption that the two images matched are 
-%related by an affine transformation. That is, there is no relative 
-%movement of objects in between images and either the viewpoint is fixed 
-%or the image resides entirely on a plane. In practice this assumption 
-%largely holds true when all objects we are interested in matching are 
-%roughly the same distance from the camera and when we expect to match 
-%objects that are consistently positioned across images.  Pairwise 
-%constraints provide a more robust approach to the same problem by 
-%looking at a set of proposed correspondences and defining a pairwise 
-%error between any two matches for example based on the assumption that 
-%two neighboring correspondences will usually have similar angles and 
-%distances. We can then convert the problem to an optimization problem 
-%and return a set of correspondences that minimizes this error such as 
-%proposed in \cite{choi2009robust} and \cite{leordeanu2005spectral}.  
-%This approach provides more robustness in cases where assumptions that 
-%are violated globally still hold on a local scale.
-%
-An alternative is to pick out different areas in each image and pair 
-areas when correspondence pairs are mainly found going from one area to 
-another. This allows for the filtering of all correspondences that do 
-not fall within paired areas. Examples include \emph{Isodata} 
-\cite{das2008event}, which clusters feature points according to their 
-position in the image, and the method from \cite{wu2011robust}, which 
-uses maximally stable extremal regions (MSER) feature points to 
-designate areas. In this paper the algorithm from \cite{das2008event} 
-will later be referred to as \emph{Isodata}.
+What is the subject of this thesis and in what part lies my 
+contribution?
+How is the report organized?
 
-%proposes clustering feature points by using their geometric position 
-%and exclude correspondences that are geometrically deviant. A more 
-%sophisticated approach is introduced in \cite{wu2011robust} where the 
-%areas are created by using the MSER feature detector to find areas of 
-%interest in the images. These areas can be defined as an ellipse with a 
-%certain radius around the interest points. The feature points that fall 
-%within this ellipse are then matched according to epipolar constraints.
+\section{Background}
+Introduction to Computer Vision
+ - Introduce common tasks that we are good at that computers aren't
+ - Single in on tasks that we can solve using feature points
 
-In practice there are many situations where relying on the geometry of 
-the image to filter correspondences is not possible, for example images 
-without overlap, or adjacent objects in one image are that are separated 
-in another.  Furthermore, methods using geometric constraints all 
-require an initial set of correspondences. If this set of 
-correspondences can be narrowed down to the most probable correct 
-matches, the geometric matching algorithm will benefit in terms of speed 
-and accuracy.  Finally some use cases might require a speed that simply 
-cannot be achieved by complex geometric methods.
+Introduction to feature points
+ - Global explanation of what they are and how they serve to solve the 
+problems mentioned before
+ - How do we find them? (Examples making it intuitive why corners are 
+nice)
+ - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
+ Scale, \ldots, Affine)
+ - Introduce SIFT and explain how the different problems are tackled in 
+SIFT)
+ - Talk about other methods and how they are different
 
-In the absence of geometric constraints, only few methods are available.  
-As pointed out in \cite{szeliski2010}, the simplest approach to matching 
-feature points is to return all matches above a given threshold of 
-similarity.  This can be done with a fixed threshold or by finding the 
-nearest neighbors for each point (still filtering by a threshold to 
-avoid including matches for feature points that have no counterpart in 
-the other image).  Lowe \cite{lowe2004sift} proposed the scale-invariant 
-feature transform (SIFT) together with an alternative measure, where the 
-uniqueness of a given match is found by looking at the two nearest 
-neighbors of each feature point and calculating the matching score as 
-the ratio of similarities.  Ranking the scores by their uniqueness and 
-picking the $n$ best produces a set of correspondences that are 
-distinctly matched across two images.
-Of these three methods (fixed threshold, nearest neighbors, and 
-\emph{SIFT}), \emph{SIFT} was found to perform best by a slight margin 
-\cite{mikolajczyk2005performance}.
+Matching feature points
+ - What applications require matching?
+ - How is matching usually done
+ - Segue into related work from paper
 
-The two methods we propose in this paper are inspired by a simple but 
-novel idea. If a given feature point in one image is better matched with 
-other feature points from the \emph{same} image than points in the other 
-image, then any matches from this feature point to points in the other 
-image are considered unreliable and should be discarded.  This approach 
-carries no implicit assumptions about the geometric consistency of 
-matches and as such can easily be extended with other geometric 
-solutions when appropriate or necessary.
+\section{Matching feature points}
+Basically c/p from paper, but better figures and maybe more explanations
+ - Add path about graphs and how they are formed. Make sure to explain 
+ the clustering in more detail and make it easier to understand
+ - Add a good explanation for new figures and how the precision and 
+ recall are calculated. This should appear somewhere before results.
+ - Add part on spectral matching and modify accordingly. Make sure to 
+ underline how the second plot shows how the geometric method is 
+ independent of MMC and that they combined yield greater results.
 
-Based on this idea,  we determine reliable matches as follows. 
-\emph{Mirror Match (MM)} matches every feature from both images with all 
-other features and filters matches based on the ratio of best to second 
-best match as in \emph{SIFT}. \emph{Mirror Match with Clustering (MMC)} 
-on the other hand takes the combined set of feature points from both 
-images and clusters these points according to their descriptors.  If a 
-resulting partition contains only feature points from one image, no 
-matches are returned.  If the partition contains points from both 
-images, \emph{Mirror Match} is used to find the best matches within this 
-partition.  The experimental results show that both approaches generally 
-outperform existing correspondence matching methods.
-
-%Matching feature points against the entire set of points from both 
-%images ensures that the distinctiveness of a returned correspondence is 
-%higher. In almost all cases\footnote{Exceptions would include cases 
-%where we want to find all particular points in a pattern and other use 
-%cases where the correspondence isn't assumed to be unique}, a good 
-%match between two images is unambiguous in the sense that there are no 
-%other equally good potential matches to the same point.  This is the 
-%key insight behind the algorithm presented by Lowe in 
-%\cite{lowe2004sift}.  However the implication doesn't follow the other 
-%way around. In the case that a feature point doesn't have a true 
-%correspondence there might still exist point with which the feature 
-%point is uniquely matched. The issue is particularly pronounced if we 
-%compare two images that do not correspond. For any proposed 
-%correspondence it is entirely probable that this correspondence is 
-%unique even if it isn't correct. When we match against the feature 
-%points of both images this ambiguity is avoided.  When the two images 
-%have no overlap or objects in common, chances are that a feature point 
-%will match better with another feature point from the same image in 
-%which case it is easily discarded.
-%
-%Often images will contain repetitive patterns that are difficult to 
-%match\footnote{In fact this particular problem has been given attention 
-%before by for example \cite{fan2011towards}} because the feature 
-%descriptors covering these patterns will be similar. If we remove points 
-%that aren't deemed sufficiently unique like in \emph{MM} this means that 
-%these points will often be discarded even if they are correctly matched.
-%\emph{MMC} makes it possible to look at groups of similar feature points 
-%one at a time and within each group find the best matches. This is done 
-%by taking the set of feature points from both images and cluster them by 
-%their similarity. In some cases the clustering will end up grouping 
-%feature points of only one image together which can then easily be 
-%discarded in the matching process.  In other cases partitions will 
-%contain similar feature points from both images that can then be matched 
-%using \emph{MM} but with much lower thresholds.
-%
-
-The paper is organized as follows.  Section~\ref{S:MatchingMethods} 
-describes the proposed \emph{Mirror Match (MM)} and \emph{Mirror Match 
-with Clustering (MMC)} algorithms.  Section~\ref{S:Experiments} presents 
-the dataset used for evaluation and the experimental setup.  
-Section~\ref{S:Results} discusses the benchmarking results obtained.  
-Section~\ref{S:Summary} concludes the paper.
-
-\section{Matching Methods}
+\subsection{Proposed Matching Methods}
 \label{S:MatchingMethods}
 
-\subsection{Mirror Match (\emph{MM})}
+\subsubsection{Mirror Match (\emph{MM})}
 
@@
 
-\subsection{Mirror Match with Clustering (\emph{MMC})}
+\subsubsection{Mirror Match with Clustering (\emph{MMC})}
 %
@@
 %
-%\subsubsection{Graph Clustering}
+%\subsubsubsection{Graph Clustering}
 %
@@
 		\includegraphics[width=\columnwidth]{images/MMC_graph_cropped}
-		\caption{Cropped Section of Graph}
+		\caption{Cropped subsection of Graph}
 		\label{fig:cropped_graph}
@@
 		points. A partition is a connected group with the same color. The border color of each node 
-		indicates which image it belongs to.  Zooming into a section of the graph (b), the various cluster sizes can be seen, ranging from 
+		indicates which image it belongs to.  Zooming into a subsection of the graph (b), the various cluster sizes can be seen, ranging from 
 	hundreds of feature points to only two or three.}
@@
 We use the Louvain Method \cite{blondel2008} for clustering feature 
-points, since it is relatively fast and performs 
-well \cite{lancichinetti2009}, does not require 
-parameters \cite{blondel2008}, and does not emphasize partitions of equal 
-size, as opposed to spectral clustering or 
-k-means \cite{von2007}, for example.
-While the Louvain clustering algorithm does not require any parameters in 
-itself, it tends towards clustering all feature points together in the 
-same partition if the graph is very connected.  To ensure that the graph 
-is well clustered, the adjacency matrix is pruned so that only edges above a 
-certain threshold are kept. From empirical analysis, retaining the top 
-2.5\% of edges with the highest similarity seems to work well in 
-practice. Figure~\ref{fig:graph} shows the result of clustering the 
-feature points as a graph.
+points, since it is relatively fast and performs well 
+\cite{lancichinetti2009}, does not require parameters 
+\cite{blondel2008}, and does not emphasize partitions of equal size, as 
+opposed to spectral clustering or k-means \cite{von2007}, for example.
+While the Louvain clustering algorithm does not require any parameters 
+in itself, it tends towards clustering all feature points together in 
+the same partition if the graph is very connected.  To ensure that the 
+graph is well clustered, the adjacency matrix is pruned so that only 
+edges above a certain threshold are kept. From empirical analysis, 
+retaining the top 2.5\% of edges with the highest similarity seems to 
+work well in practice. Figure~\ref{fig:graph} shows the result of 
+clustering the feature points as a graph.
 %
@@
 
-\section{Experiments}
+\subsection{Experiments}
 \label{S:Experiments}
@@
 %
-%\subsection{Experimental setup}
+%\subsubsection{Experimental setup}
 We compare the \emph{MM} and \emph{MMC} algorithms to 
@@
 
-\section{Results}
+\subsection{Results}
 \label{S:Results}
@@
 
+\section{Applications}
+
+\subsection{Panorama Recognition and Alignment}
+One of the oldest practical problems approached in computer vision is 
+the automatic stitching of several source images into a bigger image, 
+such as panoramas and composite satellite photos\footnote{A brief 
+overview of the history of image stitching can be found in Szeliski's 
+book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
+As part of the process of stitching together images, the individual 
+images must be aligned and often transformed in perspective. Earlier 
+methods relied on minimizing pixel dissimilarities in overlapping images 
+while more recent methods have used local feature points to estimate the 
+correct image alignment. Using local feature points carry the additional 
+advantage that it is feasible to automatically recognize where each 
+source image belong in the final panorama.
+
+In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
+image can be assembled by collecting the feature points of all source 
+images and matching them to obtain a set of inter image matches.  By 
+using \emph{RANSAC}\footnote{RANdom SAmple Consensus, an iterative 
+    algorithm to estimate parameters from noisy data introduced in 
+Fischler and Bolles in 1981 \cite{fischler1981ransac}} to find matches 
+deemed as inliers between image pairs, they are able to recognize image 
+neighbors and align them to construct the final panorama.
+
+This process hinges on the effectiveness of the matching algorithm used 
+to match the feature points. Not only is it important that true pairs 
+are accurately matched, but since we are matching points in image pairs 
+that might not be adjacent in the final panorama, we also need to make 
+sure that we consistently reject false positives, i.e.\ proposed matches 
+that link feature points which don't correspond.
+
+To demonstrate the usefulness of \emph{MMC} applied to panorama 
+recognition and alignment we construct a simple panorama stitcher taking
+as input a set of $n$ source images $\left{I_0, \ldots, I_n\right}$ and 
+returns as output a panoramic image stitched together from the source 
+images. Based on the matches found by applying \emph{MMC} to $I$, the 
+images are combined in an order corresponding to how many matches 
+connect them, as done by Brown and Lowe \cite{brown2007automatic}.
+
+Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
+provides a way to globally optimize the accuracy of the image alignment} 
+and a lot of image enhancements such as exposure adjustment and edge 
+blurring to provide a seamless panorama. While these additions improve 
+the end product, they don't influence the performance of panorama 
+alignment and recognition and haven't been included in the simple 
+comparison algorithm.
+
+% About near duplicates mention how we can't use ransac to find inliers 
+% since we can't necessarily construct a homography between two images
+
+When we are performing panorama alignment and recognition with feature 
+points, oth recognition and alignment of the source images is
+
+There are two important steps to image stitching which i- Describe in 
+general why better matching improves the results and speed on a broad 
+range of different computer vision problems
+ - Elaborate on why the two examples where chosen (are there any 
+ particular reasons?)
+ - Near duplicate detection
+ - Panorama application
+
 \section{Summary}
@@
 %
+
 \bibliographystyle{IEEEtran}

### 2013-08-05 text/thesis.tex
Included figure for panorama

@@
 recognition and alignment we construct a simple panorama stitcher taking
-as input a set of $n$ source images $\left{I_0, \ldots, I_n\right}$ and 
-returns as output a panoramic image stitched together from the source 
-images. Based on the matches found by applying \emph{MMC} to $I$, the 
-images are combined in an order corresponding to how many matches 
+as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
+and returns as output a panoramic image stitched together from the 
+source images. Based on the matches found by applying \emph{MMC} to $I$, 
+the images are combined in an order corresponding to how many matches 
 connect them, as done by Brown and Lowe \cite{brown2007automatic}.
@@
 comparison algorithm.
+
+\begin{figure}[h]
+	\begin{subfigure}[t]{0.8\columnwidth}
+		\centering
+		\includegraphics[width=\columnwidth]{images/pano_narrow}
+		\caption{Source images}
+		\label{fig:pano_images}
+	\end{subfigure}%
+	\\
+	\centering
+	\begin{subfigure}{0.4\columnwidth}
+		\includegraphics[width=\columnwidth]{images/panorama-autostitch}
+		\caption{Panorama by Autostitch}
+		\label{fig:pano_autostitch}
+	\end{subfigure}%
+	~%add desired spacing between images, e. g. ~, \quad, \qquad
+	%(or a blank line to force the subfigure onto a new line)
+	\begin{subfigure}{0.4\columnwidth}
+		\includegraphics[width=\columnwidth]{images/panorama-MMC}
+		\caption{Panorama by MMC}
+		\label{fig:pano_MMC}
+	\end{subfigure}%
+	\caption{An example of a difficult case of panorama recognition and 
+		alignment.  In a) the source images used to generate the 
+		panorama are displayed.\ b) shows the result of the Autostitch 
+		program from \cite{brown2007automatic} which fails to combine 
+		all images, while c) demonstrates the result of the simple 
+		panorama stitcher
+	using the proposed MMC algorithm. Here the two left images are 
+correctly linked}
+	\label{fig:pano_example}
+\end{figure}
 

### 2013-08-05 text/thesis.tex
Added a few figures and some more text about panorama

@@
 Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
-%
-%Before we introduce the implementation details we will go over the 
-%problem of graph clustering and how it relates to feature matching.
-%
-%\subsubsubsection{Graph Clustering}
-%
-%Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-%\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-%function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-%points in an image and returns their matching score, we can define a 
-%matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-%as the \emph{adjecency matrix} of the fully connected graph where each 
-%vertex corresponds to a keypoint and the edge between two vertices has a 
-%weight equal to the distance between the two corresponding keypoints.
-%
-%This representation reduces the problem of partitioning the keypoints 
-%into groups to that of graph clustering or community structure depending 
-%on the context. In the literature there are various ways of clustering a 
-%graph according to different measures of what constitutes an optimal 
-%partitioning. Traditionally the most used clustering algorithms have 
-%been K-means and spectral clustering, but in recent years a host of new 
-%algorithms have been proposed based on both Newman's concept of graph 
-%modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-%\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-%well as information theoretical measures\footnote{See for example 
-%\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-%in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-%new algorithms differ from K-means clustering and Spectral clustering 
-%in that they do not require the number of expected to clusters to be 
-%specified beforehand\footnote{Among the aforementioned methods, this is 
-%true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-%tests done using randomly generated graphs with a known partitioning 
-%\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-%markedly better than spectral clustering and 
-%K-means\cite{lancichinetti2009}.
-%
-%The performance of clustering algorithms is a complicated issue, since 
-%an optimal clustering given the same graph can vary depending on the 
-%application. Spectral clustering for example will usually return a 
-%partitioning where each partition is roughly equal in size\footnote{As 
-%mentioned in \cite{von2007}} while the Louvain 
-%clustering\cite{blondel2008} might return partitions of very uneven 
-%size, even if the modularity measurement has been shown to penalize very 
-%small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-%depending on the application, but when clustering feature points, 
-%maintaining clusters of an even size usually means that some clusters 
-%will be '\emph{catch-all}' clusters where the feature points that do 
-%not fit anywhere else are grouped together. The necessity of specifying 
-%the amount of partitions in for example Spectral clustering or Pott's 
-%model clustering further exacerbates the issue since smaller partitions 
-%are then combined into one to achieve the right amount of partitions.
-%
+
+Before we introduce the implementation details we will go over the 
+problem of graph clustering and how it relates to feature matching.
+
+Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
+\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
+function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
+points in an image and returns their matching score, we can define a 
+matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
+as the \emph{adjecency matrix} of the fully connected graph where each 
+vertex corresponds to a keypoint and the edge between two vertices has a 
+weight equal to the distance between the two corresponding keypoints.
+
+This representation reduces the problem of partitioning the keypoints 
+into groups to that of graph clustering or community structure depending 
+on the context. In the literature there are various ways of clustering a 
+graph according to different measures of what constitutes an optimal 
+partitioning. Traditionally the most used clustering algorithms have 
+been K-means and spectral clustering, but in recent years a host of new 
+algorithms have been proposed based on both Newman's concept of graph 
+modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
+\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
+well as information theoretical measures\footnote{See for example 
+\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
+in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
+new algorithms differ from K-means clustering and Spectral clustering 
+in that they do not require the number of expected to clusters to be 
+specified beforehand\footnote{Among the aforementioned methods, this is 
+true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
+tests done using randomly generated graphs with a known partitioning 
+\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
+markedly better than spectral clustering and 
+K-means\cite{lancichinetti2009}.
+
+The performance of clustering algorithms is a complicated issue, since 
+an optimal clustering given the same graph can vary depending on the 
+application. Spectral clustering for example will usually return a 
+partitioning where each partition is roughly equal in size\footnote{As 
+mentioned in \cite{von2007}} while the Louvain 
+clustering\cite{blondel2008} might return partitions of very uneven 
+size, even if the modularity measurement has been shown to penalize very 
+small clusters\cite{brandes2007}. Both behaviours can be beneficial 
+depending on the application, but when clustering feature points, 
+maintaining clusters of an even size usually means that some clusters 
+will be '\emph{catch-all}' clusters where the feature points that do 
+not fit anywhere else are grouped together. The necessity of specifying 
+the amount of partitions in for example Spectral clustering or Pott's 
+model clustering further exacerbates the issue since smaller partitions 
+are then combined into one to achieve the right amount of partitions.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
     \centering
-	\begin{subfigure}{0.8\columnwidth}
-		\includegraphics[width=\columnwidth]{images/MMC_graph_full}
-		\caption{Full Graph}
-		\label{fig:full_graph}
-	\end{subfigure}%
-
-	%add desired spacing between images, e. g. ~, \quad, \qquad		  
-	%(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}{0.7\columnwidth}
-		\includegraphics[width=\columnwidth]{images/MMC_graph_cropped}
-		\caption{Cropped subsection of Graph}
-		\label{fig:cropped_graph}
-	\end{subfigure}%
-	\caption{The partitioned feature graph (a). Each vertex represents a 
-		feature point; lines indicate high similarity between 
-		points. A partition is a connected group with the same color. The border color of each node 
-		indicates which image it belongs to.  Zooming into a subsection of the graph (b), the various cluster sizes can be seen, ranging from 
-	hundreds of feature points to only two or three.}
+\makebox[\textwidth][c]{%
+    \includegraphics[width=1.1\textwidth]{images/MMC_graph}
+    \label{fig:graph}
+}
+    \caption{The partitioned feature graph. Each vertex represents a 
+        feature point; lines indicate high similarity between points. A 
+        partition is a connected group with the same color. The border 
+        color of each node indicates which image it belongs to.  Zooming 
+    into a subsection of the graph (right part), the various cluster 
+sizes can be seen, ranging from hundreds of feature points to only two 
+or three.}
 	\label{fig:graph}
@@
 
+\begin{figure}[h]
+	\begin{subfigure}[t]{0.8\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/pano_narrow}
+        \label{fig:pano_images}
+		\caption{Source images}
+    \end{subfigure}%
+	\\
+	\centering
+	\begin{subfigure}{0.4\textwidth}
+		\includegraphics[width=\textwidth]{images/panorama-autostitch}
+        \label{fig:pano_autostitch}
+		\caption{Panorama by Autostitch}
+    \end{subfigure}%
+	~%add desired spacing between images, e. g. ~, \quad, \qquad
+	%(or a blank line to force the subfigure onto a new line)
+	\begin{subfigure}{0.4\textwidth}
+		\includegraphics[width=\textwidth]{images/panorama-MMC}
+		\caption{Panorama by MMC}
+		\label{fig:pano_MMC}
+	\end{subfigure}%
+    \label{fig:pano_example}
+	\caption{An example of a difficult case for panorama recognition and 
+		alignment.  In a) the source images used to generate the 
+		panorama are displayed.\ b) shows the result of the Autostitch 
+		program from \cite{brown2007automatic} which fails to combine 
+		all images, while c) demonstrates the result of the simple 
+		panorama stitcher
+	using the proposed MMC algorithm. Here the two left images are 
+correctly linked}
+\end{figure}
+
 In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
@@
 
-\begin{figure}[h]
-	\begin{subfigure}[t]{0.8\columnwidth}
-		\centering
-		\includegraphics[width=\columnwidth]{images/pano_narrow}
-		\caption{Source images}
-		\label{fig:pano_images}
-	\end{subfigure}%
-	\\
-	\centering
-	\begin{subfigure}{0.4\columnwidth}
-		\includegraphics[width=\columnwidth]{images/panorama-autostitch}
-		\caption{Panorama by Autostitch}
-		\label{fig:pano_autostitch}
-	\end{subfigure}%
-	~%add desired spacing between images, e. g. ~, \quad, \qquad
-	%(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}{0.4\columnwidth}
-		\includegraphics[width=\columnwidth]{images/panorama-MMC}
-		\caption{Panorama by MMC}
-		\label{fig:pano_MMC}
-	\end{subfigure}%
-	\caption{An example of a difficult case of panorama recognition and 
-		alignment.  In a) the source images used to generate the 
-		panorama are displayed.\ b) shows the result of the Autostitch 
-		program from \cite{brown2007automatic} which fails to combine 
-		all images, while c) demonstrates the result of the simple 
-		panorama stitcher
-	using the proposed MMC algorithm. Here the two left images are 
-correctly linked}
-	\label{fig:pano_example}
-\end{figure}
+Figure~\ref{fig:pano_example} shows an example where the added accuracy 
+of MMC enables us to correctly recognitize and align source images that 
+fail to be combined by Autostitch, a program using the algorithm 
+proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
+case the matching algorithm used in Autostitch fails to find sufficient 
+matches between two images pairs to correctly position them and fails to
+produce a panorama as a result.
 

### 2013-08-06 text/thesis.tex
Added section about near duplicate detection

@@
 case the matching algorithm used in Autostitch fails to find sufficient 
-matches between two images pairs to correctly position them and fails to
-produce a panorama as a result.
+matches between two images pairs to correctly position them and 
+consequently doesn't produce a panorama containing all images as a 
+result.
+
+This example illustrates how an improved matching algorithm can be 
+applied to panorama recognition and alignment to allow for panoramas 
+created with images that have little overlap.
+% Maybe find example of images with identical features that would be 
+% hard to match?
+
+\subsection{Near Duplicate Detection}
+Both with regards to corporate intellectual property as well as consumer 
+photo albums, being able to automatically find near duplicates of images 
+provides useful across several scenarios. A company might be interested 
+in finding images that are derived from their intellectual property, 
+while consumers taking vacation photos might be interested in grouping 
+duplicate images to allow for easier photo organization.
+
+Local features are often used to group similar images, either by looking
+at a histogram of descriptors \cite{wu2009bundling} or by looking at how
+well feature points match between images \cite{zhao2009scale},
+\cite{chu2010consumer}, \cite{vas2013cluster}. In the latter case 
+finding near duplicates means that we will be matching image pairs that 
+might or might not contain any actual matches. In this case we would 
+benefit from a reliable matching algorithm that minimizes false 
+positives, which is a characteristic of both \emph{MM} and \emph{MMC}.
+
+The PhotoCluster method introduced by Vonikakis et al.  
+\cite{vas2013cluster} shows the best clustering performance on the 
+California-nd dataset \cite{jinda2012california} which contains a set of
+annotated vacation images similar to a typical photo album in a consumer
+product. PhotoCluster works by grouping images in several steps using 
+first image metadata and global features to obtain a set of proposed 
+clusters. Then local features are used to find the best matching images 
+in these proposed clusters yielding the final groups of near duplicate 
+images. To show the viability of \emph{MMC} in the application of near 
+duplicated detection, we modify the PhotoCluster method to use 
+\emph{MMC} for matching images instead of \emph{Ratio} which was 
+previously used. Due to the time consumption of \emph{MMC}, all images 
+where resized to to 10\% before being compared. Outside of that, the 
+experiments were performed exactly as documented in 
+\cite{vas2013cluster}.
+
+\begin{table}[htb]
+\caption{Results from Near Duplicate Detection at 10\% scale}
+\label{table:ndd}
+	\centering
+%	\small
+\begin{tabular}{r*{2}{r}}
+\hline
+    Method: & Ratio & MMC   \\
+	\noalign{\smallskip}
+	%
+    F1 score: & 0.4654 & 0.5459 \\
+	\hline
+\end{tabular}
+\end{table}
+
+The results of the comparison can be seen in Table~\ref{table:nnd} where
+\emph{MMC} improves performance by 8.05\% over the original framework 
+using \emph{Ratio} to match images.
 
@@
 % since we can't necessarily construct a homography between two images
-
-When we are performing panorama alignment and recognition with feature 
-points, oth recognition and alignment of the source images is
 

### 2013-08-06 text/thesis.tex
Added introduction to applications

@@
 
+In many areas of computer vision matching local feature points is a key 
+component, and matching algorithms have applications in problems such as
+scene matching, object recognition, near duplicate detection and 
+panorama recognition. To show the practical applications of the proposed 
+matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
+improve existing methods in near duplicate detection and panorama 
+recognition. These two problems were chosen because they both involve 
+matching images that might or might not overlap. These cases requires 
+matching algorithms that limit false positives since e.g. returning the 
+top $n$ matches for any given image pair would make it hard to 
+distinguish adjacent or duplicate images from non-adjacent or dissimilar
+image pairs. Near duplicate detection also constraints normal matching 
+algorithms from relying on geometric assumptions, since we have very few
+guarantees between two potential near duplicates that they should be 
+matched using any particular geometric heuristic. In this section, we 
+will first see \emph{MMC} applied to panorama recognition and alignment,
+and next \emph{MMC} and \emph{MM} applied to near duplicate detection.
+
 \subsection{Panorama Recognition and Alignment}
@@
 \emph{MMC} improves performance by 8.05\% over the original framework 
-using \emph{Ratio} to match images.
-
-% About near duplicates mention how we can't use ransac to find inliers 
-% since we can't necessarily construct a homography between two images
-
-There are two important steps to image stitching which i- Describe in 
-general why better matching improves the results and speed on a broad 
-range of different computer vision problems
- - Elaborate on why the two examples where chosen (are there any 
- particular reasons?)
- - Near duplicate detection
- - Panorama application
+using \emph{Ratio} to match images. For comparison, the performance 
+improvement of \emph{PhotoCluster} compared to XMatch 
+\cite{zhao2009scale}, the second best performing algorithm on the 
+California-nd dataset according to \cite{vas2013cluster} is 2.52\%.
 

### 2013-08-06 text/thesis.tex
Modified summary

@@
 			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
-			\caption{\emph{SIFT}}
+			\caption{\emph{Ratio}}
 			\label{fig:unique}
@@
 Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-	(c) Result of \emph{SIFT} matching. 
+	(c) Result of \emph{Ratio} matching. 
   (d) All matches found by \emph{MM}, including intra-image matches. 
@@
 %			\includegraphics[width=\textwidth]{images/mirror_match_off}
-%			\caption{\emph{SIFT}}
+%			\caption{\emph{Ratio}}
 %			\label{fig:unique}
@@
 Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-%(c) Result of \emph{SIFT} matching the two images.% 
+%(c) Result of \emph{Ratio} matching the two images.% 
 %  (d) All matches found by \emph{MM}, including matches between points in the same image. 
@@
 \cite{gallagher2008}.
-With \emph{SIFT} (Figure~\ref{fig:unique}), many incorrect matches occur 
+With \emph{Ratio} (Figure~\ref{fig:unique}), many incorrect matches occur 
 in the fence towards the bottom of the image.
@@
 second best match and remove matches where this ratio lies above a 
-certain threshold, like in the \emph{SIFT} algorithm. For example in the 
+certain threshold, like in the \emph{Ratio} algorithm. For example in the 
 case of Figure~\ref{fig:pitts_partition}, we have feature points from a 
@@
 We compare the \emph{MM} and \emph{MMC} algorithms to 
-\emph{SIFT} \cite{lowe2004sift} as well 
+\emph{Ratio} \cite{lowe2004sift} as well 
 as \emph{Isodata} \cite{das2008event}. 
-\emph{Isodata} uses geometric constraints, whereas \emph{SIFT} does not.
+\emph{Isodata} uses geometric constraints, whereas \emph{Ratio} does not.
 %, which uses geometric information to improve the matching. 
-%The comparison  with \emph{SIFT} serves to illustrate the relative performance of 
+%The comparison  with \emph{Ratio} serves to illustrate the relative performance of 
 %\emph{MM} and \emph{MMC} to a state of the art algorithm without 
@@
 generated from images 1 and 3 of the \emph{Graf} image set (cf.~Figure~\ref{fig:Graf}). The plot 
-compares the accuracy of \emph{SIFT}, \emph{MM}, \emph{MMC}, and 
+compares the accuracy of \emph{Ratio}, \emph{MM}, \emph{MMC}, and 
 \emph{Isodata} as a function of the number of matches produced (which is achieved by varying thresholds over a certain range).
-The results show that \emph{MM} and \emph{MMC} consistently outperform \emph{SIFT}; \emph{MMC} generally lies 2-3 percentage points above \emph{MM} when both are performing at optimal accuracy.
+The results show that \emph{MM} and \emph{MMC} consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 percentage points above \emph{MM} when both are performing at optimal accuracy.
 Although \emph{Isodata} exhibits a good performance on strict thresholds (small number of matches), that quickly diminishes when more matches are desired.
@@
 last are taken from very different angles. The results from   \emph{MMC} 
-and \emph{SIFT} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{SIFT} across 
+and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
+confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
 viewpoint changes.
@@
 
-In terms of computational complexity, \emph{SIFT}, \emph{MM}, and \emph{Isodata} can be 
+In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isodata} can be 
 implemented in $O(n\log n)$, where $n$ is the total number of feature 
@@
 much of the code behind \emph{MMC} and \emph{Isodata} is implemented in 
-Python, whereas \emph{MM} and \emph{SIFT} make use of OpenCV to execute 
+Python, whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
 computationally intensive operations in C++, which makes them much 
@@
 \hline
-	Algorithm: & \emph{SIFT} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
+	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
 	\\
@@
 will first see \emph{MMC} applied to panorama recognition and alignment,
-and next \emph{MMC} and \emph{MM} applied to near duplicate detection.
+and next \emph{MM} and \emph{MMC} applied to near duplicate detection.
 
@@
 \begin{figure}[h]
-	\begin{subfigure}[t]{0.8\textwidth}
+	\begin{subfigure}[t]{0.9\textwidth}
 		\centering
-		\includegraphics[width=\textwidth]{images/pano_narrow}
+        \includegraphics[width=\textwidth]{images/pano_wide}
         \label{fig:pano_images}
@@
 	\centering
-	\begin{subfigure}{0.4\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
 		\includegraphics[width=\textwidth]{images/panorama-autostitch}
@@
 	%(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}{0.4\textwidth}
+    \begin{subfigure}[b]{0.4\textwidth}
 		\includegraphics[width=\textwidth]{images/panorama-MMC}
@@
 
-The results of the comparison can be seen in Table~\ref{table:nnd} where
-\emph{MMC} improves performance by 8.05\% over the original framework 
-using \emph{Ratio} to match images. For comparison, the performance 
-improvement of \emph{PhotoCluster} compared to XMatch 
+The results of the comparison can be seen in Table~\ref{table:nnd}. It 
+shows that \emph{MMC} improves performance by 8.05\% over the original 
+framework using \emph{Ratio} to match images. For comparison, the 
+performance improvement of \emph{PhotoCluster} compared to XMatch 
 \cite{zhao2009scale}, the second best performing algorithm on the 
-California-nd dataset according to \cite{vas2013cluster} is 2.52\%.
+California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.
 
@@
 
-We have addressed the problem of matching feature points without using 
-geometrical constraints, proposing \emph{Mirror Match 
-(MM)} and \emph{Mirror Match with Clustering (MMC)}.  The two algorithms 
-share the common idea that feature points should have better 
-matches in another image than in the image they came from to be 
-considered good matches.  \emph{MMC} further improves on this idea by 
-using the structure of the similarity graph of the feature points.
+This thesis has addressed the problem of matching feature points without 
+using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
+\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
+common idea that feature points should have better matches in another 
+image than in the image they came from to be considered good matches.  
+\emph{MMC} further improves on this idea by using the structure of the 
+similarity graph of the feature points.
 
-The algorithms show promising results when tested on the \emph{Murals} data 
-set. %, where pairs of the same object seen from different angles are %cropped to have different degrees of overlap ranging from full to non at all. The results on 900 patch pairs show that 
-\emph{MM} and \emph{MMC} 
-generally outperform existing matching algorithms \emph{SIFT} and \emph{Isodata}, and \emph{MMC} 
+The algorithms show promising results when tested on the \emph{Murals} 
+data set. The results on 900 image pairs show that \emph{MM} and 
+\emph{MMC} generally outperform existing matching algorithms 
+\emph{Ratio}, \emph{Isodata} and \emph{Spectral}. In addition \emph{MMC} 
 outperforms \emph{MM}.  We show that this result generalizes to 
-variations in viewpoint change as well as more realistic photos featuring occlusions. 
-% by comparing \emph{MMC} to \emph{SIFT} over a set of image pairs with an increasing magnitude of perspective difference. 
-%We go on to apply the algorithms to a real life image case 
-%featuring occlusion and a slight viewpoint change and show that the 
-%performance of \emph{MM} and \emph{MMC} is consistent with the results 
-%on \emph{Murals}.
+variations in viewpoint change by comparing \emph{MMC} to \emph{Ratio} 
+over a set of image pairs with an increasing magnitude of perspective 
+difference. We go on to apply the algorithms to a real life image case 
+featuring occlusion and a slight viewpoint change and show that the 
+performance of \emph{MM} and \emph{MMC} is consistent with the results 
+on \emph{Murals}. To show that \emph{MM} or \emph{MMC}
+can further improve the results of a geometrical method, we create 
+\emph{Spectral-MMC} by combining \emph{Spectral} and \emph{MMC} and 
+compare the three on the full \emph{Murals} dataset where it yields 
+results better than both \emph{Spectral} and \emph{MMC}.
 
-Given the versatility of the proposed algorithms, we are planning to apply them to problems that require high 
-reliability faced with images that might not match, such as near 
-duplicate detection or face recognition.
+The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
+applying the algorithms to the problems of near duplicate detected and 
+for the case of \emph{MMC} to panorama recognition and alignment. For 
+the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
+improvement over the state of the art \emph{Ratio} in a near duplicate 
+detection framework making use of local features. Similarly for panorama 
+recognition and alignment a simple panorama stitching method based on 
+\emph{MMC} succeeds in cases where Autostitch is unable to recognize and 
+align the source images correctly. Both applications illustrate the 
+central role that performance of the matching algorithm has on tasks 
+that makes use of local features to match image pairs with potential 
+overlap.
 %

### 2013-08-07 text/thesis.tex
Added a few algorithms

@@
 %
-%\begin{figure}
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{0.24\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%	}%
-%	\\
-%	\makebox[0.5\textwidth][c]{
-%		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		
-%		\begin{subfigure}[t]{0.5\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{A Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Example of a partition of keypoints in an image pair. The 
-%		partition shown contains window corners from a building in the 
-%		left image and similar corners on the shirt in the right image.  
-%	}
-%	\label{fig:compare_mirror}
-%\end{figure}
-%
-%The matching algorithm for \emph{MMC} (algorithm \ref{alg-getmatches}) 
-%goes through the partitions one by one and selects matches in the 
-%following way: If the partition has no edges going from a feature point 
-%in one image to a feature point in another image, the partition is 
-%discarded. If we have more than one edge going between images then 
-%$getMatches$ will behave as \emph{MM} and make sure that a 
-%correspondence is symmetric, that it has a ratio above the desired 
-%threshold and that it isn't matching two feature points from the same 
-%image. Since feature points are all guaranteed to be fairly similar 
-%this means that we can set the ratio threshold much higher than in 
-%\emph{MM} and include matches that would normally have been discarded 
-%for not being sufficiently unique.
 
-The matching algorithm for \emph{MMC}, \emph{getMatches}, finds matches 
-within all partitions with more than two elements using the \emph{MM} 
-approach.  However, as can be seen in the example in 
-Figure~\ref{fig:cropped_graph}, many of the partitions contain only two 
-feature points from different images linked by one edge. In such a case, 
-we compare the similarity of the these two feature points with their 
-second best match and remove matches where this ratio lies above a 
-certain threshold, like in the \emph{Ratio} algorithm. For example in the 
-case of Figure~\ref{fig:pitts_partition}, we have feature points from a 
-building in one image grouped together with points from a shirt pattern 
-in another.  The nearest neighbor method would have returned wrong 
-matches, but since we match the partition with \emph{MM}, points in the 
-building end up matching other points in the building, and no matches 
-are returned.
+\begin{algorithm}
+\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
+\label{alg-getmatches}
+    \fontsize{10}{10}\selectfont
+    \begin{algorithmic}
+    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
+    all features
+    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
+        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
+    \If{$\left\vert edges \right\vert > 1$}
+        \State $matches \gets MMGet(p, t)$
+    \ElsIf{$\left\vert edges \right\vert = 1$}
+        \State $matches \gets RatioGet(p, features, t)$
+    \Else
+        \State $matches \gets \varnothing$
+    \EndIf
 
-%\begin{algorithm}
-%\caption{Impl. of getMatches (\emph{from MMC algorithm})}
-%\label{alg-getmatches}
-%{\fontsize{10}{10}\selectfont
-%\begin{algorithmic}
-%\Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
-%all features
-%\State $matches \gets \varnothing$
-%\State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i) \neq 
-%	getImg(f_j)$
-%\State $\wedge f_i, f_j \in p \right\}$
-%\If{$\left\vert edges \right\vert = 1$} \Comment If $\exists$ one edge 
-%between images
-%	\State $f_i,f_j \gets getFeatures(edges_{inter}, p)$
-%	\State $f_m,f_n \gets get2NNs(f_i, features ~ 
-%\setminus ~ \left\{f_i\right\})$
-%	\State $f_s,f_t \gets get2NNs(f_j, features ~ 
-%\setminus ~ \left\{f_j\right\})$
-%	\State $ratio_i \gets similarity(f_i, f_n) / similarity(f_i, 
-%f_j)$
-%	\State $ratio_j \gets similarity(f_j, f_t) / similarity(f_j, 
-%f_i)$
-%	\If{$ratio_i < t\wedge ratio_j < t$}
-%		\State $matches \gets matches \cup (f_i, f_j)$
-%	\EndIf
-%\ElsIf{$\left\vert edges \right\vert > 1$} \Comment If $\exists$ more 
-%than one edge between images
-%	\ForAll{$f_i \in p$}
-%		\State $f_m,f_n \gets get2NNs(f_i, p \setminus 
-%\left\{f_i\right\})$
-%		\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, 
-%f_m)$
-%		\If{$getImg(f_i) \neq getImg(f_m) \wedge ratio < t
-%\wedge (f_m, f_i) \not\in matches$}
-%			\State $matches \gets matches \cup (f_i, f_m)$
-%		\EndIf
-%	\EndFor
-%\EndIf
-%
-%\Return matches
-%\end{algorithmic}
-%}
-%\end{algorithm}
+    \Return matches
+    \end{algorithmic}
+\end{algorithm}
+
+The matching algorithm for \emph{MMC} detailed in 
+Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
+more than two elements using the \emph{MM} approach.  However, as can be 
+seen in the example in Figure~\ref{fig:MMC_graph}, many of the 
+partitions contain only two feature points from different images linked 
+by one edge. In this case, we compare the similarity of the these two 
+feature points with their second best match and remove matches where 
+this ratio lies above a certain threshold, like in the \emph{Ratio} 
+algorithm.  For example in the case of Figure~\ref{fig:pitts_partition}, 
+we have feature points from a building in one image grouped together 
+with points from a shirt pattern in another.  The nearest neighbor 
+method would have returned wrong matches, but since we match the 
+partition with \emph{MM}, points in the building end up matching other 
+points in the building, and no matches are returned.
 
@@
 To reliably measure the accuracy of a matching method on real images, we 
-either need a set of image pairs tied by a homography, or we have to manually count 
-the number of inliers. The latter becomes prohibitive for large numbers of (non-trivial) images.
+either need a set of image pairs tied by a homography, or we have to 
+manually count the number of inliers. The latter becomes prohibitive for 
+large numbers of (non-trivial) images.
 
-Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a set of test images
-to compare the performance of feature detectors. The 
+Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
+set of test images to compare the performance of feature detectors. The 
 set covers different types of image variations, such as lighting change, 
-blur, rotation, and viewpoint change. Inspired by this 
-dataset (in particular the `Graf' image set) and motivated by 
-the need for more image pairs featuring viewpoint changes, we have 
-compiled a set of 8 image pairs consisting of subjects taken from two 
-different angles. The images are collected from Flickr's database of 
-images published under a creative commons 
-licence %\footnote{\href{http://creativecommons.org/}{www.creativecommons.org}, 
-%a copyleft license permitting redistribution} 
-and feature murals, which 
-makes it possible to relate points in the image pairs with a homography.  
-The images have been cropped to show the same motive and resized to 
-$900\times 600$ pixels.  This dataset will be referred to as the 
-\emph{Murals} dataset.  Figure~\ref{fig:murals} shows one image from each pair.
+blur, rotation, and viewpoint change. Inspired by this dataset (in 
+particular the `Graf' image set) and motivated by the need for more 
+image pairs featuring viewpoint changes, we have compiled a set of 8 
+image pairs consisting of subjects taken from two different angles. The 
+images are collected from Flickr's database of images published under a 
+creative commons licence and feature murals, which makes it possible to 
+relate points in the image pairs with a homography since most of the 
+points in the images will be lying on a plane.  The images have been 
+cropped to show the same motive and resized to $900\times 600$ pixels.  
+This dataset will be referred to as the \emph{Murals} dataset.  
+Figure~\ref{fig:murals} shows one image from each pair.
 
 \begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{0.048\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pair_example1}
-%			\label{fig:fairey1}
-%	\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.048\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pair_example2}
-%			\label{fig:fairey2}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.36\textwidth}
+    \makebox[1.0\textwidth][c]{%
+        \begin{subfigure}[t]{0.102\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pair_example1}
+			\label{fig:fairey1}
+	\end{subfigure}%
+		\enspace %add desired spacing between images, e. g. ~, \quad, 
+		%(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[t]{0.102\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pair_example2}
+			\label{fig:fairey2}
+		\end{subfigure}%
+		\enspace %
+        \begin{subfigure}[t]{0.77\textwidth}
    		\centering
    		\includegraphics[width=\columnwidth]{images/crop_examples}
-%		\end{subfigure}%
-%	}%
+		\end{subfigure}%
+	}%
 	\caption{Sample test patches produced from an image pair.}
@@
 
-%However in practice the view point change has gone on to be used the 
-%most for later tests given that most of the other test pairs have since 
-%become easy to match\footnote{see \cite{wu2011robust} or 
-%\cite{delponte2006svd} for examples}.
+\subsubsection{Experimental setup}
+We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
+\cite{lowe2004sift} as well as \emph{Isodata} \cite{das2008event} and 
+\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isodata} and 
+\emph{Spectral} uses geometric constraints, whereas \emph{Ratio} does 
+not.
 
-%Inspired by the graffiti image we have collected a set of image pairs 
-%featuring murals of a few different artists\footnote{Including Banksy, 
-%Blu and Shepard Fairey among others}. Each pair consist of images of 
-%the same motive taken from different angles, often including repetitive 
-%patterns and texture. Based on this image set the two algorithms are 
-%tested on a series of image patches from each pair. To verify that the 
-%algorithms proposed are reliable we need to test that we get good 
-%matches when images overlap and that we get no matches when they do 
-%not.  This means that it isn't enough just testing against pairs of 
-%images that we know match.  We also need to test against pairs that 
-%might look like they could match but in fact do not.
+\begin{algorithm}
+\caption{Ratio Match (\emph{Ratio})}
+\label{alg-ratio}
+%{\fontsize{10}{10}\selectfont
+\begin{algorithmic}
+\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
+\State $matches\gets \varnothing$
+\State $features_1 \gets getFeatures(im_1)$
+\State $features_2 \gets getFeatures(im_2)$
+\ForAll{$f_i \in features_1$}
+    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
+	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
+	\If{$ratio < t$}
+        \State $matches \gets \left(f_i, f_m\right)$
+	\EndIf
+\EndFor
+\Return $matches$
+\end{algorithmic}
+%}
+\end{algorithm}
 
-%
-%
-%\subsubsection{Experimental setup}
-We compare the \emph{MM} and \emph{MMC} algorithms to 
-\emph{Ratio} \cite{lowe2004sift} as well 
-as \emph{Isodata} \cite{das2008event}. 
-\emph{Isodata} uses geometric constraints, whereas \emph{Ratio} does not.
-%, which uses geometric information to improve the matching. 
-%The comparison  with \emph{Ratio} serves to illustrate the relative performance of 
-%\emph{MM} and \emph{MMC} to a state of the art algorithm without 
-%geometric constraints. \emph{Isodata} is included to 
-%illustrate the performance of an algorithm relying on geometric 
-%constraints faced with image pairs that might not have any overlap.  
-The 
-comparison was done using the \emph{Murals} dataset (Figure~\ref{fig:murals}), the 
-\emph{Graf} set (Figure~\ref{fig:Graf}) from \cite{mikolajczyk2005performance}, and two 
-images %\footnote{100\_1942.jpg and 100\_1941.jpg} 
-from the Gallagher dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
+\emph{Ratio} (Algorithm~\ref{alg-ratio}) is the most straightforward of 
+the three reference algorithms. Feature points are matched using K 
+Nearest Neighbor and the similarity ratio between the best and second 
+best match is then compared to a threshold to decide if the match is 
+kept.
+
+%, which uses geometric information to improve the matching.  The 
+%comparison  with \emph{Ratio} serves to illustrate the relative 
+%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
+%without geometric constraints. \emph{Isodata} is included to illustrate 
+%the performance of an algorithm relying on geometric constraints faced 
+%with image pairs that might not have any overlap.  
+The comparison was done using the \emph{Murals} dataset 
+(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
+from \cite{mikolajczyk2005performance}, and two 
+images\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher 
+dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
 
@@
 matching algorithm performs on a variety of overlaps but also how many 
-false positives we get on similar images that do not overlap at 
-all.\footnote{~The set of source images and homographies as well as the 
-script to generate the cropped test sets based on them will be made 
-available online, together with the exact test sets used in this paper 
-upon acceptance.}
-%\href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.  
-In practice the amount of overlap between pairs in a test set will 
-depend on the overlap and viewpoint change in the source image pair.  To 
-give a rough idea, Table~\ref{table:overlap} 
-shows the overlap of patch pairs created from images 1 and 3 of the 
-\emph{Graf} image set from \cite{mikolajczyk2005performance}.
+false positives we get on similar images that do not overlap at all. In 
+practice the amount of overlap between pairs in a test set will depend 
+on the overlap and viewpoint change in the source image pair.  To give a 
+rough idea, Table~\ref{table:overlap} shows the overlap of patch pairs 
+created from images 1 and 3 of the \emph{Graf} image set from 
+\cite{mikolajczyk2005performance}.
 
 \begin{table}[htb]
-\caption{Overlap in the set of 100 patch pairs created from two images of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
+\caption{Overlap in the set of 100 patch pairs created from two images 
+of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
 \label{table:overlap}
@@
 
-Given a potential match between two pixels $p_1$ and 
-$p_2$, $m = \left(p_1, p_2\right)$, and a homography $H$ relating the two images $I_1$ and $I_2$, we 
-can calculate if $m$ is an inlier by checking if the two points satisfy the following criteria:
+Given a potential match between two pixels $p_1$ and $p_2$, $m = 
+\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
+$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
+two points satisfy the following criteria:
 \begin{equation*}
@@
 Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
-generated from images 1 and 3 of the \emph{Graf} image set (cf.~Figure~\ref{fig:Graf}). The plot 
-compares the accuracy of \emph{Ratio}, \emph{MM}, \emph{MMC}, and 
-\emph{Isodata} as a function of the number of matches produced (which is achieved by varying thresholds over a certain range).
-The results show that \emph{MM} and \emph{MMC} consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 percentage points above \emph{MM} when both are performing at optimal accuracy.
-Although \emph{Isodata} exhibits a good performance on strict thresholds (small number of matches), that quickly diminishes when more matches are desired.
+generated from images 1 and 3 of the \emph{Graf} image set 
+(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
+\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isodata} as a function of 
+the number of matches produced (which is achieved by varying thresholds 
+over a certain range). The results show that \emph{MM} and \emph{MMC} 
+consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
+percentage points above \emph{MM} when both are performing at optimal 
+accuracy.  Although \emph{Isodata} exhibits a good performance on strict 
+thresholds (small number of matches), that quickly diminishes when more 
+matches are desired.
 
@@
 
-In terms of speed, Table~\ref{table:running_times} shows the 
-running time of the four algorithms over 100 image pairs of $250\!\times\!250$ pixels. 
-These numbers should be taken with a grain of salt, given that 
-much of the code behind \emph{MMC} and \emph{Isodata} is implemented in 
-Python, whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
+As for speed, Table~\ref{table:running_times} shows the running time of 
+the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
+These numbers should be taken with a grain of salt, given that much of 
+the code behind \emph{MMC} and \emph{Isodata} is implemented in Python, 
+whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
 computationally intensive operations in C++, which makes them much 
@@
 \subsection{Near Duplicate Detection}
-Both with regards to corporate intellectual property as well as consumer 
-photo albums, being able to automatically find near duplicates of images 
-provides useful across several scenarios. A company might be interested 
-in finding images that are derived from their intellectual property, 
-while consumers taking vacation photos might be interested in grouping 
-duplicate images to allow for easier photo organization.
+If we look at two images, we can often easily tell if one image 
+resembles the other enough to be redundant in a photo album. In computer 
+vision this task becomes a lot less trivial because our idea of a 
+duplicate image might only require there being some object or scene in 
+common between the image pair. In addition the object or scene might 
+have been taken from a different angle and under different camera 
+settings. Facing these challenges, a lot of work has been done trying to 
+reliably recognize duplicaes both with regards to corporate intellectual 
+property as well as consumer photo albums because both applications 
+provide useful tools.  A company might be interested in finding images 
+that are derived from their intellectual property, while consumers 
+taking vacation photos might be interested in grouping duplicate images 
+to allow for easier photo organization.
 
@@
 
-The PhotoCluster method introduced by Vonikakis et al.  
+The \emph{PhotoCluster} method introduced by Vonikakis et al.  
 \cite{vas2013cluster} shows the best clustering performance on the 
@@
 annotated vacation images similar to a typical photo album in a consumer
-product. PhotoCluster works by grouping images in several steps using 
-first image metadata and global features to obtain a set of proposed 
-clusters. Then local features are used to find the best matching images 
-in these proposed clusters yielding the final groups of near duplicate 
-images. To show the viability of \emph{MMC} in the application of near 
-duplicated detection, we modify the PhotoCluster method to use 
-\emph{MMC} for matching images instead of \emph{Ratio} which was 
-previously used. Due to the time consumption of \emph{MMC}, all images 
-where resized to to 10\% before being compared. Outside of that, the 
-experiments were performed exactly as documented in 
+product. \emph{PhotoCluster} works by grouping images in several steps 
+using first image metadata and global features to obtain a set of 
+proposed clusters. Then local features are used to find the best 
+matching images in these proposed clusters yielding the final groups of 
+near duplicate images. To show the viability of \emph{MMC} in the 
+application of near duplicated detection, we modify the PhotoCluster 
+method to use \emph{MMC} for matching images instead of \emph{Ratio} 
+which was previously used. Due to the time consumption of \emph{MMC}, 
+all images where resized to to 10\% before being compared. Outside of 
+that, the experiments were performed exactly as documented in 
 \cite{vas2013cluster}.
@@
 The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
-applying the algorithms to the problems of near duplicate detected and 
+applying the algorithms to the problems of near duplicate detection and 
 for the case of \emph{MMC} to panorama recognition and alignment. For 
 the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
-improvement over the state of the art \emph{Ratio} in a near duplicate 
-detection framework making use of local features. Similarly for panorama 
-recognition and alignment a simple panorama stitching method based on 
-\emph{MMC} succeeds in cases where Autostitch is unable to recognize and 
+improvement over \emph{Ratio} in a near duplicate detection framework 
+making use of local features. Similarly for panorama recognition and 
+alignment a simple panorama stitching method based on \emph{MMC} 
+succeeds in cases where \emph{Autostitch} is unable to recognize and 
 align the source images correctly. Both applications illustrate the 

### 2013-08-07 code/display.py
Fixed accuPlot to include recall

@@ -289,53 +289,38 @@ def accuDetail(correct, total, legend, ylim = 100, treshold=1000) :
     accuHist(accu, legend, ylim=ylim)
 
 
-def recallPlot(correct, total, nb_correspondences, legends, colors = ["blue", "red", "green", "orange", "cyan"], ylim=(0.0,1.01), xlim = None, size = (4,6)) :
+
+def accuPlot(correct, total, legends, colors = ["blue", "red", "green", "orange", "cyan"], ylim=(0.0, 1.01), xlim = None, size = (4,6), nb_correspondences = None, compareCorrect = None, compareTotal = None, compareLegend = None, outside = False, output = None) :
     fig = pylab.figure(figsize=size)
     ax = pylab.subplot(111)
     for ts, cs, l, color in zip(total, correct, legends, colors) :
-        xs = [(sum(t) - sum(c))/float(sum(t)) for c, t in zip(cs,ts)]
-        ys = [sum(c)/float(nb_correspondences) for c in cs]
-        pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.95)
-        pylab.legend(loc="best")
-    removeDecoration()
-    pylab.xlabel("1 - precision")
-    pylab.ylabel("# correct / %i" % nb_correspondences)
-    pylab.ylim(ylim[0],ylim[1])
-    if xlim != None : pylab.xlim(0,xlim)
-
-def recallInvPlot(correct, total, nb_correspondences, legends, colors = ["blue", "red", "green", "orange", "cyan"], ylim=(0.0,1.01), xlim = None, size = (4,6)) :
-    fig = pylab.figure(figsize=size)
-    ax = pylab.subplot(111)
-    for ts, cs, l, color in zip(total, correct, legends, colors) :
-        ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for c, t in zip(cs,ts)]
-        xs = [sum(c)/float(nb_correspondences) for c in cs]
-        pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.95)
-        pylab.legend(loc="best")
-    removeDecoration()
-    pylab.ylabel("precision")
-    pylab.xlabel("#correct / %i" % nb_correspondences)
-    pylab.ylim(ylim[0],ylim[1])
-    if xlim != None : pylab.xlim(0,xlim)
-
[…]

### 2013-08-07 code/isomatch.py
Proper indent in isomatch

@@ -28,143 +28,143 @@ import pylab
 
 def match(paths, options = {}) :
 
-	# Get matches in usual format
-	def matchFromIndex(i,j) :
-		return (features.getPosition(ks[indices == 0][i]), features.getPosition(ks[indices == 1][j]))
+    # Get matches in usual format
+    def matchFromIndex(i,j) :
+        return (features.getPosition(ks[indices == 0][i]), features.getPosition(ks[indices == 1][j]))
 
-	# Get options
-	k_init				= options.get("k_init", 50)
-	max_iterations		= options.get("max_iterations", 20)
-	min_partition_size	= options.get("min_partitions_size", 10)
-	max_sd				= options.get("max_sd", 40)
-	min_distance		= options.get("min_distance", 25)
-	verbose				= options.get("verbose", False)
-	keypoint_type		= options.get("keypoint_type", "SIFT")
-	descriptor_type		= options.get("descriptor_type", "SIFT")
+    # Get options
+    k_init				= options.get("k_init", 50)
+    max_iterations		= options.get("max_iterations", 20)
+    min_partition_size	= options.get("min_partitions_size", 10)
+    max_sd				= options.get("max_sd", 40)
+    min_distance		= options.get("min_distance", 25)
+    verbose				= options.get("verbose", False)
+    keypoint_type		= options.get("keypoint_type", "SIFT")
+    descriptor_type		= options.get("descriptor_type", "SIFT")
 
-	# Get images
-	images = map(features.loadImage, paths)
+    # Get images
+    images = map(features.loadImage, paths)
 
-	# Get all feature points
-	indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
+    # Get all feature points
+    indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
 
-	# Get positions
-	positions = numpy.array(features.getPositions(ks))
+    # Get positions
+    positions = numpy.array(features.getPositions(ks))
 
-	# Get matches
-	match_points = getMatchPoints(indices, ks, ds, descriptor_type = descriptor_type)
+    # Get matches
+    match_points = getMatchPoints(indices, ks, ds, descriptor_type = descriptor_type)
 
-	if len(match_points) == 0 : return [[] for _ in thresholds]
[…]

### 2013-08-07 text/thesis.tex
Added a bit of info on isodata

@@
 
-\emph{Ratio} (Algorithm~\ref{alg-ratio}) is the most straightforward of 
-the three reference algorithms. Feature points are matched using K 
-Nearest Neighbor and the similarity ratio between the best and second 
-best match is then compared to a threshold to decide if the match is 
-kept.
+\emph{Ratio} (Algorithm~\ref{alg-ratio}) \cite{lowe2004sift} is the most 
+straightforward of the three reference algorithms. Feature points are 
+matched using K Nearest Neighbor and the similarity ratio between the 
+best and second best match is then compared to a threshold to decide if 
+the match is kept.
 
+\begin{algorithm}
+\caption{Isodata Match (\emph{Isodata})}
+\label{alg-isodata}
+%{\fontsize{10}{10}\selectfont
+\begin{algorithmic}
+\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
+\State $matches_{init}\gets \varnothing$
+\State $matches_{final}\gets \varnothing$
+\State $features_1 \gets getFeatures(im_1)$
+\State $features_2 \gets getFeatures(im_2)$
+\ForAll{$f_i \in features_1$}
+    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
+    \State $matches_{init} \gets \left(f_i, f_m\right)$
+\EndFor
+\State $partitions_1 \gets isodata(getPositions(features_1))$
+\State $partitions_2 \gets isodata(getPositions(features_2))$
+\State $P_{corr} \gets getMatchMat(partitions_1, partitions_2, 
+matches_{init})$
+\ForAll{$(i,j) \in indices(P)$}
+    \If{$\left(P_{i,j} > 5\right) \wedge \left(P_{i,j} / sum(P_{i}) > 
+    0.5\right)$}
+        \State $matches_{final} \gets getMatches(matches_{init}, 
+        partitions_1, partitions_2, i, j)$
+    \EndIf
+\EndFor
+\Return $matches_{final}$
+\end{algorithmic}
+%}
+\end{algorithm}
+
+The \emph{Isodata} algorithm (Algorithm~\ref{alg-isodata}) 
+\cite{das2008event} is based on the idea that local feature points 
+within a region in one image often matches to features within a 
+corresponding region in the other image. To find these regions the 
+algorithm uses the Isodata algorithm \cite{ball1965isodata} to perform 
+unsupervised clustering on the feature points given their positions in 
+the two images. The Isodata algorithm is similar to K-means with the 
+addition that clusters are merged and split during the clustering 
+process. The initial set of matches are then filtered based on the 
+resulting regions. A match is kept only if it belongs to a region with 
+more than 5 matches and where half of the matches link the same two 
+regions. $P_{corr}$ in Algorithm~\ref{alg-isodata} is a matrix where 
+each row corresponds to a region in $im_1$, each column corresponds to a 
+region in $im_2$ and $P_{i,j}$ is the amount of matches going from 
+region $i$ to region $j$.
+
+There is no inherent threshold parameter in \emph{Isodata} so to show 
+how the algorithm performs over.
 %, which uses geometric information to improve the matching.  The 

### 2013-08-08 text/thesis.tex
Added a lot of information on spectral matching

@@
 	\If{$ratio < t$}
-		\State $matches_{init} \gets \left(f_i, f_m\right)$
+		\State $matches_{init} \gets matches_{init} \cup \left(f_i, f_m\right)$
 	\EndIf
@@
 We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
-\cite{lowe2004sift} as well as \emph{Isodata} \cite{das2008event} and 
-\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isodata} and 
+\cite{lowe2004sift} as well as \emph{Isomatch} \cite{das2008event} and 
+\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isomatch} and 
 \emph{Spectral} uses geometric constraints, whereas \emph{Ratio} does 
@@
 \begin{algorithm}
-\caption{Isodata Match (\emph{Isodata})}
+\caption{Isodata Match (\emph{Isomatch})}
 \label{alg-isodata}
@@
 
-The \emph{Isodata} algorithm (Algorithm~\ref{alg-isodata}) 
+The \emph{Isomatch} algorithm (Algorithm~\ref{alg-isodata}) 
 \cite{das2008event} is based on the idea that local feature points 
@@
 
-There is no inherent threshold parameter in \emph{Isodata} so to show 
-how the algorithm performs over.
+To threshold the \emph{Isomatch} algorithm we filter the results using 
+the ratio between first and second best match as in \emph{Ratio}, since 
+\emph{Isomatch} itself doesn't readily admit any thresholding parameter.
+
+\begin{algorithm}
+\caption{Spectral Match (\emph{Spectral})}
+\label{alg-spectral}
+%{\fontsize{10}{10}\selectfont
+\begin{algorithmic}
+\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
+\State $matches_{init}\gets \varnothing$
+\State $matches_{final} \gets \varnothing$
+\State $features_1 \gets getFeatures(im_1)$
+\State $features_2 \gets getFeatures(im_2)$
+\ForAll{$f_i \in features_1$}
+	\State $f_m,f_n \gets get2NNs(f_i, features_2)$
+	\State $matches_{init} \gets \left(f_i, f_m\right)$
+\EndFor
+\State $M \gets matrix(\left\vert matches_{init} \right\vert, \left\vert 
+matches_{init} \right\vert)$
+\ForAll{$m_i \in matches_{init}$}
+	\ForAll{$m_j \in matches_{init}$}
+		\If{$i = j$}
+			\State $M \gets matchSimilarity(m_i)$
+		\Else
+			\State $M \gets affinity(m_i, m_j)$
+		\EndIf
+	\EndFor
+\EndFor
+\State $x^{*} \gets maximumEigenvector(M)$
+\ForAll{$\left(m_i, x_i\right) \in \left(matches_{init}, x^{*}\right)$}
+	\If{$x_i > t$}
+		\State $matches_{final} \gets matchtes_{final} \cup m_i$
+	\EndIf
+\EndFor
+\Return $matches_{final}$
+\end{algorithmic}
+%}
+\end{algorithm}
+
+The \emph{Spectral} algorithm (Algorithm~\ref{alg-spectral}) is a 
+slightly modified version of the spectral matching algorithm proposed by
+Leordeanu and Herbert \cite{leordeanu2005spectral}. It is based on the 
+idea that the set of actual correspondences of feature points between 
+two images should be pairwise consistent. That is, given two feature 
+points that are geometrically close in one image, for most cases we 
+would assume that the closest correspondences in another image would be 
+similarly close. We want to pick out a set of matches $T \subset S$ 
+where $S$ is the initial set of possible matches such that the matches 
+in $T$ are as pairwise consistent as possible. If we let $x$ be a binary 
+vector corresponding in length to the set of initial matches $S$, where 
+$x_i = 1$ if $m_i \subset T$, then we can formulate a subset-score as:
+\begin{equation*}
+	S = \sum_{m_i, m_j \in T} M(m_i, m_j) = x^TMx
+\end{equation*}
+The solution $x^{*}$ that maximizes this equation is then $x^{*} = 
+argmax(x^TMx)$. By relaxing the constraints on $x$ such that it can take
+values in the range of $\left[0, 1\right]$ we can interpret $x_i$ as the
+association of $m_i$ with the optimal subset of matches $T$. Because we 
+only worry about the relative values of $x$ we can fix the norm of $x$ 
+to $1$, in which case by Raleigh's ratio theorem, the $x^{*}$ that 
+optimizes $x^TMx$ is the principal eigenvector of $M$.
+
+Leordeanu and Herbert proposes a simple affinity function to map the 
+pairwise closeness of two matches. Given a simple scene where no 
+rotation and excessive affine transformation takes place, it can 
+generally be assumed that the length and direction of the vector between
+the two feature points constituting the first match corresponds to the 
+length and direction of the vector between the two feature points 
+constituting the second match. They formulated an affinity function as 
+follows: \TODO: change this to real function
+\begin{equation*}
+	S = \sum_{m_i, m_j \in T} M(m_i, m_j) = x^TMx
+\end{equation*}
+There are a number of occasions where this assumption no longer holds 
+true. A simple example would be matches between two images of the same 
+scene where one image is rotated $180\degrees$. However for a lot of 
+applications like panorama stitching
+where we assume that images are generally not rotated a lot in between 
+each other the assumption is accurate.
+
 %, which uses geometric information to improve the matching.  The 
@@
 %performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isodata} is included to illustrate 
-%the performance of an algorithm relying on geometric constraints faced 
-%with image pairs that might not have any overlap.  
+%without geometric constraints. \emph{Isomatch} is included to 
+%illustrate the performance of an algorithm relying on geometric 
+%constraints faced with image pairs that might not have any overlap.  
 The comparison was done using the \emph{Murals} dataset 
@@
 (cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
-\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isodata} as a function of 
+\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isomatch} as a function of 
 the number of matches produced (which is achieved by varying thresholds 
@@
 percentage points above \emph{MM} when both are performing at optimal 
-accuracy.  Although \emph{Isodata} exhibits a good performance on strict 
+accuracy.  Although \emph{Isomatch} exhibits a good performance on strict 
 thresholds (small number of matches), that quickly diminishes when more 
@@
 
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isodata} can be 
+In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isomatch} can be 
 implemented in $O(n\log n)$, where $n$ is the total number of feature 
@@
 These numbers should be taken with a grain of salt, given that much of 
-the code behind \emph{MMC} and \emph{Isodata} is implemented in Python, 
+the code behind \emph{MMC} and \emph{Isomatch} is implemented in Python, 
 whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
@@
 \hline
-	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
+	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isomatch} 
 	\\
@@
 \emph{MMC} generally outperform existing matching algorithms 
-\emph{Ratio}, \emph{Isodata} and \emph{Spectral}. In addition \emph{MMC} 
+\emph{Ratio}, \emph{Isomatch} and \emph{Spectral}. In addition \emph{MMC} 
 outperforms \emph{MM}.  We show that this result generalizes to 

### 2013-08-09 text/head/settings_epfl_template.tex
Reorganized thesis

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%		Thesis Settings
%
%		EDOC Template
%		2011
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,11pt,fleqn]{book}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[french,german,english]{babel}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% EDOC THESIS TEMPLATE: Variant 1.0 -> Latin modern, large text width&height
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{lmodern}
%\usepackage[a4paper,top=22mm,bottom=28mm,inner=35mm,outer=25mm]{geometry}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDOC THESIS TEMPLATE: Variant 2.0 -> Utopia, Gabarrit A (lighter pages)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{fourier} % Utopia font-typesetting including mathematical formula compatible with newer TeX-Distributions (>2010)
%\usepackage{utopia} % on older systems -> use this package instead of fourier in combination with mathdesign for better looking results
%\usepackage[adobe-utopia]{mathdesign}
\setlength{\textwidth}{146.8mm} % = 210mm - 37mm - 26.2mm
\setlength{\oddsidemargin}{11.6mm} % 37mm - 1in (from hoffset)
\setlength{\evensidemargin}{0.8mm} % = 26.2mm - 1in (from hoffset)
\setlength{\topmargin}{-2.2mm} % = 0mm -1in + 23.2mm 
\setlength{\textheight}{221.9mm} % = 297mm -29.5mm -31.6mm - 14mm (12 to accomodate footline with pagenumber)
\setlength{\headheight}{14pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\parindent}{0pt}

\usepackage{setspace} % increase interline spacing slightly
\setstretch{1.1}

\makeatletter
\setlength{\@fptop}{0pt}  % for aligning all floating figures/tables etc... to the top margin
\makeatother

\usepackage{graphicx,xcolor}
\graphicspath{{images/}}

%\usepackage{subfig}
\usepackage{booktabs}
\usepackage{lipsum}
\usepackage{microtype}
\usepackage{url}
\usepackage[final]{pdfpages}

\usepackage{fancyhdr}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\pagestyle{fancy}
	\fancyhf{}
	\renewcommand{\headrulewidth}{0.4pt}
	\renewcommand{\footrulewidth}{0pt}
	\fancyhead[OR]{\bfseries \nouppercase{\rightmark}}
	\fancyhead[EL]{\bfseries \nouppercase{\leftmark}}
	\fancyfoot[EL,OR]{\thepage}
\fancypagestyle{plain}{
	\fancyhf{}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\footrulewidth}{0pt}
	\fancyfoot[EL,OR]{\thepage}}
\fancypagestyle{addpagenumbersforpdfimports}{
	\fancyhead{}
	\renewcommand{\headrulewidth}{0pt}
	\fancyfoot{}
	\fancyfoot[RO,LE]{\thepage}
}

\usepackage{listings}
\lstset{language=[LaTeX]Tex,tabsize=4, basicstyle=\scriptsize\ttfamily, showstringspaces=false, numbers=left, numberstyle=\tiny, numbersep=10pt, breaklines=true, breakautoindent=true, breakindent=10pt}

\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0},
	colorlinks=true,
	linkcolor=black,
	citecolor=black,
	urlcolor=black}
\urlstyle{same}

\makeatletter
\def\cleardoublepage{\clearpage\if@twoside \ifodd\c@page\else
    \hbox{}
    \thispagestyle{empty}
    \newpage
    \if@twocolumn\hbox{}\newpage\fi\fi\fi}
\makeatother \clearpage{\pagestyle{plain}\cleardoublepage}

%%%%% CHAPTER HEADER %%%%
\usepackage{color}
\usepackage{tikz}
\usepackage[explicit]{titlesec}
\newcommand*\chapterlabel{}
%\renewcommand{\thechapter}{\Roman{chapter}}
\titleformat{\chapter}[display]  % type (section,chapter,etc...) to vary,  shape (eg display-type)
	{\normalfont\bfseries\Huge} % format of the chapter
	{\gdef\chapterlabel{\thechapter\ }}     % the label 
 	{0pt} % separation between label and chapter-title
 	  {\begin{tikzpicture}[remember picture,overlay]
    \node[yshift=-8cm] at (current page.north west)
      {\begin{tikzpicture}[remember picture, overlay]
        \draw[fill=black] (0,0) rectangle(35.5mm,15mm);
        \node[anchor=north east,yshift=-7.2cm,xshift=34mm,minimum height=30mm,inner sep=0mm] at (current page.north west)
        {\parbox[top][30mm][t]{15mm}{\raggedleft $\phantom{\textrm{l}}$\color{white}\chapterlabel}};  %the black l is just to get better base-line alingement
        \node[anchor=north west,yshift=-7.2cm,xshift=37mm,text width=\textwidth,minimum height=30mm,inner sep=0mm] at (current page.north west)
              {\parbox[top][30mm][t]{\textwidth}{\color{black}#1}};
       \end{tikzpicture}
      };
   \end{tikzpicture}
   \gdef\chapterlabel{}
  } % code before the title body

\titlespacing*{\chapter}{0pt}{50pt}{30pt}
\titlespacing*{\section}{0pt}{13.2pt}{*0}  % 13.2pt is line spacing for a text with 11pt font size
\titlespacing*{\subsection}{0pt}{13.2pt}{*0}
\titlespacing*{\subsubsection}{0pt}{13.2pt}{*0}

\newcounter{myparts}
\newcommand*\partlabel{}
\titleformat{\part}[display]  % type (section,chapter,etc...) to vary,  shape (eg display-type)
	{\normalfont\bfseries\Huge} % format of the part
	{\gdef\partlabel{\thepart\ }}     % the label 
 	{0pt} % separation between label and part-title
 	  {\setlength{\unitlength}{20mm}
	  \addtocounter{myparts}{1}
	  \begin{tikzpicture}[remember picture,overlay]
    \node[anchor=north west,xshift=-65mm,yshift=-6.9cm-\value{myparts}*20mm] at (current page.north east) % for unknown reasons: 3mm missing -> 65 instead of 62
      {\begin{tikzpicture}[remember picture, overlay]
        \draw[fill=black] (0,0) rectangle(62mm,20mm);   % -\value{myparts}\unitlength
        \node[anchor=north west,yshift=-6.1cm-\value{myparts}*20mm,xshift=-60.5mm,minimum height=30mm,inner sep=0mm] at (current page.north east)
        {\parbox[top][30mm][t]{55mm}{\raggedright \color{white}Part \partlabel $\phantom{\textrm{l}}$}};  %the phantom l is just to get better base-line alingement
        \node[anchor=north east,yshift=-6.1cm-\value{myparts}*20mm,xshift=-63.5mm,text width=\textwidth,minimum height=30mm,inner sep=0mm] at (current page.north east)
              {\parbox[top][30mm][t]{\textwidth}{\raggedleft \color{black}#1}};
       \end{tikzpicture}
      };
   \end{tikzpicture}
   \gdef\partlabel{}
  } % code before the title body

### 2013-08-09 text/head/titlepage.tex
Reorganized thesis

\begin{titlepage}
\begin{center}
%\large
\sffamily

\null\vspace{2cm}
{\huge Reliable feature point matching} \\[24pt] 
\textcolor{gray}{\small{THIS IS A TEMPORARY TITLE PAGE \\ It will be 
replaced for the final print by a version \\ provided by the service 
academique.}}

\vfill

\begin{tabular} {cc}
\parbox{0.3\textwidth}{\includegraphics[width=4cm]{images/epfl}}
&
\parbox{0.7\textwidth}{%
	Thesis in Computer Science\\
	presented on September 3rd 2013\\
	at the Advanced Science Research Center\\
	Fusionopolis, Singapore\\

%
Singapore, ADSC, 2011}
\end{tabular}
\end{center}
\vspace{2cm}
\end{titlepage}

### 2013-08-09 text/main/ch2_background.tex
Reorganized thesis

--- 2013-08-07 text/thesis.tex
@@
-%\documentclass[report]{IEEEtran}
-\documentclass{article}
-\usepackage{footnote}
-%\usepackage[font={small}]{caption}
-\usepackage{sidecap}
-\usepackage{graphicx}
-\usepackage{cite}
-\usepackage{hyperref}
-%\usepackage[stable]{footmisc}
-\usepackage{caption}
-\usepackage{adjustbox}
-\usepackage{subcaption}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\chapter{Background}
 
-\begin{document}
-
-\title{Reliable feature point matching}
-\author{Jonas Arnfred}
-
-\maketitle
-
-\section{Introduction}
-What is the subject of this thesis and in what part lies my 
-contribution?
-How is the report organized?
-
-\section{Background}
 Introduction to Computer Vision
@@
  - Segue into related work from paper
-
-\section{Matching feature points}
-Basically c/p from paper, but better figures and maybe more explanations
- - Add path about graphs and how they are formed. Make sure to explain 
- the clustering in more detail and make it easier to understand
- - Add a good explanation for new figures and how the precision and 
- recall are calculated. This should appear somewhere before results.
- - Add part on spectral matching and modify accordingly. Make sure to 
- underline how the second plot shows how the geometric method is 
- independent of MMC and that they combined yield greater results.
-
-\subsection{Proposed Matching Methods}
-\label{S:MatchingMethods}
-
-\subsubsection{Mirror Match (\emph{MM})}
-
-\begin{figure}
-	\centering%
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
-			\caption{Source image pair}
-			\label{fig:pitts_source}
-		\end{subfigure}%
-		\\ %
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
-			\caption{Feature points}
-			\label{fig:pitts_keypoints}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
-			\caption{\emph{Ratio}}
-			\label{fig:unique}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
-			\caption{\emph{MM} intermediate result}
-			\label{fig:within}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
-			\caption{\emph{MM} final result}
-			\label{fig:without}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
-			\caption{\emph{MMC} Partition Example}
-			\label{fig:pitts_partition}
-		\end{subfigure}%
-	\caption{Feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-	(c) Result of \emph{Ratio} matching. 
-  (d) All matches found by \emph{MM}, including intra-image matches. 
-	(e) Final \emph{MM} result. 
-	(f) Example of a partition of feature points after clustering, which 
-includes similar feature points from building windows and shirt patterns.}%
-	\label{fig:comparemirror}%
-\end{figure}%
-
-%
-The central idea behind \emph{MM} is to match features of $n$ images by 
-taking every feature from all $n$ images and matching it against every 
-other feature from the same set. We can then discard the correspondences 
-that match two points within the same image. Algorithm~\ref{alg-mm} details  
-the implementation of \emph{MM}.
-%
-\begin{algorithm}
-\caption{Mirror Match (\emph{MM})}
-\label{alg-mm}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
-\State $features\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Acquisition Stage
-	\State $features\gets features \cup getFeatures(I_i)$
-\EndFor
-\ForAll{$f_i \in features$} \Comment Matching Stage
-	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
-	\left\{f_i\right\})$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-		\State $matches_{init} \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
-Stage
-\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
-getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
-		\State $matches_{final} \gets (f_i, f_j)$
-	\EndIf
-\EndFor \\
-\Return $matches_{final}$
-\end{algorithmic}
-%}
-\end{algorithm}
-%
-In the acquisition stage we gather all features in the set of images.  
-In the matching stage these features are matched using $k$-nearest 
-neighbors.  For any given feature $f_i$ the two most similar neighbors 
-are returned, and we calculate the ratio between them as proposed in 
-\cite{lowe2004sift}.  Any correspondence with a ratio above the 
-threshold supplied will be discarded. Finally in the filter stage we 
-check that matches are from different images and discard all matches 
-that are not symmetric.
-%
-%\begin{figure*}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image pair}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-%			\caption{Feature points}
-%			\label{fig:pitts_keypoints}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_off}
-%			\caption{\emph{Ratio}}
-%			\label{fig:unique}
-%		\end{subfigure}%
-%	}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
-%			\caption{\emph{MM} intermediate result}
-%			\label{fig:within}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match}
-%			\caption{\emph{MM} final result}
-%			\label{fig:without}
-%		\end{subfigure}%
-%		\enspace%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{\emph{MMC} Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-%(c) Result of \emph{Ratio} matching the two images.% 
-%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
-%	(e) Final \emph{MM} result with the intra-image matches removed. 
-%	(f) Example of a partition of feature points after clustering. This partition 
-%includes similar feature points around the windows of a building and the patterns of a shirt.}%
-%	\label{fig:comparemirror}%
-%\end{figure*}%
-
-Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} 
-using an example image pair from the Gallagher dataset 
-\cite{gallagher2008}.
-With \emph{Ratio} (Figure~\ref{fig:unique}), many incorrect matches occur 
-in the fence towards the bottom of the image.
-When we match all feature points together, many of these incorrect 
-matches are eliminated, because points in the fence match with other 
-points in the fence in the same image (Figures~\ref{fig:within} and
-\ref{fig:without}).
-
-\subsubsection{Mirror Match with Clustering (\emph{MMC})}
-%
-In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
-non-geometric feature matching by clustering feature points by 
-similarity. This process yields partitions of fairly similar feature 
-points that we can match using the same approach as \emph{MM}.  
-Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
-
-Before we introduce the implementation details we will go over the 
-problem of graph clustering and how it relates to feature matching.
-
-Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-points in an image and returns their matching score, we can define a 
-matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-as the \emph{adjecency matrix} of the fully connected graph where each 
-vertex corresponds to a keypoint and the edge between two vertices has a 
-weight equal to the distance between the two corresponding keypoints.
-
-This representation reduces the problem of partitioning the keypoints 
-into groups to that of graph clustering or community structure depending 
-on the context. In the literature there are various ways of clustering a 
-graph according to different measures of what constitutes an optimal 
-partitioning. Traditionally the most used clustering algorithms have 
-been K-means and spectral clustering, but in recent years a host of new 
-algorithms have been proposed based on both Newman's concept of graph 
-modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-well as information theoretical measures\footnote{See for example 
-\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-new algorithms differ from K-means clustering and Spectral clustering 
-in that they do not require the number of expected to clusters to be 
-specified beforehand\footnote{Among the aforementioned methods, this is 
-true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-tests done using randomly generated graphs with a known partitioning 
-\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-markedly better than spectral clustering and 
-K-means\cite{lancichinetti2009}.
-
-The performance of clustering algorithms is a complicated issue, since 
-an optimal clustering given the same graph can vary depending on the 
-application. Spectral clustering for example will usually return a 
-partitioning where each partition is roughly equal in size\footnote{As 
-mentioned in \cite{von2007}} while the Louvain 
-clustering\cite{blondel2008} might return partitions of very uneven 
-size, even if the modularity measurement has been shown to penalize very 
-small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-depending on the application, but when clustering feature points, 
-maintaining clusters of an even size usually means that some clusters 
-will be '\emph{catch-all}' clusters where the feature points that do 
-not fit anywhere else are grouped together. The necessity of specifying 
-the amount of partitions in for example Spectral clustering or Pott's 
-model clustering further exacerbates the issue since smaller partitions 
-are then combined into one to achieve the right amount of partitions.
-
-%
-\begin{algorithm}
-\caption{Mirror Match with Clustering (\emph{MMC})}
-\label{alg-mmc}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $M\gets \varnothing$
-\State $F\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather features
-	\State $f_i\gets getFeatures(I_i)$
-	\State $F\gets F \cup f_i$
-\EndFor
-\State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $A_{norm}\gets 1 - normalize(A)$
-\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $P\gets cluster(A_{pruned})$
-\ForAll{$p \in P$} \Comment p is a set of feature points
-	\State $M\gets M \cup getMatches(p, t, F)$
-\EndFor \\
-\Return matches
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\begin{figure}[t]
-    \centering
-\makebox[\textwidth][c]{%
-    \includegraphics[width=1.1\textwidth]{images/MMC_graph}
-    \label{fig:graph}
-}
-    \caption{The partitioned feature graph. Each vertex represents a 
-        feature point; lines indicate high similarity between points. A 
-        partition is a connected group with the same color. The border 
-        color of each node indicates which image it belongs to.  Zooming 
-    into a subsection of the graph (right part), the various cluster 
-sizes can be seen, ranging from hundreds of feature points to only two 
-or three.}
-	\label{fig:graph}
-\end{figure}
-
-We use the Louvain Method \cite{blondel2008} for clustering feature 
-points, since it is relatively fast and performs well 
-\cite{lancichinetti2009}, does not require parameters 
-\cite{blondel2008}, and does not emphasize partitions of equal size, as 
-opposed to spectral clustering or k-means \cite{von2007}, for example.
-While the Louvain clustering algorithm does not require any parameters 
-in itself, it tends towards clustering all feature points together in 
-the same partition if the graph is very connected.  To ensure that the 
-graph is well clustered, the adjacency matrix is pruned so that only 
-edges above a certain threshold are kept. From empirical analysis, 
-retaining the top 2.5\% of edges with the highest similarity seems to 
-work well in practice. Figure~\ref{fig:graph} shows the result of 
-clustering the feature points as a graph.
-%
-
-The partitions group feature points by similarity, which means that 
-repetitive structures such as buildings often appear in larger 
-partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
-%
-
-\begin{algorithm}
-\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
-\label{alg-getmatches}
-    \fontsize{10}{10}\selectfont
-    \begin{algorithmic}
-    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
-    all features
-    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
-        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
-    \If{$\left\vert edges \right\vert > 1$}
-        \State $matches \gets MMGet(p, t)$
-    \ElsIf{$\left\vert edges \right\vert = 1$}
-        \State $matches \gets RatioGet(p, features, t)$
-    \Else
-        \State $matches \gets \varnothing$
-    \EndIf
-
-    \Return matches
-    \end{algorithmic}
-\end{algorithm}
-
-The matching algorithm for \emph{MMC} detailed in 
-Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
-more than two elements using the \emph{MM} approach.  However, as can be 
-seen in the example in Figure~\ref{fig:MMC_graph}, many of the 
-partitions contain only two feature points from different images linked 
-by one edge. In this case, we compare the similarity of the these two 
-feature points with their second best match and remove matches where 
-this ratio lies above a certain threshold, like in the \emph{Ratio} 
-algorithm.  For example in the case of Figure~\ref{fig:pitts_partition}, 
-we have feature points from a building in one image grouped together 
-with points from a shirt pattern in another.  The nearest neighbor 
-method would have returned wrong matches, but since we match the 
-partition with \emph{MM}, points in the building end up matching other 
-points in the building, and no matches are returned.
-
-\subsection{Experiments}
-\label{S:Experiments}
-%
-To reliably measure the accuracy of a matching method on real images, we 
-either need a set of image pairs tied by a homography, or we have to 
-manually count the number of inliers. The latter becomes prohibitive for 
-large numbers of (non-trivial) images.
-
-Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
-set of test images to compare the performance of feature detectors. The 
-set covers different types of image variations, such as lighting change, 
-blur, rotation, and viewpoint change. Inspired by this dataset (in 
-particular the `Graf' image set) and motivated by the need for more 
-image pairs featuring viewpoint changes, we have compiled a set of 8 
-image pairs consisting of subjects taken from two different angles. The 
-images are collected from Flickr's database of images published under a 
-creative commons licence and feature murals, which makes it possible to 
-relate points in the image pairs with a homography since most of the 
-points in the images will be lying on a plane.  The images have been 
-cropped to show the same motive and resized to $900\times 600$ pixels.  
-This dataset will be referred to as the \emph{Murals} dataset.  
-Figure~\ref{fig:murals} shows one image from each pair.
-
-\begin{figure}[htb]
-    \makebox[1.0\textwidth][c]{%
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example1}
-			\label{fig:fairey1}
-	\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example2}
-			\label{fig:fairey2}
-		\end{subfigure}%
-		\enspace %
-        \begin{subfigure}[t]{0.77\textwidth}
-   		\centering
-   		\includegraphics[width=\columnwidth]{images/crop_examples}
-		\end{subfigure}%
-	}%
-	\caption{Sample test patches produced from an image pair.}
-	\label{fig:fairey}
-\end{figure}
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\textwidth]{images/murals}
-	\caption{Images in the \emph{Murals} test set.}
-	\label{fig:murals}
-\end{figure*}
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
-	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
-	\label{fig:Graf}
-\end{figure}
-
-\subsubsection{Experimental setup}
-We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
-\cite{lowe2004sift} as well as \emph{Isodata} \cite{das2008event} and 
-\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isodata} and 
-\emph{Spectral} uses geometric constraints, whereas \emph{Ratio} does 
-not.
-
-\begin{algorithm}
-\caption{Ratio Match (\emph{Ratio})}
-\label{alg-ratio}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
-\State $matches\gets \varnothing$
-\State $features_1 \gets getFeatures(im_1)$
-\State $features_2 \gets getFeatures(im_2)$
-\ForAll{$f_i \in features_1$}
-    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-        \State $matches \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\Return $matches$
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\emph{Ratio} (Algorithm~\ref{alg-ratio}) is the most straightforward of 
-the three reference algorithms. Feature points are matched using K 
-Nearest Neighbor and the similarity ratio between the best and second 
-best match is then compared to a threshold to decide if the match is 
-kept.
-
-%, which uses geometric information to improve the matching.  The 
-%comparison  with \emph{Ratio} serves to illustrate the relative 
-%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isodata} is included to illustrate 
-%the performance of an algorithm relying on geometric constraints faced 
-%with image pairs that might not have any overlap.  
-The comparison was done using the \emph{Murals} dataset 
-(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
-from \cite{mikolajczyk2005performance}, and two 
-images\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher 
-dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
-
-Test sets were generated from the image pairs by cropping square patches of
-$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
-Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
-This ensures that patch pairs with no overlap still retain a general similarity to each 
-other, while patches that do overlap often only share a small 
-part of their area. Figure~\ref{fig:fairey} shows an example of 
-possible pairs of test image patches produced from a source image pair.  
-Producing $n$ such pairs allows us to test not just how well the 
-matching algorithm performs on a variety of overlaps but also how many 
-false positives we get on similar images that do not overlap at all. In 
-practice the amount of overlap between pairs in a test set will depend 
-on the overlap and viewpoint change in the source image pair.  To give a 
-rough idea, Table~\ref{table:overlap} shows the overlap of patch pairs 
-created from images 1 and 3 of the \emph{Graf} image set from 
-\cite{mikolajczyk2005performance}.
-
-\begin{table}[htb]
-\caption{Overlap in the set of 100 patch pairs created from two images 
-of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
-\label{table:overlap}
-    \centering
-%   \small
-\begin{tabular}{r*{3}{r}}
-\hline
-    Amount of overlap: & 0\% & $< 50$\% & $> 50$\%  \\
-    \noalign{\smallskip}
-	%
-    Number of patch pairs: & 21 & 54 & 25 \\
-    \hline
-\end{tabular}
-\end{table}
-
-Given a potential match between two pixels $p_1$ and $p_2$, $m = 
-\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
-$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
-two points satisfy the following criteria:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
-\end{equation*}
-That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here).
-
-\subsection{Results}
-\label{S:Results}
-
-Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
-generated from images 1 and 3 of the \emph{Graf} image set 
-(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
-\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isodata} as a function of 
-the number of matches produced (which is achieved by varying thresholds 
-over a certain range). The results show that \emph{MM} and \emph{MMC} 
-consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
-percentage points above \emph{MM} when both are performing at optimal 
-accuracy.  Although \emph{Isodata} exhibits a good performance on strict 
-thresholds (small number of matches), that quickly diminishes when more 
-matches are desired.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.13\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_graf}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
-		shows the result of 100 patch pairs generated from the source 
-		images shown to the left. The number of matches is the total 
-		number of matches for all 100 patch pairs.}
-	\label{fig:result_graf}
-\end{figure}
-
-To validate whether these results 
-generalize to other images, we tested the four algorithms on the 
-\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
-In total 900 different patch pairs were generated from 9 
-source image pairs.  The results are shown in Figure 
-\ref{fig:result_accumulated}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/result_accumulated}
-	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
-	\label{fig:result_accumulated}
-\end{figure}
-
-To further investigate the impact of viewpoint changes, we tested the 
-algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
-contains 5 images of the same mural taken with gradually increasing 
-viewpoint changes.  The first images are almost identical, while the 
-last are taken from very different angles. The results from   \emph{MMC} 
-and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
-viewpoint changes.
-The performance of \emph{MM} (not shown in the plot) is similar to 
-\emph{MMC}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
-	\caption{Results for viewpoint changes using the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
-	\label{fig:result_viewpoint}
-\end{figure}
-
-Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
-shows the results on 100 patch pairs generated 
-from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
-change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.15\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pitts}
-%		\end{subfigure}%
-		~%add desired spacing between images, e. g. ~, \quad, \qquad
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
-	\label{fig:result_pitts}
-\end{figure}
-
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isodata} can be 
-implemented in $O(n\log n)$, where $n$ is the total number of feature 
-points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. However, it is 
-possible to approximate this in $O(n\log n)$ using search trees.
-
-As for speed, Table~\ref{table:running_times} shows the running time of 
-the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
-These numbers should be taken with a grain of salt, given that much of 
-the code behind \emph{MMC} and \emph{Isodata} is implemented in Python, 
-whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
-computationally intensive operations in C++, which makes them much 
-faster.
-
-\begin{table}[htb]
-\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
-3.30~GHz with 8~GB memory.}
-\label{table:running_times}
-	\centering
-%	\small
-\begin{tabular}{r*{4}{c}}
-\hline
-	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
-	\\
-	\noalign{\smallskip} 
-	%
-	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
-	\hline
-\end{tabular}
-\end{table}
-%
-
-\section{Applications}
-
-In many areas of computer vision matching local feature points is a key 
-component, and matching algorithms have applications in problems such as
-scene matching, object recognition, near duplicate detection and 
-panorama recognition. To show the practical applications of the proposed 
-matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
-improve existing methods in near duplicate detection and panorama 
-recognition. These two problems were chosen because they both involve 
-matching images that might or might not overlap. These cases requires 
-matching algorithms that limit false positives since e.g. returning the 
-top $n$ matches for any given image pair would make it hard to 
-distinguish adjacent or duplicate images from non-adjacent or dissimilar
-image pairs. Near duplicate detection also constraints normal matching 
-algorithms from relying on geometric assumptions, since we have very few
-guarantees between two potential near duplicates that they should be 
-matched using any particular geometric heuristic. In this section, we 
-will first see \emph{MMC} applied to panorama recognition and alignment,
-and next \emph{MM} and \emph{MMC} applied to near duplicate detection.
-
-\subsection{Panorama Recognition and Alignment}
-One of the oldest practical problems approached in computer vision is 
-the automatic stitching of several source images into a bigger image, 
-such as panoramas and composite satellite photos\footnote{A brief 
-overview of the history of image stitching can be found in Szeliski's 
-book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
-As part of the process of stitching together images, the individual 
-images must be aligned and often transformed in perspective. Earlier 
-methods relied on minimizing pixel dissimilarities in overlapping images 
-while more recent methods have used local feature points to estimate the 
-correct image alignment. Using local feature points carry the additional 
-advantage that it is feasible to automatically recognize where each 
-source image belong in the final panorama.
-
-\begin{figure}[h]
-	\begin{subfigure}[t]{0.9\textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{images/pano_wide}
-        \label{fig:pano_images}
-		\caption{Source images}
-    \end{subfigure}%
-	\\
-	\centering
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-autostitch}
-        \label{fig:pano_autostitch}
-		\caption{Panorama by Autostitch}
-    \end{subfigure}%
-	~%add desired spacing between images, e. g. ~, \quad, \qquad
-	%(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-MMC}
-		\caption{Panorama by MMC}
-		\label{fig:pano_MMC}
-	\end{subfigure}%
-    \label{fig:pano_example}
-	\caption{An example of a difficult case for panorama recognition and 
-		alignment.  In a) the source images used to generate the 
-		panorama are displayed.\ b) shows the result of the Autostitch 
-		program from \cite{brown2007automatic} which fails to combine 
-		all images, while c) demonstrates the result of the simple 
-		panorama stitcher
-	using the proposed MMC algorithm. Here the two left images are 
-correctly linked}
-\end{figure}
-
-In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
-image can be assembled by collecting the feature points of all source 
-images and matching them to obtain a set of inter image matches.  By 
-using \emph{RANSAC}\footnote{RANdom SAmple Consensus, an iterative 
-    algorithm to estimate parameters from noisy data introduced in 
-Fischler and Bolles in 1981 \cite{fischler1981ransac}} to find matches 
-deemed as inliers between image pairs, they are able to recognize image 
-neighbors and align them to construct the final panorama.
-
-This process hinges on the effectiveness of the matching algorithm used 
-to match the feature points. Not only is it important that true pairs 
-are accurately matched, but since we are matching points in image pairs 
-that might not be adjacent in the final panorama, we also need to make 
-sure that we consistently reject false positives, i.e.\ proposed matches 
-that link feature points which don't correspond.
-
-To demonstrate the usefulness of \emph{MMC} applied to panorama 
-recognition and alignment we construct a simple panorama stitcher taking
-as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
-and returns as output a panoramic image stitched together from the 
-source images. Based on the matches found by applying \emph{MMC} to $I$, 
-the images are combined in an order corresponding to how many matches 
-connect them, as done by Brown and Lowe \cite{brown2007automatic}.
-
-Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
-provides a way to globally optimize the accuracy of the image alignment} 
-and a lot of image enhancements such as exposure adjustment and edge 
-blurring to provide a seamless panorama. While these additions improve 
-the end product, they don't influence the performance of panorama 
-alignment and recognition and haven't been included in the simple 
-comparison algorithm.
-
-Figure~\ref{fig:pano_example} shows an example where the added accuracy 
-of MMC enables us to correctly recognitize and align source images that 
-fail to be combined by Autostitch, a program using the algorithm 
-proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
-case the matching algorithm used in Autostitch fails to find sufficient 
-matches between two images pairs to correctly position them and 
-consequently doesn't produce a panorama containing all images as a 
-result.
-
-This example illustrates how an improved matching algorithm can be 
-applied to panorama recognition and alignment to allow for panoramas 
-created with images that have little overlap.
-% Maybe find example of images with identical features that would be 
-% hard to match?
-
-\subsection{Near Duplicate Detection}
-If we look at two images, we can often easily tell if one image 
-resembles the other enough to be redundant in a photo album. In computer 
-vision this task becomes a lot less trivial because our idea of a 
-duplicate image might only require there being some object or scene in 
-common between the image pair. In addition the object or scene might 
-have been taken from a different angle and under different camera 
-settings. Facing these challenges, a lot of work has been done trying to 
-reliably recognize duplicaes both with regards to corporate intellectual 
-property as well as consumer photo albums because both applications 
-provide useful tools.  A company might be interested in finding images 
-that are derived from their intellectual property, while consumers 
-taking vacation photos might be interested in grouping duplicate images 
-to allow for easier photo organization.
-
-Local features are often used to group similar images, either by looking
-at a histogram of descriptors \cite{wu2009bundling} or by looking at how
-well feature points match between images \cite{zhao2009scale},
-\cite{chu2010consumer}, \cite{vas2013cluster}. In the latter case 
-finding near duplicates means that we will be matching image pairs that 
-might or might not contain any actual matches. In this case we would 
-benefit from a reliable matching algorithm that minimizes false 
-positives, which is a characteristic of both \emph{MM} and \emph{MMC}.
-
-The \emph{PhotoCluster} method introduced by Vonikakis et al.  
-\cite{vas2013cluster} shows the best clustering performance on the 
-California-nd dataset \cite{jinda2012california} which contains a set of
-annotated vacation images similar to a typical photo album in a consumer
-product. \emph{PhotoCluster} works by grouping images in several steps 
-using first image metadata and global features to obtain a set of 
-proposed clusters. Then local features are used to find the best 
-matching images in these proposed clusters yielding the final groups of 
-near duplicate images. To show the viability of \emph{MMC} in the 
-application of near duplicated detection, we modify the PhotoCluster 
-method to use \emph{MMC} for matching images instead of \emph{Ratio} 
-which was previously used. Due to the time consumption of \emph{MMC}, 
-all images where resized to to 10\% before being compared. Outside of 
-that, the experiments were performed exactly as documented in 
-\cite{vas2013cluster}.
-
-\begin{table}[htb]
-\caption{Results from Near Duplicate Detection at 10\% scale}
-\label{table:ndd}
-	\centering
-%	\small
-\begin{tabular}{r*{2}{r}}
-\hline
-    Method: & Ratio & MMC   \\
-	\noalign{\smallskip}
-	%
-    F1 score: & 0.4654 & 0.5459 \\
-	\hline
-\end{tabular}
-\end{table}
-
-The results of the comparison can be seen in Table~\ref{table:nnd}. It 
-shows that \emph{MMC} improves performance by 8.05\% over the original 
-framework using \emph{Ratio} to match images. For comparison, the 
-performance improvement of \emph{PhotoCluster} compared to XMatch 
-\cite{zhao2009scale}, the second best performing algorithm on the 
-California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.
-
-\section{Summary}
-\label{S:Summary}
-
-This thesis has addressed the problem of matching feature points without 
-using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
-\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
-common idea that feature points should have better matches in another 
-image than in the image they came from to be considered good matches.  
-\emph{MMC} further improves on this idea by using the structure of the 
-similarity graph of the feature points.
-
-The algorithms show promising results when tested on the \emph{Murals} 
-data set. The results on 900 image pairs show that \emph{MM} and 
-\emph{MMC} generally outperform existing matching algorithms 
-\emph{Ratio}, \emph{Isodata} and \emph{Spectral}. In addition \emph{MMC} 
-outperforms \emph{MM}.  We show that this result generalizes to 
-variations in viewpoint change by comparing \emph{MMC} to \emph{Ratio} 
-over a set of image pairs with an increasing magnitude of perspective 
-difference. We go on to apply the algorithms to a real life image case 
-featuring occlusion and a slight viewpoint change and show that the 
-performance of \emph{MM} and \emph{MMC} is consistent with the results 
-on \emph{Murals}. To show that \emph{MM} or \emph{MMC}
-can further improve the results of a geometrical method, we create 
-\emph{Spectral-MMC} by combining \emph{Spectral} and \emph{MMC} and 
-compare the three on the full \emph{Murals} dataset where it yields 
-results better than both \emph{Spectral} and \emph{MMC}.
-
-The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
-applying the algorithms to the problems of near duplicate detection and 
-for the case of \emph{MMC} to panorama recognition and alignment. For 
-the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
-improvement over \emph{Ratio} in a near duplicate detection framework 
-making use of local features. Similarly for panorama recognition and 
-alignment a simple panorama stitching method based on \emph{MMC} 
-succeeds in cases where \emph{Autostitch} is unable to recognize and 
-align the source images correctly. Both applications illustrate the 
-central role that performance of the matching algorithm has on tasks 
-that makes use of local features to match image pairs with potential 
-overlap.
-%
-
-\bibliographystyle{IEEEtran}
-\bibliography{bibliography}
-\end{document}

### 2013-08-09 text/main/ch3_matching_methods.tex
Reorganized thesis

--- 2013-08-07 text/thesis.tex
@@
-%\documentclass[report]{IEEEtran}
-\documentclass{article}
-\usepackage{footnote}
-%\usepackage[font={small}]{caption}
-\usepackage{sidecap}
-\usepackage{graphicx}
-\usepackage{cite}
-\usepackage{hyperref}
-%\usepackage[stable]{footmisc}
-\usepackage{caption}
-\usepackage{adjustbox}
-\usepackage{subcaption}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\begin{document}
-
-\title{Reliable feature point matching}
-\author{Jonas Arnfred}
-
-\maketitle
-
-\section{Introduction}
-What is the subject of this thesis and in what part lies my 
-contribution?
-How is the report organized?
-
-\section{Background}
-Introduction to Computer Vision
- - Introduce common tasks that we are good at that computers aren't
- - Single in on tasks that we can solve using feature points
-
-Introduction to feature points
- - Global explanation of what they are and how they serve to solve the 
-problems mentioned before
- - How do we find them? (Examples making it intuitive why corners are 
-nice)
- - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
- Scale, \ldots, Affine)
- - Introduce SIFT and explain how the different problems are tackled in 
-SIFT)
- - Talk about other methods and how they are different
-
-Matching feature points
- - What applications require matching?
- - How is matching usually done
- - Segue into related work from paper
-
-\section{Matching feature points}
+\chapter{Matching Methods}
 Basically c/p from paper, but better figures and maybe more explanations
@@
 that are not symmetric.
-%
-%\begin{figure*}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image pair}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-%			\caption{Feature points}
-%			\label{fig:pitts_keypoints}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_off}
-%			\caption{\emph{Ratio}}
-%			\label{fig:unique}
-%		\end{subfigure}%
-%	}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
-%			\caption{\emph{MM} intermediate result}
-%			\label{fig:within}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match}
-%			\caption{\emph{MM} final result}
-%			\label{fig:without}
-%		\end{subfigure}%
-%		\enspace%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{\emph{MMC} Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-%(c) Result of \emph{Ratio} matching the two images.% 
-%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
-%	(e) Final \emph{MM} result with the intra-image matches removed. 
-%	(f) Example of a partition of feature points after clustering. This partition 
-%includes similar feature points around the windows of a building and the patterns of a shirt.}%
-%	\label{fig:comparemirror}%
-%\end{figure*}%
 
@@
 points in the building, and no matches are returned.
-
-\subsection{Experiments}
-\label{S:Experiments}
-%
-To reliably measure the accuracy of a matching method on real images, we 
-either need a set of image pairs tied by a homography, or we have to 
-manually count the number of inliers. The latter becomes prohibitive for 
-large numbers of (non-trivial) images.
-
-Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
-set of test images to compare the performance of feature detectors. The 
-set covers different types of image variations, such as lighting change, 
-blur, rotation, and viewpoint change. Inspired by this dataset (in 
-particular the `Graf' image set) and motivated by the need for more 
-image pairs featuring viewpoint changes, we have compiled a set of 8 
-image pairs consisting of subjects taken from two different angles. The 
-images are collected from Flickr's database of images published under a 
-creative commons licence and feature murals, which makes it possible to 
-relate points in the image pairs with a homography since most of the 
-points in the images will be lying on a plane.  The images have been 
-cropped to show the same motive and resized to $900\times 600$ pixels.  
-This dataset will be referred to as the \emph{Murals} dataset.  
-Figure~\ref{fig:murals} shows one image from each pair.
-
-\begin{figure}[htb]
-    \makebox[1.0\textwidth][c]{%
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example1}
-			\label{fig:fairey1}
-	\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example2}
-			\label{fig:fairey2}
-		\end{subfigure}%
-		\enspace %
-        \begin{subfigure}[t]{0.77\textwidth}
-   		\centering
-   		\includegraphics[width=\columnwidth]{images/crop_examples}
-		\end{subfigure}%
-	}%
-	\caption{Sample test patches produced from an image pair.}
-	\label{fig:fairey}
-\end{figure}
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\textwidth]{images/murals}
-	\caption{Images in the \emph{Murals} test set.}
-	\label{fig:murals}
-\end{figure*}
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
-	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
-	\label{fig:Graf}
-\end{figure}
-
-\subsubsection{Experimental setup}
-We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
-\cite{lowe2004sift} as well as \emph{Isodata} \cite{das2008event} and 
-\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isodata} and 
-\emph{Spectral} uses geometric constraints, whereas \emph{Ratio} does 
-not.
-
-\begin{algorithm}
-\caption{Ratio Match (\emph{Ratio})}
-\label{alg-ratio}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
-\State $matches\gets \varnothing$
-\State $features_1 \gets getFeatures(im_1)$
-\State $features_2 \gets getFeatures(im_2)$
-\ForAll{$f_i \in features_1$}
-    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-        \State $matches \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\Return $matches$
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\emph{Ratio} (Algorithm~\ref{alg-ratio}) is the most straightforward of 
-the three reference algorithms. Feature points are matched using K 
-Nearest Neighbor and the similarity ratio between the best and second 
-best match is then compared to a threshold to decide if the match is 
-kept.
-
-%, which uses geometric information to improve the matching.  The 
-%comparison  with \emph{Ratio} serves to illustrate the relative 
-%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isodata} is included to illustrate 
-%the performance of an algorithm relying on geometric constraints faced 
-%with image pairs that might not have any overlap.  
-The comparison was done using the \emph{Murals} dataset 
-(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
-from \cite{mikolajczyk2005performance}, and two 
-images\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher 
-dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
-
-Test sets were generated from the image pairs by cropping square patches of
-$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
-Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
-This ensures that patch pairs with no overlap still retain a general similarity to each 
-other, while patches that do overlap often only share a small 
-part of their area. Figure~\ref{fig:fairey} shows an example of 
-possible pairs of test image patches produced from a source image pair.  
-Producing $n$ such pairs allows us to test not just how well the 
-matching algorithm performs on a variety of overlaps but also how many 
-false positives we get on similar images that do not overlap at all. In 
-practice the amount of overlap between pairs in a test set will depend 
-on the overlap and viewpoint change in the source image pair.  To give a 
-rough idea, Table~\ref{table:overlap} shows the overlap of patch pairs 
-created from images 1 and 3 of the \emph{Graf} image set from 
-\cite{mikolajczyk2005performance}.
-
-\begin{table}[htb]
-\caption{Overlap in the set of 100 patch pairs created from two images 
-of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
-\label{table:overlap}
-    \centering
-%   \small
-\begin{tabular}{r*{3}{r}}
-\hline
-    Amount of overlap: & 0\% & $< 50$\% & $> 50$\%  \\
-    \noalign{\smallskip}
-	%
-    Number of patch pairs: & 21 & 54 & 25 \\
-    \hline
-\end{tabular}
-\end{table}
-
-Given a potential match between two pixels $p_1$ and $p_2$, $m = 
-\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
-$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
-two points satisfy the following criteria:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
-\end{equation*}
-That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here).
-
-\subsection{Results}
-\label{S:Results}
-
-Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
-generated from images 1 and 3 of the \emph{Graf} image set 
-(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
-\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isodata} as a function of 
-the number of matches produced (which is achieved by varying thresholds 
-over a certain range). The results show that \emph{MM} and \emph{MMC} 
-consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
-percentage points above \emph{MM} when both are performing at optimal 
-accuracy.  Although \emph{Isodata} exhibits a good performance on strict 
-thresholds (small number of matches), that quickly diminishes when more 
-matches are desired.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.13\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_graf}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
-		shows the result of 100 patch pairs generated from the source 
-		images shown to the left. The number of matches is the total 
-		number of matches for all 100 patch pairs.}
-	\label{fig:result_graf}
-\end{figure}
-
-To validate whether these results 
-generalize to other images, we tested the four algorithms on the 
-\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
-In total 900 different patch pairs were generated from 9 
-source image pairs.  The results are shown in Figure 
-\ref{fig:result_accumulated}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/result_accumulated}
-	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
-	\label{fig:result_accumulated}
-\end{figure}
-
-To further investigate the impact of viewpoint changes, we tested the 
-algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
-contains 5 images of the same mural taken with gradually increasing 
-viewpoint changes.  The first images are almost identical, while the 
-last are taken from very different angles. The results from   \emph{MMC} 
-and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
-viewpoint changes.
-The performance of \emph{MM} (not shown in the plot) is similar to 
-\emph{MMC}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
-	\caption{Results for viewpoint changes using the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
-	\label{fig:result_viewpoint}
-\end{figure}
-
-Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
-shows the results on 100 patch pairs generated 
-from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
-change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.15\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pitts}
-%		\end{subfigure}%
-		~%add desired spacing between images, e. g. ~, \quad, \qquad
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
-	\label{fig:result_pitts}
-\end{figure}
-
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isodata} can be 
-implemented in $O(n\log n)$, where $n$ is the total number of feature 
-points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. However, it is 
-possible to approximate this in $O(n\log n)$ using search trees.
-
-As for speed, Table~\ref{table:running_times} shows the running time of 
-the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
-These numbers should be taken with a grain of salt, given that much of 
-the code behind \emph{MMC} and \emph{Isodata} is implemented in Python, 
-whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
-computationally intensive operations in C++, which makes them much 
-faster.
-
-\begin{table}[htb]
-\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
-3.30~GHz with 8~GB memory.}
-\label{table:running_times}
-	\centering
-%	\small
-\begin{tabular}{r*{4}{c}}
-\hline
-	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
-	\\
-	\noalign{\smallskip} 
-	%
-	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
-	\hline
-\end{tabular}
-\end{table}
-%
-
-\section{Applications}
-
-In many areas of computer vision matching local feature points is a key 
-component, and matching algorithms have applications in problems such as
-scene matching, object recognition, near duplicate detection and 
-panorama recognition. To show the practical applications of the proposed 
-matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
-improve existing methods in near duplicate detection and panorama 
-recognition. These two problems were chosen because they both involve 
-matching images that might or might not overlap. These cases requires 
-matching algorithms that limit false positives since e.g. returning the 
-top $n$ matches for any given image pair would make it hard to 
-distinguish adjacent or duplicate images from non-adjacent or dissimilar
-image pairs. Near duplicate detection also constraints normal matching 
-algorithms from relying on geometric assumptions, since we have very few
-guarantees between two potential near duplicates that they should be 
-matched using any particular geometric heuristic. In this section, we 
-will first see \emph{MMC} applied to panorama recognition and alignment,
-and next \emph{MM} and \emph{MMC} applied to near duplicate detection.
-
-\subsection{Panorama Recognition and Alignment}
-One of the oldest practical problems approached in computer vision is 
-the automatic stitching of several source images into a bigger image, 
-such as panoramas and composite satellite photos\footnote{A brief 
-overview of the history of image stitching can be found in Szeliski's 
-book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
-As part of the process of stitching together images, the individual 
-images must be aligned and often transformed in perspective. Earlier 
-methods relied on minimizing pixel dissimilarities in overlapping images 
-while more recent methods have used local feature points to estimate the 
-correct image alignment. Using local feature points carry the additional 
-advantage that it is feasible to automatically recognize where each 
-source image belong in the final panorama.
-
-\begin{figure}[h]
-	\begin{subfigure}[t]{0.9\textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{images/pano_wide}
-        \label{fig:pano_images}
-		\caption{Source images}
-    \end{subfigure}%
-	\\
-	\centering
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-autostitch}
-        \label{fig:pano_autostitch}
-		\caption{Panorama by Autostitch}
-    \end{subfigure}%
-	~%add desired spacing between images, e. g. ~, \quad, \qquad
-	%(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-MMC}
-		\caption{Panorama by MMC}
-		\label{fig:pano_MMC}
-	\end{subfigure}%
-    \label{fig:pano_example}
-	\caption{An example of a difficult case for panorama recognition and 
-		alignment.  In a) the source images used to generate the 
-		panorama are displayed.\ b) shows the result of the Autostitch 
-		program from \cite{brown2007automatic} which fails to combine 
-		all images, while c) demonstrates the result of the simple 
-		panorama stitcher
-	using the proposed MMC algorithm. Here the two left images are 
-correctly linked}
-\end{figure}
-
-In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
-image can be assembled by collecting the feature points of all source 
-images and matching them to obtain a set of inter image matches.  By 
-using \emph{RANSAC}\footnote{RANdom SAmple Consensus, an iterative 
-    algorithm to estimate parameters from noisy data introduced in 
-Fischler and Bolles in 1981 \cite{fischler1981ransac}} to find matches 
-deemed as inliers between image pairs, they are able to recognize image 
-neighbors and align them to construct the final panorama.
-
-This process hinges on the effectiveness of the matching algorithm used 
-to match the feature points. Not only is it important that true pairs 
-are accurately matched, but since we are matching points in image pairs 
-that might not be adjacent in the final panorama, we also need to make 
-sure that we consistently reject false positives, i.e.\ proposed matches 
-that link feature points which don't correspond.
-
-To demonstrate the usefulness of \emph{MMC} applied to panorama 
-recognition and alignment we construct a simple panorama stitcher taking
-as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
-and returns as output a panoramic image stitched together from the 
-source images. Based on the matches found by applying \emph{MMC} to $I$, 
-the images are combined in an order corresponding to how many matches 
-connect them, as done by Brown and Lowe \cite{brown2007automatic}.
-
-Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
-provides a way to globally optimize the accuracy of the image alignment} 
-and a lot of image enhancements such as exposure adjustment and edge 
-blurring to provide a seamless panorama. While these additions improve 
-the end product, they don't influence the performance of panorama 
-alignment and recognition and haven't been included in the simple 
-comparison algorithm.
-
-Figure~\ref{fig:pano_example} shows an example where the added accuracy 
-of MMC enables us to correctly recognitize and align source images that 
-fail to be combined by Autostitch, a program using the algorithm 
-proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
-case the matching algorithm used in Autostitch fails to find sufficient 
-matches between two images pairs to correctly position them and 
-consequently doesn't produce a panorama containing all images as a 
-result.
-
-This example illustrates how an improved matching algorithm can be 
-applied to panorama recognition and alignment to allow for panoramas 
-created with images that have little overlap.
-% Maybe find example of images with identical features that would be 
-% hard to match?
-
-\subsection{Near Duplicate Detection}
-If we look at two images, we can often easily tell if one image 
-resembles the other enough to be redundant in a photo album. In computer 
-vision this task becomes a lot less trivial because our idea of a 
-duplicate image might only require there being some object or scene in 
-common between the image pair. In addition the object or scene might 
-have been taken from a different angle and under different camera 
-settings. Facing these challenges, a lot of work has been done trying to 
-reliably recognize duplicaes both with regards to corporate intellectual 
-property as well as consumer photo albums because both applications 
-provide useful tools.  A company might be interested in finding images 
-that are derived from their intellectual property, while consumers 
-taking vacation photos might be interested in grouping duplicate images 
-to allow for easier photo organization.
-
-Local features are often used to group similar images, either by looking
-at a histogram of descriptors \cite{wu2009bundling} or by looking at how
-well feature points match between images \cite{zhao2009scale},
-\cite{chu2010consumer}, \cite{vas2013cluster}. In the latter case 
-finding near duplicates means that we will be matching image pairs that 
-might or might not contain any actual matches. In this case we would 
-benefit from a reliable matching algorithm that minimizes false 
-positives, which is a characteristic of both \emph{MM} and \emph{MMC}.
-
-The \emph{PhotoCluster} method introduced by Vonikakis et al.  
-\cite{vas2013cluster} shows the best clustering performance on the 
-California-nd dataset \cite{jinda2012california} which contains a set of
-annotated vacation images similar to a typical photo album in a consumer
-product. \emph{PhotoCluster} works by grouping images in several steps 
-using first image metadata and global features to obtain a set of 
-proposed clusters. Then local features are used to find the best 
-matching images in these proposed clusters yielding the final groups of 
-near duplicate images. To show the viability of \emph{MMC} in the 
-application of near duplicated detection, we modify the PhotoCluster 
-method to use \emph{MMC} for matching images instead of \emph{Ratio} 
-which was previously used. Due to the time consumption of \emph{MMC}, 
-all images where resized to to 10\% before being compared. Outside of 
-that, the experiments were performed exactly as documented in 
-\cite{vas2013cluster}.
-
-\begin{table}[htb]
-\caption{Results from Near Duplicate Detection at 10\% scale}
-\label{table:ndd}
-	\centering
-%	\small
-\begin{tabular}{r*{2}{r}}
-\hline
-    Method: & Ratio & MMC   \\
-	\noalign{\smallskip}
-	%
-    F1 score: & 0.4654 & 0.5459 \\
-	\hline
-\end{tabular}
-\end{table}
-
-The results of the comparison can be seen in Table~\ref{table:nnd}. It 
-shows that \emph{MMC} improves performance by 8.05\% over the original 
-framework using \emph{Ratio} to match images. For comparison, the 
-performance improvement of \emph{PhotoCluster} compared to XMatch 
-\cite{zhao2009scale}, the second best performing algorithm on the 
-California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.
-
-\section{Summary}
-\label{S:Summary}
-
-This thesis has addressed the problem of matching feature points without 
-using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
-\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
-common idea that feature points should have better matches in another 
-image than in the image they came from to be considered good matches.  
-\emph{MMC} further improves on this idea by using the structure of the 
-similarity graph of the feature points.
-
-The algorithms show promising results when tested on the \emph{Murals} 
-data set. The results on 900 image pairs show that \emph{MM} and 
-\emph{MMC} generally outperform existing matching algorithms 
-\emph{Ratio}, \emph{Isodata} and \emph{Spectral}. In addition \emph{MMC} 
-outperforms \emph{MM}.  We show that this result generalizes to 
-variations in viewpoint change by comparing \emph{MMC} to \emph{Ratio} 
-over a set of image pairs with an increasing magnitude of perspective 
-difference. We go on to apply the algorithms to a real life image case 
-featuring occlusion and a slight viewpoint change and show that the 
-performance of \emph{MM} and \emph{MMC} is consistent with the results 
-on \emph{Murals}. To show that \emph{MM} or \emph{MMC}
-can further improve the results of a geometrical method, we create 
-\emph{Spectral-MMC} by combining \emph{Spectral} and \emph{MMC} and 
-compare the three on the full \emph{Murals} dataset where it yields 
-results better than both \emph{Spectral} and \emph{MMC}.
-
-The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
-applying the algorithms to the problems of near duplicate detection and 
-for the case of \emph{MMC} to panorama recognition and alignment. For 
-the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
-improvement over \emph{Ratio} in a near duplicate detection framework 
-making use of local features. Similarly for panorama recognition and 
-alignment a simple panorama stitching method based on \emph{MMC} 
-succeeds in cases where \emph{Autostitch} is unable to recognize and 
-align the source images correctly. Both applications illustrate the 
-central role that performance of the matching algorithm has on tasks 
-that makes use of local features to match image pairs with potential 
-overlap.
-%
-
-\bibliographystyle{IEEEtran}
-\bibliography{bibliography}
-\end{document}

### 2013-08-09 text/main/ch4_competition.tex
Reorganized thesis

--- 2013-08-08 text/thesis.tex
@@
-%\documentclass[report]{IEEEtran}
-\documentclass{article}
-\usepackage{footnote}
-%\usepackage[font={small}]{caption}
-\usepackage{sidecap}
-\usepackage{graphicx}
-\usepackage{cite}
-\usepackage{hyperref}
-%\usepackage[stable]{footmisc}
-\usepackage{caption}
-\usepackage{adjustbox}
-\usepackage{subcaption}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\chapter{Competition}
 
-\begin{document}
-
-\title{Reliable feature point matching}
-\author{Jonas Arnfred}
-
-\maketitle
-
-\section{Introduction}
-What is the subject of this thesis and in what part lies my 
-contribution?
-How is the report organized?
-
-\section{Background}
-Introduction to Computer Vision
- - Introduce common tasks that we are good at that computers aren't
- - Single in on tasks that we can solve using feature points
-
-Introduction to feature points
- - Global explanation of what they are and how they serve to solve the 
-problems mentioned before
- - How do we find them? (Examples making it intuitive why corners are 
-nice)
- - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
- Scale, \ldots, Affine)
- - Introduce SIFT and explain how the different problems are tackled in 
-SIFT)
- - Talk about other methods and how they are different
-
-Matching feature points
- - What applications require matching?
- - How is matching usually done
- - Segue into related work from paper
-
-\section{Matching feature points}
-Basically c/p from paper, but better figures and maybe more explanations
- - Add path about graphs and how they are formed. Make sure to explain 
- the clustering in more detail and make it easier to understand
- - Add a good explanation for new figures and how the precision and 
- recall are calculated. This should appear somewhere before results.
- - Add part on spectral matching and modify accordingly. Make sure to 
- underline how the second plot shows how the geometric method is 
- independent of MMC and that they combined yield greater results.
-
-\subsection{Proposed Matching Methods}
-\label{S:MatchingMethods}
-
-\subsubsection{Mirror Match (\emph{MM})}
-
-\begin{figure}
-	\centering%
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
-			\caption{Source image pair}
-			\label{fig:pitts_source}
-		\end{subfigure}%
-		\\ %
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
-			\caption{Feature points}
-			\label{fig:pitts_keypoints}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
-			\caption{\emph{Ratio}}
-			\label{fig:unique}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
-			\caption{\emph{MM} intermediate result}
-			\label{fig:within}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
-			\caption{\emph{MM} final result}
-			\label{fig:without}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
-			\caption{\emph{MMC} Partition Example}
-			\label{fig:pitts_partition}
-		\end{subfigure}%
-	\caption{Feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-	(c) Result of \emph{Ratio} matching. 
-  (d) All matches found by \emph{MM}, including intra-image matches. 
-	(e) Final \emph{MM} result. 
-	(f) Example of a partition of feature points after clustering, which 
-includes similar feature points from building windows and shirt patterns.}%
-	\label{fig:comparemirror}%
-\end{figure}%
-
-%
-The central idea behind \emph{MM} is to match features of $n$ images by 
-taking every feature from all $n$ images and matching it against every 
-other feature from the same set. We can then discard the correspondences 
-that match two points within the same image. Algorithm~\ref{alg-mm} details  
-the implementation of \emph{MM}.
-%
-\begin{algorithm}
-\caption{Mirror Match (\emph{MM})}
-\label{alg-mm}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
-\State $features\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Acquisition Stage
-	\State $features\gets features \cup getFeatures(I_i)$
-\EndFor
-\ForAll{$f_i \in features$} \Comment Matching Stage
-	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
-	\left\{f_i\right\})$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-		\State $matches_{init} \gets matches_{init} \cup \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
-Stage
-\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
-getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
-		\State $matches_{final} \gets (f_i, f_j)$
-	\EndIf
-\EndFor \\
-\Return $matches_{final}$
-\end{algorithmic}
-%}
-\end{algorithm}
-%
-In the acquisition stage we gather all features in the set of images.  
-In the matching stage these features are matched using $k$-nearest 
-neighbors.  For any given feature $f_i$ the two most similar neighbors 
-are returned, and we calculate the ratio between them as proposed in 
-\cite{lowe2004sift}.  Any correspondence with a ratio above the 
-threshold supplied will be discarded. Finally in the filter stage we 
-check that matches are from different images and discard all matches 
-that are not symmetric.
-%
-%\begin{figure*}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image pair}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-%			\caption{Feature points}
-%			\label{fig:pitts_keypoints}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_off}
-%			\caption{\emph{Ratio}}
-%			\label{fig:unique}
-%		\end{subfigure}%
-%	}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
-%			\caption{\emph{MM} intermediate result}
-%			\label{fig:within}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match}
-%			\caption{\emph{MM} final result}
-%			\label{fig:without}
-%		\end{subfigure}%
-%		\enspace%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{\emph{MMC} Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-%(c) Result of \emph{Ratio} matching the two images.% 
-%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
-%	(e) Final \emph{MM} result with the intra-image matches removed. 
-%	(f) Example of a partition of feature points after clustering. This partition 
-%includes similar feature points around the windows of a building and the patterns of a shirt.}%
-%	\label{fig:comparemirror}%
-%\end{figure*}%
-
-Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} 
-using an example image pair from the Gallagher dataset 
-\cite{gallagher2008}.
-With \emph{Ratio} (Figure~\ref{fig:unique}), many incorrect matches occur 
-in the fence towards the bottom of the image.
-When we match all feature points together, many of these incorrect 
-matches are eliminated, because points in the fence match with other 
-points in the fence in the same image (Figures~\ref{fig:within} and
-\ref{fig:without}).
-
-\subsubsection{Mirror Match with Clustering (\emph{MMC})}
-%
-In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
-non-geometric feature matching by clustering feature points by 
-similarity. This process yields partitions of fairly similar feature 
-points that we can match using the same approach as \emph{MM}.  
-Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
-
-Before we introduce the implementation details we will go over the 
-problem of graph clustering and how it relates to feature matching.
-
-Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-points in an image and returns their matching score, we can define a 
-matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-as the \emph{adjecency matrix} of the fully connected graph where each 
-vertex corresponds to a keypoint and the edge between two vertices has a 
-weight equal to the distance between the two corresponding keypoints.
-
-This representation reduces the problem of partitioning the keypoints 
-into groups to that of graph clustering or community structure depending 
-on the context. In the literature there are various ways of clustering a 
-graph according to different measures of what constitutes an optimal 
-partitioning. Traditionally the most used clustering algorithms have 
-been K-means and spectral clustering, but in recent years a host of new 
-algorithms have been proposed based on both Newman's concept of graph 
-modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-well as information theoretical measures\footnote{See for example 
-\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-new algorithms differ from K-means clustering and Spectral clustering 
-in that they do not require the number of expected to clusters to be 
-specified beforehand\footnote{Among the aforementioned methods, this is 
-true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-tests done using randomly generated graphs with a known partitioning 
-\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-markedly better than spectral clustering and 
-K-means\cite{lancichinetti2009}.
-
-The performance of clustering algorithms is a complicated issue, since 
-an optimal clustering given the same graph can vary depending on the 
-application. Spectral clustering for example will usually return a 
-partitioning where each partition is roughly equal in size\footnote{As 
-mentioned in \cite{von2007}} while the Louvain 
-clustering\cite{blondel2008} might return partitions of very uneven 
-size, even if the modularity measurement has been shown to penalize very 
-small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-depending on the application, but when clustering feature points, 
-maintaining clusters of an even size usually means that some clusters 
-will be '\emph{catch-all}' clusters where the feature points that do 
-not fit anywhere else are grouped together. The necessity of specifying 
-the amount of partitions in for example Spectral clustering or Pott's 
-model clustering further exacerbates the issue since smaller partitions 
-are then combined into one to achieve the right amount of partitions.
-
-%
-\begin{algorithm}
-\caption{Mirror Match with Clustering (\emph{MMC})}
-\label{alg-mmc}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $M\gets \varnothing$
-\State $F\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather features
-	\State $f_i\gets getFeatures(I_i)$
-	\State $F\gets F \cup f_i$
-\EndFor
-\State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $A_{norm}\gets 1 - normalize(A)$
-\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $P\gets cluster(A_{pruned})$
-\ForAll{$p \in P$} \Comment p is a set of feature points
-	\State $M\gets M \cup getMatches(p, t, F)$
-\EndFor \\
-\Return matches
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\begin{figure}[t]
-    \centering
-\makebox[\textwidth][c]{%
-    \includegraphics[width=1.1\textwidth]{images/MMC_graph}
-    \label{fig:graph}
-}
-    \caption{The partitioned feature graph. Each vertex represents a 
-        feature point; lines indicate high similarity between points. A 
-        partition is a connected group with the same color. The border 
-        color of each node indicates which image it belongs to.  Zooming 
-    into a subsection of the graph (right part), the various cluster 
-sizes can be seen, ranging from hundreds of feature points to only two 
-or three.}
-	\label{fig:graph}
-\end{figure}
-
-We use the Louvain Method \cite{blondel2008} for clustering feature 
-points, since it is relatively fast and performs well 
-\cite{lancichinetti2009}, does not require parameters 
-\cite{blondel2008}, and does not emphasize partitions of equal size, as 
-opposed to spectral clustering or k-means \cite{von2007}, for example.
-While the Louvain clustering algorithm does not require any parameters 
-in itself, it tends towards clustering all feature points together in 
-the same partition if the graph is very connected.  To ensure that the 
-graph is well clustered, the adjacency matrix is pruned so that only 
-edges above a certain threshold are kept. From empirical analysis, 
-retaining the top 2.5\% of edges with the highest similarity seems to 
-work well in practice. Figure~\ref{fig:graph} shows the result of 
-clustering the feature points as a graph.
-%
-
-The partitions group feature points by similarity, which means that 
-repetitive structures such as buildings often appear in larger 
-partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
-%
-
-\begin{algorithm}
-\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
-\label{alg-getmatches}
-    \fontsize{10}{10}\selectfont
-    \begin{algorithmic}
-    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
-    all features
-    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
-        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
-    \If{$\left\vert edges \right\vert > 1$}
-        \State $matches \gets MMGet(p, t)$
-    \ElsIf{$\left\vert edges \right\vert = 1$}
-        \State $matches \gets RatioGet(p, features, t)$
-    \Else
-        \State $matches \gets \varnothing$
-    \EndIf
-
-    \Return matches
-    \end{algorithmic}
-\end{algorithm}
-
-The matching algorithm for \emph{MMC} detailed in 
-Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
-more than two elements using the \emph{MM} approach.  However, as can be 
-seen in the example in Figure~\ref{fig:MMC_graph}, many of the 
-partitions contain only two feature points from different images linked 
-by one edge. In this case, we compare the similarity of the these two 
-feature points with their second best match and remove matches where 
-this ratio lies above a certain threshold, like in the \emph{Ratio} 
-algorithm.  For example in the case of Figure~\ref{fig:pitts_partition}, 
-we have feature points from a building in one image grouped together 
-with points from a shirt pattern in another.  The nearest neighbor 
-method would have returned wrong matches, but since we match the 
-partition with \emph{MM}, points in the building end up matching other 
-points in the building, and no matches are returned.
-
-\subsection{Experiments}
-\label{S:Experiments}
-%
-To reliably measure the accuracy of a matching method on real images, we 
-either need a set of image pairs tied by a homography, or we have to 
-manually count the number of inliers. The latter becomes prohibitive for 
-large numbers of (non-trivial) images.
-
-Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
-set of test images to compare the performance of feature detectors. The 
-set covers different types of image variations, such as lighting change, 
-blur, rotation, and viewpoint change. Inspired by this dataset (in 
-particular the `Graf' image set) and motivated by the need for more 
-image pairs featuring viewpoint changes, we have compiled a set of 8 
-image pairs consisting of subjects taken from two different angles. The 
-images are collected from Flickr's database of images published under a 
-creative commons licence and feature murals, which makes it possible to 
-relate points in the image pairs with a homography since most of the 
-points in the images will be lying on a plane.  The images have been 
-cropped to show the same motive and resized to $900\times 600$ pixels.  
-This dataset will be referred to as the \emph{Murals} dataset.  
-Figure~\ref{fig:murals} shows one image from each pair.
-
-\begin{figure}[htb]
-    \makebox[1.0\textwidth][c]{%
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example1}
-			\label{fig:fairey1}
-	\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example2}
-			\label{fig:fairey2}
-		\end{subfigure}%
-		\enspace %
-        \begin{subfigure}[t]{0.77\textwidth}
-   		\centering
-   		\includegraphics[width=\columnwidth]{images/crop_examples}
-		\end{subfigure}%
-	}%
-	\caption{Sample test patches produced from an image pair.}
-	\label{fig:fairey}
-\end{figure}
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\textwidth]{images/murals}
-	\caption{Images in the \emph{Murals} test set.}
-	\label{fig:murals}
-\end{figure*}
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
-	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
-	\label{fig:Graf}
-\end{figure}
-
-\subsubsection{Experimental setup}
 We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
@@
 
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\columnwidth]{images/isomatch_partitions}
+	\caption{The result of partitioning feature points in two images.  
+	Each dot represents a feature point and feature points grouped with 
+the same color belong to the same partition.}
+	\label{fig:isomatch_partitions}
+\end{figure}
+
 The \emph{Isomatch} algorithm (Algorithm~\ref{alg-isodata}) 
@@
 addition that clusters are merged and split during the clustering 
-process. The initial set of matches are then filtered based on the 
-resulting regions. A match is kept only if it belongs to a region with 
-more than 5 matches and where half of the matches link the same two 
-regions. $P_{corr}$ in Algorithm~\ref{alg-isodata} is a matrix where 
-each row corresponds to a region in $im_1$, each column corresponds to a 
-region in $im_2$ and $P_{i,j}$ is the amount of matches going from 
-region $i$ to region $j$.
+process. In Figure~\ref{fig:isomatch_partitions} an example of a 
+partitioning can be seen. The initial set of matches are filtered based 
+on the resulting regions. A match is kept only if it at least half the 
+matches of the same region of origin also belong to the same region in 
+the other image.  $P_{corr}$ in Algorithm~\ref{alg-isodata} is a matrix 
+where each row corresponds to a region in $im_1$, each column 
+corresponds to a region in $im_2$ and $P_{i,j}$ is the amount of matches 
+going from region $i$ to region $j$.
 
@@
 
-\begin{algorithm}
+\begin{algorithm}[h!]
 \caption{Spectral Match (\emph{Spectral})}
@@
 \EndFor
+
 \Return $matches_{final}$
@@
 Leordeanu and Herbert proposes a simple affinity function to map the 
-pairwise closeness of two matches. Given a simple scene where no 
-rotation and excessive affine transformation takes place, it can 
-generally be assumed that the length and direction of the vector between
+pairwise distance of two matches. In a scene where no rotation and 
+excessive affine transformation takes place, it can generally be assumed 
+that the length and direction of the vector between
 the two feature points constituting the first match corresponds to the 
 length and direction of the vector between the two feature points 
-constituting the second match. They formulated an affinity function as 
-follows: \TODO: change this to real function
+constituting the second match. Given two matches $m_i = (f_{i,1}, 
+f_{i,2})$ and $m_j = (f_{j,1},f_{j,2})$ where $f_{k,n}$ is the feature 
+point of match $k$ in image $n$, we denote the euclidean distance 
+between feature points $f_{i,n}$ and $f_{j,n}$ in image $n$ as 
+$d_{i,j,n}$.  The affinity function assigning a score based on the 
+pairwise distance is then defined as follows:
 \begin{equation*}
-	S = \sum_{m_i, m_j \in T} M(m_i, m_j) = x^TMx
+	M(a,b) \begin{cases} 4.5 - \frac{\left(d_{i,j,1} - 
+		d_{i,j,2}\right)^2}{2\sigma^2}, & \mbox{if } \left\vert 
+				d_{i,j,1} - d_{i,j,2} \right\vert < 3\sigma \\ 0, & 
+				\mbox{otherwise}
+	\end{cases}
 \end{equation*}
-There are a number of occasions where this assumption no longer holds 
-true. A simple example would be matches between two images of the same 
-scene where one image is rotated $180\degrees$. However for a lot of 
-applications like panorama stitching
-where we assume that images are generally not rotated a lot in between 
-each other the assumption is accurate.
+In the equation above $\sigma$ is a stabilizing parameter that controls 
+the sensitivity of the score to deformations in the data. A larger 
+$\sigma$ will allow for larger deformations. In the experiments it is 
+fixed to 50. There are a number of occasions where the assumption that 
+pairwise matches should have the same distance doesn't hold true.  A 
+simple example would be matches between two images of the same scene 
+where one image is rotated $180^{\circ}$.  However for a lot of 
+applications like panorama stitching where we only see minor rotation 
+and change of perspective the assumption is accurate.
 
-%, which uses geometric information to improve the matching.  The 
-%comparison  with \emph{Ratio} serves to illustrate the relative 
-%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isomatch} is included to 
-%illustrate the performance of an algorithm relying on geometric 
-%constraints faced with image pairs that might not have any overlap.  
-The comparison was done using the \emph{Murals} dataset 
-(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
-from \cite{mikolajczyk2005performance}, and two 
-images\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher 
-dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
+In the implementation proposed by Leordeanu and Herbert 
+\cite{leordeanu2005spectral} the last step of the algorithm greedily 
+selects matches to ensure that matches are consistent, i.e.\ that two 
+feature points in one image don't match with the same feature point in 
+the other image. This is done by going through all the matches in the 
+order of their associated $x^{*}$ score and for each match eliminating 
+all matches in conflict with this match. This method ensure that as many
+matches are kept as possible since only the conflicting matches are 
+removed. However for cases where most feature points in one image will 
+not have a correspondence in the other other image (e.g.\ cases of 
+partial image overlap or object recognition) the greedy matching 
+algorithm will keep finding matches even after the actual 
+correspondences have already been found as long as they are consistent.
 
-Test sets were generated from the image pairs by cropping square patches of
-$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
-Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
-This ensures that patch pairs with no overlap still retain a general similarity to each 
-other, while patches that do overlap often only share a small 
-part of their area. Figure~\ref{fig:fairey} shows an example of 
-possible pairs of test image patches produced from a source image pair.  
-Producing $n$ such pairs allows us to test not just how well the 
-matching algorithm performs on a variety of overlaps but also how many 
-false positives we get on similar images that do not overlap at all. In 
-practice the amount of overlap between pairs in a test set will depend 
-on the overlap and viewpoint change in the source image pair.  To give a 
-rough idea, Table~\ref{table:overlap} shows the overlap of patch pairs 
-created from images 1 and 3 of the \emph{Graf} image set from 
-\cite{mikolajczyk2005performance}.
-
-\begin{table}[htb]
-\caption{Overlap in the set of 100 patch pairs created from two images 
-of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
-\label{table:overlap}
-    \centering
-%   \small
-\begin{tabular}{r*{3}{r}}
-\hline
-    Amount of overlap: & 0\% & $< 50$\% & $> 50$\%  \\
-    \noalign{\smallskip}
-	%
-    Number of patch pairs: & 21 & 54 & 25 \\
-    \hline
-\end{tabular}
-\end{table}
-
-Given a potential match between two pixels $p_1$ and $p_2$, $m = 
-\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
-$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
-two points satisfy the following criteria:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
-\end{equation*}
-That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here).
-
-\subsection{Results}
-\label{S:Results}
-
-Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
-generated from images 1 and 3 of the \emph{Graf} image set 
-(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
-\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isomatch} as a function of 
-the number of matches produced (which is achieved by varying thresholds 
-over a certain range). The results show that \emph{MM} and \emph{MMC} 
-consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
-percentage points above \emph{MM} when both are performing at optimal 
-accuracy.  Although \emph{Isomatch} exhibits a good performance on strict 
-thresholds (small number of matches), that quickly diminishes when more 
-matches are desired.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.13\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_graf}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
-		shows the result of 100 patch pairs generated from the source 
-		images shown to the left. The number of matches is the total 
-		number of matches for all 100 patch pairs.}
-	\label{fig:result_graf}
-\end{figure}
-
-To validate whether these results 
-generalize to other images, we tested the four algorithms on the 
-\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
-In total 900 different patch pairs were generated from 9 
-source image pairs.  The results are shown in Figure 
-\ref{fig:result_accumulated}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/result_accumulated}
-	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
-	\label{fig:result_accumulated}
-\end{figure}
-
-To further investigate the impact of viewpoint changes, we tested the 
-algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
-contains 5 images of the same mural taken with gradually increasing 
-viewpoint changes.  The first images are almost identical, while the 
-last are taken from very different angles. The results from   \emph{MMC} 
-and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
-viewpoint changes.
-The performance of \emph{MM} (not shown in the plot) is similar to 
-\emph{MMC}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
-	\caption{Results for viewpoint changes using the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
-	\label{fig:result_viewpoint}
-\end{figure}
-
-Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
-shows the results on 100 patch pairs generated 
-from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
-change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.15\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pitts}
-%		\end{subfigure}%
-		~%add desired spacing between images, e. g. ~, \quad, \qquad
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
-	\label{fig:result_pitts}
-\end{figure}
-
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isomatch} can be 
-implemented in $O(n\log n)$, where $n$ is the total number of feature 
-points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. However, it is 
-possible to approximate this in $O(n\log n)$ using search trees.
-
-As for speed, Table~\ref{table:running_times} shows the running time of 
-the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
-These numbers should be taken with a grain of salt, given that much of 
-the code behind \emph{MMC} and \emph{Isomatch} is implemented in Python, 
-whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
-computationally intensive operations in C++, which makes them much 
-faster.
-
-\begin{table}[htb]
-\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
-3.30~GHz with 8~GB memory.}
-\label{table:running_times}
-	\centering
-%	\small
-\begin{tabular}{r*{4}{c}}
-\hline
-	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isomatch} 
-	\\
-	\noalign{\smallskip} 
-	%
-	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
-	\hline
-\end{tabular}
-\end{table}
-%
-
-\section{Applications}
-
-In many areas of computer vision matching local feature points is a key 
-component, and matching algorithms have applications in problems such as
-scene matching, object recognition, near duplicate detection and 
-panorama recognition. To show the practical applications of the proposed 
-matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
-improve existing methods in near duplicate detection and panorama 
-recognition. These two problems were chosen because they both involve 
-matching images that might or might not overlap. These cases requires 
-matching algorithms that limit false positives since e.g. returning the 
-top $n$ matches for any given image pair would make it hard to 
-distinguish adjacent or duplicate images from non-adjacent or dissimilar
-image pairs. Near duplicate detection also constraints normal matching 
-algorithms from relying on geometric assumptions, since we have very few
-guarantees between two potential near duplicates that they should be 
-matched using any particular geometric heuristic. In this section, we 
-will first see \emph{MMC} applied to panorama recognition and alignment,
-and next \emph{MM} and \emph{MMC} applied to near duplicate detection.
-
-\subsection{Panorama Recognition and Alignment}
-One of the oldest practical problems approached in computer vision is 
-the automatic stitching of several source images into a bigger image, 
-such as panoramas and composite satellite photos\footnote{A brief 
-overview of the history of image stitching can be found in Szeliski's 
-book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
-As part of the process of stitching together images, the individual 
-images must be aligned and often transformed in perspective. Earlier 
-methods relied on minimizing pixel dissimilarities in overlapping images 
-while more recent methods have used local feature points to estimate the 
-correct image alignment. Using local feature points carry the additional 
-advantage that it is feasible to automatically recognize where each 
-source image belong in the final panorama.
-
-\begin{figure}[h]
-	\begin{subfigure}[t]{0.9\textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{images/pano_wide}
-        \label{fig:pano_images}
-		\caption{Source images}
-    \end{subfigure}%
-	\\
-	\centering
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-autostitch}
-        \label{fig:pano_autostitch}
-		\caption{Panorama by Autostitch}
-    \end{subfigure}%
-	~%add desired spacing between images, e. g. ~, \quad, \qquad
-	%(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-MMC}
-		\caption{Panorama by MMC}
-		\label{fig:pano_MMC}
-	\end{subfigure}%
-    \label{fig:pano_example}
-	\caption{An example of a difficult case for panorama recognition and 
-		alignment.  In a) the source images used to generate the 
-		panorama are displayed.\ b) shows the result of the Autostitch 
-		program from \cite{brown2007automatic} which fails to combine 
-		all images, while c) demonstrates the result of the simple 
-		panorama stitcher
-	using the proposed MMC algorithm. Here the two left images are 
-correctly linked}
-\end{figure}
-
-In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
-image can be assembled by collecting the feature points of all source 
-images and matching them to obtain a set of inter image matches.  By 
-using \emph{RANSAC}\footnote{RANdom SAmple Consensus, an iterative 
-    algorithm to estimate parameters from noisy data introduced in 
-Fischler and Bolles in 1981 \cite{fischler1981ransac}} to find matches 
-deemed as inliers between image pairs, they are able to recognize image 
-neighbors and align them to construct the final panorama.
-
-This process hinges on the effectiveness of the matching algorithm used 
-to match the feature points. Not only is it important that true pairs 
-are accurately matched, but since we are matching points in image pairs 
-that might not be adjacent in the final panorama, we also need to make 
-sure that we consistently reject false positives, i.e.\ proposed matches 
-that link feature points which don't correspond.
-
-To demonstrate the usefulness of \emph{MMC} applied to panorama 
-recognition and alignment we construct a simple panorama stitcher taking
-as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
-and returns as output a panoramic image stitched together from the 
-source images. Based on the matches found by applying \emph{MMC} to $I$, 
-the images are combined in an order corresponding to how many matches 
-connect them, as done by Brown and Lowe \cite{brown2007automatic}.
-
-Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
-provides a way to globally optimize the accuracy of the image alignment} 
-and a lot of image enhancements such as exposure adjustment and edge 
-blurring to provide a seamless panorama. While these additions improve 
-the end product, they don't influence the performance of panorama 
-alignment and recognition and haven't been included in the simple 
-comparison algorithm.
-
-Figure~\ref{fig:pano_example} shows an example where the added accuracy 
-of MMC enables us to correctly recognitize and align source images that 
-fail to be combined by Autostitch, a program using the algorithm 
-proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
-case the matching algorithm used in Autostitch fails to find sufficient 
-matches between two images pairs to correctly position them and 
-consequently doesn't produce a panorama containing all images as a 
-result.
-
-This example illustrates how an improved matching algorithm can be 
-applied to panorama recognition and alignment to allow for panoramas 
-created with images that have little overlap.
-% Maybe find example of images with identical features that would be 
-% hard to match?
-
-\subsection{Near Duplicate Detection}
-If we look at two images, we can often easily tell if one image 
-resembles the other enough to be redundant in a photo album. In computer 
-vision this task becomes a lot less trivial because our idea of a 
-duplicate image might only require there being some object or scene in 
-common between the image pair. In addition the object or scene might 
-have been taken from a different angle and under different camera 
-settings. Facing these challenges, a lot of work has been done trying to 
-reliably recognize duplicaes both with regards to corporate intellectual 
-property as well as consumer photo albums because both applications 
-provide useful tools.  A company might be interested in finding images 
-that are derived from their intellectual property, while consumers 
-taking vacation photos might be interested in grouping duplicate images 
-to allow for easier photo organization.
-
-Local features are often used to group similar images, either by looking
-at a histogram of descriptors \cite{wu2009bundling} or by looking at how
-well feature points match between images \cite{zhao2009scale},
-\cite{chu2010consumer}, \cite{vas2013cluster}. In the latter case 
-finding near duplicates means that we will be matching image pairs that 
-might or might not contain any actual matches. In this case we would 
-benefit from a reliable matching algorithm that minimizes false 
-positives, which is a characteristic of both \emph{MM} and \emph{MMC}.
-
-The \emph{PhotoCluster} method introduced by Vonikakis et al.  
-\cite{vas2013cluster} shows the best clustering performance on the 
-California-nd dataset \cite{jinda2012california} which contains a set of
-annotated vacation images similar to a typical photo album in a consumer
-product. \emph{PhotoCluster} works by grouping images in several steps 
-using first image metadata and global features to obtain a set of 
-proposed clusters. Then local features are used to find the best 
-matching images in these proposed clusters yielding the final groups of 
-near duplicate images. To show the viability of \emph{MMC} in the 
-application of near duplicated detection, we modify the PhotoCluster 
-method to use \emph{MMC} for matching images instead of \emph{Ratio} 
-which was previously used. Due to the time consumption of \emph{MMC}, 
-all images where resized to to 10\% before being compared. Outside of 
-that, the experiments were performed exactly as documented in 
-\cite{vas2013cluster}.
-
-\begin{table}[htb]
-\caption{Results from Near Duplicate Detection at 10\% scale}
-\label{table:ndd}
-	\centering
-%	\small
-\begin{tabular}{r*{2}{r}}
-\hline
-    Method: & Ratio & MMC   \\
-	\noalign{\smallskip}
-	%
-    F1 score: & 0.4654 & 0.5459 \\
-	\hline
-\end{tabular}
-\end{table}
-
-The results of the comparison can be seen in Table~\ref{table:nnd}. It 
-shows that \emph{MMC} improves performance by 8.05\% over the original 
-framework using \emph{Ratio} to match images. For comparison, the 
-performance improvement of \emph{PhotoCluster} compared to XMatch 
-\cite{zhao2009scale}, the second best performing algorithm on the 
-California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.
-
-\section{Summary}
-\label{S:Summary}
-
-This thesis has addressed the problem of matching feature points without 
-using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
-\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
-common idea that feature points should have better matches in another 
-image than in the image they came from to be considered good matches.  
-\emph{MMC} further improves on this idea by using the structure of the 
-similarity graph of the feature points.
-
-The algorithms show promising results when tested on the \emph{Murals} 
-data set. The results on 900 image pairs show that \emph{MM} and 
-\emph{MMC} generally outperform existing matching algorithms 
-\emph{Ratio}, \emph{Isomatch} and \emph{Spectral}. In addition \emph{MMC} 
-outperforms \emph{MM}.  We show that this result generalizes to 
-variations in viewpoint change by comparing \emph{MMC} to \emph{Ratio} 
-over a set of image pairs with an increasing magnitude of perspective 
-difference. We go on to apply the algorithms to a real life image case 
-featuring occlusion and a slight viewpoint change and show that the 
-performance of \emph{MM} and \emph{MMC} is consistent with the results 
-on \emph{Murals}. To show that \emph{MM} or \emph{MMC}
-can further improve the results of a geometrical method, we create 
-\emph{Spectral-MMC} by combining \emph{Spectral} and \emph{MMC} and 
-compare the three on the full \emph{Murals} dataset where it yields 
-results better than both \emph{Spectral} and \emph{MMC}.
-
-The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
-applying the algorithms to the problems of near duplicate detection and 
-for the case of \emph{MMC} to panorama recognition and alignment. For 
-the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
-improvement over \emph{Ratio} in a near duplicate detection framework 
-making use of local features. Similarly for panorama recognition and 
-alignment a simple panorama stitching method based on \emph{MMC} 
-succeeds in cases where \emph{Autostitch} is unable to recognize and 
-align the source images correctly. Both applications illustrate the 
-central role that performance of the matching algorithm has on tasks 
-that makes use of local features to match image pairs with potential 
-overlap.
-%
-
-\bibliographystyle{IEEEtran}
-\bibliography{bibliography}
-\end{document}
+Since the testing is done on images with partial overlap, the final set 
+of matches returned in Algorithm~\ref{alg-spectral} is the set of 
+matches where the association of the match with the optimal subset of 
+matches $T$ as measured by $x^{*}$ is above a certain threshold. For 
+experiments the set of initial matches were given by the best match per 
+feature point and the threshold was adjusted to allow for the best 50\% 
+to be included in the set of final matches. A rate less than 50\% 
+usually did not improve results, so to threshold the \emph{Spectral}
+algorithm we filter the output using the ratio between first and second
+best match as done in \emph{Ratio}.

### 2013-08-09 text/main/ch5_experiments.tex
Reorganized thesis

--- 2013-08-07 text/thesis.tex
@@
-%\documentclass[report]{IEEEtran}
-\documentclass{article}
-\usepackage{footnote}
-%\usepackage[font={small}]{caption}
-\usepackage{sidecap}
-\usepackage{graphicx}
-\usepackage{cite}
-\usepackage{hyperref}
-%\usepackage[stable]{footmisc}
-\usepackage{caption}
-\usepackage{adjustbox}
-\usepackage{subcaption}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\begin{document}
-
-\title{Reliable feature point matching}
-\author{Jonas Arnfred}
-
-\maketitle
-
-\section{Introduction}
-What is the subject of this thesis and in what part lies my 
-contribution?
-How is the report organized?
-
-\section{Background}
-Introduction to Computer Vision
- - Introduce common tasks that we are good at that computers aren't
- - Single in on tasks that we can solve using feature points
-
-Introduction to feature points
- - Global explanation of what they are and how they serve to solve the 
-problems mentioned before
- - How do we find them? (Examples making it intuitive why corners are 
-nice)
- - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
- Scale, \ldots, Affine)
- - Introduce SIFT and explain how the different problems are tackled in 
-SIFT)
- - Talk about other methods and how they are different
-
-Matching feature points
- - What applications require matching?
- - How is matching usually done
- - Segue into related work from paper
-
-\section{Matching feature points}
-Basically c/p from paper, but better figures and maybe more explanations
- - Add path about graphs and how they are formed. Make sure to explain 
- the clustering in more detail and make it easier to understand
- - Add a good explanation for new figures and how the precision and 
- recall are calculated. This should appear somewhere before results.
- - Add part on spectral matching and modify accordingly. Make sure to 
- underline how the second plot shows how the geometric method is 
- independent of MMC and that they combined yield greater results.
-
-\subsection{Proposed Matching Methods}
-\label{S:MatchingMethods}
-
-\subsubsection{Mirror Match (\emph{MM})}
-
-\begin{figure}
-	\centering%
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
-			\caption{Source image pair}
-			\label{fig:pitts_source}
-		\end{subfigure}%
-		\\ %
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
-			\caption{Feature points}
-			\label{fig:pitts_keypoints}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
-			\caption{\emph{Ratio}}
-			\label{fig:unique}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
-			\caption{\emph{MM} intermediate result}
-			\label{fig:within}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
-			\caption{\emph{MM} final result}
-			\label{fig:without}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
-			\caption{\emph{MMC} Partition Example}
-			\label{fig:pitts_partition}
-		\end{subfigure}%
-	\caption{Feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-	(c) Result of \emph{Ratio} matching. 
-  (d) All matches found by \emph{MM}, including intra-image matches. 
-	(e) Final \emph{MM} result. 
-	(f) Example of a partition of feature points after clustering, which 
-includes similar feature points from building windows and shirt patterns.}%
-	\label{fig:comparemirror}%
-\end{figure}%
-
-%
-The central idea behind \emph{MM} is to match features of $n$ images by 
-taking every feature from all $n$ images and matching it against every 
-other feature from the same set. We can then discard the correspondences 
-that match two points within the same image. Algorithm~\ref{alg-mm} details  
-the implementation of \emph{MM}.
-%
-\begin{algorithm}
-\caption{Mirror Match (\emph{MM})}
-\label{alg-mm}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
-\State $features\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Acquisition Stage
-	\State $features\gets features \cup getFeatures(I_i)$
-\EndFor
-\ForAll{$f_i \in features$} \Comment Matching Stage
-	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
-	\left\{f_i\right\})$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-		\State $matches_{init} \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
-Stage
-\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
-getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
-		\State $matches_{final} \gets (f_i, f_j)$
-	\EndIf
-\EndFor \\
-\Return $matches_{final}$
-\end{algorithmic}
-%}
-\end{algorithm}
-%
-In the acquisition stage we gather all features in the set of images.  
-In the matching stage these features are matched using $k$-nearest 
-neighbors.  For any given feature $f_i$ the two most similar neighbors 
-are returned, and we calculate the ratio between them as proposed in 
-\cite{lowe2004sift}.  Any correspondence with a ratio above the 
-threshold supplied will be discarded. Finally in the filter stage we 
-check that matches are from different images and discard all matches 
-that are not symmetric.
-%
-%\begin{figure*}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image pair}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-%			\caption{Feature points}
-%			\label{fig:pitts_keypoints}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_off}
-%			\caption{\emph{Ratio}}
-%			\label{fig:unique}
-%		\end{subfigure}%
-%	}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
-%			\caption{\emph{MM} intermediate result}
-%			\label{fig:within}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match}
-%			\caption{\emph{MM} final result}
-%			\label{fig:without}
-%		\end{subfigure}%
-%		\enspace%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{\emph{MMC} Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-%(c) Result of \emph{Ratio} matching the two images.% 
-%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
-%	(e) Final \emph{MM} result with the intra-image matches removed. 
-%	(f) Example of a partition of feature points after clustering. This partition 
-%includes similar feature points around the windows of a building and the patterns of a shirt.}%
-%	\label{fig:comparemirror}%
-%\end{figure*}%
-
-Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} 
-using an example image pair from the Gallagher dataset 
-\cite{gallagher2008}.
-With \emph{Ratio} (Figure~\ref{fig:unique}), many incorrect matches occur 
-in the fence towards the bottom of the image.
-When we match all feature points together, many of these incorrect 
-matches are eliminated, because points in the fence match with other 
-points in the fence in the same image (Figures~\ref{fig:within} and
-\ref{fig:without}).
-
-\subsubsection{Mirror Match with Clustering (\emph{MMC})}
-%
-In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
-non-geometric feature matching by clustering feature points by 
-similarity. This process yields partitions of fairly similar feature 
-points that we can match using the same approach as \emph{MM}.  
-Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
-
-Before we introduce the implementation details we will go over the 
-problem of graph clustering and how it relates to feature matching.
-
-Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-points in an image and returns their matching score, we can define a 
-matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-as the \emph{adjecency matrix} of the fully connected graph where each 
-vertex corresponds to a keypoint and the edge between two vertices has a 
-weight equal to the distance between the two corresponding keypoints.
-
-This representation reduces the problem of partitioning the keypoints 
-into groups to that of graph clustering or community structure depending 
-on the context. In the literature there are various ways of clustering a 
-graph according to different measures of what constitutes an optimal 
-partitioning. Traditionally the most used clustering algorithms have 
-been K-means and spectral clustering, but in recent years a host of new 
-algorithms have been proposed based on both Newman's concept of graph 
-modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-well as information theoretical measures\footnote{See for example 
-\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-new algorithms differ from K-means clustering and Spectral clustering 
-in that they do not require the number of expected to clusters to be 
-specified beforehand\footnote{Among the aforementioned methods, this is 
-true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-tests done using randomly generated graphs with a known partitioning 
-\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-markedly better than spectral clustering and 
-K-means\cite{lancichinetti2009}.
-
-The performance of clustering algorithms is a complicated issue, since 
-an optimal clustering given the same graph can vary depending on the 
-application. Spectral clustering for example will usually return a 
-partitioning where each partition is roughly equal in size\footnote{As 
-mentioned in \cite{von2007}} while the Louvain 
-clustering\cite{blondel2008} might return partitions of very uneven 
-size, even if the modularity measurement has been shown to penalize very 
-small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-depending on the application, but when clustering feature points, 
-maintaining clusters of an even size usually means that some clusters 
-will be '\emph{catch-all}' clusters where the feature points that do 
-not fit anywhere else are grouped together. The necessity of specifying 
-the amount of partitions in for example Spectral clustering or Pott's 
-model clustering further exacerbates the issue since smaller partitions 
-are then combined into one to achieve the right amount of partitions.
-
-%
-\begin{algorithm}
-\caption{Mirror Match with Clustering (\emph{MMC})}
-\label{alg-mmc}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $M\gets \varnothing$
-\State $F\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather features
-	\State $f_i\gets getFeatures(I_i)$
-	\State $F\gets F \cup f_i$
-\EndFor
-\State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $A_{norm}\gets 1 - normalize(A)$
-\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $P\gets cluster(A_{pruned})$
-\ForAll{$p \in P$} \Comment p is a set of feature points
-	\State $M\gets M \cup getMatches(p, t, F)$
-\EndFor \\
-\Return matches
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\begin{figure}[t]
-    \centering
-\makebox[\textwidth][c]{%
-    \includegraphics[width=1.1\textwidth]{images/MMC_graph}
-    \label{fig:graph}
-}
-    \caption{The partitioned feature graph. Each vertex represents a 
-        feature point; lines indicate high similarity between points. A 
-        partition is a connected group with the same color. The border 
-        color of each node indicates which image it belongs to.  Zooming 
-    into a subsection of the graph (right part), the various cluster 
-sizes can be seen, ranging from hundreds of feature points to only two 
-or three.}
-	\label{fig:graph}
-\end{figure}
-
-We use the Louvain Method \cite{blondel2008} for clustering feature 
-points, since it is relatively fast and performs well 
-\cite{lancichinetti2009}, does not require parameters 
-\cite{blondel2008}, and does not emphasize partitions of equal size, as 
-opposed to spectral clustering or k-means \cite{von2007}, for example.
-While the Louvain clustering algorithm does not require any parameters 
-in itself, it tends towards clustering all feature points together in 
-the same partition if the graph is very connected.  To ensure that the 
-graph is well clustered, the adjacency matrix is pruned so that only 
-edges above a certain threshold are kept. From empirical analysis, 
-retaining the top 2.5\% of edges with the highest similarity seems to 
-work well in practice. Figure~\ref{fig:graph} shows the result of 
-clustering the feature points as a graph.
-%
-
-The partitions group feature points by similarity, which means that 
-repetitive structures such as buildings often appear in larger 
-partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
-%
-
-\begin{algorithm}
-\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
-\label{alg-getmatches}
-    \fontsize{10}{10}\selectfont
-    \begin{algorithmic}
-    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
-    all features
-    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
-        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
-    \If{$\left\vert edges \right\vert > 1$}
-        \State $matches \gets MMGet(p, t)$
-    \ElsIf{$\left\vert edges \right\vert = 1$}
-        \State $matches \gets RatioGet(p, features, t)$
-    \Else
-        \State $matches \gets \varnothing$
-    \EndIf
-
-    \Return matches
-    \end{algorithmic}
-\end{algorithm}
-
-The matching algorithm for \emph{MMC} detailed in 
-Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
-more than two elements using the \emph{MM} approach.  However, as can be 
-seen in the example in Figure~\ref{fig:MMC_graph}, many of the 
-partitions contain only two feature points from different images linked 
-by one edge. In this case, we compare the similarity of the these two 
-feature points with their second best match and remove matches where 
-this ratio lies above a certain threshold, like in the \emph{Ratio} 
-algorithm.  For example in the case of Figure~\ref{fig:pitts_partition}, 
-we have feature points from a building in one image grouped together 
-with points from a shirt pattern in another.  The nearest neighbor 
-method would have returned wrong matches, but since we match the 
-partition with \emph{MM}, points in the building end up matching other 
-points in the building, and no matches are returned.
-
-\subsection{Experiments}
+\chapter{Experiments and Results}
 \label{S:Experiments}
@@
 
-\subsubsection{Experimental setup}
-We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
-\cite{lowe2004sift} as well as \emph{Isodata} \cite{das2008event} and 
-\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isodata} and 
-\emph{Spectral} uses geometric constraints, whereas \emph{Ratio} does 
-not.
-
-\begin{algorithm}
-\caption{Ratio Match (\emph{Ratio})}
-\label{alg-ratio}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
-\State $matches\gets \varnothing$
-\State $features_1 \gets getFeatures(im_1)$
-\State $features_2 \gets getFeatures(im_2)$
-\ForAll{$f_i \in features_1$}
-    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-        \State $matches \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\Return $matches$
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\emph{Ratio} (Algorithm~\ref{alg-ratio}) is the most straightforward of 
-the three reference algorithms. Feature points are matched using K 
-Nearest Neighbor and the similarity ratio between the best and second 
-best match is then compared to a threshold to decide if the match is 
-kept.
-
-%, which uses geometric information to improve the matching.  The 
-%comparison  with \emph{Ratio} serves to illustrate the relative 
-%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isodata} is included to illustrate 
-%the performance of an algorithm relying on geometric constraints faced 
-%with image pairs that might not have any overlap.  
 The comparison was done using the \emph{Murals} dataset 
@@
 
+The results are presented as \emph{precision} versus \emph{recall} 
+similar to \cite{ke2004pca} and \cite{mikolajczyk2005performance}.  
+Recall corresponds to the number of correct matches over the total 
+amount of possible correct matches in between the two images:
+\begin{equation*}
+	recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~ 
+	Matches}
+\end{equation*}
+This measure tells us how many thorough we are in finding all possible 
+matches that could be made between the two images. To decide whether a 
+match is correct, we use the following method:
 Given a potential match between two pixels $p_1$ and $p_2$, $m = 
@@
 \emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here).
+less than a certain threshold (we use $d_{\max}=5$ pixels here). To 
+count the number of possible matches we go over all possible 
+combinations of feature points between the two images, measure their 
+distance and count how many lie within the threshold.
+Precision on the other hand is measured by the amount of correct matches
+over the total amount of matches returned:
+\begin{equation*}
+	precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
+	~ \# ~ False ~ Matches}
+\end{equation*}
+This measures how accurate the set of returned matches from the 
+algorithm is. An algorithm that returns only a few matches out of many, 
+but most of them are correct will have a high precision and a low 
+recall, where as an algorithm that returns almost all possible matches, 
+both true and false will have a low precision but a high recall. The 
+ideal matching algorithm will be both precise but also return as many 
+correct matches as possible. However for many applications we only need 
+enough correct matches to align to the images, in which case we care 
+more about precision than recall.
 
-\subsection{Results}
+\section{Results}
 \label{S:Results}
@@
 (cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
-\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isodata} as a function of 
-the number of matches produced (which is achieved by varying thresholds 
-over a certain range). The results show that \emph{MM} and \emph{MMC} 
-consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
-percentage points above \emph{MM} when both are performing at optimal 
-accuracy.  Although \emph{Isodata} exhibits a good performance on strict 
-thresholds (small number of matches), that quickly diminishes when more 
-matches are desired.
+\emph{Ratio}, \emph{MM}, \emph{MMC}, \emph{Isomatch} and \emph{Spectral} 
+as a function of the number of matches produced (which is achieved by 
+varying thresholds over a certain range). The results show that 
+\emph{MM} and \emph{MMC} consistently outperform \emph{Ratio}; 
+\emph{MMC} generally lies 2-3 percentage points above \emph{MM} when 
+both are performing at optimal accuracy.  The geometric matching methods 
+\emph{Isomatch} and \emph{Spectral} outperform \emph{Ratio} but fall 
+short of \emph{MM} and \emph{MMC}.
 
 \begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.13\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+	\makebox[0.5\textwidth][c]{%
+		\begin{subfigure}[t]{.13\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/graf}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
    	%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
+		\begin{subfigure}[t]{.27\textwidth}
    		\centering
@@
    		%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
+		\end{subfigure}%
+	}%
 	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
@@
 
-To validate whether these results 
-generalize to other images, we tested the four algorithms on the 
-\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
-In total 900 different patch pairs were generated from 9 
-source image pairs.  The results are shown in Figure 
+To validate whether these results generalize to other images, we tested 
+the four algorithms on the \emph{Murals} dataset as well as the 
+\emph{Graf} pair tested above.  In total 900 different patch pairs were 
+generated from 9 source image pairs.  The results are shown in Figure 
 \ref{fig:result_accumulated}.
@@
 	\includegraphics[width=\columnwidth]{images/result_accumulated}
-	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
+	\caption{Results for 900 patch pairs extracted from the 
+	\emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} 
+	set.  The x-axis shows the accumulated returned matches for all 
+pairs.}
 	\label{fig:result_accumulated}
@@
 
-Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
-shows the results on 100 patch pairs generated 
-from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
-change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.
+Finally, as an example of a real life use case, 
+Figure~\ref{fig:result_pitts} shows the results on 100 patch pairs 
+generated from a typical holiday photo shot 
+(Figure~\ref{fig:pitts_source}) featuring occlusion and a slight 
+viewpoint change from the Gallagher dataset \cite{gallagher2008}.  The 
+performance is comparable to the murals, despite the lack of a simple 
+homographic mapping between the images.
 
 \begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.15\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pitts}
-%		\end{subfigure}%
+	\makebox[\textwidth][c]{%
+		\begin{subfigure}[t]{.2\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/pitts}
+		\end{subfigure}%
 		~%add desired spacing between images, e. g. ~, \quad, \qquad
 		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
+		\begin{subfigure}[t]{.8\textwidth}
    		\centering
    		\includegraphics[width=0.6\columnwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
+		\end{subfigure}%
+	}%
 	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
@@
 
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isodata} can be 
-implemented in $O(n\log n)$, where $n$ is the total number of feature 
-points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. However, it is 
-possible to approximate this in $O(n\log n)$ using search trees.
+In terms of computational complexity, \emph{Ratio}, \emph{MM}, and 
+\emph{Isomatch} can be implemented in $O(n\log n)$, where $n$ is the 
+total number of feature points. The performance of \emph{Spectral} is 
+upper bounded by $O(n^{3/2})$. Our current \emph{MMC} implementation has 
+a complexity of $O(n^2)$ due to the construction of a similarity matrix 
+of the feature points.  However, it is possible to approximate this in 
+$O(n\log n)$ using search trees.
 
@@
 %	\small
-\begin{tabular}{r*{4}{c}}
+\begin{tabular}{r*{5}{c}}
 \hline
-	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
-	\\
+	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} %
+& \emph{Isomatch} & \emph{Spectral}	\\
 	\noalign{\smallskip} 
 	%
-	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
+	Running time (seconds): & 21 & 23 & 2722 & 1146 & 994\\
 	\hline
@@
 \end{table}
-%
-
-\section{Applications}
-
-In many areas of computer vision matching local feature points is a key 
-component, and matching algorithms have applications in problems such as
-scene matching, object recognition, near duplicate detection and 
-panorama recognition. To show the practical applications of the proposed 
-matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
-improve existing methods in near duplicate detection and panorama 
-recognition. These two problems were chosen because they both involve 
-matching images that might or might not overlap. These cases requires 
-matching algorithms that limit false positives since e.g. returning the 
-top $n$ matches for any given image pair would make it hard to 
-distinguish adjacent or duplicate images from non-adjacent or dissimilar
-image pairs. Near duplicate detection also constraints normal matching 
-algorithms from relying on geometric assumptions, since we have very few
-guarantees between two potential near duplicates that they should be 
-matched using any particular geometric heuristic. In this section, we 
-will first see \emph{MMC} applied to panorama recognition and alignment,
-and next \emph{MM} and \emph{MMC} applied to near duplicate detection.
-
-\subsection{Panorama Recognition and Alignment}
-One of the oldest practical problems approached in computer vision is 
-the automatic stitching of several source images into a bigger image, 
-such as panoramas and composite satellite photos\footnote{A brief 
-overview of the history of image stitching can be found in Szeliski's 
-book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
-As part of the process of stitching together images, the individual 
-images must be aligned and often transformed in perspective. Earlier 
-methods relied on minimizing pixel dissimilarities in overlapping images 
-while more recent methods have used local feature points to estimate the 
-correct image alignment. Using local feature points carry the additional 
-advantage that it is feasible to automatically recognize where each 
-source image belong in the final panorama.
-
-\begin{figure}[h]
-	\begin{subfigure}[t]{0.9\textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{images/pano_wide}
-        \label{fig:pano_images}
-		\caption{Source images}
-    \end{subfigure}%
-	\\
-	\centering
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-autostitch}
-        \label{fig:pano_autostitch}
-		\caption{Panorama by Autostitch}
-    \end{subfigure}%
-	~%add desired spacing between images, e. g. ~, \quad, \qquad
-	%(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-MMC}
-		\caption{Panorama by MMC}
-		\label{fig:pano_MMC}
-	\end{subfigure}%
-    \label{fig:pano_example}
-	\caption{An example of a difficult case for panorama recognition and 
-		alignment.  In a) the source images used to generate the 
-		panorama are displayed.\ b) shows the result of the Autostitch 
-		program from \cite{brown2007automatic} which fails to combine 
-		all images, while c) demonstrates the result of the simple 
-		panorama stitcher
-	using the proposed MMC algorithm. Here the two left images are 
-correctly linked}
-\end{figure}
-
-In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
-image can be assembled by collecting the feature points of all source 
-images and matching them to obtain a set of inter image matches.  By 
-using \emph{RANSAC}\footnote{RANdom SAmple Consensus, an iterative 
-    algorithm to estimate parameters from noisy data introduced in 
-Fischler and Bolles in 1981 \cite{fischler1981ransac}} to find matches 
-deemed as inliers between image pairs, they are able to recognize image 
-neighbors and align them to construct the final panorama.
-
-This process hinges on the effectiveness of the matching algorithm used 
-to match the feature points. Not only is it important that true pairs 
-are accurately matched, but since we are matching points in image pairs 
-that might not be adjacent in the final panorama, we also need to make 
-sure that we consistently reject false positives, i.e.\ proposed matches 
-that link feature points which don't correspond.
-
-To demonstrate the usefulness of \emph{MMC} applied to panorama 
-recognition and alignment we construct a simple panorama stitcher taking
-as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
-and returns as output a panoramic image stitched together from the 
-source images. Based on the matches found by applying \emph{MMC} to $I$, 
-the images are combined in an order corresponding to how many matches 
-connect them, as done by Brown and Lowe \cite{brown2007automatic}.
-
-Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
-provides a way to globally optimize the accuracy of the image alignment} 
-and a lot of image enhancements such as exposure adjustment and edge 
-blurring to provide a seamless panorama. While these additions improve 
-the end product, they don't influence the performance of panorama 
-alignment and recognition and haven't been included in the simple 
-comparison algorithm.
-
-Figure~\ref{fig:pano_example} shows an example where the added accuracy 
-of MMC enables us to correctly recognitize and align source images that 
-fail to be combined by Autostitch, a program using the algorithm 
-proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
-case the matching algorithm used in Autostitch fails to find sufficient 
-matches between two images pairs to correctly position them and 
-consequently doesn't produce a panorama containing all images as a 
-result.
-
-This example illustrates how an improved matching algorithm can be 
-applied to panorama recognition and alignment to allow for panoramas 
-created with images that have little overlap.
-% Maybe find example of images with identical features that would be 
-% hard to match?
-
-\subsection{Near Duplicate Detection}
-If we look at two images, we can often easily tell if one image 
-resembles the other enough to be redundant in a photo album. In computer 
-vision this task becomes a lot less trivial because our idea of a 
-duplicate image might only require there being some object or scene in 
-common between the image pair. In addition the object or scene might 
-have been taken from a different angle and under different camera 
-settings. Facing these challenges, a lot of work has been done trying to 
-reliably recognize duplicaes both with regards to corporate intellectual 
-property as well as consumer photo albums because both applications 
-provide useful tools.  A company might be interested in finding images 
-that are derived from their intellectual property, while consumers 
-taking vacation photos might be interested in grouping duplicate images 
-to allow for easier photo organization.
-
-Local features are often used to group similar images, either by looking
-at a histogram of descriptors \cite{wu2009bundling} or by looking at how
-well feature points match between images \cite{zhao2009scale},
-\cite{chu2010consumer}, \cite{vas2013cluster}. In the latter case 
-finding near duplicates means that we will be matching image pairs that 
-might or might not contain any actual matches. In this case we would 
-benefit from a reliable matching algorithm that minimizes false 
-positives, which is a characteristic of both \emph{MM} and \emph{MMC}.
-
-The \emph{PhotoCluster} method introduced by Vonikakis et al.  
-\cite{vas2013cluster} shows the best clustering performance on the 
-California-nd dataset \cite{jinda2012california} which contains a set of
-annotated vacation images similar to a typical photo album in a consumer
-product. \emph{PhotoCluster} works by grouping images in several steps 
-using first image metadata and global features to obtain a set of 
-proposed clusters. Then local features are used to find the best 
-matching images in these proposed clusters yielding the final groups of 
-near duplicate images. To show the viability of \emph{MMC} in the 
-application of near duplicated detection, we modify the PhotoCluster 
-method to use \emph{MMC} for matching images instead of \emph{Ratio} 
-which was previously used. Due to the time consumption of \emph{MMC}, 
-all images where resized to to 10\% before being compared. Outside of 
-that, the experiments were performed exactly as documented in 
-\cite{vas2013cluster}.
-
-\begin{table}[htb]
-\caption{Results from Near Duplicate Detection at 10\% scale}
-\label{table:ndd}
-	\centering
-%	\small
-\begin{tabular}{r*{2}{r}}
-\hline
-    Method: & Ratio & MMC   \\
-	\noalign{\smallskip}
-	%
-    F1 score: & 0.4654 & 0.5459 \\
-	\hline
-\end{tabular}
-\end{table}
-
-The results of the comparison can be seen in Table~\ref{table:nnd}. It 
-shows that \emph{MMC} improves performance by 8.05\% over the original 
-framework using \emph{Ratio} to match images. For comparison, the 
-performance improvement of \emph{PhotoCluster} compared to XMatch 
-\cite{zhao2009scale}, the second best performing algorithm on the 
-California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.
-
-\section{Summary}
-\label{S:Summary}
-
-This thesis has addressed the problem of matching feature points without 
-using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
-\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
-common idea that feature points should have better matches in another 
-image than in the image they came from to be considered good matches.  
-\emph{MMC} further improves on this idea by using the structure of the 
-similarity graph of the feature points.
-
-The algorithms show promising results when tested on the \emph{Murals} 
-data set. The results on 900 image pairs show that \emph{MM} and 
-\emph{MMC} generally outperform existing matching algorithms 
-\emph{Ratio}, \emph{Isodata} and \emph{Spectral}. In addition \emph{MMC} 
-outperforms \emph{MM}.  We show that this result generalizes to 
-variations in viewpoint change by comparing \emph{MMC} to \emph{Ratio} 
-over a set of image pairs with an increasing magnitude of perspective 
-difference. We go on to apply the algorithms to a real life image case 
-featuring occlusion and a slight viewpoint change and show that the 
-performance of \emph{MM} and \emph{MMC} is consistent with the results 
-on \emph{Murals}. To show that \emph{MM} or \emph{MMC}
-can further improve the results of a geometrical method, we create 
-\emph{Spectral-MMC} by combining \emph{Spectral} and \emph{MMC} and 
-compare the three on the full \emph{Murals} dataset where it yields 
-results better than both \emph{Spectral} and \emph{MMC}.
-
-The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
-applying the algorithms to the problems of near duplicate detection and 
-for the case of \emph{MMC} to panorama recognition and alignment. For 
-the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
-improvement over \emph{Ratio} in a near duplicate detection framework 
-making use of local features. Similarly for panorama recognition and 
-alignment a simple panorama stitching method based on \emph{MMC} 
-succeeds in cases where \emph{Autostitch} is unable to recognize and 
-align the source images correctly. Both applications illustrate the 
-central role that performance of the matching algorithm has on tasks 
-that makes use of local features to match image pairs with potential 
-overlap.
-%
-
-\bibliographystyle{IEEEtran}
-\bibliography{bibliography}
-\end{document}

### 2013-08-09 text/main/ch6_applications.tex
Reorganized thesis

--- 2013-08-07 text/thesis.tex
@@
-%\documentclass[report]{IEEEtran}
-\documentclass{article}
-\usepackage{footnote}
-%\usepackage[font={small}]{caption}
-\usepackage{sidecap}
-\usepackage{graphicx}
-\usepackage{cite}
-\usepackage{hyperref}
-%\usepackage[stable]{footmisc}
-\usepackage{caption}
-\usepackage{adjustbox}
-\usepackage{subcaption}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\begin{document}
-
-\title{Reliable feature point matching}
-\author{Jonas Arnfred}
-
-\maketitle
-
-\section{Introduction}
-What is the subject of this thesis and in what part lies my 
-contribution?
-How is the report organized?
-
-\section{Background}
-Introduction to Computer Vision
- - Introduce common tasks that we are good at that computers aren't
- - Single in on tasks that we can solve using feature points
-
-Introduction to feature points
- - Global explanation of what they are and how they serve to solve the 
-problems mentioned before
- - How do we find them? (Examples making it intuitive why corners are 
-nice)
- - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
- Scale, \ldots, Affine)
- - Introduce SIFT and explain how the different problems are tackled in 
-SIFT)
- - Talk about other methods and how they are different
-
-Matching feature points
- - What applications require matching?
- - How is matching usually done
- - Segue into related work from paper
-
-\section{Matching feature points}
-Basically c/p from paper, but better figures and maybe more explanations
- - Add path about graphs and how they are formed. Make sure to explain 
- the clustering in more detail and make it easier to understand
- - Add a good explanation for new figures and how the precision and 
- recall are calculated. This should appear somewhere before results.
- - Add part on spectral matching and modify accordingly. Make sure to 
- underline how the second plot shows how the geometric method is 
- independent of MMC and that they combined yield greater results.
-
-\subsection{Proposed Matching Methods}
-\label{S:MatchingMethods}
-
-\subsubsection{Mirror Match (\emph{MM})}
-
-\begin{figure}
-	\centering%
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
-			\caption{Source image pair}
-			\label{fig:pitts_source}
-		\end{subfigure}%
-		\\ %
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
-			\caption{Feature points}
-			\label{fig:pitts_keypoints}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
-			\caption{\emph{Ratio}}
-			\label{fig:unique}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
-			\caption{\emph{MM} intermediate result}
-			\label{fig:within}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
-			\caption{\emph{MM} final result}
-			\label{fig:without}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
-			\caption{\emph{MMC} Partition Example}
-			\label{fig:pitts_partition}
-		\end{subfigure}%
-	\caption{Feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-	(c) Result of \emph{Ratio} matching. 
-  (d) All matches found by \emph{MM}, including intra-image matches. 
-	(e) Final \emph{MM} result. 
-	(f) Example of a partition of feature points after clustering, which 
-includes similar feature points from building windows and shirt patterns.}%
-	\label{fig:comparemirror}%
-\end{figure}%
-
-%
-The central idea behind \emph{MM} is to match features of $n$ images by 
-taking every feature from all $n$ images and matching it against every 
-other feature from the same set. We can then discard the correspondences 
-that match two points within the same image. Algorithm~\ref{alg-mm} details  
-the implementation of \emph{MM}.
-%
-\begin{algorithm}
-\caption{Mirror Match (\emph{MM})}
-\label{alg-mm}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
-\State $features\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Acquisition Stage
-	\State $features\gets features \cup getFeatures(I_i)$
-\EndFor
-\ForAll{$f_i \in features$} \Comment Matching Stage
-	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
-	\left\{f_i\right\})$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-		\State $matches_{init} \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
-Stage
-\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
-getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
-		\State $matches_{final} \gets (f_i, f_j)$
-	\EndIf
-\EndFor \\
-\Return $matches_{final}$
-\end{algorithmic}
-%}
-\end{algorithm}
-%
-In the acquisition stage we gather all features in the set of images.  
-In the matching stage these features are matched using $k$-nearest 
-neighbors.  For any given feature $f_i$ the two most similar neighbors 
-are returned, and we calculate the ratio between them as proposed in 
-\cite{lowe2004sift}.  Any correspondence with a ratio above the 
-threshold supplied will be discarded. Finally in the filter stage we 
-check that matches are from different images and discard all matches 
-that are not symmetric.
-%
-%\begin{figure*}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image pair}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-%			\caption{Feature points}
-%			\label{fig:pitts_keypoints}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_off}
-%			\caption{\emph{Ratio}}
-%			\label{fig:unique}
-%		\end{subfigure}%
-%	}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
-%			\caption{\emph{MM} intermediate result}
-%			\label{fig:within}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match}
-%			\caption{\emph{MM} final result}
-%			\label{fig:without}
-%		\end{subfigure}%
-%		\enspace%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{\emph{MMC} Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-%(c) Result of \emph{Ratio} matching the two images.% 
-%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
-%	(e) Final \emph{MM} result with the intra-image matches removed. 
-%	(f) Example of a partition of feature points after clustering. This partition 
-%includes similar feature points around the windows of a building and the patterns of a shirt.}%
-%	\label{fig:comparemirror}%
-%\end{figure*}%
-
-Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} 
-using an example image pair from the Gallagher dataset 
-\cite{gallagher2008}.
-With \emph{Ratio} (Figure~\ref{fig:unique}), many incorrect matches occur 
-in the fence towards the bottom of the image.
-When we match all feature points together, many of these incorrect 
-matches are eliminated, because points in the fence match with other 
-points in the fence in the same image (Figures~\ref{fig:within} and
-\ref{fig:without}).
-
-\subsubsection{Mirror Match with Clustering (\emph{MMC})}
-%
-In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
-non-geometric feature matching by clustering feature points by 
-similarity. This process yields partitions of fairly similar feature 
-points that we can match using the same approach as \emph{MM}.  
-Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
-
-Before we introduce the implementation details we will go over the 
-problem of graph clustering and how it relates to feature matching.
-
-Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-points in an image and returns their matching score, we can define a 
-matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-as the \emph{adjecency matrix} of the fully connected graph where each 
-vertex corresponds to a keypoint and the edge between two vertices has a 
-weight equal to the distance between the two corresponding keypoints.
-
-This representation reduces the problem of partitioning the keypoints 
-into groups to that of graph clustering or community structure depending 
-on the context. In the literature there are various ways of clustering a 
-graph according to different measures of what constitutes an optimal 
-partitioning. Traditionally the most used clustering algorithms have 
-been K-means and spectral clustering, but in recent years a host of new 
-algorithms have been proposed based on both Newman's concept of graph 
-modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-well as information theoretical measures\footnote{See for example 
-\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-new algorithms differ from K-means clustering and Spectral clustering 
-in that they do not require the number of expected to clusters to be 
-specified beforehand\footnote{Among the aforementioned methods, this is 
-true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-tests done using randomly generated graphs with a known partitioning 
-\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-markedly better than spectral clustering and 
-K-means\cite{lancichinetti2009}.
-
-The performance of clustering algorithms is a complicated issue, since 
-an optimal clustering given the same graph can vary depending on the 
-application. Spectral clustering for example will usually return a 
-partitioning where each partition is roughly equal in size\footnote{As 
-mentioned in \cite{von2007}} while the Louvain 
-clustering\cite{blondel2008} might return partitions of very uneven 
-size, even if the modularity measurement has been shown to penalize very 
-small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-depending on the application, but when clustering feature points, 
-maintaining clusters of an even size usually means that some clusters 
-will be '\emph{catch-all}' clusters where the feature points that do 
-not fit anywhere else are grouped together. The necessity of specifying 
-the amount of partitions in for example Spectral clustering or Pott's 
-model clustering further exacerbates the issue since smaller partitions 
-are then combined into one to achieve the right amount of partitions.
-
-%
-\begin{algorithm}
-\caption{Mirror Match with Clustering (\emph{MMC})}
-\label{alg-mmc}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $M\gets \varnothing$
-\State $F\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather features
-	\State $f_i\gets getFeatures(I_i)$
-	\State $F\gets F \cup f_i$
-\EndFor
-\State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $A_{norm}\gets 1 - normalize(A)$
-\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $P\gets cluster(A_{pruned})$
-\ForAll{$p \in P$} \Comment p is a set of feature points
-	\State $M\gets M \cup getMatches(p, t, F)$
-\EndFor \\
-\Return matches
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\begin{figure}[t]
-    \centering
-\makebox[\textwidth][c]{%
-    \includegraphics[width=1.1\textwidth]{images/MMC_graph}
-    \label{fig:graph}
-}
-    \caption{The partitioned feature graph. Each vertex represents a 
-        feature point; lines indicate high similarity between points. A 
-        partition is a connected group with the same color. The border 
-        color of each node indicates which image it belongs to.  Zooming 
-    into a subsection of the graph (right part), the various cluster 
-sizes can be seen, ranging from hundreds of feature points to only two 
-or three.}
-	\label{fig:graph}
-\end{figure}
-
-We use the Louvain Method \cite{blondel2008} for clustering feature 
-points, since it is relatively fast and performs well 
-\cite{lancichinetti2009}, does not require parameters 
-\cite{blondel2008}, and does not emphasize partitions of equal size, as 
-opposed to spectral clustering or k-means \cite{von2007}, for example.
-While the Louvain clustering algorithm does not require any parameters 
-in itself, it tends towards clustering all feature points together in 
-the same partition if the graph is very connected.  To ensure that the 
-graph is well clustered, the adjacency matrix is pruned so that only 
-edges above a certain threshold are kept. From empirical analysis, 
-retaining the top 2.5\% of edges with the highest similarity seems to 
-work well in practice. Figure~\ref{fig:graph} shows the result of 
-clustering the feature points as a graph.
-%
-
-The partitions group feature points by similarity, which means that 
-repetitive structures such as buildings often appear in larger 
-partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
-%
-
-\begin{algorithm}
-\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
-\label{alg-getmatches}
-    \fontsize{10}{10}\selectfont
-    \begin{algorithmic}
-    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
-    all features
-    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
-        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
-    \If{$\left\vert edges \right\vert > 1$}
-        \State $matches \gets MMGet(p, t)$
-    \ElsIf{$\left\vert edges \right\vert = 1$}
-        \State $matches \gets RatioGet(p, features, t)$
-    \Else
-        \State $matches \gets \varnothing$
-    \EndIf
-
-    \Return matches
-    \end{algorithmic}
-\end{algorithm}
-
-The matching algorithm for \emph{MMC} detailed in 
-Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
-more than two elements using the \emph{MM} approach.  However, as can be 
-seen in the example in Figure~\ref{fig:MMC_graph}, many of the 
-partitions contain only two feature points from different images linked 
-by one edge. In this case, we compare the similarity of the these two 
-feature points with their second best match and remove matches where 
-this ratio lies above a certain threshold, like in the \emph{Ratio} 
-algorithm.  For example in the case of Figure~\ref{fig:pitts_partition}, 
-we have feature points from a building in one image grouped together 
-with points from a shirt pattern in another.  The nearest neighbor 
-method would have returned wrong matches, but since we match the 
-partition with \emph{MM}, points in the building end up matching other 
-points in the building, and no matches are returned.
-
-\subsection{Experiments}
-\label{S:Experiments}
-%
-To reliably measure the accuracy of a matching method on real images, we 
-either need a set of image pairs tied by a homography, or we have to 
-manually count the number of inliers. The latter becomes prohibitive for 
-large numbers of (non-trivial) images.
-
-Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
-set of test images to compare the performance of feature detectors. The 
-set covers different types of image variations, such as lighting change, 
-blur, rotation, and viewpoint change. Inspired by this dataset (in 
-particular the `Graf' image set) and motivated by the need for more 
-image pairs featuring viewpoint changes, we have compiled a set of 8 
-image pairs consisting of subjects taken from two different angles. The 
-images are collected from Flickr's database of images published under a 
-creative commons licence and feature murals, which makes it possible to 
-relate points in the image pairs with a homography since most of the 
-points in the images will be lying on a plane.  The images have been 
-cropped to show the same motive and resized to $900\times 600$ pixels.  
-This dataset will be referred to as the \emph{Murals} dataset.  
-Figure~\ref{fig:murals} shows one image from each pair.
-
-\begin{figure}[htb]
-    \makebox[1.0\textwidth][c]{%
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example1}
-			\label{fig:fairey1}
-	\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example2}
-			\label{fig:fairey2}
-		\end{subfigure}%
-		\enspace %
-        \begin{subfigure}[t]{0.77\textwidth}
-   		\centering
-   		\includegraphics[width=\columnwidth]{images/crop_examples}
-		\end{subfigure}%
-	}%
-	\caption{Sample test patches produced from an image pair.}
-	\label{fig:fairey}
-\end{figure}
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\textwidth]{images/murals}
-	\caption{Images in the \emph{Murals} test set.}
-	\label{fig:murals}
-\end{figure*}
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
-	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
-	\label{fig:Graf}
-\end{figure}
-
-\subsubsection{Experimental setup}
-We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
-\cite{lowe2004sift} as well as \emph{Isodata} \cite{das2008event} and 
-\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isodata} and 
-\emph{Spectral} uses geometric constraints, whereas \emph{Ratio} does 
-not.
-
-\begin{algorithm}
-\caption{Ratio Match (\emph{Ratio})}
-\label{alg-ratio}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
-\State $matches\gets \varnothing$
-\State $features_1 \gets getFeatures(im_1)$
-\State $features_2 \gets getFeatures(im_2)$
-\ForAll{$f_i \in features_1$}
-    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-        \State $matches \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\Return $matches$
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\emph{Ratio} (Algorithm~\ref{alg-ratio}) is the most straightforward of 
-the three reference algorithms. Feature points are matched using K 
-Nearest Neighbor and the similarity ratio between the best and second 
-best match is then compared to a threshold to decide if the match is 
-kept.
-
-%, which uses geometric information to improve the matching.  The 
-%comparison  with \emph{Ratio} serves to illustrate the relative 
-%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isodata} is included to illustrate 
-%the performance of an algorithm relying on geometric constraints faced 
-%with image pairs that might not have any overlap.  
-The comparison was done using the \emph{Murals} dataset 
-(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
-from \cite{mikolajczyk2005performance}, and two 
-images\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher 
-dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
-
-Test sets were generated from the image pairs by cropping square patches of
-$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
-Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
-This ensures that patch pairs with no overlap still retain a general similarity to each 
-other, while patches that do overlap often only share a small 
-part of their area. Figure~\ref{fig:fairey} shows an example of 
-possible pairs of test image patches produced from a source image pair.  
-Producing $n$ such pairs allows us to test not just how well the 
-matching algorithm performs on a variety of overlaps but also how many 
-false positives we get on similar images that do not overlap at all. In 
-practice the amount of overlap between pairs in a test set will depend 
-on the overlap and viewpoint change in the source image pair.  To give a 
-rough idea, Table~\ref{table:overlap} shows the overlap of patch pairs 
-created from images 1 and 3 of the \emph{Graf} image set from 
-\cite{mikolajczyk2005performance}.
-
-\begin{table}[htb]
-\caption{Overlap in the set of 100 patch pairs created from two images 
-of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
-\label{table:overlap}
-    \centering
-%   \small
-\begin{tabular}{r*{3}{r}}
-\hline
-    Amount of overlap: & 0\% & $< 50$\% & $> 50$\%  \\
-    \noalign{\smallskip}
-	%
-    Number of patch pairs: & 21 & 54 & 25 \\
-    \hline
-\end{tabular}
-\end{table}
-
-Given a potential match between two pixels $p_1$ and $p_2$, $m = 
-\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
-$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
-two points satisfy the following criteria:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
-\end{equation*}
-That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here).
-
-\subsection{Results}
-\label{S:Results}
-
-Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
-generated from images 1 and 3 of the \emph{Graf} image set 
-(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
-\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isodata} as a function of 
-the number of matches produced (which is achieved by varying thresholds 
-over a certain range). The results show that \emph{MM} and \emph{MMC} 
-consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
-percentage points above \emph{MM} when both are performing at optimal 
-accuracy.  Although \emph{Isodata} exhibits a good performance on strict 
-thresholds (small number of matches), that quickly diminishes when more 
-matches are desired.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.13\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_graf}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
-		shows the result of 100 patch pairs generated from the source 
-		images shown to the left. The number of matches is the total 
-		number of matches for all 100 patch pairs.}
-	\label{fig:result_graf}
-\end{figure}
-
-To validate whether these results 
-generalize to other images, we tested the four algorithms on the 
-\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
-In total 900 different patch pairs were generated from 9 
-source image pairs.  The results are shown in Figure 
-\ref{fig:result_accumulated}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/result_accumulated}
-	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
-	\label{fig:result_accumulated}
-\end{figure}
-
-To further investigate the impact of viewpoint changes, we tested the 
-algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
-contains 5 images of the same mural taken with gradually increasing 
-viewpoint changes.  The first images are almost identical, while the 
-last are taken from very different angles. The results from   \emph{MMC} 
-and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
-viewpoint changes.
-The performance of \emph{MM} (not shown in the plot) is similar to 
-\emph{MMC}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
-	\caption{Results for viewpoint changes using the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
-	\label{fig:result_viewpoint}
-\end{figure}
-
-Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
-shows the results on 100 patch pairs generated 
-from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
-change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.15\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pitts}
-%		\end{subfigure}%
-		~%add desired spacing between images, e. g. ~, \quad, \qquad
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
-	\label{fig:result_pitts}
-\end{figure}
-
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isodata} can be 
-implemented in $O(n\log n)$, where $n$ is the total number of feature 
-points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. However, it is 
-possible to approximate this in $O(n\log n)$ using search trees.
-
-As for speed, Table~\ref{table:running_times} shows the running time of 
-the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
-These numbers should be taken with a grain of salt, given that much of 
-the code behind \emph{MMC} and \emph{Isodata} is implemented in Python, 
-whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
-computationally intensive operations in C++, which makes them much 
-faster.
-
-\begin{table}[htb]
-\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
-3.30~GHz with 8~GB memory.}
-\label{table:running_times}
-	\centering
-%	\small
-\begin{tabular}{r*{4}{c}}
-\hline
-	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
-	\\
-	\noalign{\smallskip} 
-	%
-	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
-	\hline
-\end{tabular}
-\end{table}
-%
-
-\section{Applications}
+\chapter{Applications}
 
@@
 California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.
-
-\section{Summary}
-\label{S:Summary}
-
-This thesis has addressed the problem of matching feature points without 
-using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
-\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
-common idea that feature points should have better matches in another 
-image than in the image they came from to be considered good matches.  
-\emph{MMC} further improves on this idea by using the structure of the 
-similarity graph of the feature points.
-
-The algorithms show promising results when tested on the \emph{Murals} 
-data set. The results on 900 image pairs show that \emph{MM} and 
-\emph{MMC} generally outperform existing matching algorithms 
-\emph{Ratio}, \emph{Isodata} and \emph{Spectral}. In addition \emph{MMC} 
-outperforms \emph{MM}.  We show that this result generalizes to 
-variations in viewpoint change by comparing \emph{MMC} to \emph{Ratio} 
-over a set of image pairs with an increasing magnitude of perspective 
-difference. We go on to apply the algorithms to a real life image case 
-featuring occlusion and a slight viewpoint change and show that the 
-performance of \emph{MM} and \emph{MMC} is consistent with the results 
-on \emph{Murals}. To show that \emph{MM} or \emph{MMC}
-can further improve the results of a geometrical method, we create 
-\emph{Spectral-MMC} by combining \emph{Spectral} and \emph{MMC} and 
-compare the three on the full \emph{Murals} dataset where it yields 
-results better than both \emph{Spectral} and \emph{MMC}.
-
-The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
-applying the algorithms to the problems of near duplicate detection and 
-for the case of \emph{MMC} to panorama recognition and alignment. For 
-the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
-improvement over \emph{Ratio} in a near duplicate detection framework 
-making use of local features. Similarly for panorama recognition and 
-alignment a simple panorama stitching method based on \emph{MMC} 
-succeeds in cases where \emph{Autostitch} is unable to recognize and 
-align the source images correctly. Both applications illustrate the 
-central role that performance of the matching algorithm has on tasks 
-that makes use of local features to match image pairs with potential 
-overlap.
-%
-
-\bibliographystyle{IEEEtran}
-\bibliography{bibliography}
-\end{document}

### 2013-08-09 text/main/ch7_summary.tex
Reorganized thesis

--- 2013-08-07 text/thesis.tex
@@
-%\documentclass[report]{IEEEtran}
-\documentclass{article}
-\usepackage{footnote}
-%\usepackage[font={small}]{caption}
-\usepackage{sidecap}
-\usepackage{graphicx}
-\usepackage{cite}
-\usepackage{hyperref}
-%\usepackage[stable]{footmisc}
-\usepackage{caption}
-\usepackage{adjustbox}
-\usepackage{subcaption}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-\begin{document}
-
-\title{Reliable feature point matching}
-\author{Jonas Arnfred}
-
-\maketitle
-
-\section{Introduction}
-What is the subject of this thesis and in what part lies my 
-contribution?
-How is the report organized?
-
-\section{Background}
-Introduction to Computer Vision
- - Introduce common tasks that we are good at that computers aren't
- - Single in on tasks that we can solve using feature points
-
-Introduction to feature points
- - Global explanation of what they are and how they serve to solve the 
-problems mentioned before
- - How do we find them? (Examples making it intuitive why corners are 
-nice)
- - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
- Scale, \ldots, Affine)
- - Introduce SIFT and explain how the different problems are tackled in 
-SIFT)
- - Talk about other methods and how they are different
-
-Matching feature points
- - What applications require matching?
- - How is matching usually done
- - Segue into related work from paper
-
-\section{Matching feature points}
-Basically c/p from paper, but better figures and maybe more explanations
- - Add path about graphs and how they are formed. Make sure to explain 
- the clustering in more detail and make it easier to understand
- - Add a good explanation for new figures and how the precision and 
- recall are calculated. This should appear somewhere before results.
- - Add part on spectral matching and modify accordingly. Make sure to 
- underline how the second plot shows how the geometric method is 
- independent of MMC and that they combined yield greater results.
-
-\subsection{Proposed Matching Methods}
-\label{S:MatchingMethods}
-
-\subsubsection{Mirror Match (\emph{MM})}
-
-\begin{figure}
-	\centering%
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
-			\caption{Source image pair}
-			\label{fig:pitts_source}
-		\end{subfigure}%
-		\\ %
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
-			\caption{Feature points}
-			\label{fig:pitts_keypoints}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
-			\caption{\emph{Ratio}}
-			\label{fig:unique}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
-			\caption{\emph{MM} intermediate result}
-			\label{fig:within}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
-			\caption{\emph{MM} final result}
-			\label{fig:without}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
-			\caption{\emph{MMC} Partition Example}
-			\label{fig:pitts_partition}
-		\end{subfigure}%
-	\caption{Feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-	(c) Result of \emph{Ratio} matching. 
-  (d) All matches found by \emph{MM}, including intra-image matches. 
-	(e) Final \emph{MM} result. 
-	(f) Example of a partition of feature points after clustering, which 
-includes similar feature points from building windows and shirt patterns.}%
-	\label{fig:comparemirror}%
-\end{figure}%
-
-%
-The central idea behind \emph{MM} is to match features of $n$ images by 
-taking every feature from all $n$ images and matching it against every 
-other feature from the same set. We can then discard the correspondences 
-that match two points within the same image. Algorithm~\ref{alg-mm} details  
-the implementation of \emph{MM}.
-%
-\begin{algorithm}
-\caption{Mirror Match (\emph{MM})}
-\label{alg-mm}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
-\State $features\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Acquisition Stage
-	\State $features\gets features \cup getFeatures(I_i)$
-\EndFor
-\ForAll{$f_i \in features$} \Comment Matching Stage
-	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
-	\left\{f_i\right\})$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-		\State $matches_{init} \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
-Stage
-\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
-getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
-		\State $matches_{final} \gets (f_i, f_j)$
-	\EndIf
-\EndFor \\
-\Return $matches_{final}$
-\end{algorithmic}
-%}
-\end{algorithm}
-%
-In the acquisition stage we gather all features in the set of images.  
-In the matching stage these features are matched using $k$-nearest 
-neighbors.  For any given feature $f_i$ the two most similar neighbors 
-are returned, and we calculate the ratio between them as proposed in 
-\cite{lowe2004sift}.  Any correspondence with a ratio above the 
-threshold supplied will be discarded. Finally in the filter stage we 
-check that matches are from different images and discard all matches 
-that are not symmetric.
-%
-%\begin{figure*}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image pair}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-%			\caption{Feature points}
-%			\label{fig:pitts_keypoints}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_off}
-%			\caption{\emph{Ratio}}
-%			\label{fig:unique}
-%		\end{subfigure}%
-%	}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
-%			\caption{\emph{MM} intermediate result}
-%			\label{fig:within}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match}
-%			\caption{\emph{MM} final result}
-%			\label{fig:without}
-%		\end{subfigure}%
-%		\enspace%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{\emph{MMC} Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-%(c) Result of \emph{Ratio} matching the two images.% 
-%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
-%	(e) Final \emph{MM} result with the intra-image matches removed. 
-%	(f) Example of a partition of feature points after clustering. This partition 
-%includes similar feature points around the windows of a building and the patterns of a shirt.}%
-%	\label{fig:comparemirror}%
-%\end{figure*}%
-
-Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} 
-using an example image pair from the Gallagher dataset 
-\cite{gallagher2008}.
-With \emph{Ratio} (Figure~\ref{fig:unique}), many incorrect matches occur 
-in the fence towards the bottom of the image.
-When we match all feature points together, many of these incorrect 
-matches are eliminated, because points in the fence match with other 
-points in the fence in the same image (Figures~\ref{fig:within} and
-\ref{fig:without}).
-
-\subsubsection{Mirror Match with Clustering (\emph{MMC})}
-%
-In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
-non-geometric feature matching by clustering feature points by 
-similarity. This process yields partitions of fairly similar feature 
-points that we can match using the same approach as \emph{MM}.  
-Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
-
-Before we introduce the implementation details we will go over the 
-problem of graph clustering and how it relates to feature matching.
-
-Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-points in an image and returns their matching score, we can define a 
-matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-as the \emph{adjecency matrix} of the fully connected graph where each 
-vertex corresponds to a keypoint and the edge between two vertices has a 
-weight equal to the distance between the two corresponding keypoints.
-
-This representation reduces the problem of partitioning the keypoints 
-into groups to that of graph clustering or community structure depending 
-on the context. In the literature there are various ways of clustering a 
-graph according to different measures of what constitutes an optimal 
-partitioning. Traditionally the most used clustering algorithms have 
-been K-means and spectral clustering, but in recent years a host of new 
-algorithms have been proposed based on both Newman's concept of graph 
-modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-well as information theoretical measures\footnote{See for example 
-\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-new algorithms differ from K-means clustering and Spectral clustering 
-in that they do not require the number of expected to clusters to be 
-specified beforehand\footnote{Among the aforementioned methods, this is 
-true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-tests done using randomly generated graphs with a known partitioning 
-\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-markedly better than spectral clustering and 
-K-means\cite{lancichinetti2009}.
-
-The performance of clustering algorithms is a complicated issue, since 
-an optimal clustering given the same graph can vary depending on the 
-application. Spectral clustering for example will usually return a 
-partitioning where each partition is roughly equal in size\footnote{As 
-mentioned in \cite{von2007}} while the Louvain 
-clustering\cite{blondel2008} might return partitions of very uneven 
-size, even if the modularity measurement has been shown to penalize very 
-small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-depending on the application, but when clustering feature points, 
-maintaining clusters of an even size usually means that some clusters 
-will be '\emph{catch-all}' clusters where the feature points that do 
-not fit anywhere else are grouped together. The necessity of specifying 
-the amount of partitions in for example Spectral clustering or Pott's 
-model clustering further exacerbates the issue since smaller partitions 
-are then combined into one to achieve the right amount of partitions.
-
-%
-\begin{algorithm}
-\caption{Mirror Match with Clustering (\emph{MMC})}
-\label{alg-mmc}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $M\gets \varnothing$
-\State $F\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather features
-	\State $f_i\gets getFeatures(I_i)$
-	\State $F\gets F \cup f_i$
-\EndFor
-\State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $A_{norm}\gets 1 - normalize(A)$
-\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $P\gets cluster(A_{pruned})$
-\ForAll{$p \in P$} \Comment p is a set of feature points
-	\State $M\gets M \cup getMatches(p, t, F)$
-\EndFor \\
-\Return matches
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\begin{figure}[t]
-    \centering
-\makebox[\textwidth][c]{%
-    \includegraphics[width=1.1\textwidth]{images/MMC_graph}
-    \label{fig:graph}
-}
-    \caption{The partitioned feature graph. Each vertex represents a 
-        feature point; lines indicate high similarity between points. A 
-        partition is a connected group with the same color. The border 
-        color of each node indicates which image it belongs to.  Zooming 
-    into a subsection of the graph (right part), the various cluster 
-sizes can be seen, ranging from hundreds of feature points to only two 
-or three.}
-	\label{fig:graph}
-\end{figure}
-
-We use the Louvain Method \cite{blondel2008} for clustering feature 
-points, since it is relatively fast and performs well 
-\cite{lancichinetti2009}, does not require parameters 
-\cite{blondel2008}, and does not emphasize partitions of equal size, as 
-opposed to spectral clustering or k-means \cite{von2007}, for example.
-While the Louvain clustering algorithm does not require any parameters 
-in itself, it tends towards clustering all feature points together in 
-the same partition if the graph is very connected.  To ensure that the 
-graph is well clustered, the adjacency matrix is pruned so that only 
-edges above a certain threshold are kept. From empirical analysis, 
-retaining the top 2.5\% of edges with the highest similarity seems to 
-work well in practice. Figure~\ref{fig:graph} shows the result of 
-clustering the feature points as a graph.
-%
-
-The partitions group feature points by similarity, which means that 
-repetitive structures such as buildings often appear in larger 
-partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
-%
-
-\begin{algorithm}
-\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
-\label{alg-getmatches}
-    \fontsize{10}{10}\selectfont
-    \begin{algorithmic}
-    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
-    all features
-    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
-        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
-    \If{$\left\vert edges \right\vert > 1$}
-        \State $matches \gets MMGet(p, t)$
-    \ElsIf{$\left\vert edges \right\vert = 1$}
-        \State $matches \gets RatioGet(p, features, t)$
-    \Else
-        \State $matches \gets \varnothing$
-    \EndIf
-
-    \Return matches
-    \end{algorithmic}
-\end{algorithm}
-
-The matching algorithm for \emph{MMC} detailed in 
-Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
-more than two elements using the \emph{MM} approach.  However, as can be 
-seen in the example in Figure~\ref{fig:MMC_graph}, many of the 
-partitions contain only two feature points from different images linked 
-by one edge. In this case, we compare the similarity of the these two 
-feature points with their second best match and remove matches where 
-this ratio lies above a certain threshold, like in the \emph{Ratio} 
-algorithm.  For example in the case of Figure~\ref{fig:pitts_partition}, 
-we have feature points from a building in one image grouped together 
-with points from a shirt pattern in another.  The nearest neighbor 
-method would have returned wrong matches, but since we match the 
-partition with \emph{MM}, points in the building end up matching other 
-points in the building, and no matches are returned.
-
-\subsection{Experiments}
-\label{S:Experiments}
-%
-To reliably measure the accuracy of a matching method on real images, we 
-either need a set of image pairs tied by a homography, or we have to 
-manually count the number of inliers. The latter becomes prohibitive for 
-large numbers of (non-trivial) images.
-
-Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
-set of test images to compare the performance of feature detectors. The 
-set covers different types of image variations, such as lighting change, 
-blur, rotation, and viewpoint change. Inspired by this dataset (in 
-particular the `Graf' image set) and motivated by the need for more 
-image pairs featuring viewpoint changes, we have compiled a set of 8 
-image pairs consisting of subjects taken from two different angles. The 
-images are collected from Flickr's database of images published under a 
-creative commons licence and feature murals, which makes it possible to 
-relate points in the image pairs with a homography since most of the 
-points in the images will be lying on a plane.  The images have been 
-cropped to show the same motive and resized to $900\times 600$ pixels.  
-This dataset will be referred to as the \emph{Murals} dataset.  
-Figure~\ref{fig:murals} shows one image from each pair.
-
-\begin{figure}[htb]
-    \makebox[1.0\textwidth][c]{%
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example1}
-			\label{fig:fairey1}
-	\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example2}
-			\label{fig:fairey2}
-		\end{subfigure}%
-		\enspace %
-        \begin{subfigure}[t]{0.77\textwidth}
-   		\centering
-   		\includegraphics[width=\columnwidth]{images/crop_examples}
-		\end{subfigure}%
-	}%
-	\caption{Sample test patches produced from an image pair.}
-	\label{fig:fairey}
-\end{figure}
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\textwidth]{images/murals}
-	\caption{Images in the \emph{Murals} test set.}
-	\label{fig:murals}
-\end{figure*}
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
-	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
-	\label{fig:Graf}
-\end{figure}
-
-\subsubsection{Experimental setup}
-We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
-\cite{lowe2004sift} as well as \emph{Isodata} \cite{das2008event} and 
-\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isodata} and 
-\emph{Spectral} uses geometric constraints, whereas \emph{Ratio} does 
-not.
-
-\begin{algorithm}
-\caption{Ratio Match (\emph{Ratio})}
-\label{alg-ratio}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
-\State $matches\gets \varnothing$
-\State $features_1 \gets getFeatures(im_1)$
-\State $features_2 \gets getFeatures(im_2)$
-\ForAll{$f_i \in features_1$}
-    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-        \State $matches \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\Return $matches$
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\emph{Ratio} (Algorithm~\ref{alg-ratio}) is the most straightforward of 
-the three reference algorithms. Feature points are matched using K 
-Nearest Neighbor and the similarity ratio between the best and second 
-best match is then compared to a threshold to decide if the match is 
-kept.
-
-%, which uses geometric information to improve the matching.  The 
-%comparison  with \emph{Ratio} serves to illustrate the relative 
-%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isodata} is included to illustrate 
-%the performance of an algorithm relying on geometric constraints faced 
-%with image pairs that might not have any overlap.  
-The comparison was done using the \emph{Murals} dataset 
-(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
-from \cite{mikolajczyk2005performance}, and two 
-images\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher 
-dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
-
-Test sets were generated from the image pairs by cropping square patches of
-$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
-Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
-This ensures that patch pairs with no overlap still retain a general similarity to each 
-other, while patches that do overlap often only share a small 
-part of their area. Figure~\ref{fig:fairey} shows an example of 
-possible pairs of test image patches produced from a source image pair.  
-Producing $n$ such pairs allows us to test not just how well the 
-matching algorithm performs on a variety of overlaps but also how many 
-false positives we get on similar images that do not overlap at all. In 
-practice the amount of overlap between pairs in a test set will depend 
-on the overlap and viewpoint change in the source image pair.  To give a 
-rough idea, Table~\ref{table:overlap} shows the overlap of patch pairs 
-created from images 1 and 3 of the \emph{Graf} image set from 
-\cite{mikolajczyk2005performance}.
-
-\begin{table}[htb]
-\caption{Overlap in the set of 100 patch pairs created from two images 
-of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
-\label{table:overlap}
-    \centering
-%   \small
-\begin{tabular}{r*{3}{r}}
-\hline
-    Amount of overlap: & 0\% & $< 50$\% & $> 50$\%  \\
-    \noalign{\smallskip}
-	%
-    Number of patch pairs: & 21 & 54 & 25 \\
-    \hline
-\end{tabular}
-\end{table}
-
-Given a potential match between two pixels $p_1$ and $p_2$, $m = 
-\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
-$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
-two points satisfy the following criteria:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
-\end{equation*}
-That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here).
-
-\subsection{Results}
-\label{S:Results}
-
-Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
-generated from images 1 and 3 of the \emph{Graf} image set 
-(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
-\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isodata} as a function of 
-the number of matches produced (which is achieved by varying thresholds 
-over a certain range). The results show that \emph{MM} and \emph{MMC} 
-consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
-percentage points above \emph{MM} when both are performing at optimal 
-accuracy.  Although \emph{Isodata} exhibits a good performance on strict 
-thresholds (small number of matches), that quickly diminishes when more 
-matches are desired.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.13\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_graf}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
-		shows the result of 100 patch pairs generated from the source 
-		images shown to the left. The number of matches is the total 
-		number of matches for all 100 patch pairs.}
-	\label{fig:result_graf}
-\end{figure}
-
-To validate whether these results 
-generalize to other images, we tested the four algorithms on the 
-\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
-In total 900 different patch pairs were generated from 9 
-source image pairs.  The results are shown in Figure 
-\ref{fig:result_accumulated}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/result_accumulated}
-	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
-	\label{fig:result_accumulated}
-\end{figure}
-
-To further investigate the impact of viewpoint changes, we tested the 
-algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
-contains 5 images of the same mural taken with gradually increasing 
-viewpoint changes.  The first images are almost identical, while the 
-last are taken from very different angles. The results from   \emph{MMC} 
-and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
-viewpoint changes.
-The performance of \emph{MM} (not shown in the plot) is similar to 
-\emph{MMC}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
-	\caption{Results for viewpoint changes using the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
-	\label{fig:result_viewpoint}
-\end{figure}
-
-Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
-shows the results on 100 patch pairs generated 
-from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
-change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.15\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pitts}
-%		\end{subfigure}%
-		~%add desired spacing between images, e. g. ~, \quad, \qquad
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
-	\label{fig:result_pitts}
-\end{figure}
-
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isodata} can be 
-implemented in $O(n\log n)$, where $n$ is the total number of feature 
-points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. However, it is 
-possible to approximate this in $O(n\log n)$ using search trees.
-
-As for speed, Table~\ref{table:running_times} shows the running time of 
-the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
-These numbers should be taken with a grain of salt, given that much of 
-the code behind \emph{MMC} and \emph{Isodata} is implemented in Python, 
-whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
-computationally intensive operations in C++, which makes them much 
-faster.
-
-\begin{table}[htb]
-\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
-3.30~GHz with 8~GB memory.}
-\label{table:running_times}
-	\centering
-%	\small
-\begin{tabular}{r*{4}{c}}
-\hline
-	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
-	\\
-	\noalign{\smallskip} 
-	%
-	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
-	\hline
-\end{tabular}
-\end{table}
-%
-
-\section{Applications}
-
-In many areas of computer vision matching local feature points is a key 
-component, and matching algorithms have applications in problems such as
-scene matching, object recognition, near duplicate detection and 
-panorama recognition. To show the practical applications of the proposed 
-matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
-improve existing methods in near duplicate detection and panorama 
-recognition. These two problems were chosen because they both involve 
-matching images that might or might not overlap. These cases requires 
-matching algorithms that limit false positives since e.g. returning the 
-top $n$ matches for any given image pair would make it hard to 
-distinguish adjacent or duplicate images from non-adjacent or dissimilar
-image pairs. Near duplicate detection also constraints normal matching 
-algorithms from relying on geometric assumptions, since we have very few
-guarantees between two potential near duplicates that they should be 
-matched using any particular geometric heuristic. In this section, we 
-will first see \emph{MMC} applied to panorama recognition and alignment,
-and next \emph{MM} and \emph{MMC} applied to near duplicate detection.
-
-\subsection{Panorama Recognition and Alignment}
-One of the oldest practical problems approached in computer vision is 
-the automatic stitching of several source images into a bigger image, 
-such as panoramas and composite satellite photos\footnote{A brief 
-overview of the history of image stitching can be found in Szeliski's 
-book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
-As part of the process of stitching together images, the individual 
-images must be aligned and often transformed in perspective. Earlier 
-methods relied on minimizing pixel dissimilarities in overlapping images 
-while more recent methods have used local feature points to estimate the 
-correct image alignment. Using local feature points carry the additional 
-advantage that it is feasible to automatically recognize where each 
-source image belong in the final panorama.
-
-\begin{figure}[h]
-	\begin{subfigure}[t]{0.9\textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{images/pano_wide}
-        \label{fig:pano_images}
-		\caption{Source images}
-    \end{subfigure}%
-	\\
-	\centering
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-autostitch}
-        \label{fig:pano_autostitch}
-		\caption{Panorama by Autostitch}
-    \end{subfigure}%
-	~%add desired spacing between images, e. g. ~, \quad, \qquad
-	%(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-MMC}
-		\caption{Panorama by MMC}
-		\label{fig:pano_MMC}
-	\end{subfigure}%
-    \label{fig:pano_example}
-	\caption{An example of a difficult case for panorama recognition and 
-		alignment.  In a) the source images used to generate the 
-		panorama are displayed.\ b) shows the result of the Autostitch 
-		program from \cite{brown2007automatic} which fails to combine 
-		all images, while c) demonstrates the result of the simple 
-		panorama stitcher
-	using the proposed MMC algorithm. Here the two left images are 
-correctly linked}
-\end{figure}
-
-In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
-image can be assembled by collecting the feature points of all source 
-images and matching them to obtain a set of inter image matches.  By 
-using \emph{RANSAC}\footnote{RANdom SAmple Consensus, an iterative 
-    algorithm to estimate parameters from noisy data introduced in 
-Fischler and Bolles in 1981 \cite{fischler1981ransac}} to find matches 
-deemed as inliers between image pairs, they are able to recognize image 
-neighbors and align them to construct the final panorama.
-
-This process hinges on the effectiveness of the matching algorithm used 
-to match the feature points. Not only is it important that true pairs 
-are accurately matched, but since we are matching points in image pairs 
-that might not be adjacent in the final panorama, we also need to make 
-sure that we consistently reject false positives, i.e.\ proposed matches 
-that link feature points which don't correspond.
-
-To demonstrate the usefulness of \emph{MMC} applied to panorama 
-recognition and alignment we construct a simple panorama stitcher taking
-as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
-and returns as output a panoramic image stitched together from the 
-source images. Based on the matches found by applying \emph{MMC} to $I$, 
-the images are combined in an order corresponding to how many matches 
-connect them, as done by Brown and Lowe \cite{brown2007automatic}.
-
-Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
-provides a way to globally optimize the accuracy of the image alignment} 
-and a lot of image enhancements such as exposure adjustment and edge 
-blurring to provide a seamless panorama. While these additions improve 
-the end product, they don't influence the performance of panorama 
-alignment and recognition and haven't been included in the simple 
-comparison algorithm.
-
-Figure~\ref{fig:pano_example} shows an example where the added accuracy 
-of MMC enables us to correctly recognitize and align source images that 
-fail to be combined by Autostitch, a program using the algorithm 
-proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
-case the matching algorithm used in Autostitch fails to find sufficient 
-matches between two images pairs to correctly position them and 
-consequently doesn't produce a panorama containing all images as a 
-result.
-
-This example illustrates how an improved matching algorithm can be 
-applied to panorama recognition and alignment to allow for panoramas 
-created with images that have little overlap.
-% Maybe find example of images with identical features that would be 
-% hard to match?
-
-\subsection{Near Duplicate Detection}
-If we look at two images, we can often easily tell if one image 
-resembles the other enough to be redundant in a photo album. In computer 
-vision this task becomes a lot less trivial because our idea of a 
-duplicate image might only require there being some object or scene in 
-common between the image pair. In addition the object or scene might 
-have been taken from a different angle and under different camera 
-settings. Facing these challenges, a lot of work has been done trying to 
-reliably recognize duplicaes both with regards to corporate intellectual 
-property as well as consumer photo albums because both applications 
-provide useful tools.  A company might be interested in finding images 
-that are derived from their intellectual property, while consumers 
-taking vacation photos might be interested in grouping duplicate images 
-to allow for easier photo organization.
-
-Local features are often used to group similar images, either by looking
-at a histogram of descriptors \cite{wu2009bundling} or by looking at how
-well feature points match between images \cite{zhao2009scale},
-\cite{chu2010consumer}, \cite{vas2013cluster}. In the latter case 
-finding near duplicates means that we will be matching image pairs that 
-might or might not contain any actual matches. In this case we would 
-benefit from a reliable matching algorithm that minimizes false 
-positives, which is a characteristic of both \emph{MM} and \emph{MMC}.
-
-The \emph{PhotoCluster} method introduced by Vonikakis et al.  
-\cite{vas2013cluster} shows the best clustering performance on the 
-California-nd dataset \cite{jinda2012california} which contains a set of
-annotated vacation images similar to a typical photo album in a consumer
-product. \emph{PhotoCluster} works by grouping images in several steps 
-using first image metadata and global features to obtain a set of 
-proposed clusters. Then local features are used to find the best 
-matching images in these proposed clusters yielding the final groups of 
-near duplicate images. To show the viability of \emph{MMC} in the 
-application of near duplicated detection, we modify the PhotoCluster 
-method to use \emph{MMC} for matching images instead of \emph{Ratio} 
-which was previously used. Due to the time consumption of \emph{MMC}, 
-all images where resized to to 10\% before being compared. Outside of 
-that, the experiments were performed exactly as documented in 
-\cite{vas2013cluster}.
-
-\begin{table}[htb]
-\caption{Results from Near Duplicate Detection at 10\% scale}
-\label{table:ndd}
-	\centering
-%	\small
-\begin{tabular}{r*{2}{r}}
-\hline
-    Method: & Ratio & MMC   \\
-	\noalign{\smallskip}
-	%
-    F1 score: & 0.4654 & 0.5459 \\
-	\hline
-\end{tabular}
-\end{table}
-
-The results of the comparison can be seen in Table~\ref{table:nnd}. It 
-shows that \emph{MMC} improves performance by 8.05\% over the original 
-framework using \emph{Ratio} to match images. For comparison, the 
-performance improvement of \emph{PhotoCluster} compared to XMatch 
-\cite{zhao2009scale}, the second best performing algorithm on the 
-California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.
-
-\section{Summary}
+\chapter{Summary}
 \label{S:Summary}
@@
 %
-
-\bibliographystyle{IEEEtran}
-\bibliography{bibliography}
-\end{document}

### 2013-08-09 text/thesis.tex
Reorganized thesis

--- 2013-08-07 text/thesis.tex
@@
-%\documentclass[report]{IEEEtran}
-\documentclass{article}
-\usepackage{footnote}
-%\usepackage[font={small}]{caption}
-\usepackage{sidecap}
-\usepackage{graphicx}
-\usepackage{cite}
-\usepackage{hyperref}
-%\usepackage[stable]{footmisc}
-\usepackage{caption}
-\usepackage{adjustbox}
-\usepackage{subcaption}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{amsmath}
-\usepackage{amssymb}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%		My Thesis
+%
+%		EDOC Template
+%		2011
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+\input{head/settings_epfl_template.tex}
+\input{head/settings_custom.tex}  % place your custom packages, etc... in this file!
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%% HEAD: Book-Begin
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
+\frontmatter
+\input{head/titlepage.tex}
+%\include{head/dedication}
+%\input{head/acknowledgements}
+%\include{head/preface}
+%\include{head/abstracts}
 
-\title{Reliable feature point matching}
-\author{Jonas Arnfred}
+\tableofcontents
+\addcontentsline{toc}{chapter}{List of figures} % adds an entry to the table of contents
+\listoffigures
+\addcontentsline{toc}{chapter}{List of tables} % adds an entry to the table of contents
+\listoftables
+% your list of symbols here, if needed.
 
-\maketitle
+% space before each new paragraph according to the template guidelines.
+%(needs to be after titlepage and frontmatter to keep the table of contents lists short)
+\setlength{\parskip}{1em}
 
-\section{Introduction}
-What is the subject of this thesis and in what part lies my 
-contribution?
-How is the report organized?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%% MAIN: The chapters of the thesis
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\mainmatter
+\include{main/ch1_introduction}
+\include{main/ch2_background}
+\include{main/ch3_matching_methods}
+\include{main/ch4_competition}
+\include{main/ch4_experiments}
+\include{main/ch4_applications}
+\include{main/ch4_summary}
 
-\section{Background}
-Introduction to Computer Vision
- - Introduce common tasks that we are good at that computers aren't
- - Single in on tasks that we can solve using feature points
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%% TAIL: Bibliography, Appendix, CV
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\include{tail/appendix}
+\include{tail/biblio}
+% Add your glossary here
+% Add your index here
+% Photographic credits (list of pictures&images that have been used with names of the person holding the copyright for them)
+% \include{tail/cv}
 
-Introduction to feature points
- - Global explanation of what they are and how they serve to solve the 
-problems mentioned before
- - How do we find them? (Examples making it intuitive why corners are 
-nice)
- - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
- Scale, \ldots, Affine)
- - Introduce SIFT and explain how the different problems are tackled in 
-SIFT)
- - Talk about other methods and how they are different
-
-Matching feature points
- - What applications require matching?
- - How is matching usually done
- - Segue into related work from paper
-
-\section{Matching feature points}
-Basically c/p from paper, but better figures and maybe more explanations
- - Add path about graphs and how they are formed. Make sure to explain 
- the clustering in more detail and make it easier to understand
- - Add a good explanation for new figures and how the precision and 
- recall are calculated. This should appear somewhere before results.
- - Add part on spectral matching and modify accordingly. Make sure to 
- underline how the second plot shows how the geometric method is 
- independent of MMC and that they combined yield greater results.
-
-\subsection{Proposed Matching Methods}
-\label{S:MatchingMethods}
-
-\subsubsection{Mirror Match (\emph{MM})}
-
-\begin{figure}
-	\centering%
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
-			\caption{Source image pair}
-			\label{fig:pitts_source}
-		\end{subfigure}%
-		\\ %
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
-			\caption{Feature points}
-			\label{fig:pitts_keypoints}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
-			\caption{\emph{Ratio}}
-			\label{fig:unique}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
-			\caption{\emph{MM} intermediate result}
-			\label{fig:within}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
-			\caption{\emph{MM} final result}
-			\label{fig:without}
-		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
-			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
-			\caption{\emph{MMC} Partition Example}
-			\label{fig:pitts_partition}
-		\end{subfigure}%
-	\caption{Feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-	(c) Result of \emph{Ratio} matching. 
-  (d) All matches found by \emph{MM}, including intra-image matches. 
-	(e) Final \emph{MM} result. 
-	(f) Example of a partition of feature points after clustering, which 
-includes similar feature points from building windows and shirt patterns.}%
-	\label{fig:comparemirror}%
-\end{figure}%
-
-%
-The central idea behind \emph{MM} is to match features of $n$ images by 
-taking every feature from all $n$ images and matching it against every 
-other feature from the same set. We can then discard the correspondences 
-that match two points within the same image. Algorithm~\ref{alg-mm} details  
-the implementation of \emph{MM}.
-%
-\begin{algorithm}
-\caption{Mirror Match (\emph{MM})}
-\label{alg-mm}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
-\State $features\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Acquisition Stage
-	\State $features\gets features \cup getFeatures(I_i)$
-\EndFor
-\ForAll{$f_i \in features$} \Comment Matching Stage
-	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
-	\left\{f_i\right\})$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-		\State $matches_{init} \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
-Stage
-\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
-getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
-		\State $matches_{final} \gets (f_i, f_j)$
-	\EndIf
-\EndFor \\
-\Return $matches_{final}$
-\end{algorithmic}
-%}
-\end{algorithm}
-%
-In the acquisition stage we gather all features in the set of images.  
-In the matching stage these features are matched using $k$-nearest 
-neighbors.  For any given feature $f_i$ the two most similar neighbors 
-are returned, and we calculate the ratio between them as proposed in 
-\cite{lowe2004sift}.  Any correspondence with a ratio above the 
-threshold supplied will be discarded. Finally in the filter stage we 
-check that matches are from different images and discard all matches 
-that are not symmetric.
-%
-%\begin{figure*}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image pair}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-%			\caption{Feature points}
-%			\label{fig:pitts_keypoints}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_off}
-%			\caption{\emph{Ratio}}
-%			\label{fig:unique}
-%		\end{subfigure}%
-%	}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
-%			\caption{\emph{MM} intermediate result}
-%			\label{fig:within}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match}
-%			\caption{\emph{MM} final result}
-%			\label{fig:without}
-%		\end{subfigure}%
-%		\enspace%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{\emph{MMC} Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-%(c) Result of \emph{Ratio} matching the two images.% 
-%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
-%	(e) Final \emph{MM} result with the intra-image matches removed. 
-%	(f) Example of a partition of feature points after clustering. This partition 
-%includes similar feature points around the windows of a building and the patterns of a shirt.}%
-%	\label{fig:comparemirror}%
-%\end{figure*}%
-
-Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} 
-using an example image pair from the Gallagher dataset 
-\cite{gallagher2008}.
-With \emph{Ratio} (Figure~\ref{fig:unique}), many incorrect matches occur 
-in the fence towards the bottom of the image.
-When we match all feature points together, many of these incorrect 
-matches are eliminated, because points in the fence match with other 
-points in the fence in the same image (Figures~\ref{fig:within} and
-\ref{fig:without}).
-
-\subsubsection{Mirror Match with Clustering (\emph{MMC})}
-%
-In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
-non-geometric feature matching by clustering feature points by 
-similarity. This process yields partitions of fairly similar feature 
-points that we can match using the same approach as \emph{MM}.  
-Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
-
-Before we introduce the implementation details we will go over the 
-problem of graph clustering and how it relates to feature matching.
-
-Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-points in an image and returns their matching score, we can define a 
-matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-as the \emph{adjecency matrix} of the fully connected graph where each 
-vertex corresponds to a keypoint and the edge between two vertices has a 
-weight equal to the distance between the two corresponding keypoints.
-
-This representation reduces the problem of partitioning the keypoints 
-into groups to that of graph clustering or community structure depending 
-on the context. In the literature there are various ways of clustering a 
-graph according to different measures of what constitutes an optimal 
-partitioning. Traditionally the most used clustering algorithms have 
-been K-means and spectral clustering, but in recent years a host of new 
-algorithms have been proposed based on both Newman's concept of graph 
-modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-well as information theoretical measures\footnote{See for example 
-\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-new algorithms differ from K-means clustering and Spectral clustering 
-in that they do not require the number of expected to clusters to be 
-specified beforehand\footnote{Among the aforementioned methods, this is 
-true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-tests done using randomly generated graphs with a known partitioning 
-\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-markedly better than spectral clustering and 
-K-means\cite{lancichinetti2009}.
-
-The performance of clustering algorithms is a complicated issue, since 
-an optimal clustering given the same graph can vary depending on the 
-application. Spectral clustering for example will usually return a 
-partitioning where each partition is roughly equal in size\footnote{As 
-mentioned in \cite{von2007}} while the Louvain 
-clustering\cite{blondel2008} might return partitions of very uneven 
-size, even if the modularity measurement has been shown to penalize very 
-small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-depending on the application, but when clustering feature points, 
-maintaining clusters of an even size usually means that some clusters 
-will be '\emph{catch-all}' clusters where the feature points that do 
-not fit anywhere else are grouped together. The necessity of specifying 
-the amount of partitions in for example Spectral clustering or Pott's 
-model clustering further exacerbates the issue since smaller partitions 
-are then combined into one to achieve the right amount of partitions.
-
-%
-\begin{algorithm}
-\caption{Mirror Match with Clustering (\emph{MMC})}
-\label{alg-mmc}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $M\gets \varnothing$
-\State $F\gets \varnothing$
-\ForAll{$I_i \in images$} \Comment Gather features
-	\State $f_i\gets getFeatures(I_i)$
-	\State $F\gets F \cup f_i$
-\EndFor
-\State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $A_{norm}\gets 1 - normalize(A)$
-\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $P\gets cluster(A_{pruned})$
-\ForAll{$p \in P$} \Comment p is a set of feature points
-	\State $M\gets M \cup getMatches(p, t, F)$
-\EndFor \\
-\Return matches
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\begin{figure}[t]
-    \centering
-\makebox[\textwidth][c]{%
-    \includegraphics[width=1.1\textwidth]{images/MMC_graph}
-    \label{fig:graph}
-}
-    \caption{The partitioned feature graph. Each vertex represents a 
-        feature point; lines indicate high similarity between points. A 
-        partition is a connected group with the same color. The border 
-        color of each node indicates which image it belongs to.  Zooming 
-    into a subsection of the graph (right part), the various cluster 
-sizes can be seen, ranging from hundreds of feature points to only two 
-or three.}
-	\label{fig:graph}
-\end{figure}
-
-We use the Louvain Method \cite{blondel2008} for clustering feature 
-points, since it is relatively fast and performs well 
-\cite{lancichinetti2009}, does not require parameters 
-\cite{blondel2008}, and does not emphasize partitions of equal size, as 
-opposed to spectral clustering or k-means \cite{von2007}, for example.
-While the Louvain clustering algorithm does not require any parameters 
-in itself, it tends towards clustering all feature points together in 
-the same partition if the graph is very connected.  To ensure that the 
-graph is well clustered, the adjacency matrix is pruned so that only 
-edges above a certain threshold are kept. From empirical analysis, 
-retaining the top 2.5\% of edges with the highest similarity seems to 
-work well in practice. Figure~\ref{fig:graph} shows the result of 
-clustering the feature points as a graph.
-%
-
-The partitions group feature points by similarity, which means that 
-repetitive structures such as buildings often appear in larger 
-partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
-%
-
-\begin{algorithm}
-\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
-\label{alg-getmatches}
-    \fontsize{10}{10}\selectfont
-    \begin{algorithmic}
-    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
-    all features
-    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
-        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
-    \If{$\left\vert edges \right\vert > 1$}
-        \State $matches \gets MMGet(p, t)$
-    \ElsIf{$\left\vert edges \right\vert = 1$}
-        \State $matches \gets RatioGet(p, features, t)$
-    \Else
-        \State $matches \gets \varnothing$
-    \EndIf
-
-    \Return matches
-    \end{algorithmic}
-\end{algorithm}
-
-The matching algorithm for \emph{MMC} detailed in 
-Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
-more than two elements using the \emph{MM} approach.  However, as can be 
-seen in the example in Figure~\ref{fig:MMC_graph}, many of the 
-partitions contain only two feature points from different images linked 
-by one edge. In this case, we compare the similarity of the these two 
-feature points with their second best match and remove matches where 
-this ratio lies above a certain threshold, like in the \emph{Ratio} 
-algorithm.  For example in the case of Figure~\ref{fig:pitts_partition}, 
-we have feature points from a building in one image grouped together 
-with points from a shirt pattern in another.  The nearest neighbor 
-method would have returned wrong matches, but since we match the 
-partition with \emph{MM}, points in the building end up matching other 
-points in the building, and no matches are returned.
-
-\subsection{Experiments}
-\label{S:Experiments}
-%
-To reliably measure the accuracy of a matching method on real images, we 
-either need a set of image pairs tied by a homography, or we have to 
-manually count the number of inliers. The latter becomes prohibitive for 
-large numbers of (non-trivial) images.
-
-Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
-set of test images to compare the performance of feature detectors. The 
-set covers different types of image variations, such as lighting change, 
-blur, rotation, and viewpoint change. Inspired by this dataset (in 
-particular the `Graf' image set) and motivated by the need for more 
-image pairs featuring viewpoint changes, we have compiled a set of 8 
-image pairs consisting of subjects taken from two different angles. The 
-images are collected from Flickr's database of images published under a 
-creative commons licence and feature murals, which makes it possible to 
-relate points in the image pairs with a homography since most of the 
-points in the images will be lying on a plane.  The images have been 
-cropped to show the same motive and resized to $900\times 600$ pixels.  
-This dataset will be referred to as the \emph{Murals} dataset.  
-Figure~\ref{fig:murals} shows one image from each pair.
-
-\begin{figure}[htb]
-    \makebox[1.0\textwidth][c]{%
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example1}
-			\label{fig:fairey1}
-	\end{subfigure}%
-		\enspace %add desired spacing between images, e. g. ~, \quad, 
-		%(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[t]{0.102\textwidth}
-			\centering
-			\includegraphics[width=\textwidth]{images/pair_example2}
-			\label{fig:fairey2}
-		\end{subfigure}%
-		\enspace %
-        \begin{subfigure}[t]{0.77\textwidth}
-   		\centering
-   		\includegraphics[width=\columnwidth]{images/crop_examples}
-		\end{subfigure}%
-	}%
-	\caption{Sample test patches produced from an image pair.}
-	\label{fig:fairey}
-\end{figure}
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\textwidth]{images/murals}
-	\caption{Images in the \emph{Murals} test set.}
-	\label{fig:murals}
-\end{figure*}
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
-	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
-	\label{fig:Graf}
-\end{figure}
-
-\subsubsection{Experimental setup}
-We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
-\cite{lowe2004sift} as well as \emph{Isodata} \cite{das2008event} and 
-\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isodata} and 
-\emph{Spectral} uses geometric constraints, whereas \emph{Ratio} does 
-not.
-
-\begin{algorithm}
-\caption{Ratio Match (\emph{Ratio})}
-\label{alg-ratio}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
-\State $matches\gets \varnothing$
-\State $features_1 \gets getFeatures(im_1)$
-\State $features_2 \gets getFeatures(im_2)$
-\ForAll{$f_i \in features_1$}
-    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
-	\If{$ratio < t$}
-        \State $matches \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\Return $matches$
-\end{algorithmic}
-%}
-\end{algorithm}
-
-\emph{Ratio} (Algorithm~\ref{alg-ratio}) is the most straightforward of 
-the three reference algorithms. Feature points are matched using K 
-Nearest Neighbor and the similarity ratio between the best and second 
-best match is then compared to a threshold to decide if the match is 
-kept.
-
-%, which uses geometric information to improve the matching.  The 
-%comparison  with \emph{Ratio} serves to illustrate the relative 
-%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isodata} is included to illustrate 
-%the performance of an algorithm relying on geometric constraints faced 
-%with image pairs that might not have any overlap.  
-The comparison was done using the \emph{Murals} dataset 
-(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
-from \cite{mikolajczyk2005performance}, and two 
-images\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher 
-dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
-
-Test sets were generated from the image pairs by cropping square patches of
-$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
-Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
-This ensures that patch pairs with no overlap still retain a general similarity to each 
-other, while patches that do overlap often only share a small 
-part of their area. Figure~\ref{fig:fairey} shows an example of 
-possible pairs of test image patches produced from a source image pair.  
-Producing $n$ such pairs allows us to test not just how well the 
-matching algorithm performs on a variety of overlaps but also how many 
-false positives we get on similar images that do not overlap at all. In 
-practice the amount of overlap between pairs in a test set will depend 
-on the overlap and viewpoint change in the source image pair.  To give a 
-rough idea, Table~\ref{table:overlap} shows the overlap of patch pairs 
-created from images 1 and 3 of the \emph{Graf} image set from 
-\cite{mikolajczyk2005performance}.
-
-\begin{table}[htb]
-\caption{Overlap in the set of 100 patch pairs created from two images 
-of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
-\label{table:overlap}
-    \centering
-%   \small
-\begin{tabular}{r*{3}{r}}
-\hline
-    Amount of overlap: & 0\% & $< 50$\% & $> 50$\%  \\
-    \noalign{\smallskip}
-	%
-    Number of patch pairs: & 21 & 54 & 25 \\
-    \hline
-\end{tabular}
-\end{table}
-
-Given a potential match between two pixels $p_1$ and $p_2$, $m = 
-\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
-$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
-two points satisfy the following criteria:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
-\end{equation*}
-That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here).
-
-\subsection{Results}
-\label{S:Results}
-
-Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
-generated from images 1 and 3 of the \emph{Graf} image set 
-(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
-\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isodata} as a function of 
-the number of matches produced (which is achieved by varying thresholds 
-over a certain range). The results show that \emph{MM} and \emph{MMC} 
-consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
-percentage points above \emph{MM} when both are performing at optimal 
-accuracy.  Although \emph{Isodata} exhibits a good performance on strict 
-thresholds (small number of matches), that quickly diminishes when more 
-matches are desired.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.13\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_graf}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
-		shows the result of 100 patch pairs generated from the source 
-		images shown to the left. The number of matches is the total 
-		number of matches for all 100 patch pairs.}
-	\label{fig:result_graf}
-\end{figure}
-
-To validate whether these results 
-generalize to other images, we tested the four algorithms on the 
-\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
-In total 900 different patch pairs were generated from 9 
-source image pairs.  The results are shown in Figure 
-\ref{fig:result_accumulated}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=\columnwidth]{images/result_accumulated}
-	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
-	\label{fig:result_accumulated}
-\end{figure}
-
-To further investigate the impact of viewpoint changes, we tested the 
-algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
-contains 5 images of the same mural taken with gradually increasing 
-viewpoint changes.  The first images are almost identical, while the 
-last are taken from very different angles. The results from   \emph{MMC} 
-and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
-viewpoint changes.
-The performance of \emph{MM} (not shown in the plot) is similar to 
-\emph{MMC}.
-
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
-	\caption{Results for viewpoint changes using the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
-	\label{fig:result_viewpoint}
-\end{figure}
-
-Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
-shows the results on 100 patch pairs generated 
-from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
-change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.15\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pitts}
-%		\end{subfigure}%
-		~%add desired spacing between images, e. g. ~, \quad, \qquad
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
-			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
-	\label{fig:result_pitts}
-\end{figure}
-
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isodata} can be 
-implemented in $O(n\log n)$, where $n$ is the total number of feature 
-points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. However, it is 
-possible to approximate this in $O(n\log n)$ using search trees.
-
-As for speed, Table~\ref{table:running_times} shows the running time of 
-the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
-These numbers should be taken with a grain of salt, given that much of 
-the code behind \emph{MMC} and \emph{Isodata} is implemented in Python, 
-whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
-computationally intensive operations in C++, which makes them much 
-faster.
-
-\begin{table}[htb]
-\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
-3.30~GHz with 8~GB memory.}
-\label{table:running_times}
-	\centering
-%	\small
-\begin{tabular}{r*{4}{c}}
-\hline
-	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
-	\\
-	\noalign{\smallskip} 
-	%
-	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
-	\hline
-\end{tabular}
-\end{table}
-%
-
-\section{Applications}
-
-In many areas of computer vision matching local feature points is a key 
-component, and matching algorithms have applications in problems such as
-scene matching, object recognition, near duplicate detection and 
-panorama recognition. To show the practical applications of the proposed 
-matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
-improve existing methods in near duplicate detection and panorama 
-recognition. These two problems were chosen because they both involve 
-matching images that might or might not overlap. These cases requires 
-matching algorithms that limit false positives since e.g. returning the 
-top $n$ matches for any given image pair would make it hard to 
-distinguish adjacent or duplicate images from non-adjacent or dissimilar
-image pairs. Near duplicate detection also constraints normal matching 
-algorithms from relying on geometric assumptions, since we have very few
-guarantees between two potential near duplicates that they should be 
-matched using any particular geometric heuristic. In this section, we 
-will first see \emph{MMC} applied to panorama recognition and alignment,
-and next \emph{MM} and \emph{MMC} applied to near duplicate detection.
-
-\subsection{Panorama Recognition and Alignment}
-One of the oldest practical problems approached in computer vision is 
-the automatic stitching of several source images into a bigger image, 
-such as panoramas and composite satellite photos\footnote{A brief 
-overview of the history of image stitching can be found in Szeliski's 
-book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
-As part of the process of stitching together images, the individual 
-images must be aligned and often transformed in perspective. Earlier 
-methods relied on minimizing pixel dissimilarities in overlapping images 
-while more recent methods have used local feature points to estimate the 
-correct image alignment. Using local feature points carry the additional 
-advantage that it is feasible to automatically recognize where each 
-source image belong in the final panorama.
-
-\begin{figure}[h]
-	\begin{subfigure}[t]{0.9\textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{images/pano_wide}
-        \label{fig:pano_images}
-		\caption{Source images}
-    \end{subfigure}%
-	\\
-	\centering
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-autostitch}
-        \label{fig:pano_autostitch}
-		\caption{Panorama by Autostitch}
-    \end{subfigure}%
-	~%add desired spacing between images, e. g. ~, \quad, \qquad
-	%(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.4\textwidth}
-		\includegraphics[width=\textwidth]{images/panorama-MMC}
-		\caption{Panorama by MMC}
-		\label{fig:pano_MMC}
-	\end{subfigure}%
-    \label{fig:pano_example}
-	\caption{An example of a difficult case for panorama recognition and 
-		alignment.  In a) the source images used to generate the 
-		panorama are displayed.\ b) shows the result of the Autostitch 
-		program from \cite{brown2007automatic} which fails to combine 
-		all images, while c) demonstrates the result of the simple 
-		panorama stitcher
-	using the proposed MMC algorithm. Here the two left images are 
-correctly linked}
-\end{figure}
-
-In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
-image can be assembled by collecting the feature points of all source 
-images and matching them to obtain a set of inter image matches.  By 
-using \emph{RANSAC}\footnote{RANdom SAmple Consensus, an iterative 
-    algorithm to estimate parameters from noisy data introduced in 
-Fischler and Bolles in 1981 \cite{fischler1981ransac}} to find matches 
-deemed as inliers between image pairs, they are able to recognize image 
-neighbors and align them to construct the final panorama.
-
-This process hinges on the effectiveness of the matching algorithm used 
-to match the feature points. Not only is it important that true pairs 
-are accurately matched, but since we are matching points in image pairs 
-that might not be adjacent in the final panorama, we also need to make 
-sure that we consistently reject false positives, i.e.\ proposed matches 
-that link feature points which don't correspond.
-
-To demonstrate the usefulness of \emph{MMC} applied to panorama 
-recognition and alignment we construct a simple panorama stitcher taking
-as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
-and returns as output a panoramic image stitched together from the 
-source images. Based on the matches found by applying \emph{MMC} to $I$, 
-the images are combined in an order corresponding to how many matches 
-connect them, as done by Brown and Lowe \cite{brown2007automatic}.
-
-Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
-provides a way to globally optimize the accuracy of the image alignment} 
-and a lot of image enhancements such as exposure adjustment and edge 
-blurring to provide a seamless panorama. While these additions improve 
-the end product, they don't influence the performance of panorama 
-alignment and recognition and haven't been included in the simple 
-comparison algorithm.
-
-Figure~\ref{fig:pano_example} shows an example where the added accuracy 
-of MMC enables us to correctly recognitize and align source images that 
-fail to be combined by Autostitch, a program using the algorithm 
-proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
-case the matching algorithm used in Autostitch fails to find sufficient 
-matches between two images pairs to correctly position them and 
-consequently doesn't produce a panorama containing all images as a 
-result.
-
-This example illustrates how an improved matching algorithm can be 
-applied to panorama recognition and alignment to allow for panoramas 
-created with images that have little overlap.
-% Maybe find example of images with identical features that would be 
-% hard to match?
-
-\subsection{Near Duplicate Detection}
-If we look at two images, we can often easily tell if one image 
-resembles the other enough to be redundant in a photo album. In computer 
-vision this task becomes a lot less trivial because our idea of a 
-duplicate image might only require there being some object or scene in 
-common between the image pair. In addition the object or scene might 
-have been taken from a different angle and under different camera 
-settings. Facing these challenges, a lot of work has been done trying to 
-reliably recognize duplicaes both with regards to corporate intellectual 
-property as well as consumer photo albums because both applications 
-provide useful tools.  A company might be interested in finding images 
-that are derived from their intellectual property, while consumers 
-taking vacation photos might be interested in grouping duplicate images 
-to allow for easier photo organization.
-
-Local features are often used to group similar images, either by looking
-at a histogram of descriptors \cite{wu2009bundling} or by looking at how
-well feature points match between images \cite{zhao2009scale},
-\cite{chu2010consumer}, \cite{vas2013cluster}. In the latter case 
-finding near duplicates means that we will be matching image pairs that 
-might or might not contain any actual matches. In this case we would 
-benefit from a reliable matching algorithm that minimizes false 
-positives, which is a characteristic of both \emph{MM} and \emph{MMC}.
-
-The \emph{PhotoCluster} method introduced by Vonikakis et al.  
-\cite{vas2013cluster} shows the best clustering performance on the 
-California-nd dataset \cite{jinda2012california} which contains a set of
-annotated vacation images similar to a typical photo album in a consumer
-product. \emph{PhotoCluster} works by grouping images in several steps 
-using first image metadata and global features to obtain a set of 
-proposed clusters. Then local features are used to find the best 
-matching images in these proposed clusters yielding the final groups of 
-near duplicate images. To show the viability of \emph{MMC} in the 
-application of near duplicated detection, we modify the PhotoCluster 
-method to use \emph{MMC} for matching images instead of \emph{Ratio} 
-which was previously used. Due to the time consumption of \emph{MMC}, 
-all images where resized to to 10\% before being compared. Outside of 
-that, the experiments were performed exactly as documented in 
-\cite{vas2013cluster}.
-
-\begin{table}[htb]
-\caption{Results from Near Duplicate Detection at 10\% scale}
-\label{table:ndd}
-	\centering
-%	\small
-\begin{tabular}{r*{2}{r}}
-\hline
-    Method: & Ratio & MMC   \\
-	\noalign{\smallskip}
-	%
-    F1 score: & 0.4654 & 0.5459 \\
-	\hline
-\end{tabular}
-\end{table}
-
-The results of the comparison can be seen in Table~\ref{table:nnd}. It 
-shows that \emph{MMC} improves performance by 8.05\% over the original 
-framework using \emph{Ratio} to match images. For comparison, the 
-performance improvement of \emph{PhotoCluster} compared to XMatch 
-\cite{zhao2009scale}, the second best performing algorithm on the 
-California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.
-
-\section{Summary}
-\label{S:Summary}
-
-This thesis has addressed the problem of matching feature points without 
-using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
-\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
-common idea that feature points should have better matches in another 
-image than in the image they came from to be considered good matches.  
-\emph{MMC} further improves on this idea by using the structure of the 
-similarity graph of the feature points.
-
-The algorithms show promising results when tested on the \emph{Murals} 
-data set. The results on 900 image pairs show that \emph{MM} and 
-\emph{MMC} generally outperform existing matching algorithms 
-\emph{Ratio}, \emph{Isodata} and \emph{Spectral}. In addition \emph{MMC} 
-outperforms \emph{MM}.  We show that this result generalizes to 
-variations in viewpoint change by comparing \emph{MMC} to \emph{Ratio} 
-over a set of image pairs with an increasing magnitude of perspective 
-difference. We go on to apply the algorithms to a real life image case 
-featuring occlusion and a slight viewpoint change and show that the 
-performance of \emph{MM} and \emph{MMC} is consistent with the results 
-on \emph{Murals}. To show that \emph{MM} or \emph{MMC}
-can further improve the results of a geometrical method, we create 
-\emph{Spectral-MMC} by combining \emph{Spectral} and \emph{MMC} and 
-compare the three on the full \emph{Murals} dataset where it yields 
-results better than both \emph{Spectral} and \emph{MMC}.
-
-The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
-applying the algorithms to the problems of near duplicate detection and 
-for the case of \emph{MMC} to panorama recognition and alignment. For 
-the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
-improvement over \emph{Ratio} in a near duplicate detection framework 
-making use of local features. Similarly for panorama recognition and 
-alignment a simple panorama stitching method based on \emph{MMC} 
-succeeds in cases where \emph{Autostitch} is unable to recognize and 
-align the source images correctly. Both applications illustrate the 
-central role that performance of the matching algorithm has on tasks 
-that makes use of local features to match image pairs with potential 
-overlap.
-%
-
-\bibliographystyle{IEEEtran}
-\bibliography{bibliography}
 \end{document}

### 2013-08-09 text/thesis_bak.tex
Reorganized thesis

%\documentclass[report]{IEEEtran}
\documentclass{article}
\usepackage{footnote}
%\usepackage[font={small}]{caption}
\usepackage{sidecap}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
%\usepackage[stable]{footmisc}
\usepackage{caption}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}

\title{Reliable feature point matching}
\author{Jonas Arnfred}

\maketitle

\section{Introduction}
What is the subject of this thesis and in what part lies my 
contribution?
How is the report organized?

\section{Background}
Introduction to Computer Vision
 - Introduce common tasks that we are good at that computers aren't
 - Single in on tasks that we can solve using feature points

Introduction to feature points
 - Global explanation of what they are and how they serve to solve the 
problems mentioned before
 - How do we find them? (Examples making it intuitive why corners are 
nice)
 - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
 Scale, \ldots, Affine)
 - Introduce SIFT and explain how the different problems are tackled in 
SIFT)
 - Talk about other methods and how they are different

Matching feature points
 - What applications require matching?
 - How is matching usually done
 - Segue into related work from paper

\section{Matching feature points}
Basically c/p from paper, but better figures and maybe more explanations
 - Add path about graphs and how they are formed. Make sure to explain 
 the clustering in more detail and make it easier to understand
 - Add a good explanation for new figures and how the precision and 
 recall are calculated. This should appear somewhere before results.
 - Add part on spectral matching and modify accordingly. Make sure to 
 underline how the second plot shows how the geometric method is 
 independent of MMC and that they combined yield greater results.

\subsection{Proposed Matching Methods}
\label{S:MatchingMethods}

\subsubsection{Mirror Match (\emph{MM})}

\begin{figure}
	\centering%
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
			\caption{Source image pair}
			\label{fig:pitts_source}
		\end{subfigure}%
		\\ %
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
			\caption{Feature points}
			\label{fig:pitts_keypoints}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
			\caption{\emph{Ratio}}
			\label{fig:unique}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
			\caption{\emph{MM} intermediate result}
			\label{fig:within}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
			\caption{\emph{MM} final result}
			\label{fig:without}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		\begin{subfigure}[t]{\columnwidth}
			\centering
			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
			\caption{\emph{MMC} Partition Example}
			\label{fig:pitts_partition}
		\end{subfigure}%
	\caption{Feature matching with \emph{MM} and \emph{MMC}. Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.  
	(c) Result of \emph{Ratio} matching. 
  (d) All matches found by \emph{MM}, including intra-image matches. 
	(e) Final \emph{MM} result. 
	(f) Example of a partition of feature points after clustering, which 
includes similar feature points from building windows and shirt patterns.}%
	\label{fig:comparemirror}%
\end{figure}%

%
The central idea behind \emph{MM} is to match features of $n$ images by 
taking every feature from all $n$ images and matching it against every 
other feature from the same set. We can then discard the correspondences 
that match two points within the same image. Algorithm~\ref{alg-mm} details  
the implementation of \emph{MM}.
%
\begin{algorithm}
\caption{Mirror Match (\emph{MM})}
\label{alg-mm}
%{\fontsize{10}{10}\selectfont
\begin{algorithmic}
\Require $images$ : set of images, $t \in \mathbb{R}$
\State $matches_{init}\gets \varnothing$
\State $matches_{final}\gets \varnothing$
\State $features\gets \varnothing$
\ForAll{$I_i \in images$} \Comment Acquisition Stage
	\State $features\gets features \cup getFeatures(I_i)$
\EndFor
\ForAll{$f_i \in features$} \Comment Matching Stage
	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
	\left\{f_i\right\})$
	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
	\If{$ratio < t$}
		\State $matches_{init} \gets matches_{init} \cup \left(f_i, f_m\right)$
	\EndIf
\EndFor
\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
Stage
\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
		\State $matches_{final} \gets (f_i, f_j)$
	\EndIf
\EndFor \\
\Return $matches_{final}$
\end{algorithmic}
%}
\end{algorithm}
%
In the acquisition stage we gather all features in the set of images.  
In the matching stage these features are matched using $k$-nearest 
neighbors.  For any given feature $f_i$ the two most similar neighbors 
are returned, and we calculate the ratio between them as proposed in 
\cite{lowe2004sift}.  Any correspondence with a ratio above the 
threshold supplied will be discarded. Finally in the filter stage we 
check that matches are from different images and discard all matches 
that are not symmetric.
%
%\begin{figure*}
%	\makebox[\textwidth][c]{%
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
%			\caption{Source image pair}
%			\label{fig:pitts_source}
%		\end{subfigure}%
%		\enspace %
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
%			\caption{Feature points}
%			\label{fig:pitts_keypoints}
%		\end{subfigure}%
%		\enspace %add desired spacing between images, e. g. ~, \quad, 
%		%\qquad (or a blank line to force the subfigure onto a new line)
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/mirror_match_off}
%			\caption{\emph{Ratio}}
%			\label{fig:unique}
%		\end{subfigure}%
%	}
%	\makebox[\textwidth][c]{%
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
%			\caption{\emph{MM} intermediate result}
%			\label{fig:within}
%		\end{subfigure}%
%		\enspace %add desired spacing between images, e. g. ~, \quad, 
%		%\qquad (or a blank line to force the subfigure onto a new line)
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/mirror_match}
%			\caption{\emph{MM} final result}
%			\label{fig:without}
%		\end{subfigure}%
%		\enspace%
%		\begin{subfigure}[t]{0.32\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/MMC_partition}
%			\caption{\emph{MMC} Partition Example}
%			\label{fig:pitts_partition}
%		\end{subfigure}%
%	}%
%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}. Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.  
%(c) Result of \emph{Ratio} matching the two images.% 
%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
%	(e) Final \emph{MM} result with the intra-image matches removed. 
%	(f) Example of a partition of feature points after clustering. This partition 
%includes similar feature points around the windows of a building and the patterns of a shirt.}%
%	\label{fig:comparemirror}%
%\end{figure*}%

Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} 
using an example image pair from the Gallagher dataset 
\cite{gallagher2008}.
With \emph{Ratio} (Figure~\ref{fig:unique}), many incorrect matches occur 
in the fence towards the bottom of the image.
When we match all feature points together, many of these incorrect 
matches are eliminated, because points in the fence match with other 
points in the fence in the same image (Figures~\ref{fig:within} and
\ref{fig:without}).

\subsubsection{Mirror Match with Clustering (\emph{MMC})}
%
In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
non-geometric feature matching by clustering feature points by 
similarity. This process yields partitions of fairly similar feature 
points that we can match using the same approach as \emph{MM}.  
Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.

Before we introduce the implementation details we will go over the 
problem of graph clustering and how it relates to feature matching.

Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
points in an image and returns their matching score, we can define a 
matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
as the \emph{adjecency matrix} of the fully connected graph where each 
vertex corresponds to a keypoint and the edge between two vertices has a 
weight equal to the distance between the two corresponding keypoints.

This representation reduces the problem of partitioning the keypoints 
into groups to that of graph clustering or community structure depending 
on the context. In the literature there are various ways of clustering a 
graph according to different measures of what constitutes an optimal 
partitioning. Traditionally the most used clustering algorithms have 
been K-means and spectral clustering, but in recent years a host of new 
algorithms have been proposed based on both Newman's concept of graph 
modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
well as information theoretical measures\footnote{See for example 
\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
new algorithms differ from K-means clustering and Spectral clustering 
in that they do not require the number of expected to clusters to be 
specified beforehand\footnote{Among the aforementioned methods, this is 
true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
tests done using randomly generated graphs with a known partitioning 
\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
markedly better than spectral clustering and 
K-means\cite{lancichinetti2009}.

The performance of clustering algorithms is a complicated issue, since 
an optimal clustering given the same graph can vary depending on the 
application. Spectral clustering for example will usually return a 
partitioning where each partition is roughly equal in size\footnote{As 
mentioned in \cite{von2007}} while the Louvain 
clustering\cite{blondel2008} might return partitions of very uneven 
size, even if the modularity measurement has been shown to penalize very 
small clusters\cite{brandes2007}. Both behaviours can be beneficial 
depending on the application, but when clustering feature points, 
maintaining clusters of an even size usually means that some clusters 
will be '\emph{catch-all}' clusters where the feature points that do 
not fit anywhere else are grouped together. The necessity of specifying 
the amount of partitions in for example Spectral clustering or Pott's 
model clustering further exacerbates the issue since smaller partitions 
are then combined into one to achieve the right amount of partitions.

%
\begin{algorithm}
\caption{Mirror Match with Clustering (\emph{MMC})}
\label{alg-mmc}
%{\fontsize{10}{10}\selectfont
\begin{algorithmic}
\Require $images$ : set of images, $t \in \mathbb{R}$
\State $M\gets \varnothing$
\State $F\gets \varnothing$
\ForAll{$I_i \in images$} \Comment Gather features
	\State $f_i\gets getFeatures(I_i)$
	\State $F\gets F \cup f_i$
\EndFor
\State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
\State $A_{norm}\gets 1 - normalize(A)$
\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
\State $P\gets cluster(A_{pruned})$
\ForAll{$p \in P$} \Comment p is a set of feature points
	\State $M\gets M \cup getMatches(p, t, F)$
\EndFor \\
\Return matches
\end{algorithmic}
%}
\end{algorithm}

\begin{figure}[t]
    \centering
\makebox[\textwidth][c]{%
    \includegraphics[width=1.1\textwidth]{images/MMC_graph}
    \label{fig:graph}
}
    \caption{The partitioned feature graph. Each vertex represents a 
        feature point; lines indicate high similarity between points. A 
        partition is a connected group with the same color. The border 
        color of each node indicates which image it belongs to.  Zooming 
    into a subsection of the graph (right part), the various cluster 
sizes can be seen, ranging from hundreds of feature points to only two 
or three.}
	\label{fig:graph}
\end{figure}

We use the Louvain Method \cite{blondel2008} for clustering feature 
points, since it is relatively fast and performs well 
\cite{lancichinetti2009}, does not require parameters 
\cite{blondel2008}, and does not emphasize partitions of equal size, as 
opposed to spectral clustering or k-means \cite{von2007}, for example.
While the Louvain clustering algorithm does not require any parameters 
in itself, it tends towards clustering all feature points together in 
the same partition if the graph is very connected.  To ensure that the 
graph is well clustered, the adjacency matrix is pruned so that only 
edges above a certain threshold are kept. From empirical analysis, 
retaining the top 2.5\% of edges with the highest similarity seems to 
work well in practice. Figure~\ref{fig:graph} shows the result of 
clustering the feature points as a graph.
%

The partitions group feature points by similarity, which means that 
repetitive structures such as buildings often appear in larger 
partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
%

\begin{algorithm}
\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
\label{alg-getmatches}
    \fontsize{10}{10}\selectfont
    \begin{algorithmic}
    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
    all features
    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
    \If{$\left\vert edges \right\vert > 1$}
        \State $matches \gets MMGet(p, t)$
    \ElsIf{$\left\vert edges \right\vert = 1$}
        \State $matches \gets RatioGet(p, features, t)$
    \Else
        \State $matches \gets \varnothing$
    \EndIf

    \Return matches
    \end{algorithmic}
\end{algorithm}

The matching algorithm for \emph{MMC} detailed in 
Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
more than two elements using the \emph{MM} approach.  However, as can be 
seen in the example in Figure~\ref{fig:MMC_graph}, many of the 
partitions contain only two feature points from different images linked 
by one edge. In this case, we compare the similarity of the these two 
feature points with their second best match and remove matches where 
this ratio lies above a certain threshold, like in the \emph{Ratio} 
algorithm.  For example in the case of Figure~\ref{fig:pitts_partition}, 
we have feature points from a building in one image grouped together 
with points from a shirt pattern in another.  The nearest neighbor 
method would have returned wrong matches, but since we match the 
partition with \emph{MM}, points in the building end up matching other 
points in the building, and no matches are returned.

\subsection{Experiments}
\label{S:Experiments}
%
To reliably measure the accuracy of a matching method on real images, we 
either need a set of image pairs tied by a homography, or we have to 
manually count the number of inliers. The latter becomes prohibitive for 
large numbers of (non-trivial) images.

Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
set of test images to compare the performance of feature detectors. The 
set covers different types of image variations, such as lighting change, 
blur, rotation, and viewpoint change. Inspired by this dataset (in 
particular the `Graf' image set) and motivated by the need for more 
image pairs featuring viewpoint changes, we have compiled a set of 8 
image pairs consisting of subjects taken from two different angles. The 
images are collected from Flickr's database of images published under a 
creative commons licence and feature murals, which makes it possible to 
relate points in the image pairs with a homography since most of the 
points in the images will be lying on a plane.  The images have been 
cropped to show the same motive and resized to $900\times 600$ pixels.  
This dataset will be referred to as the \emph{Murals} dataset.  
Figure~\ref{fig:murals} shows one image from each pair.

\begin{figure}[htb]
    \makebox[1.0\textwidth][c]{%
        \begin{subfigure}[t]{0.102\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/pair_example1}
			\label{fig:fairey1}
	\end{subfigure}%
		\enspace %add desired spacing between images, e. g. ~, \quad, 
		%(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[t]{0.102\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/pair_example2}
			\label{fig:fairey2}
		\end{subfigure}%
		\enspace %
        \begin{subfigure}[t]{0.77\textwidth}
   		\centering
   		\includegraphics[width=\columnwidth]{images/crop_examples}
		\end{subfigure}%
	}%
	\caption{Sample test patches produced from an image pair.}
	\label{fig:fairey}
\end{figure}

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{images/murals}
	\caption{Images in the \emph{Murals} test set.}
	\label{fig:murals}
\end{figure*}

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
	\label{fig:Graf}
\end{figure}

\subsubsection{Experimental setup}
We compare the \emph{MM} and \emph{MMC} algorithms to \emph{Ratio} 
\cite{lowe2004sift} as well as \emph{Isomatch} \cite{das2008event} and 
\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isomatch} and 
\emph{Spectral} uses geometric constraints, whereas \emph{Ratio} does 
not.

\begin{algorithm}
\caption{Ratio Match (\emph{Ratio})}
\label{alg-ratio}
%{\fontsize{10}{10}\selectfont
\begin{algorithmic}
\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
\State $matches\gets \varnothing$
\State $features_1 \gets getFeatures(im_1)$
\State $features_2 \gets getFeatures(im_2)$
\ForAll{$f_i \in features_1$}
    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
	\If{$ratio < t$}
        \State $matches \gets \left(f_i, f_m\right)$
	\EndIf
\EndFor
\Return $matches$
\end{algorithmic}
%}
\end{algorithm}

\emph{Ratio} (Algorithm~\ref{alg-ratio}) \cite{lowe2004sift} is the most 
straightforward of the three reference algorithms. Feature points are 
matched using K Nearest Neighbor and the similarity ratio between the 
best and second best match is then compared to a threshold to decide if 
the match is kept.

\begin{algorithm}
\caption{Isodata Match (\emph{Isomatch})}
\label{alg-isodata}
%{\fontsize{10}{10}\selectfont
\begin{algorithmic}
\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
\State $matches_{init}\gets \varnothing$
\State $matches_{final}\gets \varnothing$
\State $features_1 \gets getFeatures(im_1)$
\State $features_2 \gets getFeatures(im_2)$
\ForAll{$f_i \in features_1$}
    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
    \State $matches_{init} \gets \left(f_i, f_m\right)$
\EndFor
\State $partitions_1 \gets isodata(getPositions(features_1))$
\State $partitions_2 \gets isodata(getPositions(features_2))$
\State $P_{corr} \gets getMatchMat(partitions_1, partitions_2, 
matches_{init})$
\ForAll{$(i,j) \in indices(P)$}
    \If{$\left(P_{i,j} > 5\right) \wedge \left(P_{i,j} / sum(P_{i}) > 
    0.5\right)$}
        \State $matches_{final} \gets getMatches(matches_{init}, 
        partitions_1, partitions_2, i, j)$
    \EndIf
\EndFor
\Return $matches_{final}$
\end{algorithmic}
%}
\end{algorithm}

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{images/isomatch_partitions}
	\caption{The result of partitioning feature points in two images.  
	Each dot represents a feature point and feature points grouped with 
the same color belong to the same partition.}
	\label{fig:isomatch_partitions}
\end{figure}

The \emph{Isomatch} algorithm (Algorithm~\ref{alg-isodata}) 
\cite{das2008event} is based on the idea that local feature points 
within a region in one image often matches to features within a 
corresponding region in the other image. To find these regions the 
algorithm uses the Isodata algorithm \cite{ball1965isodata} to perform 
unsupervised clustering on the feature points given their positions in 
the two images. The Isodata algorithm is similar to K-means with the 
addition that clusters are merged and split during the clustering 
process. In Figure~\ref{fig:isomatch_partitions} an example of a 
partitioning can be seen. The initial set of matches are filtered based 
on the resulting regions. A match is kept only if it at least half the 
matches of the same region of origin also belong to the same region in 
the other image.  $P_{corr}$ in Algorithm~\ref{alg-isodata} is a matrix 
where each row corresponds to a region in $im_1$, each column 
corresponds to a region in $im_2$ and $P_{i,j}$ is the amount of matches 
going from region $i$ to region $j$.

To threshold the \emph{Isomatch} algorithm we filter the results using 
the ratio between first and second best match as in \emph{Ratio}, since 
\emph{Isomatch} itself doesn't readily admit any thresholding parameter.

\begin{algorithm}
\caption{Spectral Match (\emph{Spectral})}
\label{alg-spectral}
%{\fontsize{10}{10}\selectfont
\begin{algorithmic}
\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
\State $matches_{init}\gets \varnothing$
\State $matches_{final} \gets \varnothing$
\State $features_1 \gets getFeatures(im_1)$
\State $features_2 \gets getFeatures(im_2)$
\ForAll{$f_i \in features_1$}
	\State $f_m,f_n \gets get2NNs(f_i, features_2)$
	\State $matches_{init} \gets \left(f_i, f_m\right)$
\EndFor
\State $M \gets matrix(\left\vert matches_{init} \right\vert, \left\vert 
matches_{init} \right\vert)$
\ForAll{$m_i \in matches_{init}$}
	\ForAll{$m_j \in matches_{init}$}
		\If{$i = j$}
			\State $M \gets matchSimilarity(m_i)$
		\Else
			\State $M \gets affinity(m_i, m_j)$
		\EndIf
	\EndFor
\EndFor
\State $x^{*} \gets maximumEigenvector(M)$
\ForAll{$\left(m_i, x_i\right) \in \left(matches_{init}, x^{*}\right)$}
	\If{$x_i > t$}
		\State $matches_{final} \gets matchtes_{final} \cup m_i$
	\EndIf
\EndFor
\Return $matches_{final}$
\end{algorithmic}
%}
\end{algorithm}

The \emph{Spectral} algorithm (Algorithm~\ref{alg-spectral}) is a 
slightly modified version of the spectral matching algorithm proposed by
Leordeanu and Herbert \cite{leordeanu2005spectral}. It is based on the 
idea that the set of actual correspondences of feature points between 
two images should be pairwise consistent. That is, given two feature 
points that are geometrically close in one image, for most cases we 
would assume that the closest correspondences in another image would be 
similarly close. We want to pick out a set of matches $T \subset S$ 
where $S$ is the initial set of possible matches such that the matches 
in $T$ are as pairwise consistent as possible. If we let $x$ be a binary 
vector corresponding in length to the set of initial matches $S$, where 
$x_i = 1$ if $m_i \subset T$, then we can formulate a subset-score as:
\begin{equation*}
	S = \sum_{m_i, m_j \in T} M(m_i, m_j) = x^TMx
\end{equation*}
The solution $x^{*}$ that maximizes this equation is then $x^{*} = 
argmax(x^TMx)$. By relaxing the constraints on $x$ such that it can take
values in the range of $\left[0, 1\right]$ we can interpret $x_i$ as the
association of $m_i$ with the optimal subset of matches $T$. Because we 
only worry about the relative values of $x$ we can fix the norm of $x$ 
to $1$, in which case by Raleigh's ratio theorem, the $x^{*}$ that 
optimizes $x^TMx$ is the principal eigenvector of $M$.

Leordeanu and Herbert proposes a simple affinity function to map the 
pairwise distance of two matches. In a scene where no rotation and 
excessive affine transformation takes place, it can generally be assumed 
that the length and direction of the vector between
the two feature points constituting the first match corresponds to the 
length and direction of the vector between the two feature points 
constituting the second match. Given two matches $m_i = (f_{i,1}, 
f_{i,2})$ and $m_j = (f_{j,1},f_{j,2})$ where $f_{k,n}$ is the feature 
point of match $k$ in image $n$, we denote the euclidean distance 
between feature points $f_{i,n}$ and $f_{j,n}$ in image $n$ as 
$d_{i,j,n}$.  The affinity function assigning a score based on the 
pairwise distance is then defined as follows:
\begin{equation*}
	M(a,b) \begin{cases} 4.5 - \frac{\left(d_{i,j,1} - 
		d_{i,j,2}\right)^2}{2\sigma^2}, & \mbox{if } \left\vert 
				d_{i,j,1} - d_{i,j,2} \right\vert < 3\sigma \\ 0, & 
				\mbox{otherwise}
	\end{cases}
\end{equation*}
Here $\sigma$ is a stabilizing parameter and in the following 
experiments it is fixed to 50 after empirical optimization.  There are a 
number of occasions where the assumption that pairwise matches should 
have the same distance doesn't hold true.  A simple example would be 
matches between two images of the same scene where one image is rotated 
$180^{\circ}$.  However for a lot of applications like panorama 
stitching where we only see minor rotation and change of perspective the 
assumption is accurate.

In the implementation proposed by Leordeanu and Herbert 
\cite{leordeanu2005spectral} the last step of the algorithm greedily 
selects matches to ensure that matches are consistent, i.e.\ that two 
feature points in one image don't match with the same feature point in 
the other image. This is done by going through all the matches in the 
order of their associated $x^{*}$ score and for each match eliminating 
all matches in conflict with this match. This method ensure that as many
matches are kept as possible since only the conflicting matches are 
removed. However for cases where most feature points in one image will 
not have a correspondence in the other other image (e.g.\ cases of 
partial image overlap or object recognition) the greedy matching 
algorithm will keep finding matches even after the actual 
correspondences have already been found as long as they are consistent.

Since the testing is done on images with partial overlap, the final set 
of matches returned in Algorithm~\ref{alg-spectral} is the set of 
matches where the association of the match with the optimal subset of 
matches $T$ as measured by $x^{*}$ is above a certain threshold. For 
experiments the set of initial matches were given by the best match per 
feature point and the threshold was adjusted to allow for the best 50\% 
to be included in the set of final matches. A rate less than 50\% 
usually did not improve results, so to threshold the \emph{Spectral}
algorithm we filter the output using the ratio between first and second
best match as done in \emph{Ratio}.

%, which uses geometric information to improve the matching.  The 
%comparison  with \emph{Ratio} serves to illustrate the relative 
%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
%without geometric constraints. \emph{Isomatch} is included to 
%illustrate the performance of an algorithm relying on geometric 
%constraints faced with image pairs that might not have any overlap.  
The comparison was done using the \emph{Murals} dataset 
(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
from \cite{mikolajczyk2005performance}, and two 
images\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher 
dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).

Test sets were generated from the image pairs by cropping square patches of
$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
This ensures that patch pairs with no overlap still retain a general similarity to each 
other, while patches that do overlap often only share a small 
part of their area. Figure~\ref{fig:fairey} shows an example of 
possible pairs of test image patches produced from a source image pair.  
Producing $n$ such pairs allows us to test not just how well the 
matching algorithm performs on a variety of overlaps but also how many 
false positives we get on similar images that do not overlap at all. In 
practice the amount of overlap between pairs in a test set will depend 
on the overlap and viewpoint change in the source image pair.  To give a 
rough idea, Table~\ref{table:overlap} shows the overlap of patch pairs 
created from images 1 and 3 of the \emph{Graf} image set from 
\cite{mikolajczyk2005performance}.

\begin{table}[htb]
\caption{Overlap in the set of 100 patch pairs created from two images 
of the \emph{Graf} image set (Figure~\ref{fig:Graf}).}
\label{table:overlap}
    \centering
%   \small
\begin{tabular}{r*{3}{r}}
\hline
    Amount of overlap: & 0\% & $< 50$\% & $> 50$\%  \\
    \noalign{\smallskip}
	%
    Number of patch pairs: & 21 & 54 & 25 \\
    \hline
\end{tabular}
\end{table}

Given a potential match between two pixels $p_1$ and $p_2$, $m = 
\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
two points satisfy the following criteria:
\begin{equation*}
\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
\end{equation*}
That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
less than a certain threshold (we use $d_{\max}=5$ pixels here).

\subsection{Results}
\label{S:Results}

Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
generated from images 1 and 3 of the \emph{Graf} image set 
(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isomatch} as a function of 
the number of matches produced (which is achieved by varying thresholds 
over a certain range). The results show that \emph{MM} and \emph{MMC} 
consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
percentage points above \emph{MM} when both are performing at optimal 
accuracy.  Although \emph{Isomatch} exhibits a good performance on strict 
thresholds (small number of matches), that quickly diminishes when more 
matches are desired.

\begin{figure}[htb]
%	\makebox[0.5\textwidth][c]{%
%		\begin{subfigure}[t]{.13\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/graf}
%		\end{subfigure}%
%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
		%(or a blank line to force the subfigure onto a new line)
%		\begin{subfigure}[t]{.27\textwidth}
			\centering
			\includegraphics[width=0.6\columnwidth]{images/result_graf}
			%\caption{Performance on Scharf}
%		\end{subfigure}%
%	}%
	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
		shows the result of 100 patch pairs generated from the source 
		images shown to the left. The number of matches is the total 
		number of matches for all 100 patch pairs.}
	\label{fig:result_graf}
\end{figure}

To validate whether these results 
generalize to other images, we tested the four algorithms on the 
\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
In total 900 different patch pairs were generated from 9 
source image pairs.  The results are shown in Figure 
\ref{fig:result_accumulated}.

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{images/result_accumulated}
	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
	\label{fig:result_accumulated}
\end{figure}

To further investigate the impact of viewpoint changes, we tested the 
algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
contains 5 images of the same mural taken with gradually increasing 
viewpoint changes.  The first images are almost identical, while the 
last are taken from very different angles. The results from   \emph{MMC} 
and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
viewpoint changes.
The performance of \emph{MM} (not shown in the plot) is similar to 
\emph{MMC}.

\begin{figure}[htb]
	\centering
	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
	\caption{Results for viewpoint changes using the \emph{Graf} set from 
		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
	\label{fig:result_viewpoint}
\end{figure}

Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
shows the results on 100 patch pairs generated 
from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.

\begin{figure}[htb]
%	\makebox[0.5\textwidth][c]{%
%		\begin{subfigure}[t]{.15\textwidth}
%			\centering
%			\includegraphics[width=\textwidth]{images/pitts}
%		\end{subfigure}%
		~%add desired spacing between images, e. g. ~, \quad, \qquad
		%(or a blank line to force the subfigure onto a new line)
%		\begin{subfigure}[t]{.27\textwidth}
			\centering
			\includegraphics[width=0.6\columnwidth]{images/result_pitts}
			%\caption{Performance on Scharf}
%		\end{subfigure}%
%	}%
	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
	\label{fig:result_pitts}
\end{figure}

In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isomatch} can be 
implemented in $O(n\log n)$, where $n$ is the total number of feature 
points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
construction of a similarity matrix of the feature points. However, it is 
possible to approximate this in $O(n\log n)$ using search trees.

As for speed, Table~\ref{table:running_times} shows the running time of 
the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
These numbers should be taken with a grain of salt, given that much of 
the code behind \emph{MMC} and \emph{Isomatch} is implemented in Python, 
whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
computationally intensive operations in C++, which makes them much 
faster.

\begin{table}[htb]
\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
3.30~GHz with 8~GB memory.}
\label{table:running_times}
	\centering
%	\small
\begin{tabular}{r*{4}{c}}
\hline
	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isomatch} 
	\\
	\noalign{\smallskip} 
	%
	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
	\hline
\end{tabular}
\end{table}
%

\section{Applications}

In many areas of computer vision matching local feature points is a key 
component, and matching algorithms have applications in problems such as
scene matching, object recognition, near duplicate detection and 
panorama recognition. To show the practical applications of the proposed 
matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
improve existing methods in near duplicate detection and panorama 
recognition. These two problems were chosen because they both involve 
matching images that might or might not overlap. These cases requires 
matching algorithms that limit false positives since e.g. returning the 
top $n$ matches for any given image pair would make it hard to 
distinguish adjacent or duplicate images from non-adjacent or dissimilar
image pairs. Near duplicate detection also constraints normal matching 
algorithms from relying on geometric assumptions, since we have very few
guarantees between two potential near duplicates that they should be 
matched using any particular geometric heuristic. In this section, we 
will first see \emph{MMC} applied to panorama recognition and alignment,
and next \emph{MM} and \emph{MMC} applied to near duplicate detection.

\subsection{Panorama Recognition and Alignment}
One of the oldest practical problems approached in computer vision is 
the automatic stitching of several source images into a bigger image, 
such as panoramas and composite satellite photos\footnote{A brief 
overview of the history of image stitching can be found in Szeliski's 
book: Computer Vision: Algorithms and Applications \cite{szeliski2010}}.  
As part of the process of stitching together images, the individual 
images must be aligned and often transformed in perspective. Earlier 
methods relied on minimizing pixel dissimilarities in overlapping images 
while more recent methods have used local feature points to estimate the 
correct image alignment. Using local feature points carry the additional 
advantage that it is feasible to automatically recognize where each 
source image belong in the final panorama.

\begin{figure}[h]
	\begin{subfigure}[t]{0.9\textwidth}
		\centering
        \includegraphics[width=\textwidth]{images/pano_wide}
        \label{fig:pano_images}
		\caption{Source images}
    \end{subfigure}%
	\\
	\centering
    \begin{subfigure}[b]{0.4\textwidth}
		\includegraphics[width=\textwidth]{images/panorama-autostitch}
        \label{fig:pano_autostitch}
		\caption{Panorama by Autostitch}
    \end{subfigure}%
	~%add desired spacing between images, e. g. ~, \quad, \qquad
	%(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
		\includegraphics[width=\textwidth]{images/panorama-MMC}
		\caption{Panorama by MMC}
		\label{fig:pano_MMC}
	\end{subfigure}%
    \label{fig:pano_example}
	\caption{An example of a difficult case for panorama recognition and 
		alignment.  In a) the source images used to generate the 
		panorama are displayed.\ b) shows the result of the Autostitch 
		program from \cite{brown2007automatic} which fails to combine 
		all images, while c) demonstrates the result of the simple 
		panorama stitcher
	using the proposed MMC algorithm. Here the two left images are 
correctly linked}
\end{figure}

In \cite{brown2007automatic}, Brown and Lowe demonstrate how a panoramic 
image can be assembled by collecting the feature points of all source 
images and matching them to obtain a set of inter image matches.  By 
using \emph{RANSAC}\footnote{RANdom SAmple Consensus, an iterative 
    algorithm to estimate parameters from noisy data introduced in 
Fischler and Bolles in 1981 \cite{fischler1981ransac}} to find matches 
deemed as inliers between image pairs, they are able to recognize image 
neighbors and align them to construct the final panorama.

This process hinges on the effectiveness of the matching algorithm used 
to match the feature points. Not only is it important that true pairs 
are accurately matched, but since we are matching points in image pairs 
that might not be adjacent in the final panorama, we also need to make 
sure that we consistently reject false positives, i.e.\ proposed matches 
that link feature points which don't correspond.

To demonstrate the usefulness of \emph{MMC} applied to panorama 
recognition and alignment we construct a simple panorama stitcher taking
as input a set of $n$ source images $\left\{I_0, \ldots, I_n\right\}$ 
and returns as output a panoramic image stitched together from the 
source images. Based on the matches found by applying \emph{MMC} to $I$, 
the images are combined in an order corresponding to how many matches 
connect them, as done by Brown and Lowe \cite{brown2007automatic}.

Brown and Lowe make use of bundle adjustment\footnote{Bundle adjustment 
provides a way to globally optimize the accuracy of the image alignment} 
and a lot of image enhancements such as exposure adjustment and edge 
blurring to provide a seamless panorama. While these additions improve 
the end product, they don't influence the performance of panorama 
alignment and recognition and haven't been included in the simple 
comparison algorithm.

Figure~\ref{fig:pano_example} shows an example where the added accuracy 
of MMC enables us to correctly recognitize and align source images that 
fail to be combined by Autostitch, a program using the algorithm 
proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
case the matching algorithm used in Autostitch fails to find sufficient 
matches between two images pairs to correctly position them and 
consequently doesn't produce a panorama containing all images as a 
result.

This example illustrates how an improved matching algorithm can be 
applied to panorama recognition and alignment to allow for panoramas 
created with images that have little overlap.
% Maybe find example of images with identical features that would be 
% hard to match?

\subsection{Near Duplicate Detection}
If we look at two images, we can often easily tell if one image 
resembles the other enough to be redundant in a photo album. In computer 
vision this task becomes a lot less trivial because our idea of a 
duplicate image might only require there being some object or scene in 
common between the image pair. In addition the object or scene might 
have been taken from a different angle and under different camera 
settings. Facing these challenges, a lot of work has been done trying to 
reliably recognize duplicaes both with regards to corporate intellectual 
property as well as consumer photo albums because both applications 
provide useful tools.  A company might be interested in finding images 
that are derived from their intellectual property, while consumers 
taking vacation photos might be interested in grouping duplicate images 
to allow for easier photo organization.

Local features are often used to group similar images, either by looking
at a histogram of descriptors \cite{wu2009bundling} or by looking at how
well feature points match between images \cite{zhao2009scale},
\cite{chu2010consumer}, \cite{vas2013cluster}. In the latter case 
finding near duplicates means that we will be matching image pairs that 
might or might not contain any actual matches. In this case we would 
benefit from a reliable matching algorithm that minimizes false 
positives, which is a characteristic of both \emph{MM} and \emph{MMC}.

The \emph{PhotoCluster} method introduced by Vonikakis et al.  
\cite{vas2013cluster} shows the best clustering performance on the 
California-nd dataset \cite{jinda2012california} which contains a set of
annotated vacation images similar to a typical photo album in a consumer
product. \emph{PhotoCluster} works by grouping images in several steps 
using first image metadata and global features to obtain a set of 
proposed clusters. Then local features are used to find the best 
matching images in these proposed clusters yielding the final groups of 
near duplicate images. To show the viability of \emph{MMC} in the 
application of near duplicated detection, we modify the PhotoCluster 
method to use \emph{MMC} for matching images instead of \emph{Ratio} 
which was previously used. Due to the time consumption of \emph{MMC}, 
all images where resized to to 10\% before being compared. Outside of 
that, the experiments were performed exactly as documented in 
\cite{vas2013cluster}.

\begin{table}[htb]
\caption{Results from Near Duplicate Detection at 10\% scale}
\label{table:ndd}
	\centering
%	\small
\begin{tabular}{r*{2}{r}}
\hline
    Method: & Ratio & MMC   \\
	\noalign{\smallskip}
	%
    F1 score: & 0.4654 & 0.5459 \\
	\hline
\end{tabular}
\end{table}

The results of the comparison can be seen in Table~\ref{table:nnd}. It 
shows that \emph{MMC} improves performance by 8.05\% over the original 
framework using \emph{Ratio} to match images. For comparison, the 
performance improvement of \emph{PhotoCluster} compared to XMatch 
\cite{zhao2009scale}, the second best performing algorithm on the 
California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.

\section{Summary}
\label{S:Summary}

This thesis has addressed the problem of matching feature points without 
using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
common idea that feature points should have better matches in another 
image than in the image they came from to be considered good matches.  
\emph{MMC} further improves on this idea by using the structure of the 
similarity graph of the feature points.

The algorithms show promising results when tested on the \emph{Murals} 
data set. The results on 900 image pairs show that \emph{MM} and 
\emph{MMC} generally outperform existing matching algorithms 
\emph{Ratio}, \emph{Isomatch} and \emph{Spectral}. In addition \emph{MMC} 
outperforms \emph{MM}.  We show that this result generalizes to 
variations in viewpoint change by comparing \emph{MMC} to \emph{Ratio} 
over a set of image pairs with an increasing magnitude of perspective 
difference. We go on to apply the algorithms to a real life image case 
featuring occlusion and a slight viewpoint change and show that the 
performance of \emph{MM} and \emph{MMC} is consistent with the results 
on \emph{Murals}. To show that \emph{MM} or \emph{MMC}
can further improve the results of a geometrical method, we create 
\emph{Spectral-MMC} by combining \emph{Spectral} and \emph{MMC} and 
compare the three on the full \emph{Murals} dataset where it yields 
results better than both \emph{Spectral} and \emph{MMC}.

The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
applying the algorithms to the problems of near duplicate detection and 
for the case of \emph{MMC} to panorama recognition and alignment. For 
the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
improvement over \emph{Ratio} in a near duplicate detection framework 
making use of local features. Similarly for panorama recognition and 
alignment a simple panorama stitching method based on \emph{MMC} 
succeeds in cases where \emph{Autostitch} is unable to recognize and 
align the source images correctly. Both applications illustrate the 
central role that performance of the matching algorithm has on tasks 
that makes use of local features to match image pairs with potential 
overlap.
%

\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\end{document}

### 2013-08-10 text/main/ch5_experiments.tex
Updated thesis with spectral-mmc info and better figures

@@
 \begin{figure}[htb]
-	\makebox[0.5\textwidth][c]{%
-		\begin{subfigure}[t]{.13\textwidth}
+	\begin{subfigure}[c]{0.2\textwidth}
 		\centering
@@
 	%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{.27\textwidth}
+	\begin{subfigure}[c]{0.8\textwidth}
 	\centering
-   		\includegraphics[width=0.6\columnwidth]{images/result_graf}
+	\includegraphics[width=\columnwidth]{images/result_graf}
 	%\caption{Performance on Scharf}
 	\end{subfigure}%
-	}%
-	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
-		shows the result of 100 patch pairs generated from the source 
-		images shown to the left. The number of matches is the total 
-		number of matches for all 100 patch pairs.}
+	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The 
+	plot shows the result of 100 patch pairs generated from the source 
+images shown to the left. The number of matches is the total number of 
+matches for all 100 patch pairs.}
 	\label{fig:result_graf}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
-	\caption{Results for viewpoint changes using the \emph{Graf} set from 
-		\cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: img1\&4; XL: img1\&5.}
+	\includegraphics[width=1\textwidth]{images/result_viewpoint}
+	\caption{Results for viewpoint changes using the \emph{Graf} set 
+	from \cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: 
+	img1\&4; XL: img1\&5.}
 	\label{fig:result_viewpoint}
+\end{figure}
+
+In order to investigate whether a geometric algorithm can be improved by
+pruning the initial matching set, we tested a hybrid algorithm 
+\emph{Spectral-MMC} where matches are pruned by \emph{MMC} before being 
+applied to \emph{Spectral}. The results are shown in 
+Figure~\ref{fig:result_spectral-mmc} and show that \emph{Spectral-MMC} 
+not only outperforms \emph{Spectral} but also improves on \emph{MMC} at 
+similar recall rates, illustrating how a geometric algorithm can be 
+complemented by a reliable non-geometric pruning of matches.
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=1\textwidth]{images/result_spectral-mmc}
+	\caption{Results for filtering matches with \emph{MMC} before 
+	applying the \emph{Spectral} algorithm.}
+	\label{fig:result_spectral-mmc}
 \end{figure}
@@
 \begin{figure}[htb]
-	\makebox[\textwidth][c]{%
-		\begin{subfigure}[t]{.2\textwidth}
+	\begin{subfigure}[c]{.2\textwidth}
 		\centering
@@
 	%(or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{.8\textwidth}
+	\begin{subfigure}[c]{.8\textwidth}
 	\centering
-   		\includegraphics[width=0.6\columnwidth]{images/result_pitts}
+	\includegraphics[width=1\columnwidth]{images/result_pitts}
 	\end{subfigure}%
-	}%
-	\caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
+	\caption{Results for the image pair in 
+	Figure~\ref{fig:pitts_source}.}
 	\label{fig:result_pitts}

### 2013-08-10 code/display.py
Updated a bunch of simulations

@@ -289,8 +289,67 @@ def accuDetail(correct, total, legend, ylim = 100, treshold=1000) :
     accuHist(accu, legend, ylim=ylim)
 
 
+def comparePlot(correct, 
+                compareCorrect, 
+                total, 
+                compareTotal,
+                legends, 
+                compareLegends,
+                colors  = ["blue", "red", "green", "maroon", "cyan"], 
+                ylim=(0.0, 1.01), 
+                xlim = (0.01, 0.5),
+                size = (4,6), 
+                nb_correspondences = None, 
+                outside = False, 
+                output = None) :
+    """ Plot that show curves but compares with a different line in dots """
 
-def accuPlot(correct, total, legends, colors = ["blue", "red", "green", "orange", "cyan"], ylim=(0.0, 1.01), xlim = None, size = (4,6), nb_correspondences = None, compareCorrect = None, compareTotal = None, compareLegend = None, outside = False, output = None) :
+    fig = pylab.figure(figsize=size)
+    ax = pylab.subplot(111)
+    if nb_correspondences == None :
+        nb_correspondences = [1 for ts in total]
+
+    for i in range(0,len(total)) :
+        ts, ts_i = total[i], compareTotal[i]
+        cs, cs_i = correct[i], compareCorrect[i]
+        l, l_i = legends[i], compareLegends[i]
+        color = colors[i]
+        nb_corr = nb_correspondences[i]
+        xs = [sum(c)/float(nb_corr) for c in cs]
+        ys = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for (c, t) in zip(cs, ts)]
+        xs_i = [sum(c)/float(nb_corr) for c in cs_i]
+        ys_i = [1 if sum(t) == 0 else sum(c)/float(sum(t)) for (c, t) in zip(cs_i, ts_i)]
+        pylab.plot(xs, ys, '-', label=l, color=color, alpha=0.95)
+        pylab.plot(xs_i, ys_i, '--', label="%s" % (l_i), color=color, alpha=1)
+
+    # Remove superflous lines and add axis labels
+    removeDecoration()
+    if nb_correspondences != None :
+        pylab.xlabel("Recall")
+    else :
+        pylab.xlabel("# of Matches")
+    pylab.ylabel("Precision")
+    pylab.ylim(ylim[0],ylim[1])
+
+    # Put legend outside of plot
+    pylab.legend(loc="best")
+    if outside == True :
[…]

### 2013-08-10 code/isomatch.py

@@ -41,6 +41,7 @@ def match(paths, options = {}) :
     verbose				= options.get("verbose", False)
     keypoint_type		= options.get("keypoint_type", "SIFT")
     descriptor_type		= options.get("descriptor_type", "SIFT")
+    ratio_threshold		= options.get("ratio_threshold", 1.0)
 
     # Get images
     images = map(features.loadImage, paths)
@@ -61,7 +62,7 @@ def match(paths, options = {}) :
     part_2 = isodata.cluster(positions[indices==1], k_init=k_init, max_iterations=max_iterations, min_partition_size=min_partition_size, max_sd=max_sd, min_distance=min_distance)
 
     # Show the clusters
-    if verbose : showPartitions(part_1, part_2, indices, images, positions)
+    if verbose : display.showTwoPartitions(part_1, part_2, indices, images, positions)
 
     # Get a matrix of the matches so that part_corr_{i,j} is equal to the
     # amount of matches between partition i and j
@@ -76,6 +77,20 @@ def match(paths, options = {}) :
         for (j,s) in ms :
             match_set.extend(getPartitionMatches(match_points, part_1 == i, part_2 == j))
     
+    # def match_fun(threshold) :
+    #     # For each partition figure out which partitions correspond
+    #     partition_links = [getPartitionLinks(row, threshold) for row in part_corr]
+
+    #     # Get all keypoint matches from the matching clusters
+    #     match_set = []
+    #     for i, ms in enumerate(partition_links) :
+    #         for (j, s) in ms :
+    #             match_set.extend(getPartitionMatches(match_points, part_1 == i, part_2 == j))
+    #     match_data = [(matchFromIndex(i, j), u, 0) for((i,j),u) in match_set if u < ratio_threshold]
+    #     if len(match_data) == 0 : return [], [], []
+    #     matches, ratios, scores = zip(*match_data)
+    #     return matches, ratios, scores
+
     # Define a function that given a threshold returns a set of matches
     def match_fun(threshold) :
         match_data = [(matchFromIndex(i,j), u, 0) for ((i,j),u) in match_set if u < threshold]
@@ -132,15 +147,6 @@ def getLinkMat(part_1, part_2, match_points) :
     return part_corr
 
 
-def showPartitions(part_1, part_2, indices, images, positions) :
-    pylab.figure(frameon=False, figsize=(14,5))
[…]

### 2013-08-10 code/spectralmatch.py

@@ -35,7 +35,7 @@ def match(paths, options ={}) :
     affinity_fun = options.get("affinity", affinity_simple)
     matching_fun = options.get("match_fun", ratiomatch.getMatchSet)
     sigma = options.get("affinity", 50)
-    keep_ratio = options.get("keep_ratio", 0.75)
+    keep_ratio = options.get("keep_ratio", 0.5)
     verbose = options.get("verbose", False)
 
     matches, ratios, scores = matching_fun(paths, options)
@@ -68,6 +68,7 @@ def match(paths, options ={}) :
 
     def match_fun(threshold) :
         """ Given a threshold we return a list of matches """
+
         match_data = [(pos, u, s) for (pos, u, s) 
                 in zip(best_m, best_ratios, best_scores) if u < threshold]
 

### 2013-08-10 text/main/ch2_background.tex
Updated thesis with spectral-mmc info and better figures
Added computer vision background

@@
-\chapter{Background}
+\chapter{Matching local image features}
+
+In this chapter we will introduce local feature points in images and 
+explain how they are used. We will start out by discussing why we need 
+local features in the first place before looking at the inner workings 
+of modern local image features. Finally we will look at how they are 
+used, in particular how corresponding pairs are found in between two or 
+more images.
+
+\section{A brief look at computer vision}
+
+The field of computer vision is anecdotally said to have been founded 
+when Marvin Minsky assigned the problem of making a computer see as an 
+undergraduate summer project back in 1966\footnote{This is the same 
+Marvin who invented neural networks and went on to serve as scientific 
+adviser on Kubrick's movie \emph{Space Odyssey 2001}}. Whether or not 
+the anecdote is true, the idea that the field of computer vision should 
+be solvable in a summer's worth of time but still to this days remains 
+an active field of research, illustrates an interesting notion: Making 
+computers solve tasks involving seeing turns out to be much harder than 
+we would initially assume.
+
+Part of this notion stems from the fact that vision is a problem that we 
+as humans are very good at. We can easily recognize objects under 
+different light, or stitch together photographies to a panorama, or 
+navigate a corridor identifying obstacles along the way. In fact these 
+things are so easy to us, that it seems strange that they should be 
+difficult at all, yet consistently recognizing an object under different 
+lighting conditions and from different angles can still cause problems 
+for even the best object recognition algorithms.
+
+The main difficulty lies in how the world we see around us constantly 
+varies. Try for a moment to imagine that you enter a room and recognize 
+the newspaper that is lying on the table, illuminated from the grey 
+light coming in of the window on the opposing wall. You move across the 
+room and switch on the light make out if the paper is from today, and 
+then you sit down and put on your glasses to read the headline. Try to 
+imagine the newspaper as you see it on three different stages. First as 
+you enter the room, then as you turn after turning on the light, now 
+standing on the other side of the table, and last when you are sitting 
+with the paper in your hand after you put on your glasses. For each of 
+these stages, picture the situation as a photography and look at how the 
+newspaper changes as you move around. At first you see it at an angle 
+lying in a fairly dark and grey room, the white pages reflecting the 
+light from the window with a cold bluish hue and the words too far away 
+to make out. Then in the second stage with light on, the object you are 
+looking at has suddenly changed. When you turned on the light in the 
+room, you also changed the color of the newspaper, which now has a warm 
+and yellowy white color. The angle you are looking at the paper from has 
+changed too, and the words and pictures are no longer upside down, 
+although still slightly rotated and with the increased light in the room 
+the contrast of the words and pictures of the page makes it possible for 
+you to make recognize that the newspaper is from today. Finally as you 
+sit down and put your glasses on the newspaper changes again. The color 
+might be the same, but if you imagine taking a photography as you are 
+sitting with the paper in your hand, the newspaper will look much bigger 
+almost taking up the entire frame. Now that your glasses are on, the 
+words stand out much clearer and you can see what is in the pictures on 
+the front page.
+
+Intuitively you know that the paper you sat down to read is the same 
+object as the paper you saw when you entered the room, but if we limit 
+ourselves to only looking at the object itself, almost everything about 
+it changed in the process, from the color of the pages to the sharpness 
+of the lines. On top of that the paper has changed in size and rotation 
+from lying on the table to being in your hand. In our daily lives we are 
+aided in the process of recognizing the paper by our memory and idea of 
+how the world works. When we walked in to the dark room and saw 
+something on the table, it was probably safe to assume that it was a 
+newspaper. Maybe the newspaper always lies like that on the table, or 
+maybe we left it there ourselves. Afterwards as we move around in the 
+room, we can safely assume that the paper didn't move and even if it 
+might not look exactly the same after we turned on the light, it's safe 
+to guess that nobody took the old newspaper and replaced it with a new 
+and yellower version.
+
+On the other hand a computer algorithm trying to recognize objects will 
+not be able to make the same assumptions about the world. We might just 
+give as input to the program to pictures of the newspaper. One from the 
+first stage where the light was turned off, the paper was far away and 
+the lens wasn't focused correctly, and one from the third stage with the 
+light on, the image in focus and the paper taking up the entire photo.  
+Now we ask the algorithm: "Is this the same newspaper?". In this case it 
+is fair to ask how the algorithm can reliably make this judgement.
+
+\section{Introducing local features}
 

### 2013-08-10 text/main/ch5_experiments.tex
Added computer vision background

@@
 	plot shows the result of 100 patch pairs generated from the source 
-images shown to the left. The number of matches is the total number of 
-matches for all 100 patch pairs.}
+	images shown to the left. The x-axis shows the recall based on the 
+accumulated amount of potential matches for all 100 patch pairs. }
 	\label{fig:result_graf}
@@
 	\emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} 
-	set.  The x-axis shows the accumulated returned matches for all 
-pairs.}
+	set.  The x-axis shows the recall based on the accumulated amount of 
+potential matches for all patch pairs.}
 	\label{fig:result_accumulated}
@@
 complemented by a reliable non-geometric pruning of matches.
+
 \begin{figure}[htb]
@@
 	\caption{Results for filtering matches with \emph{MMC} before 
-	applying the \emph{Spectral} algorithm.}
+	applying the \emph{Spectral} algorithm. The algorithm is tested on 
+900 patch pairs extracted from the \emph{Murals} dataset and the image 
+pair 1\&3 from the \emph{Graf} set. The x-axis shows the recall based on 
+the accumulated amount of potential matches for all patch pairs.}
 	\label{fig:result_spectral-mmc}
@@
 	\end{subfigure}%
-	\caption{Results for the image pair in 
+	\caption{Results for 100 patch pairs based on the image pair in 
 	Figure~\ref{fig:pitts_source}.}

### 2013-08-10 text/main/ch2_background.tex
Added info on descriptors

@@
 
-Introduction to Computer Vision
- - Introduce common tasks that we are good at that computers aren't
- - Single in on tasks that we can solve using feature points
+The example of the newspaper focuses on a particular branch of computer 
+vision; object recognition, but the exact same problem remains for most 
+of the various subfields. In automatic panorama stitching where we try 
+to create a panorama from a set of images, we need to recognize which 
+images fit together even if they are taken with different camera 
+settings. In near duplicate detection where we try to find images that 
+appear to be duplicates of other images we need to recognize if the same 
+scene appears from slightly different angles under slightly different 
+light. In scene matching where we try to find out if two images are 
+taken of the same scene the two images could be taken on different days 
+under different conditions. The list continues and it should hopefully 
+be clear that in order to solve a lot of problems in computer vision, we 
+need a way to deal with these variations.
 
-Introduction to feature points
- - Global explanation of what they are and how they serve to solve the 
-problems mentioned before
- - How do we find them? (Examples making it intuitive why corners are 
-nice)
- - How do we describe them? (Relate invariance: Light, Rotation, Noise, 
- Scale, \ldots, Affine)
- - Introduce SIFT and explain how the different problems are tackled in 
-SIFT)
- - Talk about other methods and how they are different
+One particularly successful approach over recent years has been to use 
+\emph{local image features}. As opposed to global image features like 
+the image histogram or the position of edges, local features are each 
+constrained to a small point-like area in the image. The idea behind 
+local features is that we pick distinct points in the image and describe 
+the local neighborhood in a way that remains stable even if the image is 
+taken under different light or from slightly different angles. Then 
+given two images we can find some local feature points of each and see 
+if any correspond across images.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=1\columnwidth]{images/feature_point}
+	\caption{Example of feature point location. In the image, feature a) 
+is ambiguous because it can match any location along the left edge of 
+the building, while feature b) is distinct because only one left corner 
+of that building exists. The background image is originally from the 
+Gallagher dataset \cite{gallagher2008}}
+	\label{fig:feature_point}
+\end{figure}
+
+For this two work we need two components. First we need to find spots in 
+an image that are distinct, since if we have similar points we can't 
+uniquely match them. Secondly we need to take information around the 
+local area of the point and describe it in a way that is invariant to 
+changes like illumination and geometric distortion as well as noise, 
+blur and scale. Finding unique points in the image is called 
+\emph{feature detection} and it yields a \emph{key point}, where as we 
+describe the key point with a \emph{feature descriptor}. The key point 
+will contain the position of the point in the image while the descriptor 
+will contain information about the image data surrounding that position.
+
+\subsection{Finding Feature Points}
+
+As Figure~\ref{fig:feature_point} illustrates, an easy heuristic for 
+finding a unique point in an image is to find corners. A point lying on 
+a smooth part of the image would look identical to the surrounding 
+points, and points along an edge will look the same as other points 
+along the same edge. While corners aren't necessarily a sufficient 
+condition for finding a good feature point, they provide a good starting 
+point. Intuitively the simplest way to find corners would be to detect 
+edges in the image (for example using a high pass filter), and follow 
+these edges until they turn. Some of these approaches are detailed in 
+\cite{university1978comparison}.
+
+A different (and it turns out, better) approach is to look at the 
+gradient across the image and find spots where there is a gradient in 
+two perpendicular directions.  That is, along a dark edge on a bright 
+background there will be a gradient perpendicular to the edge, but no 
+gradient along the edge.  However in a corner we would have a gradient 
+in two different directions. The idea was originally introduced by 
+Morevec \cite{hans1977towards} and later improved upon by Harris and 
+Stephens who introduced what is now commonly known as the Harris corner 
+detector \cite{harris1988combined}.
+
+Alternatively a fast way of deciding if a point is a corner is to look 
+at all pixels surrounding the point of interest and compute the fraction 
+of pixels that have higher intensities than the center\footnote{i.e.\ 
+are brighter}. We can then find corners by thresholding on this 
+intensity difference as proposed by Smith and Brady 
+\cite{smith1997susan} as the SUSAN edge detector. Lepetit and Fua 
+proposed a similar algorithm but only looking at the pixels on the 
+circumference of a circle surrounding the point 
+\cite{lepetit2006keypoint}. This is also the central idea behind the 
+FAST detector by Rosten and Drummond \cite{rosten2006machine}.
+
+For a thorough review of the history of feature detectors, Tuytelaars 
+and Mikolajczyk presents an excellent historical retrospect in 
+\cite{tuytelaars2008local}.
+
+\subsection{Describing Feature Points}
+
+Once we have found a point of interest, we need to describe it. The 
+simplest way is to save the values of the pixels in the immediate 
+neighborhood, but this would not be very flexible. Take the case where 
+we take two images of the same scene, but overexpose one of them. Two 
+corresponding feature points would not look remotely alike in this case.
+In the feature descriptor of bright photography all the pixel values 
+would be high, while the values in the descriptor of the darker image 
+would all be low. A similar situation arise if one image is rotated or 
+there is a change in perspective.
+
+A way to work around these issues is to compile a histogram of the 
+pixels surrounding the key point. This way we would get the same 
+descriptor now matter how the image is rotated. To a certain extend this
+method is also invariant to affine transformations, that is change in 
+perspective as long as approximately the same pixels fall within the 
+zone we are taking a histogram of. If we use the raw values of the 
+pixels, the descriptor is still not invariant with respect to 
+brightness, but this is easily solved by creating a histogram of the 
+pixel values relative to the center pixel. Lazebnik et al.\ introduced 
+this method in \cite{lazebnik2003sparse} adding the distance from the 
+key point as another dimension in the histogram.
+
+Instead of using the pixel values, we can create a histogram of the 
+gradients surrounding the feature point as Lowe did in his Scale 
+Invariant Feature Detector (SIFT) \cite{lowe2004sift}. The histogram he 
+proposes is based on the gradient locations and orientations weighted by
+the gradient magnitude. To make sure that the histogram is rotation 
+invariant, the bins of the histogram are normalized and start with the 
+bin of the highest magnitude. The SIFT descriptor has been very widely 
+used since it's introduction and has become a de facto standard in 
+computer vision. To enhance the computational time needed to compute 
+descriptors, Bay et al.\ introduced the Speeded Up Robust Features 
+(SURF) that rely on a histogram of wavelets instead of gradients as used 
+in SIFT \cite{bay2006surf}.
+
+A radically different approach to a feature descriptor is to measure the
+intensity difference between a number of pixels surrounding the key 
+point and simply assign the bits to a vector that is returned as the 
+feature descriptor. Calonder et al.\ \cite{calonder2010brief} introduced 
+a feature descriptor, Binary Robust Independent Elementary Features 
+(BRIEF), based on this idea. The main advantage of their approach is 
+reduced processing and memory needed to create, store and match the 
+feature descriptors. Interestingly the positions used for pixel wise 
+comparisons were selected at random and tested against similar random 
+configurations using the configuration yielding the best result. The 
+simplicity of this method allows for real time matching of objects from 
+a video stream, something that would be too computationally tolling when 
+using a descriptor like SIFT\@. BRIEF however fails to be rotation 
+invariant making it less useful in cases where images are not 
+necessarily upright.
+
+\section{Finding the perfect match}
 

### 2013-08-10 text/main/ch2_background.tex
Added matching section to background

@@
-\chapter{Matching local image features}
+\chapter{Matching Local Image Features}
 
@@
 
-\section{A brief look at computer vision}
+\section{A Brief Look at Computer Vision}
 
@@
 
-The main difficulty lies in how the world we see around us constantly 
-varies. Try for a moment to imagine that you enter a room and recognize 
-the newspaper that is lying on the table, illuminated from the grey 
-light coming in of the window on the opposing wall. You move across the 
-room and switch on the light make out if the paper is from today, and 
-then you sit down and put on your glasses to read the headline. Try to 
-imagine the newspaper as you see it on three different stages. First as 
-you enter the room, then as you turn after turning on the light, now 
-standing on the other side of the table, and last when you are sitting 
-with the paper in your hand after you put on your glasses. For each of 
-these stages, picture the situation as a photography and look at how the 
-newspaper changes as you move around. At first you see it at an angle 
-lying in a fairly dark and grey room, the white pages reflecting the 
-light from the window with a cold bluish hue and the words too far away 
-to make out. Then in the second stage with light on, the object you are 
-looking at has suddenly changed. When you turned on the light in the 
-room, you also changed the color of the newspaper, which now has a warm 
-and yellowy white color. The angle you are looking at the paper from has 
-changed too, and the words and pictures are no longer upside down, 
-although still slightly rotated and with the increased light in the room 
-the contrast of the words and pictures of the page makes it possible for 
-you to make recognize that the newspaper is from today. Finally as you 
-sit down and put your glasses on the newspaper changes again. The color 
-might be the same, but if you imagine taking a photography as you are 
-sitting with the paper in your hand, the newspaper will look much bigger 
-almost taking up the entire frame. Now that your glasses are on, the 
-words stand out much clearer and you can see what is in the pictures on 
-the front page.
+\subsection{A Thought Experiment}
+
+The main factor that makes computer vision difficult is how the world we 
+see around us constantly varies. This is not something that is 
+immediately obvious to the casual observer, so for the sake of clarity 
+let us do a small thought experiment. Try for a moment to imagine that 
+you enter a room and recognize the newspaper that is lying on the table, 
+illuminated from the grey light coming in of the window on the opposing 
+wall. You move across the room and switch on the light make out if the 
+paper is from today, and then you sit down and put on your glasses to 
+read the headline. Try to imagine the newspaper as you see it on three 
+different stages. First as you enter the room, then as you turn after 
+turning on the light, now standing on the other side of the table, and 
+last when you are sitting with the paper in your hand after you put on 
+your glasses. For each of these stages, picture the situation as a 
+photography and look at how the newspaper changes as you move around. At 
+first you see it at an angle lying in a fairly dark and grey room, the 
+white pages reflecting the light from the window with a cold bluish hue 
+and the words too far away to make out. Then in the second stage with 
+light on, the object you are looking at has suddenly changed. When you 
+turned on the light in the room, you also changed the color of the 
+newspaper, which now has a warm and yellowy white color.  The angle you 
+are looking at the paper from has changed too, and the words and 
+pictures are no longer upside down, although still slightly rotated and 
+with the increased light in the room the contrast of the words and 
+pictures of the page makes it possible for you to make recognize that 
+the newspaper is from today. Finally as you sit down and put your 
+glasses on the newspaper changes again. The color might be the same, but 
+if you imagine taking a photography as you are sitting with the paper in 
+your hand, the newspaper will look much bigger almost taking up the 
+entire frame. Now that your glasses are on, the words stand out much 
+clearer and you can see what is in the pictures on the front page.
 
@@
 
-\section{Introducing local features}
+\section{Introducing Local Features}
 
@@
 
-\section{Finding the perfect match}
+\section{Finding the Perfect Match}
 
-Matching feature points
- - What applications require matching?
- - How is matching usually done
- - Segue into related work from paper
+Most applications of feature points use them to match features across 
+different images. The standard out of the box way most feature points 
+are matched involve comparing the feature descriptor using some kind of 
+distance measure. If we match all features of one image with all 
+features of another and discard all matches that are below a certain 
+threshold of similarity, we have in essence a set of matches between the
+two images. For most feature points (for example SIFT and SURF), this 
+similarity is measured by the cosine similarity. Binary descriptors such
+as BRIEF can take advantage of the faster computation of the hamming 
+distance.
+
+\subsection{Geometric Constraints}
+
+While the standard matching method is often computationally efficient, 
+it isn't necessarily the best way to match feature points. Many matching 
+methods make use of the knowledge of the position of the keypoints in 
+the image, i.e.\ the geometrical meta data. Using this information can 
+often yield more accurate outcomes, but they inevitably make assumptions
+about the geometric relationship between the images that are being 
+matched which might not hold true.
+
+A simple example would be to only consider matches that aren't deviating 
+too much with respect to the average angle and distancen as considered 
+by \cite{kim2008efficient}.  This performs well in situations where no 
+camera rotation occurs between the two images, but fails when this 
+assumption isn't met. Various scenarios have been proposed to improve on 
+this simple assumption such as epipolar constraints 
+(\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
+constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}). The 
+Epipolar constraint carries the assumption that the two images matched 
+are related by an affine transformation. That is, that there is no 
+relative movement of objects in between images and either the viewpoint 
+is fixed or the image resides entirely on a plane. In practice this 
+assumption largely holds true when all objects we are interested in 
+matching are roughly the same distance from the camera given that 
+objects don't move across images.  Pairwise constraints provide a more 
+robust approach to the same problem by looking at a set of proposed 
+correspondences and defining a pairwise error between any two matches 
+for example based on the assumption that two neighboring correspondences 
+will usually have similar angles and distances. We can then convert the 
+problem to an optimization problem and return a set of correspondences 
+that minimizes this error such as proposed in \cite{choi2009robust} and 
+\cite{leordeanu2005spectral}.  This approach provides more robustness in 
+cases where assumptions that are violated globally still hold on a local 
+scale.
+
+An alternative is to pick out different areas in each image and pair 
+areas when correspondence pairs are mainly found going from one area to 
+another. This allows for the filtering of all correspondences that do 
+not fall within paired areas. Examples include \emph{Isodata} 
+\cite{das2008event}, which clusters feature points according to their 
+position in the image, and the method from \cite{wu2011robust}, which 
+uses maximally stable extremal regions (MSER) feature points to 
+designate areas.
+
+\subsection{Matching Without Assumptions}
+
+In practice there are many situations where relying on the geometry of 
+the image to filter correspondences is not possible, for example images 
+without overlap, or adjacent objects in one image are that are separated 
+in another. Furthermore, methods using geometric constraints all require 
+an initial set of correspondences. If this set of correspondences can be 
+narrowed down to the most probable correct matches, the geometric 
+matching algorithm will benefit in terms of speed and accuracy.  Finally 
+some use cases might require a speed that simply cannot be achieved by 
+complex geometric methods.
+
+In the absence of geometric constraints, only few methods are available.  
+As pointed out in \cite{szeliski2010} and mentioned above, the simplest 
+approach to matching feature points is to return all matches above a 
+given threshold of similarity.  This can be done with a fixed threshold 
+or by finding the nearest neighbors for each point (still filtering by a 
+threshold to avoid including matches for feature points that have no 
+counterpart in the other image).  When Lowe \cite{lowe2004sift} proposed 
+the scale-invariant feature transform he included an alternative 
+matching measure. Instead of rating matching by similarity assessed the 
+uniqueness of a given match by looking at the two nearest neighbors of 
+each feature point and calculating the matching score as the ratio of 
+similarities. This method will later be referred to as \emph{Ratio}.  
+Ranking the scores by their uniqueness and picking the $n$ best produces 
+a set of correspondences that are distinctly matched across two images.  
+Of these three methods (fixed threshold, nearest neighbors, and 
+\emph{RATIO}), \emph{RATIO} was found to perform best by a slight margin 
+\cite{mikolajczyk2005performance}.
+
+%Matching feature points
+% - What applications require matching?
+% - How is matching usually done
+% - Segue into related work from paper

### 2013-08-11 text/main/ch1_introduction.tex
Wrote introduction

\addcontentsline{toc}{chapter}{Introduction}
\chapter*{Introduction}
Matching feature points is one of the problems in computer vision that 
if solved well will provide a useful tool for improving methods on a 
host of interesting problems. If we can match feature points reliably we 
can recognize objects, make panoramas, recognize duplicate photos, guide 
robots and airplanes and a host of other interesting applications 
\footnote{For a few examples of some of these applications, check out: 
\cite{se2002global} (robot guidance), \cite{brown2007automatic} 
(panorama construction), \cite{lowe2004sift} (has parts on object 
recognition), \cite{chu2010consumer} (duplicate detection)}.  For all 
these problems better feature point matching will most likely yield 
better solutions.

My goal when I started working on this thesis was not to improve feature 
point matching, but via a series of detours I ended up circling the 
problem which attracted me, not just because it its importance, but also 
because of its inherent simplicity. Out of two sets, finding pairs of 
similar elements seems like a problem that should have been solved long 
ago, yet because of the nature of feature points and the data they are 
used on, there seems to be plenty of progress to be made.

As the outcome of my work  I propose two algorithms, \emph{Mirror Match 
(MM)} and \emph{Mirror Match with Clustering (MMC)}, both designed to 
improve feature point matching. The goal of this thesis will be to 
introduce these algorithms and convincingly demonstrate that they are 
useful. While doing this I hope to provide sufficient background for a 
technically minded reader without any necessary background in computer 
vision to follow the motivation behind \emph{MM} and \emph{MMC} as well 
as the place of both algorithms in a bigger scientific perspective.

The thesis is organized as follows: Chapter~\ref{C:background} provides 
background and motivation for the development of \emph{MM} and 
\emph{MMC}. The chapter serves two purposes.  For those that might be 
reading this introduction wondering what a feature point really is and 
how it is matched, it provides a gentle introduction to the why's and 
how's of feature point matching. At the same time the chapter is meant 
as an introduction to related work which is hopefully useful for those 
who might use this thesis as a starting point for finding other research 
on the same subject. Chapter~\ref{C:algorithms} will introduce in detail 
the algorithms proposed in this thesis. The reference algorithms used to 
benchmark \emph{MM} and \emph{MMC} are also introduced in detail.  
Chapter~\ref{C:experiments} details the experiments done to evaluate the 
proposed algorithms both in terms of how they were conducted as well as 
their results. Chapter~\ref{C:applications} provides two examples of how 
the matching algorithms can improve on panorama stitching and near 
duplicate matching.

For the remainder of the thesis I will make use of the academic 
'\emph{we}' to underline the fact that I cannot take credit for this 
work alone.  This thesis had not been possible had it not been for the 
guidance of Stefan Winkler and Sabine S\"usstrunk as well as the support 
of Advanced Digital Science Center in Singapore that hosted me as an 
intern for the duration of my thesis work.

### 2013-08-11 text/main/ch2_background.tex
Wrote introduction

@@
 \chapter{Matching Local Image Features}
+\label{C:background}
 
@@
 
-\subsection{A Thought Experiment}
+\subsection{An Ever Changing Constant World}
 
@@
 (\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
-constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral}). The 
-Epipolar constraint carries the assumption that the two images matched 
-are related by an affine transformation. That is, that there is no 
-relative movement of objects in between images and either the viewpoint 
-is fixed or the image resides entirely on a plane. In practice this 
-assumption largely holds true when all objects we are interested in 
-matching are roughly the same distance from the camera given that 
-objects don't move across images.  Pairwise constraints provide a more 
-robust approach to the same problem by looking at a set of proposed 
-correspondences and defining a pairwise error between any two matches 
-for example based on the assumption that two neighboring correspondences 
-will usually have similar angles and distances. We can then convert the 
-problem to an optimization problem and return a set of correspondences 
-that minimizes this error such as proposed in \cite{choi2009robust} and 
-\cite{leordeanu2005spectral}.  This approach provides more robustness in 
-cases where assumptions that are violated globally still hold on a local 
-scale.
+constraints (\cite{choi2009robust}, \cite{leordeanu2005spectral} --- 
+later referred to as \emph{Spectral}).  The Epipolar constraint carries 
+the assumption that the two images matched are related by an affine 
+transformation.  That is, that there is no relative movement of objects 
+in between images and either the viewpoint is fixed or the image resides 
+entirely on a plane.  In practice this assumption largely holds true 
+when all objects we are interested in matching are roughly the same 
+distance from the camera given that objects don't move across images.  
+Pairwise constraints provide a more robust approach to the same problem 
+by looking at a set of proposed correspondences and defining a pairwise 
+error between any two matches for example based on the assumption that 
+two neighboring correspondences will usually have similar angles and 
+distances. This approach provides more robustness in cases where 
+assumptions that are violated globally still hold on a local scale.
 
@@
 without overlap, or adjacent objects in one image are that are separated 
-in another. Furthermore, methods using geometric constraints all require 
-an initial set of correspondences. If this set of correspondences can be 
-narrowed down to the most probable correct matches, the geometric 
-matching algorithm will benefit in terms of speed and accuracy.  Finally 
-some use cases might require a speed that simply cannot be achieved by 
-complex geometric methods.
+in another. In these cases the assumptions behind the geometric 
+algorithms will often cause them to return incorrect matches.
+
+In addition methods using geometric constraints all require an initial 
+set of correspondences. If this set of correspondences can be narrowed 
+down to the most probable correct matches, the geometric matching 
+algorithm will benefit in terms of speed and accuracy.  Finally some use 
+cases might require a speed that simply cannot be achieved by complex 
+geometric methods.
 
@@
 
-%Matching feature points
-% - What applications require matching?
-% - How is matching usually done
-% - Segue into related work from paper
+The two methods we propose in this paper are inspired by a simple but 
+novel idea. If a given feature point in one image is better matched with 
+other feature points from the \emph{same} image than points in the other 
+image, then any matches from this feature point to points in the other 
+image are considered unreliable and should be discarded.  This approach 
+carries no implicit assumptions about the geometric consistency of 
+matches and as such can easily be extended with other geometric 
+solutions when appropriate or necessary.
+
+Based on this idea,  we determine reliable matches as follows. 
+\emph{Mirror Match (MM)} matches every feature from both images with all 
+other features and filters matches based on the ratio of best to second 
+best match as in \emph{SIFT}. \emph{Mirror Match with Clustering (MMC)} 
+on the other hand takes the combined set of feature points from both 
+images and clusters these points according to their descriptors.  If a 
+resulting partition contains only feature points from one image, no 
+matches are returned.  If the partition contains points from both 
+images, \emph{Mirror Match} is used to find the best matches within this 
+partition.  The experimental results show that both approaches generally 
+outperform existing correspondence matching methods.

### 2013-08-11 text/main/ch1_introduction.tex
Added some introduction to matching methods

@@
 For the remainder of the thesis I will make use of the academic 
-'\emph{we}' to underline the fact that I cannot take credit for this 
-work alone.  This thesis had not been possible had it not been for the 
-guidance of Stefan Winkler and Sabine S\"usstrunk as well as the support 
-of Advanced Digital Science Center in Singapore that hosted me as an 
-intern for the duration of my thesis work.
+'\emph{we}' to underline the fact this thesis had not been possible had 
+it not been for the guidance of Stefan Winkler and Sabine S\"usstrunk as 
+well as the support of Advanced Digital Science Center in Singapore that 
+hosted me as an intern for the duration of my thesis work.

### 2013-08-11 text/main/ch3_matching_methods.tex
Updated thesis with spectral-mmc info and better figures
Added some introduction to matching methods

@@
-\chapter{Matching Methods}
-Basically c/p from paper, but better figures and maybe more explanations
- - Add path about graphs and how they are formed. Make sure to explain 
- the clustering in more detail and make it easier to understand
- - Add a good explanation for new figures and how the precision and 
- recall are calculated. This should appear somewhere before results.
- - Add part on spectral matching and modify accordingly. Make sure to 
- underline how the second plot shows how the geometric method is 
- independent of MMC and that they combined yield greater results.
+\chapter{Algorithms}
+\label{C:algorithms}
 
-\subsection{Proposed Matching Methods}
+In this chapter we will describe the algorithms used in the experiements
+in detail. We start with the proposed algorithms \emph{MM} and 
+\emph{MMC}, and continue with the algorithms used for comparison, 
+\emph{Ratio}, \emph{Spectral} and \emph{Isomatch}.
+
+\section{Proposed Matching Methods}
 \label{S:MatchingMethods}
 
-\subsubsection{Mirror Match (\emph{MM})}
+\subsection{Mirror Match (\emph{MM})}
 
-\begin{figure}
+\begin{figure}[h]
 	\centering%
-		\begin{subfigure}[t]{\columnwidth}
+		\begin{subfigure}[t]{0.5\columnwidth}
 			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_source}
+			\includegraphics[width=0.95\columnwidth]{images/MMC_pitts_source}
 			\caption{Source image pair}
@@
 		\end{subfigure}%
-		\\ %
-		\begin{subfigure}[t]{\columnwidth}
+		~ %
+		\begin{subfigure}[t]{0.5\columnwidth}
 			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_pitts_keypoints}
+			\includegraphics[width=0.95\columnwidth]{images/MMC_pitts_keypoints}
 			\caption{Feature points}
@@
 		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
+		\begin{subfigure}[t]{0.5\columnwidth}
 			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
+			\includegraphics[width=0.95\columnwidth]{images/mirror_match_off}
 			\caption{\emph{Ratio}}
@@
 		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
+		~ %add desired spacing between images, e. g. ~, \quad, 
+		\begin{subfigure}[t]{0.5\columnwidth}
 			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match_with_pruned}
+			\includegraphics[width=0.95\columnwidth]{images/mirror_match_with_pruned}
 			\caption{\emph{MM} intermediate result}
@@
 		%\qquad (or a blank line to force the subfigure onto a new line)
-		\begin{subfigure}[t]{\columnwidth}
+		\begin{subfigure}[t]{0.5\columnwidth}
 			\centering
-			\includegraphics[width=0.85\columnwidth]{images/mirror_match}
+			\includegraphics[width=0.95\columnwidth]{images/mirror_match}
 			\caption{\emph{MM} final result}
@@
 		\end{subfigure}%
-		\\ %add desired spacing between images, e. g. ~, \quad, 
-		\begin{subfigure}[t]{\columnwidth}
+		~ %add desired spacing between images, e. g. ~, \quad, 
+		\begin{subfigure}[t]{0.5\columnwidth}
 			\centering
-			\includegraphics[width=0.85\columnwidth]{images/MMC_partition}
+			\includegraphics[width=0.95\columnwidth]{images/MMC_partition}
 			\caption{\emph{MMC} Partition Example}
@@
 
-%
 The central idea behind \emph{MM} is to match features of $n$ images by 
@@
 other feature from the same set. We can then discard the correspondences 
-that match two points within the same image. Algorithm~\ref{alg-mm} details  
-the implementation of \emph{MM}.
-%
-\begin{algorithm}
+that match two points within the same image. Algorithm~\ref{alg-mm} 
+details the implementation of \emph{MM}.
+
+\begin{algorithm}[htb]
 \caption{Mirror Match (\emph{MM})}
@@
 \end{algorithm}
-%
+
 In the acquisition stage we gather all features in the set of images.  
@@
 
-\subsubsection{Mirror Match with Clustering (\emph{MMC})}
-%
+\subsection{Mirror Match with Clustering (\emph{MMC})}
+
 In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
@@
 
-Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-points in an image and returns their matching score, we can define a 
-matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-as the \emph{adjecency matrix} of the fully connected graph where each 
-vertex corresponds to a keypoint and the edge between two vertices has a 
-weight equal to the distance between the two corresponding keypoints.
+To cluster the feature points, we construct a graph with the feature 
+points as nodes and their similarity score as edge weights. Given a 
+matching function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two 
+feature points in an image and returns their matching score, we can 
+define a matrix $A$ where each element $A_ij = M(k_i, k_j)$. $A$ can be 
+interpreted as the \emph{adjecency matrix} of the fully connected graph.
 
-This representation reduces the problem of partitioning the keypoints 
-into groups to that of graph clustering or community structure depending 
-on the context. In the literature there are various ways of clustering a 
-graph according to different measures of what constitutes an optimal 
-partitioning. Traditionally the most used clustering algorithms have 
-been K-means and spectral clustering, but in recent years a host of new 
-algorithms have been proposed based on both Newman's concept of graph 
+In the literature there are various ways of clustering a graph according 
+to different measures of what constitutes an optimal partitioning. 
+Traditionally the most used clustering algorithms have been K-means and 
+spectral clustering, but in recent years a host of new algorithms have 
+been proposed based on both Newman's concept of graph 
 modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
@@
 \cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-new algorithms differ from K-means clustering and Spectral clustering 
-in that they do not require the number of expected to clusters to be 
-specified beforehand\footnote{Among the aforementioned methods, this is 
-true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-tests done using randomly generated graphs with a known partitioning 
-\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-markedly better than spectral clustering and 
-K-means\cite{lancichinetti2009}.
+in \cite{ronhovde2009}} just to mention a few. On tests done using 
+randomly generated graphs with a known partitioning \cite{blondel2008}, 
+\cite{rosvall2008} and \cite{ronhovde2009} perform markedly better than 
+spectral clustering and K-means\cite{lancichinetti2009}.
 
-The performance of clustering algorithms is a complicated issue, since 
-an optimal clustering given the same graph can vary depending on the 
-application. Spectral clustering for example will usually return a 
-partitioning where each partition is roughly equal in size\footnote{As 
-mentioned in \cite{von2007}} while the Louvain 
-clustering\cite{blondel2008} might return partitions of very uneven 
-size, even if the modularity measurement has been shown to penalize very 
-small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-depending on the application, but when clustering feature points, 
-maintaining clusters of an even size usually means that some clusters 
-will be '\emph{catch-all}' clusters where the feature points that do 
-not fit anywhere else are grouped together. The necessity of specifying 
-the amount of partitions in for example Spectral clustering or Pott's 
-model clustering further exacerbates the issue since smaller partitions 
-are then combined into one to achieve the right amount of partitions.
-
-%
-\begin{algorithm}
+\begin{algorithm}[htb]
 \caption{Mirror Match with Clustering (\emph{MMC})}
@@
     \centering
-\makebox[\textwidth][c]{%
-    \includegraphics[width=1.1\textwidth]{images/MMC_graph}
+	\includegraphics[width=\textwidth]{images/MMC_graph}
     \label{fig:graph}
-}
 	\caption{The partitioned feature graph. Each vertex represents a 
@@
 the same partition if the graph is very connected.  To ensure that the 
-graph is well clustered, the adjacency matrix is pruned so that only 
-edges above a certain threshold are kept. From empirical analysis, 
+graph is well clustered, the adjacency matrix is pruned by setting all 
+edges below a certain threshold to $0$.  From empirical analysis, 
 retaining the top 2.5\% of edges with the highest similarity seems to 
@@
 clustering the feature points as a graph.
-%
 
@@
 partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
-%
 
-\begin{algorithm}
+\begin{algorithm}[htb]
 \caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
@@
 more than two elements using the \emph{MM} approach.  However, as can be 
-seen in the example in Figure~\ref{fig:MMC_graph}, many of the 
-partitions contain only two feature points from different images linked 
-by one edge. In this case, we compare the similarity of the these two 
-feature points with their second best match and remove matches where 
-this ratio lies above a certain threshold, like in the \emph{Ratio} 
-algorithm.  For example in the case of Figure~\ref{fig:pitts_partition}, 
-we have feature points from a building in one image grouped together 
-with points from a shirt pattern in another.  The nearest neighbor 
-method would have returned wrong matches, but since we match the 
-partition with \emph{MM}, points in the building end up matching other 
-points in the building, and no matches are returned.
+seen in the example in Figure~\ref{fig:graph}, many of the partitions 
+contain only two feature points from different images linked by one 
+edge. In this case, we compare the similarity of the these two feature 
+points with their second best match and remove matches where this ratio 
+lies above a certain threshold, like in the \emph{Ratio} algorithm.  For 
+example in the case of Figure~\ref{fig:pitts_partition}, we have feature 
+points from a building in one image grouped together with points from a 
+shirt pattern in another.  The nearest neighbor method would have 
+returned wrong matches, but since we match the partition with \emph{MM}, 
+points in the building end up matching other points in the building, and 
+no matches are returned.
+
+\section{The Competition}
+
+The algorithms used in the comparison consists of two algorithms that 
+use geometric data to enhance the matching, \emph{Isomatch} 
+\cite{das2008event} and \emph{Spectral} \cite{leordeanu2005spectral} and 
+one non geometric algorithm \emph{Ratio} \cite{lowe2004sift}.  
+\emph{Ratio} is selected because it is a de facto standard for matching 
+feature points, but also because it performs very well as shown by 
+Mikolajczyk and Schmid in \cite{mikolajczyk2005performance}.  
+\emph{Isomatch} and \emph{Spectral} on the other hand are selected 
+because they are examples of two different approaches to geometric 
+matching. \emph{Spectral} uses pairwise optimization to find a set of 
+matches that is consistent in terms of direction and length which makes 
+it less ideal in case of rotation and perspective change. 
+\emph{Isomatch} focuses on matching only between geometric regions found 
+by clustering the keypoints in the image.  This approach makes the 
+algorithm resilient to rotation and perspective change, but will cause 
+problems when the images matched are only partially overlapping and 
+several regions do not have any corresponding regions in the other 
+image.
+
+\subsection{Ratio}
+
+\begin{algorithm}[htb]
+\caption{Ratio Match (\emph{Ratio})}
+\label{alg-ratio}
+%{\fontsize{10}{10}\selectfont
+\begin{algorithmic}
+\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
+\State $matches\gets \varnothing$
+\State $features_1 \gets getFeatures(im_1)$
+\State $features_2 \gets getFeatures(im_2)$
+\ForAll{$f_i \in features_1$}
+    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
+	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
+	\If{$ratio < t$}
+        \State $matches \gets \left(f_i, f_m\right)$
+	\EndIf
+\EndFor
+\Return $matches$
+\end{algorithmic}
+%}
+\end{algorithm}
+
+\emph{Ratio} (Algorithm~\ref{alg-ratio}) \cite{lowe2004sift} is the most 
+straightforward of the three reference algorithms. Feature points are 
+matched using K Nearest Neighbor and the similarity ratio between the 
+best and second best match is then compared to a threshold to decide if 
+the match is kept.
+
+\subsection{Isomatch}
+
+\begin{algorithm}[h]
+\caption{Isomatch (\emph{Isomatch})}
+\label{alg-isomatch}
+%{\fontsize{10}{10}\selectfont
+\begin{algorithmic}
+\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
+\State $matches_{init}\gets \varnothing$
+\State $matches_{final}\gets \varnothing$
+\State $features_1 \gets getFeatures(im_1)$
+\State $features_2 \gets getFeatures(im_2)$
+\ForAll{$f_i \in features_1$}
+    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
+    \State $matches_{init} \gets \left(f_i, f_m\right)$
+\EndFor
+\State $partitions_1 \gets isodata(getPositions(features_1))$
+\State $partitions_2 \gets isodata(getPositions(features_2))$
+\State $P_{corr} \gets getMatchMat(partitions_1, partitions_2, 
+matches_{init})$
+\ForAll{$(i,j) \in indices(P)$}
+    \If{$\left(P_{i,j} > 5\right) \wedge \left(P_{i,j} / sum(P_{i}) > 
+    0.5\right)$}
+        \State $matches_{final} \gets getMatches(matches_{init}, 
+        partitions_1, partitions_2, i, j)$
+    \EndIf
+\EndFor
+\Return $matches_{final}$
+\end{algorithmic}
+%}
+\end{algorithm}
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=\columnwidth]{images/isomatch_partitions}
+	\caption{The result of partitioning feature points in two images.  
+	Each dot represents a feature point and feature points grouped with 
+the same color belong to the same partition.}
+	\label{fig:isomatch_partitions}
+\end{figure}
+
+The \emph{Isomatch} algorithm (Algorithm~\ref{alg-isomatch}) 
+\cite{das2008event} is based on the idea that local feature points 
+within a region in one image often matches to features within a 
+corresponding region in the other image. To find these regions the 
+algorithm uses the Isodata algorithm \cite{ball1965isodata} to perform 
+unsupervised clustering on the feature points given their positions in 
+the two images. The Isodata algorithm is similar to K-means with the 
+addition that clusters are merged and split during the clustering 
+process. In Figure~\ref{fig:isomatch_partitions} an example of a 
+partitioning can be seen. The initial set of matches are filtered based 
+on the resulting regions. A match is kept only if it at least half the 
+matches of the same region of origin also belong to the same region in 
+the other image.  $P_{corr}$ in Algorithm~\ref{alg-isomatch} is a matrix 
+where each row corresponds to a region in $im_1$, each column 
+corresponds to a region in $im_2$ and $P_{i,j}$ is the amount of matches 
+going from region $i$ to region $j$.
+
+To threshold the \emph{Isomatch} algorithm we filter the results using 
+the ratio between first and second best match as in \emph{Ratio}, since 
+\emph{Isomatch} itself doesn't readily admit any thresholding parameter.
+
+\subsection{Spectral}
+
+\begin{algorithm}[h]
+\caption{Spectral Match (\emph{Spectral})}
+\label{alg-spectral}
+%{\fontsize{10}{10}\selectfont
+\begin{algorithmic}
+\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
+\State $matches_{init}\gets \varnothing$
+\State $matches_{final} \gets \varnothing$
+\State $features_1 \gets getFeatures(im_1)$
+\State $features_2 \gets getFeatures(im_2)$
+\ForAll{$f_i \in features_1$}
+	\State $f_m,f_n \gets get2NNs(f_i, features_2)$
+	\State $matches_{init} \gets \left(f_i, f_m\right)$
+\EndFor
+\State $M \gets matrix(\left\vert matches_{init} \right\vert, \left\vert 
+matches_{init} \right\vert)$
+\ForAll{$m_i \in matches_{init}$}
+	\ForAll{$m_j \in matches_{init}$}
+		\If{$i = j$}
+			\State $M \gets matchSimilarity(m_i)$
+		\Else
+			\State $M \gets affinity(m_i, m_j)$
+		\EndIf
+	\EndFor
+\EndFor
+\State $x^{*} \gets maximumEigenvector(M)$
+\ForAll{$\left(m_i, x_i\right) \in \left(matches_{init}, x^{*}\right)$}
+	\If{$x_i > t$}
+		\State $matches_{final} \gets matchtes_{final} \cup m_i$
+	\EndIf
+\EndFor
+
+\Return $matches_{final}$
+\end{algorithmic}
+%}
+\end{algorithm}
+
+The \emph{Spectral} algorithm (Algorithm~\ref{alg-spectral}) is a 
+slightly modified version of the spectral matching algorithm proposed by
+Leordeanu and Herbert \cite{leordeanu2005spectral}. It is based on the 
+idea that the set of actual correspondences of feature points between 
+two images should be pairwise consistent. That is, given two feature 
+points that are geometrically close in one image, for most cases we 
+would assume that the closest correspondences in another image would be 
+similarly close. We want to pick out a set of matches $T \subset S$ 
+where $S$ is the initial set of possible matches such that the matches 
+in $T$ are as pairwise consistent as possible. If we let $x$ be a binary 
+vector corresponding in length to the set of initial matches $S$, where 
+$x_i = 1$ if $m_i \subset T$, then we can formulate a subset-score as:
+\begin{equation*}
+	S = \sum_{m_i, m_j \in T} M(m_i, m_j) = x^TMx
+\end{equation*}
+The solution $x^{*}$ that maximizes this equation is then $x^{*} = 
+argmax(x^TMx)$. By relaxing the constraints on $x$ such that it can take
+values in the range of $\left[0, 1\right]$ we can interpret $x_i$ as the
+association of $m_i$ with the optimal subset of matches $T$. Because we 
+only worry about the relative values of $x$ we can fix the norm of $x$ 
+to $1$, in which case by Raleigh's ratio theorem, the $x^{*}$ that 
+optimizes $x^TMx$ is the principal eigenvector of $M$.
+
+Leordeanu and Herbert proposes a simple affinity function to map the 
+pairwise distance of two matches. In a scene where no rotation and 
+excessive affine transformation takes place, it can generally be assumed 
+that the length and direction of the vector between
+the two feature points constituting the first match corresponds to the 
+length and direction of the vector between the two feature points 
+constituting the second match. Given two matches $m_i = (f_{i,1}, 
+f_{i,2})$ and $m_j = (f_{j,1},f_{j,2})$ where $f_{k,n}$ is the feature 
+point of match $k$ in image $n$, we denote the euclidean distance 
+between feature points $f_{i,n}$ and $f_{j,n}$ in image $n$ as 
+$d_{i,j,n}$.  The affinity function assigning a score based on the 
+pairwise distance is then defined as follows:
+\begin{equation*}
+	M(a,b) \begin{cases} 4.5 - \frac{\left(d_{i,j,1} - 
+		d_{i,j,2}\right)^2}{2\sigma^2}, & \mbox{if } \left\vert 
+				d_{i,j,1} - d_{i,j,2} \right\vert < 3\sigma \\ 0, & 
+				\mbox{otherwise}
+	\end{cases}
+\end{equation*}
+In the equation above $\sigma$ is a stabilizing parameter that controls 
+the sensitivity of the score to deformations in the data. A larger 
+$\sigma$ will allow for larger deformations. In the experiments it is 
+fixed to 50. There are a number of occasions where the assumption that 
+pairwise matches should have the same distance doesn't hold true.  A 
+simple example would be matches between two images of the same scene 
+where one image is rotated $180^{\circ}$.  However for a lot of 
+applications like panorama stitching where we only see minor rotation 
+and change of perspective the assumption is accurate.
+
+In the implementation proposed by Leordeanu and Herbert 
+\cite{leordeanu2005spectral} the last step of the algorithm greedily 
+selects matches to ensure that matches are consistent, i.e.\ that two 
+feature points in one image don't match with the same feature point in 
+the other image. This is done by going through all the matches in the 
+order of their associated $x^{*}$ score and for each match eliminating 
+all matches in conflict with this match. This method ensure that as many
+matches are kept as possible since only the conflicting matches are 
+removed. However for cases where most feature points in one image will 
+not have a correspondence in the other other image (e.g.\ cases of 
+partial image overlap or object recognition) the greedy matching 
+algorithm will keep finding matches even after the actual 
+correspondences have already been found as long as they are consistent.
+
+Since the testing is done on images with partial overlap, the final set 
+of matches returned in Algorithm~\ref{alg-spectral} is the set of 
+matches where the association of the match with the optimal subset of 
+matches $T$ as measured by $x^{*}$ is above a certain threshold. For 
+experiments the set of initial matches were given by the best match per 
+feature point and the threshold was adjusted to allow for the best 50\% 
+to be included in the set of final matches. A rate less than 50\% 
+usually did not improve results, so to threshold the \emph{Spectral}
+algorithm we filter the output using the ratio between first and second
+best match as done in \emph{Ratio}.

### 2013-08-12 text/main/ch3_matching_methods.tex
Corrections

@@
 In this chapter we will describe the algorithms used in the experiements
-in detail. We start with the proposed algorithms \emph{MM} and 
-\emph{MMC}, and continue with the algorithms used for comparison, 
-\emph{Ratio}, \emph{Spectral} and \emph{Isomatch}.
+in detail. We start by introducing the proposed algorithms \emph{MM} and 
+\emph{MMC}, and continue with the reference algorithms used for 
+comparison, \emph{Ratio}, \emph{Spectral} and \emph{Isomatch}.
 
@@
 
-In the acquisition stage we gather all features in the set of images.  
-In the matching stage these features are matched using $k$-nearest 
-neighbors.  For any given feature $f_i$ the two most similar neighbors 
-are returned, and we calculate the ratio between them as proposed in 
-\cite{lowe2004sift}.  Any correspondence with a ratio above the 
-threshold supplied will be discarded. Finally in the filter stage we 
-check that matches are from different images and discard all matches 
-that are not symmetric.
+In the \emph{acquisition stage} we extract local feature points and 
+obtain their descriptors from the set of images. The algorithm is not 
+designed to make use of any feature extractor in particular, but for the
+experiments (Chapter~\ref{S:Experiments}) the SIFT feature extractor and
+descriptor has been used. In the \emph{matching} stage these features 
+are matched using $k$-nearest neighbors.  The similarity between 
+features is calculated according to the feature descriptor. For SIFT we 
+use the cosine similarity between the two descriptor vectors.  For any 
+given feature $f_i$ the two most similar neighbors are returned, and we 
+calculate the ratio between them as proposed in \cite{lowe2004sift} (In 
+Part~\ref{ss:ratio} this calculation and other details of \emph{Ratio} 
+will be discussed).  Any correspondence with a ratio above the threshold 
+supplied will be discarded. Finally in the filter stage we check that 
+matches are from different images and discard all matches that are not 
+symmetric. That is; if a feature, $f_i$, is best matched to another 
+feature, $f_j$, we would want for $f_j$ to be best matched to $f_i$ too.
+This isn't always the case, for example if $f_i$ doesn't have a true 
+correspondance in the other image, its closest neighbor $f_j$ might 
+likely be better matched with a different feature point.
 
@@
 non-geometric feature matching by clustering feature points by 
-similarity. This process yields partitions of fairly similar feature 
-points that we can match using the same approach as \emph{MM}.  
-Algorithm~\ref{alg-mmc} shows the pseudocode implementation of \emph{MMC}.
-
-Before we introduce the implementation details we will go over the 
-problem of graph clustering and how it relates to feature matching.
-
-To cluster the feature points, we construct a graph with the feature 
-points as nodes and their similarity score as edge weights. Given a 
-matching function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two 
-feature points in an image and returns their matching score, we can 
-define a matrix $A$ where each element $A_ij = M(k_i, k_j)$. $A$ can be 
-interpreted as the \emph{adjecency matrix} of the fully connected graph.
-
-In the literature there are various ways of clustering a graph according 
-to different measures of what constitutes an optimal partitioning. 
-Traditionally the most used clustering algorithms have been K-means and 
-spectral clustering, but in recent years a host of new algorithms have 
-been proposed based on both Newman's concept of graph 
-modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-well as information theoretical measures\footnote{See for example 
-\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-in \cite{ronhovde2009}} just to mention a few. On tests done using 
-randomly generated graphs with a known partitioning \cite{blondel2008}, 
-\cite{rosvall2008} and \cite{ronhovde2009} perform markedly better than 
-spectral clustering and K-means\cite{lancichinetti2009}.
+similarity. This process yields partitions of similar feature points 
+that we can match using the same approach as \emph{MM}.  
+Algorithm~\ref{alg-mmc} shows the implementation of \emph{MMC}.
 
@@
 \end{algorithm}
+
+To cluster the feature points, we construct a graph with the feature 
+points as nodes and their similarity score as normalized edge weights.  
+Given a set of $n$ features $F = {f_1, \ldots, f_n}$ and a matching 
+function $M : (f_i, f_j) \rightarrow \mathbb{R}$ that takes two feature 
+points as input and returns their matching score, we can define a matrix 
+$A$ as follows:
+\begin{equation*}
+	A_ij = \frac{M(k_i, k_j)}{\frac{\sum_{f_i,f_j \in F\\f_i \neq f_j} 
+	M(f_i, f_j)}{\left\vert F \right\vert ^ {2} - \left\vert F 
+\right\vert}}
+\end{equation*}
+$A$ can be interpreted as the normalized \emph{adjecency matrix} of the 
+fully connected graph.
+
+In the literature there are various ways of clustering a graph according 
+to different measures of what constitutes an optimal partitioning. 
+Traditionally the most used clustering algorithms have been K-means and 
+spectral clustering, but in recent years a host of new algorithms have 
+been proposed based on both Newman's concept of graph 
+modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
+\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
+well as information theoretical measures\footnote{See for example 
+\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
+in \cite{ronhovde2009}} just to mention a few. On tests done using 
+randomly generated graphs with a known partitioning \cite{blondel2008}, 
+\cite{rosvall2008} and \cite{ronhovde2009} perform markedly better than 
+spectral clustering and K-means\cite{lancichinetti2009}.
 
@@
 \subsection{Ratio}
+\label{ss:ratio}
 

### 2013-08-12 text/thesis_bak.tex
Corrections

@@
 \end{equation*}
-Here $\sigma$ is a stabilizing parameter and in the following 
-experiments it is fixed to 50 after empirical optimization.  There are a 
-number of occasions where the assumption that pairwise matches should 
-have the same distance doesn't hold true.  A simple example would be 
-matches between two images of the same scene where one image is rotated 
-$180^{\circ}$.  However for a lot of applications like panorama 
-stitching where we only see minor rotation and change of perspective the 
-assumption is accurate.
+In the equation above $\sigma$ is a stabilizing parameter that controls 
+the sensitivity of the score to deformations in the data. A larger 
+$\sigma$ will allow for larger deformations. In the experiments it is 
+fixed to 50. There are a number of occasions where the assumption that 
+pairwise matches should have the same distance doesn't hold true.  A 
+simple example would be matches between two images of the same scene 
+where one image is rotated $180^{\circ}$.  However for a lot of 
+applications like panorama stitching where we only see minor rotation 
+and change of perspective the assumption is accurate.
 
@@
 
-%, which uses geometric information to improve the matching.  The 
-%comparison  with \emph{Ratio} serves to illustrate the relative 
-%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isomatch} is included to 
-%illustrate the performance of an algorithm relying on geometric 
-%constraints faced with image pairs that might not have any overlap.  
+\subsubsection{And now for something completely different}
+
 The comparison was done using the \emph{Murals} dataset 
@@
 \emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here).
+less than a certain threshold (we use $d_{\max}=5$ pixels here). To 
+count the number of possible matches we go over all possible 
+combinations of feature points between the two images, measure their 
+distance and count how many lie within the threshold.
+Precision on the other hand is measured by the amount of correct matches
+over the total amount of matches returned:
+\begin{equation*}
+	precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
+	~ \# ~ False ~ Matches}
+\end{equation*}
+This measures how accurate the set of returned matches from the 
+algorithm is. An algorithm that returns only a few matches out of many, 
+but most of them are correct will have a high precision and a low 
+recall, where as an algorithm that returns almost all possible matches, 
+both true and false will have a low precision but a high recall. The 
+ideal matching algorithm will be both precise but also return as many 
+correct matches as possible. However for many applications we only need 
+enough correct matches to align to the images, in which case we care 
+more about precision than recall.
 
@@
 (cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
-\emph{Ratio}, \emph{MM}, \emph{MMC}, and \emph{Isomatch} as a function of 
-the number of matches produced (which is achieved by varying thresholds 
-over a certain range). The results show that \emph{MM} and \emph{MMC} 
-consistently outperform \emph{Ratio}; \emph{MMC} generally lies 2-3 
-percentage points above \emph{MM} when both are performing at optimal 
-accuracy.  Although \emph{Isomatch} exhibits a good performance on strict 
-thresholds (small number of matches), that quickly diminishes when more 
-matches are desired.
+\emph{Ratio}, \emph{MM}, \emph{MMC}, \emph{Isomatch} and \emph{Spectral} 
+as a function of the number of matches produced (which is achieved by 
+varying thresholds over a certain range). The results show that 
+\emph{MM} and \emph{MMC} consistently outperform \emph{Ratio}; 
+\emph{MMC} generally lies 2-3 percentage points above \emph{MM} when 
+both are performing at optimal accuracy.  The geometric matching methods 
+\emph{Isomatch} and \emph{Spectral} outperform \emph{Ratio} but fall 
+short of \emph{MM} and \emph{MMC}.
 
 \begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.13\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+	\makebox[0.5\textwidth][c]{%
+		\begin{subfigure}[t]{.13\textwidth}
+			\centering
+			\includegraphics[width=\textwidth]{images/graf}
+		\end{subfigure}%
+		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
    	%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
+		\begin{subfigure}[t]{.27\textwidth}
    		\centering
@@
 
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and \emph{Isomatch} can be 
-implemented in $O(n\log n)$, where $n$ is the total number of feature 
-points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. However, it is 
-possible to approximate this in $O(n\log n)$ using search trees.
+In terms of computational complexity, \emph{Ratio}, \emph{MM}, and 
+\emph{Isomatch} can be implemented in $O(n\log n)$, where $n$ is the 
+total number of feature points. The performance of \emph{Spectral} is 
+upper bounded by $O(n^{3/2})$. Our current \emph{MMC} implementation has 
+a complexity of $O(n^2)$ due to the construction of a similarity matrix 
+of the feature points.  However, it is possible to approximate this in 
+$O(n\log n)$ using search trees.
 
@@
 %	\small
-\begin{tabular}{r*{4}{c}}
+\begin{tabular}{r*{5}{c}}
 \hline
-	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} & \emph{Isomatch} 
-	\\
+	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} %
+& \emph{Isomatch} & \emph{Spectral}	\\
 	\noalign{\smallskip} 
 	%
-	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
+	Running time (seconds): & 21 & 23 & 2722 & 1146 & 994\\
 	\hline

### 2013-08-12 text/main/ch3_matching_methods.tex
Added information about isodata and ratiomatch

@@
 	\left\{f_i\right\})$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
+    \State $ratio \gets d(f_i, f_m) / d(f_i, f_n)$
 	\If{$ratio < t$}
@@
 descriptor has been used. In the \emph{matching} stage these features 
-are matched using $k$-nearest neighbors.  The similarity between 
-features is calculated according to the feature descriptor. For SIFT we 
-use the cosine similarity between the two descriptor vectors.  For any 
-given feature $f_i$ the two most similar neighbors are returned, and we 
-calculate the ratio between them as proposed in \cite{lowe2004sift} (In 
-Part~\ref{ss:ratio} this calculation and other details of \emph{Ratio} 
-will be discussed).  Any correspondence with a ratio above the threshold 
-supplied will be discarded. Finally in the filter stage we check that 
-matches are from different images and discard all matches that are not 
-symmetric. That is; if a feature, $f_i$, is best matched to another 
-feature, $f_j$, we would want for $f_j$ to be best matched to $f_i$ too.
+are matched using $k$-nearest neighbors.  The distance function $d(f_i, 
+f_j)$ between features is calculated according to the feature 
+descriptor. For SIFT we use the cosine similarity between the two 
+descriptor vectors, while other descriptors might use other 
+measures\footnote{BRIEF for example uses the hamming measure to speed up 
+the computation}.  For any given feature $f_i$ the two closest neighbors 
+are returned, and we calculate the ratio between them as proposed in 
+\cite{lowe2004sift} (In Part~\ref{ss:ratio} this calculation and other 
+details of \emph{Ratio} will be discussed).  Any correspondence with a 
+ratio above the threshold supplied will be discarded. Finally in the 
+filter stage we check that matches are from different images and discard 
+all matches that are not symmetric. That is; if a feature, $f_i$, is 
+best matched to another feature, $f_j$, we would want for $f_j$ to be 
+best matched to $f_i$ too.
 This isn't always the case, for example if $f_i$ doesn't have a true 
@@
 \begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
+\Require $images$ : set of images, $t \in \mathbb{R}$, $\alpha \in 
+\mathbb{R}$
 \State $M\gets \varnothing$
@@
 \State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $A_{norm}\gets 1 - normalize(A)$
-\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $P\gets cluster(A_{pruned})$
+\State $A_{norm}\gets normalize(A)$
+\ForAll{$(i,j) \in indices(A)$} \Comment Prune edges
+    \If{$A_{norm}[i,j] < \alpha$}
+        \State $A_{norm}[i,j] \gets 0$
+    \EndIf
+\EndFor
+\State $P\gets cluster(A_{norm})$
 \ForAll{$p \in P$} \Comment p is a set of feature points
@@
 points as nodes and their similarity score as normalized edge weights.  
-Given a set of $n$ features $F = {f_1, \ldots, f_n}$ and a matching 
-function $M : (f_i, f_j) \rightarrow \mathbb{R}$ that takes two feature 
-points as input and returns their matching score, we can define a matrix 
-$A$ as follows:
+Given a set of $n$ features $F = {f_1, \ldots, f_n}$ and a similarity 
+function $s$ we can define the matching function $M : (f_i, f_j) 
+\rightarrow \mathbb{R}$ as follows:
 \begin{equation*}
-	A_ij = \frac{M(k_i, k_j)}{\frac{\sum_{f_i,f_j \in F\\f_i \neq f_j} 
-	M(f_i, f_j)}{\left\vert F \right\vert ^ {2} - \left\vert F 
-\right\vert}}
+    M(a,b) = \begin{cases} similarity(f_i, f_j) & \mbox{if } f_i \neq 
+    f_j \\ 0 & \mbox{otherwise}
+	\end{cases}
 \end{equation*}
-$A$ can be interpreted as the normalized \emph{adjecency matrix} of the 
-fully connected graph.
+The similarity function is based on the distance measure $d(f_i,f_j)$ 
+(cosine similarity in the case of SIFT): $similarity(f_i, f_j) = 1 - 
+d(f_i,f_j) / c$ where $c$ is a normalization constant normalizing the 
+distance values between $0$ and $1$.
+We obtain $A$, the normalized adjecency matrix of the fully connected 
+similarity graph of feature points as follows:
+\begin{equation*}
+    A_{i,j} = \frac{M(f_i, f_j)}{\sum\limits_{f_i,f_j \in F} M(f_i, f_j) 
+    / \left\vert F \right\vert ^ {2}}
+\end{equation*}
 
@@
 \cite{blondel2008}, and does not emphasize partitions of equal size, as 
-opposed to spectral clustering or k-means \cite{von2007}, for example.
+opposed to e.g.\ spectral clustering or k-means \cite{von2007}.
+
+The louvain method is based on optimizing the \emph{Modularity} proposed 
+by \cite{girvan2002} and defined as:
+\begin{eqnarray*}
+	Q & = & (\mbox{fraction of edges within communities}) \\
+	  & & - (\mbox{expected fraction of such edges}) \\
+	& = & \frac{1}{2m} \sum_{i,j} \left[ A_{ij} - \frac{k_i k_j}{2m} \
+\right] \delta(c_i, c_j)
+\end{eqnarray*}
+Where $m=\frac{1}{2} \sum_{ij} A_{ij}$, $k_i = \sum_j A_{ij}$ and 
+$A_{ij}$ is the weight between the edge connecting $i$ and $j$.  
+$\delta(c_i, c_j)$ is the Kroneker Delta which is 1 only if the 
+community assignment $c_i$ is equal to the community assignment $c_j$.
+
+The Louvain Method is based on the maximizing the \emph{Modularity} of a 
+graph iteratively. This is done efficiently because the gain in 
+modularity from moving a vertex $v_i$ to a community $C$ can be 
+calculated easily:
+\begin{equation*}
+	\Delta Q = \left[ \frac{\sum_{in} + 2 k_{i,in}}{2m} - \
+    \left(\frac{\sum_{tot} + k_i}{2m} \right)^2 \right]
+	- \left[\frac{\sum_{in}}{2m} - \left(\frac{\sum_{tot}}{2m} \
+	\right)^2 - \left( \frac{k_i}{2m} \right)^2 \right]
+\end{equation*}
+Here as in the definition of \emph{Modularity}, $m=\frac{1}{2} \sum_{ij} 
+A_{ij}$, $k_i = \sum_j A_{ij}$ and $k_{i,in}$ is the summed weights of 
+the edges from $v_i$ to vertices in $C$.  $\sum_{in}$ is the sum of the 
+weights of the edges of $C$ while $\sum_{tot}$ is the sum of all edges 
+with at least one vertex in $C$.  The algorithm works by assigning each 
+vertex to its proper cluster and then for each iteration reassign 
+vertices to neighboring communities if it increases the 
+\emph{Modularity}.  These iterations are carried out until there are no 
+reassignments in which case an initial clustering has been reached.  For 
+graphs consisting of a large number of vertices, the algorithm can now 
+be repeated, treating each of the resulting clusters as a vertex and 
+repeating the same procedure.
+
 While the Louvain clustering algorithm does not require any parameters 
@@
 the same partition if the graph is very connected.  To ensure that the 
-graph is well clustered, the adjacency matrix is pruned by setting all 
-edges below a certain threshold to $0$.  From empirical analysis, 
-retaining the top 2.5\% of edges with the highest similarity seems to 
-work well in practice.  Figure~\ref{fig:graph} shows the result of 
-clustering the feature points as a graph.
+graph is well clustered, the adjacency matrix is pruned setting all 
+edges below a certain threshold to $0$. In Algorithm~\ref{alg-mmc} this 
+threshold is provided as the variable $\alpha$.  From empirical 
+analysis, retaining the top 2.5\% of edges with the highest similarity 
+seems to work well in practice. This requires estimating $\alpha$ 
+parameter after obtaining the adjecency matrix.  Figure~\ref{fig:graph} 
+shows the result of clustering the feature points as a graph.
 
@@
 \label{alg-getmatches}
-    \fontsize{10}{10}\selectfont
+%\fontsize{10}{10}\selectfont
     \begin{algorithmic}
@@
 Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
-more than two elements using the \emph{MM} approach.  However, as can be 
-seen in the example in Figure~\ref{fig:graph}, many of the partitions 
-contain only two feature points from different images linked by one 
-edge. In this case, we compare the similarity of the these two feature 
-points with their second best match and remove matches where this ratio 
-lies above a certain threshold, like in the \emph{Ratio} algorithm.  For 
-example in the case of Figure~\ref{fig:pitts_partition}, we have feature 
-points from a building in one image grouped together with points from a 
-shirt pattern in another.  The nearest neighbor method would have 
-returned wrong matches, but since we match the partition with \emph{MM}, 
-points in the building end up matching other points in the building, and 
-no matches are returned.
+more than two elements using the \emph{MM} approach (\emph{MMGet}).  
+However, as can be seen in the example in Figure~\ref{fig:graph}, many 
+of the partitions contain only two feature points from different images 
+linked by one edge. In this case, we compare the similarity of the these 
+two feature points with their second best match and remove matches where 
+this ratio lies above a certain threshold, like in the \emph{Ratio} 
+algorithm (\emph{RatioGet}).  For example in the case of 
+Figure~\ref{fig:pitts_partition}, we have feature points from a building 
+in one image grouped together with points from a shirt pattern in 
+another.  The nearest neighbor method would have returned wrong matches, 
+but since we match the partition with \emph{MM}, points in the building 
+end up matching other points in the building, and no matches are 
+returned.
 
@@
     \State $f_m,f_n \gets get2NNs(f_i, features_2)$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
+    \State $ratio \gets d(f_i, f_m) / d(f_i, f_n)$
 	\If{$ratio < t$}
@@
 
-\emph{Ratio} (Algorithm~\ref{alg-ratio}) \cite{lowe2004sift} is the most 
-straightforward of the three reference algorithms. Feature points are 
-matched using K Nearest Neighbor and the similarity ratio between the 
-best and second best match is then compared to a threshold to decide if 
-the match is kept.
+\emph{Ratio} (Algorithm~\ref{alg-ratio}) \cite{lowe2004sift} diverges 
+from from matching feature points by distance in that the metric we use 
+to evaluate the feature points is the ratio of the distance to best 
+match compared to the distance of the second best match. In detail, say 
+$f_i$ is a feature point in an image $im_1$ and we are finding the 
+closest match in another image $im_2$. Given the two closest neighbors 
+to $f_i$ in in $im_l$, $f_m$ and $f_n$ ($d(f_i,f_m) < 
+similarity(f_i,f_n)$ and a threshold $\beta$, we decide to return a 
+match between $f_i$ and $f_j$ as follows:
+\begin{equation*}
+    match(f_i,(f_m,f_n)) = \begin{cases}
+        \left\{(f_i,f_m)\right\} &
+        \frac{d(f_i,f_m)}{d(f_i,f_n)} > \beta \\ \varnothing & 
+        \mbox{otherwise}
+    \end{cases}
+\end{equation*}
+
+We can call a distance measure \emph{Metric} given that it adheres to 
+the following four properties: it is non-negative: $d(f_i,f_j) \geq 0$.  
+It is only zero for identical inputs: $d(f_i,f_j) = 0 \Leftrightarrow 
+f_i = f_j$. It is symmetric: $d(f_i,f_j) = d(f_j,f_i)$. It obeys the 
+triangle inequality: $d(f_i,f_k) \leq d(f_i,f_j) + d(f_j,f_k)$.
+
+This holds true for both cosine similarity and the hamming distance for 
+which reason we can insert the feature points in a metric tree and 
+retrieve the nearest neighbors in $O(log(n))$ computational time where 
+$n$ is the amount of feature points.  Both \emph{Ratio} and \emph{MM} 
+takes advantage of this property to match $n$ feature points in 
+$O(nlog(n))$ computational time.
 
@@
 \State $partitions_2 \gets isodata(getPositions(features_2))$
-\State $P_{corr} \gets getMatchMat(partitions_1, partitions_2, 
-matches_{init})$
+\State $P \gets getMatchMat(partitions_1, partitions_2, matches_{init})$
 \ForAll{$(i,j) \in indices(P)$}
-    \If{$\left(P_{i,j} > 5\right) \wedge \left(P_{i,j} / sum(P_{i}) > 
+\If{$\left(P[i,j] > 5\right) \wedge \left(P[i,j] / sum(P_{i}) > 
 0.5\right)$}
@@
 
-The \emph{Isomatch} algorithm (Algorithm~\ref{alg-isomatch}) 
-\cite{das2008event} is based on the idea that local feature points 
-within a region in one image often matches to features within a 
-corresponding region in the other image. To find these regions the 
-algorithm uses the Isodata algorithm \cite{ball1965isodata} to perform 
-unsupervised clustering on the feature points given their positions in 
-the two images. The Isodata algorithm is similar to K-means with the 
-addition that clusters are merged and split during the clustering 
-process. In Figure~\ref{fig:isomatch_partitions} an example of a 
-partitioning can be seen. The initial set of matches are filtered based 
-on the resulting regions. A match is kept only if it at least half the 
-matches of the same region of origin also belong to the same region in 
-the other image.  $P_{corr}$ in Algorithm~\ref{alg-isomatch} is a matrix 
-where each row corresponds to a region in $im_1$, each column 
-corresponds to a region in $im_2$ and $P_{i,j}$ is the amount of matches 
-going from region $i$ to region $j$.
+\emph{Isomatch} (Algorithm~\ref{alg-isomatch}) \cite{das2008event} is 
+based on the idea that local feature points within a region in one image 
+often matches to features within a corresponding region in the other 
+image. To find these regions the algorithm uses the Isodata algorithm 
+\cite{ball1965isodata} to perform unsupervised clustering on the 
+positions of the feature points in the two images. This results in a 
+fragmentation of the feature points into different regions based on 
+their position in the image as demonstrated in 
+Figure~\ref{fig:isomatch_partitions}. Based on this partitioning we 
+create a correspondence matrix $P$. If we have $n$ regions in one image 
+and $m$ regions in the other, $P$ is an $n \times m$ matrix. Given a set 
+of matches $M = \{(f_{i,1}, f_{j}), \ldots \}$ and $n$ regions returned 
+by Isodata, each region consisting of a set of feature points $R_i = 
+\{f_i, f_j, \ldots\}$ we can construct $P$ as follows:
+\begin{equation*}
+    P_{i,j} = \sum_{(f_i,f_j) \in M} \delta_{f_i \in R_i}\delta_{f_j \in 
+    R_j}
+\end{equation*}
+Here $\delta_{f_i \in R_i}$ is $1$ if $f_i \in R_i$ and $0$ otherwise.  
+The initial set of matches are filtered based on $P$ by the $getMatches$ 
+function. A match is kept only if it at least half the matches of the 
+same region of origin also belong to the same region in the other image.
+
+The Isodata algorithm is similar to K-means with the addition that 
+clusters are merged and split during the clustering process. In K-means 
+we randomly assign the data points to $k$ clusters to begin with and 
+calculate their mean. Then for each data point we reassign it to the 
+cluster closest in mean. We then calculate the mean of the updated 
+clusters and reiterate the process until we have spent a set amount of 
+iterations or no reassignments have taken place. Isodata runs the same 
+algorithm, but for each iteration it goes through the clusters and 
+checks if any can be merged or split. Clusters are split if their 
+variance along an axis is beyond a threshold, while two clusters are 
+merged if their distance is below another threshold. This approach is 
+beneficial when we don't know from the outside the amount of clusters we 
+expect to see. For example in the case of feature points it is not 
+obvious before clustering them regionally how many regions we obtain for 
+an image.
 
@@
 
-The \emph{Spectral} algorithm (Algorithm~\ref{alg-spectral}) is a 
-slightly modified version of the spectral matching algorithm proposed by
-Leordeanu and Herbert \cite{leordeanu2005spectral}. It is based on the 
-idea that the set of actual correspondences of feature points between 
-two images should be pairwise consistent. That is, given two feature 
-points that are geometrically close in one image, for most cases we 
-would assume that the closest correspondences in another image would be 
-similarly close. We want to pick out a set of matches $T \subset S$ 
-where $S$ is the initial set of possible matches such that the matches 
-in $T$ are as pairwise consistent as possible. If we let $x$ be a binary 
-vector corresponding in length to the set of initial matches $S$, where 
-$x_i = 1$ if $m_i \subset T$, then we can formulate a subset-score as:
+The \emph{Spectral} algorithm (Algorithm~\ref{alg-spectral}) used in the 
+comparison of matching algorithms is based on the spectral matching 
+algorithm proposed by Leordeanu and Herbert 
+\cite{leordeanu2005spectral}.  The central idea behind it is that the 
+set of actual correspondences of feature points between two images 
+should be pairwise consistent. That is, given two feature points that 
+are geometrically close in one image, for most cases we would assume 
+that the closest correspondences of these two points in another image 
+would be similarly close.  Based on this assumption we want to pick out 
+a set of matches $T \subset S$ where $S$ is the initial set of possible 
+matches such that the matches in $T$ are as pairwise consistent as 
+possible. If we let $x$ be a binary vector corresponding in length to 
+the set of initial matches $S$, where $x_i = 1$ if $m_i \subset T$, then 
+we can formulate a subset-score as:
 \begin{equation*}
@@
 \begin{equation*}
-	M(a,b) \begin{cases} 4.5 - \frac{\left(d_{i,j,1} - 
+    M(a,b) = \begin{cases} 4.5 - \frac{\left(d_{i,j,1} - 
         d_{i,j,2}\right)^2}{2\sigma^2}, & \mbox{if } \left\vert 

### 2013-08-12 text/main/ch1_introduction.tex
Fixed references

@@
 \chapter*{Introduction}
-Matching feature points is one of the problems in computer vision that 
-if solved well will provide a useful tool for improving methods on a 
-host of interesting problems. If we can match feature points reliably we 
-can recognize objects, make panoramas, recognize duplicate photos, guide 
-robots and airplanes and a host of other interesting applications 
-\footnote{For a few examples of some of these applications, check out: 
-\cite{se2002global} (robot guidance), \cite{brown2007automatic} 
-(panorama construction), \cite{lowe2004sift} (has parts on object 
-recognition), \cite{chu2010consumer} (duplicate detection)}.  For all 
-these problems better feature point matching will most likely yield 
-better solutions.
+%Matching feature points is one of the problems in computer vision that 
+%if solved well will provide a useful tool for improving methods on a 
+%host of interesting problems. If we can match feature points reliably 
+%we can recognize objects, make panoramas, recognize duplicate photos, 
+%guide robots and airplanes and a host of other interesting applications 
+%\footnote{For a few examples of some of these applications, check out: 
+%\cite{se2002global} (robot guidance), \cite{brown2007automatic} 
+%(panorama construction), \cite{lowe2004sift} (has parts on object 
+%recognition), \cite{chu2010consumer} (duplicate detection)}.  For all 
+%these problems better feature point matching will most likely yield 
+%better solutions.
 
@@
 
-The thesis is organized as follows: Chapter~\ref{C:background} provides 
+The thesis is organized as follows: Chapter~\ref{C:Background} provides 
 background and motivation for the development of \emph{MM} and 
@@
 who might use this thesis as a starting point for finding other research 
-on the same subject. Chapter~\ref{C:algorithms} will introduce in detail 
+on the same subject. Chapter~\ref{C:Algorithms} will introduce in detail 
 the algorithms proposed in this thesis. The reference algorithms used to 
 benchmark \emph{MM} and \emph{MMC} are also introduced in detail.  
-Chapter~\ref{C:experiments} details the experiments done to evaluate the 
+Chapter~\ref{C:Experiments} details the experiments done to evaluate the 
 proposed algorithms both in terms of how they were conducted as well as 
-their results. Chapter~\ref{C:applications} provides two examples of how 
+their results. Chapter~\ref{C:Applications} provides two examples of how 
 the matching algorithms can improve on panorama stitching and near 
@@
 well as the support of Advanced Digital Science Center in Singapore that 
-hosted me as an intern for the duration of my thesis work.
+hosted me as an intern during my thesis work.

### 2013-08-12 text/main/ch3_matching_methods.tex
Fixed references

@@
 \chapter{Algorithms}
-\label{C:algorithms}
+\label{C:Algorithms}
 
@@
 designed to make use of any feature extractor in particular, but for the
-experiments (Chapter~\ref{S:Experiments}) the SIFT feature extractor and
+experiments (Chapter~\ref{C:Experiments}) the SIFT feature extractor and
 descriptor has been used. In the \emph{matching} stage these features 
@@
 are returned, and we calculate the ratio between them as proposed in 
-\cite{lowe2004sift} (In Part~\ref{ss:ratio} this calculation and other 
-details of \emph{Ratio} will be discussed).  Any correspondence with a 
-ratio above the threshold supplied will be discarded. Finally in the 
-filter stage we check that matches are from different images and discard 
-all matches that are not symmetric. That is; if a feature, $f_i$, is 
-best matched to another feature, $f_j$, we would want for $f_j$ to be 
-best matched to $f_i$ too.
+\cite{lowe2004sift}\footnote{In Part~\ref{ss:ratio} this calculation and 
+other details of \emph{Ratio} will be discussed}.  Any correspondence 
+with a ratio above the threshold supplied will be discarded. Finally in 
+the filter stage we check that matches are from different images and 
+discard all matches that are not symmetric. That is; if a feature, 
+$f_i$, is best matched to another feature, $f_j$, we would want for 
+$f_j$ to be best matched to $f_i$ too.
 This isn't always the case, for example if $f_i$ doesn't have a true 
@@
 \begin{equation*}
-    M(a,b) = \begin{cases} similarity(f_i, f_j) & \mbox{if } f_i \neq 
-    f_j \\ 0 & \mbox{otherwise}
+    M(a,b) = \begin{cases} s(f_i, f_j) & \mbox{if } f_i \neq f_j \\ 0 & 
+    \mbox{otherwise}
 	\end{cases}
 \end{equation*}
-The similarity function is based on the distance measure $d(f_i,f_j)$ 
-(cosine similarity in the case of SIFT): $similarity(f_i, f_j) = 1 - 
+The similarity function $s$ is based on the distance measure 
+$d(f_i,f_j)$ (cosine similarity in the case of SIFT): $s(f_i, f_j) = 1 - 
 d(f_i,f_j) / c$ where $c$ is a normalization constant normalizing the 
@@
 	\includegraphics[width=\textwidth]{images/MMC_graph}
-    \label{fig:graph}
     \caption{The partitioned feature graph. Each vertex represents a 
@@
 or three.}
-	\label{fig:graph}
+    \label{fig:graph-view}
 \end{figure}
@@
 seems to work well in practice. This requires estimating $\alpha$ 
-parameter after obtaining the adjecency matrix.  Figure~\ref{fig:graph} 
-shows the result of clustering the feature points as a graph.
+parameter after obtaining the adjecency matrix.  
+Figure~\ref{fig:graph-view} shows the result of clustering the feature 
+points as a graph.
 
@@
 more than two elements using the \emph{MM} approach (\emph{MMGet}).  
-However, as can be seen in the example in Figure~\ref{fig:graph}, many 
-of the partitions contain only two feature points from different images 
-linked by one edge. In this case, we compare the similarity of the these 
-two feature points with their second best match and remove matches where 
-this ratio lies above a certain threshold, like in the \emph{Ratio} 
-algorithm (\emph{RatioGet}).  For example in the case of 
+However, as can be seen in the example in Figure~\ref{fig:graph-view}, 
+many of the partitions contain only two feature points from different 
+images linked by one edge. In this case, we compare the similarity of 
+the these two feature points with their second best match and remove 
+matches where this ratio lies above a certain threshold, like in the 
+\emph{Ratio} algorithm (\emph{RatioGet}).  For example in the case of 
 Figure~\ref{fig:pitts_partition}, we have feature points from a building 

### 2013-08-12 text/main/ch5_experiments.tex
Fixed references

@@
 \chapter{Experiments and Results}
-\label{S:Experiments}
-%
-To reliably measure the accuracy of a matching method on real images, we 
-either need a set of image pairs tied by a homography, or we have to 
-manually count the number of inliers. The latter becomes prohibitive for 
-large numbers of (non-trivial) images.
+\label{C:Experiments}
+
+In order to demonstrate that the algorithms we propose are in fact 
+superior to similar algorithms in the field, we will have to compare 
+them. In this chapter we will first describe exactly how we intent to 
+test the algorithms and then discuss the results of these comparisons.
+
+\section{Experiments}
+For our ideal matching algorithm we would like it to return not only 
+correct matches but all possible correct matches when images overlap and 
+no matches at all when they don't.  We would like it to work flawlessly 
+not just one a few images but on all possible images, and we would 
+expect it to run fast even on when faced with tens of thousands of 
+feature points.
+
+These requirements fall in to three different categories. We want to 
+verify that the algorithm is \emph{accurate}, \emph{general} and 
+\emph{fast}.
+
+\subsection{Measuring Accuracy}
+
+To measure the accuracy of an algorithm we are interested in two values:
+Precision and Recall. These measures were introduced in \cite{ke2004pca}
+and later used in \cite{mikolajczyk2005performance}. Recall corresponds 
+to the number of correct matches over the total amount of possible 
+correct matches in between the two images:
+\begin{equation*}
+	recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~ 
+	Matches}
+\end{equation*}
+This measure tells us how thorough we are in finding all possible 
+matches that could be made between the two images. To decide whether a 
+match is correct, we use the following method:
+Given a potential match between two pixels $p_1$ and $p_2$, $m = 
+\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
+$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
+two points satisfy the following criteria:
+\begin{equation*}
+\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
+\end{equation*}
+That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
+\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
+less than a certain threshold (we use $d_{\max}=5$ pixels here). To 
+count the number of possible matches we go over all possible 
+combinations of feature points between the two images, measure their 
+distance and count how many lie within the threshold.
+Precision on the other hand is measured by the amount of correct matches
+over the total amount of matches returned:
+\begin{equation*}
+	precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
+	~ \# ~ False ~ Matches}
+\end{equation*}
+This measures how accurate the set of returned matches from the 
+algorithm is. An algorithm that returns only a few matches out of many, 
+but most of them are correct will have a high precision and a low 
+recall, where as an algorithm that returns almost all possible matches, 
+both true and false will have a low precision but a high recall. The 
+ideal matching algorithm will be both precise but also return as many 
+correct matches as possible. However for many applications we only need 
+enough correct matches to align to the images, in which case we care 
+more about precision than recall.
+
+\subsection{Measuring Generality}
+
+To convincingly show that the algorithms work for general cases we need 
+to demonstrate good recall and precision across a wide range of images.  
+However if we are just given to images and a set of matches, there is no
+way to tell which matches are correct and which aren't without going 
+through them by hand and count them. For any but the simplest cases this
+becomes prohibitively time consuming.
+
+A way to circumvent this problem is to restrict the images we test on to 
+image pairs that are linked by a homography. Two images linked by a 
+homography are tied by a change in perspective such that we given a 
+point in one image and the homography we can calculate the corresponding 
+position of the point in the other image. Not all image pairs can be 
+linked with a homography, something that is intuitive if we image two 
+pictures of a playing child. We can't predict the positions of the hands
+of the child in the second image with pixel precision just by knowing 
+the position of the hands in the first image. However for images where 
+all points are situated on a plane or where all the points are far away,
+a homography is usually sufficent to describe the pixel transformations 
+from one image to the next.
 
@@
 
-The comparison was done using the \emph{Murals} dataset 
-(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
-from \cite{mikolajczyk2005performance}, and two 
-images\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher 
-dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
-
-Test sets were generated from the image pairs by cropping square patches of
-$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
-Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
-This ensures that patch pairs with no overlap still retain a general similarity to each 
-other, while patches that do overlap often only share a small 
-part of their area. Figure~\ref{fig:fairey} shows an example of 
+To increase the generality of the image pairs to cases that partially 
+overlap or have no overlap at all, we generated test sets from the image 
+pairs by cropping square patches of $250\!\times\!250$ pixels with a 
+random vertical and horizontal offset.  Given a source image pair, we 
+produce 100 pairs of patches that might or might not overlap.  This 
+ensures that patch pairs with no overlap still retain a general 
+similarity to each other, while patches that do overlap often only share 
+a small part of their area.  Figure~\ref{fig:fairey} shows an example of 
 possible pairs of test image patches produced from a source image pair.  
@@
 \cite{mikolajczyk2005performance}.
+
+In addition to the \emph{Murals} data set we created a similar test set
+based on the the \emph{Graf} set (Figure~\ref{fig:Graf}) showing 
+different amounts of viewpoint change. A more typical real life test 
+case was created as well using two images\footnote{100\_1942.jpg and 
+100\_1941.jpg} (\emph{Pitts}) from the Gallagher dataset 
+\cite{gallagher2008} (Figure~\ref{fig:comparemirror}). These two images 
+are typical holiday shots and feature occlusion as well as a slight 
+change in perspective.
 
@@
 
-The results are presented as \emph{precision} versus \emph{recall} 
-similar to \cite{ke2004pca} and \cite{mikolajczyk2005performance}.  
-Recall corresponds to the number of correct matches over the total 
-amount of possible correct matches in between the two images:
-\begin{equation*}
-	recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~ 
-	Matches}
-\end{equation*}
-This measure tells us how many thorough we are in finding all possible 
-matches that could be made between the two images. To decide whether a 
-match is correct, we use the following method:
-Given a potential match between two pixels $p_1$ and $p_2$, $m = 
-\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
-$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
-two points satisfy the following criteria:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
-\end{equation*}
-That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here). To 
-count the number of possible matches we go over all possible 
-combinations of feature points between the two images, measure their 
-distance and count how many lie within the threshold.
-Precision on the other hand is measured by the amount of correct matches
-over the total amount of matches returned:
-\begin{equation*}
-	precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
-	~ \# ~ False ~ Matches}
-\end{equation*}
-This measures how accurate the set of returned matches from the 
-algorithm is. An algorithm that returns only a few matches out of many, 
-but most of them are correct will have a high precision and a low 
-recall, where as an algorithm that returns almost all possible matches, 
-both true and false will have a low precision but a high recall. The 
-ideal matching algorithm will be both precise but also return as many 
-correct matches as possible. However for many applications we only need 
-enough correct matches to align to the images, in which case we care 
-more about precision than recall.
+\subsection{Measuring Speed}
+
+To gain an intuition about the typical running time of an algorithm we 
+need to understand how the speed of the algorithm varies with different 
+input lengths (i.e.\ pictures of different sizes in our case) as well as 
+a general idea of how long it takes the algorithm to run given inputs of
+a typical case. The first is usually denoted the computational 
+complexity of the algorithm, while the second is a measure of speed.
+
+Once we know how long it will take the algorithm to run for inputs of a 
+certain size we can use the complexity to extrapolate how much longer it
+will take to run for inputs of e.g.\ double or half that size. For 
+example a matching algorithm with a complexity of $O(n^2)$ that takes 
+four seconds to find matches for $100$ feature points will take most 
+likely take $16$ seconds to find matches for $200$ feature points. If 
+the algorithm had a complexity of $O(n)$ it would more likely take $8$ 
+seconds to run on $200$ feature points.
+
+For this reason we will have to look at both the measuring speed as well
+as the computational complexity of the algorithms.
 
@@
 \label{S:Results}
+
+Using the \emph{Murals} dataset as well as test sets created from the 
+\emph{Graf} and \emph{Pitts} images we tested \emph{MM} and \emph{MMC} 
+against \emph{Ratio}, \emph{Spectral} and \emph{Isomatch}.
+
+\subsection{Accuracy and Generality}
 
@@
 pruning the initial matching set, we tested a hybrid algorithm 
-\emph{Spectral-MMC} where matches are pruned by \emph{MMC} before being 
-applied to \emph{Spectral}. The results are shown in 
+\emph{Spectral-MMC} where matches are selected by \emph{MMC} before 
+being filtered by \emph{Spectral}. The results are shown in 
 Figure~\ref{fig:result_spectral-mmc} and show that \emph{Spectral-MMC} 
@@
 
+\subsection{Computational Complexity and Speed}
+
 In terms of computational complexity, \emph{Ratio}, \emph{MM}, and 

### 2013-08-13 text/head/abstracts.tex
A few touches on the thesis

%\begingroup
%\let\cleardoublepage\clearpage

% English abstract
\cleardoublepage
\chapter*{Abstract}
%\markboth{Abstract}{Abstract}
\addcontentsline{toc}{chapter}{Abstract} % adds an entry to the table of 
% put your text here
Many algorithms have been proposed to solve the problem of matching 
feature points in two or more images using geometric assumptions to 
increase the robustness of the matching. However, very little work 
addresses the case where these assumptions might not hold. In particular 
few methods address the problem of reliable matching in cases where it 
is unknown whether two images have any corresponding areas or objects in 
the first place.  \\

We propose two algorithms for matching feature points without the use of 
geometric constraints. The first relies on the fact that any match 
between two images should be better than all possible matches within a 
single image. The second algorithm extends this idea by using community 
structure in the similarity graph of feature points to find reliable 
correspondences. To evaluate the algorithms experimentally, we introduce 
a simple method to generate a large amount of test cases based on a set 
of image pairs with viewpoint changes. Our results show that the 
proposed algorithm is generally superior to traditional approaches in 
finding correct correspondences.

### 2013-08-13 text/head/titlepage.tex
A few touches on the thesis

@@
 \null\vspace{2cm}
-{\huge Reliable feature point matching} \\[24pt] 
-\textcolor{gray}{\small{THIS IS A TEMPORARY TITLE PAGE \\ It will be 
-replaced for the final print by a version \\ provided by the service 
-academique.}}
+{\huge Reliable Feature Point Matching} \\[24pt]
+{\small MASTER'S THESIS}
 
@@
 \begin{tabular} {cc}
-\parbox{0.3\textwidth}{\includegraphics[width=4cm]{images/epfl}}
+\parbox{0.3\textwidth}{\includegraphics[width=4cm]{images/adsc}\\[18pt]
+\includegraphics[width=4cm]{images/epfl}}
 &
 \parbox{0.7\textwidth}{%
-	Thesis in Computer Science\\
-	presented on September 3rd 2013\\
-	at the Advanced Science Research Center\\
-	Fusionopolis, Singapore\\
+    Jonas Toft Arnfred\\
+    Master's student in Computer Science\\
+	at École Polytechnique Fédérale de Lausanne (EPFL)\\[9pt]
+	Spring semester 2013\\
+	Advanced Digital Sciences Center (Singapore)\\[9pt]
+    Supervisors at ADSC: \ Dr. Stefan Winkler\\ [4pt]
+    Supervisor at EPFL: ~ \ Prof. Sabine Süsstrunk\\ [4pt]
+    \null \hspace{3em} }
 
 %
-Singapore, ADSC, 2011}
+%Singapore, ADSC, August 2013
 \end{tabular}

### 2013-08-13 text/main/ch1_introduction.tex
A few touches on the thesis

@@
 point matching, but via a series of detours I ended up circling the 
-problem which attracted me, not just because it its importance, but also 
-because of its inherent simplicity. Out of two sets, finding pairs of 
-similar elements seems like a problem that should have been solved long 
-ago, yet because of the nature of feature points and the data they are 
-used on, there seems to be plenty of progress to be made.
+problem which I found alluring, not just because it its importance, but 
+also because of its inherent simplicity. Out of two sets, finding pairs 
+of similar elements seems like a problem that should have been solved 
+long ago, yet because of the nature of feature points and the data they 
+are used on, there seems to be plenty of progress to be made still.
 
 As the outcome of my work I propose two algorithms, \emph{Mirror Match 
-(MM)} and \emph{Mirror Match with Clustering (MMC)}, both designed to 
-improve feature point matching. The goal of this thesis will be to 
-introduce these algorithms and convincingly demonstrate that they are 
-useful. While doing this I hope to provide sufficient background for a 
-technically minded reader without any necessary background in computer 
-vision to follow the motivation behind \emph{MM} and \emph{MMC} as well 
-as the place of both algorithms in a bigger scientific perspective.
+(MM)} and \emph{Mirror Match with Clustering (MMC)}. Both algorithms are 
+designed to tackle the problem of reliably matching feature points under 
+circumstances where we cannot assume two images necessarily have any 
+correspondences.  The goal of this thesis will be to describe these 
+algorithms and convincingly demonstrate that they outperform traditional 
+approaches.  While doing this I hope to provide sufficient background 
+for a technically minded reader without any necessary experience in 
+computer vision to follow the motivation behind \emph{MM} and \emph{MMC} 
+and enable him or her to place both algorithms in a bigger scientific 
+perspective.
 
@@
 '\emph{we}' to underline the fact this thesis had not been possible had 
-it not been for the guidance of Stefan Winkler and Sabine S\"usstrunk as 
-well as the support of Advanced Digital Science Center in Singapore that 
-hosted me as an intern during my thesis work.
+it not been for the guidance of \emph{Stefan Winkler} and \emph{Sabine 
+S\"usstrunk} as well as the support of \emph{Advanced Digital Science 
+Center} in Singapore that hosted me as an intern during the work on this 
+thesis.

### 2013-08-13 text/main/ch2_background.tex
Added some introduction to matching methods
Corrections
Fixed references
A few touches on the thesis

@@
 \chapter{Matching Local Image Features}
-\label{C:background}
+\label{C:Background}
 
@@
 an active field of research, illustrates an interesting notion: Making 
-computers solve tasks involving seeing turns out to be much harder than 
+computers solve tasks involving vision turns out to be much harder than 
 we would initially assume.
@@
 as humans are very good at. We can easily recognize objects under 
-different light, or stitch together photographies to a panorama, or 
-navigate a corridor identifying obstacles along the way. In fact these 
-things are so easy to us, that it seems strange that they should be 
-difficult at all, yet consistently recognizing an object under different 
-lighting conditions and from different angles can still cause problems 
-for even the best object recognition algorithms.
+different light, stitch together photographies to a panorama or navigate 
+a corridor identifying obstacles along the way. In fact these things are 
+so easy to us, that it seems strange that they should be difficult at 
+all, yet consistently recognizing an object under different lighting 
+conditions and from different angles can still cause problems for even 
+the best object recognition algorithms.
 
@@
 paper is from today, and then you sit down and put on your glasses to 
-read the headline. Try to imagine the newspaper as you see it on three 
-different stages. First as you enter the room, then as you turn after 
-turning on the light, now standing on the other side of the table, and 
-last when you are sitting with the paper in your hand after you put on 
-your glasses. For each of these stages, picture the situation as a 
-photography and look at how the newspaper changes as you move around. At 
-first you see it at an angle lying in a fairly dark and grey room, the 
-white pages reflecting the light from the window with a cold bluish hue 
-and the words too far away to make out. Then in the second stage with 
-light on, the object you are looking at has suddenly changed. When you 
-turned on the light in the room, you also changed the color of the 
-newspaper, which now has a warm and yellowy white color.  The angle you 
-are looking at the paper from has changed too, and the words and 
+read the headline. Try to imagine the newspaper as you see it at three 
+different stages. First as you enter the slightly obscure room, then as 
+you turn around after turning on the light, now standing on the other 
+side of the table, and finally when you are sitting with the paper in 
+your hands after you have put on your glasses. For each of these stages, 
+try to mentally picture the situation as a photography and look at how 
+the newspaper changes as you move around. At first you see it at an 
+angle lying in a fairly dark and grey room, the white pages reflecting 
+the light from the window with a cold bluish hue and the words too far 
+away to make out.  Then in the second stage with the lights turned on, 
+the object you are looking at has suddenly changed.  When you turned on 
+the light in the room, you also changed the color of the newspaper, 
+which now has a warm and yellowy white color to its pages.  The angle 
+you are looking at the paper from has changed too, and the words and 
 pictures are no longer upside down, although still slightly rotated and 
@@
 if you imagine taking a photography as you are sitting with the paper in 
-your hand, the newspaper will look much bigger almost taking up the 
+your hand, the newspaper will look much bigger, almost taking up the 
 entire frame. Now that your glasses are on, the words stand out much 
@@
 it changed in the process, from the color of the pages to the sharpness 
-of the lines. On top of that the paper has changed in size and rotation 
+of the lines. On top of that, the paper has changed in size and rotation 
 from lying on the table to being in your hand. In our daily lives we are 
 aided in the process of recognizing the paper by our memory and idea of 
-how the world works. When we walked in to the dark room and saw 
-something on the table, it was probably safe to assume that it was a 
-newspaper. Maybe the newspaper always lies like that on the table, or 
-maybe we left it there ourselves. Afterwards as we move around in the 
-room, we can safely assume that the paper didn't move and even if it 
-might not look exactly the same after we turned on the light, it's safe 
-to guess that nobody took the old newspaper and replaced it with a new 
-and yellower version.
+how the world works. When we went in to the dark room and saw something 
+on the table, it was probably safe to assume that it was a newspaper.  
+Maybe the newspaper always lies like that on the table, or maybe we left 
+it there ourselves. Afterwards when we move around in the room, we can 
+safely assume that the paper didn't move while our back is turned and 
+even if it might not look exactly the same after we turned on the light, 
+it's safe to guess that nobody took the old newspaper and replaced it 
+with a new and yellower version.
 
@@
 not be able to make the same assumptions about the world. We might just 
-give as input to the program to pictures of the newspaper. One from the 
+give as input to the program two pictures of the newspaper. One from the 
 first stage where the light was turned off, the paper was far away and 
@@
 taken of the same scene the two images could be taken on different days 
-under different conditions. The list continues and it should hopefully 
-be clear that in order to solve a lot of problems in computer vision, we 
+under different conditions. The list goes on and it should hopefully be 
+clear that in order to solve a lot of problems in computer vision, we 
 need a way to deal with these variations.
@@
 condition for finding a good feature point, they provide a good starting 
-point. Intuitively the simplest way to find corners would be to detect 
-edges in the image (for example using a high pass filter), and follow 
-these edges until they turn. Some of these approaches are detailed in 
-\cite{university1978comparison}.
+point.
 
-A different (and it turns out, better) approach is to look at the 
-gradient across the image and find spots where there is a gradient in 
-two perpendicular directions.  That is, along a dark edge on a bright 
-background there will be a gradient perpendicular to the edge, but no 
-gradient along the edge.  However in a corner we would have a gradient 
-in two different directions. The idea was originally introduced by 
-Morevec \cite{hans1977towards} and later improved upon by Harris and 
-Stephens who introduced what is now commonly known as the Harris corner 
-detector \cite{harris1988combined}.
+Intuitively the simplest way to find corners would be to detect edges in 
+the image (for example using a high pass filter), and follow these edges 
+until they turn. Some of these approaches are detailed in 
+\cite{university1978comparison}. A different (and it turns out, better) 
+approach is to look at the gradient across the image and find spots 
+where there is a gradient in two perpendicular directions.  That is, 
+along a dark edge on a bright background there will be a gradient 
+perpendicular to the edge, but no gradient along the edge.  However in a 
+corner we would have a gradient in two different directions. The idea 
+was originally introduced by Morevec \cite{hans1977towards} and later 
+improved upon by Harris and Stephens who introduced what is now commonly 
+known as the Harris corner detector \cite{harris1988combined}.
 
@@
 For a thorough review of the history of feature detectors, Tuytelaars 
-and Mikolajczyk presents an excellent historical retrospect in 
+and Mikolajczyk presents an excellent retrospect in 
 \cite{tuytelaars2008local}.
@@
 bin of the highest magnitude. The SIFT descriptor has been very widely 
-used since it's introduction and has become a de facto standard in 
+used since its introduction and has become a de facto standard in 
 computer vision. To enhance the computational time needed to compute 
@@
 comparisons were selected at random and tested against similar random 
-configurations using the configuration yielding the best result. The 
-simplicity of this method allows for real time matching of objects from 
-a video stream, something that would be too computationally tolling when 
-using a descriptor like SIFT\@. BRIEF however fails to be rotation 
-invariant making it less useful in cases where images are not 
-necessarily upright.
+configurations. They then went on to use the configuration yielding the 
+best result.  The simplicity of this method allows for real time 
+matching of objects from a video stream, something that would be too 
+computationally tolling when using a descriptor like SIFT\@. BRIEF 
+however fails to be rotation invariant making it less useful in cases 
+where images are not necessarily upright.
 
@@
 Most applications of feature points use them to match features across 
-different images. The standard out of the box way most feature points 
-are matched involve comparing the feature descriptor using some kind of 
-distance measure. If we match all features of one image with all 
-features of another and discard all matches that are below a certain 
-threshold of similarity, we have in essence a set of matches between the
+different images. The standard way most feature points are matched 
+involve comparing the feature descriptor using some kind of distance 
+measure. If we match all features of one image with all features of 
+another and discard all matches that are below a certain threshold of 
+similarity, we have in essence a set of matches between the
 two images. For most feature points (for example SIFT and SURF), this 
@@
 another. This allows for the filtering of all correspondences that do 
-not fall within paired areas. Examples include \emph{Isodata} 
+not fall within paired areas. Examples include \emph{Isomatch} 
 \cite{das2008event}, which clusters feature points according to their 
@@
 the image to filter correspondences is not possible, for example images 
-without overlap, or adjacent objects in one image are that are separated 
-in another. In these cases the assumptions behind the geometric 
-algorithms will often cause them to return incorrect matches.
+without much overlap, or adjacent objects in one image are that are 
+separated in another. In these cases the assumptions behind the 
+geometric algorithms will often cause them to return incorrect matches.
 
@@
 Of these three methods (fixed threshold, nearest neighbors, and 
-\emph{RATIO}), \emph{RATIO} was found to perform best by a slight margin 
+\emph{Ratio}), \emph{Ratio} was found to perform best by a slight margin 
 \cite{mikolajczyk2005performance}.

### 2013-08-13 text/main/ch3_matching_methods.tex
A few touches on the thesis

@@
 In this chapter we will describe the algorithms used in the experiements
-in detail. We start by introducing the proposed algorithms \emph{MM} and 
-\emph{MMC}, and continue with the reference algorithms used for 
-comparison, \emph{Ratio}, \emph{Spectral} and \emph{Isomatch}.
+in detail. We start by introducing the proposed algorithms \emph{Mirror 
+Match (MM)} and \emph{Mirror Match with Clustering (MMC)}, and continue 
+with the reference algorithms used for comparison, \emph{Ratio}, 
+\emph{Spectral} and \emph{Isomatch}.
 
@@
 \label{S:MatchingMethods}
+In this section we describe the two proposed algorithms for matching 
+feature points \emph{Mirror Match
+(MM)} and \emph{Mirror Match with Clustering (MMC)}.
 
@@
     (f) Example of a partition of feature points after clustering, which 
-includes similar feature points from building windows and shirt patterns.}%
+includes similar feature points from different sides of a building.}%
 	\label{fig:comparemirror}%
@@
 
-\begin{algorithm}[htb]
+\begin{algorithm}[t]
 \caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
@@
 \emph{Ratio} algorithm (\emph{RatioGet}).  For example in the case of 
-Figure~\ref{fig:pitts_partition}, we have feature points from a building 
-in one image grouped together with points from a shirt pattern in 
-another.  The nearest neighbor method would have returned wrong matches, 
-but since we match the partition with \emph{MM}, points in the building 
-end up matching other points in the building, and no matches are 
-returned.
+Figure~\ref{fig:pitts_partition}, we have several feature points from a 
+building in one image grouped together with points from the same 
+building in another image. If we try to match them globally, the 
+differences in similarities are two miniscule to confidently match, 
+because setting a threshold this high would lead to wrong matches 
+elsewhere, but if we only look at the group of feature points we can use 
+\emph{MM} with a much higher threshold and correctly match the points.
 
@@
 
-\begin{algorithm}[htb]
-\caption{Ratio Match (\emph{Ratio})}
-\label{alg-ratio}
-%{\fontsize{10}{10}\selectfont
-\begin{algorithmic}
-\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
-\State $matches\gets \varnothing$
-\State $features_1 \gets getFeatures(im_1)$
-\State $features_2 \gets getFeatures(im_2)$
-\ForAll{$f_i \in features_1$}
-    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
-    \State $ratio \gets d(f_i, f_m) / d(f_i, f_n)$
-	\If{$ratio < t$}
-        \State $matches \gets \left(f_i, f_m\right)$
-	\EndIf
-\EndFor
-\Return $matches$
-\end{algorithmic}
-%}
-\end{algorithm}
-
 \emph{Ratio} (Algorithm~\ref{alg-ratio}) \cite{lowe2004sift} diverges 
@@
 triangle inequality: $d(f_i,f_k) \leq d(f_i,f_j) + d(f_j,f_k)$.
+
+\begin{algorithm}[t]
+\caption{Ratio Match (\emph{Ratio})}
+\label{alg-ratio}
+%{\fontsize{10}{10}\selectfont
+\begin{algorithmic}
+\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
+\State $matches\gets \varnothing$
+\State $features_1 \gets getFeatures(im_1)$
+\State $features_2 \gets getFeatures(im_2)$
+\ForAll{$f_i \in features_1$}
+    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
+    \State $ratio \gets d(f_i, f_m) / d(f_i, f_n)$
+	\If{$ratio < t$}
+        \State $matches \gets \left(f_i, f_m\right)$
+	\EndIf
+\EndFor
+\Return $matches$
+\end{algorithmic}
+%}
+\end{algorithm}
 
@@
 
-The \emph{Spectral} algorithm (Algorithm~\ref{alg-spectral}) used in the 
-comparison of matching algorithms is based on the spectral matching 
-algorithm proposed by Leordeanu and Herbert 
+\emph{Spectral} (Algorithm~\ref{alg-spectral}) is based on the spectral 
+matching algorithm proposed by Leordeanu and Herbert 
 \cite{leordeanu2005spectral}.  The central idea behind it is that the 
@@
 matches where the association of the match with the optimal subset of 
-matches $T$ as measured by $x^{*}$ is above a certain threshold. For 
-experiments the set of initial matches were given by the best match per 
-feature point and the threshold was adjusted to allow for the best 50\% 
-to be included in the set of final matches. A rate less than 50\% 
-usually did not improve results, so to threshold the \emph{Spectral}
+matches, $T$, is above a certain threshold. For the experiments the set 
+of initial matches was given by the nearest neighbor of each feature 
+point and the threshold was adjusted to allow for the best 50\% to be 
+included in the set of final matches. A rate less than 50\% usually did 
+not improve results, so to threshold the \emph{Spectral}
 algorithm we filter the output using the ratio between first and second

### 2013-08-13 text/main/ch5_experiments.tex
A few touches on the thesis

@@
 superior to similar algorithms in the field, we will have to compare 
-them. In this chapter we will first describe exactly how we intent to 
-test the algorithms and then discuss the results of these comparisons.
+them with the state of the art. In this chapter we will first describe 
+exactly how we intent to compare the algorithms and then discuss the 
+results of these comparisons.
 
 \section{Experiments}
-For our ideal matching algorithm we would like it to return not only 
-correct matches but all possible correct matches when images overlap and 
-no matches at all when they don't.  We would like it to work flawlessly 
-not just one a few images but on all possible images, and we would 
-expect it to run fast even on when faced with tens of thousands of 
+For our ideal matching algorithm we would like it to return not just 
+some correct matches but all possible correct matches when images 
+overlap and no matches at all when they don't.  We would like it to work 
+flawlessly not just one a few images but on all possible images, and we 
+would expect it to run fast even on when faced with tens of thousands of 
 feature points.
@@
 These requirements fall in to three different categories. We want to 
-verify that the algorithm is \emph{accurate}, \emph{general} and 
+verify that the algorithm is \emph{general}, \emph{accurate} and 
 \emph{fast}.
-
-\subsection{Measuring Accuracy}
-
-To measure the accuracy of an algorithm we are interested in two values:
-Precision and Recall. These measures were introduced in \cite{ke2004pca}
-and later used in \cite{mikolajczyk2005performance}. Recall corresponds 
-to the number of correct matches over the total amount of possible 
-correct matches in between the two images:
-\begin{equation*}
-	recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~ 
-	Matches}
-\end{equation*}
-This measure tells us how thorough we are in finding all possible 
-matches that could be made between the two images. To decide whether a 
-match is correct, we use the following method:
-Given a potential match between two pixels $p_1$ and $p_2$, $m = 
-\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
-$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
-two points satisfy the following criteria:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
-\end{equation*}
-That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=5$ pixels here). To 
-count the number of possible matches we go over all possible 
-combinations of feature points between the two images, measure their 
-distance and count how many lie within the threshold.
-Precision on the other hand is measured by the amount of correct matches
-over the total amount of matches returned:
-\begin{equation*}
-	precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
-	~ \# ~ False ~ Matches}
-\end{equation*}
-This measures how accurate the set of returned matches from the 
-algorithm is. An algorithm that returns only a few matches out of many, 
-but most of them are correct will have a high precision and a low 
-recall, where as an algorithm that returns almost all possible matches, 
-both true and false will have a low precision but a high recall. The 
-ideal matching algorithm will be both precise but also return as many 
-correct matches as possible. However for many applications we only need 
-enough correct matches to align to the images, in which case we care 
-more about precision than recall.
 
@@
 To convincingly show that the algorithms work for general cases we need 
-to demonstrate good recall and precision across a wide range of images.  
-However if we are just given to images and a set of matches, there is no
+to demonstrate good results across a wide range of images.  However if 
+we are just given to images and a set of matches, there is no
 way to tell which matches are correct and which aren't without going 
-through them by hand and count them. For any but the simplest cases this
-becomes prohibitively time consuming.
+through the output by hand and for each match verify that it is correct.  
+For any but the simplest cases this becomes prohibitively time 
+consuming.
+
+\begin{figure}[tb]
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/homography_possible}
+        \caption{Homography possible}
+        \label{fig:hom_possible}
+    \end{subfigure}%
+        \quad %add desired spacing between images, e. g. ~, \quad, (or a 
+    %blank line to force the subfigure onto a new line)
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/homography_not_possible}
+        \caption{Homography not possible}
+        \label{fig:hom_impossible}
+    \end{subfigure}%
+    \caption{Example of images that can and cannot be tied with a 
+        homography: Figure~\ref{fig:hom_possible} shows an image pair 
+        that can be linked by a homography, since all common areas lie 
+        on a plane.  Figure~\ref{fig:hom_impossible} shows an image pair 
+        that can't reliably be linked by a homography. Even if we 
+        discount the change of people in the scence, the position of the 
+        bell compared to the building in the background changes as we 
+        change our viewpoint. Images in Figure~\ref{fig:hom_possible} 
+        are from the \emph{Murals} dataset while images in 
+        Figure~\ref{fig:hom_impossible} are from the Gallagher dataset 
+    \cite{gallagher2008}.}
+    \label{fig:homography_example}
+\end{figure}
 
@@
 image pairs that are linked by a homography. Two images linked by a 
-homography are tied by a change in perspective such that we given a 
-point in one image and the homography we can calculate the corresponding 
-position of the point in the other image. Not all image pairs can be 
-linked with a homography, something that is intuitive if we image two 
-pictures of a playing child. We can't predict the positions of the hands
-of the child in the second image with pixel precision just by knowing 
-the position of the hands in the first image. However for images where 
-all points are situated on a plane or where all the points are far away,
-a homography is usually sufficent to describe the pixel transformations 
-from one image to the next.
+homography are are related in a way that means that any point in the 
+first image can be translated a point in the second by a linear 
+equation. This holds true for two images where the points they have in 
+common are situated on a plan, or in the case that the camera only 
+rotated in between images. Figure~\ref{fig:homography_example} shows an 
+example of an image pair that can be linked with a homography and 
+another that cannot. In the second image pair, the change in camera 
+position means that pixels can't be linearly translated from one image 
+to another. For example would a pixel on the bell be translated to one 
+location while an adjacent pixel on the building in the background would
+move differently. For this reason we are constrained in which images 
+it's possible to test the algorithms on since we cannot evaluate the 
+results if the images are not tied by a homography.
 
@@
 
-\begin{figure}[htb]
-    \makebox[1.0\textwidth][c]{%
+\begin{figure}[b]
     \begin{subfigure}[t]{0.102\textwidth}
@@
         \includegraphics[width=\textwidth]{images/pair_example1}
-			\label{fig:fairey1}
     \end{subfigure}%
@@
         \includegraphics[width=\textwidth]{images/pair_example2}
-			\label{fig:fairey2}
     \end{subfigure}%
@@
     \end{subfigure}%
-	}%
     \caption{Sample test patches produced from an image pair.}
@@
 
-\begin{figure}[htb]
+\begin{figure}[tb]
 	\centering
@@
 
+\subsection{Measuring Accuracy}
+
+To measure the accuracy of an algorithm we are interested in two values:
+Precision and Recall. These measures were introduced in \cite{ke2004pca}
+and later used in \cite{mikolajczyk2005performance}. Recall corresponds 
+to the number of correct matches over the total amount of possible 
+correct matches in between the two images:
+\begin{equation*}
+	recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~ 
+	Matches}
+\end{equation*}
+This measure tells us how thorough we are in finding all possible 
+matches that could be made between the two images. To decide whether a 
+match is correct, we use the following method:
+Given a potential match between two pixels $p_1$ and $p_2$, $m = 
+\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
+$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
+two points satisfy the following criteria:
+\begin{equation*}
+\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
+\end{equation*}
+That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
+\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
+less than a certain threshold (we use $d_{\max}=5$ pixels here). To 
+count the number of possible matches we go over all possible 
+combinations of feature points between the two images, measure their 
+distance and count how many lie within the threshold.
+Precision on the other hand is measured by the amount of correct matches
+over the total amount of matches returned:
+\begin{equation*}
+	precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
+	~ \# ~ False ~ Matches}
+\end{equation*}
+This measures how accurate the set of returned matches from the 
+algorithm is. An algorithm that returns only a few matches out of many, 
+but most of them are correct will have a high precision and a low 
+recall, where as an algorithm that returns almost all possible matches, 
+both true and false will have a low precision but a high recall. The 
+ideal matching algorithm will be both precise but also return as many 
+correct matches as possible. However for many applications we only need 
+enough correct matches to align to the images, in which case we care 
+more about precision than recall.
+
 \subsection{Measuring Speed}
@@
 as the computational complexity of the algorithms.
+
+\begin{figure}[t]
+	\begin{subfigure}[c]{0.2\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/graf}
+	\end{subfigure}%
+	~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
+	%(or a blank line to force the subfigure onto a new line)
+	\begin{subfigure}[c]{0.8\textwidth}
+	\centering
+	\includegraphics[width=\columnwidth]{images/result_graf}
+	%\caption{Performance on Scharf}
+	\end{subfigure}%
+	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The 
+	plot shows the result of 100 patch pairs generated from the source 
+	images shown to the left. The x-axis shows the recall based on the 
+accumulated amount of potential matches for all 100 patch pairs. }
+	\label{fig:result_graf}
+\end{figure}
 
@@
 
-\begin{figure}[htb]
-	\begin{subfigure}[c]{0.2\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/graf}
-	\end{subfigure}%
-	~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-	%(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}[c]{0.8\textwidth}
-	\centering
-	\includegraphics[width=\columnwidth]{images/result_graf}
-	%\caption{Performance on Scharf}
-	\end{subfigure}%
-	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The 
-	plot shows the result of 100 patch pairs generated from the source 
-	images shown to the left. The x-axis shows the recall based on the 
-accumulated amount of potential matches for all 100 patch pairs. }
-	\label{fig:result_graf}
-\end{figure}
-
 To validate whether these results generalize to other images, we tested 
@@
 
-To further investigate the impact of viewpoint changes, we tested the 
-algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
-contains 5 images of the same mural taken with gradually increasing 
-viewpoint changes.  The first images are almost identical, while the 
-last are taken from very different angles. The results from   \emph{MMC} 
-and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
-viewpoint changes.
-The performance of \emph{MM} (not shown in the plot) is similar to 
-\emph{MMC}.
-
 \begin{figure}[htb]
@@
 
+To further investigate the impact of viewpoint changes, we tested the 
+algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
+contains 5 images of the same mural taken with gradually increasing 
+viewpoint changes.  The first images are almost identical, while the 
+last are taken from increasingly different angles. The results from   
+\emph{MMC} and \emph{Ratio} as shown in 
+Figure~\ref{fig:result_viewpoint}, confirm that \emph{MMC} is generally 
+superior to \emph{Ratio} across viewpoint changes. For both methods 
+however we see a stark decrease in recall as the viewpoint change 
+increases. The performance of \emph{MM} (not shown in the plot) is 
+similar to \emph{MMC}.
+
 In order to investigate whether a geometric algorithm can be improved by
@@
 similar recall rates, illustrating how a geometric algorithm can be 
-complemented by a reliable non-geometric pruning of matches.
+complemented by a reliable non-geometric selection of matches.
 
@@
 
-In terms of computational complexity, \emph{Ratio}, \emph{MM}, and 
-\emph{Isomatch} can be implemented in $O(n\log n)$, where $n$ is the 
-total number of feature points. The performance of \emph{Spectral} is 
-upper bounded by $O(n^{3/2})$. Our current \emph{MMC} implementation has 
-a complexity of $O(n^2)$ due to the construction of a similarity matrix 
-of the feature points.  However, it is possible to approximate this in 
-$O(n\log n)$ using search trees.
-
-As for speed, Table~\ref{table:running_times} shows the running time of 
-the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
-These numbers should be taken with a grain of salt, given that much of 
-the code behind \emph{MMC} and \emph{Isomatch} is implemented in Python, 
-whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
-computationally intensive operations in C++, which makes them much 
-faster.
-
 \begin{table}[htb]
@@
 \end{table}
+In terms of computational complexity, \emph{Ratio}, \emph{MM}, and 
+\emph{Isomatch} can be implemented in $O(n\log n)$, where $n$ is the 
+total number of feature points. The performance of \emph{Spectral} is 
+upper bounded by $O(n^{3/2})$. Our current \emph{MMC} implementation has 
+a complexity of $O(n^2)$ due to the construction of a similarity matrix 
+of the feature points.  However, it is possible to approximate this in 
+$O(n\log n)$ using search trees.
+
+As for speed, Table~\ref{table:running_times} shows the running time of 
+the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
+These numbers should be taken with a grain of salt, given that much of 
+the code behind \emph{MMC} and \emph{Isomatch} is implemented in Python, 
+whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
+computationally intensive operations in C++, which makes them much 
+faster.

### 2013-08-13 text/main/ch6_applications.tex
Updated thesis with spectral-mmc info and better figures
Fixed references
A few touches on the thesis

@@
 \chapter{Applications}
+\label{C:Applications}
 
@@
 matching images that might or might not overlap. These cases requires 
-matching algorithms that limit false positives since e.g. returning the 
-top $n$ matches for any given image pair would make it hard to 
+matching algorithms that limit false positives since the alternative 
+would be to select the top $n$ matches which would make it hard to 
 distinguish adjacent or duplicate images from non-adjacent or dissimilar
@@
 
-\subsection{Panorama Recognition and Alignment}
+\section{Panorama Recognition and Alignment}
 One of the oldest practical problems approached in computer vision is 
@@
 	\end{subfigure}%
-    \label{fig:pano_example}
     \caption{An example of a difficult case for panorama recognition and 
@@
 correctly linked}
+    \label{fig:pano_example}
 \end{figure}
@@
 
-\subsection{Near Duplicate Detection}
+\section{Near Duplicate Detection}
 If we look at two images, we can often easily tell if one image 
@@
 settings. Facing these challenges, a lot of work has been done trying to 
-reliably recognize duplicaes both with regards to corporate intellectual 
-property as well as consumer photo albums because both applications 
-provide useful tools.  A company might be interested in finding images 
-that are derived from their intellectual property, while consumers 
-taking vacation photos might be interested in grouping duplicate images 
-to allow for easier photo organization.
+reliably recognize duplicates both with regards to corporate 
+intellectual property as well as consumer photo albums because both 
+applications provide useful tools.  A company might be interested in 
+finding images that are derived from their intellectual property, while 
+consumers taking vacation photos might be interested in grouping 
+duplicate images to allow for easier photo organization.
+
+\begin{figure}[h]
+	\includegraphics[width=\textwidth]{images/near_duplicate_example}
+	\caption{Example of a near duplicate image pair from the 
+	California-nd dataset \cite{jinda2012california}}
+	\label{fig:near_duplicate}
+\end{figure}
 
@@
 product. \emph{PhotoCluster} works by grouping images in several steps 
-using first image metadata and global features to obtain a set of 
+using first image meta data and global features to obtain a set of 
 proposed clusters. Then local features are used to find the best 
@@
 
-The results of the comparison can be seen in Table~\ref{table:nnd}. It 
+The results of the comparison can be seen in Table~\ref{table:ndd}. It 
 shows that \emph{MMC} improves performance by 8.05\% over the original 

### 2013-08-14 text/main/ch6_applications.tex
Added a few references to applications

@@
 methods relied on minimizing pixel dissimilarities in overlapping images
-while more recent methods have used local feature points to estimate the 
-correct image alignment. Using local feature points carry the additional 
-advantage that it is feasible to automatically recognize where each 
-source image belong in the final panorama.
+(\cite{shum1997panoramic}, \cite{szeliski1995direct}) while more recent 
+methods have used local feature points to estimate the correct image 
+alignment (\cite{mclauchlan2002image}, \cite{capel1998automated}, 
+\cite{brown2007automatic}).  Using local feature points carry the 
+additional advantage that it is feasible to automatically recognize 
+where each source image belong in the final panorama.
 
@@
 the images are combined in an order corresponding to how many matches 
-connect them, as done by Brown and Lowe \cite{brown2007automatic}.
+connect them, as done by Brown and Lowe \cite{brown2007automatic}. That 
+is, homographies are estimated between all images with sufficient 
+feature point matches in between them as returned by \emph{MMC}. Then 
+the images are stitched together starting with the image pair having the 
+highest amount of matches, and continuing in a decrease order of 
+matches.
 
@@
 provides a way to globally optimize the accuracy of the image alignment} 
-and a lot of image enhancements such as exposure adjustment and edge 
+and various image enhancements such as exposure adjustment and edge 
 blurring to provide a seamless panorama. While these additions improve 
-the end product, they don't influence the performance of panorama 
-alignment and recognition and haven't been included in the simple 
-comparison algorithm.
+the end product, they don't influence the performance of the alignment 
+and recognition parts of panorama stitching and for this reason haven't 
+been included in the simple comparison algorithm.
 
 Figure~\ref{fig:pano_example} shows an example where the added accuracy 
-of MMC enables us to correctly recognitize and align source images that 
+of MMC enables us to correctly recognize and align source images that 
 fail to be combined by Autostitch, a program using the algorithm 
@@
 resembles the other enough to be redundant in a photo album. In computer 
-vision this task becomes a lot less trivial because our idea of a 
-duplicate image might only require there being some object or scene in 
-common between the image pair. In addition the object or scene might 
-have been taken from a different angle and under different camera 
-settings. Facing these challenges, a lot of work has been done trying to 
-reliably recognize duplicates both with regards to corporate 
-intellectual property as well as consumer photo albums because both 
-applications provide useful tools.  A company might be interested in 
-finding images that are derived from their intellectual property, while 
-consumers taking vacation photos might be interested in grouping 
-duplicate images to allow for easier photo organization.
+vision this task is nontrivial because our idea of a duplicate image 
+might only require there being some object or scene in common between 
+the image pair. In addition the object or scene might have been taken 
+from a different angle and under different camera settings. Facing these 
+challenges, work has been done trying to reliably recognize duplicates 
+both with regards to corporate intellectual property as well as consumer 
+photo albums.  A company might be interested in finding images that are 
+derived from their intellectual property, while it allows consumers 
+taking vacation photos to automatically grouping duplicate images which 
+allows for easier photo organization.
 
@@
 matching images in these proposed clusters yielding the final groups of 
-near duplicate images. To show the viability of \emph{MMC} in the 
-application of near duplicated detection, we modify the PhotoCluster 
-method to use \emph{MMC} for matching images instead of \emph{Ratio} 
-which was previously used. Due to the time consumption of \emph{MMC}, 
-all images where resized to to 10\% before being compared. Outside of 
-that, the experiments were performed exactly as documented in 
-\cite{vas2013cluster}.
+near duplicate images. To show the viability of \emph{MM} and \emph{MMC} 
+in the application of near duplicated detection, we modify the 
+PhotoCluster method to use the proposed algorithms for matching images 
+instead of \emph{Ratio} which was previously used. The experiments were 
+performed as documented in \cite{vas2013cluster}, however due to the 
+running time of \emph{MMC} it is intractable to calculate the test 
+scores on full scale images. To showcase the performance of \emph{MMC} 
+we add a test case using images resizes to 10\% of their original size.
 
 \begin{table}[htb]
-\caption{Results from Near Duplicate Detection at 10\% scale}
+\caption{Results from Near Duplicate Detection}
 \label{table:ndd}
@@
 %	\small
-\begin{tabular}{r*{2}{r}}
+\begin{tabular}{r*{3}{r}}
 \hline
-    Method: & Ratio & MMC   \\
+F1 score & \emph{Ratio} & \emph{MM} & \emph{MMC}   \\
 	\noalign{\smallskip}
 	%
-    F1 score: & 0.4654 & 0.5459 \\
+    10\% Scale: & 0.5013 & 0.5990 & 0.5785 \\
+    100\% Scale: & 0.0 & 0.0 & --- \\
 	\hline
@@
 The results of the comparison can be seen in Table~\ref{table:ndd}. It 
-shows that \emph{MMC} improves performance by 8.05\% over the original 
-framework using \emph{Ratio} to match images. For comparison, the 
-performance improvement of \emph{PhotoCluster} compared to XMatch 
+shows that \emph{MM} improves performance by 19.49\% over the original 
+framework using \emph{Ratio} to match images. For comparison 
+\emph{PhotoCluster} improves on the results of Xmatch 
 \cite{zhao2009scale}, the second best performing algorithm on the 
-California-nd dataset according to \cite{vas2013cluster}, is 2.52\%.
+California-nd dataset according to \cite{vas2013cluster}, with 2.52\%.

### 2013-08-15 text/head/abstracts.tex
Corrections

@@
 increase the robustness of the matching. However, very little work 
-addresses the case where these assumptions might not hold. In particular 
-few methods address the problem of reliable matching in cases where it 
-is unknown whether two images have any corresponding areas or objects in 
-the first place.  \\
+addresses the cases where these assumptions might not hold. In 
+particular, few methods address the problem of reliable matching in 
+cases where it is unknown whether two images have any corresponding 
+areas or objects in the first place.  \\
 
 We propose two algorithms for matching feature points without the use of 
-geometric constraints. The first relies on the fact that any match 
+geometric constraints. The first relies on the idea that any match 
 between two images should be better than all possible matches within a 
-single image. The second algorithm extends this idea by using community 
-structure in the similarity graph of feature points to find reliable 
-correspondences. To evaluate the algorithms experimentally, we introduce 
-a simple method to generate a large amount of test cases based on a set 
-of image pairs with viewpoint changes. Our results show that the 
-proposed algorithm is generally superior to traditional approaches in 
-finding correct correspondences.
+single image. The second algorithm extends this idea by using the 
+community structure in the similarity graph of feature points to find 
+reliable correspondences. To evaluate the algorithms experimentally, we 
+introduce a simple method to generate a large number of test cases based 
+on a set of image pairs with viewpoint changes. Our results show that 
+the proposed algorithm is generally superior to traditional approaches 
+in finding correct correspondences.

### 2013-08-15 text/main/ch1_introduction.tex
Corrections

@@
 
-My goal when I started working on this thesis was not to improve feature 
-point matching, but via a series of detours I ended up circling the 
-problem which I found alluring, not just because it its importance, but 
-also because of its inherent simplicity. Out of two sets, finding pairs 
-of similar elements seems like a problem that should have been solved 
-long ago, yet because of the nature of feature points and the data they 
-are used on, there seems to be plenty of progress to be made still.
+My original goal when I started working on this thesis was not to 
+improve feature point matching. I started out working on face 
+clustering, but via a series of detours I ended up circling the problem,
+which I found alluring not just because it its importance, but also 
+because of its inherent simplicity.  Out of two sets, finding pairs of 
+similar elements seems like a problem that should have been solved long 
+ago, yet because of the nature of feature points and the data they are 
+used on, there still seems to be plenty of progress to be made.
 
@@
 correspondences.  The goal of this thesis will be to describe these 
-algorithms and convincingly demonstrate that they outperform traditional 
+algorithms and convincingly demonstrate that they outperform existing 
 approaches.  While doing this I hope to provide sufficient background 
-for a technically minded reader without any necessary experience in 
+for a technically-minded reader without any necessary experience in 
 computer vision to follow the motivation behind \emph{MM} and \emph{MMC} 
-and enable him or her to place both algorithms in a bigger scientific 
-perspective.
+and enable him or her to understand both algorithms within a bigger 
+scientific perspective.
 
@@
 background and motivation for the development of \emph{MM} and 
-\emph{MMC}. The chapter serves two purposes.  For those that might be 
+\emph{MMC}. The chapter serves two purposes:  For those who might be 
 reading this introduction wondering what a feature point really is and 
-how it is matched, it provides a gentle introduction to the why's and 
-how's of feature point matching. At the same time the chapter is meant 
+how it is matched, it provides a gentle introduction to the hows and 
+whys of feature point matching. At the same time, the chapter is meant 
 as an introduction to related work which is hopefully useful for those 
 who might use this thesis as a starting point for finding other research 
-on the same subject. Chapter~\ref{C:Algorithms} will introduce in detail 
-the algorithms proposed in this thesis. The reference algorithms used to 
+on the same subject. Chapter~\ref{C:Algorithms} introduces in detail the 
+algorithms proposed in this thesis. The reference algorithms used to 
 benchmark \emph{MM} and \emph{MMC} are also introduced in detail.  
-Chapter~\ref{C:Experiments} details the experiments done to evaluate the 
-proposed algorithms both in terms of how they were conducted as well as 
-their results. Chapter~\ref{C:Applications} provides two examples of how 
-the matching algorithms can improve on panorama stitching and near 
-duplicate matching.
+Chapter~\ref{C:Experiments} details both the setup and results of the 
+experiments done to evaluate the proposed algorithms. 
+Chapter~\ref{C:Applications} provides two examples of how the matching 
+algorithms can improve on panorama stitching and near duplicate 
+matching.
 
 For the remainder of the thesis I will make use of the academic 
-'\emph{we}' to underline the fact this thesis had not been possible had 
-it not been for the guidance of \emph{Stefan Winkler} and \emph{Sabine 
-S\"usstrunk} as well as the support of \emph{Advanced Digital Science 
-Center} in Singapore that hosted me as an intern during the work on this 
-thesis.
+'\emph{we}' to underline the fact this thesis would not have been 
+possible had it not been for the guidance of \emph{Stefan Winkler} and 
+\emph{Sabine S\"usstrunk} as well as the support of \emph{Advanced 
+Digital Science Center} in Singapore, which hosted me as an intern 
+during the term in which I worked on this thesis.

### 2013-08-15 text/main/ch2_background.tex
Corrections

@@
 
-In this chapter we will introduce local feature points in images and 
-explain how they are used. We will start out by discussing why we need 
-local features in the first place before looking at the inner workings 
-of modern local image features. Finally we will look at how they are 
-used, in particular how corresponding pairs are found in between two or 
-more images.
+In this chapter we introduce the concept of local feature points in 
+images and explain how they are used. We will start out by discussing 
+the significance of local features in the first place before looking at 
+the inner workings of modern local image features. Finally we will look 
+at how they are used, in particular in terms of matching corresponding 
+points between two or more images.
 
@@
 The field of computer vision is anecdotally said to have been founded 
-when Marvin Minsky assigned the problem of making a computer see as an 
+when Marvin Minsky assigned the task of making a computer see as an 
 undergraduate summer project back in 1966\footnote{This is the same 
@@
 adviser on Kubrick's movie \emph{Space Odyssey 2001}}.  Whether or not 
-the anecdote is true, the idea that the field of computer vision should 
-be solvable in a summer's worth of time but still to this days remains 
-an active field of research, illustrates an interesting notion: Making 
-computers solve tasks involving vision turns out to be much harder than 
-we would initially assume.
+the anecdote is true, the fact remains that what was assigned as a 
+summer's worth of work remains to this day an active field of research, 
+which illustrates an interesting notion: Making computers solve tasks 
+involving vision turns out to be much harder than we would initially 
+assume.
 
-Part of this notion stems from the fact that vision is a problem that we 
-as humans are very good at. We can easily recognize objects under 
-different light, stitch together photographies to a panorama or navigate 
-a corridor identifying obstacles along the way. In fact these things are 
-so easy to us, that it seems strange that they should be difficult at 
-all, yet consistently recognizing an object under different lighting 
-conditions and from different angles can still cause problems for even 
-the best object recognition algorithms.
+Part of this notion of simplicity stems from the fact that vision is a 
+task that we as humans are very good at. We can easily recognize objects 
+under different light, stitch various perspectvies into a panorama or 
+navigate a corridor identifying obstacles along the way.  In fact, these 
+things are so easy to us, that it seems strange that they should be 
+difficult at all; yet consistently recognizing an object under different 
+lighting conditions and from different angles can still cause problems 
+for even the best object recognition algorithms.
 
@@
 read the headline. Try to imagine the newspaper as you see it at three 
-different stages. First as you enter the slightly obscure room, then as 
+different stages. First as you enter the slightly obscure room. Then as 
 you turn around after turning on the light, now standing on the other 
-side of the table, and finally when you are sitting with the paper in 
+side of the table; and finally when you are sitting with the paper in 
 your hands after you have put on your glasses. For each of these stages, 
@@
 of the lines. On top of that, the paper has changed in size and rotation 
-from lying on the table to being in your hand. In our daily lives we are 
-aided in the process of recognizing the paper by our memory and idea of 
-how the world works. When we went in to the dark room and saw something 
-on the table, it was probably safe to assume that it was a newspaper.  
-Maybe the newspaper always lies like that on the table, or maybe we left 
-it there ourselves. Afterwards when we move around in the room, we can 
-safely assume that the paper didn't move while our back is turned and 
-even if it might not look exactly the same after we turned on the light, 
-it's safe to guess that nobody took the old newspaper and replaced it 
-with a new and yellower version.
+from lying on the table to being in your hand.
+
+In our daily lives we are aided in the process of recognizing the paper 
+by our memory and idea of how the world works. When we went in to the 
+dark room and saw something on the table, it was probably safe to assume 
+that it was a newspaper.  Maybe the newspaper always lies like that on 
+the table, or maybe we left it there ourselves. Afterwards when we move 
+around in the room, we can safely assume that the paper didn't move 
+while our back is turned and even if it might not look exactly the same 
+after we turned on the light, it is reasonable to guess that nobody took 
+the old newspaper and replaced it with a new and yellower version.
 
@@
 
-For this two work we need two components. First we need to find spots in 
+For this to work we need two components. First we need to find spots in 
 an image that are distinct, since if we have similar points we can't 
@@
 Intuitively the simplest way to find corners would be to detect edges in 
-the image (for example using a high pass filter), and follow these edges 
+the image (for example using a high-pass filter), and follow these edges 
 until they turn. Some of these approaches are detailed in 
@@
 improved upon by Harris and Stephens who introduced what is now commonly 
-known as the Harris corner detector \cite{harris1988combined}.
+known as the Harris corner detector \cite{harris1988combined} building 
+on the idea.
 
@@
 intensity difference as proposed by Smith and Brady 
-\cite{smith1997susan} as the SUSAN edge detector. Lepetit and Fua 
-proposed a similar algorithm but only looking at the pixels on the 
-circumference of a circle surrounding the point 
+\cite{smith1997susan} in their SUSAN edge detector. Lepetit and Fua 
+proposed a similar algorithm which only took in to account the pixels on 
+the circumference of a circle surrounding the point 
 \cite{lepetit2006keypoint}. This is also the central idea behind the 
@@
 neighborhood, but this would not be very flexible. Take the case where 
-we take two images of the same scene, but overexpose one of them. Two 
+we take two images of the same scene but overexpose one of them. Two 
 corresponding feature points would not look remotely alike in this case.
@@
 pixels surrounding the key point. This way we would get the same 
-descriptor now matter how the image is rotated. To a certain extend this
-method is also invariant to affine transformations, that is change in 
-perspective as long as approximately the same pixels fall within the 
-zone we are taking a histogram of. If we use the raw values of the 
-pixels, the descriptor is still not invariant with respect to 
-brightness, but this is easily solved by creating a histogram of the 
-pixel values relative to the center pixel. Lazebnik et al.\ introduced 
-this method in \cite{lazebnik2003sparse} adding the distance from the 
-key point as another dimension in the histogram.
+descriptor no matter how the image is rotated. To a certain extent this
+method is also invariant to changes in perspective as long as 
+approximately the same pixels fall within the zone we are taking a 
+histogram of. If we use the raw values of the pixels, the descriptor is 
+still not invariant with respect to brightness, but this is easily 
+solved by creating a histogram of the pixel values relative to the pixel 
+at the center of the feature point.  Lazebnik et al.\ introduced this 
+method in \cite{lazebnik2003sparse} adding the distance from the key 
+point as another dimension in the histogram.
 
@@
 gradients surrounding the feature point as Lowe did in his Scale 
-Invariant Feature Detector (SIFT) \cite{lowe2004sift}. The histogram he 
-proposes is based on the gradient locations and orientations weighted by
+Invariant Feature Detector (\emph{SIFT}) \cite{lowe2004sift}. The 
+histogram he proposes is based on the gradient locations and 
+orientations weighted by
 the gradient magnitude. To make sure that the histogram is rotation 
 invariant, the bins of the histogram are normalized and start with the 
-bin of the highest magnitude. The SIFT descriptor has been very widely 
-used since its introduction and has become a de facto standard in 
+bin of the highest magnitude. The \emph{SIFT} descriptor has been very 
+widely used since its introduction and has become a de facto standard in 
 computer vision. To enhance the computational time needed to compute 
@@
 (SURF) that rely on a histogram of wavelets instead of gradients as used 
-in SIFT \cite{bay2006surf}.
+in \emph{SIFT} \cite{bay2006surf}.
 
@@
 a feature descriptor, Binary Robust Independent Elementary Features 
-(BRIEF), based on this idea. The main advantage of their approach is 
-reduced processing and memory needed to create, store and match the 
-feature descriptors. Interestingly the positions used for pixel wise 
+(\emph{BRIEF}), based on this idea. The main advantage of their approach 
+is the reduced processing and memory needed to create, store and match 
+the feature descriptors. Interestingly the positions used for pixel wise 
 comparisons were selected at random and tested against similar random 
 configurations. They then went on to use the configuration yielding the 
-best result.  The simplicity of this method allows for real time 
-matching of objects from a video stream, something that would be too 
-computationally tolling when using a descriptor like SIFT\@. BRIEF 
-however fails to be rotation invariant making it less useful in cases 
-where images are not necessarily upright.
+best result as tested on a series of images. \emph{BRIEF} however is not 
+rotation invariant making it less useful in cases where images are not 
+necessarily upright.
 
@@
 different images. The standard way most feature points are matched 
-involve comparing the feature descriptor using some kind of distance 
-measure. If we match all features of one image with all features of 
-another and discard all matches that are below a certain threshold of 
-similarity, we have in essence a set of matches between the
-two images. For most feature points (for example SIFT and SURF), this 
-similarity is measured by the cosine similarity. Binary descriptors such
-as BRIEF can take advantage of the faster computation of the hamming 
-distance.
+involve finding the distance between any two feature descriptors. If we 
+match all features of one image with all features of another and discard 
+all matches that are futher apart than some threshold distance, we have 
+in essence a filtered set of matches between the two images. For most 
+feature points (for example \emph{SIFT} and \emph{SURF}), this distance 
+is measured by their cosine similarity. Binary descriptors such
+as \emph{BRIEF} can take advantage of the faster computation of the 
+hamming distance.
 
@@
 methods make use of the knowledge of the position of the keypoints in 
-the image, i.e.\ the geometrical meta data. Using this information can 
+the image, i.e.\ the geometrical metadata. Using this information can 
 often yield more accurate outcomes, but they inevitably make assumptions
@@
 too much with respect to the average angle and distancen as considered 
-by \cite{kim2008efficient}.  This performs well in situations where no 
-camera rotation occurs between the two images, but fails when this 
-assumption isn't met. Various scenarios have been proposed to improve on 
-this simple assumption such as epipolar constraints 
+by \cite{kim2008efficient}.  This method performs well in situations 
+where no camera rotation occurs between the two images, but fails when 
+this assumption isn't met. Various scenarios have been proposed to 
+improve on this simple assumption such as epipolar constraints 
 (\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
@@
 the assumption that the two images matched are related by an affine 
-transformation.  That is, that there is no relative movement of objects 
-in between images and either the viewpoint is fixed or the image resides 
+transformation.  That is; there is no relative movement of objects in 
+between images and either the viewpoint is fixed or the image resides 
 entirely on a plane.  In practice this assumption largely holds true 
-when all objects we are interested in matching are roughly the same 
-distance from the camera given that objects don't move across images.  
-Pairwise constraints provide a more robust approach to the same problem 
-by looking at a set of proposed correspondences and defining a pairwise 
-error between any two matches for example based on the assumption that 
-two neighboring correspondences will usually have similar angles and 
-distances. This approach provides more robustness in cases where 
-assumptions that are violated globally still hold on a local scale.
+when all objects we are interested in matching are roughly at the same 
+distance from the camera given that objects stay fixed from one image to 
+another.  Pairwise constraints provide a more robust approach to the 
+same problem by looking at a set of proposed correspondences and 
+defining a pairwise error between any two matches for example based on 
+the assumption that two neighboring correspondences will usually have 
+similar angles and distances. This approach provides more robustness in 
+cases where assumptions that are violated globally still hold on a local 
+scale.
 
@@
 \cite{das2008event}, which clusters feature points according to their 
-position in the image, and the method from \cite{wu2011robust}, which 
-uses maximally stable extremal regions (MSER) feature points to 
-designate areas.
+position in the image, and the matching method from \cite{wu2011robust}, 
+which uses Maximally Stable Extremal Regions (\emph{MSER}) feature 
+points to designate areas.
 
@@
 given threshold of similarity.  This can be done with a fixed threshold 
-or by finding the nearest neighbors for each point (still filtering by a 
-threshold to avoid including matches for feature points that have no 
-counterpart in the other image).  When Lowe \cite{lowe2004sift} proposed 
-the scale-invariant feature transform he included an alternative 
-matching measure. Instead of rating matching by similarity assessed the 
-uniqueness of a given match by looking at the two nearest neighbors of 
-each feature point and calculating the matching score as the ratio of 
-similarities. This method will later be referred to as \emph{Ratio}.  
-Ranking the scores by their uniqueness and picking the $n$ best produces 
-a set of correspondences that are distinctly matched across two images.  
-Of these three methods (fixed threshold, nearest neighbors, and 
-\emph{Ratio}), \emph{Ratio} was found to perform best by a slight margin 
-\cite{mikolajczyk2005performance}.
+or by finding the nearest neighbors for each point while still filtering 
+by a threshold to avoid including matches for feature points that have 
+no counterpart in the other image.  When Lowe \cite{lowe2004sift} 
+proposed the scale-invariant feature transform he included an 
+alternative matching measure. Instead of rating matching by similarity 
+he assessed the uniqueness of a given match by looking at the two 
+nearest neighbors of each feature point and calculating the matching 
+score as the ratio of similarities. This method will later be referred 
+to as \emph{Ratio}.  Lowe ranks the scores by their uniqueness and picks 
+the $n$ best ones, which yields a set of correspondences that are 
+distinctly matched across two images.  Of these three methods (fixed 
+threshold, nearest neighbors, and \emph{Ratio}), \emph{Ratio} was found 
+to perform best by a slight margin \cite{mikolajczyk2005performance}.
 
@@
 partition.  The experimental results show that both approaches generally 
-outperform existing correspondence matching methods.
+outperform existing matching methods.

### 2013-08-15 text/main/ch3_matching_methods.tex
Corrections

@@
 in detail. We start by introducing the proposed algorithms \emph{Mirror 
-Match (MM)} and \emph{Mirror Match with Clustering (MMC)}, and continue 
-with the reference algorithms used for comparison, \emph{Ratio}, 
+Match (MM)} and \emph{Mirror Match with Clustering (MMC)} and continue 
+with the reference algorithms used later for comparison, \emph{Ratio}, 
 \emph{Spectral} and \emph{Isomatch}.
@@
         \end{subfigure}%
-	\caption{Feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-	(c) Result of \emph{Ratio} matching. 
-  (d) All matches found by \emph{MM}, including intra-image matches. 
-	(e) Final \emph{MM} result. 
-    (f) Example of a partition of feature points after clustering, which 
-includes similar feature points from different sides of a building.}%
+    \caption{Feature matching with \emph{MM} and \emph{MMC}. Dots 
+        represent feature points; green/red lines indicate 
+        correct/incorrect matches, respectively; black lines represent 
+        edges in the feature graph.  (c) Result of \emph{Ratio} 
+        matching.  (d) All matches found by \emph{MM}, including 
+        intra-image matches.  (e) Final \emph{MM} result.  (f) Example 
+    of a graph partition of feature points after clustering in 
+\emph{MMC}, which includes similar feature points from different sides 
+of a building.}%
     \label{fig:comparemirror}%
@@
 The central idea behind \emph{MM} is to match features of $n$ images by 
-taking every feature from all $n$ images and matching it against every 
-other feature from the same set. We can then discard the correspondences 
+taking every feature from all $n$ images and matching them against every 
+other feature from the same set. We then discard the correspondences 
 that match two points within the same image. Algorithm~\ref{alg-mm} 
@@
 designed to make use of any feature extractor in particular, but for the
-experiments (Chapter~\ref{C:Experiments}) the SIFT feature extractor and
-descriptor has been used. In the \emph{matching} stage these features 
-are matched using $k$-nearest neighbors.  The distance function $d(f_i, 
-f_j)$ between features is calculated according to the feature 
-descriptor. For SIFT we use the cosine similarity between the two 
-descriptor vectors, while other descriptors might use other 
-measures\footnote{BRIEF for example uses the hamming measure to speed up 
-the computation}.  For any given feature $f_i$ the two closest neighbors 
-are returned, and we calculate the ratio between them as proposed in 
-\cite{lowe2004sift}\footnote{In Part~\ref{ss:ratio} this calculation and 
-other details of \emph{Ratio} will be discussed}.  Any correspondence 
-with a ratio above the threshold supplied will be discarded. Finally in 
-the filter stage we check that matches are from different images and 
-discard all matches that are not symmetric. That is; if a feature, 
-$f_i$, is best matched to another feature, $f_j$, we would want for 
-$f_j$ to be best matched to $f_i$ too.
-This isn't always the case, for example if $f_i$ doesn't have a true 
+experiments (Chapter~\ref{C:Experiments}) the \emph{SIFT} feature 
+extractor and descriptor has been used. In the \emph{matching} stage 
+these features are matched using $k$-nearest neighbors.  The distance 
+function $d(f_i, f_j)$ between features is calculated according to the 
+feature descriptor. For \emph{SIFT} we use the cosine similarity between 
+the two descriptor vectors, while other descriptors might use other 
+measures\footnote{\emph{BRIEF} for example uses the hamming measure to 
+speed up the computation.}.  For any given feature $f_i$ the two closest 
+neighbors are returned, and we calculate the ratio between them as 
+proposed in \cite{lowe2004sift}\footnote{In Part~\ref{ss:ratio} this 
+calculation and other details of \emph{Ratio} will be discussed.}.  Any 
+correspondence with a ratio above the threshold supplied will be 
+discarded. Finally in the filter stage we check that matches are from 
+different images and discard all matches that are not symmetric. That 
+is, if a feature $f_i$, is best matched to another feature $f_j$, we 
+would want for $f_j$ to be best matched to $f_i$ too.
+This isn't always the case, for example if $f_i$ does not have a true 
 correspondance in the other image, its closest neighbor $f_j$ might 
@@
 Figure~\ref{fig:comparemirror} illustrates the benefits of \emph{MM} 
-using an example image pair from the Gallagher dataset 
+using an example image pair from the \emph{Gallagher} dataset 
 \cite{gallagher2008}.
@@
 \ForAll{$p \in P$} \Comment p is a set of feature points
-	\State $M\gets M \cup getMatches(p, t, F)$
+    \State $M\gets M \cup getMatches(p, t, F)$ \Comment See 
+    Algorithm~\ref{alg-getmatches}
 \EndFor \\
@@
 
-To cluster the feature points, we construct a graph with the feature 
-points as nodes and their similarity score as normalized edge weights.  
-Given a set of $n$ features $F = {f_1, \ldots, f_n}$ and a similarity 
-function $s$ we can define the matching function $M : (f_i, f_j) 
-\rightarrow \mathbb{R}$ as follows:
+To cluster the feature points, we construct a weighted graph with the 
+feature points as nodes and their similarity score as normalized edge 
+weights.  Given a set of $n$ features $F = {f_1, \ldots, f_n}$ and a 
+similarity function $s$ we can define the matching function $M : (f_i, 
+f_j) \rightarrow \mathbb{R}$ as follows:
 \begin{equation*}
@@
 to different measures of what constitutes an optimal partitioning.  
-Traditionally the most used clustering algorithms have been K-means and 
-spectral clustering, but in recent years a host of new algorithms have 
-been proposed based on both Newman's concept of graph 
-modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
+Traditionally the most used clustering algorithms have been 
+\emph{K-means} and spectral clustering, but in recent years a host of 
+new algorithms have been proposed based on both Newman's concept of 
+graph modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
 \cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
@@
 in \cite{ronhovde2009}} just to mention a few.  On tests done using 
-randomly generated graphs with a known partitioning \cite{blondel2008}, 
+randomly generated graphs with a known partitioning, \cite{blondel2008}, 
 \cite{rosvall2008} and \cite{ronhovde2009} perform markedly better than 
-spectral clustering and K-means\cite{lancichinetti2009}.
+spectral clustering and \emph{K-means}\cite{lancichinetti2009}.
 
@@
     \caption{The partitioned feature graph. Each vertex represents a 
-        feature point; lines indicate high similarity between points. A 
-        partition is a connected group with the same color. The border 
-        color of each node indicates which image it belongs to.  Zooming 
-    into a subsection of the graph (right part), the various cluster 
-sizes can be seen, ranging from hundreds of feature points to only two 
-or three.}
+        feature point while lines indicate high similarity between 
+        points.  A partition is a connected group with the same color.  
+        The border color of each node indicates which image it belongs 
+        to.  Zooming into a subsection of the graph (right part), the 
+    various cluster sizes can be seen, ranging from hundreds of feature 
+points to only two or three.}
     \label{fig:graph-view}
@@
 
-We use the Louvain Method \cite{blondel2008} for clustering feature 
-points, since it is relatively fast and performs well 
+We use the \emph{Louvain Method} \cite{blondel2008} for clustering 
+feature points, since it is relatively fast and performs well 
 \cite{lancichinetti2009}, does not require parameters 
@@
 
-The louvain method is based on optimizing the \emph{Modularity} proposed 
-by \cite{girvan2002} and defined as:
+The \emph{Louvain Method} is based on optimizing the \emph{Modularity} 
+proposed by \cite{girvan2002} and defined as:
 \begin{eqnarray*}
-	Q & = & (\mbox{fraction of edges within communities}) \\
+    Q & = & (\mbox{fraction of edges within clusters}) \\
 	  & & - (\mbox{expected fraction of such edges}) \\
@@
 $A_{ij}$ is the weight between the edge connecting $i$ and $j$.  
-$\delta(c_i, c_j)$ is the Kroneker Delta which is 1 only if the 
-community assignment $c_i$ is equal to the community assignment $c_j$.
+$\delta(c_i, c_j)$ is the \emph{Kroneker Delta} which is 1 only if the 
+cluster assignment $c_i$ is equal to the cluster assignment $c_j$.
 
-The Louvain Method is based on the maximizing the \emph{Modularity} of a 
-graph iteratively. This is done efficiently because the gain in 
-modularity from moving a vertex $v_i$ to a community $C$ can be 
+We can optimize the modularity efficiently iteratively because the gain 
+in modularity from moving a vertex $v_i$ to a cluster $C$ can be 
 calculated easily:
@@
 vertex to its proper cluster and then for each iteration reassign 
-vertices to neighboring communities if it increases the 
-\emph{Modularity}.  These iterations are carried out until there are no 
-reassignments in which case an initial clustering has been reached.  For 
-graphs consisting of a large number of vertices, the algorithm can now 
-be repeated, treating each of the resulting clusters as a vertex and 
+vertices to neighboring clusters if it increases the \emph{Modularity}.  
+These iterations are carried out until there are no reassignments in 
+which case an initial clustering has been reached.  For graphs 
+consisting of a large number of vertices, the algorithm can now be 
+repeated, treating each of the resulting clusters as a vertex and 
 repeating the same procedure.
 
-While the Louvain clustering algorithm does not require any parameters 
-in itself, it tends towards clustering all feature points together in 
-the same partition if the graph is very connected.  To ensure that the 
+While the \emph{Louvain Method} does not require any parameters in 
+itself, it tends towards clustering all feature points together in the 
+same partition when the graph is very connected.  To ensure that the 
 graph is well clustered, the adjacency matrix is pruned setting all 
@@
 
-\section{The Competition}
+\section{The Competitors}
 
@@
 \emph{Ratio} (Algorithm~\ref{alg-ratio}) \cite{lowe2004sift} diverges 
-from from matching feature points by distance in that the metric we use 
-to evaluate the feature points is the ratio of the distance to best 
-match compared to the distance of the second best match. In detail, say 
-$f_i$ is a feature point in an image $im_1$ and we are finding the 
-closest match in another image $im_2$. Given the two closest neighbors 
-to $f_i$ in in $im_l$, $f_m$ and $f_n$ ($d(f_i,f_m) < 
-similarity(f_i,f_n)$ and a threshold $\beta$, we decide to return a 
-match between $f_i$ and $f_j$ as follows:
+from matching feature points by distance in that the metric we use to 
+evaluate the feature points is the ratio of the distance to best match 
+compared to the distance of the second best match. In detail, say $f_i$ 
+is a feature point in an image $im_1$ and we are finding the closest 
+match in another image $im_2$. Given the two closest neighbors to $f_i$ 
+in $im_l$, $f_m$ and $f_n$ ($d(f_i,f_m) < similarity(f_i,f_n)$ and a 
+threshold $\beta$, we decide to return a match between $f_i$ and $f_j$ 
+as follows:
 \begin{equation*}
@@
 \ForAll{$f_i \in features_1$}
-    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
+    \State $f_m,f_n \gets get2NearestNeighbors(f_i, features_2)$
     \State $ratio \gets d(f_i, f_m) / d(f_i, f_n)$
@@
 based on the idea that local feature points within a region in one image 
-often matches to features within a corresponding region in the other 
-image. To find these regions the algorithm uses the Isodata algorithm 
-\cite{ball1965isodata} to perform unsupervised clustering on the 
-positions of the feature points in the two images. This results in a 
-fragmentation of the feature points into different regions based on 
+often match to features within a corresponding region in the other 
+image. To find these regions the algorithm uses the \emph{Isodata} 
+algorithm \cite{ball1965isodata} to perform unsupervised clustering on 
+the positions of the feature points in the two images.  This results in 
+a fragmentation of the feature points into different regions based on 
 their position in the image as demonstrated in 
@@
 create a correspondence matrix $P$. If we have $n$ regions in one image 
-and $m$ regions in the other, $P$ is an $n \times m$ matrix. Given a set 
-of matches $M = \{(f_{i,1}, f_{j}), \ldots \}$ and $n$ regions returned 
-by Isodata, each region consisting of a set of feature points $R_i = 
-\{f_i, f_j, \ldots\}$ we can construct $P$ as follows:
+and $m$ regions in the other, $P$ is an $n \times m$ matrix.  Given a 
+set of matches $M = \{(f_{i,1}, f_{j}), \ldots \}$ and $n$ regions 
+returned by \emph{Isodata}, each region consisting of a set of feature 
+points $R_i = \{f_i, f_j, \ldots\}$ we can construct $P$ as follows:
 \begin{equation*}
@@
 
-The Isodata algorithm is similar to K-means with the addition that 
-clusters are merged and split during the clustering process. In K-means 
-we randomly assign the data points to $k$ clusters to begin with and 
-calculate their mean. Then for each data point we reassign it to the 
-cluster closest in mean. We then calculate the mean of the updated 
-clusters and reiterate the process until we have spent a set amount of 
-iterations or no reassignments have taken place. Isodata runs the same 
-algorithm, but for each iteration it goes through the clusters and 
-checks if any can be merged or split. Clusters are split if their 
-variance along an axis is beyond a threshold, while two clusters are 
-merged if their distance is below another threshold. This approach is 
-beneficial when we don't know from the outside the amount of clusters we 
-expect to see. For example in the case of feature points it is not 
-obvious before clustering them regionally how many regions we obtain for 
-an image.
+The \emph{Isodata} algorithm is similar to \emph{K-means} with the 
+addition that clusters are merged and split during the clustering 
+process. In \emph{K-means} we randomly assign the data points to $k$ 
+clusters to begin with and calculate their mean. Then for each data 
+point we reassign it to the cluster closest in mean. We then calculate 
+the mean of the updated clusters and reiterate the process until we have 
+spent a set amount of iterations or no reassignments have taken place.  
+\emph{Isodata} runs the same algorithm, but for each iteration it goes 
+through the clusters and checks if any can be merged or split.  Clusters 
+are split if their variance along an axis is beyond a threshold, while 
+two clusters are merged if their distance is below another threshold.  
+This approach is beneficial when we don't know from the outside the 
+amount of clusters we expect to see. For example in the case of feature 
+points it is not obvious before clustering them regionally how many 
+regions we obtain for an image.
 
@@
 f_{i,2})$ and $m_j = (f_{j,1},f_{j,2})$ where $f_{k,n}$ is the feature 
-point of match $k$ in image $n$, we denote the euclidean distance 
+point of match $k$ in image $n$, we denote the Euclidean distance 
 between feature points $f_{i,n}$ and $f_{j,n}$ in image $n$ as 
@@
 algorithm will keep finding matches even after the actual 
-correspondences have already been found as long as they are consistent.
+correspondences have already been found, as long as they are consistent.
 

### 2013-08-15 text/main/ch5_experiments.tex
Corrections

@@
 overlap and no matches at all when they don't.  We would like it to work 
-flawlessly not just one a few images but on all possible images, and we 
-would expect it to run fast even on when faced with tens of thousands of 
+flawlessly not just on a few images but on all possible images, and we 
+would expect it to run fast even when faced with tens of thousands of 
 feature points.
@@
 to demonstrate good results across a wide range of images.  However if 
-we are just given to images and a set of matches, there is no
+we are just given two images and a set of matches, there is no
 way to tell which matches are correct and which aren't without going 
@@
 image pairs that are linked by a homography. Two images linked by a 
-homography are are related in a way that means that any point in the 
-first image can be translated a point in the second by a linear 
-equation. This holds true for two images where the points they have in 
-common are situated on a plan, or in the case that the camera only 
-rotated in between images. Figure~\ref{fig:homography_example} shows an 
-example of an image pair that can be linked with a homography and 
-another that cannot. In the second image pair, the change in camera 
-position means that pixels can't be linearly translated from one image 
-to another. For example would a pixel on the bell be translated to one 
-location while an adjacent pixel on the building in the background would
+homography are related in a way that means that any point in the first 
+image can be translated a point in the second by a affine equation. This 
+holds true for two images where the points they have in common are 
+situated on a plan, or in the case that the camera only rotated in 
+between images.  Figure~\ref{fig:homography_example} shows an example of 
+an image pair that can be linked with a homography and another that 
+cannot. In the second image pair, the change in camera position means 
+that pixels can't be linearly translated from one image to another. For 
+example a pixel on the bell would be translated to one location while an 
+adjacent pixel on the building in the background would
 move differently. For this reason we are constrained in which images 
@@
 blur, rotation, and viewpoint change. Inspired by this dataset (in 
-particular the `Graf' image set) and motivated by the need for more 
-image pairs featuring viewpoint changes, we have compiled a set of 8 
-image pairs consisting of subjects taken from two different angles. The 
-images are collected from Flickr's database of images published under a 
-creative commons licence and feature murals, which makes it possible to 
-relate points in the image pairs with a homography since most of the 
-points in the images will be lying on a plane.  The images have been 
-cropped to show the same motive and resized to $900\times 600$ pixels.  
-This dataset will be referred to as the \emph{Murals} dataset.  
-Figure~\ref{fig:murals} shows one image from each pair.
+particular the `\emph{Graf}' image set) and motivated by the need for 
+more image pairs featuring viewpoint changes, we have compiled a set of 
+8 image pairs consisting of subjects taken from two different angles.  
+The images are collected from \emph{Flickr's} database of images 
+published under a \emph{Creative Commons Licence} and feature murals, 
+which makes it possible to relate points in the image pairs with a 
+homography since most of the points in the images will be lying on a 
+plane.  The images have been cropped to show the same motive and resized 
+to $900\times 600$ pixels.  This dataset will be referred to as the 
+\emph{Murals} dataset.  Figure~\ref{fig:murals} shows one image from 
+each pair.
 
@@
 To measure the accuracy of an algorithm we are interested in two values:
-Precision and Recall. These measures were introduced in \cite{ke2004pca}
+Recall and Precision. These measures were introduced in \cite{ke2004pca}
 and later used in \cite{mikolajczyk2005performance}. Recall corresponds 
@@
 \begin{equation*}
-	recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~ 
+	Recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~ 
 	Matches}
@@
 \begin{equation*}
-	precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
+	Precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
 	~ \# ~ False ~ Matches}
@@
 algorithm is. An algorithm that returns only a few matches out of many, 
-but most of them are correct will have a high precision and a low 
-recall, where as an algorithm that returns almost all possible matches, 
-both true and false will have a low precision but a high recall. The 
+but most of them are correct will have a high Precision and a low 
+Recall, where as an algorithm that returns almost all possible matches, 
+both true and false will have a low Precision but a high Recall. The 
 ideal matching algorithm will be both precise but also return as many 
@@
 enough correct matches to align to the images, in which case we care 
-more about precision than recall.
+more about Precision than Recall.
 
@@
 	plot shows the result of 100 patch pairs generated from the source 
-	images shown to the left. The x-axis shows the recall based on the 
+	images shown to the left. The x-axis shows the Recall based on the 
 accumulated amount of potential matches for all 100 patch pairs. }
@@
 varying thresholds over a certain range). The results show that 
-\emph{MM} and \emph{MMC} consistently outperform \emph{Ratio}; 
+\emph{MM} and \emph{MMC} consistently outperform \emph{Ratio}, 
 \emph{MMC} generally lies 2-3 percentage points above \emph{MM} when 
@@
 	\emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} 
-	set.  The x-axis shows the recall based on the accumulated amount of 
+	set.  The x-axis shows the Recall based on the accumulated amount of 
 potential matches for all patch pairs.}
@@
     \caption{Results for viewpoint changes using the \emph{Graf} set 
-	from \cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: 
-	img1\&4; XL: img1\&5.}
+    from \cite{mikolajczyk2005performance}.  S: img1 \& 2; M: img1 \& 3; 
+    L: img1 \& 4; XL: img1 \& 5.}
 	\label{fig:result_viewpoint}
@@
 superior to \emph{Ratio} across viewpoint changes. For both methods 
-however we see a stark decrease in recall as the viewpoint change 
+however we see a stark decrease in Recall as the viewpoint change 
 increases. The performance of \emph{MM} (not shown in the plot) is 
@@
 not only outperforms \emph{Spectral} but also improves on \emph{MMC} at 
-similar recall rates, illustrating how a geometric algorithm can be 
+similar Recall rates, illustrating how a geometric algorithm can be 
 complemented by a reliable non-geometric selection of matches.
@@
 900 patch pairs extracted from the \emph{Murals} dataset and the image 
-pair 1\&3 from the \emph{Graf} set. The x-axis shows the recall based on 
+pair 1\&3 from the \emph{Graf} set. The x-axis shows the Recall based on 
 the accumulated amount of potential matches for all patch pairs.}
@@
 (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight 
-viewpoint change from the Gallagher dataset \cite{gallagher2008}.  The 
-performance is comparable to the murals, despite the lack of a simple 
-homographic mapping between the images.
+viewpoint change from the \emph{Gallagher} dataset \cite{gallagher2008}.  
+The performance is comparable to the murals, despite the lack of a 
+simple homographic mapping between the images.
 
@@
 These numbers should be taken with a grain of salt, given that much of 
-the code behind \emph{MMC} and \emph{Isomatch} is implemented in Python, 
-whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
-computationally intensive operations in C++, which makes them much 
-faster.
+the code behind \emph{MMC} and \emph{Isomatch} is implemented in 
+\emph{Python}, whereas \emph{MM} and \emph{Ratio} make use of 
+\emph{OpenCV} to execute computationally intensive operations in 
+\emph{C++}, which makes them much faster.

### 2013-08-15 text/main/ch6_applications.tex
Corrections

@@
 panorama recognition. To show the practical applications of the proposed 
-matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
-improve existing methods in near duplicate detection and panorama 
-recognition. These two problems were chosen because they both involve 
-matching images that might or might not overlap. These cases requires 
-matching algorithms that limit false positives since the alternative 
-would be to select the top $n$ matches which would make it hard to 
-distinguish adjacent or duplicate images from non-adjacent or dissimilar
+matching algorithms, \emph{MM} and \emph{MMC}, we show how they improve 
+existing methods in near duplicate detection and panorama recognition. 
+These two problems were chosen because they both involve matching images 
+that might or might not overlap. These cases requires matching 
+algorithms that limit false positives since the alternative would be to 
+select the top $n$ matches which would make it hard to distinguish 
+adjacent or duplicate images from non-adjacent or dissimilar
 image pairs. Near duplicate detection also constraints normal matching 
@@
         \label{fig:pano_autostitch}
-		\caption{Panorama by Autostitch}
+		\caption{Panorama by \emph{Autostitch}}
     \end{subfigure}%
@@
         alignment.  In a) the source images used to generate the 
-        panorama are displayed.\ b) shows the result of the Autostitch 
+        panorama are displayed.\ b) shows the result of the \emph{Autostitch} 
         program from \cite{brown2007automatic} which fails to combine 
@@
 of MMC enables us to correctly recognize and align source images that 
-fail to be combined by Autostitch, a program using the algorithm 
+fail to be combined by \emph{Autostitch}, a program using the algorithm 
 proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
-case the matching algorithm used in Autostitch fails to find sufficient 
+case the matching algorithm used in \emph{Autostitch} fails to find sufficient 
 matches between two images pairs to correctly position them and 
@@
 vision this task is nontrivial because our idea of a duplicate image 
-might only require there being some object or scene in common between 
+might only require that there is some object or scene in common between 
 the image pair. In addition the object or scene might have been taken 
@@
 	\caption{Example of a near duplicate image pair from the 
-	California-nd dataset \cite{jinda2012california}}
+	\emph{California-nd} dataset \cite{jinda2012california}}
 	\label{fig:near_duplicate}
@@
 \cite{vas2013cluster} shows the best clustering performance on the 
-California-nd dataset \cite{jinda2012california} which contains a set of
+\emph{California-nd} dataset \cite{jinda2012california} which contains a set of
 annotated vacation images similar to a typical photo album in a consumer
@@
 running time of \emph{MMC} it is intractable to calculate the test 
-scores on full scale images. To showcase the performance of \emph{MMC} 
-we add a test case using images resizes to 10\% of their original size.
+scores on full scale images.
 
@@
 \hline
-F1 score & \emph{Ratio} & \emph{MM} & \emph{MMC}   \\
+Algorithm & \emph{Ratio} & \emph{MM} & \emph{MMC}   \\
 	\noalign{\smallskip}
 	%
-    10\% Scale: & 0.5013 & 0.5990 & 0.5785 \\
-    100\% Scale: & 0.0 & 0.0 & --- \\
+    F1 score: & 0.5013 & 0.5990 & 0.6053 \\
     \hline
@@
 The results of the comparison can be seen in Table~\ref{table:ndd}. It 
-shows that \emph{MM} improves performance by 19.49\% over the original 
-framework using \emph{Ratio} to match images. For comparison 
-\emph{PhotoCluster} improves on the results of Xmatch 
-\cite{zhao2009scale}, the second best performing algorithm on the 
-California-nd dataset according to \cite{vas2013cluster}, with 2.52\%.
+shows that \emph{MM} and \emph{MMC} improves performance by 19.49\% and 
+20.75\% respectively over the original framework using \emph{Ratio} to 
+match images.

### 2013-08-15 text/main/ch7_summary.tex
Corrections

@@
 
-This thesis has addressed the problem of matching feature points without 
-using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
+This thesis address the problem of matching feature points without using 
+geometrical constraints, proposing \emph{Mirror Match (MM)} and 
 \emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
@@
 for the case of \emph{MMC} to panorama recognition and alignment. For 
-the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
+the case of near duplicate detection, \emph{MMC} provides an 20.75\% 
 improvement over \emph{Ratio} in a near duplicate detection framework 

### 2013-08-27 text/main/ch3_matching_methods.tex
Added ball tree to github

@@
 \emph{Spectral} and \emph{Isomatch}.
-
+%
 \section{Proposed Matching Methods}
@@
 (MM)} and \emph{Mirror Match with Clustering (MMC)}. 
-
+%
 \subsection{Mirror Match (\emph{MM})}
-
+%
 \begin{figure}[h]
@@
 \end{figure}%
-
+%
 The central idea behind \emph{MM} is to match features of $n$ images by 
@@
 details the implementation of \emph{MM}.
-
+%
 \begin{algorithm}[htb]
@@
 \label{alg-mm}
-%{\fontsize{10}{10}\selectfont
+{\fontsize{11}{11}\selectfont
 \begin{algorithmic}
 \Require $images$ : set of images, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
-\State $features\gets \varnothing$
+\State $matches_{init}\gets \varnothing$, $matches_{final}\gets 
+\varnothing$, $features\gets \varnothing$
 \ForAll{$I_i \in images$} \Comment Acquisition Stage
@@
 \end{algorithmic}
-%}
+}
 \end{algorithm}
-
+%
 In the \emph{acquisition stage} we extract local feature points and 
@@
 \ref{fig:without}).
-
+%
 \subsection{Mirror Match with Clustering (\emph{MMC})}
-
+%
 In contrast to \emph{MM}, \emph{MMC} diverges from traditional 
@@
 Algorithm~\ref{alg-mmc} shows the implementation of \emph{MMC}.
-
+%
 \begin{algorithm}[htb]
@@
 \label{alg-mmc}
-%{\fontsize{10}{10}\selectfont
+{\fontsize{11}{11}\selectfont
 \begin{algorithmic}
@@
 \mathbb{R}$
-\State $M\gets \varnothing$
-\State $F\gets \varnothing$
+\State $M\gets \varnothing$, $F\gets \varnothing$
 \ForAll{$I_i \in images$} \Comment Gather features
@@
 \end{algorithmic}
-%}
+}
 \end{algorithm}
-
+%
 To cluster the feature points, we construct a weighted graph with the 
@@
 \end{equation*}
-
-In the literature there are various ways of clustering a graph according 
-to different measures of what constitutes an optimal partitioning.  
+%
 Traditionally the most used clustering algorithms have been 
@@
 new algorithms have been proposed based on both Newman's concept of 
-graph modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
+\emph{Modularity}\footnote{Introduced in \cite{girvan2002}, discussed in 
 \cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
@@
 spectral clustering and \emph{K-means}\cite{lancichinetti2009}.
-
+%
 \begin{figure}[t]
@@
 \end{figure}
-
+%
 We use the \emph{Louvain Method} \cite{blondel2008} for clustering 
@@
 
-We can optimize the modularity efficiently iteratively because the gain 
-in modularity from moving a vertex $v_i$ to a cluster $C$ can be 
-calculated easily:
+We can optimize the \emph{Modularity} efficiently iteratively because 
+the gain in \emph{Modularity} from moving a vertex $v_i$ to a cluster 
+$C$ can be calculated easily:
 \begin{equation*}
@@
 \label{alg-getmatches}
-%\fontsize{10}{10}\selectfont
+{\fontsize{11}{11}\selectfont
     \begin{algorithmic}
@@
     \end{algorithmic}
+}
 \end{algorithm}
@@
 \label{alg-ratio}
-%{\fontsize{10}{10}\selectfont
+{\fontsize{11}{11}\selectfont
 \begin{algorithmic}
@@
 \end{algorithmic}
-%}
+}
 \end{algorithm}
@@
 \label{alg-isomatch}
-%{\fontsize{10}{10}\selectfont
+{\fontsize{11}{11}\selectfont
 \begin{algorithmic}
 \Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
+\State $matches_{init}\gets \varnothing$, $matches_{final}\gets 
+\varnothing$
 \State $features_1 \gets getFeatures(im_1)$
@@
 two clusters are merged if their distance is below another threshold.  
-This approach is beneficial when we don't know from the outside the 
+This approach is beneficial when we do not know from the outside the 
 amount of clusters we expect to see. For example in the case of feature 
@@
 \label{alg-spectral}
-%{\fontsize{10}{10}\selectfont
+{\fontsize{11}{11}\selectfont
 \begin{algorithmic}
 \Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final} \gets \varnothing$
+\State $matches_{init}\gets \varnothing$, $matches_{final} \gets 
+\varnothing$
 \State $features_1 \gets getFeatures(im_1)$
@@
 matching algorithm proposed by Leordeanu and Herbert 
-\cite{leordeanu2005spectral}.  The central idea behind it is that the 
-set of actual correspondences of feature points between two images 
-should be pairwise consistent. That is, given two feature points that 
-are geometrically close in one image, for most cases we would assume 
-that the closest correspondences of these two points in another image 
-would be similarly close.  Based on this assumption we want to pick out 
-a set of matches $T \subset S$ where $S$ is the initial set of possible 
-matches such that the matches in $T$ are as pairwise consistent as 
-possible. If we let $x$ be a binary vector corresponding in length to 
+\cite{leordeanu2005spectral}.  The central idea behind spectral matching 
+is that the set of actual correspondences of feature points between two 
+images should be pairwise consistent. That is, given two feature points 
+that are geometrically close in one image, for most cases we would 
+assume that the closest correspondences of these two points in another 
+image would be similarly close.  Based on this assumption we want to 
+pick out a set of matches $T \subset S$ where $S$ is the initial set of 
+possible matches such that the matches in $T$ are as pairwise consistent 
+as possible. If we let $x$ be a binary vector corresponding in length to 
 the set of initial matches $S$, where $x_i = 1$ if $m_i \subset T$, then 
@@
 argmax(x^TMx)$. By relaxing the constraints on $x$ such that it can take
-values in the range of $\left[0, 1\right]$ we can interpret $x_i$ as the
+values in the range $\left[0, 1\right]$ we can interpret $x_i$ as the
 association of $m_i$ with the optimal subset of matches $T$. Because we 
@@
 selects matches to ensure that matches are consistent, i.e.\ that two 
-feature points in one image don't match with the same feature point in 
+feature points in one image do not match with the same feature point in 
 the other image. This is done by going through all the matches in the 

### 2013-08-27 text/main/ch5_experiments.tex
Added ball tree to github

@@
 
-In order to demonstrate that the algorithms we propose are in fact 
-superior to similar algorithms in the field, we will have to compare 
-them with the state of the art. In this chapter we will first describe 
-exactly how we intent to compare the algorithms and then discuss the 
-results of these comparisons.
+In order to demonstrate that the algorithms we propose are superior to 
+similar algorithms in the field, we will have to compare them with the 
+state of the art. In this chapter we will first describe exactly how we 
+intent to compare the algorithms and then discuss the results of these 
+comparisons.
 
 \section{Experiments}
-For our ideal matching algorithm we would like it to return not just 
-some correct matches but all possible correct matches when images 
-overlap and no matches at all when they don't.  We would like it to work 
-flawlessly not just on a few images but on all possible images, and we 
-would expect it to run fast even when faced with tens of thousands of 
-feature points.
-
-These requirements fall in to three different categories. We want to 
-verify that the algorithm is \emph{general}, \emph{accurate} and 
-\emph{fast}.
+These requirements we expect from a matching algorithm fall in to three 
+categories.  We want to the algorithm to be \emph{general}, 
+\emph{accurate} and \emph{fast}. In the experiments we hope to measure 
+how \emph{MM} and \emph{MMC} perform on those three accounts compared to
+\emph{Ratio}, \emph{Isomatch} and \emph{Spectral}.
 
@@
         on a plane.  Figure~\ref{fig:hom_impossible} shows an image pair 
-        that can't reliably be linked by a homography. Even if we 
+        that cannot reliably be linked by a homography. Even if we 
         discount the change of people in the scence, the position of the 
@@
 cannot. In the second image pair, the change in camera position means 
-that pixels can't be linearly translated from one image to another. For 
+that pixels cannot be linearly translated from one image to another. For 
 example a pixel on the bell would be translated to one location while an 
@@
 more about Precision than Recall. 
-
+%
 \subsection{Measuring Speed}
-
+%
 To gain an intuition about the typical running time of an algorithm we 
@@
 certain size we can use the complexity to extrapolate how much longer it
-will take to run for inputs of e.g.\ double or half that size. For 
-example a matching algorithm with a complexity of $O(n^2)$ that takes 
-four seconds to find matches for $100$ feature points will take most 
-likely take $16$ seconds to find matches for $200$ feature points. If 
-the algorithm had a complexity of $O(n)$ it would more likely take $8$ 
-seconds to run on $200$ feature points.
-
-For this reason we will have to look at both the measuring speed as well
+will take to run for inputs of e.g.\ double or half that size. For this 
+reason we will have to look at both the measuring speed as well
 as the computational complexity of the algorithms.
-
+%
 \begin{figure}[t]
-	\begin{subfigure}[c]{0.2\textwidth}
     \centering
+    \begin{subfigure}[c]{0.18\textwidth}
         \includegraphics[width=\textwidth]{images/graf}
@@
 	%(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}[c]{0.8\textwidth}
-	\centering
+    \begin{subfigure}[c]{0.76\textwidth}
+%    \centering
 	\includegraphics[width=\columnwidth]{images/result_graf}
@@
 \end{figure}
-
+%
 \section{Results}
 \label{S:Results}
-
+%
 Using the \emph{Murals} dataset as well as test sets created from the 
@@
 against \emph{Ratio}, \emph{Spectral} and \emph{Isomatch}.
-
+%
 \subsection{Accuracy and Generality}
-
+%
 Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
@@
 \ref{fig:result_accumulated}. 
-
+%
 \begin{figure}[htb]
 	\centering
-	\includegraphics[width=\columnwidth]{images/result_accumulated}
+    \includegraphics[width=0.9\columnwidth]{images/result_accumulated}
 	\caption{Results for 900 patch pairs extracted from the 
@@
 \end{figure}
-
+%
 \begin{figure}[htb]
 	\centering
-	\includegraphics[width=1\textwidth]{images/result_viewpoint}
+    \includegraphics[width=0.9\textwidth]{images/result_viewpoint}
     \caption{Results for viewpoint changes using the \emph{Graf} set 
@@
 \end{figure}
-
+%
+\begin{figure}[htb]
+	\centering
+    \includegraphics[width=0.9\textwidth]{images/result_spectral-mmc}
+	\caption{Results for filtering matches with \emph{MMC} before 
+	applying the \emph{Spectral} algorithm. The algorithm is tested on 
+900 patch pairs extracted from the \emph{Murals} dataset and the image 
+pair 1\&3 from the \emph{Graf} set. The x-axis shows the Recall based on 
+the accumulated amount of potential matches for all patch pairs.}
+	\label{fig:result_spectral-mmc}
+\end{figure}
+%
 To further investigate the impact of viewpoint changes, we tested the 
@@
 
-\begin{figure}[htb]
-	\centering
-	\includegraphics[width=1\textwidth]{images/result_spectral-mmc}
-	\caption{Results for filtering matches with \emph{MMC} before 
-	applying the \emph{Spectral} algorithm. The algorithm is tested on 
-900 patch pairs extracted from the \emph{Murals} dataset and the image 
-pair 1\&3 from the \emph{Graf} set. The x-axis shows the Recall based on 
-the accumulated amount of potential matches for all patch pairs.}
-	\label{fig:result_spectral-mmc}
-\end{figure}
-
 Finally, as an example of a real life use case, 
@@
 simple homographic mapping between the images.
-
+%
 \begin{figure}[htb]
-	\begin{subfigure}[c]{.2\textwidth}
     \centering
+    \begin{subfigure}[c]{.18\textwidth}
         \includegraphics[width=\textwidth]{images/pitts}
@@
 	%(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}[c]{.8\textwidth}
-	\centering
+    \begin{subfigure}[c]{.76\textwidth}
     \includegraphics[width=1\columnwidth]{images/result_pitts}
@@
 \end{figure}
-
+%
 \subsection{Computational Complexity and Speed}
-
+%
 \begin{table}[htb]

### 2013-08-28 text/main/ch2_background.tex
Ball match method implemented

@@
 In this chapter we introduce the concept of local feature points in 
-images and explain how they are used. We will start out by discussing 
-the significance of local features in the first place before looking at 
-the inner workings of modern local image features. Finally we will look 
-at how they are used, in particular in terms of matching corresponding 
+images and explain how they are used. We will begin by discussing the 
+significance of local features in the first place before looking at the 
+inner workings of modern local image features. Finally we will look at 
+how they are used, in particular in terms of matching corresponding 
 points between two or more images.
@@
 
-The field of computer vision is anecdotally said to have been founded 
-when Marvin Minsky assigned the task of making a computer see as an 
+Anecdote claims that the field of computer vision was founded when 
+Marvin Minsky assigned the task of making a computer see as an 
 undergraduate summer project back in 1966\footnote{This is the same 
-Marvin who invented neural networks and went on to serve as scientific 
-adviser on Kubrick's movie \emph{Space Odyssey 2001}}.  Whether or not 
-the anecdote is true, the fact remains that what was assigned as a 
-summer's worth of work remains to this day an active field of research, 
-which illustrates an interesting notion: Making computers solve tasks 
-involving vision turns out to be much harder than we would initially 
-assume.
+    Marvin who invented neural networks and went on to serve as 
+scientific adviser on Kubrick's movie \emph{Space Odyssey 2001}}.  
+Whether or not this anecdote is true, the fact remains that what was 
+assigned as a summer's worth of work remains to this day an active field 
+of research today, which illustrates an interesting notion: Making 
+computers solve tasks involving vision turns out to be much harder than 
+we would initially assume.
 
@@
 task that we as humans are very good at. We can easily recognize objects 
-under different light, stitch various perspectvies into a panorama or 
+under different lights, stitch various perspectives into a panorama or 
 navigate a corridor identifying obstacles along the way.  In fact, these 
@@
 
-\subsection{An Ever Changing Constant World}
+\subsection{An Ever-changing Constant World}
 
 The main factor that makes computer vision difficult is how the world we 
-see around us constantly varies. This is not something that is 
-immediately obvious to the casual observer, so for the sake of clarity 
-let us do a small thought experiment. Try for a moment to imagine that 
-you enter a room and recognize the newspaper that is lying on the table, 
-illuminated from the grey light coming in of the window on the opposing 
-wall. You move across the room and switch on the light make out if the 
-paper is from today, and then you sit down and put on your glasses to 
-read the headline. Try to imagine the newspaper as you see it at three 
-different stages. First as you enter the slightly obscure room. Then as 
-you turn around after turning on the light, now standing on the other 
-side of the table; and finally when you are sitting with the paper in 
-your hands after you have put on your glasses. For each of these stages, 
-try to mentally picture the situation as a photography and look at how 
-the newspaper changes as you move around. At first you see it at an 
-angle lying in a fairly dark and grey room, the white pages reflecting 
-the light from the window with a cold bluish hue and the words too far 
-away to make out.  Then in the second stage with the lights turned on, 
-the object you are looking at has suddenly changed.  When you turned on 
-the light in the room, you also changed the color of the newspaper, 
-which now has a warm and yellowy white color to its pages.  The angle 
-you are looking at the paper from has changed too, and the words and 
-pictures are no longer upside down, although still slightly rotated and 
-with the increased light in the room the contrast of the words and 
-pictures of the page makes it possible for you to make recognize that 
-the newspaper is from today.  Finally as you sit down and put your 
-glasses on the newspaper changes again. The color might be the same, but 
-if you imagine taking a photography as you are sitting with the paper in 
-your hand, the newspaper will look much bigger, almost taking up the 
-entire frame. Now that your glasses are on, the words stand out much 
-clearer and you can see what is in the pictures on the front page.
+see around us constantly varies. Since this is not something that is 
+immediately obvious to the casual observer, let us do a small thought 
+experiment for the sake of clarity. Try for a moment to imagine that you 
+enter a room and notice a newspaper that is lying on the table, 
+illuminated by the grey light filtering in through a window on the 
+opposing wall.  You move across the room and switch on the light to make 
+out if the paper is from today, and then you sit down and put on your 
+glasses to read the headlines. Try to imagine the newspaper as you see 
+it at three different stages. First as you enter the slightly obscure 
+room.  Then as you turn around after turning on the light, now standing 
+on the other side of the table; and finally when you are sitting with 
+the paper in your hands after you have put on your glasses.  For each of 
+these stages, try to mentally picture the situation as a photograph and 
+look at how the newspaper changes as you move around. At first you see 
+it at an angle lying in a fairly dark and grey room, the white pages 
+reflecting the light from the window with a cold bluish hue and the 
+words too far away to be legible.  Then in the second stage with the 
+lights turned on, the object you are looking at has suddenly changed.  
+When you turned on the light in the room, you also changed the color of 
+the newspaper, which now has a warm and yellowy white color to its 
+pages.  The angle you are looking at the paper from has changed too, and 
+the words and pictures are no longer upside down, although still angled 
+away from you. In the increased light in the room, the sharper contrast 
+of the words and pictures on the page makes it possible for you to 
+recognize that the newspaper is from today.  Finally as you sit down and 
+put your glasses on, the newspaper changes again. The color might be the 
+same, but if you imagine taking a photograph as you are sitting with the 
+paper in your hand, the newspaper will look much bigger, almost taking 
+up the entire frame. Now that your glasses are on, the words stand out 
+much clearer, and you can see what is in the pictures on the front page.
 
@@
 it changed in the process, from the color of the pages to the sharpness 
-of the lines. On top of that, the paper has changed in size and rotation 
-from lying on the table to being in your hand.
+of the lines. Moreover, the paper changed in size and rotation from 
+lying on the table to being in your hand.
 
@@
 around in the room, we can safely assume that the paper didn't move 
-while our back is turned and even if it might not look exactly the same 
+while our back was turned. Even if it might not look exactly the same 
 after we turned on the light, it is reasonable to guess that nobody took 
-the old newspaper and replaced it with a new and yellower version.
+the old newspaper and replaced it with a different yellower version.
 
-On the other hand a computer algorithm trying to recognize objects will 
-not be able to make the same assumptions about the world. We might just 
-give as input to the program two pictures of the newspaper. One from the 
-first stage where the light was turned off, the paper was far away and 
-the lens wasn't focused correctly, and one from the third stage with the 
-light on, the image in focus and the paper taking up the entire photo.  
-Now we ask the algorithm: "Is this the same newspaper?". In this case it 
-is fair to ask how the algorithm can reliably make this judgement.
+On the other hand, a computer algorithm trying to recognize objects will 
+not be able to make the same assumptions about the world. We might 
+provide as input to the program two pictures of the newspaper. One from 
+the first stage where the light was turned off, the paper was far away 
+and the lens wasn't focused correctly, and one from the third stage with 
+the light on, the image in focus and the paper taking up the entire 
+photo.  Now we ask the algorithm: "Is this the same newspaper?". In this 
+case it is important to ask how the algorithm can reliably make this 
+judgement.
 
@@
 The example of the newspaper focuses on a particular branch of computer 
-vision; object recognition, but the exact same problem remains for most 
-of the various subfields. In automatic panorama stitching where we try 
-to create a panorama from a set of images, we need to recognize which 
-images fit together even if they are taken with different camera 
+vision; object recognition, but the same problem remains for most of the 
+various subfields. In automatic panorama stitching where we try to 
+create a panorama from a set of images, we need to recognize which 
+images fit together even if they were taken with different camera 
 settings.  In near duplicate detection where we try to find images that 
@@
 light.  In scene matching where we try to find out if two images are 
-taken of the same scene the two images could be taken on different days 
-under different conditions. The list goes on and it should hopefully be 
-clear that in order to solve a lot of problems in computer vision, we 
-need a way to deal with these variations.
+taken of the same scene the two images could have been taken on 
+different days under different conditions. The list goes on, 
+illustrating how it is essential to deal with these variations in order 
+to overcome the challenges of computer vision.
 
-One particularly successful approach over recent years has been to use 
+One particularly successful approach in the recent years has been to use 
 \emph{local image features}. As opposed to global image features like 
@@
 taken under different light or from slightly different angles. Then 
-given two images we can find some local feature points of each and see 
+given two images we can locate some local feature points in each and see 
 if any correspond across images.
@@
 For this to work we need two components. First we need to find spots in 
-an image that are distinct, since if we have similar points we can't 
+an image that are distinct, since if we have similar points we cannot 
 uniquely match them. Secondly we need to take information around the 
@@
 blur and scale. Finding unique points in the image is called 
-\emph{feature detection} and it yields a \emph{key point}, where as we 
-describe the key point with a \emph{feature descriptor}. The key point 
-will contain the position of the point in the image while the descriptor 
-will contain information about the image data surrounding that position.
+\emph{feature detection} and it yields a \emph{key point}. The key point
+is described with a \emph{feature descriptor}. The key point contains 
+the position of the point in the image while the descriptor will contain 
+information about the image data surrounding that position.
 
@@
 points, and points along an edge will look the same as other points 
-along the same edge. While corners aren't necessarily a sufficient 
+along the same edge. While corners are not necessarily a sufficient 
 condition for finding a good feature point, they provide a good starting 
@@
 Intuitively the simplest way to find corners would be to detect edges in 
-the image (for example using a high-pass filter), and follow these edges 
+the image (for example using a high-pass filter) and follow these edges 
 until they turn. Some of these approaches are detailed in 
@@
 perpendicular to the edge, but no gradient along the edge.  However in a 
-corner we would have a gradient in two different directions. The idea 
+corner we would have a gradient in two different directions. This idea 
 was originally introduced by Morevec \cite{hans1977towards} and later 
@@
 Alternatively a fast way of deciding if a point is a corner is to look 
-at all pixels surrounding the point of interest and compute the fraction 
-of pixels that have higher intensities than the center\footnote{i.e.\ 
-are brighter}. We can then find corners by thresholding on this 
-intensity difference as proposed by Smith and Brady 
+at all the pixels surrounding the point of interest and compute the 
+fraction of pixels that have higher intensities than the 
+center\footnote{i.e.\ are brighter}. We can then find corners by 
+thresholding on this intensity difference as proposed by Smith and Brady 
 \cite{smith1997susan} in their SUSAN edge detector. Lepetit and Fua 
@@
 simplest way is to save the values of the pixels in the immediate 
-neighborhood, but this would not be very flexible. Take the case where 
-we take two images of the same scene but overexpose one of them. Two 
-corresponding feature points would not look remotely alike in this case.
+neighborhood, but this would not be very flexible. Consider the case 
+where we take two images of the same scene but overexpose one of them.  
+Two corresponding feature points would not look remotely alike in this 
+case.
 In the feature descriptor of bright photography all the pixel values 
 would be high, while the values in the descriptor of the darker image 
-would all be low. A similar situation arise if one image is rotated or 
-there is a change in perspective.
+would all be low. A similar situation would arise if one image is 
+rotated or there is a change in perspective.
 
@@
 gradients surrounding the feature point as Lowe did in his Scale 
-Invariant Feature Detector (\emph{SIFT}) \cite{lowe2004sift}. The 
+Invariant Feature Transform (\emph{SIFT}) \cite{lowe2004sift}. The 
 histogram he proposes is based on the gradient locations and 
@@
 a feature descriptor, Binary Robust Independent Elementary Features 
-(\emph{BRIEF}), based on this idea. The main advantage of their approach 
-is the reduced processing and memory needed to create, store and match 
-the feature descriptors. Interestingly the positions used for pixel wise 
-comparisons were selected at random and tested against similar random 
-configurations. They then went on to use the configuration yielding the 
-best result as tested on a series of images. \emph{BRIEF} however is not 
-rotation invariant making it less useful in cases where images are not 
-necessarily upright.
+(\emph{BRIEF}), based on this idea. The main advantage of this approach 
+is the reduced amount of computations and memory needed to create, store 
+and match the feature descriptors. Interestingly the positions used for 
+pixel wise comparisons were selected at random and tested against 
+similar random configurations. They then went on to use the 
+configuration yielding the best result as tested on a series of images.  
+\emph{BRIEF} however is not rotation invariant making it less useful in 
+cases where images are not necessarily upright.
 
@@
 While the standard matching method is often computationally efficient, 
-it isn't necessarily the best way to match feature points. Many matching 
-methods make use of the knowledge of the position of the keypoints in 
-the image, i.e.\ the geometrical metadata. Using this information can 
-often yield more accurate outcomes, but they inevitably make assumptions
+it is not necessarily the best way to match feature points. Many 
+matching methods make use of the knowledge of the position of the 
+keypoints in the image, i.e.\ the geometrical metadata. Using this 
+information can often yield more accurate outcomes, but they inevitably 
+make assumptions
 about the geometric relationship between the images that are being 
@@
 where no camera rotation occurs between the two images, but fails when 
-this assumption isn't met. Various scenarios have been proposed to 
-improve on this simple assumption such as epipolar constraints 
+this assumption is not met. Various scenarios have been proposed to 
+improve on this simple assumption such as Epipolar constraints 
 (\cite{torr2000mlesac}, \cite{chum2005matching}) and pairwise 
@@
 transformation.  That is; there is no relative movement of objects in 
-between images and either the viewpoint is fixed or the image resides 
-entirely on a plane.  In practice this assumption largely holds true 
-when all objects we are interested in matching are roughly at the same 
-distance from the camera given that objects stay fixed from one image to 
-another.  Pairwise constraints provide a more robust approach to the 
-same problem by looking at a set of proposed correspondences and 
+between images and that either the viewpoint is fixed or the image 
+resides entirely on a plane.  In practice this assumption largely holds 
+true when all objects we are interested in matching are roughly at the 
+same distance from the camera given that objects stay fixed from one 
+image to another.  Pairwise constraints provide a more robust approach 
+to the same problem by looking at a set of proposed correspondences and 
 defining a pairwise error between any two matches for example based on 
@@
 In practice there are many situations where relying on the geometry of 
-the image to filter correspondences is not possible, for example images 
-without much overlap, or adjacent objects in one image are that are 
-separated in another. In these cases the assumptions behind the 
+the image to filter correspondences is not possible, for example in 
+images without much overlap, or adjacent objects in one image are that 
+are separated in another. In these cases the assumptions behind the 
 geometric algorithms will often cause them to return incorrect matches.
 
-In addition methods using geometric constraints all require an initial 
+In addition, all methods using geometric constraints require an initial 
 set of correspondences. If this set of correspondences can be narrowed 
@@
 
-In the absence of geometric constraints, only few methods are available.  
-As pointed out in \cite{szeliski2010} and mentioned above, the simplest 
-approach to matching feature points is to return all matches above a 
-given threshold of similarity.  This can be done with a fixed threshold 
-or by finding the nearest neighbors for each point while still filtering 
-by a threshold to avoid including matches for feature points that have 
-no counterpart in the other image.  When Lowe \cite{lowe2004sift} 
-proposed the scale-invariant feature transform he included an 
-alternative matching measure. Instead of rating matching by similarity 
-he assessed the uniqueness of a given match by looking at the two 
-nearest neighbors of each feature point and calculating the matching 
-score as the ratio of similarities. This method will later be referred 
-to as \emph{Ratio}.  Lowe ranks the scores by their uniqueness and picks 
-the $n$ best ones, which yields a set of correspondences that are 
-distinctly matched across two images.  Of these three methods (fixed 
+In the absence of geometric constraints, only a few methods are 
+available.  As pointed out in \cite{szeliski2010} and mentioned above, 
+the simplest approach to matching feature points is to return all 
+matches above a given threshold of similarity.  This can be done with a 
+fixed threshold or by finding the nearest neighbors for each point while 
+still filtering by a threshold to avoid including matches for feature 
+points that have no counterpart in the other image.  When Lowe 
+\cite{lowe2004sift} proposed the scale-invariant feature transform he 
+included an alternative matching measure. Instead of rating matching by 
+similarity, he assessed the uniqueness of a given match by looking at 
+the two nearest neighbors of each feature point and calculating the 
+matching score as the ratio of similarities. This method will later be 
+referred to as \emph{Ratio}.  Lowe ranks the scores by their uniqueness 
+and picks the $n$ best ones, which yields a set of correspondences that 
+are distinctly matched across two images.  Of these three methods (fixed 
 threshold, nearest neighbors, and \emph{Ratio}), \emph{Ratio} was found 

### 2013-08-28 code/ballmatch.py

@@ -1,0 +1,130 @@
+"""
+Python module for matching two images using clustering with ball tress
+
+Jonas Toft Arnfred, 2013-08-28
+
+"""
+####################################
+#                                  #
+#            Imports               #
+#                                  #
+####################################
+
+import features
+import numpy
+from sklearn.neighbors.ball_tree import BallTree
+
+
+####################################
+#                                  #
+#           Functions              #
+#                                  #
+####################################
+
+def match(paths, options = {}) :
+
+    keypoint_type		= options.get("keypoint_type", "SIFT")
+    descriptor_type		= options.get("descriptor_type", "SIFT")
+    leaf_size		    = options.get("leaf_size", 2)
+    radius_size         = options.get("radius_size", 300)
+    dist_threshold      = options.get("dist_threshold", 100)
+
+    # Get all feature points
+    indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
+
+    # Construct ball tree
+    bt = BallTree(ds, leaf_size=leaf_size)
+
+    # Filter nodes
+    ns = filterNodes(bt, radius_size)
+
+    def match_fun(ratio_threshold) :
+        return zip(*list(getMatches(bt, ns, indices, ks, ds, dist_threshold, ratio_threshold)))
+
+    return match_fun
+
+
+
+# utility function for getting a node
+def getNode(bt, index) :
+    return bt.node_data[index]
+
+
+# Produce new ball tree with node as head.  This could be done more
+# efficiently, but that would be tricky because of the underlying data
+# structure of the ball tree
+def newTree(bt, ds, index) :
+    node = getNode(bt, index)
+    idx = numpy.array(bt.idx_array[node['idx_start']: node['idx_end']+1])
+    node_features = ds[idx]
+    node_bt = BallTree(node_features, leaf_size=5)
+    return (node_bt, idx)
+
+
+# I'd like to go through the tree and find all the nodes first nodes (counting
+# from the top) that have a radius less than a certain size
+def filterNodes(bt, radius) :
+    # Initialize an empty set of nodes
+    akin = []
+    
+    # Initialize a list of nodes to skip
+    skip = numpy.zeros(bt.node_data.shape, dtype=numpy.bool)
+    
+    # For each node, add it to akin if the node is small enough and shouldn't be skipped
[…]

### 2013-08-28 code/display.py

@@ -289,6 +289,16 @@ def accuDetail(correct, total, legend, ylim = 100, treshold=1000) :
     accuHist(accu, legend, ylim=ylim)
 
 
+# Showing all keypoints from a given node in a ball tree
+def showNode(bt, ks, indices, node_index) :
+    node = getNode(bt, node_index)
+    idx = numpy.array(bt.idx_array[node['idx_start']:node['idx_end']])
+    keypoints = ks[idx]
+    im_idx = indices[idx]
+    positions = numpy.array(features.getPositions(keypoints))
+    display.compareKeypoints(images[0], images[1], positions[im_idx == 0], positions[im_idx == 1])
+
+
 def comparePlot(correct, 
                 compareCorrect, 
                 total, 

### 2013-08-28 code/features.py

@@ -18,6 +18,7 @@ Jonas Toft Arnfred, 2013-03-07
 
 import cv2
 import numpy
+from sklearn.neighbors.ball_tree import BallTree
 
 
 
@@ -161,6 +162,35 @@ def match(descriptor_type, D1, D2) :
     #T = dist_fun(D1,D2)
     #matchscores = [bestMatch(row) for row in T]
     #return matchscores
+
+
+
+def ballMatch(descriptor_type, D1, D2, match_same = False, leaf_size = 10) :
+    # Map for the type of distance measure to use
+    dist_map = {
+        "SIFT"   : 'minkowski',
+        "SURF"   : 'minkowski',
+        "ORB"    : 'hamming',
+        "BRISK"  : 'hamming',
+        "BRIEF"  : 'hamming',
+        "FREAK"  : 'hamming'
+    }
+
+    # Construct ball tree
+    tree = BallTree(D2, leaf_size=leaf_size, metric=dist_map[descriptor_type])
+
+    # For each descriptor in D2, query tree
+    def query() :
+        for descriptor in D1 :
+            if match_same :
+                (dist, index) = tree.query(descriptor, k=3)
+                yield index[0][1], dist[0][1], dist[0][1]/float(dist[0][2])
+            else :
+                (dist, index) = tree.query(descriptor, k=2)
+                yield index[0][0], dist[0][0], dist[0][0]/float(dist[0][1])
+
+    # Return matches
+    return zip(*list(query()))
 
 
 

### 2013-08-28 code/ratiomatch.py

@@ -36,13 +36,17 @@ def match(paths, options = {}) :
 
     keypoint_type		= options.get("keypoint_type", "SIFT")
     descriptor_type		= options.get("descriptor_type", "SIFT")
+    use_ball_tree       = options.get("use_ball_tree", False)
 
     # Get all feature points
     indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
 
     # Use cv2's matcher to get matching feature points
-    ii, ss, uu = features.bfMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
-    
+    if use_ball_tree :
+        ii, ss, uu = features.ballMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
+    else :
+        ii, ss, uu = features.bfMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
+
     # Get all positions
     (pos_im1, pos_im2) = (features.getPositions(ks[indices == 0]), features.getPositions(ks[indices == 1]))
 

### 2013-09-11 text/clustering.tex
Rewrote ACPR paper

@@
 \usepackage{footnote}
-%\usepackage[font={small}]{caption}
+\usepackage[font={small}]{caption}
 %\usepackage{sidecap}
@@
 \usepackage{amssymb}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{authblk}
+\pdfminorversion=4
+
+\title{Mirror Match: Reliable Feature Point Matching Without Geometric 
+Constraints}
+
+\author[1,2]{Jonas Toft Arnfred\thanks{j.arnfred@adsc.sg.com}}
+\author[1]{Dr. Stefan Winkler\thanks{Stefan.Winkler@adsc.com.sg}}
+\author[2]{Prof. Sabine S\"usstrunk\thanks{sabine.susstrunk@epfl.ch}}
+\affil[1]{Advanced Digital Science Center, Singapore}
+\affil[2]{\'Ecole Polytechnique F\'ed\'erale de Lausanne}
 
 \begin{document}
-
-\title{Mirror Match: Reliable Feature Point Matching Without Geometric Constraints}
-\author{Anonymous ACPR Submission}
-
 \maketitle
@@
 %
-When matching feature points between two or more images we are often 
-faced with the problem of correctly identifying the actual 
-correspondences among many possible pairings. Several methods have been 
-proposed in the literature to solve this problem. Many approaches look 
-at the geometric configuration of feature points and match them based on 
-various assumptions about the geometric relationship between the images. 
-These assumptions are then used to create different constraints on the 
-matches, e.g.\ angular constraints \cite{kim2008efficient}, epipolar 
+When finding correspondence pairs between two or more images we are 
+often faced with the problem that feature points in one image cannot be 
+uniquely matched with feature points in another image. This is partly 
+due to the fact that the discriminatory powers of modern feature 
+descriptors such as \emph{SIFT} \cite{lowe2004sift} and \emph{SURF} 
+\cite{bay2006surf} is reduced to approximate invariance to light and 
+perspective changes.  Additionally corners detected by feature detectors 
+such as \emph{SIFT} and \emph{Harris} \cite{harris1988combined} are only 
+approximations of the ideal unique feature point in an image which is 
+uniquely identifiable.  Both deficiencies often lead to a sub optimal 
+matching when we match feature points by finding the nearest neighbors 
+in terms of descriptor similarity. For this reason Lowe introduced a 
+matching method tailored to find unique matches when he introduced the 
+\emph{SIFT} feature point \cite{lowe2004sift}. The uniqueness of a given 
+match is assessed by looking at the two nearest neighbors of each 
+feature point and calculating the matching score as the ratio of 
+similarities. The method, \emph{NN-Ratio} then matches feature points by 
+matching each feature point with its nearest neighbor and only returning 
+the matches which a ratio better than a given threshold. Compared to a 
+nearest neighbor approach using the similarity of the descriptors as 
+threshold, Lowe's \emph{NN-Ratio} performs better as shown by 
+Mikolajczyk \cite{mikolajczyk2005performance}.
+
+More recent methods for matching feature points consider the geometric 
+configuration of feature points and match them based on assumptions 
+about the geometric relationship between images.  These assumptions are 
+then used to select a subset of matches according to different 
+constraints e.g.\ angular constraints \cite{kim2008efficient}, epipolar 
 constraints \cite{torr2000mlesac,chum2005matching}, or pairwise 
 constraints \cite{choi2009robust,leordeanu2005spectral}.
-%
-%When matching feature points between two or more images we are often 
-%faced with the problem of correctly identifying the actual 
-%correspondences among many possible pairings. Several methods have been 
-%proposed in the literature to solve this problem. In particular many 
-%approaches look at the geometric configuration of the feature points 
-%and match them according to assumptions made about the geometric 
-%relationship between the images matched. A simple example would be to 
-%only consider matches that aren't   too much with respect to the 
-%average angle and distancen as considered by \cite{kim2008efficient}.  
-%This performs well in situations where no camera rotation occurs 
-%between the two images, but fails when this assumption isn't met. 
-%Various scenarios have been proposed to improve on this simple 
-%assumption such as epipolar constraints (\cite{torr2000mlesac}, 
-%\cite{chum2005matching}) and pairwise constraints 
-%(\cite{choi2009robust}, \cite{leordeanu2005spectral}). The Epipolar 
-%constraint carries the assumption that the two images matched are 
-%related by an affine transformation. That is, there is no relative 
-%movement of objects in between images and either the viewpoint is fixed 
-%or the image resides entirely on a plane. In practice this assumption 
-%largely holds true when all objects we are interested in matching are 
-%roughly the same distance from the camera and when we expect to match 
-%objects that are consistently positioned across images.  Pairwise 
-%constraints provide a more robust approach to the same problem by 
-%looking at a set of proposed correspondences and defining a pairwise 
-%error between any two matches for example based on the assumption that 
-%two neighboring correspondences will usually have similar angles and 
-%distances. We can then convert the problem to an optimization problem 
-%and return a set of correspondences that minimizes this error such as 
-%proposed in \cite{choi2009robust} and \cite{leordeanu2005spectral}.  
-%This approach provides more robustness in cases where assumptions that 
-%are violated globally still hold on a local scale.
-%
-An alternative is to pick out different areas in each image and pair 
-areas when correspondence pairs are mainly found going from one area to 
-another. This allows for the filtering of all correspondences that do 
-not fall within paired areas. Examples include \emph{Isodata} 
-\cite{das2008event}, which clusters feature points according to their 
-position in the image, and the method from \cite{wu2011robust}, which 
-uses maximally stable extremal regions (MSER) feature points to 
-designate areas. In this paper the algorithm from \cite{das2008event} 
-will later be referred to as \emph{Isodata}.
 
-%proposes clustering feature points by using their geometric position 
-%and exclude correspondences that are geometrically deviant. A more 
-%sophisticated approach is introduced in \cite{wu2011robust} where the 
-%areas are created by using the MSER feature detector to find areas of 
-%interest in the images. These areas can be defined as an ellipse with a 
-%certain radius around the interest points. The feature points that fall 
-%within this ellipse are then matched according to epipolar constraints.
+Alternatively we can pick out different regions in each image and pair 
+regions according to how many correspondences there are between them.  
+This allows for the filtering of all correspondences that do not match 
+points within paired regions.  Examples include \cite{das2008event} and 
+\cite{wu2011robust}, the first (later referred to as \emph{Isodata}) 
+uses clustering to find regions while the latter uses maximally stable 
+extremal regions (MSER) to designate areas.
 
-In practice there are many situations where relying on the geometry of 
-the image to filter correspondences is not possible, for example images 
-without overlap, or adjacent objects in one image are that are separated 
-in another.  Furthermore, methods using geometric constraints all 
-require an initial set of correspondences. If this set of 
-correspondences can be narrowed down to the most probable correct 
-matches, the geometric matching algorithm will benefit in terms of speed 
-and accuracy.  Finally some use cases might require a speed that simply 
-cannot be achieved by complex geometric methods.
+Solutions that make use of geometric assumptions about the images fall 
+short in many practical applications. For example images with partial or 
+no overlap often leads to feature points that match to arbitrary points 
+in the other image leading to noise that makes it hard to pick the right 
+subset of correct matches. Similarly adjacent objects in one image that 
+are separated in another will void any global geometric assumptions of 
+the geometric relationship between two images.  Furthermore, methods 
+using geometric constraints all require an initial set of 
+correspondences. If this set of correspondences can be narrowed down to 
+the most probable correct matches, the geometric matching algorithm will 
+benefit in terms of speed and accuracy in cases where geometric 
+assumptions indeed hold true. For these reasons many applications call 
+for reliable non geometric matching methods.
 
-In the absence of geometric constraints, only few methods are available.  
-As pointed out in \cite{szeliski2010}, the simplest approach to matching 
-feature points is to return all matches above a given threshold of 
-similarity.  This can be done with a fixed threshold or by finding the 
-nearest neighbors for each point (still filtering by a threshold to 
-avoid including matches for feature points that have no counterpart in 
-the other image).  Lowe \cite{lowe2004sift} proposed the scale-invariant 
-feature transform (SIFT) together with an alternative measure, where the 
-uniqueness of a given match is found by looking at the two nearest 
-neighbors of each feature point and calculating the matching score as 
-the ratio of similarities.  Ranking the scores by their uniqueness and 
-picking the $n$ best produces a set of correspondences that are 
-distinctly matched across two images.
-Of these three methods (fixed threshold, nearest neighbors, and 
-\emph{SIFT}), \emph{SIFT} was found to perform best by a slight margin 
-\cite{mikolajczyk2005performance}.
-
-The two methods we propose in this paper are inspired by a simple but 
-novel idea. If a given feature point in one image is better matched with 
-other feature points from the \emph{same} image than points in the other 
-image, then any matches from this feature point to points in the other 
-image are considered unreliable and should be discarded.  This approach 
-carries no implicit assumptions about the geometric consistency of 
-matches and as such can easily be extended with other geometric 
-solutions when appropriate or necessary.
-
-Based on this idea,  we determine reliable matches as follows. 
-\emph{Mirror Match (MM)} matches every feature from both images with all 
-other features and filters matches based on the ratio of best to second 
-best match as in \emph{SIFT}. \emph{Mirror Match with Clustering (MMC)} 
-on the other hand takes the combined set of feature points from both 
-images and clusters these points according to their descriptors.  If a 
-resulting partition contains only feature points from one image, no 
-matches are returned.  If the partition contains points from both 
-images, \emph{Mirror Match} is used to find the best matches within this 
-partition.  The experimental results show that both approaches generally 
-outperform existing correspondence matching methods.
-
-%Matching feature points against the entire set of points from both 
-%images ensures that the distinctiveness of a returned correspondence is 
-%higher. In almost all cases\footnote{Exceptions would include cases 
-%where we want to find all particular points in a pattern and other use 
-%cases where the correspondence isn't assumed to be unique}, a good 
-%match between two images is unambiguous in the sense that there are no 
-%other equally good potential matches to the same point.  This is the 
-%key insight behind the algorithm presented by Lowe in 
-%\cite{lowe2004sift}.  However the implication doesn't follow the other 
-%way around. In the case that a feature point doesn't have a true 
-%correspondence there might still exist point with which the feature 
-%point is uniquely matched. The issue is particularly pronounced if we 
-%compare two images that do not correspond. For any proposed 
-%correspondence it is entirely probable that this correspondence is 
-%unique even if it isn't correct. When we match against the feature 
-%points of both images this ambiguity is avoided.  When the two images 
-%have no overlap or objects in common, chances are that a feature point 
-%will match better with another feature point from the same image in 
-%which case it is easily discarded.
-%
-%Often images will contain repetitive patterns that are difficult to 
-%match\footnote{In fact this particular problem has been given attention 
-%before by for example \cite{fan2011towards}} because the feature 
-%descriptors covering these patterns will be similar. If we remove points 
-%that aren't deemed sufficiently unique like in \emph{MM} this means that 
-%these points will often be discarded even if they are correctly matched.
-%\emph{MMC} makes it possible to look at groups of similar feature points 
-%one at a time and within each group find the best matches. This is done 
-%by taking the set of feature points from both images and cluster them by 
-%their similarity. In some cases the clustering will end up grouping 
-%feature points of only one image together which can then easily be 
-%discarded in the matching process.  In other cases partitions will 
-%contain similar feature points from both images that can then be matched 
-%using \emph{MM} but with much lower thresholds.
-%
+The two methods we propose in this paper are designed to be free of 
+assumptions about the image geometry. They improve on Lowe's 
+\emph{NN-Ratio} by attempting at matching only feature points that have 
+a unique correspondence. The first algorithm, \emph{Mirror Match (MM)} 
+is inspired by a simple but novel idea.  If a given feature point in one 
+image is better matched with other feature points from the \emph{same} 
+image than points in the other image, then any matches from this feature 
+point to points in the other image are considered unreliable and should 
+be discarded.  This approach carries no implicit assumptions about the 
+geometric consistency of matches and as such can easily be extended with 
+other geometric solutions when appropriate or necessary. \emph{Mirror 
+Match with Clustering (MMC)} builds upon this idea by trying to group 
+similar feature points and match them separately from the feature points 
+that have unique correspondences. The experimental results show that 
+both approaches generally outperform existing correspondence matching 
+methods when tested on partially overlapping images.
 
@@
 \label{S:MatchingMethods}
-
+%
 \subsection{Mirror Match (\emph{MM})}
-
+%
 \begin{figure}
@@
 			\includegraphics[width=0.85\columnwidth]{images/mirror_match_off}
-			\caption{\emph{SIFT}}
+            \caption{\emph{NN-Ratio}}
 			\label{fig:unique}
@@
 		\end{subfigure}%
-	\caption{Feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-	(c) Result of \emph{SIFT} matching. 
-  (d) All matches found by \emph{MM}, including intra-image matches. 
-	(e) Final \emph{MM} result. 
-	(f) Example of a partition of feature points after clustering, which 
-includes similar feature points from building windows and shirt patterns.}%
+    \caption{Feature matching with \emph{MM} and \emph{MMC}. Dots 
+        represent feature points; green/red lines indicate 
+        correct/incorrect matches, respectively; black lines represent 
+        edges in the feature graph.  (c) Result of \emph{NN-Ratio} 
+        matching.  (d) All matches found by \emph{MM}, including 
+        intra-image matches.  (e) Final \emph{MM} result.  (f) Example 
+        of a partition of feature points after clustering, which 
+        includes similar feature points from the same building across 
+    both images.}%
 	\label{fig:comparemirror}%
@@
 
+The central idea behind \emph{MM} is to match features of $n$ images by 
+taking every feature from all $n$ images and matching them against every 
+other feature from the same set. We can then discard the correspondences 
+that match two points within the same image. Algorithm~\ref{alg-mm} 
+details  the implementation of \emph{MM}.
 %
-The central idea behind \emph{MM} is to match features of $n$ images by 
-taking every feature from all $n$ images and matching it against every 
-other feature from the same set. We can then discard the correspondences 
-that match two points within the same image. Algorithm~\ref{alg-mm} details  
-the implementation of \emph{MM}.
-%
-\begin{algorithm}
+\begin{algorithm}[htb]
 \caption{Mirror Match (\emph{MM})}
 \label{alg-mm}
-%{\fontsize{10}{10}\selectfont
 \begin{algorithmic}
 \Require $images$ : set of images, $t \in \mathbb{R}$
-\State $matches_{init}\gets \varnothing$
-\State $matches_{final}\gets \varnothing$
-\State $features\gets \varnothing$
+\State $M_{init}\gets \varnothing$, $M_{final}\gets 
+\varnothing$, $F\gets \varnothing$
 \ForAll{$I_i \in images$} \Comment Acquisition Stage
-	\State $features\gets features \cup getFeatures(I_i)$
+	\State $F\gets F \cup getF(I_i)$
 \EndFor
-\ForAll{$f_i \in features$} \Comment Matching Stage
-	\State $f_m,f_n \gets get2NNs(f_i, features \setminus 
+\ForAll{$f_i \in F$} \Comment Matching Stage
+    \State $f_m,f_n \gets get2NearestNeighbors(f_i, F \setminus 
     \left\{f_i\right\})$
-	\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, f_m)$
+    \State $ratio \gets distance(f_i, f_m) / distance(f_i, f_n)$
 	\If{$ratio < t$}
-		\State $matches_{init} \gets \left(f_i, f_m\right)$
+		\State $M_{init} \gets M_{init} \cup \left(f_i, f_m\right)$
 	\EndIf
 \EndFor
-\ForAll{$\left(f_i, f_j \right) \in matches_{init}$} \Comment Filter 
+\ForAll{$\left(f_i, f_j \right) \in M_{init}$} \Comment Filter 
 Stage
-\If{$\left(f_j, f_i \right) \in matches_{init} \wedge getImg(f_i) \neq 
-getImg(f_j) \wedge \left(f_j, f_i\right) \not\in matches_{final}$}
-		\State $matches_{final} \gets (f_i, f_j)$
+\If{$\left(f_j, f_i \right) \in M_{init} \wedge getImg(f_i) \neq 
+getImg(f_j) \wedge \left(f_j, f_i\right) \not\in M_{final}$}
+		\State $M_{final} \gets (f_i, f_j)$
 	\EndIf
 \EndFor \\
-\Return $matches_{final}$
+\Return $M_{final}$
 \end{algorithmic}
-%}
 \end{algorithm}
@@
 that are not symmetric.
-%
-%\begin{figure*}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image pair}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_keypoints}
-%			\caption{Feature points}
-%			\label{fig:pitts_keypoints}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_off}
-%			\caption{\emph{SIFT}}
-%			\label{fig:unique}
-%		\end{subfigure}%
-%	}
-%	\makebox[\textwidth][c]{%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match_with_pruned}
-%			\caption{\emph{MM} intermediate result}
-%			\label{fig:within}
-%		\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%\qquad (or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/mirror_match}
-%			\caption{\emph{MM} final result}
-%			\label{fig:without}
-%		\end{subfigure}%
-%		\enspace%
-%		\begin{subfigure}[t]{0.32\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{\emph{MMC} Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Illustration of feature matching with \emph{MM} and \emph{MMC}.
-Dots represent feature points; green/red lines indicate %correct/incorrect matches, respectively; black lines represent edges in the feature graph.
-%(c) Result of \emph{SIFT} matching the two images.% 
-%  (d) All matches found by \emph{MM}, including matches between points in the same image. 
-%	(e) Final \emph{MM} result with the intra-image matches removed. 
-%	(f) Example of a partition of feature points after clustering. This partition 
-%includes similar feature points around the windows of a building and the patterns of a shirt.}%
-%	\label{fig:comparemirror}%
-%\end{figure*}%
 
@@
 \cite{gallagher2008}.
-With \emph{SIFT} (Figure~\ref{fig:unique}), many incorrect matches occur 
-in the fence towards the bottom of the image.
+With \emph{NN-Ratio} (Figure~\ref{fig:unique}), many incorrect matches 
+occur in the fence towards the bottom of the image.
 When we match all feature points together, many of these incorrect 
 matches are eliminated, because points in the fence match with other 
-points in the fence in the same image (Figures~\ref{fig:within} and
-\ref{fig:without}).
-
+points in the fence in the same image (Figures~\ref{fig:within} 
+and~\ref{fig:without}).
+%
 \subsection{Mirror Match with Clustering (\emph{MMC})}
@@
 %
-%Before we introduce the implementation details we will go over the 
-%problem of graph clustering and how it relates to feature matching.
-%
-%\subsubsection{Graph Clustering}
-%
-%Given a set of feature points from two images, $im_1$ and $im_2$: $F_k = 
-%\{k_i, k_j$ for $k_i \in im_1, k_j \in im_2\}$ as well as a matching 
-%function $M(k_i, k_j) \rightarrow \mathbb{R}$ that takes two feature 
-%points in an image and returns their matching score, we can define a 
-%matrix $A$ where each element $A_ij = M(k_i, k_j)$. A can be interpreted 
-%as the \emph{adjecency matrix} of the fully connected graph where each 
-%vertex corresponds to a keypoint and the edge between two vertices has a 
-%weight equal to the distance between the two corresponding keypoints.
-%
-%This representation reduces the problem of partitioning the keypoints 
-%into groups to that of graph clustering or community structure depending 
-%on the context. In the literature there are various ways of clustering a 
-%graph according to different measures of what constitutes an optimal 
-%partitioning. Traditionally the most used clustering algorithms have 
-%been K-means and spectral clustering, but in recent years a host of new 
-%algorithms have been proposed based on both Newman's concept of graph 
-%modularity\footnote{Introduced in \cite{girvan2002}, discussed in 
-%\cite{brandes2007} and used in \cite{blondel2008} as well as others} as 
-%well as information theoretical measures\footnote{See for example 
-%\cite{rosvall2008}} and the Potts spin model from physics\footnote{Used 
-%in \cite{ronhovde2009}} just to mention a few approaches. Many of the 
-%new algorithms differ from K-means clustering and Spectral clustering 
-%in that they do not require the number of expected to clusters to be 
-%specified beforehand\footnote{Among the aforementioned methods, this is 
-%true for \cite{blondel2008} and \cite{rosvall2008}}.  Furthermore, on 
-%tests done using randomly generated graphs with a known partitioning 
-%\cite{blondel2008}, \cite{rosvall2008} and \cite{ronhovde2009} perform 
-%markedly better than spectral clustering and 
-%K-means\cite{lancichinetti2009}.
-%
-%The performance of clustering algorithms is a complicated issue, since 
-%an optimal clustering given the same graph can vary depending on the 
-%application. Spectral clustering for example will usually return a 
-%partitioning where each partition is roughly equal in size\footnote{As 
-%mentioned in \cite{von2007}} while the Louvain 
-%clustering\cite{blondel2008} might return partitions of very uneven 
-%size, even if the modularity measurement has been shown to penalize very 
-%small clusters\cite{brandes2007}. Both behaviours can be beneficial 
-%depending on the application, but when clustering feature points, 
-%maintaining clusters of an even size usually means that some clusters 
-%will be '\emph{catch-all}' clusters where the feature points that do 
-%not fit anywhere else are grouped together. The necessity of specifying 
-%the amount of partitions in for example Spectral clustering or Pott's 
-%model clustering further exacerbates the issue since smaller partitions 
-%are then combined into one to achieve the right amount of partitions.
-%
-
-%
-\begin{algorithm}
+\begin{algorithm}[htb]
 \caption{Mirror Match with Clustering (\emph{MMC})}
 \label{alg-mmc}
-%{\fontsize{10}{10}\selectfont
 \begin{algorithmic}
-\Require $images$ : set of images, $t \in \mathbb{R}$
-\State $M\gets \varnothing$
-\State $F\gets \varnothing$
+\Require $images$ : set of images, $t \in \mathbb{R}$, $\alpha \in 
+\mathbb{R}$
+\State $M\gets \varnothing$, $F\gets \varnothing$
 \ForAll{$I_i \in images$} \Comment Gather features
-	\State $f_i\gets getFeatures(I_i)$
-	\State $F\gets F \cup f_i$
+    \State $F\gets F \cup getFeatures(I_i)$
 \EndFor
 \State $A\gets getAdjacencyMatrix(f_1, f_2,\; \ldots \;, f_n)$
-\State $A_{norm}\gets 1 - normalize(A)$
-\State $A_{pruned}\gets pruneEdges(A_{norm},\alpha)$
-\State $P\gets cluster(A_{pruned})$
+\State $A_{norm}\gets normalize(A)$
+\ForAll{$(i,j) \in indices(A)$} \Comment Prune edges
+    \If{$A_{norm}[i,j] < \alpha$}
+        \State $A_{norm}[i,j] \gets 0$
+    \EndIf
+\EndFor
+\State $P\gets cluster(A_{norm})$
 \ForAll{$p \in P$} \Comment p is a set of feature points
@@
 \end{algorithmic}
-%}
 \end{algorithm}
-
+%
 \begin{figure}[h]
 	\centering
-	\begin{subfigure}{0.8\columnwidth}
-		\includegraphics[width=\columnwidth]{images/MMC_graph_full}
-		\caption{Full Graph}
-		\label{fig:full_graph}
-	\end{subfigure}%
-
-	%add desired spacing between images, e. g. ~, \quad, \qquad		  
-	%(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}{0.7\columnwidth}
-		\includegraphics[width=\columnwidth]{images/MMC_graph_cropped}
-		\caption{Cropped Section of Graph}
-		\label{fig:cropped_graph}
-	\end{subfigure}%
-	\caption{The partitioned feature graph (a). Each vertex represents a 
-		feature point; lines indicate high similarity between 
-		points. A partition is a connected group with the same color. The border color of each node 
-		indicates which image it belongs to.  Zooming into a section of the graph (b), the various cluster sizes can be seen, ranging from 
-	hundreds of feature points to only two or three.}
+    \includegraphics[width=0.7\columnwidth]{images/MMC_graph_vert}
+    \caption{The partitioned feature graph. Each vertex represents a 
+        feature point; lines indicate high similarity between points. A 
+        partition is a connected group with the same color. The border 
+        color of each node indicates which image it belongs to.  Zooming 
+    into a section of the graph, the various cluster sizes can be seen, 
+ranging from hundreds of feature points to only two or three.}
 	\label{fig:graph}
@@
 feature points as a graph.
-%
 
@@
 partitions, as exemplified in Figure~\ref{fig:pitts_partition}.
-%
-%\begin{figure}
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{0.24\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_pitts_source}
-%			\caption{Source image}
-%			\label{fig:pitts_source}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%	}%
-%	\\
-%	\makebox[0.5\textwidth][c]{
-%		%~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-%		%(or a blank line to force the subfigure onto a new line)
-%		
-%		\begin{subfigure}[t]{0.5\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/MMC_partition}
-%			\caption{A Partition Example}
-%			\label{fig:pitts_partition}
-%		\end{subfigure}%
-%	}%
-%	\caption{Example of a partition of keypoints in an image pair. The 
-%		partition shown contains window corners from a building in the 
-%		left image and similar corners on the shirt in the right image.  
-%	}
-%	\label{fig:compare_mirror}
-%\end{figure}
-%
-%The matching algorithm for \emph{MMC} (algorithm \ref{alg-getmatches}) 
-%goes through the partitions one by one and selects matches in the 
-%following way: If the partition has no edges going from a feature point 
-%in one image to a feature point in another image, the partition is 
-%discarded. If we have more than one edge going between images then 
-%$getMatches$ will behave as \emph{MM} and make sure that a 
-%correspondence is symmetric, that it has a ratio above the desired 
-%threshold and that it isn't matching two feature points from the same 
-%image. Since feature points are all guaranteed to be fairly similar 
-%this means that we can set the ratio threshold much higher than in 
-%\emph{MM} and include matches that would normally have been discarded 
-%for not being sufficiently unique.
 
@@
 approach.  However, as can be seen in the example in 
-Figure~\ref{fig:cropped_graph}, many of the partitions contain only two 
-feature points from different images linked by one edge. In such a case, 
-we compare the similarity of the these two feature points with their 
-second best match and remove matches where this ratio lies above a 
-certain threshold, like in the \emph{SIFT} algorithm. For example in the 
-case of Figure~\ref{fig:pitts_partition}, we have feature points from a 
-building in one image grouped together with points from a shirt pattern 
-in another.  The nearest neighbor method would have returned wrong 
-matches, but since we match the partition with \emph{MM}, points in the 
-building end up matching other points in the building, and no matches 
-are returned.
-
-%\begin{algorithm}
-%\caption{Impl. of getMatches (\emph{from MMC algorithm})}
-%\label{alg-getmatches}
-%{\fontsize{10}{10}\selectfont
-%\begin{algorithmic}
-%\Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
-%all features
-%\State $matches \gets \varnothing$
-%\State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i) \neq 
-%	getImg(f_j)$
-%\State $\wedge f_i, f_j \in p \right\}$
-%\If{$\left\vert edges \right\vert = 1$} \Comment If $\exists$ one edge 
-%between images
-%	\State $f_i,f_j \gets getFeatures(edges_{inter}, p)$
-%	\State $f_m,f_n \gets get2NNs(f_i, features ~ 
-%\setminus ~ \left\{f_i\right\})$
-%	\State $f_s,f_t \gets get2NNs(f_j, features ~ 
-%\setminus ~ \left\{f_j\right\})$
-%	\State $ratio_i \gets similarity(f_i, f_n) / similarity(f_i, 
-%f_j)$
-%	\State $ratio_j \gets similarity(f_j, f_t) / similarity(f_j, 
-%f_i)$
-%	\If{$ratio_i < t\wedge ratio_j < t$}
-%		\State $matches \gets matches \cup (f_i, f_j)$
-%	\EndIf
-%\ElsIf{$\left\vert edges \right\vert > 1$} \Comment If $\exists$ more 
-%than one edge between images
-%	\ForAll{$f_i \in p$}
-%		\State $f_m,f_n \gets get2NNs(f_i, p \setminus 
-%\left\{f_i\right\})$
-%		\State $ratio \gets similarity(f_i, f_n) / similarity(f_i, 
-%f_m)$
-%		\If{$getImg(f_i) \neq getImg(f_m) \wedge ratio < t
-%\wedge (f_m, f_i) \not\in matches$}
-%			\State $matches \gets matches \cup (f_i, f_m)$
-%		\EndIf
-%	\EndFor
-%\EndIf
+Figure~\ref{fig:graph}, many of the partitions contain only two feature 
+points from different images linked by one edge. In such a case, we 
+compare the similarity of the these two feature points with their second 
+best match and remove matches where this ratio lies above a certain 
+threshold, like in the \emph{NN-Ratio} algorithm. For example in the 
+case of Figure~\ref{fig:pitts_partition}, we have several feature points 
+from a building in one image grouped together with points from the same 
+building in another image.
 %
-%\Return matches
-%\end{algorithmic}
-%}
-%\end{algorithm}
-
 \section{Experiments}
@@
 different angles. The images are collected from Flickr's database of 
-images published under a creative commons 
-licence %\footnote{\href{http://creativecommons.org/}{www.creativecommons.org}, 
-%a copyleft license permitting redistribution} 
-and feature murals, which 
-makes it possible to relate points in the image pairs with a homography.  
-The images have been cropped to show the same motive and resized to 
-$900\times 600$ pixels.  This dataset will be referred to as the 
-\emph{Murals} dataset.  Figure~\ref{fig:murals} shows one image from each pair.
+images published under a creative commons licence and feature murals, 
+which makes it possible to relate points in the image pairs with a 
+homography.  The images have been cropped to show the same motive and 
+resized to $900\times 600$ pixels.  This dataset will be referred to as 
+the \emph{Murals} dataset.  Figure~\ref{fig:murals} shows one image from 
+each pair.
 
@@
 %\subsection{Experimental setup}
-We compare the \emph{MM} and \emph{MMC} algorithms to 
-\emph{SIFT} \cite{lowe2004sift} as well 
-as \emph{Isodata} \cite{das2008event}. 
-\emph{Isodata} uses geometric constraints, whereas \emph{SIFT} does not.
-%, which uses geometric information to improve the matching. 
-%The comparison  with \emph{SIFT} serves to illustrate the relative performance of 
-%\emph{MM} and \emph{MMC} to a state of the art algorithm without 
-%geometric constraints. \emph{Isodata} is included to 
-%illustrate the performance of an algorithm relying on geometric 
-%constraints faced with image pairs that might not have any overlap.  
-The 
-comparison was done using the \emph{Murals} dataset (Figure~\ref{fig:murals}), the 
-\emph{Graf} set (Figure~\ref{fig:Graf}) from \cite{mikolajczyk2005performance}, and two 
-images %\footnote{100\_1942.jpg and 100\_1941.jpg} 
-from the Gallagher dataset \cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
+We compare the \emph{MM} and \emph{MMC} algorithms to \emph{NN-Ratio} 
+\cite{lowe2004sift} as well as \emph{Isodata} \cite{das2008event} and 
+\emph{Spectral} \cite{leordeanu2005spectral}.  \emph{Isodata} and 
+\emph{Spectral} use geometric constraints, whereas \emph{NN-Ratio} does 
+not.
+%, which uses geometric information to improve the matching.  The 
+%comparison  with \emph{NN-Ratio} serves to illustrate the relative 
+%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
+%without geometric constraints. \emph{Isodata} is included to illustrate 
+%the performance of an algorithm relying on geometric constraints faced 
+%with image pairs that might not have any overlap.  
+The comparison was done using the \emph{Murals} dataset 
+(Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
+from \cite{mikolajczyk2005performance}, and two images 
+%\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher dataset 
+%\cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
 
@@
 matching algorithm performs on a variety of overlaps but also how many 
-false positives we get on similar images that do not overlap at 
-all.\footnote{~The set of source images and homographies as well as the 
-script to generate the cropped test sets based on them will be made 
-available online, together with the exact test sets used in this paper 
-upon acceptance.}
-%\href{https://github.com/arnfred/Murals}{www.github.com/arnfred/Murals}}.  
+false positives we get on similar images that do not 
+overlap.\footnote{~The set of source images and homographies as well as 
+the script to generate the cropped test sets based on them can be found 
+at 
+\href{http://vintage.winklerbros.net/murals.html}{http://vintage.winklerbros.net/murals.html}}.  
 In practice the amount of overlap between pairs in a test set will 
 depend on the overlap and viewpoint change in the source image pair.  To 
-give a rough idea, Table~\ref{table:overlap} 
-shows the overlap of patch pairs created from images 1 and 3 of the 
-\emph{Graf} image set from \cite{mikolajczyk2005performance}.
+give a rough idea, Table~\ref{table:overlap} shows the overlap of patch 
+pairs created from images 1 and 3 of the \emph{Graf} image set from 
+\cite{mikolajczyk2005performance}.
 
@@
 Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
-generated from images 1 and 3 of the \emph{Graf} image set (cf.~Figure~\ref{fig:Graf}). The plot 
-compares the accuracy of \emph{SIFT}, \emph{MM}, \emph{MMC}, and 
-\emph{Isodata} as a function of the number of matches produced (which is achieved by varying thresholds over a certain range).
-The results show that \emph{MM} and \emph{MMC} consistently outperform \emph{SIFT}; \emph{MMC} generally lies 2-3 percentage points above \emph{MM} when both are performing at optimal accuracy.
-Although \emph{Isodata} exhibits a good performance on strict thresholds (small number of matches), that quickly diminishes when more matches are desired.
+generated from images 1 and 3 of the \emph{Graf} image set 
+(cf.~Figure~\ref{fig:Graf}). We plot the precision and recall of 
+\emph{MMC}, \emph{MM}, \emph{Isodata}, \emph{Spectral} and 
+\emph{NN-Ratio}. The precision and recall is calculated as follows:
+
+\begin{equation*}
+    Precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
+    ~ \# ~ False ~ Matches} \\
+\end{equation*}
+\begin{equation*}
+    Recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~
+    Matches}
+\end{equation*}
+
+The plot data is obtained by varying ratio thresholds.  The results show 
+that \emph{MM} and \emph{MMC} consistently outperform \emph{NN-Ratio}; 
+\emph{MMC} generally lies 2-3 percentage points above \emph{MM} when 
+both are performing at optimal accuracy.  Although \emph{Isodata} and 
+\emph{Spectral} exhibits a good performance on strict thresholds (small 
+number of matches), that quickly diminishes when more matches are 
+desired.
 
@@
 			\centering
-			\includegraphics[width=0.6\columnwidth]{images/result_graf}
+            \includegraphics[width=0.8\columnwidth]{images/result_graf}
 			%\caption{Performance on Scharf}
@@
 
-To validate whether these results 
-generalize to other images, we tested the four algorithms on the 
-\emph{Murals} dataset as well as the \emph{Graf} pair tested above.  
-In total 900 different patch pairs were generated from 9 
-source image pairs.  The results are shown in Figure 
+To validate whether these results generalize to other images, we tested 
+the five algorithms on the \emph{Murals} dataset as well as the 
+\emph{Graf} pair tested above.  In total 900 different patch pairs were 
+generated from 9 source image pairs.  The results are shown in Figure 
 \ref{fig:result_accumulated}.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{images/result_accumulated}
+    \includegraphics[width=0.8\columnwidth]{images/result_accumulated}
 	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
@@
 last are taken from very different angles. The results from   \emph{MMC} 
-and \emph{SIFT} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{SIFT} across 
-viewpoint changes.
+and \emph{NN-Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
+confirming that \emph{MMC} is generally superior to \emph{NN-Ratio} 
+across viewpoint changes.
 The performance of \emph{MM} (not shown in the plot) is similar to 
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{images/result_viewpoint}
+    \includegraphics[width=0.8\columnwidth]{images/result_viewpoint}
 	\caption{Results for viewpoint changes using the \emph{Graf} set from 
@@
 
-Finally, for an example of a real life use case, Figure~\ref{fig:result_pitts} 
-shows the results on 100 patch pairs generated 
-from a typical holiday photo shot (Figure~\ref{fig:pitts_source}) featuring occlusion and a slight viewpoint 
-change from the Gallagher dataset \cite{gallagher2008}.  The performance is comparable to the murals, despite the lack of a simple homographic mapping between the images.
+Finally, for an example of a real life use case, 
+Figure~\ref{fig:result_pitts} shows the results on 100 patch pairs 
+generated from a typical holiday photo shot 
+(Figure~\ref{fig:pitts_source}) featuring occlusion and a slight 
+viewpoint change from the Gallagher dataset \cite{gallagher2008}.  The 
+performance is comparable to the murals, despite the lack of a simple 
+homographic mapping between the images.
 
 \begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.15\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pitts}
-%		\end{subfigure}%
-		~%add desired spacing between images, e. g. ~, \quad, \qquad
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
 \centering
-			\includegraphics[width=0.6\columnwidth]{images/result_pitts}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
+\includegraphics[width=0.8\columnwidth]{images/result_pitts}
 \caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
@@
 
-In terms of computational complexity, \emph{SIFT}, \emph{MM}, and \emph{Isodata} can be 
-implemented in $O(n\log n)$, where $n$ is the total number of feature 
-points.  Our current \emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
-construction of a similarity matrix of the feature points. However, it is 
-possible to approximate this in $O(n\log n)$ using search trees.
+In terms of computational complexity, \emph{NN-Ratio}, \emph{MM}, and 
+\emph{Isodata} can be implemented in $O(n\log n)$, where $n$ is the 
+total number of feature points.  \emph{Spectral} and our current 
+\emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
+construction of a similarity matrix of the feature points. However, both
+can be approximated in $O(n\log n)$ using search trees to sparsely 
+populate the adjacency matrix.
 
@@
 much of the code behind \emph{MMC} and \emph{Isodata} is implemented in 
-Python, whereas \emph{MM} and \emph{SIFT} make use of OpenCV to execute 
-computationally intensive operations in C++, which makes them much 
-faster.
+Python, whereas \emph{MM} and \emph{NN-Ratio} make use of OpenCV to 
+execute computationally intensive operations in C++, which makes them 
+much faster.
 
@@
 %	\small
-\begin{tabular}{r*{4}{c}}
+\begin{tabular}{r*{5}{c}}
 \hline
-	Algorithm: & \emph{SIFT} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
-	\\
+	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} %
+& \emph{Isomatch} & \emph{Spectral}	\\
 	\noalign{\smallskip} 
 	%
-	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
+	Running time (seconds): & 21 & 23 & 2722 & 1146 & 994\\
 	\hline
@@
 
-The algorithms show promising results when tested on the \emph{Murals} data 
-set. %, where pairs of the same object seen from different angles are %cropped to have different degrees of overlap ranging from full to non at all. The results on 900 patch pairs show that 
-\emph{MM} and \emph{MMC} 
-generally outperform existing matching algorithms \emph{SIFT} and \emph{Isodata}, and \emph{MMC} 
+The algorithms show promising results when tested on the \emph{Murals} 
+data set. \emph{MM} and \emph{MMC} generally outperform existing 
+matching algorithms \emph{NN-Ratio} and \emph{Isodata}, and \emph{MMC} 
 outperforms \emph{MM}. We show that this result generalizes to 
-variations in viewpoint change as well as more realistic photos featuring occlusions. 
-% by comparing \emph{MMC} to \emph{SIFT} over a set of image pairs with an increasing magnitude of perspective difference. 
-%We go on to apply the algorithms to a real life image case 
-%featuring occlusion and a slight viewpoint change and show that the 
-%performance of \emph{MM} and \emph{MMC} is consistent with the results 
-%on \emph{Murals}.
+variations in viewpoint change as well as more realistic photos 
+featuring occlusions.
 
-Given the versatility of the proposed algorithms, we are planning to apply them to problems that require high 
-reliability faced with images that might not match, such as near 
-duplicate detection or face recognition.
+Given the versatility of the proposed algorithms, we are planning to 
+apply them to problems that require high reliability faced with images 
+that might not match, such as near duplicate detection or face 
+recognition.
+
+\textit{This work is supported by the research grant for ADSC's Human 
+Sixth Sense Programme from Singapore's Agency for Science, Technology 
+and Research ($\text{A}^\star$STAR).}
 %
 \bibliographystyle{IEEEtran}
-\bibliography{bibliography}
+\bibliography{tail/bibliography}
 \end{document}

### 2013-09-11 code/ballmatch.py

@@ -88,33 +88,36 @@ def match_radius(paths, options = {}) :
 
                 # If the group size is bigger than 4 items
                 if group_size >= group_limit :
-                    for (i,j), m, s, u in query_cluster(idxs, ds, ratio_boost, indices, ks) : 
+                    for (i, j), m, s, u in query_cluster(idxs, ds, ratio_boost, indices, ks) : 
                         if not (i,j) in seen :
-                            seen.add((i,j))
-                            seen.add((j,i))
-                            yield m, s, u
+                            seen.add((i, j))
+                            seen.add((j, i))
+                            yield m, s, u, group_size
 
                 # If the group size is less use mirror match
                 else :
                     for (i,j), m, s, u in query_unique(bt, i, descriptor, indices, ks) : 
                         if not (i,j) in seen :
-                            seen.add((i,j))
-                            seen.add((j,i))
-                            yield m, s, u
+                            seen.add((i, j))
+                            seen.add((j, i))
+                            yield m, s, u, group_size
 
 
     # Get matches
     match_data = list(query_all())
 
     def match_fun(ratio_threshold) :
-        matches = [(pos, s, u) for pos, s, u in match_data if u < ratio_threshold]
+        matches = [(pos, s, u, g) for pos, s, u, g in match_data if u < ratio_threshold]
         if len(matches) == 0 :
-            return [], [], []
+            return [], [], [], []
         else :
             return zip(*matches)
 
     return lambda t : match_fun(t)
 
+
+def query_cluster_best(idxs, i, ds, ratio_boost, indices, ks) :
+    pass
 
 def query_cluster(idxs, ds, ratio_boost, indices, ks) :
     ds_cluster = ds[idxs]

### 2013-09-11 code/display.py

@@ -98,7 +98,7 @@ def compareKeypoints(im1, im2, pos1, pos2, filename = None, separation = 0) :
     pylab.ylim(im3.shape[0],0)
 
     if filename != None :
-        fig.savefig(filename, bbox_inches='tight', dpi=72)
+        fig.savefig(filename, bbox_inches='tight', dpi=300)
 
 
 def matchPoints(im1, im2, matches, dist = None, filename = None, max_dist = 100, line_width = 0.8, matches_im1 = None, dist_im1 = None, matches_im2 = None, dist_im2 = None) :

### 2013-09-11 code/matching.py

@@ -285,8 +285,8 @@ def mirrorMatch(distance_threshold, paths, homography, thresholds, keypoint, des
 
 def ballMatch(distance_threshold, paths, homography, thresholds, keypoint, descriptor) :
     options = {
-      "leaf_size": 10,
-       "radius_size": 250,
+       "leaf_size": 10,
+       "radius_size": 300,
        "dist_threshold": 300,
        "ratio_boost" : 1.2,
        "shuffle_keypoints" : False,

### 2013-09-19 text/clustering.tex
Updated features to use options and kp max length

@@
 \usepackage{cite}
-\usepackage{hyperref}
+\usepackage[draft]{hyperref}
+%\usepackage[options]{nohyperref}
+%\usepackage{url}
 %\usepackage[stable]{footmisc}
@@
 \usepackage[utf8]{inputenc}
-\usepackage{authblk}
+%\usepackage{authblk}
 \pdfminorversion=4
@@
 
-\author[1,2]{Jonas Toft Arnfred\thanks{j.arnfred@adsc.sg.com}}
-\author[1]{Dr. Stefan Winkler\thanks{Stefan.Winkler@adsc.com.sg}}
-\author[2]{Prof. Sabine S\"usstrunk\thanks{sabine.susstrunk@epfl.ch}}
-\affil[1]{Advanced Digital Science Center, Singapore}
-\affil[2]{\'Ecole Polytechnique F\'ed\'erale de Lausanne}
+\author{
+\IEEEauthorblockN{
+Jonas Toft Arnfred,\IEEEauthorrefmark{1}\IEEEauthorrefmark{2} Stefan Winkler,\IEEEauthorrefmark{1} Sabine S\"usstrunk\IEEEauthorrefmark{2}}
+\vspace{1mm}
+\IEEEauthorblockA{
+\IEEEauthorrefmark{1}~Advanced Digital Sciences Center (ADSC), University of Illinois at Urbana-Champaign (UIUC), Singapore\\
+\IEEEauthorrefmark{2}~\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland}
+}
+
+%\author[1,2]{Jonas Toft Arnfred\thanks{j.arnfred@adsc.com.sg}}
+%\author[1]{Stefan Winkler\thanks{stefan.winkler@adsc.com.sg}}
+%\author[2]{Sabine S\"usstrunk\thanks{sabine.susstrunk@epfl.ch}}
+%\affil[1]{~Advanced Digital Sciences Center (ADSC), University of Illinois at Urbana-Champaign (UIUC), Singapore}
+%\affil[2]{~\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland}
 
@@
 feature points in two or more images using geometric assumptions to 
-increase the robustness of the matching. However, very little work 
-addresses the case where these assumptions might not hold. In particular 
-few methods address the problem of reliable matching in cases where it 
-is unknown whether two images have any corresponding areas or objects in 
+increase the robustness of the matching. However, these assumptions do not always hold; 
+in particular, few methods address the problem of reliable matching in cases where it 
+is unknown whether the images have any corresponding areas or objects in 
 the first place.
 
-We propose two algorithms for matching feature points without the use of 
+We propose two algorithms for matching feature points \emph{without} the use of 
 geometric constraints. The first relies on the fact that any match 
@@
 %
-When finding correspondence pairs between two or more images we are 
-often faced with the problem that feature points in one image cannot be 
+When finding correspondence pairs between two or more images, feature points in one image cannot always be 
 uniquely matched with feature points in another image. This is partly 
-due to the fact that the discriminatory powers of modern feature 
-descriptors such as \emph{SIFT} \cite{lowe2004sift} and \emph{SURF} 
-\cite{bay2006surf} is reduced to approximate invariance to light and 
-perspective changes.  Additionally corners detected by feature detectors 
+due to the fact that the discriminatory power of modern feature 
+descriptors such as \emph{SIFT} \cite{lowe2004sift} or \emph{SURF} 
+\cite{bay2006surf} is traded off with invariance to light and 
+perspective changes.  Additionally, corners detected by feature detectors 
 such as \emph{SIFT} and \emph{Harris} \cite{harris1988combined} are only 
-approximations of the ideal unique feature point in an image which is 
-uniquely identifiable.  Both deficiencies often lead to a sub optimal 
-matching when we match feature points by finding the nearest neighbors 
-in terms of descriptor similarity. For this reason Lowe introduced a 
-matching method tailored to find unique matches when he introduced the 
-\emph{SIFT} feature point \cite{lowe2004sift}. The uniqueness of a given 
-match is assessed by looking at the two nearest neighbors of each 
+approximations of the ideal feature point in an image which is 
+uniquely identifiable.  These deficiencies often lead to suboptimal results
+when matching feature points by finding the nearest neighbors 
+in terms of descriptor similarity.  Therefore, Lowe introduced \emph{SIFT} together with a 
+matching method tailored to finding unique matches \cite{lowe2004sift}. 
+The method, \emph{NN-Ratio}, assesses the uniqueness of a given match by looking at the two nearest neighbors of each 
 feature point and calculating the matching score as the ratio of 
-similarities. The method, \emph{NN-Ratio} then matches feature points by 
-matching each feature point with its nearest neighbor and only returning 
-the matches which a ratio better than a given threshold. Compared to a 
-nearest neighbor approach using the similarity of the descriptors as 
-threshold, Lowe's \emph{NN-Ratio} performs better as shown by 
-Mikolajczyk \cite{mikolajczyk2005performance}.
+similarities; only matches with a ratio above a given threshold are retained. 
+Lowe's \emph{NN-Ratio} has been shown to outperform nearest neighbor approaches that use only the similarity of the descriptors as a
+threshold \cite{mikolajczyk2005performance}.
 
@@
 then used to select a subset of matches according to different 
-constraints e.g.\ angular constraints \cite{kim2008efficient}, epipolar 
+constraints, e.g.\ angular constraints \cite{kim2008efficient}, epipolar 
 constraints \cite{torr2000mlesac,chum2005matching}, or pairwise 
@@
 Alternatively we can pick out different regions in each image and pair 
-regions according to how many correspondences there are between them.  
+regions according to the number of correspondences between them.  
 This allows for the filtering of all correspondences that do not match 
-points within paired regions.  Examples include \cite{das2008event} and 
-\cite{wu2011robust}, the first (later referred to as \emph{Isodata}) 
-uses clustering to find regions while the latter uses maximally stable 
-extremal regions (MSER) to designate areas.
+points within paired regions.  Examples include \emph{Isodata} \cite{das2008event}, which 
+uses clustering to find regions, or \cite{wu2011robust}, which designate areas based on maximally stable 
+extremal regions (MSER).
 
-Solutions that make use of geometric assumptions about the images fall 
-short in many practical applications. For example images with partial or 
-no overlap often leads to feature points that match to arbitrary points 
-in the other image leading to noise that makes it hard to pick the right 
-subset of correct matches. Similarly adjacent objects in one image that 
+Solutions that rely on geometric assumptions about the images fall 
+short in many practical applications. For example, images with partial or 
+no overlap often result in feature points that match to arbitrary points 
+in the other image; this introduces noise that makes it hard to pick the right 
+subset of correct matches. Similarly, adjacent objects in one image that 
 are separated in another will void any global geometric assumptions of 
@@
 correspondences. If this set of correspondences can be narrowed down to 
-the most probable correct matches, the geometric matching algorithm will 
+the most probable correct matches, any geometric matching algorithm will 
 benefit in terms of speed and accuracy in cases where geometric 
-assumptions indeed hold true. For these reasons many applications call 
-for reliable non geometric matching methods.
+assumptions do hold true. For these reasons reliable non-geometric matching methods are essential.
 
 The two methods we propose in this paper are designed to be free of 
-assumptions about the image geometry. They improve on Lowe's 
-\emph{NN-Ratio} by attempting at matching only feature points that have 
-a unique correspondence. The first algorithm, \emph{Mirror Match (MM)} 
-is inspired by a simple but novel idea.  If a given feature point in one 
+assumptions about image geometry. They improve on Lowe's 
+\emph{NN-Ratio} by attempting to match only feature points that have 
+a unique correspondence. The first algorithm, \emph{Mirror Match (MM)}, 
+is inspired by a simple but novel idea:  If a given feature point in one 
 image is better matched with other feature points from the \emph{same} 
@@
 Match with Clustering (MMC)} builds upon this idea by trying to group 
-similar feature points and match them separately from the feature points 
-that have unique correspondences. The experimental results show that 
-both approaches generally outperform existing correspondence matching 
+similar feature points and matching them separately from the feature points 
+that have unique correspondences. Our experimental results show that 
+both approaches generally outperform existing 
 methods when tested on partially overlapping images.
@@
 with Clustering (MMC)} algorithms.  Section~\ref{S:Experiments} presents 
-the dataset used for evaluation and the experimental setup.  
+the dataset and its use for the evaluation.  
 Section~\ref{S:Results} discusses the benchmarking results obtained.  
@@
 %
-\begin{figure}[h]
+\begin{figure}[ht]
 	\centering
@@
 the need for more image pairs featuring viewpoint changes, we have 
-compiled a set of 8 image pairs consisting of subjects taken from two 
-different angles. The images are collected from Flickr's database of 
-images published under a creative commons licence and feature murals, 
-which makes it possible to relate points in the image pairs with a 
-homography.  The images have been cropped to show the same motive and 
-resized to $900\times 600$ pixels.  This dataset will be referred to as 
-the \emph{Murals} dataset.  Figure~\ref{fig:murals} shows one image from 
-each pair.
-
-\begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{0.048\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pair_example1}
-%			\label{fig:fairey1}
-%	\end{subfigure}%
-%		\enspace %add desired spacing between images, e. g. ~, \quad, 
-%		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{0.048\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/pair_example2}
-%			\label{fig:fairey2}
-%		\end{subfigure}%
-%		\enspace %
-%		\begin{subfigure}[t]{0.36\textwidth}
-			\centering
-			\includegraphics[width=\columnwidth]{images/crop_examples}
-%		\end{subfigure}%
-%	}%
-	\caption{Sample test patches produced from an image pair.}
-	\label{fig:fairey}
-\end{figure}
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[width=\textwidth]{images/murals}
-	\caption{Images in the \emph{Murals} test set.}
-	\label{fig:murals}
-\end{figure*}
+compiled the \emph{Murals} dataset.\footnote{~The set of source images and homographies as well as 
+the script to generate the cropped test sets based on them can be found 
+at \url{http://vintage.winklerbros.net/murals.html}} It comprises 8 image pairs that feature murals taken from two 
+different angles, which makes it possible to relate points in the image pairs with a 
+homography.  The images were collected from Flickr's database of 
+photos published under a creative commons licence and have been cropped to show the same motive and 
+resized to $900\times 600$ pixels.  Figure~\ref{fig:murals} shows one image from each pair.
 
@@
 
-%However in practice the view point change has gone on to be used the 
-%most for later tests given that most of the other test pairs have since 
-%become easy to match\footnote{see \cite{wu2011robust} or 
-%\cite{delponte2006svd} for examples}.
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\textwidth]{images/murals}
+	\caption{Images in the \emph{Murals} dataset.}
+	\label{fig:murals}
+\end{figure*}
 
-%Inspired by the graffiti image we have collected a set of image pairs 
-%featuring murals of a few different artists\footnote{Including Banksy, 
-%Blu and Shepard Fairey among others}. Each pair consist of images of 
-%the same motive taken from different angles, often including repetitive 
-%patterns and texture. Based on this image set the two algorithms are 
-%tested on a series of image patches from each pair. To verify that the 
-%algorithms proposed are reliable we need to test that we get good 
-%matches when images overlap and that we get no matches when they do 
-%not.  This means that it isn't enough just testing against pairs of 
-%images that we know match.  We also need to test against pairs that 
-%might look like they could match but in fact do not.
-
-%
-%
-%\subsection{Experimental setup}
 We compare the \emph{MM} and \emph{MMC} algorithms to \emph{NN-Ratio} 
@@
 \emph{Spectral} use geometric constraints, whereas \emph{NN-Ratio} does 
-not.
-%, which uses geometric information to improve the matching.  The 
-%comparison  with \emph{NN-Ratio} serves to illustrate the relative 
-%performance of \emph{MM} and \emph{MMC} to a state of the art algorithm 
-%without geometric constraints. \emph{Isodata} is included to illustrate 
-%the performance of an algorithm relying on geometric constraints faced 
-%with image pairs that might not have any overlap.  
-The comparison was done using the \emph{Murals} dataset 
+not. The comparison was done using the \emph{Murals} dataset 
 (Figure~\ref{fig:murals}), the \emph{Graf} set (Figure~\ref{fig:Graf}) 
 from \cite{mikolajczyk2005performance}, and two images
-%\footnote{100\_1942.jpg and 100\_1941.jpg} from the Gallagher dataset 
-%\cite{gallagher2008} (Figure~\ref{fig:comparemirror}).
 
-Test sets were generated from the image pairs by cropping square patches of
-$250\!\times\!250$ pixels with a random vertical and horizontal offset.  
-Given a source image pair, we produce 100 pairs of patches, which might or might not overlap.  
-This ensures that patch pairs with no overlap still retain a general similarity to each 
-other, while patches that do overlap often only share a small 
-part of their area. Figure~\ref{fig:fairey} shows an example of 
-possible pairs of test image patches produced from a source image pair.  
+Test sets were generated from the image pairs by cropping square patches 
+of $250\!\times\!250$ pixels with a random vertical and horizontal 
+offset.  Given a source image pair, we produce 100 pairs of patches, 
+which might or might not overlap.  This ensures that patch pairs with no 
+overlap still retain a general similarity to each other, while patches 
+that do overlap often only share a small part of their area.  
+Figure~\ref{fig:fairey} shows an example of possible pairs of test image 
+patches produced from a source image pair.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{images/crop_examples}
+    \caption{Sample test patches produced from an image pair.}
+	\label{fig:fairey}
+\end{figure}
+
 Producing $n$ such pairs allows us to test not just how well the 
@@
 false positives we get on similar images that do not 
-overlap.\footnote{~The set of source images and homographies as well as 
-the script to generate the cropped test sets based on them can be found 
-at 
-\href{http://vintage.winklerbros.net/murals.html}{http://vintage.winklerbros.net/murals.html}}.  
+overlap.
 In practice the amount of overlap between pairs in a test set will 
@@
 generated from images 1 and 3 of the \emph{Graf} image set 
-(cf.~Figure~\ref{fig:Graf}). We plot the precision and recall of 
+(cf.~Figure~\ref{fig:Graf}). We plot the precision and recall for 
 \emph{MMC}, \emph{MM}, \emph{Isodata}, \emph{Spectral} and 
-\emph{NN-Ratio}. The precision and recall is calculated as follows:
+\emph{NN-Ratio}, which are calculated as follows:
 
 \begin{equation*}
-    Precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
-    ~ \# ~ False ~ Matches} \\
+    \textrm{Precision} = \frac{\#\textrm{Correct Matches}}{\#\textrm{Correct Matches} + 
+     \#\textrm{False Matches}} \\
 \end{equation*}
 \begin{equation*}
-    Recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~
-    Matches}
+    \textrm{Recall} = \frac{\#\textrm{Correct Matches}}{\#\textrm{Total Possible Matches}}
 \end{equation*}
@@
 both are performing at optimal accuracy.  Although \emph{Isodata} and 
-\emph{Spectral} exhibits a good performance on strict thresholds (small 
+\emph{Spectral} exhibit good performance on strict thresholds (small 
 number of matches), that quickly diminishes when more matches are 
@@
 \begin{figure}[htb]
-%	\makebox[0.5\textwidth][c]{%
-%		\begin{subfigure}[t]{.13\textwidth}
-%			\centering
-%			\includegraphics[width=\textwidth]{images/graf}
-%		\end{subfigure}%
-%		~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
-		%(or a blank line to force the subfigure onto a new line)
-%		\begin{subfigure}[t]{.27\textwidth}
     \centering
-            \includegraphics[width=0.8\columnwidth]{images/result_graf}
-			%\caption{Performance on Scharf}
-%		\end{subfigure}%
-%	}%
-	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The plot 
-		shows the result of 100 patch pairs generated from the source 
-		images shown to the left. The number of matches is the total 
-		number of matches for all 100 patch pairs.}
+    \includegraphics[width=0.9\columnwidth]{images/result_graf}
+    \caption{Results for 100 patch pairs generated from image pair 1\&3 
+from the \emph{Graf} set.}
 	\label{fig:result_graf}
@@
 \emph{Graf} pair tested above.  In total 900 different patch pairs were 
-generated from 9 source image pairs.  The results are shown in Figure 
-\ref{fig:result_accumulated}.
+generated from 9 source image pairs.  The results are shown in 
+Figure~\ref{fig:result_accumulated}.
 
@@
 	\centering
-    \includegraphics[width=0.8\columnwidth]{images/result_accumulated}
-	\caption{Results for 900 patch pairs extracted from the \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} set.  The x-axis shows the accumulated returned matches for all pairs.}
+    \includegraphics[width=0.9\columnwidth]{images/result_accumulated}
+	\caption{Results for 900 patch pairs extracted from the 
+    \emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} 
+    set.}
 	\label{fig:result_accumulated}
@@
 and \emph{NN-Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
-confirming that \emph{MMC} is generally superior to \emph{NN-Ratio} 
-across viewpoint changes.
-The performance of \emph{MM} (not shown in the plot) is similar to 
-\emph{MMC}.
+confirm that \emph{MMC} is generally superior to \emph{NN-Ratio} across 
+viewpoint changes. The performance of \emph{MM} (not shown in the plot) 
+is similar to \emph{MMC}.
 
@@
 	\centering
-    \includegraphics[width=0.8\columnwidth]{images/result_viewpoint}
+    \includegraphics[width=0.9\columnwidth]{images/result_viewpoint}
 	\caption{Results for viewpoint changes using the \emph{Graf} set from 
@@
 \centering
-\includegraphics[width=0.8\columnwidth]{images/result_pitts}
+\includegraphics[width=0.9\columnwidth]{images/result_pitts}
 \caption{Results for the image pair in Figure~\ref{fig:pitts_source}.}
@@
 total number of feature points.  \emph{Spectral} and our current 
-\emph{MMC} implementation has a complexity of $O(n^2)$ due to the 
+\emph{MMC} implementation have a complexity of $O(n^2)$ due to the 
 construction of a similarity matrix of the feature points. However, both
@@
 	%
-	Running time (seconds): & 21 & 23 & 2722 & 1146 & 994\\
+	Running time: & 21s & 23s & 2722s & 1146s & 994s\\
 	\hline
@@
 data set. \emph{MM} and \emph{MMC} generally outperform existing 
-matching algorithms \emph{NN-Ratio} and \emph{Isodata}, and \emph{MMC} 
-outperforms \emph{MM}. We show that this result generalizes to 
-variations in viewpoint change as well as more realistic photos 
-featuring occlusions.
+matching algorithms \emph{NN-Ratio}, \emph{Spectral} and \emph{Isodata}, 
+and \emph{MMC} outperforms \emph{MM}. We show that this result 
+generalizes to variations in viewpoint change as well as more realistic 
+photos featuring occlusions.
 
@@
 apply them to problems that require high reliability faced with images 
-that might not match, such as near duplicate detection or face 
-recognition.
+that might not match, such as near duplicate detection or image 
+retrieval.
 
+\vspace{2mm}
 \textit{This work is supported by the research grant for ADSC's Human 

### 2013-09-19 code/ballmatch.py

@@ -86,22 +86,13 @@ def match_radius(paths, options = {}) :
                 idxs = numpy.array(bt.query_radius(descriptor, r=radius_size)[0])
                 group_size = len(idxs)
 
-                # If the group size is bigger than 4 items
-                if group_size >= group_limit :
-                    for (i, j), m, s, u in query_cluster(idxs, ds, ratio_boost, indices, ks) : 
-                        if not (i,j) in seen :
-                            seen.add((i, j))
-                            seen.add((j, i))
-                            yield m, s, u, group_size
+                # Get unique match
+                for (i,j), m, s, u in query_unique(bt, i, descriptor, indices, ks) : 
 
-                # If the group size is less use mirror match
-                else :
-                    for (i,j), m, s, u in query_unique(bt, i, descriptor, indices, ks) : 
-                        if not (i,j) in seen :
-                            seen.add((i, j))
-                            seen.add((j, i))
-                            yield m, s, u, group_size
-
+                    if group_size >= group_limit :
+                        yield m, s, u*ratio_boost, group_size
+                    else :
+                        yield m, s, u, group_size
 
     # Get matches
     match_data = list(query_all())
@@ -114,20 +105,6 @@ def match_radius(paths, options = {}) :
             return zip(*matches)
 
     return lambda t : match_fun(t)
-
-
-def query_cluster_best(idxs, i, ds, ratio_boost, indices, ks) :
-    pass
-
-def query_cluster(idxs, ds, ratio_boost, indices, ks) :
-    ds_cluster = ds[idxs]
-    ks_cluster = ks[idxs]
-    indices_cluster = indices[idxs]
-    bt = BallTree(ds_cluster, leaf_size=10)
-    for i, d in enumerate(ds_cluster) :
-        matches = query_unique(bt, i, d, indices_cluster, ks_cluster, ratio_boost)
-        for (k,j), m, s, u in matches : yield (idxs[k], idxs[j]), m, s, u
-
 
 def query_unique(tree, i, descriptor, indices, ks, ratio_boost = 1) : 
     #print("."),

### 2013-09-19 code/clustermatch.py

@@ -37,7 +37,7 @@ def match(paths, options = {}) :
     cluster_prune_limit = options.get("cluster_prune_limit", 1.5)
 
     # Get all feature points
-    indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
+    indices, ks, ds = features.getFeatures(paths, options)
 
     # Calculate weight matrix
     weights = weightMatrix.init(ds, descriptor_type)

### 2013-09-19 code/display.py

@@ -374,7 +374,7 @@ def accuPlot(correct, total, legends, colors = ["blue", "red", "green", "orange"
     # Remove superflous lines and add axis labels
     removeDecoration()
     if nb_correspondences != None :
-        pylab.xlabel("#Correct / %i" % nb_correspondences)
+        pylab.xlabel("Recall" % nb_correspondences)
     else :
         pylab.xlabel("# of Matches")
     pylab.ylabel("Precision")

### 2013-09-19 code/features.py

@@ -39,47 +39,72 @@ supported_descriptor_types = ["SIFT","SURF","ORB","BRISK","BRIEF","FREAK"]
 ####################################
 
 
-def getFeatures(paths, keypoint_type = "SIFT", descriptor_type = "SIFT", shuffle = False) :
+def getFeatures(paths, options = {}) :
     """ Given a list of paths to images, the function returns a list of 
         descriptors and keypoints
         Input: paths [list of strings] The paths to the images we are using
+               options [dictionary of options] shuffle, group, max_kp, keypoint_type, descriptor_type
         Out:   [pair of list of descriptors and list of keypoints]
     """
-    # Get all images and labels
-    labels = map(getLabel, paths)
+
+    # Get options
+    shuffle             = options.get("shuffle", False)
+    group               = options.get("group", False)
+
+    # Get all images
     images = map(loadImage, paths)
 
-    # Get feature descriptors
+    # Find feature points
     if shuffle :
-        keypoints = [numpy.array(getKeypoints(keypoint_type, im)) for im in images]
+        keypoints = [numpy.array(getKeypoints(im, options)) for im in images]
         map(numpy.random.shuffle, keypoints)
     else :
-        keypoints = [numpy.array(getKeypoints(keypoint_type, im)) for im in images]
+        keypoints = [numpy.array(getKeypoints(im, options)) for im in images]
 
-    data = [getDescriptors(descriptor_type, im, k) for (im, k) in zip(images, keypoints)]
+    # Describe featre points
+    data = [getDescriptors(im, k, options) for (im, k) in zip(images, keypoints)]
     keypoints, descriptors = zip(*data)
 
-    # Check that we could get descriptors for all images
+    # Check that we could get descriptors for all images (TODO: throw exception?)
     if sum(map(lambda d : d == None, descriptors)) > 0 : return (None, None, None)
-    indices = [l for i, n in zip(range(len(labels)), map(len, descriptors)) for l in [i]*n]
-    ind = numpy.array(indices)
-    return (ind, numpy.concatenate(keypoints), numpy.concatenate(descriptors))
+
+    # Create a list of indices
+    indices = numpy.concatenate([numpy.array([i]*n) for i,n in zip(range(len(paths)), map(len, descriptors))])
+
+    # Should we concatenate?
+    if group :
[…]

### 2013-09-19 code/isomatch.py

@@ -47,7 +47,7 @@ def match(paths, options = {}) :
     images = map(features.loadImage, paths)
 
     # Get all feature points
-    indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
+    indices, ks, ds = features.getFeatures(paths, options)
 
     # Get positions
     positions = numpy.array(features.getPositions(ks))

### 2013-09-19 code/matching.py

@@ -283,6 +283,18 @@ def mirrorMatch(distance_threshold, paths, homography, thresholds, keypoint, des
     return evaluate(match_fun, thresholds, homography)
 
 
+def mirrorOnlyMatch(distance_threshold, paths, homography, thresholds, keypoint, descriptor) :
+    options = {
+        "thresholds" : thresholds,
+        "distance_threshold" : distance_threshold,
+        "keypoint_type" : keypoint,
+        "descriptor_type" : descriptor,
+        "only_mirror" : True,
+    }
+    match_fun = mirrormatch.match(paths, options)
+    return evaluate(match_fun, thresholds, homography)
+
+
 def ballMatch(distance_threshold, paths, homography, thresholds, keypoint, descriptor) :
     options = {
        "leaf_size": 10,

### 2013-09-19 code/mirrormatch.py

@@ -27,43 +27,79 @@ def match(paths, options = {}) :
         return (features.getPosition(ks[i]), features.getPosition(ks[j]))
 
     # Get options
-    keypoint_type		= options.get("keypoint_type", "SIFT")
-    descriptor_type		= options.get("descriptor_type", "SIFT")
-    include_keypoints	= options.get("include_keypoints", False)
     with_pruned         = options.get("with_pruned", False)
+    only_mirror         = options.get("only_mirror", False)
+
+    # Add options
+    options['group'] = only_mirror
+    options['match_same'] = True
 
     # Get all feature points
-    indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
+    indices, ks, ds = features.getFeatures(paths, options)
 
     # Use cv2's matcher to get matching feature points
-    jj,ss,uu = features.bfMatch(descriptor_type, ds, ds, match_same=True)
-    
+    if only_mirror :
+        jj, ss, uu = features.mirrorMatch(ds, options)
+    else :
+        jj, ss, uu = features.bfMatch(ds, ds, options)
+
     # See if matches go both ways
-    bothways = [(i,j) for i,j in enumerate(jj) if indices[i] == 0 and indices[j] == 1 and jj[j] == i]
-    
-    if with_pruned :
-        im1_ways = [(i,j) for i,j in enumerate(jj) if indices[i] == 0 and indices[j] == 0 and jj[j] == i]
-        im2_ways = [(i,j) for i,j in enumerate(jj) if indices[i] == 1 and indices[j] == 1 and jj[j] == i]
+    nb_images = len(paths)
+    seen = set([])
+    def add_match(i,j) :
+        seen.add((i,j))
+        seen.add((j,i))
+        return (i,j)
+    bothways = [add_match(i,j) for i, j in enumerate(jj) if (not (i,j) in seen) and (nb_images > 2 or jj[j] == i)]
+
+    # Define a function that given a threshold returns a set of matches
+    def match_fun(threshold) :
+        match_data = [(matchPos(i, j), ss[i], uu[i], (indices[i],indices[j])) for i,j in bothways if uu[i] < threshold]
+        if len(match_data) == 0 : return [], [], []
+        return zip(*match_data)
+
+    return match_fun
+
+
+# C/P version for creating a figure containing the wrong match within an image
+def match_show(paths, options = {}) : 
+    # Returns the position of a match
[…]

### 2013-09-19 code/ratiomatch.py

@@ -34,18 +34,16 @@ import numpy
 
 def match(paths, options = {}) :
 
-    keypoint_type		= options.get("keypoint_type", "SIFT")
-    descriptor_type		= options.get("descriptor_type", "SIFT")
     use_ball_tree       = options.get("use_ball_tree", False)
 
     # Get all feature points
-    indices, ks, ds = features.getFeatures(paths, keypoint_type = keypoint_type, descriptor_type = descriptor_type)
+    indices, ks, ds = features.getFeatures(paths, options)
 
     # Use cv2's matcher to get matching feature points
     if use_ball_tree :
-        ii, ss, uu = features.ballMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
+        ii, ss, uu = features.ballMatch(ds[indices == 0], ds[indices == 1])
     else :
-        ii, ss, uu = features.bfMatch(descriptor_type, ds[indices == 0], ds[indices == 1])
+        ii, ss, uu = features.bfMatch(ds[indices == 0], ds[indices == 1])
 
     # Get all positions
     (pos_im1, pos_im2) = (features.getPositions(ks[indices == 0]), features.getPositions(ks[indices == 1]))

### 2013-12-04 code/features.py
Updated turntable

@@ -20,6 +20,7 @@ import cv2
 import numpy
 import trees
 import collections
+import pylab
 from sklearn.neighbors.ball_tree import BallTree
 
 
@@ -96,7 +97,7 @@ def getKeypoints(image, options = {}) :
     # Get amount of feature points
     keypoint_type		= options.get("keypoint_type", "SIFT")
     max_kp              = options.get("max_kp", 9999) 
-    #kp_threshold        = options.get("kp_threshold", (0.04, 10.0))
+    kp_threshold        = options.get("kp_threshold", (0.04, 10.0))
     verbose             = options.get("feature_verbose", False)
 
     if verbose : print(":"),
@@ -106,7 +107,7 @@ def getKeypoints(image, options = {}) :
 
     # Get specific feature type
     if keypoint_type.upper() == "SIFT" :
-        feature = cv2.SIFT()#nfeatures = max_kp, contrastThreshold = kp_threshold[0], edgeThreshold = kp_threshold[1])
+        feature = cv2.SIFT()#nfeatures = max_kp)#, contrastThreshold = kp_threshold[0], edgeThreshold = kp_threshold[1])
     elif keypoint_type.upper() == "FAST" :
         feature = cv2.FastFeatureDetector()
     elif keypoint_type.upper() == "SURF" :
@@ -229,12 +230,17 @@ def match(D, indices, options = {}) :
                 # Get the baseline score
                 score_baseline = dist_baseline[fst_baseline]
 
-                # For each match we make in the images
-                for i in range(fst_proposed, len(idx_proposed)) :
-                    index_to = index_map_to[idx_proposed[i]]
-                    score_proposed = dist_proposed[i]
-                    ratio = score_proposed / float( score_baseline )
-                    yield (index_from, index_to), score_proposed, ratio
+                index_to = index_map_to[idx_proposed[fst_proposed]]
+                score_proposed = dist_proposed[fst_proposed]
+                ratio = score_proposed / float( score_baseline )
+                yield (index_from, index_to), score_proposed, ratio
+
+                ## For each match we make in the images
+                #for i in range(fst_proposed, len(idx_proposed)) :
+                #    index_to = index_map_to[idx_proposed[i]]
+                #    score_proposed = dist_proposed[i]
+                #    ratio = score_proposed / float( score_baseline )
+                #    yield (index_from, index_to), score_proposed, ratio
 
 
     # Produce matches within the same tree

### 2013-12-04 code/matching.py

@@ -30,6 +30,7 @@ import ratiomatch
 import features
 import weightMatrix
 import display
+import trees
 
 
 
@@ -40,25 +41,48 @@ import display
 ####################################
 
 
-def evaluate(match_fun, thresholds, homography, return_matches = False) :
+def evaluate(match_fun, paths, thresholds, homography, options) :
 
-    match_set = [match_fun(t)[0] for t in thresholds]
+    # Get distance_threshold
+    distance_threshold      = options.get("distance_threshold", 5)
+    verbose                 = options.get("evaluate_verbose", False)
+    metric                  = options.get("metric", "match_count")
+
+    # Get matches
+    positions, distances, ratios, image_indices, indices = match_fun(paths, options = options)(9999)
+
+    if verbose :
+        path = lambda p : "/".join(p.split("/")[-2:])
+        print("Found %i matches for images (%s, %s)" % (len(ratios), path(paths[0]), path(paths[1])))
 
     # Get distances
-    getDist = lambda ms : [matchDistance(m1, m2, homography) for (m1, m2) in ms]
-    match_dist = [getDist(ms) for ms in match_set]
+    distances = [matchDistance(p1, p2, homography) for (p1, p2) in positions]
 
-    if return_matches : return match_set, match_dist
-    else : return match_dist
+    if verbose :
+        print("Found %i distances" % (len(distances)))
+
+    # Collect precision per ratio_threshold
+    if metric == "match_count" :
+        def get_count(t, dt) : return len([1 for d,r in zip(distances, ratios) if r <= t and d < dt])
+        correct = [get_count(t, distance_threshold) for t in thresholds]
+        total = [get_count(t, 9999999) for t in thresholds]
+        return { "correct" : correct, "total" : total }
+
+    if metric == "ratio" :
+        correct = [r for d,r in zip(distances, ratios) if d < distance_threshold]
+        return { "correct" : correct, "total" : ratios }
 
 
-def folderMatch(directory, dt, match_fun, thresholds, keypoint, descriptor) : 
+def folderMatch(directory, match_fun, options) : 
+
+    # Get distance_threshold
+    distance_threshold      = options.get("distance_threshold", 5)
 
     def flatten(l) :
         return list(itertools.chain.from_iterable(l))
 
     def nb_correct_matches(distances) :
[…]

### 2013-12-04 code/mirrormatch.py

@@ -36,6 +36,14 @@ def match(paths, options = {}) :
     # Get all feature points
     indices, ks, ds = getFeatures(paths, filter_features, options)
 
+    if verbose : print("\n%i Keypoints found" % (len(ks)))
+
+    # Check that we have enough features to continue
+    if len(ks[indices == 0]) <= 3 :
+        def fun(t) :
+            return [], [], [], [], []
+        return fun
+
     # Match
     match_data = features.match(ds, indices, options)
 

### 2013-12-04 code/turntable.py

@@ -17,6 +17,7 @@ import features
 import os
 import fnmatch
 import display
+import matching
 import mirrormatch
 import colors
 import random
@@ -42,6 +43,7 @@ def evaluate(match_fun, angles, object_type, thresholds, ground_truth_data = Non
     # Get distance_threshold
     distance_threshold      = options.get("distance_threshold", 5)
     verbose                 = options.get("evaluate_verbose", False)
+    metric                  = options.get("metric", "match_count")
 
     # Get paths to the three images
     def get_path(i) : return {
@@ -57,7 +59,7 @@ def evaluate(match_fun, angles, object_type, thresholds, ground_truth_data = Non
 
         # Collect matches
         paths = get_path(i)
-        return match_fun([paths["A"], paths["C"]], options = options)(1.0)
+        return match_fun([paths["A"], paths["C"]], options = options)(9999)
 
 
     # Get match results
@@ -76,14 +78,21 @@ def evaluate(match_fun, angles, object_type, thresholds, ground_truth_data = Non
         print("Found %i distances" % (len(distances)))
 
     # Collect precision per ratio_threshold
-    def get_count(t, dt) : return len([1 for d,r in zip(distances, ratios) if r <= t and d < dt])
-    correct = [get_count(t, distance_threshold) for t in thresholds]
-    total = [get_count(t, 9999999) for t in thresholds]
-    return { "correct" : correct, "total" : total }
+    if metric == "match_count" :
+        def get_count(t, dt) : return len([1 for d,r in zip(distances, ratios) if r <= t and d < dt])
+        correct = [get_count(t, distance_threshold) for t in thresholds]
+        total = [get_count(t, 9999999) for t in thresholds]
+        return { "correct" : correct, "total" : total }
+
+    if metric == "ratio" :
+        correct = [r for d,r in zip(distances, ratios) if d < distance_threshold]
+        return { "correct" : correct, "total" : ratios }
 
 
 
-def evaluate_objects(match_fun, angles, object_types, thresholds, ground_truth_data, options = {}) :
+
+
+def evaluate_objects(match_fun, angles, object_types, thresholds, ground_truth_data = None, options = {}) :
     """ Returns number of correct and total matches of match_fun on objects:
         match_fun : Function (Function that takes a list of paths and returns matches)
[…]

### 2013-12-04 text/journal/paper.tex
Added journal paper

\documentclass[journal]{IEEEtran}
%\documentclass{article}
\usepackage{footnote}
\usepackage{multirow} 
%\usepackage[font={small}]{caption}
%\usepackage{sidecap}
\usepackage{graphicx}
\usepackage{cite}
\usepackage[draft]{hyperref}
%\usepackage[options]{nohyperref}
%\usepackage{url}
%\usepackage[stable]{footmisc}
%\usepackage{caption}
%\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%\usepackage{authblk}
\pdfminorversion=4
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand{\twopartdef}[4]
{
	\left\{
		\begin{array}{ll}
			#1 & \mbox{if } #2 \\
			#3 & \mbox{if } #4
		\end{array}
	\right.
}

\title{A general framework for local feature matching in images}

\author{%
\IEEEauthorblockN{%
Jonas Toft Arnfred,\IEEEauthorrefmark{1} Stefan 
Winkler,\IEEEauthorrefmark{1} Sabine S\"usstrunk\IEEEauthorrefmark{2}}\\
\vspace{1mm}
\IEEEauthorblockA{%
\IEEEauthorrefmark{1}~Advanced Digital Sciences Center (ADSC), University of Illinois at Urbana-Champaign (UIUC), Singapore\\
\IEEEauthorrefmark{2}~\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland}
}

\begin{document}
\maketitle
%
\begin{abstract}
TODO
\end{abstract}
%
\section{Introduction}
%
Matching image points is a crucial ingredient in almost all computer 
vision algorithms that deal with sparse local image features. This 
includes image categorisation \cite{bosch2008scene}, image stitching 
\cite{brown2007automatic}, object detection \cite{zhang2007local} and 
near duplicate detection \cite{zhao2009scale} to mention a few examples.  
These problems all rely on being able to accurately find the 
correspondence(s) of a point on an object in a \emph{query image} given 
one or more \emph{target images} that might contain the same object.  In 
many applications the target images have undergone transformations with 
respect to the query image; in stereo vision, the camera angle is 
different, while in object recognition and near duplicate detection both 
the lighting and even the object itself can also be transformed.

In the literature two approaches to feature point matching have been 
pursued and later merged. The geometric approach tries to find unique 
keypoints in an image pair and match them based on their location.  The 
descriptor centric approach on the other hand uses the local image 
information around the keypoint to create a descriptor and match 
descriptors based on their similarity.

In the purely geometric approach we try to consistently match feature 
points based on their position in the images. Scott and Longuet-Higgins 
\cite{scott1991algorithm} and Shapiro and Brady 
\cite{shapiro1992feature} introduced the use of spectral methods by 
deriving a coherent set of matches from the eigenvalues of the 
correspondence matrix. Other examples of this approach include Sclaroff 
and Pentland \cite{sclaroff1995modal} as well as Carcassoni and Hancock 
\cite{carcassoni2003spectral}.

The descriptor centric approach on the other hand finds matches by 
pairing keypoints from locations where the images are similar. The first 
examples of this approach used the correlation of the raw image data 
immidiately surrounding the feature point \cite{deriche1994robust}, 
\cite{baumberg2000reliable} to calculate this similarity. Later 
algorithms were enhanced by creating invariant feature descriptors first 
introduced in \cite{schmid1997local} and later popularized by the work 
of Lowe introducing SIFT \cite{lowe2004sift} and Bay introducing SURF 
\cite{bay2006surf}.

Many descriptor variations have since been proposed and a few surveys 
have emerged comparing them. Mikolajczyk and Schmid evaluates 11 such 
feature descriptors in a paper where they also introduce the graffiti 
image set which has later become a common benchmark for image matching 
algorithms \cite{mikolajczyk2005performance}.  Later Moreels and Perona 
evaluated 5 descriptors with different keypoint detectors using a large 
image set consisting of 3D models \cite{moreels2007evaluation}. Finally 
Heinly et al.\ take a closer look at binary features such as BRIEF 
\cite{calonder2010brief}, BRISK \cite{leutenegger2011brisk} and ORB 
\cite{rublee2011orb} comparing them to SIFT and SURF 
\cite{heinly2012comparative}.

A straightforward way to find a set of correspondences using only 
feature points is to threshold the similarity measure of the feature 
vectors, accepting only correspondences that score above a certain 
threshold \cite{szeliski2010}. When we match images with the assumption 
that the correspondence between two feature points will be unique we can 
further increase precision by only matching a feature point to its 
nearest neighbor in terms of descriptor similarity. Instead of 
thresholding based on similarity, Deriche et 
al.~\cite{deriche1994robust} and Baumberg~\cite{baumberg2000reliable} 
propose using the ratio of the similarity of the best to second best 
correspondence of a given point to evaluate how unique it is. Their 
finding has later been tested by several independent teams, all 
concluding that thresholding based on the ratio is generally superior to 
thresholding on similarity \cite{lowe2004sift}, 
\cite{mikolajczyk2005performance}, \cite{moreels2007evaluation}, 
\cite{rabin2009statistical}. Brown and Lowe extends ratio match to deal 
with a set of images by using not the ratio of the best and second best 
correspondence, but the average ratio of the best and the average of 
second best correspondences across a set of images 
\cite{brown2005multi}.  Rabin et al.\ tries to enhance descriptor 
matching by looking at the statistical distribution of local features in 
the matched images, and only return a correspondence when such a 
correspondence would not occur by mere chance 
\cite{rabin2009statistical}. Finally, a precursor of the algorithms 
discussed in this paper were introduced by the authors as 
\emph{Mirror-Match} \cite{arnfred2013mirror} which makes use of the 
feature points in both images to decide if a match is valid.

A plethora of solutions have combined ratio match with various geometric 
constraints to improve matching. These constraints are
based on assumptions regarding the transformation between the query and 
target images. At the stricter end we have epipolar constraints assuming
that the images can be tied by a homography \cite{torr2000mlesac}, 
\cite{chum2005matching} and angular constraints assuming the 
correspondences are angled similarly \cite{kim2008efficient}, 
\cite{schmid1997local}, \cite{leordeanu2005spectral}. Instead of 
modelling the relationship between two images as an epipolar relation, 
we can try to allow for more lenient transformation with more 
sophisticated models.  Torresani et al.~\cite{torresani2008feature} 
attempted to model these transformations using graph matching similar to 
\cite{deriche1994robust}. Others define image regions and reject or 
accept correspondences based on the regions they connect 
\cite{cho2009feature}, \cite{wu2011robust}.

Any matching method relying on geometric constraints is restrained by an
inherent assumptions about the geometric relationship between the two 
images. Broad assumptions such as the epipolar constraint only apply in 
simple image transformations. For more complex transformations we need 
models suitable for each particular case and hence limit the algorithm 
to the subset of images that fit the model.  In the case of object 
recognition for example, the transformations from one scene to another 
often feature a change
in perspective, background and sometimes variations within the object 
itself.  A person can change pose, a car model can have different 
configurations, a flower can bloom etc.

When matching these instances we are forced to either create a 
sophisticated model that represents the variables of transformation 
within the object, or alternatively find correspondences using an 
algorithm with no inherent geometric assumptions. In addition the 
advantage of purely descriptor based methods is motivated by the fact 
that any geometric method acts as a filter on a given set of 
correspondences.  If this set contains less incorrect correspondences, 
the final set can be calculated faster and more accurately.

The methods we propose in this paper are designed to be free of 
assumptions about image geometry. They extend and improve on Lowe's 
\emph{Ratio-Match} \cite{lowe2004sift} and the author's \emph{Mirror 
Match} \cite{arnfred2013mirror} by generalizing both algorithms to a 
framework of matching methods. We go on to formally establish an order 
comparing how well different methods within the framework compares in 
terms of precision and recall. Our experimental evaluations confirm the 
theoretical results and show that \emph{Ratio-Match} on all counts is a 
unoptimal choice as a matching algorithm independent of application.

The paper is organized as follows. I section~\ref{S:MatchingMethods} we 
introduce the original \emph{Ratio-Match}, extend on this method to 
introduce the proposed framework and go on to compare the members of the 
framework theoretically.  In section~\ref{S:Experiments} we present 
evaluations and discuss the results obtained.  Section~\ref{S:Summary} 
concludes the paper.

\section{Matching Methods}
\label{S:MatchingMethods}
%
\subsection{Ratio-Match}
%
\emph{Ratio-Match} as introduced by Deriche et al.
\cite{deriche1994robust} and later used by 
Baumberg~\cite{baumberg2000reliable} and Lowe~\cite{lowe2004sift} makes 
use of a \emph{uniqueness ratio}. For each feature in the \emph{query 
image} we find a possible match by identifying the nearest neighbor and 
returning this match only if the \emph{uniqueness ratio} is above a 
given threshold, $\tau$. Given $f_q$, a feature from the \emph{query 
image} and $F_{target}$, a set of features from the \emph{target image}, 
the nearest neighbor of $f_q$ in $F_{target}$ is:
\begin{equation*}
    f_{nn} = \argmin_{f_t \in F_{target}} d(f_q, f_t)
\end{equation*}
Here, $d(f_i, f_j)$ is the distance between the feature descriptors.  
With SIFT and SURF this is the euclidian distance of the feature vectors
\cite{lowe2004sift} \cite{bay2006surf} where as BRIEF, BRISK and FREAK 
measure the distance as the hamming distance \cite{leutenegger2011brisk} 
\cite{calonder2010brief} \cite{alahi2012freak}.  If we let $f_p$ and 
$f_b$ be the nearest and second nearest neighbor of a feature, $f_q$, 
the \emph{uniqueness ratio} is defined as follows:
\begin{equation*}
    r = d(f_q, f_p) / d(f_q, f_b)
\end{equation*}
Because $f_p$ is the nearest neighbor and $f_b$ the second nearest 
neighbor we know that $d(f_q, f_p) \leq d(f_q, f_b)$ and since $d(f_i, 
f_j) \geq 0, \forall f_i,f_j$, the uniqueness ratio is bounded by $0$ 
and $1$, both inclusive. For the degenerate case where $d(f_q, f_b) = 0$
we let the \emph{uniqueness ratio} be $0$.

The underlying assumption in ratio match is that the point we seek to 
match in the \emph{query image} has only one match in a given 
\emph{target image} or no matches at all. In both cases should expect 
that the \emph{second} nearest neighbor in the target image to be an 
untrue correspondence.  This means we can use the distance between the 
feature point and the second closest descriptor as a \emph{baseline} for 
false correspondences. By dividing the distance to the nearest neighbor 
with this baseline we get an estimated measure for how distinct the 
correspondence is from a false match.

To make further discussion easier we introduce the following 
nomenclature:

\begin{itemize}
\item{Let $f_q$ be any feature point in the \emph{query image} that we 
    are currently trying to match}
\item{Let $F$ be a set of features. $F_{target}$ for example is the set 
    of features from the \emph{target image}}
\item{Let $\tau \in [0 \ldots 1]$ be a threshold used to decide whether 
    to keep a match or discard it. We keep a match only if is has a 
\emph{uniqueness ratio} lower than $\tau$}
\item{Let the \emph{proposed match} be the nearest neighbor of $f_q$
    picked from a set of feature points that we will call the 
\emph{proposal set} which does not include $f_q$}
\item{Let the \emph{baseline match} be the nearest neighbor of $f_q$ 
    picked from a set of feature points that we will call the 
\emph{baseline set} which neither contains the \emph{proposed match} nor 
$f_q$}
\end{itemize}

In the case of \emph{Ratio-Match} \cite{lowe2004sift} the \emph{proposal 
set} consists of all the feature points in the target image.  Similarly 
the \emph{baseline set} consists of all the feature points in the target 
image except the \emph{proposed} match. For \emph{Ratio-Match} this 
practically means that given a feature, $f_q$, the \emph{proposed match} 
and the \emph{baseline match} are the two nearest neighbors in the set 
of feature points in the \emph{target image}.

Brown et al.\ extends \emph{Ratio-Match} for the case of $n$ target 
images by letting the baseline be the average of the distance to the 
second nearest neighbors for all $n$ target images 
\cite{brown2005multi}.  ``\emph{[W]e can improve outlier rejection}'' 
they write ``\emph{by using information from all of the images (rather 
than just the two being matched) This improves the matching 
precision}''.  The idea of improving matching precision by expanding the 
knowledge used to reject outliers is the central tenet in this paper.

\begin{figure}[t]
\centering
\includegraphics[width=0.85\columnwidth]{images/overview}
\caption{Graphical representation of the \emph{Baseline} and 
\emph{Proposal Set} for different methods in the proposed framework}
\label{fig:overview}
\end{figure}
%
\subsection{A framework of matching methods}
%
\begin{table}[htb]
\caption{Calculating the uniqueness ratio using different sources for 
    the \emph{proposal set} and \emph{baseline set} for the case of two 
images.}
\label{table:distinctness}
	\centering
%	\small
\bgroup
\def\arraystretch{1.5}
    \begin{tabular}{l l | l l}
        %
        %&  \multicolumn{1}{l}{Target}
        %& \multicolumn{1}{l}{Target and Query} \\
\multicolumn{2}{r}{} & \multicolumn{2}{c}{\emph{Proposal Set}} \\
                     & & Target & Target and Query \\
        \cline{2-4}
        \multirow{3}{*}{\rotatebox[origin=c]{90}{\emph{Baseline Set}}} &
  Query            & \emph{Self-Match}   & \emph{Self-Match-Ext} \\
& Target           & \emph{Ratio-Match}   & \emph{Ratio-Match-Ext} \\
& Target and Query & \emph{Mirror-Match} & \emph{Mirror-Match-Ext} \\
        \cline{2-4}
\end{tabular}
\egroup
\end{table}

\emph{Ratio-Match} is only one instance of a framework of algorithms we can 
construct by different combinations of \emph{proposed} and 
\emph{baseline sets}. As shown in Table~\ref{table:distinctness} for the 
case of two images the \emph{proposal set} can be constructed by either 
looking only at the nearest neighbors in the target image, or 
alternatively by looking at the nearest neighbors in both the query and 
target image. The \emph{baseline set} can either be the query image 
itself, the target image or the combination of the two.  Seen in this 
light, the matching algorithm \emph{Ratio-Match} draws both its 
\emph{proposal set} and \emph{baseline set} from the target image. In 
turn \emph{Mirror-Match-Ext} as introduced by the authors in 
\cite{arnfred2013mirror}, works by constructing the \emph{proposal set} 
and \emph{baseline set} by combining features from both the \emph{query} 
and \emph{target image}. Alternatively \emph{Self-Match} looks only to 
the query image for the \emph{baseline set} but constructs the 
\emph{proposal set} from the target image like \emph{Ratio-Match}. In 
Figure~\ref{fig:overview} we illustrate how each method is derrived.

\begin{algorithm}[htb]
\caption{Generalized matching algorithm for two images}
\label{alg-gen}
\begin{algorithmic}
    \Require $I_{query}, I_{target}$ : images, $\tau \in [0,1]$
    \State $F_{query} = get\_features(I_{query})$
    \State $F_{target} = get\_features(I_{target})$
\State $F_{proposal} = get\_proposal\_set(F_{query}, F_{target})$
\State $F_{baseline} = get\_baseline\_set(F_{query}, F_{target})$
\State $M = \varnothing$
\ForAll{$f_q \in F_{query}$}
    \State $f_p \gets getNearestNeighbo\text{r}(f_q, F_{proposal} \setminus 
    \left\{f_q\right\})$
    \State $f_b \gets getNearestNeighbo\text{r}(f_q, F_{baseline} \setminus 
    \left\{f_q, f_p\right\})$
    \State $ratio \gets distance(f_q, f_p) / distance(f_q, f_b)$
    \If{$(ratio < \tau) \wedge (f_p \in F_{target})$}
        \State $matches \gets matches \cup \left(f_q, f_p\right)$
	\EndIf
\EndFor
\Return $M$
\end{algorithmic}
\end{algorithm}

In algorithm~\ref{alg-gen} we show the generalized matching framework 
where the \emph{proposal set} and \emph{baseline set} are defined 
according to Table~\ref{table:distinctness}.  In practice for i.e.\ 
\emph{Ratio-Match} we can obtain $f_p$ and $f_b$ by finding the 2 
nearest neighbors of $F_{target}$. The other algorithms can be optimized 
similarly. In Figure~\ref{fig:matching} we illustrate the structure of 
this algorithm.

For some methods it is possible that the \emph{proposal match} is a 
feature from the \emph{query image}, in which case we discard the match 
as an untrue correspondence.  It also happens that we encounter 
correspondences where the uniqueness ratio is more than $1$ in which 
case we set it to $1$ to maintain a bounded \emph{uniqueness ratio}.  
Take for example the case of \emph{Self-Match}. Using this method we 
might find that the nearest neighbor of a feature in the target image is 
further from the query feature than the nearest neighbor in the query 
image. In this case the match is discarded.

\subsection{Generalized Uniqueness Ratio}

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{images/matching}
\caption{Flow chart showing what happens when we match a feature. $\tau$ 
is the ratio threshold and $d(x,y)$ is the distance between two feature 
descriptors, $x$ and $y$.}
\label{fig:matching}
\end{figure}
%

For $F_{query} = \left\{f_{q_1} \ldots f_{q_n}\right\}$ and $F_{target} 
= \left\{f_{t_1} \ldots f_{t_m}\right\}$.  We can obtain $F_{proposed}$ 
and $F_{baseline}$ from these sets according to the algorithm used (see 
Table~\ref{table:distinctness}). $r = \text{r}(f_{q}, F_{proposed}, 
F_{baseline})$ is the ratio of query feature $f_{q}$ given 
$F_{proposed}$ and $F_{baseline}$.  If $f_{p}$ is the nearest neighbor 
of $f_{q}$ in $F_{proposed}$ and $f_{b}$ is the nearest neighbor of 
$f_{q}$ in $F_{baseline} \setminus \left\{f_{p}\right\}$ then the 
generalized \emph{uniqueness} ratio is:
\begin{align*}
    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
        &= \frac{d(f_{q}, f_{p})}{d(f_{q}, f_{b})}
\end{align*}
We let $K$ be the number of possible true correspondences \emph{query} 
and \emph{target image}. The \emph{precision} and \emph{recall} are then 
defined as:
\begin{align*}
    \textrm{Recall} &= \frac{\#\textrm{Correct Matches}}{K} \\
    \textrm{Precision} &= \frac{\#\textrm{Correct 
    Matches}}{\#\textrm{Correct Matches} + \#\textrm{Incorrect Matches}}
\end{align*}
Given $f_{nn} \in F_{target}$ defined as the nearest neighbor of any 
$f_q \in F_{query}$ then we define the set of features $F_{true}$ as 
$\left\{ f_{q} \in F_{query} \mid f_{nn} \text{ is a true correspondence 
of } f_{q} \right\}$ and $F_{false}$ as $F_{query} \setminus F_{true}$.  
We can the define the number of correct and incorrect matches as 
follows:
\begin{align*}
    \textrm{keep\_match}(f_{q}) &= \twopartdef{ 1 }{\text{r}(f_{q}, 
    F_{proposed}, F_{baseline}) <
    \tau}{0}{\textrm{otherwise}} \\
    \#\textrm{Correct Matches} &= \sum_{f_{q} \in F_{true}} 
    \textrm{keep\_match}(f_{q})\\
    %\mathbbm{1}_{\left\{ \right\}} \\
    \#\textrm{Incorrect Matches} &= \sum_{f_{q} \in F_{false}}
    \textrm{keep\_match}(f_{q})
    %\mathbbm{1}_{\left\{ r < \tau\right\}}
\end{align*}

From the above we can conclude that the performance in terms of 
precision and recall of any method from the proposed framework is 
uniquely identified by the uniqueness ratio $r$.  If for every query 
feature $f_{q}$, $r$ is identical across two matching methods, then they 
return identical results.

\subsection{Proofs of Ordering}

Under three assumptions that largely reflects the performance of 
matching feature points in practice we can theoretically compare the 
performance of the different algorithms shown in 
Table~\ref{table:distinctness}.

\begin{enumerate}
    \item{For a query and target image we assume that for any point in 
        the query image there is at most one real correspondence in the 
    target image and no real correspondences in the query image itself 
as assumed by \emph{Ratio-Match}}
    \item{We assume that distances of feature descriptors are well 
            behaved.  More precisely, given $f_q$, a feature from the 
            \emph{query image} and $f_{match}$, the real correspondence 
            from the set of features in the \emph{target image} 
            $F_{target}$, we have that $\forall f_i \in F_{proposal}, 
            f_i \neq f_{match}: d(f_q,f_{match}) < d(f_q, f_i)$}
    %\item{We assume that features within one image resemble each other 
            %more than features in different images. That is, given 
            %$f_a,
    %        f_i \in F_1$ and $f_b, f_j \in F_2$ where $(f_i, f_j)$ and 
    %    $(f_a, f_b)$ are true correspondences, and $F_1$ and $F_2$ are 
    %features collected from different images then we expect that 
            %$d(f_a, f_i)% < d(f_a, f_j)$ and $d(f_b, f_j) < d(f_b, 
            %f_i)$}
     \item{For a set of query features $F_{query}$ with a true 
             correspondence in the \emph{target image}, we assume that 
             the distribution of uniqueness ratios using $F_{target}$ as 
             the baseline set is similar to using $F_{query}$, since the 
         two images in the case of true correspondences are guaranteed 
     to share part of the same scene.}
    \end{enumerate}

Based on these assumptions we first prove that the results of 
\emph{Self-Match} is identical to \emph{Self-Match-Ext}. To do this, we 
look at the nearest neighbor $f_{nn}$ of every query feature $f_{q}$ and 
consider the two cases of $f_{nn} \in F_{query}$ and $f_{nn} \in
F_{target}$. For $f_{nn} \in F_{target}$ the uniqueness ratio of 
\emph{Self-Match-Ext} is:
\begin{align*}
    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
        &= \text{r}(f_{q}, F_{target}, F_{baseline})
\end{align*}

Since $F_{proposed} = F_{target}$ for \emph{Self-Match} this shows that
when the nearest neighbor is found in the target image, the two 
algorithms behave identically. For $f_{nn} \in F_{query}$ 
\emph{Self-Match} gives us the following ratio:
\begin{align*}
    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
        &= \text{r}(f_{q}, F_{target}, F_{query}) \\
        &\geq 1
\end{align*}

The closest neighbor is found in the query image, so $d(f_{q}, f_{nn}) < 
d(f_{q},f_{p})$ where $f_{p}$ is the nearest neighbor from 
$F_{proposal}$. \emph{Self-Match-Ext} does not return a correspondence 
found in the \emph{query image} and since $\tau \in [0,1]$, neither does 
\emph{Self-Match}. This proves that for any set of \emph{query features} 
\emph{Self-Match} returns the same matches as \emph{Self-Match-Ext}. For 
this reason both algorithms will later be referred to as just 
\emph{Self-Match}.

The above proof can easily be extended to show that \emph{Mirror-Match 
1} and \emph{Mirror-Match-Ext} returns the same correspondences too, and 
both will be referred to as \emph{Mirror Match} from here on.

For the case of \emph{Ratio-Match} and \emph{Ratio-Match-Ext} however we 
can show that \emph{Ratio-Match-Ext} is equal or better than 
\emph{Ratio-Match}.  Consider again the nearest neighbor $f_{nn}$ of a 
query feature $f_{q}$ and the two cases where we either have the $f_{nn} 
\in F_{query}$ or $f_{nn} \in F_{target}$. For $f_{nn} \in F_{target}$ 
the uniqueness ratio of \emph{Ratio-Match-Ext} is:
\begin{align*}
    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
        &= \text{r}(f_{q}, F_{target}, F_{baseline})
\end{align*}

Since $F_{proposed} = F_{target}$ for \emph{Ratio-Match} this shows that
when the nearest neighbor is found in the target image, the two 
algorithms behave identically. For $f_{nn} \in F_{query}$ 
\emph{Ratio-Match} gives us the following ratio:
\begin{align*}
    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
        &= \text{r}(f_{q}, F_{target}, F_{target})
\end{align*}

Where as \emph{Ratio-Match-Ext} does not return the correspondence if 
the nearest neighbor of a query feature is in the \emph{query image}, 
\emph{Ratio-Match} is likely to do so, since the uniqueness ratio is 
found by dividing with the second nearest neighbor in the \emph{target 
image}. This shows us that for cases where a query feature has a nearest 
neighbor in the \emph{query image}, \emph{Ratio-Match-Ext} is superior 
to \emph{Ratio-Match}. Since query features with a nearest neighbor in 
the \emph{query image} are false correspondences per assumption \#1 and 
\#2, this proves that \emph{Ratio-Match-Ext} has superior 
\emph{Precision} to \emph{Ratio-Match} while maintaining equal 
\emph{Recall}.

Finally we show that \emph{Mirror Match} is equal or better than 
\emph{Ratio-Match-Ext}. Consider as before the nearest neighbor $f_{nn}$ 
of a query feature $f_{q}$. When $f_{nn}$ resides in the \emph{query 
image} both algorithms behave alike and discard the match.  However, 
consider the uniqueness ratio of \emph{Mirror Match} for the case where 
$f_{nn}$ resides in the \emph{target image}:
\begin{align*}
    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
        &= \text{r}(f_{q}, F_{proposed}, F_{query} \cup F_{target})\\
        &= max( \text{r}(f_{q}, F_{proposed}, F_{target}), 
    \text{r}(f_{q}, F_{proposed}, F_{query}) )
\end{align*}

For a true correspondence we have that the uniqueness ratio using 
$F_{query}$ as baseline is distributed similarly to the ratio when using 
$F_{target}$ by assumption \#3. In this case the algorithm performs like 
\emph{Ratio-Match-Ext}.  However for an untrue correspondence with a 
baseline match in the \emph{query image} which is closer than the
baseline match in the \emph{target image}, \emph{Mirror Match} will 
return a worse uniqueness ratio. This in turns means that \emph{Mirror 
Match} is equal or better than \emph{Ratio-Match-Ext} in terms of  
\emph{Precision} while maintaining equal \emph{Recall}.

For any given recall we have proven based on assumption \#1-3 that the 
precision of the algorithms in the framework compares as follows:
\begin{align*}
    \textit{Self-Match} &= \textit{Self-Match-Ext} \\
    \textit{Mirror-Match} &= \textit{Mirror-Match-Ext} \\
    \textit{Ratio-Match} &\leq \textit{Ratio-Match-Ext} \leq 
    \textit{Mirror Match}
\end{align*}

The difference between \emph{Self-Match} and \emph{Ratio-Match} is is 
the source of the \emph{baseline set}. For true correspondences we 
assume that they should perform similarly but as for the rest the 
performance of the two depends entirely on the images we are matching. 
When we match images where the target image might not overlap at all 
with the query image, using the query image and not the target image as 
a \emph{baseline set} seems like a reasonable choice given that the 
baseline set in this case would be closer to the feature matched and 
more strictly rule out untrue correspondences.

\subsection{Discussion of assumptions}
\label{ref:disc_assumptions}

% Assumption 1
%For a query and target image we assume that for any point in the query 
%image there is at most one real correspondence in the target image and 
%no real correspondences in the query image itself as assumed by 
%\emph{Ratio-Match}

% Assumption 2
%We assume the distances of feature descriptors behave in a \emph{nice} 
%manner. That is, given $f_q$, a feature from the \emph{query image} and 
%$f_{match}$, the real correspondence from the set of features in the 
%\emph{target image} $F_{target}$, we have that $\forall f_i \in 
%F_{proposal}, f_i \neq f_{match}: d(f_q,f_{match}) < d(f_q, f_i)$

% Assumption 3
%For a query feature, $f_q$ with a true correspondence in the 
%\emph{target image}, we assume that the uniqueness ratio using 
%$F_{target}$ is similar to the uniqueness ratio using $F_{query}$, 
%since the two images in this case are guaranteed to share part of the 
%same scene

The three assumptions proposed in order to formalize the order of the 
algorithms have been chosen to reflect conditions under which we usually 
match feature points. However, for each assumption there exists corner 
cases where it might not hold true. In this section we intent to discuss 
these corner cases in order to give an impression of the circumstances 
under which the absolute or relative performance of the algorithms might 
differ.

The first assumption states that there is at most one unique match to 
every feature point which is often the case when in e.g.\ stereo 
matching with natural images. However for recognition of object classes 
or in generated images with repetitive content this assumption is no 
longer valid and using any type of ratio match will lead to incorrect 
results.  As we discussed related to matching more than two images, as 
long as the query image does not contain repetitive objects we can still 
use \emph{Self-Match} without loss of precision even if the target image 
might not contain a unique match.

According to the second assumption, feature descriptors behave such that
when matched, a true correspondence to a query feature will always be 
the nearest neighbor. For actual feature detectors and descriptors 
Mikolajczyk and Tuytelaars shows that this property depends strongly on 
the differences between \emph{query} and \emph{target} image 
\cite{mikolajczyk2005performance} \cite{tuytelaars2008local}. In the 
degenerate case where the closest match is not an actual correspondence, 
it is often the case that other matches are similarly close resulting in 
a uniqueness ratio near 1, effectively filtering out bad 
correspondences.  However when we accept matches with a uniqueness ratio
close to 1, the guarantees about precision and recall equivalence in 
between the different ratio algorithms might no longer hold due to the 
lack of consistent descriptor behaviour. It is worth pointing out that 
if this assumption holds true, matching using only nearest neighbor is 
not necessarily optimal unless there is a complete scene overlap between
the images matched. For cases where there is little or no overlap, a 
nearest neighbor would indiscriminately return false matches even with 
well behaved feature descriptors.

\begin{figure}[t]
\centering
\includegraphics[width=0.99\columnwidth]{images/results_ratio_hist}
\caption{Normalized histogram of the \emph{uniqueness ratios} of true 
correspondences for 84 different 3D objects.}
\label{fig:ratio_hist}
\end{figure}

The last assumption states that the uniqueness ratio using either the 
\emph{query} or \emph{target image} as the baseline set would be similar
in distribution when we know that the feature point we are matching has 
a true correspondence. For an ideal feature descriptor where any true 
correspondence between two feature points will have a distance of $0$, 
the third assumption is obviously true for any cases where the second 
closest feature point has a true correspondence in the other image. In 
the general case it is likely that the baseline yields different 
uniqueness ratios depending on the features it contains, but for the 
case where the baseline match has a true correspondence in the other 
image we can verify the assumption by looking at the performance of 
\emph{Self-Match} compared with \emph{Ratio-Match}. To compare we plot 
the actual \emph{uniqueness ratios} measured from 84 3D objects in 
Figure~\ref{fig:ratio_hist}. For ratios lower than $0.7$ this is 
generally the case, but as we approach more lenient thresholds we should
expect the performance of \emph{Self-Match} and \emph{Mirror-Match} to 
decline compared with \emph{Ratio-Match} and \emph{Ratio-Match-Ext}.
% Needs rewording

\section{Experiments and Results}
\label{S:Experiments}
%
\begin{figure}[htb]
    \begin{subfigure}[t]{0.48\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{images/Frog_A}
        \caption{Query Image}
        \label{fig:frog_a}
    \end{subfigure}%
    \quad %add desired spacing between images, e. g. ~, \quad, \qquad a 
    %blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.48\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{images/Frog_B}
        \caption{Auxiliary Image}
        \label{fig:frog_b}
    \end{subfigure}%
    \\ %add desired spacing between images, e. g. ~, \quad, \qquad 
    %a blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.48\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{images/Frog_C}
        \caption{Target Image}
        \label{fig:frog_c}
    \end{subfigure}%
    \quad %add desired spacing between images, e. g. ~, \quad, \qquad 
    %blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.48\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{images/Frog_C_lines}
        \caption{Target Image with epipolar constraints}
        \label{fig:frog_c_lines}
    \end{subfigure}%
    \caption{Creating epipolar constraints based on three source images.  
        In a) the \emph{query image} has been marked with the position 
        of the feature we are attempting to match. In b) the 
        \emph{auxiliary image} is shown. This image is taken with the 
        same rotation as the \emph{query image} but from a higher 
        viewpoint. The line going through the image is the epipolar line 
        of the feature point in the \emph{query image}.  The markers 
        indicate all feature points in the image found near the epipolar 
        line.  In c) we show the \emph{target image} which in this case 
        is rotated 45 degrees from the \emph{query image}.  The line 
        overlaid on the image represents the epipolar line corresponding 
        to the feature point shown in the \emph{query image}.  The 
        markers indicate all feature points in the image found near the 
    epipolar line. In d) we show the \emph{target image} again, this 
time overlaid with the epipolar line corresponding to all the features 
shown in the \emph{auxiliary image}. A true correspondence should be 
found within a small distance of one of the intersections of the line in 
c) and the lines in d). In this particular case both feature points 
shown in c) and d) could possible be a correct correspondence.
}%
    \label{fig:frog}%
\end{figure}%
In this section we will go over the experimental results comparing 
\emph{Self-Match}, \emph{Ratio-Match}, \emph{Ratio-Match-Ext} and 
\emph{Mirror-Match} to each other. We compare the algorithms across 
different image variations and over various descriptors. We use two 
different image databases to compile results over different variations.  
To measure results on non-planar images we test the algorithm on the 3D 
Objects database released by Moreels and Pietro 
\cite{moreels2007evaluation}. The database contains a set of 86 3D 
objects photographed from all sides at 5 degree intervals from two 
different viewpoints and under three different lighting conditions.
To measure the performance over variations such as viewpoint change, 
blur, compression noise, rotation and zoom we also use the graffiti 
image set introduced by Mikolajczyk and Schmid 
\cite{mikolajczyk2005performance}.  This dataset contains 8 scenes each 
with 6 images linked by homographies and for that reason feature only 
planar or almost planar scenes.

The general tests are performed using the \emph{SIFT} descriptor and 
keypoint detector with default parameters as implemented in the OpenCV 
library. To see how the framework performs across descriptors we 
evaluate SURF \cite{bay2006surf}, BRISK \cite{leutenegger2011brisk}, 
BRIEF \cite{calonder2010brief} and FREAK \cite{alahi2012freak} in 
subsection~\ref{label:desc}. Images larger than 1024x768 have been
resized to fit within those dimensions using Imagemagick with default 
parameters and only the luminance channel has been used in the feature 
detection and description stage.

\subsection{Experiments on 3D objects}

\begin{figure*}[ht]
	\centering
    \includegraphics[width=2\columnwidth]{images/results_all_objects}
    \caption{Accumulated results from the 3D objects dataset. Each plot 
    contains data accumulated from 84 objects photographed under 3 
different lighting conditions.}
    \label{fig:all_objects}
\end{figure*}

The 3D objects dataset allows us to experimentally comparing matching 
algorithms over a large range of object and surface types rotated on a 
turnstile and photographed from every 5 degree turn. We used 84 images 
under three different lighting conditions at 12 different angle 
intervals conducting experiments with a total of 3024 image pairs. To 
validate matches, Moreels and Pietro propose a method to that will 
validate a match as a true or false correspondence \cite[p.  
266]{moreels2007evaluation} using the epipolar constraints.  The method 
is outlined in Figure~\ref{fig:frog}.  According to their experiments 
these constraints are sufficient to reduce the error rate recognizing 
true correspondences to $2\%$. We have used this method
to evaluate the precision and recall of the match algorithms.

To compute the total number of possible correspondences we took each 
feature in a \emph{query image} and counted for how many we could find a 
feature in \emph{target image} which would satisfy the epipolar 
constraints outlined above. In the tests features with no correspondence 
was filtered from the features used to test the matching algorithms to 
avoid matching non-moving background and foreground objects.

We evaluated the 4 matching algorithms on the 3D objects dataset by 
matching images at angular intervals. For each object we picked the 
\emph{query} image as the image taken at 10 degrees rotation for 
calibration stability.  We then proceeded to match this image with the 
same object turned an additional $5, 10, \ldots, 60$ degrees. For every 
angle interval we paired images taken under 3 different lighting 
conditions provided by the dataset.
We included all objects in the database for which angular photos at 5 
degree intervals were available except for the ``Rooster'' and 
``Sponge'' objects due to image irregularities. For each plot we show 
the accumulated results on all 3D objects, weighed by the number of 
possible true correspondences for each. This ensures that each object 
contributes equally to the final result despite some objects
resulting in disproportionally more matches than others.

The results can be seen in Figure~\ref{fig:all_objects}.  
\emph{Ratio-Match} and \emph{Self-Match} show similar results, 
\emph{Self-Match} performing slightly worse for trivial cases and 
improving on \emph{Ratio-Match} for angular differences of more than 30 
degrees. \emph{Mirror-Match} and \emph{Ratio-Match-Ext} clearly 
outperform the others, showing the advantage of composing the set of 
\emph{proposed} features of features from both images. As predicted 
\emph{Mirror-Match} performs better or equal to \emph{Ratio-Match-Ext} 
only rarely showing worse results at high recall. The convergence of all 
algorithms at higher recall is the natural consequence of the 
limitations of the feature descriptors used as noted in the discussion 
of assumptions (Section~\ref{ref:disc_assumptions}). At higher recall we 
start meeting descriptors that are not well behaved meaning that cannot 
rely on the ratio as an indicator of match uniqueness which all ratio 
based algorithms responds equally bad to.

\begin{figure*}[t!]
	\centering
    \includegraphics[width=2\columnwidth]{images/results_acr_all}
    \caption{Accumulated results for each scene in the image dataset by 
    Mikolajczyk and Schmid \cite{mikolajczyk2005performance}.}
    \label{fig:acr_objects}
\end{figure*}

\subsection{Planar Scenes}

To evaluate local feature descriptors, Mikolajczyk and Schmid introduced
a serie of $8$ image sets featuring different transformations such as 
compression noise, rotation and zoom, blur and viewpoint change. All 
images are tied by homographies which makes them convenient for testing 
purposes but as a consequence they all depict planar scenes which is 
somewhat restrictive in terms of image variation. Each scene contains 6 
different images ranged in order of increasing levels of 
transformations. The transformation between image 1 and image 2 in a 
scene is usually only slight while image 6 for the most cases is 
markedly different than image 1.

For each scene we match the first image in the scene with image 3, 4, 5 
and 6 and show the accumulated result weighed by the possible number of 
true correspondences for each pair. We exclude the comparison with image 
2 because it for the most cases is trivial and does not tell us anything 
about the relative performance of the different algorithms. We find 
inliers by using the homography between image pairs as follows: Given a 
potential match between two pixels $p_1$ and $p_2$, $m = \left(p_1, 
p_2\right)$, and a homography $H$ relating the two images $I_1$ and 
$I_2$, we can calculate if $m$ is an inlier by checking if the two 
points satisfy the following criteria:
\begin{equation*}
\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
\end{equation*}
That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
less than a certain threshold (we use $d_{\max}=10$ pixels here).

Figure~\ref{fig:acr_objects} show the results plotted with precision on 
the y-axis and recall along the x-axis. For scenes such as `bark, `boat' 
(zoom and rotation), `leuven' (light) and `wall' (viewpoint) all 
algorithms show similar results, largely because the precision for all 
algorithms approach 100\% for low recall which does not leave much room 
for improvement. For `bikes' and `trees' (blur) as well as `ubc'
(compression) and `graf' (viewpoint) we see \emph{Mirror-Match} clearly 
outperforming \emph{Ratio-Match}.

\subsection{Descriptor evaluation}
\label{label:desc}

\begin{figure*}[t!]
    \begin{subfigure}[t]{1\textwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/results_descriptors_imageset1}
        \caption{Keypoint /Descriptor combinations evaluated on 3D 
        Objects}
        \label{fig:descriptors}
    \end{subfigure}%

    \begin{subfigure}[t]{1\textwidth}
        \centering
        \includegraphics[width=1\columnwidth]{images/results_descriptors_easy}
        \caption{Keypoint / Descriptor combinations evaluated on `Bikes' 
        scene}
        \label{fig:descriptors_easy}
    \end{subfigure}%
    \caption{a) Keypoint / Descriptor combinations measured on 15 pairs 
    of photos of 3D objects taken 15 degrees apart. K = Keypoint, D = 
Descriptor\. b) Same experiment evaluated on a simple to match image 
pair; image 1 and 3 in the `Bikes' scene from Mikolaczyk and Schmid's 
review of descriptors \cite{mikolajczyk2005performance}.}
\end{figure*}

We performed the above experiments with the SIFT feature descriptor and 
keypoint detector because this descriptor is the de facto standard in 
local image features. However it is of interest if the improvement gains
shown with the SIFT descriptor translates to other feature descriptors 
such as SURF \cite{bay2006surf} or binary features such as BRIEF 
\cite{calonder2010brief}, BRISK \cite{leutenegger2011brisk} or FREAK 
\cite{alahi2012freak}. To do this we paired each binary descriptor with 
the best performing keypoint detector according to a comparison 
performed by Heinly et al.\ \cite{heinly2012comparative} and the SIFT 
and SURF descriptors with their accompanying keypoint detectors, 
yielding the following matches: BRIEF descriptor with HARRIS keypoint 
detector, BRISK descriptor with FAST keypoint detector. For FREAK we 
used the BRISK feature detector as recommended by Heinly et al. For each 
keypoint detector and feature descriptor pair we used the standard 
implementation from OpenCV 2.4.6.

The descriptors were evaluated on 15 3D images of the 3D object dataset 
with a fixed angle offset of 15 degrees. The evaluation was otherwise 
performed according to the general evaluation of 3D Objects, and the 
data presented is accumulated over the 15 objects, each set of results 
weighted by the possible amount of correspondences.

The results can be seen in Figure~\ref{fig:descriptors} and shows a 
clear difference in effectiveness in between SIFT and the rest of the 
descriptors. While SIFT shows a clear increase in precision at equal 
recall levels, the improvement is much less pronounced for the other 
descriptors. For the case of SURF, BRISK and BRIEF we see a small 
improvement in precision using \emph{Mirror-Match} over 
\emph{Ratio-Match} and \emph{Ratio-Match-ext} while FREAK yields similar 
results no matter what algorithm is used. For all descriptors it is the 
case that \emph{Self-Match} performs equally well to \emph{Ratio-Match}.

Part of the explanation behind this difference between SIFT and the 
other descriptors can be found by looking at the recall rate in the case
of for example SURF\@. Given the same amount of possible matches, 
\emph{Ratio-Match} in the case of SURF spans a larger range of recall.  
Since all other methods filter out matches that are better matched 
within the same image, we can conclude that correct matches are
discarded because there are better matches within the same image, 
violating assumption \#2 stating that we expect the feature descriptor 
to have a shorter distance to a true correspondence than an untrue 
correspondence. This means that for this particular evaluation case SURF 
and the binary features tested are not sufficiently discriminative to 
provide a viable case for preferring \emph{Mirror-Match} over 
\emph{Ratio-Match}. To test this hypothesis we looked at the results 
from matching an image pair with very little inter image variation.  We 
compare two image 1 and image 3 from the `bikes' scene in the image set 
released by Mikolajczyk and Schmid \cite{mikolajczyk2005performance}.  
The results are displayed in Figure~\ref{fig:descriptors_easy} and show 
a market improvement for \emph{Self-Match}, \emph{Mirror-Match} and 
\emph{Ratio-Match-Ext} over \emph{Ratio-Match} for the case of BRISK, 
BRIEF and FREAK as expected. For SURF however the algorithms perform 
similarly at low recall while \emph{Ratio-Match} show better performance
at more lenient thresholds.

\subsection{Performance}

In terms of computational complexity the algorithms can be implemented 
in $O(n\log n)$, if we assume that both the \emph{query} and the 
\emph{target} image has $n$ feature points. For a target image with $m$ 
features where $m$ is significantly different from $n$ the complexities 
are as noted in Table~\ref{table:running_times}. Note that 
implementations refer to the algorithms as specified in 
Table~\ref{table:distinctness}. In practice the constant factors 
involved in the actual matching of two images with approximately the 
same amount of feature points are usually small enough that all the 
algorithms run at a similar speed. To illustrate 
Table~\ref{table:running_times} contains the running times as measured 
while matching 15 3D objects under three different lighting conditions 
($42$ image pairs were matched in total). The running times are averaged 
over three separate runs of each algorithm implemented using the same 
data structures and libraries in Python.

\begin{table}[htb]
\caption{Complexity and running times tested on 15 image pairs on 3 
lighting conditions with average $n = 236.73$ and average $m = 247.38$ 
as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
3.30~GHz with 8~GB memory.}
\label{table:running_times}
	\centering
%	\small
    \begin{tabular}{{l}{l}{l}}
    Algorithm & Complexity & Running Time\\
    \hline
    \noalign{\smallskip}
    %
    \emph{Self-Match} & $O(n\log(nm))$ & 118s  \\
    \emph{Self-Match-Ext} & $O(n\log(n(n+m)))$ & 109s\\
    \emph{Ratio-Match} & $O(n\log(m))$ & 114s\\
    \emph{Ratio-Match-Ext} & $O(n\log(n+m))$ & 112s\\
    \emph{Mirror-Match} & $O(n\log(n(n+m)))$ & 116s\\
    \emph{Mirror-Match-Ext} & $O(n\log(n+m))$ & 110s \\
    \hline
\end{tabular}
\end{table}

\subsection{Extending to multiple target images}
%
When we match a query image against multiple target images as seen in 
for example image stitching, assumption \#1 that any feature in the 
query image has at most 1 real correspondence in the set of target 
features is no longer true. It might be the case that two target images 
contain the same real object which yields two target features that are 
both real correspondences. In this case calculating the \emph{uniqueness 
ratio} by dividing the distance of one real correspondence with the 
distance to another renders it entirely useless if the two features are 
found in sets where there might be more than one correct 
correspondences.

Brown et al.\ \cite{brown2005multi} proposes calculating the uniqueness 
ratio by taking the average of the $n$ nearest neighbors in each of the 
$n$ target images. Since their particular case deals with images that 
are aligned horizontally one after the other, this approach is not 
flawed per se. However for the more general case of $n$ target images 
with an unknown amount of overlaps in the target group, their approach 
would not work since several features in the target group could possible 
be a correct correspondence.

This leaves us with two alternatives. Either we match the query image to 
every target image individually or we use a matching strategy where the 
\emph{baseline set} is guaranteed not to contain any real 
correspondences. \emph{Self-Match} provides such a set, since the 
\emph{baseline set} of \emph{Self-Match} only contains features in the 
query image itself. In addition, matching a query image to $n$ target 
images with \emph{Self-Match} is vastly faster than matching the query 
image to every target image: If we for the sake of simplicity assume 
that every of the $n$ images has $k$ features then matching the query 
image to all $n$ images can be done in $O(nklog(k))$ using a metric 
tree. However, matching with \emph{Self-Match} is done in $O(klog(nk)) =
O(klog(n) + klog(k))$.

\section{Conclusion}
\label{S:Summary}

Nothing here yet

% Descripe the two basic image sets we use to measure this

% Premature ending for now
\bibliographystyle{IEEEtran}
\bibliography{tail/bibliography}
\end{document}

### 2014-04-10 text/journal/paper.tex
State of project by April 10 2014

@@
+% To compile, make sure to have the following packages installed:
+% texlive, texlive-latex-extra, texlive-science, 
+% texlive-fonts-recommended, texlive-fonts-extras
+
 \documentclass[journal]{IEEEtran}
@@
 
-\title{A general framework for local feature matching in images}
+\title{A decade of lost precision: Introducing a general framework for 
+image feature matching without geometric constraints}
 
@@
 \begin{abstract}
-TODO
+Solutions in computer vision involving the matching of local image 
+features frequently use \emph{Ratio-Match} as introduced by Lowe and 
+others, but is this really the best approach? We formalize the 
+theoretical foundation of \emph{Ratio-Match} and propose a general 
+framework encompassing \emph{Ratio-Match} and five other matching 
+methods. Using the framework we establish a theoretical order of 
+performance in terms of precision and recall between the methods and 
+prove that \emph{Ratio-Match} is consistently equalled or outperformed 
+by all other methods of the framework.
+
+We confirm the theoretical results experimentally on over 3000 image 
+pairs and show that we can easily increase matching precision
+without further assumptions about the images we are using. These gains 
+comes without increased computation time by changing only a few key 
+components of the \emph{Ratio-Match} algorithm.
+
 \end{abstract}
@@
 
+\begin{figure}[b]
+\centering
+\includegraphics[width=0.85\columnwidth]{images/overview}
+\caption{Graphical representation of the \emph{Baseline} and 
+\emph{Proposal Set} for different methods in the proposed framework}
+\label{fig:overview}
+\end{figure}
+
 In the case of \emph{Ratio-Match} \cite{lowe2004sift} the \emph{proposal 
@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.85\columnwidth]{images/overview}
-\caption{Graphical representation of the \emph{Baseline} and 
-\emph{Proposal Set} for different methods in the proposed framework}
-\label{fig:overview}
-\end{figure}
 %
@@
 %
-\begin{table}[htb]
+\begin{table}[t]
 \caption{Calculating the uniqueness ratio using different sources for 
@@
 The three assumptions proposed in order to formalize the order of the 
-algorithms have been chosen to reflect conditions under which we usually 
-match feature points. However, for each assumption there exists corner 
-cases where it might not hold true. In this section we intent to discuss 
-these corner cases in order to give an impression of the circumstances 
-under which the absolute or relative performance of the algorithms might 
-differ.
+algorithms have been chosen to reflect conditions under which we ideally
+would match feature points. However, for each assumption there exists 
+corner cases where it is no longer valid. In this section we intent to 
+discuss these corner cases in order to give an impression of the 
+circumstances under which the absolute or relative performance of the 
+algorithms might differ.
 
@@
 or in generated images with repetitive content this assumption is no 
-longer valid and using any type of ratio match will lead to incorrect 
-results.  As we discussed related to matching more than two images, as 
-long as the query image does not contain repetitive objects we can still 
-use \emph{Self-Match} without loss of precision even if the target image 
-might not contain a unique match.
+longer valid and using any assumption of uniqueness will lead to 
+incorrect results. However, as long as the query image does not contain 
+repetitive objects we can still use \emph{Self-Match} without loss of 
+precision even if the target image might not contain a unique match.
 
@@
 a uniqueness ratio near 1, effectively filtering out bad 
-correspondences.  However when we accept matches with a uniqueness ratio
-close to 1, the guarantees about precision and recall equivalence in 
-between the different ratio algorithms might no longer hold due to the 
-lack of consistent descriptor behaviour. It is worth pointing out that 
-if this assumption holds true, matching using only nearest neighbor is 
-not necessarily optimal unless there is a complete scene overlap between
+correspondences.  This means that with a lenient threshold close to 1, 
+the guarantees about precision and recall equivalence in between the 
+different ratio algorithms might no longer hold due to the lack of 
+consistent descriptor behaviour. It is worth pointing out that if this 
+assumption holds true, matching using only nearest neighbor is not 
+necessarily optimal unless there is a complete scene overlap between
 the images matched. For cases where there is little or no overlap, a 
@@
 Figure~\ref{fig:ratio_hist}. For ratios lower than $0.7$ this is 
-generally the case, but as we approach more lenient thresholds we should
-expect the performance of \emph{Self-Match} and \emph{Mirror-Match} to 
-decline compared with \emph{Ratio-Match} and \emph{Ratio-Match-Ext}.
+generally the case, but as we approach more lenient thresholds the 
+performance of \emph{Mirror-Match} might no longer be equal or better 
+than \emph{Ratio-Match-Ext} in terms of precision.
 % Needs rewording
@@
     epipolar line. In d) we show the \emph{target image} again, this 
-time overlaid with the epipolar line corresponding to all the features 
-shown in the \emph{auxiliary image}. A true correspondence should be 
-found within a small distance of one of the intersections of the line in 
-c) and the lines in d). In this particular case both feature points 
-shown in c) and d) could possible be a correct correspondence.
+    time overlaid with the epipolar lines corresponding to all the 
+    features shown in the \emph{auxiliary image}. A true correspondence 
+    should be found within a small distance of one of the intersections 
+    of the line in c) and the lines in d). In this particular case both 
+    feature points shown in c) and d) could possible be a correct 
+    correspondence.
 }%
@@
 \emph{Self-Match}, \emph{Ratio-Match}, \emph{Ratio-Match-Ext} and 
-\emph{Mirror-Match} to each other. We compare the algorithms across 
-different image variations and over various descriptors. We use two 
-different image databases to compile results over different variations.  
-To measure results on non-planar images we test the algorithm on the 3D 
-Objects database released by Moreels and Pietro 
-\cite{moreels2007evaluation}. The database contains a set of 86 3D 
-objects photographed from all sides at 5 degree intervals from two 
-different viewpoints and under three different lighting conditions.
+\emph{Mirror-Match}. We use two different image databases to compile 
+results over different variations.  To measure results on realistic and 
+variate non-planar images we test the algorithm on the 3D Objects 
+database released by Moreels and Pietro \cite{moreels2007evaluation} in 
+Section~\ref{S:3dobjects}. The database contains a set of 86 3D objects 
+photographed from all sides at 5 degree intervals from two different 
+viewpoints and under three different lighting conditions.
 To measure the performance over variations such as viewpoint change, 
@@
 image set introduced by Mikolajczyk and Schmid 
-\cite{mikolajczyk2005performance}.  This dataset contains 8 scenes each 
-with 6 images linked by homographies and for that reason feature only 
-planar or almost planar scenes.
-
-The general tests are performed using the \emph{SIFT} descriptor and 
-keypoint detector with default parameters as implemented in the OpenCV 
-library. To see how the framework performs across descriptors we 
+\cite{mikolajczyk2005performance} in Section~\ref{S:Planar}.  This 
+dataset contains 8 scenes each with 6 images linked by homographies and 
+for that reason feature only planar or almost planar scenes.
+
+In the experiments we use the \emph{SIFT} descriptor and keypoint 
+detector with default parameters as implemented in the OpenCV library 
+v.\ 2.4.6.  To test how the framework performs across descriptors we 
 evaluate SURF \cite{bay2006surf}, BRISK \cite{leutenegger2011brisk}, 
 BRIEF \cite{calonder2010brief} and FREAK \cite{alahi2012freak} in 
-subsection~\ref{label:desc}. Images larger than 1024x768 have been
-resized to fit within those dimensions using Imagemagick with default 
-parameters and only the luminance channel has been used in the feature 
-detection and description stage.
+Section~\ref{label:desc}. Across all experiments images larger than 
+1024x768 have been resized to fit within those dimensions using 
+Imagemagick with default parameters and only the luminance channel has 
+been used in the feature detection and description stage.
 
 \subsection{Experiments on 3D objects}
+\label{S:3dobjects}
+
+\begin{figure}[t]
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/1}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/2}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/3}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/4}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/5}
+    \end{subfigure}%
+    \vspace{1.5 mm}
+
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/6}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/7}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/8}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/9}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/10}
+    \end{subfigure}%
+    \vspace{1.5 mm}
+
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/11}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/12}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/13}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/14}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/15}
+    \end{subfigure}%
+    \vspace{1.5 mm}
+
+    \caption{The first 15 objects from the 3D objects dataset by Moreels
+    and Pietro \cite{moreels2007evaluation}}
+    \label{fig:3d_objects}
+\end{figure}
 
@@
 algorithms over a large range of object and surface types rotated on a 
-turnstile and photographed from every 5 degree turn. We used 84 images 
-under three different lighting conditions at 12 different angle 
-intervals conducting experiments with a total of 3024 image pairs. To 
-validate matches, Moreels and Pietro propose a method to that will 
-validate a match as a true or false correspondence \cite[p.  
-266]{moreels2007evaluation} using the epipolar constraints.  The method 
-is outlined in Figure~\ref{fig:frog}.  According to their experiments 
-these constraints are sufficient to reduce the error rate recognizing 
-true correspondences to $2\%$. We have used this method
-to evaluate the precision and recall of the match algorithms.
+turnstile and photographed from every 5 degree turn. We used images of 
+84 different objects under three different lighting conditions at 12 
+different angle intervals conducting experiments with a total of 3024 
+image pairs.  To validate matches, Moreels and Pietro propose a method 
+to that will validate a match as a true or false correspondence using 
+epipolar constraints \cite[p.  266]{moreels2007evaluation}.  Their 
+method is outlined in Figure~\ref{fig:frog}.  According to their 
+experiments these constraints are sufficient to reduce the error rate 
+recognizing true correspondences to $2\%$. We have used their proposed 
+method to evaluate the precision and recall of the framework methods.
 
 To compute the total number of possible correspondences we took each 
-feature in a \emph{query image} and counted for how many we could find a 
-feature in \emph{target image} which would satisfy the epipolar 
-constraints outlined above. In the tests features with no correspondence 
-was filtered from the features used to test the matching algorithms to 
-avoid matching non-moving background and foreground objects.
+feature in a \emph{query image} and counted how many of them had a 
+feature in the \emph{target image} which would satisfy the epipolar 
+constraints outlined above. In the experiments on 3D objects features 
+with no correspondences were not included in the set of features used to 
+test the matching algorithms to avoid matching non-moving background and 
+foreground objects.
 
 We evaluated the 4 matching algorithms on the 3D objects dataset by 
-matching images at angular intervals. For each object we picked the 
-\emph{query} image as the image taken at 10 degrees rotation for 
-calibration stability.  We then proceeded to match this image with the 
-same object turned an additional $5, 10, \ldots, 60$ degrees. For every 
-angle interval we paired images taken under 3 different lighting 
-conditions provided by the dataset.
-We included all objects in the database for which angular photos at 5 
-degree intervals were available except for the ``Rooster'' and 
-``Sponge'' objects due to image irregularities. For each plot we show 
-the accumulated results on all 3D objects, weighed by the number of 
-possible true correspondences for each. This ensures that each object 
-contributes equally to the final result despite some objects
+matching images at different angular intervals. For each object we 
+picked the \emph{query} image as the image taken at 10 degrees rotation 
+for calibration stability.  We then proceeded to match this image with 
+the same object turned an additional $d$ degrees, $d \in \{5, 10, 
+\ldots, 60\}$.  For every angle interval we compaired images taken under 
+3 different lighting conditions as provided by the dataset.
+We included all objects in the database for which photos at 5 degree 
+angle intervals were available except for the ``Rooster'' and ``Sponge'' 
+objects due to image irregularities. For each plot we show the 
+accumulated results on all 3D objects, weighed by the number of possible 
+true correspondences for the particular object. This ensures that each 
+object contributes equally to the final result despite some objects
 resulting in disproportionally more matches than others.
 
-The results can be seen in Figure~\ref{fig:all_objects}.  
-\emph{Ratio-Match} and \emph{Self-Match} show similar results, 
-\emph{Self-Match} performing slightly worse for trivial cases and 
-improving on \emph{Ratio-Match} for angular differences of more than 30 
-degrees. \emph{Mirror-Match} and \emph{Ratio-Match-Ext} clearly 
-outperform the others, showing the advantage of composing the set of 
-\emph{proposed} features of features from both images. As predicted 
-\emph{Mirror-Match} performs better or equal to \emph{Ratio-Match-Ext} 
-only rarely showing worse results at high recall. The convergence of all 
-algorithms at higher recall is the natural consequence of the 
-limitations of the feature descriptors used as noted in the discussion 
-of assumptions (Section~\ref{ref:disc_assumptions}). At higher recall we 
-start meeting descriptors that are not well behaved meaning that cannot 
-rely on the ratio as an indicator of match uniqueness which all ratio 
-based algorithms responds equally bad to.
+The results can be seen in Figure~\ref{fig:all_objects}. In the figure 
+we see the performance of the different matching methods in our proposed
+framework for $12$ increasingly bigger rotations. The results are shown 
+in a precision / recall plot to make it easy to compare performance in 
+terms of precision at similar levels of recall.
+
+For objects in the top row rotated between $5$ and $20$ degrees we see a 
+gradual increase in the performance gap between the methods as the angle 
+increases.  \emph{Ratio-Match} and \emph{Self-Match} show similar 
+results while \emph{Mirror-Match} and \emph{Ratio-Match-Ext} outperform 
+the them, showing the advantage of composing the \emph{proposed set} of 
+features from both images. \emph{Mirror-Match} show performance which is 
+consistently slightly better than \emph{Ratio-Match-Ext}. In general we 
+see the largest performance improvements at lower recall and a 
+convergence of precision at higher recall. This is expected since a 
+higher recall is a direct consequence of a more lenient threshold and as
+we let the threshold approach $1$ we lose the benefits of thresholding 
+on the \emph{uniqueness ratio} the methods all start approximating the 
+results of a simple nearest neighbor match. However for all but 
+\emph{Ratio-Match} the features with better matches within the same 
+image are still weeded out, which explains the tail end of 
+\emph{Ratio-Match} at high recall where the other algorithms no longer 
+have results. As we demonstrated in \cite{arnfred2013mirror} the removal 
+of within-image matches improves performance on image pairs with partial 
+or no overlap. For no overlap we would expect a matching algorithm to 
+reject matches within regions that have no matching counterparts in the 
+other image.
+
+In the middle row featuring rotations of between $25$ and $40$ degrees 
+we see the strongest improvement of \emph{Mirror-Match} compared to 
+\emph{Ratio-Match} generally peaking at around
+a 20 percentage-point increase in precision. Finally the the performance
+gain decreases as we further increase the rotation to between $45$ and 
+$60$. We suspect that this is partly because assumption \#2 that a 
+descriptor is well behaved and match best with a descriptor of a true 
+correspondence stops being valid when the images are transformed beyond 
+a certain level of recognizability.
+
+To summarize, the methods perform as predicted on the 3D Objects dataset
+with \emph{Mirror-Match} in general performing better than 
+\emph{Ratio-Match-Ext} which in turn was performing better than 
+\emph{Ratio-Match}. The experimental results also show that 
+\emph{Self-Match} overall perform equal to or better than 
+\emph{Ratio-Match}.
+
+\subsection{Planar Scenes}
+\label{S:Planar}
 
@@
 
-\subsection{Planar Scenes}
+\begin{figure}[t]
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/bark}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/bikes}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/boat}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/graf}
+    \end{subfigure}%
+    \vspace{1.5 mm}
+    % Linebreak
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/leuven}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/trees}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/ubc}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/wall}
+    \end{subfigure}%
+    \caption{Scenes from the image dataset by Mikolajczyk and Schmid 
+    \cite{mikolajczyk2005performance} ordered as they appear in 
+Figure~\ref{fig:acr_objects}.}
+    \label{fig:acr_images}
+\end{figure}
 
@@
 purposes but as a consequence they all depict planar scenes which is 
-somewhat restrictive in terms of image variation. Each scene contains 6 
-different images ranged in order of increasing levels of 
-transformations. The transformation between image 1 and image 2 in a 
-scene is usually only slight while image 6 for the most cases is 
-markedly different than image 1.
+restrictive in terms of image variation. Each scene contains 6 different 
+images ranged in order of increasing levels of transformations. The 
+transformation between image 1 and image 2 in a scene is only slight 
+while image 6 for the most cases is markedly different than image 1.
 
@@
 true correspondences for each pair. We exclude the comparison with image 
-2 because it for the most cases is trivial and does not tell us anything 
-about the relative performance of the different algorithms. We find 
-inliers by using the homography between image pairs as follows: Given a 
-potential match between two pixels $p_1$ and $p_2$, $m = \left(p_1, 
-p_2\right)$, and a homography $H$ relating the two images $I_1$ and 
-$I_2$, we can calculate if $m$ is an inlier by checking if the two 
-points satisfy the following criteria:
+2 because it is trivial in most cases and does not tell us much about 
+the relative performance of the different methods. We find inliers by 
+using the homography between image pairs as follows: Given a potential 
+match between two pixels $p_1$ and $p_2$, $m = \left(p_1, p_2\right)$, 
+and a homography $H$ relating the two images $I_1$ and $I_2$, we can 
+calculate if $m$ is an inlier by checking if the two points satisfy the 
+following criteria:
 \begin{equation*}
@@
 
-Figure~\ref{fig:acr_objects} show the results plotted with precision on 
+Figure~\ref{fig:acr_objects} shows the results plotted with precision on 
 the y-axis and recall along the x-axis. For scenes such as `bark, `boat' 
-(zoom and rotation), `leuven' (light) and `wall' (viewpoint) all 
-algorithms show similar results, largely because the precision for all 
-algorithms approach 100\% for low recall which does not leave much room 
+(zoom and rotation), `leuven' (light) and `wall' (viewpoint) all methods 
+in the framework show similar results, largely because the precision for 
+all methods approach 100\% for low recall which does not leave much room 
 for improvement. For `bikes' and `trees' (blur) as well as `ubc'
 (compression) and `graf' (viewpoint) we see \emph{Mirror-Match} clearly 
-outperforming \emph{Ratio-Match}.
+outperforming \emph{Ratio-Match} although with a smaller margin than 
+with the 3D objects dataset. Because many images in the dataset are 
+trivial to match and a few are very difficult we see less spread in 
+between the algorithms than with the 3D objects dataset. However the 
+theoretical predictions still hold true with \emph{Mirror-Match} 
+performing better or equal to \emph{Ratio-Match-Ext} which in turns 
+perform better or equal to \emph{Ratio-Match}. As for \emph{Self-Match} 
+we are again confirmed that we can achieve performance rivaling 
+\emph{Ratio-Match} using only the \emph{query image} as \emph{baseline 
+set}.
 
@@
 
-We performed the above experiments with the SIFT feature descriptor and 
-keypoint detector because this descriptor is the de facto standard in 
-local image features. However it is of interest if the improvement gains
-shown with the SIFT descriptor translates to other feature descriptors 
-such as SURF \cite{bay2006surf} or binary features such as BRIEF 
-\cite{calonder2010brief}, BRISK \cite{leutenegger2011brisk} or FREAK 
-\cite{alahi2012freak}. To do this we paired each binary descriptor with 
-the best performing keypoint detector according to a comparison 
-performed by Heinly et al.\ \cite{heinly2012comparative} and the SIFT 
-and SURF descriptors with their accompanying keypoint detectors, 
-yielding the following matches: BRIEF descriptor with HARRIS keypoint 
-detector, BRISK descriptor with FAST keypoint detector. For FREAK we 
-used the BRISK feature detector as recommended by Heinly et al. For each 
+To evaluate whether the improvement gains shown with the SIFT descriptor 
+translates to other feature descriptors such as SURF \cite{bay2006surf} 
+or binary features such as BRIEF \cite{calonder2010brief}, BRISK 
+\cite{leutenegger2011brisk} or FREAK \cite{alahi2012freak} we evaluated 
+the different descriptors on the 3D objects data set.  For the binary 
+features they were each paired with the FAST feature detector while SIFT 
+and SURF were tested with their respective feature detectors.  For each 
 keypoint detector and feature descriptor pair we used the standard 
@@
 
-The descriptors were evaluated on 15 3D images of the 3D object dataset 
-with a fixed angle offset of 15 degrees. The evaluation was otherwise 
-performed according to the general evaluation of 3D Objects, and the 
-data presented is accumulated over the 15 objects, each set of results 
-weighted by the possible amount of correspondences.
+The descriptors were evaluated on 15 images of the 3D object dataset 
+with a fixed angle offset of 25 degrees (pictured in 
+Figure~\ref{fig:3d_objects}).  The evaluation was otherwise performed as
+in the general evaluation of 3D Objects, and the data presented is 
+accumulated over the 15 objects, each set of results weighted by the 
+possible amount of correspondences.
 
 The results can be seen in Figure~\ref{fig:descriptors} and shows a 
-clear difference in effectiveness in between SIFT and the rest of the 
-descriptors. While SIFT shows a clear increase in precision at equal 
-recall levels, the improvement is much less pronounced for the other 
-descriptors. For the case of SURF, BRISK and BRIEF we see a small 
-improvement in precision using \emph{Mirror-Match} over 
-\emph{Ratio-Match} and \emph{Ratio-Match-ext} while FREAK yields similar 
-results no matter what algorithm is used. For all descriptors it is the 
-case that \emph{Self-Match} performs equally well to \emph{Ratio-Match}.
+clear difference in the variance of matching method performance in 
+between SIFT and the rest of the descriptors. The performance of 
+\emph{Mirror-Match} using SIFT shows a clear increase in precision over 
+\emph{Ratio-Match} at equal recall levels. For other descriptors the 
+improvement is much less pronounced.  For the case of SURF, BRISK and 
+BRIEF we see a small improvement in precision using \emph{Mirror-Match} 
+over \emph{Ratio-Match} and \emph{Ratio-Match-ext} while FREAK yields 
+similar results no matter what algorithm is used. For all descriptors it 
+is the case that \emph{Self-Match} performs equally well to 
+\emph{Ratio-Match}.
 
@@
 Since all other methods filter out matches that are better matched 
-within the same image, we can conclude that correct matches are
-discarded because there are better matches within the same image, 
-violating assumption \#2 stating that we expect the feature descriptor 
-to have a shorter distance to a true correspondence than an untrue 
+within the same image but show no increase in precision, we can conclude 
+that correct matches are discarded because there are better matches 
+within the same image. This violates assumption \#2 stating that a 
+descriptor is well behaved and match best with a descriptor of a true 
 correspondence. This means that for this particular evaluation case SURF 
@@
 provide a viable case for preferring \emph{Mirror-Match} over 
-\emph{Ratio-Match}. To test this hypothesis we looked at the results 
-from matching an image pair with very little inter image variation.  We 
-compare two image 1 and image 3 from the `bikes' scene in the image set 
-released by Mikolajczyk and Schmid \cite{mikolajczyk2005performance}.  
-The results are displayed in Figure~\ref{fig:descriptors_easy} and show 
-a market improvement for \emph{Self-Match}, \emph{Mirror-Match} and 
-\emph{Ratio-Match-Ext} over \emph{Ratio-Match} for the case of BRISK, 
-BRIEF and FREAK as expected. For SURF however the algorithms perform 
-similarly at low recall while \emph{Ratio-Match} show better performance
-at more lenient thresholds.
+\emph{Ratio-Match}.
+
+To test this hypothesis we looked at the results from matching an image 
+pair with very little inter image variation. We compare two image 1 and 
+image 3 from the `bikes' scene in the image set released by Mikolajczyk 
+and Schmid \cite{mikolajczyk2005performance}. The results are displayed 
+in Figure~\ref{fig:descriptors_easy} and show a market improvement for 
+\emph{Self-Match}, \emph{Mirror-Match} and \emph{Ratio-Match-Ext} over 
+\emph{Ratio-Match} for the case of BRISK, BRIEF and FREAK as expected.  
+For SURF however the algorithms perform similarly at low recall while 
+\emph{Ratio-Match} show better performance at more lenient thresholds.
 
@@
 
-Nothing here yet
-
-% Descripe the two basic image sets we use to measure this
-
-% Premature ending for now
+We have proposed a framework of matching methods building on the ideas 
+behind \emph{Ratio-Match} and \emph{Mirror-Match} introducing the 
+variations \emph{Self-Match} and \emph{Ratio-Match-Ext}. We proved that 
+in terms of precision and recall \emph{Mirror-Match} performs better or 
+equal to \emph{Ratio-Match-Ext} which in turn performs better or equal 
+to \emph{Ratio-Match} under three common assumptions.
+
+From an evaluation using images of rotated 3D objects we have shown that
+the theoretical conclusions are reflected in experimental data with 
+\emph{Mirror-Match} often outperforming \emph{Ratio-Match}
+significantly over 3024 image pairs. We went on to show that this 
+behaviour was repeated for the classical `graffiti' imageset although 
+with less variation in between the algorithms. This performance gain 
+comes free in terms of both computational complexity as well as actual 
+time consumption as measured over 45 image pairs. Finally evaluations 
+across several different descriptors show that the gains in performance 
+are tied to descriptor performance with significantly smaller gains 
+occuring with descriptors that are less performant.
+
+With the framework we introduced three simple methods that are all 
+applicable in situations where \emph{Ratio-Match} is currently used.  
+\emph{Self-Match} is on par with \emph{Ratio-Match} across all 
+evaluations but can be applied when matching multiple overlapping 
+images. \emph{Ratio-Match-Ext} and \emph{Mirror-Match} on the other hand 
+can easily replace \emph{Ratio-Match} without any performance penalty 
+and with an increase in precisionon but are both limited to matching 
+image pairs like \emph{Ratio-Match}.
+
 \bibliographystyle{IEEEtran}

### 2014-04-10 text/journal/paper.tex
Removed figures containing planar plots from paper

@@
 viewpoints and under three different lighting conditions.
-To measure the performance over variations such as viewpoint change, 
-blur, compression noise, rotation and zoom we also use the graffiti 
-image set introduced by Mikolajczyk and Schmid 
-\cite{mikolajczyk2005performance} in Section~\ref{S:Planar}.  This 
-dataset contains 8 scenes each with 6 images linked by homographies and 
-for that reason feature only planar or almost planar scenes.
 
@@
 
-\subsection{Planar Scenes}
-\label{S:Planar}
-
-\begin{figure*}[t!]
-	\centering
-    \includegraphics[width=2\columnwidth]{images/results_acr_all}
-    \caption{Accumulated results for each scene in the image dataset by 
-    Mikolajczyk and Schmid \cite{mikolajczyk2005performance}.}
-    \label{fig:acr_objects}
-\end{figure*}
-
-\begin{figure}[t]
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/bark}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/bikes}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/boat}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/graf}
-    \end{subfigure}%
-    \vspace{1.5 mm}
-    % Linebreak
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/leuven}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/trees}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/ubc}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/wall}
-    \end{subfigure}%
-    \caption{Scenes from the image dataset by Mikolajczyk and Schmid 
-    \cite{mikolajczyk2005performance} ordered as they appear in 
-Figure~\ref{fig:acr_objects}.}
-    \label{fig:acr_images}
-\end{figure}
-
-To evaluate local feature descriptors, Mikolajczyk and Schmid introduced
-a serie of $8$ image sets featuring different transformations such as 
-compression noise, rotation and zoom, blur and viewpoint change. All 
-images are tied by homographies which makes them convenient for testing 
-purposes but as a consequence they all depict planar scenes which is 
-restrictive in terms of image variation. Each scene contains 6 different 
-images ranged in order of increasing levels of transformations. The 
-transformation between image 1 and image 2 in a scene is only slight 
-while image 6 for the most cases is markedly different than image 1.
-
-For each scene we match the first image in the scene with image 3, 4, 5 
-and 6 and show the accumulated result weighed by the possible number of 
-true correspondences for each pair. We exclude the comparison with image 
-2 because it is trivial in most cases and does not tell us much about 
-the relative performance of the different methods. We find inliers by 
-using the homography between image pairs as follows: Given a potential 
-match between two pixels $p_1$ and $p_2$, $m = \left(p_1, p_2\right)$, 
-and a homography $H$ relating the two images $I_1$ and $I_2$, we can 
-calculate if $m$ is an inlier by checking if the two points satisfy the 
-following criteria:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
-\end{equation*}
-That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=10$ pixels here).
-
-Figure~\ref{fig:acr_objects} shows the results plotted with precision on 
-the y-axis and recall along the x-axis. For scenes such as `bark, `boat' 
-(zoom and rotation), `leuven' (light) and `wall' (viewpoint) all methods 
-in the framework show similar results, largely because the precision for 
-all methods approach 100\% for low recall which does not leave much room 
-for improvement. For `bikes' and `trees' (blur) as well as `ubc'
-(compression) and `graf' (viewpoint) we see \emph{Mirror-Match} clearly 
-outperforming \emph{Ratio-Match} although with a smaller margin than 
-with the 3D objects dataset. Because many images in the dataset are 
-trivial to match and a few are very difficult we see less spread in 
-between the algorithms than with the 3D objects dataset. However the 
-theoretical predictions still hold true with \emph{Mirror-Match} 
-performing better or equal to \emph{Ratio-Match-Ext} which in turns 
-perform better or equal to \emph{Ratio-Match}. As for \emph{Self-Match} 
-we are again confirmed that we can achieve performance rivaling 
-\emph{Ratio-Match} using only the \emph{query image} as \emph{baseline 
-set}.
-
 \subsection{Descriptor evaluation}
@@
 
-    \begin{subfigure}[t]{1\textwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/results_descriptors_easy}
-        \caption{Keypoint / Descriptor combinations evaluated on `Bikes' 
-        scene}
-        \label{fig:descriptors_easy}
-    \end{subfigure}%
-    \caption{a) Keypoint / Descriptor combinations measured on 15 pairs 
-    of photos of 3D objects taken 15 degrees apart. K = Keypoint, D = 
-Descriptor\. b) Same experiment evaluated on a simple to match image 
-pair; image 1 and 3 in the `Bikes' scene from Mikolaczyk and Schmid's 
-review of descriptors \cite{mikolajczyk2005performance}.}
+    \caption{Keypoint / Descriptor combinations measured on 15 pairs of 
+    photos of 3D objects taken 15 degrees apart. K = Keypoint, D = 
+Descriptor\.}
 \end{figure*}
@@
 \emph{Ratio-Match}.
-
-To test this hypothesis we looked at the results from matching an image 
-pair with very little inter image variation. We compare two image 1 and 
-image 3 from the `bikes' scene in the image set released by Mikolajczyk 
-and Schmid \cite{mikolajczyk2005performance}. The results are displayed 
-in Figure~\ref{fig:descriptors_easy} and show a market improvement for 
-\emph{Self-Match}, \emph{Mirror-Match} and \emph{Ratio-Match-Ext} over 
-\emph{Ratio-Match} for the case of BRISK, BRIEF and FREAK as expected.  
-For SURF however the algorithms perform similarly at low recall while 
-\emph{Ratio-Match} show better performance at more lenient thresholds.
 
@@
     \emph{Self-Match} & $O(n\log(nm))$ & 118s  \\
-    \emph{Self-Match-Ext} & $O(n\log(n(n+m)))$ & 109s\\
+    %\emph{Self-Match-Ext} & $O(n\log(n(n+m)))$ & 109s\\
     \emph{Ratio-Match} & $O(n\log(m))$ & 114s\\
@@
     \emph{Mirror-Match} & $O(n\log(n(n+m)))$ & 116s\\
-    \emph{Mirror-Match-Ext} & $O(n\log(n+m))$ & 110s \\
+    %\emph{Mirror-Match-Ext} & $O(n\log(n+m))$ & 110s \\
     \hline
@@
 \emph{Mirror-Match} often outperforming \emph{Ratio-Match}
-significantly over 3024 image pairs. We went on to show that this 
-behaviour was repeated for the classical `graffiti' imageset although 
-with less variation in between the algorithms. This performance gain 
-comes free in terms of both computational complexity as well as actual 
-time consumption as measured over 45 image pairs. Finally evaluations 
-across several different descriptors show that the gains in performance 
-are tied to descriptor performance with significantly smaller gains 
-occuring with descriptors that are less performant.
+significantly over 3024 image pairs. This performance gain comes free in 
+terms of both computational complexity as well as actual time 
+consumption as measured over 45 image pairs. Finally evaluations across 
+several different descriptors show that the gains in performance are 
+tied to descriptor performance with significantly smaller gains occuring 
+with descriptors that are less performant.
 

### 2014-04-11 text/journal/paper.tex
Corrected introduction and added citation

@@
 theoretical foundation of \emph{Ratio-Match} and propose a general 
-framework encompassing \emph{Ratio-Match} and five other matching 
+framework encompassing \emph{Ratio-Match} and three other matching 
 methods. Using the framework we establish a theoretical order of 
@@
 A plethora of solutions have combined ratio match with various geometric 
-constraints to improve matching. These constraints are
-based on assumptions regarding the transformation between the query and 
-target images. At the stricter end we have epipolar constraints assuming
+constraints to improve matching. These constraints are based on 
+assumptions regarding the transformation between the query and target 
+images. At the stricter end we have epipolar constraints assuming
 that the images can be tied by a homography \cite{torr2000mlesac}, 
@@
 correspondences are angled similarly \cite{kim2008efficient}, 
-\cite{schmid1997local}, \cite{leordeanu2005spectral}. Instead of 
-modelling the relationship between two images as an epipolar relation, 
-we can try to allow for more lenient transformation with more 
-sophisticated models.  Torresani et al.~\cite{torresani2008feature} 
-attempted to model these transformations using graph matching similar to 
-\cite{deriche1994robust}. Others define image regions and reject or 
-accept correspondences based on the regions they connect 
+\cite{schmid1997local}. Often these approaches are made computationally 
+feasible by modelling the case of feature correspondences as an instance 
+of graph matching where each feature is a vertex and edge values 
+correspond to a geometric relation between two features. In this case 
+approximate graph matching algorithms can be used to efficiently 
+establish an isomorphism between the graph of features in two images 
+\cite{leordeanu2005spectral}, \cite{torresani2008feature}, 
+\cite{yarkony2010covering}. Finally others define image regions and 
+reject or accept correspondences based on the regions they connect 
 \cite{cho2009feature}, \cite{wu2011robust}.
@@
 inherent assumptions about the geometric relationship between the two 
-images. Broad assumptions such as the epipolar constraint only apply in 
-simple image transformations. For more complex transformations we need 
-models suitable for each particular case and hence limit the algorithm 
-to the subset of images that fit the model.  In the case of object 
-recognition for example, the transformations from one scene to another 
-often feature a change
-in perspective, background and sometimes variations within the object 
-itself.  A person can change pose, a car model can have different 
-configurations, a flower can bloom etc.
-
-When matching these instances we are forced to either create a 
-sophisticated model that represents the variables of transformation 
-within the object, or alternatively find correspondences using an 
-algorithm with no inherent geometric assumptions. In addition the 
+images. Broad assumptions such as angular constraints often used in 
+graph matching only apply to simple image transformations. For more 
+complex transformations we need models suitable for each particular case 
+and hence limit the algorithm to the subset of images that fit the 
+model. In the case of object recognition for example, the 
+transformations from one scene to another often feature a change in 
+perspective, background and sometimes variations within the object 
+itself. In most circumstances this makes these methods unsuited for 
+epipolar or angular constraints.
+
+If we intent to match these instances using geometric features we are 
+forced to used a sophisticated model that reflects the variations in 
+which we find these objects, an in the process lose generality. For this 
+reason general descriptor based algorithms are crucial for 
+correspondence applications calling for generality. In addition the 
 advantage of purely descriptor based methods is motivated by the fact 
@@
 unoptimal choice as a matching algorithm independent of application.
+
+In the author's last paper we introduced \emph{Mirror Match} and 
+\emph{Mirror-Match with Clustering}, two algorithms that we showed to 
+perform better than the state of the art. The novel contributions of 
+this paper consists of two new algorithms completing a framework of four 
+related matching algorithms as well as the theoretical foundation which 
+enables us to understand why \emph{Mirror Match} performs better than 
+\emph{Ratio Match} in the first place.
 
@@
 \begin{equation*}
-    f_{nn} = \argmin_{f_t \in F_{target}} d(f_q, f_t)
+    \argmin_{f_t \in F_{target}} d(f_q, f_t)
 \end{equation*}
@@
 \emph{uniqueness ratio} lower than $\tau$}
-\item{Let the \emph{proposed match} be the nearest neighbor of $f_q$
-    picked from a set of feature points that we will call the 
-\emph{proposal set} which does not include $f_q$}
-\item{Let the \emph{baseline match} be the nearest neighbor of $f_q$ 
-    picked from a set of feature points that we will call the 
-\emph{baseline set} which neither contains the \emph{proposed match} nor 
-$f_q$}
+\item{Let the \emph{proposed match} be the nearest neighbor of the query 
+    feature $f_q$ picked from a set of feature points that we will call 
+the \emph{proposal set} which does not contain the query feature itself}
+\item{Let the \emph{baseline match} be the nearest neighbor of the query 
+    feature $f_q$ picked from a set of feature points that we will call 
+the \emph{baseline set} which neither contains the \emph{proposed match} 
+nor the query feature}
 \end{itemize}
 
-\begin{figure}[b]
+%
+\subsection{A framework of matching methods}
+%
+
+\begin{figure}[t]
 \centering
@@
 
-In the case of \emph{Ratio-Match} \cite{lowe2004sift} the \emph{proposal 
-set} consists of all the feature points in the target image.  Similarly 
-the \emph{baseline set} consists of all the feature points in the target 
+Given two images we can construct the proposal and baseline sets in six 
+different ways as illustrated in Figure~\ref{fig:overview}. In the case 
+of \emph{Ratio-Match} \cite{lowe2004sift} the \emph{proposal set} 
+consists of all the feature points in the target image.  Similarly the 
+\emph{baseline set} consists of all the feature points in the target 
 image except the \emph{proposed} match. For \emph{Ratio-Match} this 
-practically means that given a feature, $f_q$, the \emph{proposed match} 
-and the \emph{baseline match} are the two nearest neighbors in the set 
-of feature points in the \emph{target image}.
-
-Brown et al.\ extends \emph{Ratio-Match} for the case of $n$ target 
-images by letting the baseline be the average of the distance to the 
-second nearest neighbors for all $n$ target images 
-\cite{brown2005multi}.  ``\emph{[W]e can improve outlier rejection}'' 
-they write ``\emph{by using information from all of the images (rather 
-than just the two being matched) This improves the matching 
-precision}''.  The idea of improving matching precision by expanding the 
-knowledge used to reject outliers is the central tenet in this paper.
-
-%
-\subsection{A framework of matching methods}
-%
-\begin{table}[t]
-\caption{Calculating the uniqueness ratio using different sources for 
-    the \emph{proposal set} and \emph{baseline set} for the case of two 
-images.}
-\label{table:distinctness}
-	\centering
-%	\small
-\bgroup
-\def\arraystretch{1.5}
-    \begin{tabular}{l l | l l}
-        %
-        %&  \multicolumn{1}{l}{Target}
-        %& \multicolumn{1}{l}{Target and Query} \\
-\multicolumn{2}{r}{} & \multicolumn{2}{c}{\emph{Proposal Set}} \\
-                     & & Target & Target and Query \\
-        \cline{2-4}
-        \multirow{3}{*}{\rotatebox[origin=c]{90}{\emph{Baseline Set}}} &
-  Query            & \emph{Self-Match}   & \emph{Self-Match-Ext} \\
-& Target           & \emph{Ratio-Match}   & \emph{Ratio-Match-Ext} \\
-& Target and Query & \emph{Mirror-Match} & \emph{Mirror-Match-Ext} \\
-        \cline{2-4}
-\end{tabular}
-\egroup
-\end{table}
-
-\emph{Ratio-Match} is only one instance of a framework of algorithms we can 
-construct by different combinations of \emph{proposed} and 
-\emph{baseline sets}. As shown in Table~\ref{table:distinctness} for the 
-case of two images the \emph{proposal set} can be constructed by either 
-looking only at the nearest neighbors in the target image, or 
-alternatively by looking at the nearest neighbors in both the query and 
-target image. The \emph{baseline set} can either be the query image 
-itself, the target image or the combination of the two.  Seen in this 
-light, the matching algorithm \emph{Ratio-Match} draws both its 
-\emph{proposal set} and \emph{baseline set} from the target image. In 
-turn \emph{Mirror-Match-Ext} as introduced by the authors in 
+practically means that given a query feature, $f_q$, the \emph{proposed 
+match} and the \emph{baseline match} are the two nearest neighbors in 
+the set of feature points in the \emph{target image} and the ratio is 
+decided uniquely based on the \emph{target image}. In turn 
+\emph{Mirror-Match-Ext} as introduced by the authors in 
 \cite{arnfred2013mirror}, works by constructing the \emph{proposal set} 
 and \emph{baseline set} by combining features from both the \emph{query} 
-and \emph{target image}. Alternatively \emph{Self-Match} looks only to 
-the query image for the \emph{baseline set} but constructs the 
-\emph{proposal set} from the target image like \emph{Ratio-Match}. In 
-Figure~\ref{fig:overview} we illustrate how each method is derrived.
+and \emph{target image}.
 
@@
     \State $F_{target} = get\_features(I_{target})$
-\State $F_{proposal} = get\_proposal\_set(F_{query}, F_{target})$
-\State $F_{baseline} = get\_baseline\_set(F_{query}, F_{target})$
+\State $F_{proposal-all} = get\_proposal\_features(F_{query}, 
+F_{target})$
+\State $F_{baseline-all} = get\_baseline\_features(F_{query}, 
+F_{target})$
 \State $M = \varnothing$
 \ForAll{$f_q \in F_{query}$}
-    \State $f_p \gets getNearestNeighbo\text{r}(f_q, F_{proposal} \setminus 
-    \left\{f_q\right\})$
-    \State $f_b \gets getNearestNeighbo\text{r}(f_q, F_{baseline} \setminus 
-    \left\{f_q, f_p\right\})$
+    \State $F_{proposal} = F_{proposal-all} \setminus 
+    \left\{f_q\right\}$
+    \State $F_{baseline} = F_{baseline-all} \setminus \left\{f_q, 
+    f_p\right\}$
+    \State $f_p \gets getNearestNeighbo\text{r}(f_q, F_{proposal})$
+    \State $f_b \gets getNearestNeighbo\text{r}(f_q, F_{baseline})$
     \State $ratio \gets distance(f_q, f_p) / distance(f_q, f_b)$
@@
 where the \emph{proposal set} and \emph{baseline set} are defined 
-according to Table~\ref{table:distinctness}.  In practice for i.e.\ 
+according to Figure~\ref{fig:overview}.  In practice for i.e.\ 
 \emph{Ratio-Match} we can obtain $f_p$ and $f_b$ by finding the 2 
@@
 and $F_{baseline}$ from these sets according to the algorithm used (see 
-Table~\ref{table:distinctness}). $r = \text{r}(f_{q}, F_{proposed}, 
+Figure~\ref{fig:overview}). $r = \text{r}(f_{q}, F_{proposed}, 
 F_{baseline})$ is the ratio of query feature $f_{q}$ given 
@@
 performance of the different algorithms shown in 
-Table~\ref{table:distinctness}.
+Figure~\ref{fig:overview}.
 
@@
 
-\begin{figure*}[t!]
-    \begin{subfigure}[t]{1\textwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/results_descriptors_imageset1}
-        \caption{Keypoint /Descriptor combinations evaluated on 3D 
-        Objects}
-        \label{fig:descriptors}
-    \end{subfigure}%
-
+\begin{figure*}[t]
+    photos of 3D objects taken 15 degrees apart. K = Keypoint, D = 
+Descriptor\.}
     \caption{Keypoint / Descriptor combinations measured on 15 pairs of 
     photos of 3D objects taken 15 degrees apart. K = Keypoint, D = 
-Descriptor\.}
+Descriptor.}
+    \label{fig:descriptors}
 \end{figure*}

### 2014-04-11 text/journal/paper.tex
Moved proofs to appendix

@@
 and \emph{baseline set} by combining features from both the \emph{query} 
-and \emph{target image}.
+and \emph{target image}. By similar compositions of the \emph{proposal} 
+and \emph{baseline set} we derive four more algorithms as illustrated in 
+Figure~\ref{fig:overview}.
 
@@
 
-For some methods it is possible that the \emph{proposal match} is a 
-feature from the \emph{query image}, in which case we discard the match 
-as an untrue correspondence.  It also happens that we encounter 
+For methods where the \emph{proposal set} includes the \emph{query 
+features} it is possible that the \emph{proposal match} is a feature 
+from the \emph{query image}, in which case we discard the match as an 
+untrue correspondence.  It also happens that we encounter 
 correspondences where the uniqueness ratio is more than $1$ in which 
@@
 
+% TODO: include point about two of the algorithms being identical
+%
 \subsection{Generalized Uniqueness Ratio}
+%
 
@@
 
-For $F_{query} = \left\{f_{q_1} \ldots f_{q_n}\right\}$ and $F_{target} 
-= \left\{f_{t_1} \ldots f_{t_m}\right\}$.  We can obtain $F_{proposed}$ 
-and $F_{baseline}$ from these sets according to the algorithm used (see 
-Figure~\ref{fig:overview}). $r = \text{r}(f_{q}, F_{proposed}, 
-F_{baseline})$ is the ratio of query feature $f_{q}$ given 
-$F_{proposed}$ and $F_{baseline}$.  If $f_{p}$ is the nearest neighbor 
-of $f_{q}$ in $F_{proposed}$ and $f_{b}$ is the nearest neighbor of 
-$f_{q}$ in $F_{baseline} \setminus \left\{f_{p}\right\}$ then the 
-generalized \emph{uniqueness} ratio is:
+The main distinguishing factor in between the algorithms in the 
+framework is the final ratio between the distance of the two nearest 
+neighbors of a query feature which decides if we keep or discard a 
+match. We illustrate this process in Figure~\ref{fig:matching}.
+
+We can define a calculation of this ratio common to all algorithms in 
+the framework which allows us to compare the algorithms theoretically. 
+The theoretical ratio, $r$ is defined as follows:
+
+If $f_{p}$ is the nearest neighbor of $f_{q}$ in $F_{proposed}$ and 
+$f_{b}$ is the nearest neighbor of $f_{q}$ in $F_{baseline} \setminus 
+\left\{f_{p}\right\}$ then the generalized \emph{uniqueness} ratio is:
 \begin{align*}
@@
 
-Based on these assumptions we first prove that the results of 
-\emph{Self-Match} is identical to \emph{Self-Match-Ext}. To do this, we 
-look at the nearest neighbor $f_{nn}$ of every query feature $f_{q}$ and 
-consider the two cases of $f_{nn} \in F_{query}$ and $f_{nn} \in
-F_{target}$. For $f_{nn} \in F_{target}$ the uniqueness ratio of 
-\emph{Self-Match-Ext} is:
-\begin{align*}
-    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
-        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
-        &= \text{r}(f_{q}, F_{target}, F_{baseline})
-\end{align*}
-
-Since $F_{proposed} = F_{target}$ for \emph{Self-Match} this shows that
-when the nearest neighbor is found in the target image, the two 
-algorithms behave identically. For $f_{nn} \in F_{query}$ 
-\emph{Self-Match} gives us the following ratio:
-\begin{align*}
-    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
-        &= \text{r}(f_{q}, F_{target}, F_{query}) \\
-        &\geq 1
-\end{align*}
-
-The closest neighbor is found in the query image, so $d(f_{q}, f_{nn}) < 
-d(f_{q},f_{p})$ where $f_{p}$ is the nearest neighbor from 
-$F_{proposal}$. \emph{Self-Match-Ext} does not return a correspondence 
-found in the \emph{query image} and since $\tau \in [0,1]$, neither does 
-\emph{Self-Match}. This proves that for any set of \emph{query features} 
-\emph{Self-Match} returns the same matches as \emph{Self-Match-Ext}. For 
-this reason both algorithms will later be referred to as just 
-\emph{Self-Match}.
-
+Based on these assumptions we first prove that 
 The above proof can easily be extended to show that \emph{Mirror-Match 
@@
 \begin{figure*}[t]
-    photos of 3D objects taken 15 degrees apart. K = Keypoint, D = 
-Descriptor\.}
+    \centering
+    \includegraphics[width=2\columnwidth]{images/results_descriptors_imageset1}
     \caption{Keypoint / Descriptor combinations measured on 15 pairs of 
@@
 
+\appendix
+\section{Proof of equivalence between \emph{Self-Match} and 
+\emph{Self-Match-Ext}}
+In this appendix we prove the equivalence between \emph{Self-Match} and 
+\emph{Self-Match-Ext}. To do this, we look at the nearest neighbor 
+$f_{nn}$ of every query feature $f_{q}$ and consider the two cases of 
+$f_{nn} \in F_{query}$ and $f_{nn} \in
+F_{target}$. For $f_{nn} \in F_{target}$ the uniqueness ratio of 
+\emph{Self-Match-Ext} is:
+\begin{align*}
+    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
+        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
+        &= \text{r}(f_{q}, F_{target}, F_{baseline})
+\end{align*}
+
+Since $F_{proposed} = F_{target}$ for \emph{Self-Match} this shows that
+when the nearest neighbor is found in the target image, the two 
+algorithms behave identically. For $f_{nn} \in F_{query}$ we know that 
+the best match for the query feature is in the query image itself. Since 
+neither algorithm returns a correspondence within the same image, they 
+also behave identically for this case. This proves that for any set of 
+\emph{query features} \emph{Self-Match} returns the same matches as 
+\emph{Self-Match-Ext}.
+
+\section{Proof of equivalence between \emph{Mirror-Match} and 
+\emph{Mirror-Match-Ext}}
+
+In this appendix we prove the equivalence between \emph{Mirror-Match} 
+and \emph{Mirror-Match-Ext}. This proof is almost identical to the 
+equivalence proof between \emph{Self-Match} and \emph{Self-Match-Ext}. 
+To prove this, we look at the nearest neighbor $f_{nn}$ of every query 
+feature $f_{q}$ and consider the two cases of $f_{nn} \in F_{query}$ and 
+$f_{nn} \in
+F_{target}$. For $f_{nn} \in F_{target}$ the uniqueness ratio of 
+\emph{Mirror-Match-Ext} is:
+\begin{align*}
+    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
+        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
+        &= \text{r}(f_{q}, F_{target}, F_{baseline})
+\end{align*}
+
+Since $F_{proposed} = F_{target}$ for \emph{Mirror-Match} this shows that
+when the nearest neighbor is found in the target image, the two 
+algorithms behave identically. For $f_{nn} \in F_{query}$ we know that 
+the best match for the query feature is in the query image itself. Since 
+neither algorithm returns a correspondence within the same image, they 
+also behave identically for this case. This proves that for any set of 
+\emph{query features} \emph{Mirror-Match} returns the same matches as 
+\emph{Mirror-Match-Ext}.
+
 \bibliographystyle{IEEEtran}

### 2014-04-14 text/journal/paper.tex
Various improvements in terms of clarity

@@
 
-In the author's last paper we introduced \emph{Mirror Match} and 
+In the author's last paper we introduced \emph{Mirror-Match} and 
 \emph{Mirror-Match with Clustering}, two algorithms that we showed to 
@@
 related matching algorithms as well as the theoretical foundation which 
-enables us to understand why \emph{Mirror Match} performs better than 
+enables us to understand why \emph{Mirror-Match} performs better than 
 \emph{Ratio Match} in the first place.
@@
 decided uniquely based on the \emph{target image}. In turn 
-\emph{Mirror-Match-Ext} as introduced by the authors in 
+\emph{Mirror-Match} as introduced by the authors in 
 \cite{arnfred2013mirror}, works by constructing the \emph{proposal set} 
 and \emph{baseline set} by combining features from both the \emph{query} 
-and \emph{target image}. By similar compositions of the \emph{proposal} 
+and \emph{target image}. By similar variations of the \emph{proposal} 
 and \emph{baseline set} we derive four more algorithms as illustrated in 
-Figure~\ref{fig:overview}.
+Figure~\ref{fig:overview}, however we will not discuss 
+\emph{Self-Match-Ext} and \emph{Both-Match} further in this paper since 
+we show them to be equivalent with \emph{Self-Match} and 
+\emph{Mirror-Match} respectively in Appendix~\ref{A:self} and 
+\ref{A:mirror}.
 
@@
 
-% TODO: include point about two of the algorithms being identical
 %
@@
 
-Based on these assumptions we first prove that 
-The above proof can easily be extended to show that \emph{Mirror-Match 
-1} and \emph{Mirror-Match-Ext} returns the same correspondences too, and 
-both will be referred to as \emph{Mirror Match} from here on.
-
-For the case of \emph{Ratio-Match} and \emph{Ratio-Match-Ext} however we 
-can show that \emph{Ratio-Match-Ext} is equal or better than 
-\emph{Ratio-Match}.  Consider again the nearest neighbor $f_{nn}$ of a 
-query feature $f_{q}$ and the two cases where we either have the $f_{nn} 
-\in F_{query}$ or $f_{nn} \in F_{target}$. For $f_{nn} \in F_{target}$ 
-the uniqueness ratio of \emph{Ratio-Match-Ext} is:
+Based on these assumptions we prove that \emph{Ratio-Match-Ext} is equal 
+or better than \emph{Ratio-Match} in terms both precision and recall.  
+Consider the nearest neighbor $f_{nn}$ of a query feature $f_{q}$ and 
+the two cases where we either have the $f_{nn} \in F_{query}$ or $f_{nn} 
+\in F_{target}$. For $f_{nn} \in F_{target}$ the uniqueness ratio of 
+\emph{Ratio-Match-Ext} is:
 \begin{align*}
@@
 
-Where as \emph{Ratio-Match-Ext} does not return the correspondence if 
-the nearest neighbor of a query feature is in the \emph{query image}, 
-\emph{Ratio-Match} is likely to do so, since the uniqueness ratio is 
-found by dividing with the second nearest neighbor in the \emph{target 
-image}. This shows us that for cases where a query feature has a nearest 
-neighbor in the \emph{query image}, \emph{Ratio-Match-Ext} is superior 
-to \emph{Ratio-Match}. Since query features with a nearest neighbor in 
-the \emph{query image} are false correspondences per assumption \#1 and 
-\#2, this proves that \emph{Ratio-Match-Ext} has superior 
-\emph{Precision} to \emph{Ratio-Match} while maintaining equal 
-\emph{Recall}.
-
-Finally we show that \emph{Mirror Match} is equal or better than 
-\emph{Ratio-Match-Ext}. Consider as before the nearest neighbor $f_{nn}$ 
-of a query feature $f_{q}$. When $f_{nn}$ resides in the \emph{query 
-image} both algorithms behave alike and discard the match.  However, 
-consider the uniqueness ratio of \emph{Mirror Match} for the case where 
-$f_{nn}$ resides in the \emph{target image}:
+That is, \emph{Ratio-Match} calculates the ratio based on the two 
+nearest correspondences in the \emph{Target Image}. 
+\emph{Ratio-Match-Ext} on the other hand does not return any 
+correspondence because the nearest neighbor is in the \emph{Query 
+Image}. Since query features with a nearest neighbor in the \emph{query 
+image} are false correspondences per assumption \#1 and \#2, this proves 
+that \emph{Ratio-Match-Ext} has superior \emph{Precision} to 
+\emph{Ratio-Match} while maintaining equal \emph{Recall}.
+
+Next we show that \emph{Mirror-Match} is equal or better than 
+\emph{Ratio-Match-Ext} in terms of precision and recall. Consider as 
+before the nearest neighbor $f_{nn}$ of a query feature $f_{q}$. When 
+$f_{nn}$ resides in the \emph{query image} both algorithms behave alike 
+and discard the match.  However, consider the uniqueness ratio of 
+\emph{Mirror-Match} for the case where $f_{nn}$ resides in the 
+\emph{target image}:
 \begin{align*}
@@
 \emph{Ratio-Match-Ext}.  However for an untrue correspondence with a 
-baseline match in the \emph{query image} which is closer than the
-baseline match in the \emph{target image}, \emph{Mirror Match} will 
-return a worse uniqueness ratio. This in turns means that \emph{Mirror 
-Match} is equal or better than \emph{Ratio-Match-Ext} in terms of  
+baseline match in the query image which is closer than the
+baseline match in the target image, \emph{Mirror-Match} will return a 
+worse uniqueness ratio. This in turns means that \emph{Mirror-Match} is 
+equal or better than \emph{Ratio-Match-Ext} in terms of  
 \emph{Precision} while maintaining equal \emph{Recall}.
+
+Using a similar procedure we prove that \emph{Self-Match} is equal to
+\emph{Self-Match-Ext} and \emph{Both-Match} is equal to \emph{Mirror
+Match} in Appendix~\ref{A:self} and \ref{A:mirror} respectively.
 
@@
 \begin{align*}
-    \textit{Self-Match} &= \textit{Self-Match-Ext} \\
-    \textit{Mirror-Match} &= \textit{Mirror-Match-Ext} \\
     \textit{Ratio-Match} &\leq \textit{Ratio-Match-Ext} \leq 
-    \textit{Mirror Match}
+    \textit{Mirror-Match}
 \end{align*}
 
-The difference between \emph{Self-Match} and \emph{Ratio-Match} is is 
+The difference between \emph{Self-Match} and \emph{Ratio-Match} is
 the source of the \emph{baseline set}. For true correspondences we 
@@
 Mikolajczyk and Tuytelaars shows that this property depends strongly on 
-the differences between \emph{query} and \emph{target} image 
+the differences between query and target image 
 \cite{mikolajczyk2005performance} \cite{tuytelaars2008local}. In the 
@@
 The last assumption states that the uniqueness ratio using either the 
-\emph{query} or \emph{target image} as the baseline set would be similar
+\emph{query} or target image as the baseline set would be similar
 in distribution when we know that the feature point we are matching has 
@@
 the third assumption is obviously true for any cases where the second 
-closest feature point has a true correspondence in the other image. In 
-the general case it is likely that the baseline yields different 
-uniqueness ratios depending on the features it contains, but for the 
-case where the baseline match has a true correspondence in the other 
-image we can verify the assumption by looking at the performance of 
-\emph{Self-Match} compared with \emph{Ratio-Match}. To compare we plot 
-the actual \emph{uniqueness ratios} measured from 84 3D objects in 
-Figure~\ref{fig:ratio_hist}. For ratios lower than $0.7$ this is 
-generally the case, but as we approach more lenient thresholds the 
-performance of \emph{Mirror-Match} might no longer be equal or better 
-than \emph{Ratio-Match-Ext} in terms of precision.
+closest feature point has a true correspondence in the other image. For 
+non-ideal feature descriptors where the baseline match has a true 
+correspondence in the other image we can verify the assumption by 
+looking at the \emph{uniqueness ratio} for a true correspondences when 
+it is based on the query image compared to when it is based on the 
+target image. To compare we plot the actual \emph{uniqueness ratios} 
+measured from $84$ 3D objects in Figure~\ref{fig:ratio_hist}. For ratios 
+lower than $0.7$ this is generally the case, but as we approach more 
+lenient thresholds the performance of \emph{Mirror-Match} might no 
+longer be equal or better than \emph{Ratio-Match-Ext} in terms of 
+precision.
 % Needs rewording
@@
 in a precision / recall plot to make it easy to compare performance in
-terms of precision at similar levels of recall.
+terms of precision at similar levels of recall. For the application of
+feature matching it is important to keep in mind that for many
+applications, such as image stitching, object and scene recognition and
+near duplicate detection, precision is much more important than recall,
+since a handfull of highly reliable correspondences tells us much more
+about the similarity of image components than a high number of imprecise
+matches. For applications where we intent to combine one of the
+algorithms with a geometric method, we would ideally like for it to
+produce results with a high recall that can then be further filtered by
+a geometric method.
 
@@
 \emph{Ratio-Match} generally peaking at around
-a 20 percentage-point increase in precision. Finally the the performance
+a $20$ percentage-point increase in precision. Finally the the performance
 gain decreases as we further increase the rotation to between $45$ and 
@@
 \begin{table}[htb]
-\caption{Complexity and running times tested on 15 image pairs on 3 
-lighting conditions with average $n = 236.73$ and average $m = 247.38$ 
+\caption{Complexity and running times tested on 45 image pairs with average $n = 237$ and average $m = 247$ 
 as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
@@
     \emph{Ratio-Match-Ext} & $O(n\log(n+m))$ & 112s\\
-    \emph{Mirror-Match} & $O(n\log(n(n+m)))$ & 116s\\
-    %\emph{Mirror-Match-Ext} & $O(n\log(n+m))$ & 110s \\
+    %\emph{Both-Match} & $O(n\log(n(n+m)))$ & 116s\\
+    \emph{Mirror-Match} & $O(n\log(n+m))$ & 110s \\
     \hline
@@
 \appendix
-\section{Proof of equivalence between \emph{Self-Match} and 
-\emph{Self-Match-Ext}}
+
+\subsection{Proof of equivalence of Self-Match and Self-Match-Ext}
+\label{A:self}
+
 In this appendix we prove the equivalence between \emph{Self-Match} and 
@@
 
-\section{Proof of equivalence between \emph{Mirror-Match} and 
-\emph{Mirror-Match-Ext}}
-
-In this appendix we prove the equivalence between \emph{Mirror-Match} 
-and \emph{Mirror-Match-Ext}. This proof is almost identical to the 
-equivalence proof between \emph{Self-Match} and \emph{Self-Match-Ext}. 
-To prove this, we look at the nearest neighbor $f_{nn}$ of every query 
-feature $f_{q}$ and consider the two cases of $f_{nn} \in F_{query}$ and 
-$f_{nn} \in
+\subsection{Proof of equivalence of Both-Match and Mirror-Match}
+\label{A:mirror}
+
+In this appendix we prove the equivalence between \emph{Both-Match} and 
+\emph{Mirror-Match}. This proof is almost identical to the equivalence 
+proof between \emph{Self-Match} and \emph{Self-Match-Ext}. To prove 
+this, we look at the nearest neighbor $f_{nn}$ of every query feature 
+$f_{q}$ and consider the two cases of $f_{nn} \in F_{query}$ and $f_{nn} 
+\in
 F_{target}$. For $f_{nn} \in F_{target}$ the uniqueness ratio of 
-\emph{Mirror-Match-Ext} is:
+\emph{Mirror-Match} is:
 \begin{align*}
@@
 
-Since $F_{proposed} = F_{target}$ for \emph{Mirror-Match} this shows that
+Since $F_{proposed} = F_{target}$ for \emph{Both-Match} this shows that
 when the nearest neighbor is found in the target image, the two 
@@
 also behave identically for this case. This proves that for any set of 
-\emph{query features} \emph{Mirror-Match} returns the same matches as 
-\emph{Mirror-Match-Ext}.
+\emph{query features} \emph{Both-Match} returns the same matches as 
+\emph{Mirror-Match}.
 

### 2014-04-15 text/journal/paper.tex
Last updates to paper

@@
 features where $m$ is significantly different from $n$ the complexities 
-are as noted in Table~\ref{table:running_times}. Note that 
-implementations refer to the algorithms as specified in 
-Table~\ref{table:distinctness}. In practice the constant factors 
+are as noted in Table~\ref{table:running_times}. In practice the constant factors 
 involved in the actual matching of two images with approximately the 
@@
 can easily replace \emph{Ratio-Match} without any performance penalty 
-and with an increase in precisionon but are both limited to matching 
+and with an increase in precision but are both limited to matching 
 image pairs like \emph{Ratio-Match}.

### 2014-04-15 text/journal/paper.tex
Stefans changes

--- 2014-04-11 text/journal/paper.tex
@@
-% To compile, make sure to have the following packages installed:
-% texlive, texlive-latex-extra, texlive-science, 
-% texlive-fonts-recommended, texlive-fonts-extras
-
-\documentclass[journal]{IEEEtran}
+%% bare_jrnl_compsoc.tex
+%% V1.3
+%% 2007/01/11
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.7 or later) with an IEEE Computer
+%% Society journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%
+%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
+%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. IEEE's font choices can trigger bugs that do  ***
+% *** not appear when using other class files.                            ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+% Note that the a4paper option is mainly intended so that authors in
+% countries using A4 can easily print to A4 and see how their papers will
+% look in print - the typesetting of the document will not typically be
+% affected with changes in paper size (but the bottom and side margins will).
+% Use the testflow package mentioned above to verify correct handling of
+% both paper sizes by the user's LaTeX system.
+%
+% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
+% should be used if it is desired that the figures are to be displayed in
+% draft mode.
+%
+% The Computer Society usually requires 10pt for submissions.
+%
+\documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[12pt,journal,compsoc]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress]{cite}
+\else
+  % normal IEEE
+  \usepackage{cite}
+\fi
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
+% not currently provide for hyperlinked citations.
+% The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
+% The documentation is contained in the cite.sty file itself.
+%
+% Note that some packages require special options to format as the Computer
+% Society requires. In particular, Computer Society  papers do not use
+% compressed citation ranges as is done in typical IEEE papers
+% (e.g., [1]-[4]). Instead, they list every citation separately in order
+% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
+% package with the nocompress option which is supported by cite.sty v4.0
+% and later. Note also the use of a CLASSOPTION conditional provided by
+% IEEEtran.cls V1.7 and later.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation can
+% be obtained at: 
+% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
+% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+\usepackage[cmex10]{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics. If using
+% it, be sure to load this package with the cmex10 option to ensure that
+% only type 1 fonts will utilized at all point sizes. Without this option,
+% it is possible that some math symbols, particularly those within
+% footnotes, will be rendered in bitmap form which will result in a
+% document that can not be IEEE Xplore compliant!
+%
+% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
+% There is also a support site at:
+% http://algorithms.berlios.de/index.html
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/tools/
+
+%\usepackage{mdwmath}
+%\usepackage{mdwtab}
+% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
+% especially mdwmath.sty and mdwtab.sty which are used to format equations
+% and tables, respectively. The MDWtools set is already installed on most
+% LaTeX systems. The lastest version and documentation is available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+%\usepackage{eqparbox}
+% Also of notable interest is Scott Pakin's eqparbox package for creating
+% (automatically sized) equal width boxes - aka "natural width parboxes".
+% Available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
+
+% *** SUBFIGURE PACKAGES ***
+\ifCLASSOPTIONcompsoc
+%\usepackage[tight,normalsize,sf,SF]{subfigure}
+\else
+%\usepackage[tight,footnotesize]{subfigure}
+ \fi
+% subfigure.sty was written by Steven Douglas Cochran. This package makes it
+% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
+% work, it is a good idea to load it with the tight package option to reduce
+% the amount of white space around the subfigures. Computer Society papers
+% use a larger font and \sffamily font for their captions, hence the
+% additional options needed under compsoc mode. subfigure.sty is already
+% installed on most LaTeX systems. The latest version and documentation can
+% be obtained at:
+% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
+% subfigure.sty has been superceeded by subfig.sty.
+
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false]{caption}
+%  \usepackage[font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false]{caption}
+%  \usepackage[font=footnotesize]{subfig}
+%\fi
+% subfig.sty, also written by Steven Douglas Cochran, is the modern
+% replacement for subfigure.sty. However, subfig.sty requires and
+% automatically loads Axel Sommerfeldt's caption.sty which will override
+% IEEEtran.cls handling of captions and this will result in nonIEEE style
+% figure/table captions. To prevent this problem, be sure and preload
+% caption.sty with its "caption=false" package option. This is will preserve
+% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
+% (recommended due to many improvements over 1.2) of subfig.sty supports
+% the caption=false option directly:
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+%
+% The latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
+% The latest version and documentation of caption.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure. The latest version and documentation can be found at:
+% http://www.ctan.org/tex-archive/macros/latex/base/
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
+% Documentation is contained in the stfloats.sty comments as well as in the
+% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
+% does not allow \baselineskip to stretch. Authors submitting work to the
+% IEEE should note that IEEE rarely uses double column equations and
+% that authors should try to avoid such use. Do not be tempted to use the
+% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
+% not format its papers in such ways.
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
+% This package may be useful when used in conjunction with IEEEtran.cls'
+% captionsoff option. Some IEEE journals/societies require that submissions
+% have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.3.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% For subfigure.sty:
+% \let\MYorigsubfigure\subfigure
+% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat/subfig command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
+% Read the url.sty source comments for usage information. Basically,
+% \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
 %\documentclass{article}
@@
 %\usepackage{sidecap}
-\usepackage{graphicx}
 \usepackage{cite}
@@
 %\usepackage[stable]{footmisc}
-%\usepackage{caption}
 %\usepackage{adjustbox}
+\usepackage{balance}
 \usepackage{subcaption}
@@
 \usepackage{algorithm}
-\usepackage{amsmath}
 \usepackage{amssymb}
@@
 
-\title{A decade of lost precision: Introducing a general framework for 
-image feature matching without geometric constraints}
-
-\author{%
-\IEEEauthorblockN{%
-Jonas Toft Arnfred,\IEEEauthorrefmark{1} Stefan 
-Winkler,\IEEEauthorrefmark{1} Sabine S\"usstrunk\IEEEauthorrefmark{2}}\\
-\vspace{1mm}
-\IEEEauthorblockA{%
-\IEEEauthorrefmark{1}~Advanced Digital Sciences Center (ADSC), University of Illinois at Urbana-Champaign (UIUC), Singapore\\
-\IEEEauthorrefmark{2}~\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland}
-}
-
 \begin{document}
+%
+% paper title
+% can use linebreaks \\ within to get better formatting as desired
+\title{Decade of Lost Precision:\\
+A General Framework For Image Feature Matching Without Geometric Constraints}
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
+%
+%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
+% lists the Computer Society journals use for "first footnote" author
+% affiliations. Use \IEEEcompsocthanksitem which works much like \item
+% for each affiliation group. When not in compsoc mode,
+% \IEEEcompsocitemizethanks becomes like \thanks and
+% \IEEEcompsocthanksitem becomes a line break with idention. This
+% facilitates dual compilation, although admittedly the differences in the
+% desired content of \author between the different types of papers makes a
+% one-size-fits-all approach a daunting prospect. For instance, compsoc 
+% journal papers have the author affiliations above the "Manuscript
+% received ..."  text while in non-compsoc journals this is reversed. Sigh.
+
+\author{Jonas~Toft~Arnfred,
+        Stefan~Winkler,
+        Sabine~S\"usstrunk% <-this % stops a space
+\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem J.~T.~Arnfred and S.~Winkler are with the Advanced Digital Sciences Center (ADSC), University of Illinois at Urbana-Champaign (UIUC), Singapore.\protect\\
+% note need leading \protect in front of \\ to get a newline within \thanks as
+% \\ is fragile and will error, could use \hfil\break instead.
+% E-mail: 
+\IEEEcompsocthanksitem S.~S\"usstrunk is with the \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland.}% <-this % stops a space
+\thanks{}}
+
+%\IEEEauthorblockN{%
+%Jonas Toft Arnfred,\IEEEauthorrefmark{1} Stefan Winkler,\IEEEauthorrefmark{1} Sabine S\"usstrunk\IEEEauthorrefmark{2}}\\
+%\vspace{1mm}
+%\IEEEauthorblockA{%
+%\IEEEauthorrefmark{1}~Advanced Digital Sciences Center (ADSC), University of Illinois at Urbana-Champaign (UIUC), Singapore\\
+%\IEEEauthorrefmark{2}~\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland}
+
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+% 
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+%\markboth{IEEE Trans. PAMI}%
+%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% The publisher's ID mark at the bottom of the page is less important with
+% Computer Society journal papers as those publications place the marks
+% outside of the main text columns and, therefore, unlike regular IEEE
+% journals, the available text space is not reduced by their presence.
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}
+% or like this to get the Computer Society new two part style.
+%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2007 IEEE}%
+%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark (Computer Society jorunal
+% papers don't need this extra clearance.)
+
+% for Computer Society papers, we must declare the abstract and index terms
+% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
+% command as these need to go into the title area created by \maketitle.
+\IEEEcompsoctitleabstractindextext{%
+\begin{abstract}
+%\boldmath
+Computer vision applications that involve the matching of local image 
+features frequently use \emph{Ratio-Match} as introduced by Lowe and 
+others, but is this really the optimal approach?  We formalize the 
+theoretical foundation of \emph{Ratio-Match} and propose a general 
+framework encompassing \emph{Ratio-Match} and five other matching 
+methods. Using this framework, we establish a theoretical 
+performance ranking in terms of precision and recall, 
+proving that all five methods consistently outperform or equal \emph{Ratio-Match}.
+
+We confirm the theoretical results experimentally on over 3000 image 
+pairs and show that we can increase matching precision
+without further assumptions about the images we are using.  These gains 
+are achieved by making only a few key changes of the \emph{Ratio-Match} algorithm and do not increase computation times.
+\end{abstract}
+% IEEEtran.cls defaults to using nonbold math in the Abstract.
+% This preserves the distinction between vectors and scalars. However,
+% if the journal you are submitting to favors bold math in the abstract,
+% then you can use LaTeX's standard command \boldmath at the very start
+% of the abstract to achieve this. Many IEEE journals frown on math
+% in the abstract anyway. In particular, the Computer Society does
+% not want either math or citations to appear in the abstract.
+
+% Note that keywords are not normally used for peer review papers.
+\begin{keywords}
+Feature matching, ratio match, mirror match, self match
+\end{keywords}}
+
+% make the title area
 \maketitle
-%
-\begin{abstract}
-Solutions in computer vision involving the matching of local image 
-features frequently use \emph{Ratio-Match} as introduced by Lowe and 
-others, but is this really the best approach? We formalize the 
-theoretical foundation of \emph{Ratio-Match} and propose a general 
-framework encompassing \emph{Ratio-Match} and three other matching 
-methods. Using the framework we establish a theoretical order of 
-performance in terms of precision and recall between the methods and 
-prove that \emph{Ratio-Match} is consistently equalled or outperformed 
-by all other methods of the framework.
-
-We confirm the theoretical results experimentally on over 3000 image 
-pairs and show that we can easily increase matching precision
-without further assumptions about the images we are using. These gains 
-comes without increased computation time by changing only a few key 
-components of the \emph{Ratio-Match} algorithm.
-
-\end{abstract}
-%
+
+% To allow for easy dual compilation without having to reenter the
+% abstract/keywords data, the \IEEEcompsoctitleabstractindextext text will
+% not be used in maketitle, but will appear (i.e., to be "transported")
+% here as \IEEEdisplaynotcompsoctitleabstractindextext when compsoc mode
+% is not selected <OR> if conference mode is selected - because compsoc
+% conference papers position the abstract like regular (non-compsoc)
+% papers do!
+\IEEEdisplaynotcompsoctitleabstractindextext
+% \IEEEdisplaynotcompsoctitleabstractindextext has no effect when using
+% compsoc under a non-conference mode.
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
 \section{Introduction}
@@
 vision algorithms that deal with sparse local image features. This 
-includes image categorisation \cite{bosch2008scene}, image stitching 
-\cite{brown2007automatic}, object detection \cite{zhang2007local} and 
-near duplicate detection \cite{zhao2009scale} to mention a few examples.  
+includes image categorization \cite{bosch2008scene}, image stitching 
+\cite{brown2007automatic}, object detection \cite{zhang2007local}, and 
+near duplicate detection \cite{zhao2009scale}, to mention just a few examples.  
 These problems all rely on being able to accurately find the 
@@
 many applications the target images have undergone transformations with 
-respect to the query image; in stereo vision, the camera angle is 
+respect to the query image; in stereo vision, the viewpoint is 
 different, while in object recognition and near duplicate detection both 
-the lighting and even the object itself can also be transformed.
+the lighting and even the object itself may also be transformed.
 
@@
 descriptor centric approach on the other hand uses the local image 
-information around the keypoint to create a descriptor and match 
+information around the keypoint to create a descriptor and matches 
 descriptors based on their similarity.
 
-In the purely geometric approach we try to consistently match feature 
-points based on their position in the images. Scott and Longuet-Higgins 
+In the purely geometric approach, feature points are matched based on their position in the images. 
+Scott and Longuet-Higgins 
 \cite{scott1991algorithm} and Shapiro and Brady 
@@
 deriving a coherent set of matches from the eigenvalues of the 
-correspondence matrix. Other examples of this approach include Sclaroff 
-and Pentland \cite{sclaroff1995modal} as well as Carcassoni and Hancock 
-\cite{carcassoni2003spectral}.
+correspondence matrix. Other examples of this approach include \cite{sclaroff1995modal,carcassoni2003spectral}.
 
 The descriptor centric approach on the other hand finds matches by 
-pairing keypoints from locations where the images are similar. The first 
+pairing similar keypoints. The first 
 examples of this approach used the correlation of the raw image data 
-immidiately surrounding the feature point \cite{deriche1994robust}, 
-\cite{baumberg2000reliable} to calculate this similarity. Later 
-algorithms were enhanced by creating invariant feature descriptors first 
+immediately surrounding the feature point \cite{deriche1994robust,baumberg2000reliable} to calculate this similarity. Later 
+algorithms were enhanced by invariant feature descriptors as first 
 introduced in \cite{schmid1997local} and later popularized by the work 
-of Lowe introducing SIFT \cite{lowe2004sift} and Bay introducing SURF 
+of Lowe introducing SIFT \cite{lowe2004sift} and Bay et al.\ introducing SURF 
 \cite{bay2006surf}.
 
-Many descriptor variations have since been proposed and a few surveys 
-have emerged comparing them. Mikolajczyk and Schmid evaluates 11 such 
+Many descriptor variations have since been proposed, and a few surveys 
+have emerged comparing them. Mikolajczyk and Schmid \cite{mikolajczyk2005performance} evaluate 11 such 
 feature descriptors in a paper where they also introduce the graffiti 
 image set which has later become a common benchmark for image matching 
-algorithms \cite{mikolajczyk2005performance}.  Later Moreels and Perona 
-evaluated 5 descriptors with different keypoint detectors using a large 
-image set consisting of 3D models \cite{moreels2007evaluation}. Finally 
-Heinly et al.\ take a closer look at binary features such as BRIEF 
-\cite{calonder2010brief}, BRISK \cite{leutenegger2011brisk} and ORB 
-\cite{rublee2011orb} comparing them to SIFT and SURF 
-\cite{heinly2012comparative}.
+algorithms.  Moreels and Perona \cite{moreels2007evaluation}
+evaluate 5 descriptors with different keypoint detectors using a large 
+image set consisting of 3D models. 
+Heinly et al.\ \cite{heinly2012comparative} take a closer look at binary features such as BRIEF 
+\cite{calonder2010brief}, BRISK \cite{leutenegger2011brisk}, and ORB 
+\cite{rublee2011orb}, comparing them to SIFT and SURF.
 
 A straightforward way to find a set of correspondences using only 
-feature points is to threshold the similarity measure of the feature 
+feature points is to apply a threshold to the similarity measure of the feature 
 vectors, accepting only correspondences that score above a certain 
-threshold \cite{szeliski2010}. When we match images with the assumption 
-that the correspondence between two feature points will be unique we can 
+level of similarity \cite{szeliski2010}. When we match images with the assumption 
+that the correspondence between two feature points will be unique, we can 
 further increase precision by only matching a feature point to its 
@@
 finding has later been tested by several independent teams, all 
-concluding that thresholding based on the ratio is generally superior to 
-thresholding on similarity \cite{lowe2004sift}, 
-\cite{mikolajczyk2005performance}, \cite{moreels2007evaluation}, 
-\cite{rabin2009statistical}. Brown and Lowe extends ratio match to deal 
+concluding that thresholding based on this ratio is generally superior to 
+thresholding based on similarity \cite{lowe2004sift,mikolajczyk2005performance,moreels2007evaluation,rabin2009statistical}.
+
+Brown and Lowe \cite{brown2005multi} extend ratio match to deal 
 with a set of images by using not the ratio of the best and second best 
 correspondence, but the average ratio of the best and the average of 
-second best correspondences across a set of images 
-\cite{brown2005multi}.  Rabin et al.\ tries to enhance descriptor 
+second best correspondences across a set of images.  Rabin et al.\ tries to enhance descriptor 
 matching by looking at the statistical distribution of local features in 
-the matched images, and only return a correspondence when such a 
+the matched images, and only return a match when such a 
 correspondence would not occur by mere chance 
 \cite{rabin2009statistical}. Finally, a precursor of the algorithms 
-discussed in this paper were introduced by the authors as 
-\emph{Mirror-Match} \cite{arnfred2013mirror} which makes use of the 
+discussed in this paper was introduced by the authors as 
+\emph{Mirror-Match} \cite{arnfred2013mirror}, which makes use of the 
 feature points in both images to decide if a match is valid.
@@
 A plethora of solutions have combined ratio match with various geometric 
-constraints to improve matching. These constraints are based on 
-assumptions regarding the transformation between the query and target 
-images. At the stricter end we have epipolar constraints assuming
-that the images can be tied by a homography \cite{torr2000mlesac}, 
-\cite{chum2005matching} and angular constraints assuming the 
-correspondences are angled similarly \cite{kim2008efficient}, 
-\cite{schmid1997local}. Often these approaches are made computationally 
-feasible by modelling the case of feature correspondences as an instance 
-of graph matching where each feature is a vertex and edge values 
-correspond to a geometric relation between two features. In this case 
-approximate graph matching algorithms can be used to efficiently 
-establish an isomorphism between the graph of features in two images 
-\cite{leordeanu2005spectral}, \cite{torresani2008feature}, 
-\cite{yarkony2010covering}. Finally others define image regions and 
-reject or accept correspondences based on the regions they connect 
-\cite{cho2009feature}, \cite{wu2011robust}.
-
-Any matching method relying on geometric constraints is restrained by an
+constraints to improve matching. These constraints are
+based on assumptions regarding the transformation between the query and 
+target images. At the stricter end we have epipolar constraints, assuming
+that the images can be tied by a homography \cite{torr2000mlesac,chum2005matching}, and angular constraints, assuming the 
+correspondences are angled similarly \cite{kim2008efficient,schmid1997local,leordeanu2005spectral}. 
+These constraints can be relaxed using more sophisticated models.  Torresani et al.\ \cite{torresani2008feature} 
+attempted to model transformations using graph matching similar to 
+\cite{deriche1994robust}. Others define image regions and reject or 
+accept correspondences based on the regions they connect 
+\cite{cho2009feature,wu2011robust}.
+
+Any matching method relying on geometric constraints is restrained by 
 inherent assumptions about the geometric relationship between the two 
-images. Broad assumptions such as angular constraints often used in 
-graph matching only apply to simple image transformations. For more 
-complex transformations we need models suitable for each particular case 
-and hence limit the algorithm to the subset of images that fit the 
-model. In the case of object recognition for example, the 
-transformations from one scene to another often feature a change in 
-perspective, background and sometimes variations within the object 
-itself. In most circumstances this makes these methods unsuited for 
-epipolar or angular constraints.
-
-If we intent to match these instances using geometric features we are 
-forced to used a sophisticated model that reflects the variations in 
-which we find these objects, an in the process lose generality. For this 
-reason general descriptor based algorithms are crucial for 
-correspondence applications calling for generality. In addition the 
-advantage of purely descriptor based methods is motivated by the fact 
-that any geometric method acts as a filter on a given set of 
-correspondences.  If this set contains less incorrect correspondences, 
+images. Broad assumptions such as the epipolar constraint only apply in 
+simple image transformations. For more complex transformations we need 
+models suitable for each particular case, which limits the algorithm 
+to the subset of images that fit the model.  In the case of object 
+recognition for example, the transformations from one scene to another 
+often feature a change in perspective, background, and sometimes variations within the object 
+itself: a person can change pose, a car model can have different 
+configurations, a flower can bloom etc.
+
+When matching these instances we are forced to either create a 
+sophisticated model that represents the variables of transformation 
+within the object, or alternatively find correspondences using an 
+algorithm with no inherent geometric assumptions. Besides, 
+any geometric method acts as a filter on a given set of 
+correspondences.  Therefore, if the initial set of purely descriptor-based matches contains fewer incorrect correspondences, 
 the final set can be calculated faster and more accurately.
 
-The methods we propose in this paper are designed to be free of 
+The methods we propose in this paper are designed to be free from 
 assumptions about image geometry. They extend and improve on Lowe's 
-\emph{Ratio-Match} \cite{lowe2004sift} and the author's \emph{Mirror 
+\emph{Ratio-Match} \cite{lowe2004sift} and the authors' \emph{Mirror 
 Match} \cite{arnfred2013mirror} by generalizing both algorithms to a 
-framework of matching methods. We go on to formally establish an order 
-comparing how well different methods within the framework compares in 
+framework of matching methods. We go on to formally establish a ranking
+based on how well different methods within the framework compare in 
 terms of precision and recall. Our experimental evaluations confirm the 
-theoretical results and show that \emph{Ratio-Match} on all counts is a 
-unoptimal choice as a matching algorithm independent of application.
-
-In the author's last paper we introduced \emph{Mirror Match} and 
-\emph{Mirror-Match with Clustering}, two algorithms that we showed to 
-perform better than the state of the art. The novel contributions of 
-this paper consists of two new algorithms completing a framework of four 
-related matching algorithms as well as the theoretical foundation which 
-enables us to understand why \emph{Mirror Match} performs better than 
-\emph{Ratio Match} in the first place.
-
-The paper is organized as follows. I section~\ref{S:MatchingMethods} we 
-introduce the original \emph{Ratio-Match}, extend on this method to 
-introduce the proposed framework and go on to compare the members of the 
-framework theoretically.  In section~\ref{S:Experiments} we present 
-evaluations and discuss the results obtained.  Section~\ref{S:Summary} 
+theoretical results and show that \emph{Ratio-Match} on all counts is generally a 
+sub-optimal choice as a matching algorithm.
+
+The paper is organized as follows. In Section~\ref{S:MatchingMethods} we 
+introduce the original \emph{Ratio-Match}, generalize this method to 
+introduce the proposed framework, and compare the methods of the 
+framework theoretically.  In Section~\ref{S:Experiments} we present 
+our experimental validation and discuss the results obtained.  Section~\ref{S:Summary} 
 concludes the paper.
 
-\section{Matching Methods}
+\section{Matching Framework}
 \label{S:MatchingMethods}
@@
 %
-\emph{Ratio-Match} as introduced by Deriche et al.
+\emph{Ratio-Match} as introduced by Deriche et al.\ 
 \cite{deriche1994robust} and later used by 
@@
 use of a \emph{uniqueness ratio}. For each feature in the \emph{query 
-image} we find a possible match by identifying the nearest neighbor and 
+image}, it finds a possible match by identifying the nearest neighbor and 
 returning this match only if the \emph{uniqueness ratio} is above a 
-given threshold, $\tau$. Given $f_q$, a feature from the \emph{query 
+given threshold $\tau$.
+
+Given $f_q$, a feature from the \emph{query 
 image} and $F_{target}$, a set of features from the \emph{target image}, 
@@
 \begin{equation*}
-    \argmin_{f_t \in F_{target}} d(f_q, f_t)
+    f_{nn} = \argmin_{f_t \in F_{target}} d(f_q, f_t).
 \end{equation*}
-Here, $d(f_i, f_j)$ is the distance between the feature descriptors.  
-With SIFT and SURF this is the euclidian distance of the feature vectors
-\cite{lowe2004sift} \cite{bay2006surf} where as BRIEF, BRISK and FREAK 
-measure the distance as the hamming distance \cite{leutenegger2011brisk} 
-\cite{calonder2010brief} \cite{alahi2012freak}.  If we let $f_p$ and 
-$f_b$ be the nearest and second nearest neighbor of a feature, $f_q$, 
+Here, $d(f_i, f_j)$ is the distance between feature descriptors.  
+With SIFT and SURF this is the Euclidean distance of the feature vectors
+\cite{lowe2004sift,bay2006surf}, whereas BRIEF, BRISK, and FREAK 
+use the Hamming distance \cite{leutenegger2011brisk,calonder2010brief,alahi2012freak}.
+
+If we let $f_p$ and $f_b$ be the nearest and second nearest neighbor of a feature $f_q$, 
 the \emph{uniqueness ratio} is defined as follows:
 \begin{equation*}
-    r = d(f_q, f_p) / d(f_q, f_b)
+    r = d(f_q, f_p) / d(f_q, f_b).
 \end{equation*}
 Because $f_p$ is the nearest neighbor and $f_b$ the second nearest 
-neighbor we know that $d(f_q, f_p) \leq d(f_q, f_b)$ and since $d(f_i, 
-f_j) \geq 0, \forall f_i,f_j$, the uniqueness ratio is bounded by $0$ 
+neighbor, we know that $d(f_q, f_p) \leq d(f_q, f_b)$, and since $d(f_i, 
+f_j) \geq 0, \forall f_i,f_j$, the \emph{uniqueness ratio} is bounded by $0$ 
 and $1$, both inclusive. For the degenerate case where $d(f_q, f_b) = 0$
@@
 match in the \emph{query image} has only one match in a given 
-\emph{target image} or no matches at all. In both cases should expect 
-that the \emph{second} nearest neighbor in the target image to be an 
+\emph{target image} or no matches at all. In both cases we should expect 
+the \emph{second} nearest neighbor in the target image to be an 
 untrue correspondence.  This means we can use the distance between the 
@@
 false correspondences. By dividing the distance to the nearest neighbor 
-with this baseline we get an estimated measure for how distinct the 
+with this baseline, we get an estimated measure for how distinct the 
 correspondence is from a false match.
@@
 nomenclature:
-
 \begin{itemize}
 \item{Let $f_q$ be any feature point in the \emph{query image} that we 
-    are currently trying to match}
+    are currently trying to match}.
 \item{Let $F$ be a set of features. $F_{target}$ for example is the set 
-    of features from the \emph{target image}}
+    of features from the \emph{target image}}.
 \item{Let $\tau \in [0 \ldots 1]$ be a threshold used to decide whether 
-    to keep a match or discard it. We keep a match only if is has a 
-\emph{uniqueness ratio} lower than $\tau$}
-\item{Let the \emph{proposed match} be the nearest neighbor of the query 
-    feature $f_q$ picked from a set of feature points that we will call 
-the \emph{proposal set} which does not contain the query feature itself}
-\item{Let the \emph{baseline match} be the nearest neighbor of the query 
-    feature $f_q$ picked from a set of feature points that we will call 
-the \emph{baseline set} which neither contains the \emph{proposed match} 
-nor the query feature}
+	to keep a match or discard it. We keep a match only if it has a 
+uniqueness ratio lower than $\tau$}.
+\item{Let the \emph{proposed match} be the nearest neighbor of $f_q$
+    picked from a set of feature points that we will call the 
+\emph{proposal set} which does not include $f_q$}.
+\item{Let the \emph{baseline match} be the nearest neighbor of $f_q$ 
+    picked from a set of feature points that we will call the 
+\emph{baseline set}, which neither contains the \emph{proposed match} nor 
+$f_q$}.
 \end{itemize}
 
-%
-\subsection{A framework of matching methods}
-%
-
-\begin{figure}[t]
+In the case of \emph{Ratio-Match} \cite{lowe2004sift}, the \emph{proposal 
+set} consists of all the feature points in the target image.  Similarly 
+the \emph{baseline set} consists of all the feature points in the target 
+image except the \emph{proposed} match. For \emph{Ratio-Match} this 
+practically means that given a feature $f_q$, the \emph{proposed match} 
+and the \emph{baseline match} are the two nearest neighbors in the set 
+of feature points in the \emph{target image}.
+
+Brown et al.\ \cite{brown2005multi} extend \emph{Ratio-Match} for the case of $n$ target 
+images by letting the baseline be the average of the distance to the 
+second nearest neighbors for all $n$ target images.  They write, ``\emph{[W]e can improve outlier rejection by using information from all of the images (rather 
+than just the two being matched). This improves the matching precision}''.  The idea of improving matching precision by expanding the 
+knowledge used to reject outliers is also the central tenet of the framework presented in this paper.
+
+%
+\subsection{Framework of Matching Methods}
+%
+
+\emph{Ratio-Match} is only one instance of a framework of six algorithms we can 
+construct by different combinations of \emph{proposed} and 
+\emph{baseline sets}. As shown in Table~\ref{table:distinctness} for the 
+case of two images, the \emph{proposal set} can be constructed by either 
+looking only at the nearest neighbors in the target image, or 
+alternatively by looking at the nearest neighbors in both the query and 
+target image. The \emph{baseline set} can either be the query image 
+itself, the target image, or the combination of the two.  Seen in this 
+light, the matching algorithm \emph{Ratio-Match} draws both its 
+\emph{proposal set} and \emph{baseline set} from the target image. In 
+turn \emph{Mirror-Match-Ext} as introduced by the authors in 
+\cite{arnfred2013mirror}, works by constructing the \emph{proposal set} 
+and \emph{baseline set} by combining features from both the \emph{query} 
+and \emph{target image}. Alternatively \emph{Self-Match} looks only to 
+the query image for the \emph{baseline set} but constructs the 
+\emph{proposal set} from the target image like \emph{Ratio-Match}. In 
+Figure~\ref{fig:overview} we illustrate how each method is derived.
+
+\begin{table}[htb]
+\caption{Classification of the methods of the proposed framework based on the feature sources for 
+    \emph{proposal set} and \emph{baseline set} for calculating the \emph{uniqueness ratio}.}
+\label{table:distinctness}
+	\centering
+\bgroup
+\def\arraystretch{1.5}
+    \begin{tabular}{l l | l l}
+        %
+        %&  \multicolumn{1}{l}{Target}
+        %& \multicolumn{1}{l}{Target and Query} \\
+\multicolumn{2}{r}{} & \multicolumn{2}{c}{\emph{Proposal Set}} \\
+                     & & Target & Target and Query \\
+        \cline{2-4}
+        \multirow{3}{*}{\rotatebox[origin=c]{90}{\emph{Baseline Set}}} &
+  Query            & \emph{Self-Match}   & \emph{Self-Match-Ext} \\
+& Target           & \emph{Ratio-Match}   & \emph{Ratio-Match-Ext} \\
+& Target and Query & \emph{Mirror-Match} & \emph{Mirror-Match-Ext} \\
+        \cline{2-4}
+\end{tabular}
+\egroup
+\end{table}
+
+\begin{figure}[htb]
 \centering
 \includegraphics[width=0.85\columnwidth]{images/overview}
-\caption{Graphical representation of the \emph{Baseline} and 
-\emph{Proposal Set} for different methods in the proposed framework}
+\caption{Graphical representation of the \emph{baseline} and 
+\emph{proposal sets} for the methods in the proposed framework.}
 \label{fig:overview}
@@
 
-Given two images we can construct the proposal and baseline sets in six 
-different ways as illustrated in Figure~\ref{fig:overview}. In the case 
-of \emph{Ratio-Match} \cite{lowe2004sift} the \emph{proposal set} 
-consists of all the feature points in the target image.  Similarly the 
-\emph{baseline set} consists of all the feature points in the target 
-image except the \emph{proposed} match. For \emph{Ratio-Match} this 
-practically means that given a query feature, $f_q$, the \emph{proposed 
-match} and the \emph{baseline match} are the two nearest neighbors in 
-the set of feature points in the \emph{target image} and the ratio is 
-decided uniquely based on the \emph{target image}. In turn 
-\emph{Mirror-Match-Ext} as introduced by the authors in 
-\cite{arnfred2013mirror}, works by constructing the \emph{proposal set} 
-and \emph{baseline set} by combining features from both the \emph{query} 
-and \emph{target image}. By similar compositions of the \emph{proposal} 
-and \emph{baseline set} we derive four more algorithms as illustrated in 
-Figure~\ref{fig:overview}.
+Algorithm~\ref{alg-gen} shows the generalized matching framework, 
+where the \emph{proposal set} and \emph{baseline set} are defined 
+according to Table~\ref{table:distinctness}.  In practice for e.g.\ 
+\emph{Ratio-Match} we can obtain $f_p$ and $f_b$ by finding the two 
+nearest neighbors of $F_{target}$. The other algorithms can be optimized 
+similarly. Figure~\ref{fig:matching} illustrates the structure of 
+the generalized algorithm.
 
@@
     \State $F_{target} = get\_features(I_{target})$
-\State $F_{proposal-all} = get\_proposal\_features(F_{query}, 
-F_{target})$
-\State $F_{baseline-all} = get\_baseline\_features(F_{query}, 
-F_{target})$
+\State $F_{proposal} = get\_proposal\_set(F_{query}, F_{target})$
+\State $F_{baseline} = get\_baseline\_set(F_{query}, F_{target})$
 \State $M = \varnothing$
 \ForAll{$f_q \in F_{query}$}
-    \State $F_{proposal} = F_{proposal-all} \setminus 
-    \left\{f_q\right\}$
-    \State $F_{baseline} = F_{baseline-all} \setminus \left\{f_q, 
-    f_p\right\}$
-    \State $f_p \gets getNearestNeighbo\text{r}(f_q, F_{proposal})$
-    \State $f_b \gets getNearestNeighbo\text{r}(f_q, F_{baseline})$
+    \State $f_p \gets getNearestNeighbo\text{r}(f_q, F_{proposal} \setminus 
+    \left\{f_q\right\})$
+    \State $f_b \gets getNearestNeighbo\text{r}(f_q, F_{baseline} \setminus 
+    \left\{f_q, f_p\right\})$
     \State $ratio \gets distance(f_q, f_p) / distance(f_q, f_b)$
@@
 
-In algorithm~\ref{alg-gen} we show the generalized matching framework 
-where the \emph{proposal set} and \emph{baseline set} are defined 
-according to Figure~\ref{fig:overview}.  In practice for i.e.\ 
-\emph{Ratio-Match} we can obtain $f_p$ and $f_b$ by finding the 2 
-nearest neighbors of $F_{target}$. The other algorithms can be optimized 
-similarly. In Figure~\ref{fig:matching} we illustrate the structure of 
-this algorithm.
-
-For methods where the \emph{proposal set} includes the \emph{query 
-features} it is possible that the \emph{proposal match} is a feature 
-from the \emph{query image}, in which case we discard the match as an 
-untrue correspondence.  It also happens that we encounter 
-correspondences where the uniqueness ratio is more than $1$ in which 
-case we set it to $1$ to maintain a bounded \emph{uniqueness ratio}.  
-Take for example the case of \emph{Self-Match}. Using this method we 
-might find that the nearest neighbor of a feature in the target image is 
-further from the query feature than the nearest neighbor in the query 
-image. In this case the match is discarded.
-
-% TODO: include point about two of the algorithms being identical
-%
-\subsection{Generalized Uniqueness Ratio}
-%
-
-\begin{figure}[t]
+\begin{figure}[htb]
 \centering
 \includegraphics[width=0.9\columnwidth]{images/matching}
-\caption{Flow chart showing what happens when we match a feature. $\tau$ 
-is the ratio threshold and $d(x,y)$ is the distance between two feature 
-descriptors, $x$ and $y$.}
+\caption{Feature matching flow chart. $\tau$ 
+is the ratio threshold, and $d(x,y)$ is the distance between two feature 
+descriptors $x$ and $y$.}
 \label{fig:matching}
@@
 
-The main distinguishing factor in between the algorithms in the 
-framework is the final ratio between the distance of the two nearest 
-neighbors of a query feature which decides if we keep or discard a 
-match. We illustrate this process in Figure~\ref{fig:matching}.
-
-We can define a calculation of this ratio common to all algorithms in 
-the framework which allows us to compare the algorithms theoretically. 
-The theoretical ratio, $r$ is defined as follows:
-
-If $f_{p}$ is the nearest neighbor of $f_{q}$ in $F_{proposed}$ and 
-$f_{b}$ is the nearest neighbor of $f_{q}$ in $F_{baseline} \setminus 
-\left\{f_{p}\right\}$ then the generalized \emph{uniqueness} ratio is:
+For some methods it is possible that the \emph{proposal match} is a 
+feature from the \emph{query image}, in which case we discard the match 
+as an untrue correspondence.  It also happens that we encounter 
+correspondences with a \emph{uniqueness ratio} above $1$, in which case we set 
+it to $1$ to maintain a bounded \emph{uniqueness ratio}.  Take for example the 
+case of \emph{Self-Match}. Using this method we might find that the 
+nearest neighbor of a feature in the target image is further from the 
+query feature than the nearest neighbor in the query image. In this case 
+the match is discarded.
+
+\subsection{Generalized Uniqueness Ratio}
+
+Form $F_{query} = \left\{f_{q_1} \ldots f_{q_n}\right\}$ and $F_{target} 
+= \left\{f_{t_1} \ldots f_{t_m}\right\}$.  We can obtain $F_{proposed}$ 
+and $F_{baseline}$ from these sets depending on the algorithm used (see 
+Table~\ref{table:distinctness}). $r = \text{r}(f_{q}, F_{proposed}, 
+F_{baseline})$ is the ratio of query feature $f_{q}$ given 
+$F_{proposed}$ and $F_{baseline}$.  If $f_{p}$ is the nearest neighbor 
+of $f_{q}$ in $F_{proposed}$ and $f_{b}$ is the nearest neighbor of 
+$f_{q}$ in $F_{baseline} \setminus \left\{f_{p}\right\}$, then the 
+generalized \emph{uniqueness} ratio is:
 \begin{align*}
     r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
-        &= \frac{d(f_{q}, f_{p})}{d(f_{q}, f_{b})}
+        &= \frac{d(f_{q}, f_{p})}{d(f_{q}, f_{b})}.
 \end{align*}
-We let $K$ be the number of possible true correspondences \emph{query} 
-and \emph{target image}. The \emph{precision} and \emph{recall} are then 
+
+We let $K$ be the number of possible true correspondences between \emph{query} 
+and \emph{target image}. \emph{Precision} and \emph{recall} are 
 defined as:
@@
 \end{align*}
-Given $f_{nn} \in F_{target}$ defined as the nearest neighbor of any 
-$f_q \in F_{query}$ then we define the set of features $F_{true}$ as 
+Given $f_{nn} \in F_{target}$ as the nearest neighbor of any 
+$f_q \in F_{query}$, we define the set of features $F_{true}$ as 
 $\left\{ f_{q} \in F_{query} \mid f_{nn} \text{ is a true correspondence 
 of } f_{q} \right\}$ and $F_{false}$ as $F_{query} \setminus F_{true}$.  
-We can the define the number of correct and incorrect matches as 
+We can then define the number of correct and incorrect matches as 
 follows:
@@
 precision and recall of any method from the proposed framework is 
-uniquely identified by the uniqueness ratio $r$.  If for every query 
+uniquely identified by the \emph{uniqueness ratio} $r$.  If for every query 
 feature $f_{q}$, $r$ is identical across two matching methods, then they 
@@
 
-\subsection{Proofs of Ordering}
-
-Under three assumptions that largely reflects the performance of 
-matching feature points in practice we can theoretically compare the 
+\subsection{Proofs of Algorithm Performance}
+\label{S:Proofs}
+
+Under the following three assumptions, which largely reflect the performance of 
+matching feature points in practice, we can theoretically compare the 
 performance of the different algorithms shown in 
-Figure~\ref{fig:overview}.
-
+Table~\ref{table:distinctness}:
 \begin{enumerate}
@@
     target image and no real correspondences in the query image itself 
-as assumed by \emph{Ratio-Match}}
+as assumed by \emph{Ratio-Match}.}
     \item{We assume that distances of feature descriptors are well 
             behaved.  More precisely, given $f_q$, a feature from the 
-            \emph{query image} and $f_{match}$, the real correspondence 
+            \emph{query image}, and $f_{match}$, the real correspondence 
             from the set of features in the \emph{target image} 
-            $F_{target}$, we have that $\forall f_i \in F_{proposal}, 
-            f_i \neq f_{match}: d(f_q,f_{match}) < d(f_q, f_i)$}
+            $F_{target}$, we have $\forall f_i \in F_{proposal}, 
+            f_i \neq f_{match}: d(f_q,f_{match}) < d(f_q, f_i)$.}
     %\item{We assume that features within one image resemble each other 
@@
              correspondence in the \emph{target image}, we assume that 
-             the distribution of uniqueness ratios using $F_{target}$ as 
+             the distribution of \emph{uniqueness ratios} using $F_{target}$ as 
              the baseline set is similar to using $F_{query}$, since the 
@@
 
-Based on these assumptions we first prove that 
-The above proof can easily be extended to show that \emph{Mirror-Match 
-1} and \emph{Mirror-Match-Ext} returns the same correspondences too, and 
-both will be referred to as \emph{Mirror Match} from here on.
-
-For the case of \emph{Ratio-Match} and \emph{Ratio-Match-Ext} however we 
-can show that \emph{Ratio-Match-Ext} is equal or better than 
-\emph{Ratio-Match}.  Consider again the nearest neighbor $f_{nn}$ of a 
-query feature $f_{q}$ and the two cases where we either have the $f_{nn} 
-\in F_{query}$ or $f_{nn} \in F_{target}$. For $f_{nn} \in F_{target}$ 
-the uniqueness ratio of \emph{Ratio-Match-Ext} is:
+Based on these assumptions we first prove that the results of 
+\emph{Self-Match} are identical to \emph{Self-Match-Ext}. To do this, we 
+look at the nearest neighbor $f_{nn}$ of every query feature $f_{q}$ and 
+consider the two cases of $f_{nn} \in F_{query}$ and $f_{nn} \in
+F_{target}$. For $f_{nn} \in F_{target}$ the \emph{uniqueness ratio} of 
+\emph{Self-Match-Ext} is:
 \begin{align*}
@@
         &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
-        &= \text{r}(f_{q}, F_{target}, F_{baseline})
+        &= \text{r}(f_{q}, F_{target}, F_{baseline}).
 \end{align*}
-
+Since $F_{proposed} = F_{target}$ for \emph{Self-Match}, this shows that
+when the nearest neighbor is found in the target image, the two 
+algorithms behave identically. For $f_{nn} \in F_{query}$ 
+\emph{Self-Match} gives us the following ratio:
+\begin{align*}
+    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
+        &= \text{r}(f_{q}, F_{target}, F_{query}) \\
+        &\geq 1.
+\end{align*}
+The closest neighbor is found in the query image, so $d(f_{q}, f_{nn}) < 
+d(f_{q},f_{p})$, where $f_{p}$ is the nearest neighbor from 
+$F_{proposal}$. \emph{Self-Match-Ext} does not return a correspondence 
+found in the \emph{query image}, and since $\tau \in [0,1]$, neither does 
+\emph{Self-Match}. This proves that 
+\emph{Self-Match} returns the same matches as \emph{Self-Match-Ext} for any set of query features. For 
+this reason both algorithms will be referred to as just 
+\emph{Self-Match}.
+
+The above proof can easily be extended to show that \emph{Mirror-Match} and \emph{Mirror-Match-Ext} also return the same correspondences, and 
+both will be referred to as \emph{Mirror Match} from here on.
+
+For the case of \emph{Ratio-Match} and \emph{Ratio-Match-Ext}, we 
+can show that \emph{Ratio-Match-Ext} is equal or better than 
+\emph{Ratio-Match}.  Consider again the nearest neighbor $f_{nn}$ of a 
+query feature $f_{q}$, and the two cases where we either have $f_{nn} 
+\in F_{query}$ or $f_{nn} \in F_{target}$. For $f_{nn} \in F_{target}$ 
+the \emph{uniqueness ratio} of \emph{Ratio-Match-Ext} is:
+\begin{align*}
+    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
+        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
+        &= \text{r}(f_{q}, F_{target}, F_{baseline}).
+\end{align*}
 Since $F_{proposed} = F_{target}$ for \emph{Ratio-Match} this shows that
@@
     r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
-        &= \text{r}(f_{q}, F_{target}, F_{target})
+        &= \text{r}(f_{q}, F_{target}, F_{target}).
 \end{align*}
-
-Where as \emph{Ratio-Match-Ext} does not return the correspondence if 
+While \emph{Ratio-Match-Ext} does not return the correspondence if 
 the nearest neighbor of a query feature is in the \emph{query image}, 
-\emph{Ratio-Match} is likely to do so, since the uniqueness ratio is 
+\emph{Ratio-Match} is likely to do so, since the \emph{uniqueness ratio} is 
 found by dividing with the second nearest neighbor in the \emph{target 
-image}. This shows us that for cases where a query feature has a nearest 
+image}. This shows that for cases where a query feature has a nearest 
 neighbor in the \emph{query image}, \emph{Ratio-Match-Ext} is superior 
 to \emph{Ratio-Match}. Since query features with a nearest neighbor in 
-the \emph{query image} are false correspondences per assumption \#1 and 
+the \emph{query image} are false correspondences per assumptions \#1 and 
 \#2, this proves that \emph{Ratio-Match-Ext} has superior 
@@
 
-Finally we show that \emph{Mirror Match} is equal or better than 
+Finally we show that the accuracy of \emph{Mirror-Match} is equal to or better than 
 \emph{Ratio-Match-Ext}. Consider as before the nearest neighbor $f_{nn}$ 
 of a query feature $f_{q}$. When $f_{nn}$ resides in the \emph{query 
-image} both algorithms behave alike and discard the match.  However, 
-consider the uniqueness ratio of \emph{Mirror Match} for the case where 
+image}, both algorithms behave alike and discard the match.  However, 
+consider the \emph{uniqueness ratio} of \emph{Mirror Match} for the case where 
 $f_{nn}$ resides in the \emph{target image}:
@@
         &= max( \text{r}(f_{q}, F_{proposed}, F_{target}), 
-    \text{r}(f_{q}, F_{proposed}, F_{query}) )
+    \text{r}(f_{q}, F_{proposed}, F_{query}) ).
 \end{align*}
-
-For a true correspondence we have that the uniqueness ratio using 
-$F_{query}$ as baseline is distributed similarly to the ratio when using 
-$F_{target}$ by assumption \#3. In this case the algorithm performs like 
-\emph{Ratio-Match-Ext}.  However for an untrue correspondence with a 
+For a true correspondence the \emph{uniqueness ratio} using 
+$F_{query}$ as a baseline is distributed similarly to the ratio when using 
+$F_{target}$ according to assumption \#3. In this case the algorithm performs like 
+\emph{Ratio-Match-Ext}.  However, for an untrue correspondence with a 
 baseline match in the \emph{query image} which is closer than the
 baseline match in the \emph{target image}, \emph{Mirror Match} will 
-return a worse uniqueness ratio. This in turns means that \emph{Mirror 
+return a worse \emph{uniqueness ratio}. This in turns means that \emph{Mirror 
 Match} is equal or better than \emph{Ratio-Match-Ext} in terms of  
@@
 
-For any given recall we have proven based on assumption \#1-3 that the 
+We have thus proven that -- based on assumptions \#1-3 -- for any given recall rate, the 
 precision of the algorithms in the framework compares as follows:
@@
 
-The difference between \emph{Self-Match} and \emph{Ratio-Match} is is 
-the source of the \emph{baseline set}. For true correspondences we 
-assume that they should perform similarly but as for the rest the 
-performance of the two depends entirely on the images we are matching. 
-When we match images where the target image might not overlap at all 
+The difference between \emph{Self-Match} and \emph{Ratio-Match} is  
+the source of the \emph{baseline set}. For true correspondences 
+they should perform similarly, otherwise the 
+performance of the two depends entirely on the images being matched. 
+When we match images where the target image may not overlap at all 
 with the query image, using the query image and not the target image as 
@@
 
-\subsection{Discussion of assumptions}
+\subsection{Discussion of Assumptions}
 \label{ref:disc_assumptions}
@@
 %For a query feature, $f_q$ with a true correspondence in the 
-%\emph{target image}, we assume that the uniqueness ratio using 
-%$F_{target}$ is similar to the uniqueness ratio using $F_{query}$, 
+%\emph{target image}, we assume that the \emph{uniqueness ratio} using 
+%$F_{target}$ is similar to the \emph{uniqueness ratio} using $F_{query}$, 
 %since the two images in this case are guaranteed to share part of the 
@@
 
-The three assumptions proposed in order to formalize the order of the 
-algorithms have been chosen to reflect conditions under which we ideally
-would match feature points. However, for each assumption there exists 
-corner cases where it is no longer valid. In this section we intent to 
-discuss these corner cases in order to give an impression of the 
+The three assumptions underlying the formal ranking of 
+algorithms presented above have been chosen to reflect conditions under which we would ideally
+match feature points. However, for each assumption there exist 
+corner cases where it is no longer valid. In this section we 
+discuss these corner cases in order to review the 
 circumstances under which the absolute or relative performance of the 
@@
 The first assumption states that there is at most one unique match to 
-every feature point which is often the case when in e.g.\ stereo 
-matching with natural images. However for recognition of object classes 
-or in generated images with repetitive content this assumption is no 
-longer valid and using any assumption of uniqueness will lead to 
-incorrect results. However, as long as the query image does not contain 
-repetitive objects we can still use \emph{Self-Match} without loss of 
-precision even if the target image might not contain a unique match.
-
-According to the second assumption, feature descriptors behave such that
+every feature point, which is often the case for natural images. 
+However, for the recognition of object classes or in generated images 
+with repetitive content, a point in the \emph{query image} might have 
+several true correspondences in the \emph{target image}, so using a 
+\emph{baseline match} from the target image will lead to a much higher 
+\emph{uniqueness ratio}. However, as long as the query image does not 
+contain repetitive objects, we can still use \emph{Self-Match} without 
+loss of precision.
+
+According to the second assumption, feature descriptors should behave such that
 when matched, a true correspondence to a query feature will always be 
-the nearest neighbor. For actual feature detectors and descriptors 
-Mikolajczyk and Tuytelaars shows that this property depends strongly on 
-the differences between \emph{query} and \emph{target} image 
-\cite{mikolajczyk2005performance} \cite{tuytelaars2008local}. In the 
-degenerate case where the closest match is not an actual correspondence, 
-it is often the case that other matches are similarly close resulting in 
-a uniqueness ratio near 1, effectively filtering out bad 
-correspondences.  This means that with a lenient threshold close to 1, 
-the guarantees about precision and recall equivalence in between the 
-different ratio algorithms might no longer hold due to the lack of 
-consistent descriptor behaviour. It is worth pointing out that if this 
-assumption holds true, matching using only nearest neighbor is not 
-necessarily optimal unless there is a complete scene overlap between
+the nearest neighbor. For practical implementations of feature detectors and descriptors, 
+this property strongly depends on the differences between \emph{query} 
+and \emph{target image}, as shown in  
+\cite{mikolajczyk2005performance,tuytelaars2008local}. In the degenerate 
+case where the closest match is not an actual correspondence, there is 
+no reason why this match should be disproportionately closer to the 
+\emph{query feature} than any matches in the \emph{target image}, so in 
+most cases we would expect the \emph{uniqueness ratio} to be high 
+(signifying a bad match). This means that with a lenient threshold (close 
+to 1), the guarantees about precision and recall equivalence between the 
+different ratio algorithms might no longer hold due to the inconsistent descriptor behavior. 
+It is worth noting that if 
+assumption \#2 holds, matching using only nearest neighbor is not 
+necessarily optimal, unless there is a complete scene overlap between
 the images matched. For cases where there is little or no overlap, a 
 nearest neighbor would indiscriminately return false matches even with 
-well behaved feature descriptors.
-
-\begin{figure}[t]
+well-behaved feature descriptors.
+
+The third assumption states that the \emph{uniqueness ratios} using either the 
+\emph{query} or \emph{target image} as the baseline set would be similar
+in distribution given that the feature point we are matching has a true 
+correspondence. We can support this assumption by looking at the 
+\emph{uniqueness ratios} returned by \emph{Self-Match} and 
+\emph{Ratio-Match}, since they use the \emph{query} and 
+\emph{target image} respectively to calculate the \emph{uniqueness ratio}.  
+Figure~\ref{fig:ratio_hist} shows the actual \emph{uniqueness ratios} 
+measured from 3024 image pairs featuring 3D objects (see below for more on this dataset).  
+For ratios lower than $0.7$, the \emph{uniqueness ratios} are similar, but as we approach 
+more lenient thresholds, the ratios based on the \emph{query image} are 
+higher than those for the \emph{target image}. This means that the third assumption 
+is invalid for more lenient thresholds, and we can no longer expect \emph{Mirror-Match} to outperform 
+\emph{Ratio-Match-Ext} in terms of precision without a penalty in recall.
+
+\begin{figure}[htb]
 \centering
@@
 
-The last assumption states that the uniqueness ratio using either the 
-\emph{query} or \emph{target image} as the baseline set would be similar
-in distribution when we know that the feature point we are matching has 
-a true correspondence. For an ideal feature descriptor where any true 
-correspondence between two feature points will have a distance of $0$, 
-the third assumption is obviously true for any cases where the second 
-closest feature point has a true correspondence in the other image. In 
-the general case it is likely that the baseline yields different 
-uniqueness ratios depending on the features it contains, but for the 
-case where the baseline match has a true correspondence in the other 
-image we can verify the assumption by looking at the performance of 
-\emph{Self-Match} compared with \emph{Ratio-Match}. To compare we plot 
-the actual \emph{uniqueness ratios} measured from 84 3D objects in 
-Figure~\ref{fig:ratio_hist}. For ratios lower than $0.7$ this is 
-generally the case, but as we approach more lenient thresholds the 
-performance of \emph{Mirror-Match} might no longer be equal or better 
-than \emph{Ratio-Match-Ext} in terms of precision.
-% Needs rewording
-
 \section{Experiments and Results}
@@
 %
-\begin{figure}[htb]
-    \begin{subfigure}[t]{0.48\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{images/Frog_A}
-        \caption{Query Image}
-        \label{fig:frog_a}
-    \end{subfigure}%
-    \quad %add desired spacing between images, e. g. ~, \quad, \qquad a 
-    %blank line to force the subfigure onto a new line)
-    \begin{subfigure}[t]{0.48\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{images/Frog_B}
-        \caption{Auxiliary Image}
-        \label{fig:frog_b}
-    \end{subfigure}%
-    \\ %add desired spacing between images, e. g. ~, \quad, \qquad 
-    %a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[t]{0.48\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{images/Frog_C}
-        \caption{Target Image}
-        \label{fig:frog_c}
-    \end{subfigure}%
-    \quad %add desired spacing between images, e. g. ~, \quad, \qquad 
-    %blank line to force the subfigure onto a new line)
-    \begin{subfigure}[t]{0.48\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{images/Frog_C_lines}
-        \caption{Target Image with epipolar constraints}
-        \label{fig:frog_c_lines}
-    \end{subfigure}%
-    \caption{Creating epipolar constraints based on three source images.  
-        In a) the \emph{query image} has been marked with the position 
-        of the feature we are attempting to match. In b) the 
-        \emph{auxiliary image} is shown. This image is taken with the 
-        same rotation as the \emph{query image} but from a higher 
-        viewpoint. The line going through the image is the epipolar line 
-        of the feature point in the \emph{query image}.  The markers 
-        indicate all feature points in the image found near the epipolar 
-        line.  In c) we show the \emph{target image} which in this case 
-        is rotated 45 degrees from the \emph{query image}.  The line 
-        overlaid on the image represents the epipolar line corresponding 
-        to the feature point shown in the \emph{query image}.  The 
-        markers indicate all feature points in the image found near the 
-    epipolar line. In d) we show the \emph{target image} again, this 
-    time overlaid with the epipolar lines corresponding to all the 
-    features shown in the \emph{auxiliary image}. A true correspondence 
-    should be found within a small distance of one of the intersections 
-    of the line in c) and the lines in d). In this particular case both 
-    feature points shown in c) and d) could possible be a correct 
-    correspondence.
-}%
-    \label{fig:frog}%
-\end{figure}%
-In this section we will go over the experimental results comparing 
+In this section we present the experiments and evaluation results comparing 
 \emph{Self-Match}, \emph{Ratio-Match}, \emph{Ratio-Match-Ext} and 
-\emph{Mirror-Match}. We use two different image databases to compile 
-results over different variations.  To measure results on realistic and 
-variate non-planar images we test the algorithm on the 3D Objects 
+\emph{Mirror-Match}. We use two different databases to compile 
+results over different image variations.
+
+To measure results on realistic and 
+variate non-planar images, we test the algorithm on the 3D Objects 
 database released by Moreels and Pietro \cite{moreels2007evaluation} in 
-Section~\ref{S:3dobjects}. The database contains a set of 86 3D objects 
+Section~\ref{S:3dobjects}. This database contains a set of 86 3D objects 
 photographed from all sides at 5 degree intervals from two different 
-viewpoints and under three different lighting conditions.
-
-In the experiments we use the \emph{SIFT} descriptor and keypoint 
+elevation angles and under three different lighting conditions.
+To measure the performance over variations such as viewpoint change, 
+blur, compression noise, rotation, and zoom, we use the graffiti 
+image set introduced by Mikolajczyk and Schmid 
+\cite{mikolajczyk2005performance} in Section~\ref{S:Planar}.  This 
+dataset contains 8 scenes each with 6 images linked by homographies and 
+features only planar or almost planar scenes.
+
+For the experiments we use the \emph{SIFT} descriptor and keypoint 
 detector with default parameters as implemented in the OpenCV library 
-v.\ 2.4.6.  To test how the framework performs across descriptors we 
+2.4.6.  To further test how the framework performs across descriptors, we 
 evaluate SURF \cite{bay2006surf}, BRISK \cite{leutenegger2011brisk}, 
-BRIEF \cite{calonder2010brief} and FREAK \cite{alahi2012freak} in 
-Section~\ref{label:desc}. Across all experiments images larger than 
-1024x768 have been resized to fit within those dimensions using 
-Imagemagick with default parameters and only the luminance channel has 
-been used in the feature detection and description stage.
-
-\subsection{Experiments on 3D objects}
+BRIEF \cite{calonder2010brief}, and FREAK \cite{alahi2012freak} in 
+Section~\ref{label:desc}.
+
+Across all experiments, only the luminance channel is used in the feature detection and description stage.  
+Images larger than $1024\!\times\!768$ are resized to fit within those dimensions using 
+ImageMagick with default parameters.
+
+\subsection{Experiments on 3D Objects}
 \label{S:3dobjects}
 
-\begin{figure}[t]
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/1}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/2}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/3}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/4}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/5}
-    \end{subfigure}%
-    \vspace{1.5 mm}
-
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/6}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/7}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/8}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/9}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/10}
-    \end{subfigure}%
-    \vspace{1.5 mm}
-
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/11}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/12}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/13}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/14}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/3d/15}
-    \end{subfigure}%
-    \vspace{1.5 mm}
-
-    \caption{The first 15 objects from the 3D objects dataset by Moreels
-    and Pietro \cite{moreels2007evaluation}}
-    \label{fig:3d_objects}
-\end{figure}
-
-\begin{figure*}[ht]
+\begin{figure*}[t]
 	\centering
     \includegraphics[width=2\columnwidth]{images/results_all_objects}
-    \caption{Accumulated results from the 3D objects dataset. Each plot 
+    \caption{Results for the 3D objects dataset. Each plot 
     contains data accumulated from 84 objects photographed under 3 
@@
 
-The 3D objects dataset allows us to experimentally comparing matching 
+The 3D objects dataset by Moreels and Pietro \cite{moreels2007evaluation} allows us to experimentally compare matching 
 algorithms over a large range of object and surface types rotated on a 
-turnstile and photographed from every 5 degree turn. We used images of 
+turnstile and photographed from every 5 degree turn.  15 objects from the dataset are shown in Figure~\ref{fig:3d_objects}.  We use images of 
 84 different objects under three different lighting conditions at 12 
-different angle intervals conducting experiments with a total of 3024 
-image pairs.  To validate matches, Moreels and Pietro propose a method 
-to that will validate a match as a true or false correspondence using 
-epipolar constraints \cite[p.  266]{moreels2007evaluation}.  Their 
-method is outlined in Figure~\ref{fig:frog}.  According to their 
-experiments these constraints are sufficient to reduce the error rate 
-recognizing true correspondences to $2\%$. We have used their proposed 
-method to evaluate the precision and recall of the framework methods.
-
-To compute the total number of possible correspondences we took each 
-feature in a \emph{query image} and counted how many of them had a 
+different angle intervals, conducting experiments with a total of 3024 
+image pairs.
+
+\begin{figure}[htb]
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/1}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/2}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/3}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/4}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/5}
+    \end{subfigure}%
+    \vspace{1.5 mm}
+
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/6}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/7}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/8}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/9}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/10}
+    \end{subfigure}%
+    \vspace{1.5 mm}
+
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/11}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/12}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/13}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/14}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.19\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/3d/15}
+    \end{subfigure}%
+    \vspace{1.5 mm}
+
+    \caption{15 objects from the 3D Objects dataset by Moreels
+    and Pietro \cite{moreels2007evaluation}.}
+    \label{fig:3d_objects}
+\end{figure}
+
+To validate matches, Moreels and Pietro propose a method 
+using epipolar constraints \cite[p.266]{moreels2007evaluation}, which is 
+outlined in Figure~\ref{fig:frog}.  According to their 
+experiments, these constraints are able to identify 
+true correspondences with an error rate of $2\%$. We use their proposed 
+method to generate the ground truth for the evaluation of our framework.
+
+\begin{figure}[htb]
+    \begin{subfigure}[t]{0.48\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{images/Frog_A}
+        \caption{Query Image}
+        \label{fig:frog_a}
+    \end{subfigure}%
+    \quad %add desired spacing between images, e. g. ~, \quad, \qquad a 
+    %blank line to force the subfigure onto a new line)
+    \begin{subfigure}[t]{0.48\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{images/Frog_B}
+        \caption{Auxiliary Image}
+        \label{fig:frog_b}
+    \end{subfigure}%
+    \\ %add desired spacing between images, e. g. ~, \quad, \qquad 
+    %a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[t]{0.48\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{images/Frog_C}
+        \caption{Target Image}
+        \label{fig:frog_c}
+    \end{subfigure}%
+    \quad %add desired spacing between images, e. g. ~, \quad, \qquad 
+    %blank line to force the subfigure onto a new line)
+    \begin{subfigure}[t]{0.48\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{images/Frog_C_lines}
+        \caption{Target Image with epipolar constraints}
+        \label{fig:frog_c_lines}
+    \end{subfigure}%
+    \caption{Creating epipolar constraints based on three source images \cite{moreels2007evaluation}.  
+        (a) \emph{Query image} marked with the position 
+        of the feature we are attempting to match. (b) 
+        Auxiliary image, taken at the 
+        same rotation as the \emph{query image} but from a higher 
+        viewpoint. Feature points near the epipolar line 
+        of the feature point from the \emph{query image} are shown as dots.
+				(c) Sample \emph{target image} with feature points near the epipolar line of the feature point from the \emph{query image}.
+				(d) Same \emph{target image} with epipolar lines from all the 
+    feature points shown in the \emph{auxiliary image}. 
+		True correspondences should lie close to the intersections 
+    of the epipolar line from (c) with the lines from (d). In this particular case two 
+    feature points are possible correspondences.
+}%
+    \label{fig:frog}%
+\end{figure}%
+
+To compute the total number of possible correspondences, we take each 
+feature in a \emph{query image} and count how many of them have a 
 feature in the \emph{target image} which would satisfy the epipolar 
-constraints outlined above. In the experiments on 3D objects features 
-with no correspondences were not included in the set of features used to 
-test the matching algorithms to avoid matching non-moving background and 
+constraints outlined above. When using this dataset, features 
+with no correspondences were not included in the set of features for testing, 
+so as to avoid matching non-moving background and 
 foreground objects.
 
-We evaluated the 4 matching algorithms on the 3D objects dataset by 
+We evaluate all matching algorithms from our framework on the 3D objects dataset by 
 matching images at different angular intervals. For each object we 
-picked the \emph{query} image as the image taken at 10 degrees rotation 
-for calibration stability.  We then proceeded to match this image with 
-the same object turned an additional $d$ degrees, $d \in \{5, 10, 
-\ldots, 60\}$.  For every angle interval we compaired images taken under 
+pick the \emph{query} image as the image taken at 10 degrees rotation 
+for calibration stability.  We then match this image with 
+the same object turned an additional $\Delta$ degrees, $\Delta \in \{5, 10, 
+\ldots, 60\}$.  For every angle interval we compare images taken under 
 3 different lighting conditions as provided by the dataset.
-We included all objects in the database for which photos at 5 degree 
-angle intervals were available except for the ``Rooster'' and ``Sponge'' 
+We include all objects in the database for which photos at 5 degree 
+angle intervals are available except for the ``Rooster'' and ``Sponge'' 
 objects due to image irregularities. For each plot we show the 
-accumulated results on all 3D objects, weighed by the number of possible 
+accumulated results on all 3D objects, weighted by the number of possible 
 true correspondences for the particular object. This ensures that each 
-object contributes equally to the final result despite some objects
+object contributes equally to the final result, despite some objects
 resulting in disproportionally more matches than others.
 
-The results can be seen in Figure~\ref{fig:all_objects}. In the figure 
-we see the performance of the different matching methods in our proposed
-framework for $12$ increasingly bigger rotations. The results are shown 
+Figure~\ref{fig:all_objects} shows the performance of the different matching methods in our proposed
+framework for $12$ increasingly bigger angle differences. The results are shown 
 in a precision / recall plot to make it easy to compare performance in 
-terms of precision at similar levels of recall.
-
-For objects in the top row rotated between $5$ and $20$ degrees we see a 
-gradual increase in the performance gap between the methods as the angle 
-increases.  \emph{Ratio-Match} and \emph{Self-Match} show similar 
-results while \emph{Mirror-Match} and \emph{Ratio-Match-Ext} outperform 
-the them, showing the advantage of composing the \emph{proposed set} of 
-features from both images. \emph{Mirror-Match} show performance which is 
-consistently slightly better than \emph{Ratio-Match-Ext}. In general we 
+terms of precision at similar levels of recall.  \emph{Ratio-Match} and \emph{Self-Match} show similar 
+results, while \emph{Mirror-Match} and \emph{Ratio-Match-Ext} outperform 
+both of them, showing the advantage of composing the \emph{proposed set} of 
+features from both images. \emph{Mirror-Match} fares slightly but
+consistently better than \emph{Ratio-Match-Ext}. In general we 
 see the largest performance improvements at lower recall and a 
 convergence of precision at higher recall. This is expected since a 
-higher recall is a direct consequence of a more lenient threshold and as
-we let the threshold approach $1$ we lose the benefits of thresholding 
-on the \emph{uniqueness ratio} the methods all start approximating the 
-results of a simple nearest neighbor match. However for all but 
-\emph{Ratio-Match} the features with better matches within the same 
+higher recall is a direct consequence of a more lenient threshold; as
+we let the threshold approach $1$, we lose the benefits of thresholding 
+on the \emph{uniqueness ratio}, and all methods start approximating the 
+results of a simple nearest neighbor match. For all but 
+\emph{Ratio-Match}, the features with better matches within the same 
 image are still weeded out, which explains the tail end of 
 \emph{Ratio-Match} at high recall where the other algorithms no longer 
-have results. As we demonstrated in \cite{arnfred2013mirror} the removal 
+have results. As we demonstrated in \cite{arnfred2013mirror}, the removal 
 of within-image matches improves performance on image pairs with partial 
@@
 
-In the middle row featuring rotations of between $25$ and $40$ degrees 
-we see the strongest improvement of \emph{Mirror-Match} compared to 
-\emph{Ratio-Match} generally peaking at around
-a 20 percentage-point increase in precision. Finally the the performance
-gain decreases as we further increase the rotation to between $45$ and 
-$60$. We suspect that this is partly because assumption \#2 that a 
-descriptor is well behaved and match best with a descriptor of a true 
-correspondence stops being valid when the images are transformed beyond 
+The performance gap between methods increases gradually with angle, reaching its maximum between $25$ and $40$ degrees, 
+where \emph{Mirror-Match} exhibits about 20 percentage-points higher precision than \emph{Ratio-Match}. 
+At larger viewpoint differences above $45$ degrees, the performance gain decreases.  We suspect this is partly because assumption \#2 stops being valid when the images are transformed beyond 
 a certain level of recognizability.
@@
 with \emph{Mirror-Match} in general performing better than 
-\emph{Ratio-Match-Ext} which in turn was performing better than 
+\emph{Ratio-Match-Ext}, which in turn outperforms
 \emph{Ratio-Match}. The experimental results also show that 
-\emph{Self-Match} overall perform equal to or better than 
+\emph{Self-Match} overall performs equally well as or better than 
 \emph{Ratio-Match}.
 
-\subsection{Descriptor evaluation}
+\subsection{Planar Scenes}
+\label{S:Planar}
+
+\begin{figure*}[t!]
+	\centering
+    \includegraphics[width=2\columnwidth]{images/results_acr_all}
+    \caption{Accumulated results for each scene in the image dataset by 
+    Mikolajczyk and Schmid \cite{mikolajczyk2005performance}.}
+    \label{fig:acr_objects}
+\end{figure*}
+
+To evaluate local feature descriptors, Mikolajczyk and Schmid \cite{mikolajczyk2005performance} introduced
+a series of $8$ image sets featuring different transformations such as 
+compression noise, rotation and zoom, blur and viewpoint change. The 8 source scenes are shown in Figure~\ref{fig:acr_images}.  
+All  images are tied by homographies, which makes them convenient for testing 
+purposes, but as a consequence they all depict planar scenes, which is 
+somewhat limited and unrealistic. For each scene, there are 6 different 
+images with increasing levels of a certain transformation, such that 
+the change between image 1 and image 2 in a scene is only slight, while image 6 is markedly different from image 1 for most cases.
+
+\begin{figure}[htb]
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/bark}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/bikes}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/boat}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/graf}
+    \end{subfigure}%
+    \vspace{1.5 mm}
+    % Linebreak
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/leuven}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/trees}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/ubc}
+    \end{subfigure}%
+    ~ %
+    \begin{subfigure}[t]{0.24\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/acr/wall}
+    \end{subfigure}%
+    \caption{Scenes from the image dataset by Mikolajczyk and Schmid 
+    \cite{mikolajczyk2005performance}, ordered as they appear in 
+Figure~\ref{fig:acr_objects}.}
+    \label{fig:acr_images}
+\end{figure}
+
+We match the first image in each scene with images 3, 4, 5, 
+and 6 and show the accumulated result weighted by the possible number of 
+true correspondences for each pair. We exclude the comparison with image 
+2 because it is trivial in most cases and does not tell us much about 
+the relative performance of the different methods. We find inliers by 
+using the homography between image pairs as follows: Given a potential 
+match between two pixels $p_1$ and $p_2$, $m = \left(p_1, p_2\right)$, 
+and a homography $H$ relating the two images $I_1$ and $I_2$, we can 
+calculate if $m$ is an inlier by checking if the two points satisfy the 
+following criterion:
+\begin{equation*}
+\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max},
+\end{equation*}
+i.e.\ the distance between $p_1$ translated to $I_2$ and $p_2$ 
+\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
+less than a certain threshold (we use $d_{\max}=10$ pixels here).
+
+Figure~\ref{fig:acr_objects} shows the results plotted with precision on 
+the y-axis and recall along the x-axis. For scenes such as `bark', `boat' 
+(zoom and rotation), `leuven' (lighting changes) and `wall' (viewpoint changes), all methods 
+in the framework show similar results, largely because the precision approaches 100\% for low recall, which does not leave much room 
+for improvement. For `bikes' and `trees' (blur) as well as `ubc'
+(compression) and `graf' (viewpoint), \emph{Mirror-Match} clearly 
+outperforms \emph{Ratio-Match}, albeit with a smaller margin than 
+for the 3D objects dataset. Because many images in the dataset are 
+trivial to match and only a few are very difficult, there is less difference
+between the algorithms than with the 3D objects dataset. However, the 
+theoretical predictions are still confirmed, with \emph{Mirror-Match} 
+performing better than or equal to \emph{Ratio-Match-Ext}, which in turn 
+performs better than or equal to \emph{Ratio-Match}. \emph{Self-Match} 
+again achieves a performance comparable to \emph{Ratio-Match} using only the \emph{query image} as \emph{baseline 
+set}.
+
+\subsection{Descriptor Evaluation}
 \label{label:desc}
 
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=2\columnwidth]{images/results_descriptors_imageset1}
-    \caption{Keypoint / Descriptor combinations measured on 15 pairs of 
-    photos of 3D objects taken 15 degrees apart. K = Keypoint, D = 
-Descriptor.}
+\begin{figure*}[t!]
+    \begin{subfigure}[t]{1\textwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/results_descriptors_imageset1}
+		\caption{Keypoint / Descriptor combinations evaluated on 15 
+		pairs of photos of 3D objects taken 25 degrees apart.}
         \label{fig:descriptors}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{1\textwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{images/results_descriptors_easy}
+        \caption{Keypoint / Descriptor combinations evaluated on images 1 and 3 from the `Bikes' 
+        scene.}
+        \label{fig:descriptors_easy}
+    \end{subfigure}%
+    \caption{Evaluation of Keypoint / Descriptor combinations (K = Keypoint, D = 
+Descriptor).}
 \end{figure*}
 
-To evaluate whether the improvement gains shown with the SIFT descriptor 
-translates to other feature descriptors such as SURF \cite{bay2006surf} 
+To evaluate whether the improvement gains with the SIFT descriptor 
+translate to other feature descriptors such as SURF \cite{bay2006surf} 
 or binary features such as BRIEF \cite{calonder2010brief}, BRISK 
-\cite{leutenegger2011brisk} or FREAK \cite{alahi2012freak} we evaluated 
-the different descriptors on the 3D objects data set.  For the binary 
-features they were each paired with the FAST feature detector while SIFT 
-and SURF were tested with their respective feature detectors.  For each 
-keypoint detector and feature descriptor pair we used the standard 
-implementation from OpenCV 2.4.6.
+\cite{leutenegger2011brisk}, or FREAK \cite{alahi2012freak}, we evaluated 
+the different descriptors on the 3D objects data set.  The binary 
+features were each paired with the FAST feature detector for 
+consistency, while SIFT and SURF were tested with their respective 
+feature detectors.  For each keypoint detector and feature descriptor 
+pair we used the standard implementation from OpenCV 2.4.6.
 
@@
 with a fixed angle offset of 25 degrees (pictured in 
-Figure~\ref{fig:3d_objects}).  The evaluation was otherwise performed as
-in the general evaluation of 3D Objects, and the data presented is 
+Figure~\ref{fig:3d_objects}).  Otherwise the evaluation performed in the same manner as
+the general evaluation of 3D Objects in Section~ref{S:3dobjects}, and the data presented is 
 accumulated over the 15 objects, each set of results weighted by the 
-possible amount of correspondences.
-
-The results can be seen in Figure~\ref{fig:descriptors} and shows a 
-clear difference in the variance of matching method performance in 
-between SIFT and the rest of the descriptors. The performance of 
-\emph{Mirror-Match} using SIFT shows a clear increase in precision over 
-\emph{Ratio-Match} at equal recall levels. For other descriptors the 
-improvement is much less pronounced.  For the case of SURF, BRISK and 
-BRIEF we see a small improvement in precision using \emph{Mirror-Match} 
-over \emph{Ratio-Match} and \emph{Ratio-Match-ext} while FREAK yields 
-similar results no matter what algorithm is used. For all descriptors it 
-is the case that \emph{Self-Match} performs equally well to 
+possible number of correspondences.
+
+The results in Figure~\ref{fig:descriptors} are again in line with the theoretical performance analysis of Section~\ref{S:Proofs} .
+They also show a clear difference in the variance of matching method 
+performance between SIFT and the rest of the descriptors. The 
+performance of \emph{Mirror-Match} using SIFT shows a clear increase in 
+precision over \emph{Ratio-Match} at equal recall levels. For other 
+descriptors the improvement is much less pronounced.  For SURF, BRISK, 
+and BRIEF we see a small improvement in precision using 
+\emph{Mirror-Match} over \emph{Ratio-Match} and \emph{Ratio-Match-ext}, 
+whereas FREAK yields similar results no matter what algorithm is used.  
+For all descriptors \emph{Self-Match} performs on par with 
 \emph{Ratio-Match}.
 
-Part of the explanation behind this difference between SIFT and the 
-other descriptors can be found by looking at the recall rate in the case
-of for example SURF\@. Given the same amount of possible matches, 
-\emph{Ratio-Match} in the case of SURF spans a larger range of recall.  
+Part of this difference between SIFT and the 
+other descriptors can be explained by looking at the recall rate 
+with for example SURF\@. Given the same amount of possible matches, 
+\emph{Ratio-Match} with SURF spans a larger range of recall.  
 Since all other methods filter out matches that are better matched 
-within the same image but show no increase in precision, we can conclude 
+within the same image, but show no increase in precision, we can conclude 
 that correct matches are discarded because there are better matches 
 within the same image. This violates assumption \#2 stating that a 
-descriptor is well behaved and match best with a descriptor of a true 
-correspondence. This means that for this particular evaluation case SURF 
+descriptor is well behaved and matches best with a descriptor of a true 
+correspondence. This means that for this particular evaluation case, SURF 
 and the binary features tested are not sufficiently discriminative to 
@@
 
+To test this hypothesis we looked at the results from matching an image 
+pair with very little inter image variation. We compare images 1 and 
+image 3 from the `bikes' scene in the image set released by Mikolajczyk 
+and Schmid \cite{mikolajczyk2005performance}. The results 
+in Figure~\ref{fig:descriptors_easy} show a market improvement for 
+\emph{Self-Match}, \emph{Mirror-Match}, and \emph{Ratio-Match-Ext} over 
+\emph{Ratio-Match} for the case of BRISK, BRIEF, and FREAK as expected.  
+For SURF however, the algorithms perform similarly at low recall while 
+\emph{Ratio-Match} shows better performance at more lenient thresholds.
+
 \subsection{Performance}
 
-In terms of computational complexity the algorithms can be implemented 
+In terms of computational complexity, the algorithms can be implemented 
 in $O(n\log n)$, if we assume that both the \emph{query} and the 
-\emph{target} image has $n$ feature points. For a target image with $m$ 
-features where $m$ is significantly different from $n$ the complexities 
-are as noted in Table~\ref{table:running_times}. Note that 
-implementations refer to the algorithms as specified in 
-Table~\ref{table:distinctness}. In practice the constant factors 
+\emph{target} image have $n$ feature points. For a target image with $m$ 
+features where $m$ is significantly different from $n$, the complexities 
+are as noted in Table~\ref{table:running_times}. 
+In practice the constant factors 
 involved in the actual matching of two images with approximately the 
-same amount of feature points are usually small enough that all the 
-algorithms run at a similar speed. To illustrate 
-Table~\ref{table:running_times} contains the running times as measured 
+same number of feature points are usually small enough that all the 
+algorithms run at very similar speeds. This is also shown in 
+Table~\ref{table:running_times}, which contains the running times as measured 
 while matching 15 3D objects under three different lighting conditions 
@@
 \caption{Complexity and running times tested on 15 image pairs on 3 
-lighting conditions with average $n = 236.73$ and average $m = 247.38$ 
-as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
+lighting conditions with average $n = 236.7$ and average $m = 247.4$ feature points,
+as tested on an Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
 3.30~GHz with 8~GB memory.}
@@
     \emph{Self-Match} & $O(n\log(nm))$ & 118s  \\
-    %\emph{Self-Match-Ext} & $O(n\log(n(n+m)))$ & 109s\\
+    \emph{Self-Match-Ext} & $O(n\log(n(n+m)))$ & 109s\\
     \emph{Ratio-Match} & $O(n\log(m))$ & 114s\\
@@
     \emph{Mirror-Match} & $O(n\log(n(n+m)))$ & 116s\\
-    %\emph{Mirror-Match-Ext} & $O(n\log(n+m))$ & 110s \\
+    \emph{Mirror-Match-Ext} & $O(n\log(n+m))$ & 110s \\
     \hline
@@
 
-\subsection{Extending to multiple target images}
-%
-When we match a query image against multiple target images as seen in 
-for example image stitching, assumption \#1 that any feature in the 
-query image has at most 1 real correspondence in the set of target 
+\subsection{Extending to Multiple Target Images}
+%
+When we match a query image against multiple target images, as 
+for example in image stitching, assumption \#1 that any feature in the 
+query image has at most one real correspondence in the set of target 
 features is no longer true. It might be the case that two target images 
@@
 found in sets where there might be more than one correct 
-correspondences.
-
-Brown et al.\ \cite{brown2005multi} proposes calculating the uniqueness 
+correspondence.
+
+Brown et al.\ \cite{brown2005multi} propose calculating the uniqueness 
 ratio by taking the average of the $n$ nearest neighbors in each of the 
@@
 are aligned horizontally one after the other, this approach is not 
-flawed per se. However for the more general case of $n$ target images 
-with an unknown amount of overlaps in the target group, their approach 
-would not work since several features in the target group could possible 
+flawed per se. However for the more general case of $N$ target images 
+with an unknown amount of overlap in the target group, their approach 
+would not work since several features in the target group could possibly 
 be a correct correspondence.
@@
 This leaves us with two alternatives. Either we match the query image to 
-every target image individually or we use a matching strategy where the 
+every target image individually, or we use a matching strategy where the 
 \emph{baseline set} is guaranteed not to contain any real 
@@
 \emph{baseline set} of \emph{Self-Match} only contains features in the 
-query image itself. In addition, matching a query image to $n$ target 
+query image itself. In addition, matching a query image to $N$ target 
 images with \emph{Self-Match} is vastly faster than matching the query 
-image to every target image: If we for the sake of simplicity assume 
-that every of the $n$ images has $k$ features then matching the query 
-image to all $n$ images can be done in $O(nklog(k))$ using a metric 
-tree. However, matching with \emph{Self-Match} is done in $O(klog(nk)) =
-O(klog(n) + klog(k))$.
+image to every target image: If we assume 
+that every of the $N$ images has $n$ features, then matching the query 
+image to all $N$ images can be done in $O(Nn\log(n))$ using a metric 
+tree. However, matching with \emph{Self-Match} is done in $O(n\log(nN)) =
+O(n\log(N) + n\log(n))$.
 
@@
 
-We have proposed a framework of matching methods building on the ideas 
-behind \emph{Ratio-Match} and \emph{Mirror-Match} introducing the 
-variations \emph{Self-Match} and \emph{Ratio-Match-Ext}. We proved that 
-in terms of precision and recall \emph{Mirror-Match} performs better or 
-equal to \emph{Ratio-Match-Ext} which in turn performs better or equal 
-to \emph{Ratio-Match} under three common assumptions.
-
-From an evaluation using images of rotated 3D objects we have shown that
-the theoretical conclusions are reflected in experimental data with 
+We have proposed a general framework of matching methods; building on the ideas 
+behind \emph{Ratio-Match} and \emph{Mirror-Match}, we also introduced the 
+variations \emph{Self-Match} and \emph{Ratio-Match-Ext}.
+
+We formally proved under three assumptions that \emph{Mirror-Match} 
+performs better than or equal to \emph{Ratio-Match-Ext} in terms of 
+precision and recall, which in turn performs better than or equal to 
+\emph{Ratio-Match}.
+
+From an evaluation using images of rotated 3D objects, we have shown that
+the theoretical conclusions are reflected in the experimental results with 
 \emph{Mirror-Match} often outperforming \emph{Ratio-Match}
-significantly over 3024 image pairs. This performance gain comes free in 
-terms of both computational complexity as well as actual time 
-consumption as measured over 45 image pairs. Finally evaluations across 
-several different descriptors show that the gains in performance are 
-tied to descriptor performance with significantly smaller gains occuring 
-with descriptors that are less performant.
+significantly over 3024 image pairs. We further confirmed this behavior 
+for the classical `graffiti' image set, although there is less variation 
+between the algorithms. Finally we show that the theoretical conclusions 
+hold across a variety of popular feature descriptors (SIFT, SURF, BRISK, 
+BRIEF, and FREAK).  These performance gains 
+come free in terms of both computational complexity as well as actual 
+computing time.
 
@@
 applicable in situations where \emph{Ratio-Match} is currently used.  
-\emph{Self-Match} is on par with \emph{Ratio-Match} across all 
-evaluations but can be applied when matching multiple overlapping 
-images. \emph{Ratio-Match-Ext} and \emph{Mirror-Match} on the other hand 
-can easily replace \emph{Ratio-Match} without any performance penalty 
-and with an increase in precisionon but are both limited to matching 
-image pairs like \emph{Ratio-Match}.
-
-\appendix
-\section{Proof of equivalence between \emph{Self-Match} and 
-\emph{Self-Match-Ext}}
-In this appendix we prove the equivalence between \emph{Self-Match} and 
-\emph{Self-Match-Ext}. To do this, we look at the nearest neighbor 
-$f_{nn}$ of every query feature $f_{q}$ and consider the two cases of 
-$f_{nn} \in F_{query}$ and $f_{nn} \in
-F_{target}$. For $f_{nn} \in F_{target}$ the uniqueness ratio of 
-\emph{Self-Match-Ext} is:
-\begin{align*}
-    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
-        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
-        &= \text{r}(f_{q}, F_{target}, F_{baseline})
-\end{align*}
-
-Since $F_{proposed} = F_{target}$ for \emph{Self-Match} this shows that
-when the nearest neighbor is found in the target image, the two 
-algorithms behave identically. For $f_{nn} \in F_{query}$ we know that 
-the best match for the query feature is in the query image itself. Since 
-neither algorithm returns a correspondence within the same image, they 
-also behave identically for this case. This proves that for any set of 
-\emph{query features} \emph{Self-Match} returns the same matches as 
-\emph{Self-Match-Ext}.
-
-\section{Proof of equivalence between \emph{Mirror-Match} and 
-\emph{Mirror-Match-Ext}}
-
-In this appendix we prove the equivalence between \emph{Mirror-Match} 
-and \emph{Mirror-Match-Ext}. This proof is almost identical to the 
-equivalence proof between \emph{Self-Match} and \emph{Self-Match-Ext}. 
-To prove this, we look at the nearest neighbor $f_{nn}$ of every query 
-feature $f_{q}$ and consider the two cases of $f_{nn} \in F_{query}$ and 
-$f_{nn} \in
-F_{target}$. For $f_{nn} \in F_{target}$ the uniqueness ratio of 
-\emph{Mirror-Match-Ext} is:
-\begin{align*}
-    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
-        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
-        &= \text{r}(f_{q}, F_{target}, F_{baseline})
-\end{align*}
-
-Since $F_{proposed} = F_{target}$ for \emph{Mirror-Match} this shows that
-when the nearest neighbor is found in the target image, the two 
-algorithms behave identically. For $f_{nn} \in F_{query}$ we know that 
-the best match for the query feature is in the query image itself. Since 
-neither algorithm returns a correspondence within the same image, they 
-also behave identically for this case. This proves that for any set of 
-\emph{query features} \emph{Mirror-Match} returns the same matches as 
-\emph{Mirror-Match-Ext}.
-
+\emph{Ratio-Match-Ext} and \emph{Mirror-Match} 
+can readily and easily replace \emph{Ratio-Match} without any performance penalty 
+and with an increase in precision.  However, both are limited to matching 
+image pairs like \emph{Ratio-Match}. \emph{Self-Match} on the other hand is on par with \emph{Ratio-Match} across all 
+evaluations, but can be applied when matching multiple overlapping images.
+
+\balance
 \bibliographystyle{IEEEtran}
-\bibliography{tail/bibliography}
+\bibliography{bibliography}
 \end{document}

### 2014-04-16 text/journal/paper.tex
Modified paper to integrate stefan's changes

@@
 %\boldmath
-Computer vision applications that involve the matching of local image 
-features frequently use \emph{Ratio-Match} as introduced by Lowe and 
-others, but is this really the optimal approach?  We formalize the 
-theoretical foundation of \emph{Ratio-Match} and propose a general 
-framework encompassing \emph{Ratio-Match} and five other matching 
-methods. Using this framework, we establish a theoretical 
-performance ranking in terms of precision and recall, 
-proving that all five methods consistently outperform or equal \emph{Ratio-Match}.
-
-We confirm the theoretical results experimentally on over 3000 image 
-pairs and show that we can increase matching precision
-without further assumptions about the images we are using.  These gains 
-are achieved by making only a few key changes of the \emph{Ratio-Match} algorithm and do not increase computation times.
+Computer vision applications that involve the matching of local image features frequently use \emph{Ratio-Match} as introduced by Lowe and others, but is this really the optimal approach?
+We formalize the theoretical foundation of \emph{Ratio-Match} and propose a general framework encompassing \emph{Ratio-Match} and three other matching methods.
+Using this framework, we establish a theoretical performance ranking in terms of precision and recall, proving that all five methods consistently outperform or equal \emph{Ratio-Match}.
+
+We confirm the theoretical results experimentally on over 3000 image pairs and show that we can increase matching precision without further assumptions about the images we are using.
+These gains are achieved by making only a few key changes of the \emph{Ratio-Match} algorithm and do not increase computation times.
 \end{abstract}
@@
 %
-Matching image points is a crucial ingredient in almost all computer 
-vision algorithms that deal with sparse local image features. This 
-includes image categorization \cite{bosch2008scene}, image stitching 
-\cite{brown2007automatic}, object detection \cite{zhang2007local}, and 
-near duplicate detection \cite{zhao2009scale}, to mention just a few examples.  
-These problems all rely on being able to accurately find the 
-correspondence(s) of a point on an object in a \emph{query image} given 
-one or more \emph{target images} that might contain the same object.  In 
-many applications the target images have undergone transformations with 
-respect to the query image; in stereo vision, the viewpoint is 
-different, while in object recognition and near duplicate detection both 
-the lighting and even the object itself may also be transformed.
-
-In the literature two approaches to feature point matching have been 
-pursued and later merged. The geometric approach tries to find unique 
-keypoints in an image pair and match them based on their location.  The 
-descriptor centric approach on the other hand uses the local image 
-information around the keypoint to create a descriptor and matches 
-descriptors based on their similarity.
+Matching image points is a crucial ingredient in almost all computer vision algorithms that deal with sparse local image features.
+This includes image categorization \cite{bosch2008scene}, image stitching \cite{brown2007automatic}, object detection \cite{zhang2007local}, and near duplicate detection \cite{zhao2009scale}, to mention just a few examples.
+These problems all rely on being able to accurately find the correspondence(s) of a point on an object in a \emph{query image} given one or more \emph{target images} that might contain the same object.
+In many applications the target images have undergone transformations with respect to the query image; in stereo vision, the viewpoint is different, while in object recognition and near duplicate detection both the lighting and even the object itself may also be transformed.
+
+In the literature two approaches to feature point matching have been pursued and later merged.
+The geometric approach tries to find unique keypoints in an image pair and match them based on their location.
+The descriptor centric approach on the other hand uses the local image information around the keypoint to create a descriptor and matches descriptors based on their similarity.
 
 In the purely geometric approach, feature points are matched based on their position in the images.
-Scott and Longuet-Higgins 
-\cite{scott1991algorithm} and Shapiro and Brady 
-\cite{shapiro1992feature} introduced the use of spectral methods by 
-deriving a coherent set of matches from the eigenvalues of the 
-correspondence matrix. Other examples of this approach include \cite{sclaroff1995modal,carcassoni2003spectral}.
-
-The descriptor centric approach on the other hand finds matches by 
-pairing similar keypoints. The first 
-examples of this approach used the correlation of the raw image data 
-immediately surrounding the feature point \cite{deriche1994robust,baumberg2000reliable} to calculate this similarity. Later 
-algorithms were enhanced by invariant feature descriptors as first 
-introduced in \cite{schmid1997local} and later popularized by the work 
-of Lowe introducing SIFT \cite{lowe2004sift} and Bay et al.\ introducing SURF 
-\cite{bay2006surf}.
-
-Many descriptor variations have since been proposed, and a few surveys 
-have emerged comparing them. Mikolajczyk and Schmid \cite{mikolajczyk2005performance} evaluate 11 such 
-feature descriptors in a paper where they also introduce the graffiti 
-image set which has later become a common benchmark for image matching 
-algorithms.  Moreels and Perona \cite{moreels2007evaluation}
-evaluate 5 descriptors with different keypoint detectors using a large 
-image set consisting of 3D models. 
-Heinly et al.\ \cite{heinly2012comparative} take a closer look at binary features such as BRIEF 
-\cite{calonder2010brief}, BRISK \cite{leutenegger2011brisk}, and ORB 
-\cite{rublee2011orb}, comparing them to SIFT and SURF.
-
-A straightforward way to find a set of correspondences using only 
-feature points is to apply a threshold to the similarity measure of the feature 
-vectors, accepting only correspondences that score above a certain 
-level of similarity \cite{szeliski2010}. When we match images with the assumption 
-that the correspondence between two feature points will be unique, we can 
-further increase precision by only matching a feature point to its 
-nearest neighbor in terms of descriptor similarity. Instead of 
-thresholding based on similarity, Deriche et 
-al.~\cite{deriche1994robust} and Baumberg~\cite{baumberg2000reliable} 
-propose using the ratio of the similarity of the best to second best 
-correspondence of a given point to evaluate how unique it is. Their 
-finding has later been tested by several independent teams, all 
-concluding that thresholding based on this ratio is generally superior to 
-thresholding based on similarity \cite{lowe2004sift,mikolajczyk2005performance,moreels2007evaluation,rabin2009statistical}.
-
-Brown and Lowe \cite{brown2005multi} extend ratio match to deal 
-with a set of images by using not the ratio of the best and second best 
-correspondence, but the average ratio of the best and the average of 
-second best correspondences across a set of images.  Rabin et al.\ tries to enhance descriptor 
-matching by looking at the statistical distribution of local features in 
-the matched images, and only return a match when such a 
-correspondence would not occur by mere chance 
-\cite{rabin2009statistical}. Finally, a precursor of the algorithms 
-discussed in this paper was introduced by the authors as 
-\emph{Mirror-Match} \cite{arnfred2013mirror}, which makes use of the 
-feature points in both images to decide if a match is valid.
-
-A plethora of solutions have combined ratio match with various geometric 
-constraints to improve matching. These constraints are
-based on assumptions regarding the transformation between the query and 
-target images. At the stricter end we have epipolar constraints, assuming
-that the images can be tied by a homography \cite{torr2000mlesac,chum2005matching}, and angular constraints, assuming the 
-correspondences are angled similarly \cite{kim2008efficient,schmid1997local,leordeanu2005spectral}. 
-These constraints can be relaxed using more sophisticated models.  Torresani et al.\ \cite{torresani2008feature} 
-attempted to model transformations using graph matching similar to 
-\cite{deriche1994robust}. Others define image regions and reject or 
-accept correspondences based on the regions they connect 
-\cite{cho2009feature,wu2011robust}.
-
-Any matching method relying on geometric constraints is restrained by 
-inherent assumptions about the geometric relationship between the two 
-images. Broad assumptions such as the epipolar constraint only apply in 
-simple image transformations. For more complex transformations we need 
-models suitable for each particular case, which limits the algorithm 
-to the subset of images that fit the model.  In the case of object 
-recognition for example, the transformations from one scene to another 
-often feature a change in perspective, background, and sometimes variations within the object 
-itself: a person can change pose, a car model can have different 
-configurations, a flower can bloom etc.
-
-When matching these instances we are forced to either create a 
-sophisticated model that represents the variables of transformation 
-within the object, or alternatively find correspondences using an 
-algorithm with no inherent geometric assumptions. Besides, 
-any geometric method acts as a filter on a given set of 
-correspondences.  Therefore, if the initial set of purely descriptor-based matches contains fewer incorrect correspondences, 
-the final set can be calculated faster and more accurately.
-
-The methods we propose in this paper are designed to be free from 
-assumptions about image geometry. They extend and improve on Lowe's 
-\emph{Ratio-Match} \cite{lowe2004sift} and the authors' \emph{Mirror 
-Match} \cite{arnfred2013mirror} by generalizing both algorithms to a 
-framework of matching methods. We go on to formally establish a ranking
-based on how well different methods within the framework compare in 
-terms of precision and recall. Our experimental evaluations confirm the 
-theoretical results and show that \emph{Ratio-Match} on all counts is generally a 
-sub-optimal choice as a matching algorithm.
-
-The paper is organized as follows. In Section~\ref{S:MatchingMethods} we 
-introduce the original \emph{Ratio-Match}, generalize this method to 
-introduce the proposed framework, and compare the methods of the 
-framework theoretically.  In Section~\ref{S:Experiments} we present 
-our experimental validation and discuss the results obtained.  Section~\ref{S:Summary} 
-concludes the paper.
+Scott and Longuet-Higgins \cite{scott1991algorithm} and Shapiro and Brady \cite{shapiro1992feature} introduced the use of spectral methods by deriving a coherent set of matches from the eigenvalues of the correspondence matrix.
+Other examples of this approach include \cite{sclaroff1995modal,carcassoni2003spectral}.
+
+The descriptor centric approach on the other hand finds matches by pairing similar keypoints.
+The first examples of this approach used the correlation of the raw image data immediately surrounding the feature point \cite{deriche1994robust,baumberg2000reliable} to calculate this similarity.
+Later algorithms were enhanced by invariant feature descriptors as first introduced in \cite{schmid1997local} and later popularized by the work of Lowe introducing SIFT \cite{lowe2004sift} and Bay et al.\ introducing SURF \cite{bay2006surf}.
+
+Many descriptor variations have since been proposed, and a few surveys have emerged comparing them.
+Mikolajczyk and Schmid \cite{mikolajczyk2005performance} evaluate 11 such feature descriptors in a paper where they also introduce the graffiti image set which has later become a common benchmark for image matching algorithms.
+Moreels and Perona \cite{moreels2007evaluation} evaluate 5 descriptors with different keypoint detectors using a large image set consisting of 3D models.
+Heinly et al.\ \cite{heinly2012comparative} take a closer look at binary features such as BRIEF \cite{calonder2010brief}, BRISK \cite{leutenegger2011brisk}, and ORB \cite{rublee2011orb}, comparing them to SIFT and SURF.
+
+A straightforward way to find a set of correspondences using only feature points is to apply a threshold to the similarity measure of the feature vectors, accepting only correspondences that score above a certain level of similarity \cite{szeliski2010}.
+When we match images with the assumption that the correspondence between two feature points will be unique, we can further increase precision by only matching a feature point to its nearest neighbor in terms of descriptor similarity.
+Instead of thresholding based on similarity, Deriche et al.~\cite{deriche1994robust} and Baumberg~\cite{baumberg2000reliable} propose using the ratio of the similarity of the best to second best correspondence of a given point to evaluate how unique it is.
+Their finding has later been tested by several independent teams, all concluding that thresholding based on this ratio is generally superior to thresholding based on similarity \cite{lowe2004sift,mikolajczyk2005performance,moreels2007evaluation,rabin2009statistical}.
+
+Brown and Lowe \cite{brown2005multi} extend ratio match to deal with a set of images by using not the ratio of the best and second best correspondence, but the average ratio of the best and the average of second best correspondences across a set of images.
+Rabin et al.\ tries to enhance descriptor matching by looking at the statistical distribution of local features in the matched images, and only return a match when such a correspondence would not occur by mere chance \cite{rabin2009statistical}.
+Finally, a precursor of the algorithms discussed in this paper was introduced by the authors as \emph{Mirror-Match} \cite{arnfred2013mirror}, which makes use of the feature points in both images to decide if a match is valid.
+
+A plethora of solutions have combined ratio match with various geometric constraints to improve matching.
+These constraints are based on assumptions regarding the transformation between the query and target images.
+At the stricter end we have epipolar constraints assuming that the images can be tied by a homography \cite{torr2000mlesac, chum2005matching} and angular constraints assuming the correspondences are angled similarly \cite{kim2008efficient, schmid1997local}.
+Often these approaches are made computationally feasible by modelling the case of feature correspondences as an instance of graph matching where each feature is a vertex and edge values correspond to a geometric relation between two features.
+In this case approximate graph matching algorithms can be used to efficiently establish an isomorphism between the graph of features in two images \cite{leordeanu2005spectral, torresani2008feature, yarkony2010covering}.
+Finally others define image regions and reject or accept correspondences based on the regions they connect \cite{cho2009feature, wu2011robust}.
+
+Any matching method relying on geometric constraints is restrained by inherent assumptions about the geometric relationship between the two images.
+Broad assumptions such as the epipolar constraint only apply in simple image transformations.
+For more complex transformations we need models suitable for each particular case, which limits the algorithm to the subset of images that fit the model.
+In the case of object recognition for example, the transformations from one scene to another often feature a change in perspective, background, and sometimes variations within the object itself: a person can change pose, a car model can have different configurations, a flower can bloom etc.
+
+When matching these instances we are forced to either create a sophisticated model that represents the variables of transformation within the object, or alternatively find correspondences using an algorithm with no inherent geometric assumptions.
+Besides, any geometric method acts as a filter on a given set of correspondences.
+Therefore, if the initial set of purely descriptor-based matches contains fewer incorrect correspondences, the final set can be calculated faster and more accurately.
+
+The methods we propose in this paper are designed to be free from assumptions about image geometry.
+They extend and improve on Lowe's \emph{Ratio-Match} \cite{lowe2004sift} and the authors' \emph{Mirror Match} \cite{arnfred2013mirror} by generalizing both algorithms to a framework of matching methods.
+We go on to formally establish a ranking based on how well different methods within the framework compare in terms of precision and recall.
+Our experimental evaluations confirm the theoretical results and show that \emph{Ratio-Match} on all counts is generally a sub-optimal choice as a matching algorithm.
+
+In the author's last paper we introduced \emph{Mirror-Match} and \emph{Mirror-Match with Clustering}, two algorithms that we showed to perform better than the state of the art.
+The novel contributions of this paper consists of two new algorithms completing a framework of four related matching algorithms as well as the theoretical foundation which enables us to understand why \emph{Mirror-Match} performs better than \emph{Ratio Match} in the first place.
+
+The paper is organized as follows.
+I section~\ref{S:MatchingMethods} we introduce the original \emph{Ratio-Match}, extend on this method to introduce the proposed framework and go on to compare the members of the framework theoretically.
+In section~\ref{S:Experiments} we present evaluations and discuss the results obtained.
+Section~\ref{S:Summary} concludes the paper.
 
@@
 %
-\subsection{Ratio-Match}
-%
-\emph{Ratio-Match} as introduced by Deriche et al.\ 
-\cite{deriche1994robust} and later used by 
-Baumberg~\cite{baumberg2000reliable} and Lowe~\cite{lowe2004sift} makes 
-use of a \emph{uniqueness ratio}. For each feature in the \emph{query 
-image}, it finds a possible match by identifying the nearest neighbor and 
-returning this match only if the \emph{uniqueness ratio} is above a 
-given threshold $\tau$.
-
-Given $f_q$, a feature from the \emph{query 
-image} and $F_{target}$, a set of features from the \emph{target image}, 
-the nearest neighbor of $f_q$ in $F_{target}$ is:
-\begin{equation*}
-    f_{nn} = \argmin_{f_t \in F_{target}} d(f_q, f_t).
-\end{equation*}
-Here, $d(f_i, f_j)$ is the distance between feature descriptors.  
-With SIFT and SURF this is the Euclidean distance of the feature vectors
-\cite{lowe2004sift,bay2006surf}, whereas BRIEF, BRISK, and FREAK 
-use the Hamming distance \cite{leutenegger2011brisk,calonder2010brief,alahi2012freak}.
-
-If we let $f_p$ and $f_b$ be the nearest and second nearest neighbor of a feature $f_q$, 
-the \emph{uniqueness ratio} is defined as follows:
-\begin{equation*}
-    r = d(f_q, f_p) / d(f_q, f_b).
-\end{equation*}
-Because $f_p$ is the nearest neighbor and $f_b$ the second nearest 
-neighbor, we know that $d(f_q, f_p) \leq d(f_q, f_b)$, and since $d(f_i, 
-f_j) \geq 0, \forall f_i,f_j$, the \emph{uniqueness ratio} is bounded by $0$ 
-and $1$, both inclusive. For the degenerate case where $d(f_q, f_b) = 0$
-we let the \emph{uniqueness ratio} be $0$.
-
-The underlying assumption in ratio match is that the point we seek to 
-match in the \emph{query image} has only one match in a given 
-\emph{target image} or no matches at all. In both cases we should expect 
-the \emph{second} nearest neighbor in the target image to be an 
-untrue correspondence.  This means we can use the distance between the 
-feature point and the second closest descriptor as a \emph{baseline} for 
-false correspondences. By dividing the distance to the nearest neighbor 
-with this baseline, we get an estimated measure for how distinct the 
-correspondence is from a false match.
-
-To make further discussion easier we introduce the following 
-nomenclature:
+\subsection{Definitions}
+%
+The proposed framework is inspired by \emph{Ratio-Match} as introduced by Deriche et al.\ \cite{deriche1994robust} and later used by Baumberg~\cite{baumberg2000reliable} and Lowe~\cite{lowe2004sift}.
+\emph{Ratio-Match} makes use of a \emph{uniqueness ratio} as a heuristic for finding correspondences between feature points.
+For each feature in the \emph{query image}, it finds a possible match by identifying the nearest and second nearest neighbor and returns this match only if the ratio between the distance of the nearest and second nearest neighbor is above a given threshold $\tau$.
+
+The underlying assumption in ratio match is that the point we seek to match in the \emph{query image} has only one match in a given \emph{target image} or no matches at all.
+In both cases we should expect the \emph{second} nearest neighbor in the target image to be an untrue correspondence.
+This means that we can use the distance between the feature point and the second closest descriptor as a \emph{baseline} for false correspondences.
+By dividing the distance to the nearest neighbor with this baseline, we get an estimated measure for how distinct the correspondence is from a false match.
+
+To make further discussion easier we introduce the following nomenclature:
 \begin{itemize}
@@
 \item{Let $\tau \in [0 \ldots 1]$ be a threshold used to decide whether 
-	to keep a match or discard it. We keep a match only if it has a 
-uniqueness ratio lower than $\tau$}.
-\item{Let the \emph{proposed match} be the nearest neighbor of $f_q$
-    picked from a set of feature points that we will call the 
-\emph{proposal set} which does not include $f_q$}.
-\item{Let the \emph{baseline match} be the nearest neighbor of $f_q$ 
-    picked from a set of feature points that we will call the 
-\emph{baseline set}, which neither contains the \emph{proposed match} nor 
-$f_q$}.
+    to keep a match or discard it. We keep a match only if is has a 
+\emph{uniqueness ratio} lower than $\tau$}
+\item{Let the \emph{proposed match} be the nearest neighbor of the query 
+    feature $f_q$ picked from a set of feature points that we will call 
+the \emph{proposal set} which does not contain the query feature itself}
+\item{Let the \emph{baseline match} be the nearest neighbor of the query 
+    feature $f_q$ picked from a set of feature points that we will call 
+the \emph{baseline set} which neither contains the \emph{proposed match} 
+nor the query feature}
 \end{itemize}
 
-In the case of \emph{Ratio-Match} \cite{lowe2004sift}, the \emph{proposal 
-set} consists of all the feature points in the target image.  Similarly 
-the \emph{baseline set} consists of all the feature points in the target 
-image except the \emph{proposed} match. For \emph{Ratio-Match} this 
-practically means that given a feature $f_q$, the \emph{proposed match} 
-and the \emph{baseline match} are the two nearest neighbors in the set 
-of feature points in the \emph{target image}.
-
-Brown et al.\ \cite{brown2005multi} extend \emph{Ratio-Match} for the case of $n$ target 
-images by letting the baseline be the average of the distance to the 
-second nearest neighbors for all $n$ target images.  They write, ``\emph{[W]e can improve outlier rejection by using information from all of the images (rather 
-than just the two being matched). This improves the matching precision}''.  The idea of improving matching precision by expanding the 
-knowledge used to reject outliers is also the central tenet of the framework presented in this paper.
-
-%
-\subsection{Framework of Matching Methods}
-%
-
-\emph{Ratio-Match} is only one instance of a framework of six algorithms we can 
-construct by different combinations of \emph{proposed} and 
-\emph{baseline sets}. As shown in Table~\ref{table:distinctness} for the 
-case of two images, the \emph{proposal set} can be constructed by either 
-looking only at the nearest neighbors in the target image, or 
-alternatively by looking at the nearest neighbors in both the query and 
-target image. The \emph{baseline set} can either be the query image 
-itself, the target image, or the combination of the two.  Seen in this 
-light, the matching algorithm \emph{Ratio-Match} draws both its 
-\emph{proposal set} and \emph{baseline set} from the target image. In 
-turn \emph{Mirror-Match-Ext} as introduced by the authors in 
-\cite{arnfred2013mirror}, works by constructing the \emph{proposal set} 
-and \emph{baseline set} by combining features from both the \emph{query} 
-and \emph{target image}. Alternatively \emph{Self-Match} looks only to 
-the query image for the \emph{baseline set} but constructs the 
-\emph{proposal set} from the target image like \emph{Ratio-Match}. In 
-Figure~\ref{fig:overview} we illustrate how each method is derived.
-
-\begin{table}[htb]
-\caption{Classification of the methods of the proposed framework based on the feature sources for 
-    \emph{proposal set} and \emph{baseline set} for calculating the \emph{uniqueness ratio}.}
-\label{table:distinctness}
-	\centering
-\bgroup
-\def\arraystretch{1.5}
-    \begin{tabular}{l l | l l}
-        %
-        %&  \multicolumn{1}{l}{Target}
-        %& \multicolumn{1}{l}{Target and Query} \\
-\multicolumn{2}{r}{} & \multicolumn{2}{c}{\emph{Proposal Set}} \\
-                     & & Target & Target and Query \\
-        \cline{2-4}
-        \multirow{3}{*}{\rotatebox[origin=c]{90}{\emph{Baseline Set}}} &
-  Query            & \emph{Self-Match}   & \emph{Self-Match-Ext} \\
-& Target           & \emph{Ratio-Match}   & \emph{Ratio-Match-Ext} \\
-& Target and Query & \emph{Mirror-Match} & \emph{Mirror-Match-Ext} \\
-        \cline{2-4}
-\end{tabular}
-\egroup
-\end{table}
-
-\begin{figure}[htb]
+%
+\subsection{A framework of matching methods}
+%
+
+\begin{figure}[t]
 \centering
 \includegraphics[width=0.85\columnwidth]{images/overview}
-\caption{Graphical representation of the \emph{baseline} and 
-\emph{proposal sets} for the methods in the proposed framework.}
+\caption{Graphical representation of the \emph{Baseline} and 
+\emph{Proposal Set} for different methods in the proposed framework}
 \label{fig:overview}
@@
 
-Algorithm~\ref{alg-gen} shows the generalized matching framework, 
-where the \emph{proposal set} and \emph{baseline set} are defined 
-according to Table~\ref{table:distinctness}.  In practice for e.g.\ 
-\emph{Ratio-Match} we can obtain $f_p$ and $f_b$ by finding the two 
-nearest neighbors of $F_{target}$. The other algorithms can be optimized 
-similarly. Figure~\ref{fig:matching} illustrates the structure of 
-the generalized algorithm.
+Given two images we can construct the proposal and baseline sets in six different ways as illustrated in Figure~\ref{fig:overview}.
+In the case of \emph{Ratio-Match} \cite{lowe2004sift} the \emph{proposal set} consists of all the feature points in the target image.
+Similarly the \emph{baseline set} consists of all the feature points in the target image except the \emph{proposed} match.
+For \emph{Ratio-Match} this practically means that given a query feature, $f_q$, the \emph{proposed match} and the \emph{baseline match} are the two nearest neighbors in the set of feature points in the \emph{target image} and the ratio is decided uniquely based on the \emph{target image}.
+In turn \emph{Mirror-Match} as introduced by the authors in \cite{arnfred2013mirror}, works by constructing the \emph{proposal set} and \emph{baseline set} by combining features from both the \emph{query} and \emph{target image}.
+By similar variations of the \emph{proposal} and \emph{baseline set} we derive four more algorithms as illustrated in Figure~\ref{fig:overview}, however we will not discuss \emph{Self-Match-Ext} and \emph{Both-Match} further in this paper since we show them to be equivalent with \emph{Self-Match} and \emph{Mirror-Match} respectively in Appendix~\ref{A:self} and \ref{A:mirror}.
 
@@
     \State $F_{target} = get\_features(I_{target})$
-\State $F_{proposal} = get\_proposal\_set(F_{query}, F_{target})$
-\State $F_{baseline} = get\_baseline\_set(F_{query}, F_{target})$
+\State $F_{proposal-all} = get\_proposal\_features(F_{query}, 
+F_{target})$
+\State $F_{baseline-all} = get\_baseline\_features(F_{query}, 
+F_{target})$
 \State $M = \varnothing$
 \ForAll{$f_q \in F_{query}$}
-    \State $f_p \gets getNearestNeighbo\text{r}(f_q, F_{proposal} \setminus 
-    \left\{f_q\right\})$
-    \State $f_b \gets getNearestNeighbo\text{r}(f_q, F_{baseline} \setminus 
-    \left\{f_q, f_p\right\})$
+    \State $F_{proposal} = F_{proposal-all} \setminus 
+    \left\{f_q\right\}$
+    \State $f_p \gets getNearestNeighbo\text{r}(f_q, F_{proposal})$
+    \State $F_{baseline} = F_{baseline-all} \setminus \left\{f_q, 
+    f_p\right\}$
+    \State $f_b \gets getNearestNeighbo\text{r}(f_q, F_{baseline})$
     \State $ratio \gets distance(f_q, f_p) / distance(f_q, f_b)$
@@
 	\EndIf
-\EndFor
+\EndFor \\
 \Return $M$
@@
 \end{algorithm}
+
+Algorithm~\ref{alg-gen} shows the generalized matching framework where the \emph{proposal set} and \emph{baseline set} are defined according to Figure~\ref{fig:overview}.
+In practice for e.g.\ \emph{Ratio-Match} we can obtain $f_p$ and $f_b$ by finding the two nearest neighbors of $F_{target}$.
+The other algorithms can be optimized similarly.
+Figure~\ref{fig:matching} illustrates the structure of this algorithm.
 
@@
 
-For some methods it is possible that the \emph{proposal match} is a 
-feature from the \emph{query image}, in which case we discard the match 
-as an untrue correspondence.  It also happens that we encounter 
-correspondences with a \emph{uniqueness ratio} above $1$, in which case we set 
-it to $1$ to maintain a bounded \emph{uniqueness ratio}.  Take for example the 
-case of \emph{Self-Match}. Using this method we might find that the 
-nearest neighbor of a feature in the target image is further from the 
-query feature than the nearest neighbor in the query image. In this case 
-the match is discarded.
-
-\subsection{Generalized Uniqueness Ratio}
-
-Form $F_{query} = \left\{f_{q_1} \ldots f_{q_n}\right\}$ and $F_{target} 
-= \left\{f_{t_1} \ldots f_{t_m}\right\}$.  We can obtain $F_{proposed}$ 
-and $F_{baseline}$ from these sets depending on the algorithm used (see 
-Table~\ref{table:distinctness}). $r = \text{r}(f_{q}, F_{proposed}, 
-F_{baseline})$ is the ratio of query feature $f_{q}$ given 
-$F_{proposed}$ and $F_{baseline}$.  If $f_{p}$ is the nearest neighbor 
-of $f_{q}$ in $F_{proposed}$ and $f_{b}$ is the nearest neighbor of 
-$f_{q}$ in $F_{baseline} \setminus \left\{f_{p}\right\}$, then the 
-generalized \emph{uniqueness} ratio is:
+For some methods it is possible that the \emph{proposal match} is a feature from the \emph{query image}, in which case we discard the match as an untrue correspondence.
+It also happens that we encounter correspondences with a \emph{uniqueness ratio} above $1$, in which case the match is also discarded.
+Take for example the case of \emph{Self-Match} where we might find that the nearest neighbor of a feature in the target image is further from the query feature than the nearest neighbor in the query image.
+In this case the match is discarded.
+
+%
+\subsection{Uniqueness Ratio}
+%
+
+The main distinguishing factor in between the algorithms in the framework is the final ratio between the distance of the two nearest neighbors of a query feature which decides if we keep or discard a match.
+We illustrate this process in Figure~\ref{fig:matching}.
+
+We can define a calculation of this ratio common to all algorithms in the framework which allows us to compare the algorithms theoretically.
+To do so we first define the concept of a nearest neighbor and then based on that the \emph{uniqueness ratio}, $r$:
+
+Given a feature, $f_i$ and a set of features, $F$ the nearest neighbor of $f_i$ in $F$ is: 
+\begin{equation*}
+\argmin_{f_j \in F} d(f, f_j)
+\end{equation*}
+Here, $d(f_i, f_j)$ is the distance between feature descriptors.With SIFT and SURF this is the Euclidean distance of the feature vectors \cite{lowe2004sift,bay2006surf}, whereas BRIEF, BRISK, and FREAK use the Hamming distance \cite{leutenegger2011brisk,calonder2010brief,alahi2012freak}.
+
+If we let $f_p \in F_{proposed}$ and $f_b \in F_{baseline}$ be the nearest neighbors of a feature $f_q$ in $F_{proposed}$ and $F_{baseline}$, the \emph{uniqueness ratio} is defined as follows:
 \begin{align*}
@@
 
-We let $K$ be the number of possible true correspondences between \emph{query} 
-and \emph{target image}. \emph{Precision} and \emph{recall} are 
-defined as:
+The performance in terms of precision and recall of any algorithm from the proposed framework is uniquely identified by the \emph{uniqueness ratio} $r$.
+To show this we let $K$ be the number of possible true correspondences between \emph{query} and \emph{target image}.
+\emph{Precision} and \emph{recall} are defined as:
 \begin{align*}
-    \textrm{Recall} &= \frac{\#\textrm{Correct Matches}}{K} \\
-    \textrm{Precision} &= \frac{\#\textrm{Correct 
-    Matches}}{\#\textrm{Correct Matches} + \#\textrm{Incorrect Matches}}
+    \textrm{Recall} &= \frac{\#\textrm{Correct}}{K} \\
+    \textrm{Precision} &= \frac{\#\textrm{Correct}}{\#\textrm{Correct} + \#\textrm{Incorrect}}
 \end{align*}
-Given $f_{nn} \in F_{target}$ as the nearest neighbor of any 
-$f_q \in F_{query}$, we define the set of features $F_{true}$ as 
-$\left\{ f_{q} \in F_{query} \mid f_{nn} \text{ is a true correspondence 
-of } f_{q} \right\}$ and $F_{false}$ as $F_{query} \setminus F_{true}$.  
-We can then define the number of correct and incorrect matches as 
-follows:
+Given $f_{p} \in F_{proposed}$ as the nearest neighbor of some $f_q \in F_{query}$, we define the set of features $F_{true}$ as $\left\{ f_{q} \in F_{query} \mid f_{p} \text{ is a true correspondence of } f_{q} \right\}$ and $F_{false}$ as $F_{query} \setminus F_{true}$.
+We can then define the number of correct and incorrect matches as follows:
 \begin{align*}
@@
     \tau}{0}{\textrm{otherwise}} \\
-    \#\textrm{Correct Matches} &= \sum_{f_{q} \in F_{true}} 
+    \#\textrm{Correct} &= \sum_{f_{q} \in F_{true}} 
     \textrm{keep\_match}(f_{q})\\
     %\mathbbm{1}_{\left\{ \right\}} \\
-    \#\textrm{Incorrect Matches} &= \sum_{f_{q} \in F_{false}}
+    \#\textrm{Incorrect} &= \sum_{f_{q} \in F_{false}}
     \textrm{keep\_match}(f_{q})
@@
 \end{align*}
-
-From the above we can conclude that the performance in terms of 
-precision and recall of any method from the proposed framework is 
-uniquely identified by the \emph{uniqueness ratio} $r$.  If for every query 
-feature $f_{q}$, $r$ is identical across two matching methods, then they 
-return identical results.
+If for every query feature $f_{q}$, $r$ is identical across two matching methods, then they return identical results.
 
@@
 
-Under the following three assumptions, which largely reflect the performance of 
-matching feature points in practice, we can theoretically compare the 
-performance of the different algorithms shown in 
-Table~\ref{table:distinctness}:
+Under the following three assumptions, which largely reflect the performance of matching feature points in practice, we can theoretically compare the performance of the different algorithms shown in Figure~\ref{fig:overview}:
+
 \begin{enumerate}
@@
 
-Based on these assumptions we first prove that the results of 
-\emph{Self-Match} are identical to \emph{Self-Match-Ext}. To do this, we 
-look at the nearest neighbor $f_{nn}$ of every query feature $f_{q}$ and 
-consider the two cases of $f_{nn} \in F_{query}$ and $f_{nn} \in
-F_{target}$. For $f_{nn} \in F_{target}$ the \emph{uniqueness ratio} of 
-\emph{Self-Match-Ext} is:
+Based on these assumptions we prove that \emph{Ratio-Match-Ext} is equal or better than \emph{Ratio-Match} in terms both precision and recall.
+Consider the nearest neighbor $f_{p}$ of a query feature $f_{q}$ and the two cases where we either have the $f_{p} \in F_{query}$ or $f_{p} \in F_{target}$.
+For $f_{p} \in F_{target}$ the uniqueness ratio of \emph{Ratio-Match-Ext} is:
 \begin{align*}
@@
         &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
-        &= \text{r}(f_{q}, F_{target}, F_{baseline}).
+        &= \text{r}(f_{q}, F_{target}, F_{baseline})
 \end{align*}
-Since $F_{proposed} = F_{target}$ for \emph{Self-Match}, this shows that
-when the nearest neighbor is found in the target image, the two 
-algorithms behave identically. For $f_{nn} \in F_{query}$ 
-\emph{Self-Match} gives us the following ratio:
-\begin{align*}
-    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
-        &= \text{r}(f_{q}, F_{target}, F_{query}) \\
-        &\geq 1.
-\end{align*}
-The closest neighbor is found in the query image, so $d(f_{q}, f_{nn}) < 
-d(f_{q},f_{p})$, where $f_{p}$ is the nearest neighbor from 
-$F_{proposal}$. \emph{Self-Match-Ext} does not return a correspondence 
-found in the \emph{query image}, and since $\tau \in [0,1]$, neither does 
-\emph{Self-Match}. This proves that 
-\emph{Self-Match} returns the same matches as \emph{Self-Match-Ext} for any set of query features. For 
-this reason both algorithms will be referred to as just 
-\emph{Self-Match}.
-
-The above proof can easily be extended to show that \emph{Mirror-Match} and \emph{Mirror-Match-Ext} also return the same correspondences, and 
-both will be referred to as \emph{Mirror Match} from here on.
-
-For the case of \emph{Ratio-Match} and \emph{Ratio-Match-Ext}, we 
-can show that \emph{Ratio-Match-Ext} is equal or better than 
-\emph{Ratio-Match}.  Consider again the nearest neighbor $f_{nn}$ of a 
-query feature $f_{q}$, and the two cases where we either have $f_{nn} 
-\in F_{query}$ or $f_{nn} \in F_{target}$. For $f_{nn} \in F_{target}$ 
-the \emph{uniqueness ratio} of \emph{Ratio-Match-Ext} is:
-\begin{align*}
-    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
-        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
-        &= \text{r}(f_{q}, F_{target}, F_{baseline}).
-\end{align*}
-Since $F_{proposed} = F_{target}$ for \emph{Ratio-Match} this shows that
-when the nearest neighbor is found in the target image, the two 
-algorithms behave identically. For $f_{nn} \in F_{query}$ 
-\emph{Ratio-Match} gives us the following ratio:
+Since $F_{proposed} = F_{target}$ for \emph{Ratio-Match} this shows that when the nearest neighbor is found in the target image, the two algorithms behave identically.
+For $f_{p} \in F_{query}$ \emph{Ratio-Match} gives us the following ratio:
 \begin{align*}
@@
 \end{align*}
-While \emph{Ratio-Match-Ext} does not return the correspondence if 
-the nearest neighbor of a query feature is in the \emph{query image}, 
-\emph{Ratio-Match} is likely to do so, since the \emph{uniqueness ratio} is 
-found by dividing with the second nearest neighbor in the \emph{target 
-image}. This shows that for cases where a query feature has a nearest 
-neighbor in the \emph{query image}, \emph{Ratio-Match-Ext} is superior 
-to \emph{Ratio-Match}. Since query features with a nearest neighbor in 
-the \emph{query image} are false correspondences per assumptions \#1 and 
-\#2, this proves that \emph{Ratio-Match-Ext} has superior 
-\emph{Precision} to \emph{Ratio-Match} while maintaining equal 
-\emph{Recall}.
-
-Finally we show that the accuracy of \emph{Mirror-Match} is equal to or better than 
-\emph{Ratio-Match-Ext}. Consider as before the nearest neighbor $f_{nn}$ 
-of a query feature $f_{q}$. When $f_{nn}$ resides in the \emph{query 
-image}, both algorithms behave alike and discard the match.  However, 
-consider the \emph{uniqueness ratio} of \emph{Mirror Match} for the case where 
-$f_{nn}$ resides in the \emph{target image}:
+
+That is, \emph{Ratio-Match} calculates the ratio based on the two nearest correspondences in the \emph{target image}.
+\emph{Ratio-Match-Ext} on the other hand does not return any correspondence because the nearest neighbor is in the \emph{query image}.
+Since query features with a nearest neighbor in the \emph{query image} are false correspondences per assumption \#1 and \#2, this proves that \emph{Ratio-Match-Ext} has superior \emph{Precision} to \emph{Ratio-Match} while maintaining equal \emph{Recall}.
+
+Next we show that \emph{Mirror-Match} is equal or better than \emph{Ratio-Match-Ext} in terms of precision and recall.
+Consider as before the nearest neighbor $f_{p}$ of a query feature $f_{q}$.
+When $f_{p}$ resides in the \emph{query image} both algorithms behave alike and discard the match.
+However, consider the uniqueness ratio of \emph{Mirror-Match} for the case where $f_{p}$ resides in the \emph{target image}:
 \begin{align*}
@@
 \end{align*}
-For a true correspondence the \emph{uniqueness ratio} using 
-$F_{query}$ as a baseline is distributed similarly to the ratio when using 
-$F_{target}$ according to assumption \#3. In this case the algorithm performs like 
-\emph{Ratio-Match-Ext}.  However, for an untrue correspondence with a 
-baseline match in the \emph{query image} which is closer than the
-baseline match in the \emph{target image}, \emph{Mirror Match} will 
-return a worse \emph{uniqueness ratio}. This in turns means that \emph{Mirror 
-Match} is equal or better than \emph{Ratio-Match-Ext} in terms of  
-\emph{Precision} while maintaining equal \emph{Recall}.
-
-We have thus proven that -- based on assumptions \#1-3 -- for any given recall rate, the 
-precision of the algorithms in the framework compares as follows:
+For a true correspondence the \emph{uniqueness ratio} using $F_{query}$ as a baseline is distributed similarly to the ratio when using $F_{target}$ according to assumption \#3.
+In this case the algorithm performs like \emph{Ratio-Match-Ext}.
+However, for an untrue correspondence with a baseline match in the \emph{query image} which is closer than the baseline match in the \emph{target image}, \emph{Mirror Match} will return a worse \emph{uniqueness ratio}.
+This in turns means that \emph{Mirror Match} is equal or better than \emph{Ratio-Match-Ext} in terms of  \emph{Precision} while maintaining equal \emph{Recall}.
+
+Using a similar procedure we prove that \emph{Self-Match} is equal to \emph{Self-Match-Ext} and \emph{Both-Match} is equal to \emph{Mirror Match} in Appendix~\ref{A:self} and \ref{A:mirror} respectively.
+
+We have thus proven that -- based on assumptions \#1-3 -- for any given recall rate, the precision of the algorithms in the framework compares as follows: 
 \begin{align*}
-    \textit{Self-Match} &= \textit{Self-Match-Ext} \\
-    \textit{Mirror-Match} &= \textit{Mirror-Match-Ext} \\
     \textit{Ratio-Match} &\leq \textit{Ratio-Match-Ext} \leq 
-    \textit{Mirror Match}
+    \textit{Mirror-Match}
 \end{align*}
 
-The difference between \emph{Self-Match} and \emph{Ratio-Match} is  
-the source of the \emph{baseline set}. For true correspondences 
-they should perform similarly, otherwise the 
-performance of the two depends entirely on the images being matched. 
-When we match images where the target image may not overlap at all 
-with the query image, using the query image and not the target image as 
-a \emph{baseline set} seems like a reasonable choice given that the 
-baseline set in this case would be closer to the feature matched and 
-more strictly rule out untrue correspondences.
+The difference between \emph{Self-Match} and \emph{Ratio-Match} is  the source of the \emph{baseline set}.
+For true correspondences they should perform similarly, otherwise the performance of the two depends entirely on the images being matched.
+When we match images where the target image may not overlap at all with the query image, using the query image and not the target image as a \emph{baseline set} seems like a reasonable choice given that the baseline set in this case would be closer to the feature matched and more strictly rule out untrue correspondences.
 
@@
 
-The three assumptions underlying the formal ranking of 
-algorithms presented above have been chosen to reflect conditions under which we would ideally
-match feature points. However, for each assumption there exist 
-corner cases where it is no longer valid. In this section we 
-discuss these corner cases in order to review the 
-circumstances under which the absolute or relative performance of the 
-algorithms might differ.
-
-The first assumption states that there is at most one unique match to 
-every feature point, which is often the case for natural images. 
-However, for the recognition of object classes or in generated images 
-with repetitive content, a point in the \emph{query image} might have 
-several true correspondences in the \emph{target image}, so using a 
-\emph{baseline match} from the target image will lead to a much higher 
-\emph{uniqueness ratio}. However, as long as the query image does not 
-contain repetitive objects, we can still use \emph{Self-Match} without 
-loss of precision.
-
-According to the second assumption, feature descriptors should behave such that
-when matched, a true correspondence to a query feature will always be 
-the nearest neighbor. For practical implementations of feature detectors and descriptors, 
-this property strongly depends on the differences between \emph{query} 
-and \emph{target image}, as shown in  
-\cite{mikolajczyk2005performance,tuytelaars2008local}. In the degenerate 
-case where the closest match is not an actual correspondence, there is 
-no reason why this match should be disproportionately closer to the 
-\emph{query feature} than any matches in the \emph{target image}, so in 
-most cases we would expect the \emph{uniqueness ratio} to be high 
-(signifying a bad match). This means that with a lenient threshold (close 
-to 1), the guarantees about precision and recall equivalence between the 
-different ratio algorithms might no longer hold due to the inconsistent descriptor behavior. 
-It is worth noting that if 
-assumption \#2 holds, matching using only nearest neighbor is not 
-necessarily optimal, unless there is a complete scene overlap between
-the images matched. For cases where there is little or no overlap, a 
-nearest neighbor would indiscriminately return false matches even with 
-well-behaved feature descriptors.
-
-The third assumption states that the \emph{uniqueness ratios} using either the 
-\emph{query} or \emph{target image} as the baseline set would be similar
-in distribution given that the feature point we are matching has a true 
-correspondence. We can support this assumption by looking at the 
-\emph{uniqueness ratios} returned by \emph{Self-Match} and 
-\emph{Ratio-Match}, since they use the \emph{query} and 
-\emph{target image} respectively to calculate the \emph{uniqueness ratio}.  
-Figure~\ref{fig:ratio_hist} shows the actual \emph{uniqueness ratios} 
-measured from 3024 image pairs featuring 3D objects (see below for more on this dataset).  
-For ratios lower than $0.7$, the \emph{uniqueness ratios} are similar, but as we approach 
-more lenient thresholds, the ratios based on the \emph{query image} are 
-higher than those for the \emph{target image}. This means that the third assumption 
-is invalid for more lenient thresholds, and we can no longer expect \emph{Mirror-Match} to outperform 
-\emph{Ratio-Match-Ext} in terms of precision without a penalty in recall.
+The three assumptions underlying the formal ranking of algorithms presented above have been chosen to reflect conditions under which we would ideally match feature points.
+However, for each assumption there exist corner cases where it is no longer valid.
+In this section we discuss these corner cases in order to review the circumstances under which the absolute or relative performance of the algorithms might differ.
+
+The first assumption states that there is at most one unique match to every feature point, which is often the case for natural images.
+However, for the recognition of object classes or in generated images with repetitive content, a point in the \emph{query image} might have several true correspondences in the \emph{target image}, so using a \emph{baseline match} from the target image will lead to a much higher \emph{uniqueness ratio}.
+However, as long as the query image does not contain repetitive objects, we can still use \emph{Self-Match} without loss of precision.
+
+According to the second assumption, feature descriptors behave such that when matched, a true correspondence to a query feature will always be the nearest neighbor.
+For practical implementations of feature detectors and descriptors, this property strongly depends on the differences between \emph{query} and \emph{target image}, as shown in  \cite{mikolajczyk2005performance,tuytelaars2008local}.
+In the degenerate case where the closest match is not an actual correspondence, there is no reason why this match should be disproportionately closer to the \emph{query feature} than any matches in the \emph{target image}, so in most cases we would expect the \emph{uniqueness ratio} to be high (signifying a bad match).
+This means that with a lenient threshold (close to 1), the guarantees about precision and recall equivalence between the different ratio algorithms might no longer hold due to the inconsistent descriptor behavior.
+It is worth noting that if assumption \#2 holds, matching using only nearest neighbor is not necessarily optimal, unless there is a complete scene overlap between the images matched.
+For cases where there is little or no overlap, a nearest neighbor would indiscriminately return false matches even with well-behaved feature descriptors.
+
+The third assumption states that the \emph{uniqueness ratios} using either the \emph{query} or \emph{target image} as the baseline set would be similar in distribution given that the feature point we are matching has a true correspondence.
+We can support this assumption by looking at the \emph{uniqueness ratios} returned by \emph{Self-Match} and \emph{Ratio-Match}, since they use the \emph{query} and \emph{target image} respectively to calculate the \emph{uniqueness ratio}.
+Figure~\ref{fig:ratio_hist} shows the actual \emph{uniqueness ratios} measured from 3024 image pairs featuring 3D objects (see below for more on this dataset).
+For ratios lower than $0.7$, the \emph{uniqueness ratios} are similar, but as we approach more lenient thresholds, the ratios based on the \emph{query image} are higher than those for the \emph{target image}.
+This means that the third assumption is invalid for more lenient thresholds, and we can no longer expect \emph{Mirror-Match} to outperform \emph{Ratio-Match-Ext} in terms of precision without a penalty in recall.
 
@@
 %
-In this section we present the experiments and evaluation results comparing 
-\emph{Self-Match}, \emph{Ratio-Match}, \emph{Ratio-Match-Ext} and 
-\emph{Mirror-Match}. We use two different databases to compile 
-results over different image variations.
-
-To measure results on realistic and 
-variate non-planar images, we test the algorithm on the 3D Objects 
-database released by Moreels and Pietro \cite{moreels2007evaluation} in 
-Section~\ref{S:3dobjects}. This database contains a set of 86 3D objects 
-photographed from all sides at 5 degree intervals from two different 
-elevation angles and under three different lighting conditions.
-To measure the performance over variations such as viewpoint change, 
-blur, compression noise, rotation, and zoom, we use the graffiti 
-image set introduced by Mikolajczyk and Schmid 
-\cite{mikolajczyk2005performance} in Section~\ref{S:Planar}.  This 
-dataset contains 8 scenes each with 6 images linked by homographies and 
-features only planar or almost planar scenes.
-
-For the experiments we use the \emph{SIFT} descriptor and keypoint 
-detector with default parameters as implemented in the OpenCV library 
-2.4.6.  To further test how the framework performs across descriptors, we 
-evaluate SURF \cite{bay2006surf}, BRISK \cite{leutenegger2011brisk}, 
-BRIEF \cite{calonder2010brief}, and FREAK \cite{alahi2012freak} in 
-Section~\ref{label:desc}.
+In this section we present the experiments and evaluation results comparing \emph{Self-Match}, \emph{Ratio-Match}, \emph{Ratio-Match-Ext} and \emph{Mirror-Match}.
+We use two different databases to compile results over different image variations.
+
+To measure results on realistic and variate non-planar images, we test the algorithm on the 3D Objects database released by Moreels and Pietro \cite{moreels2007evaluation} in Section~\ref{S:3dobjects}.
+This database contains a set of 86 3D objects photographed from all sides at 5 degree intervals from two different elevation angles and under three different lighting conditions.
+
+For the experiments we use the \emph{SIFT} descriptor and keypoint detector with default parameters as implemented in the OpenCV library 2.4.6.
+To further test how the framework performs across descriptors, we evaluate SURF \cite{bay2006surf}, BRISK \cite{leutenegger2011brisk}, BRIEF \cite{calonder2010brief}, and FREAK \cite{alahi2012freak} in Section~\ref{label:desc}.
 
 Across all experiments, only the luminance channel is used in the feature detection and description stage.
-Images larger than $1024\!\times\!768$ are resized to fit within those dimensions using 
-ImageMagick with default parameters.
+Images larger than $1024\!\times\!768$ are resized to fit within those dimensions using ImageMagick with default parameters.
 
@@
 
-The 3D objects dataset by Moreels and Pietro \cite{moreels2007evaluation} allows us to experimentally compare matching 
-algorithms over a large range of object and surface types rotated on a 
-turnstile and photographed from every 5 degree turn.  15 objects from the dataset are shown in Figure~\ref{fig:3d_objects}.  We use images of 
-84 different objects under three different lighting conditions at 12 
-different angle intervals, conducting experiments with a total of 3024 
-image pairs.
+The 3D objects dataset by Moreels and Pietro \cite{moreels2007evaluation} allows us to experimentally compare matching algorithms over a large range of object and surface types rotated on a turnstile and photographed from every 5 degree turn.
+15 objects from the dataset are shown in Figure~\ref{fig:3d_objects}.
+We use images of 84 different objects under three different lighting conditions at 12 different angle intervals, conducting experiments with a total of 3024 image pairs.
 
@@
 
-To validate matches, Moreels and Pietro propose a method 
-using epipolar constraints \cite[p.266]{moreels2007evaluation}, which is 
-outlined in Figure~\ref{fig:frog}.  According to their 
-experiments, these constraints are able to identify 
-true correspondences with an error rate of $2\%$. We use their proposed 
-method to generate the ground truth for the evaluation of our framework.
+To validate matches, Moreels and Pietro propose a method using epipolar constraints \cite[p.266]{moreels2007evaluation}, which is outlined in Figure~\ref{fig:frog}.
+According to their experiments, these constraints are able to identify true correspondences with an error rate of $2\%$.
+We use their proposed method to generate the ground truth for the evaluation of our framework.
 
@@
     \caption{Creating epipolar constraints based on three source images \cite{moreels2007evaluation}.
-        (a) \emph{Query image} marked with the position 
-        of the feature we are attempting to match. (b) 
-        Auxiliary image, taken at the 
-        same rotation as the \emph{query image} but from a higher 
-        viewpoint. Feature points near the epipolar line 
-        of the feature point from the \emph{query image} are shown as dots.
-				(c) Sample \emph{target image} with feature points near the epipolar line of the feature point from the \emph{query image}.
-				(d) Same \emph{target image} with epipolar lines from all the 
-    feature points shown in the \emph{auxiliary image}. 
-		True correspondences should lie close to the intersections 
-    of the epipolar line from (c) with the lines from (d). In this particular case two 
-    feature points are possible correspondences.
+(a) \emph{Query image} marked with the position of the feature we are attempting to match.
+(b) Auxiliary image, taken at the same rotation as the \emph{query image} but from a higher viewpoint.
+The line going through the image is the epipolar line of the feature point in the \emph{query image}.
+The markers indicate all feature points in the image found near the epipolar line.
+In c) we show the \emph{target image} which in this case is rotated 45 degrees from the \emph{query image}.
+The line overlaid on the image represents the epipolar line corresponding to the feature point shown in the \emph{query image}.
+The markers indicate all feature points in the image found near the epipolar line.
+In d) we show the \emph{target image} again, this time overlaid with the epipolar lines corresponding to all the features shown in the \emph{auxiliary image}.
+A true correspondence should be found within a small distance of one of the intersections of the line in c) and the lines in d).
+In this particular case both feature points shown in c) and d) could possible be a correct correspondence.
 }%
@@
 
-To compute the total number of possible correspondences, we take each 
-feature in a \emph{query image} and count how many of them have a 
-feature in the \emph{target image} which would satisfy the epipolar 
-constraints outlined above. When using this dataset, features 
-with no correspondences were not included in the set of features for testing, 
-so as to avoid matching non-moving background and 
-foreground objects.
-
-We evaluate all matching algorithms from our framework on the 3D objects dataset by 
-matching images at different angular intervals. For each object we 
-pick the \emph{query} image as the image taken at 10 degrees rotation 
-for calibration stability.  We then match this image with 
-the same object turned an additional $\Delta$ degrees, $\Delta \in \{5, 10, 
-\ldots, 60\}$.  For every angle interval we compare images taken under 
-3 different lighting conditions as provided by the dataset.
-We include all objects in the database for which photos at 5 degree 
-angle intervals are available except for the ``Rooster'' and ``Sponge'' 
-objects due to image irregularities. For each plot we show the 
-accumulated results on all 3D objects, weighted by the number of possible 
-true correspondences for the particular object. This ensures that each 
-object contributes equally to the final result, despite some objects
-resulting in disproportionally more matches than others.
-
-Figure~\ref{fig:all_objects} shows the performance of the different matching methods in our proposed
-framework for $12$ increasingly bigger angle differences. The results are shown 
-in a precision / recall plot to make it easy to compare performance in 
-terms of precision at similar levels of recall.  \emph{Ratio-Match} and \emph{Self-Match} show similar 
-results, while \emph{Mirror-Match} and \emph{Ratio-Match-Ext} outperform 
-both of them, showing the advantage of composing the \emph{proposed set} of 
-features from both images. \emph{Mirror-Match} fares slightly but
-consistently better than \emph{Ratio-Match-Ext}. In general we 
-see the largest performance improvements at lower recall and a 
-convergence of precision at higher recall. This is expected since a 
-higher recall is a direct consequence of a more lenient threshold; as
-we let the threshold approach $1$, we lose the benefits of thresholding 
-on the \emph{uniqueness ratio}, and all methods start approximating the 
-results of a simple nearest neighbor match. For all but 
-\emph{Ratio-Match}, the features with better matches within the same 
-image are still weeded out, which explains the tail end of 
-\emph{Ratio-Match} at high recall where the other algorithms no longer 
-have results. As we demonstrated in \cite{arnfred2013mirror}, the removal 
-of within-image matches improves performance on image pairs with partial 
-or no overlap. For no overlap we would expect a matching algorithm to 
-reject matches within regions that have no matching counterparts in the 
-other image.
-
-The performance gap between methods increases gradually with angle, reaching its maximum between $25$ and $40$ degrees, 
-where \emph{Mirror-Match} exhibits about 20 percentage-points higher precision than \emph{Ratio-Match}. 
-At larger viewpoint differences above $45$ degrees, the performance gain decreases.  We suspect this is partly because assumption \#2 stops being valid when the images are transformed beyond 
-a certain level of recognizability.
-
-To summarize, the methods perform as predicted on the 3D Objects dataset
-with \emph{Mirror-Match} in general performing better than 
-\emph{Ratio-Match-Ext}, which in turn outperforms
-\emph{Ratio-Match}. The experimental results also show that 
-\emph{Self-Match} overall performs equally well as or better than 
-\emph{Ratio-Match}.
-
-\subsection{Planar Scenes}
-\label{S:Planar}
-
-\begin{figure*}[t!]
-	\centering
-    \includegraphics[width=2\columnwidth]{images/results_acr_all}
-    \caption{Accumulated results for each scene in the image dataset by 
-    Mikolajczyk and Schmid \cite{mikolajczyk2005performance}.}
-    \label{fig:acr_objects}
-\end{figure*}
-
-To evaluate local feature descriptors, Mikolajczyk and Schmid \cite{mikolajczyk2005performance} introduced
-a series of $8$ image sets featuring different transformations such as 
-compression noise, rotation and zoom, blur and viewpoint change. The 8 source scenes are shown in Figure~\ref{fig:acr_images}.  
-All  images are tied by homographies, which makes them convenient for testing 
-purposes, but as a consequence they all depict planar scenes, which is 
-somewhat limited and unrealistic. For each scene, there are 6 different 
-images with increasing levels of a certain transformation, such that 
-the change between image 1 and image 2 in a scene is only slight, while image 6 is markedly different from image 1 for most cases.
-
-\begin{figure}[htb]
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/bark}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/bikes}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/boat}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/graf}
-    \end{subfigure}%
-    \vspace{1.5 mm}
-    % Linebreak
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/leuven}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/trees}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/ubc}
-    \end{subfigure}%
-    ~ %
-    \begin{subfigure}[t]{0.24\columnwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/acr/wall}
-    \end{subfigure}%
-    \caption{Scenes from the image dataset by Mikolajczyk and Schmid 
-    \cite{mikolajczyk2005performance}, ordered as they appear in 
-Figure~\ref{fig:acr_objects}.}
-    \label{fig:acr_images}
-\end{figure}
-
-We match the first image in each scene with images 3, 4, 5, 
-and 6 and show the accumulated result weighted by the possible number of 
-true correspondences for each pair. We exclude the comparison with image 
-2 because it is trivial in most cases and does not tell us much about 
-the relative performance of the different methods. We find inliers by 
-using the homography between image pairs as follows: Given a potential 
-match between two pixels $p_1$ and $p_2$, $m = \left(p_1, p_2\right)$, 
-and a homography $H$ relating the two images $I_1$ and $I_2$, we can 
-calculate if $m$ is an inlier by checking if the two points satisfy the 
-following criterion:
-\begin{equation*}
-\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max},
-\end{equation*}
-i.e.\ the distance between $p_1$ translated to $I_2$ and $p_2$ 
-\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
-less than a certain threshold (we use $d_{\max}=10$ pixels here).
-
-Figure~\ref{fig:acr_objects} shows the results plotted with precision on 
-the y-axis and recall along the x-axis. For scenes such as `bark', `boat' 
-(zoom and rotation), `leuven' (lighting changes) and `wall' (viewpoint changes), all methods 
-in the framework show similar results, largely because the precision approaches 100\% for low recall, which does not leave much room 
-for improvement. For `bikes' and `trees' (blur) as well as `ubc'
-(compression) and `graf' (viewpoint), \emph{Mirror-Match} clearly 
-outperforms \emph{Ratio-Match}, albeit with a smaller margin than 
-for the 3D objects dataset. Because many images in the dataset are 
-trivial to match and only a few are very difficult, there is less difference
-between the algorithms than with the 3D objects dataset. However, the 
-theoretical predictions are still confirmed, with \emph{Mirror-Match} 
-performing better than or equal to \emph{Ratio-Match-Ext}, which in turn 
-performs better than or equal to \emph{Ratio-Match}. \emph{Self-Match} 
-again achieves a performance comparable to \emph{Ratio-Match} using only the \emph{query image} as \emph{baseline 
-set}.
+To compute the total number of possible correspondences, we take each feature in a \emph{query image} and count how many of them have a feature in the \emph{target image} which would satisfy the epipolar constraints outlined above.
+When using this dataset, features with no correspondences were not included in the set of features for testing, so as to avoid matching non-moving background and foreground objects.
+
+We evaluate all matching algorithms from our framework on the 3D objects dataset by matching images at different angular intervals.
+For each object we pick the \emph{query} image as the image taken at 10 degrees rotation for calibration stability.
+We then match this image with the same object turned an additional $\Delta$ degrees, $\Delta \in \{5, 10, \ldots, 60\}$.
+For every angle interval we compare images taken under 3 different lighting conditions as provided by the dataset.
+We include all objects in the database for which photos at 5 degree angle intervals are available except for the ``Rooster'' and ``Sponge'' objects due to image irregularities.
+For each plot we show the accumulated results on all 3D objects, weighted by the number of possible true correspondences for the particular object.
+This ensures that each object contributes equally to the final result, despite some objects resulting in disproportionally more matches than others.
+
+Figure~\ref{fig:all_objects} shows the performance of the different matching methods in our proposed framework for $12$ increasingly bigger angle differences.
+The results are shown in a precision / recall plot to make it easy to compare performance in terms of precision at similar levels of recall.
+\emph{Ratio-Match} and \emph{Self-Match} show similar results, while \emph{Mirror-Match} and \emph{Ratio-Match-Ext} outperform both of them, showing the advantage of composing the \emph{proposed set} of features from both images.
+\emph{Mirror-Match} fares slightly but consistently better than \emph{Ratio-Match-Ext}.
+In general we see the largest performance improvements at lower recall and a  convergence of precision at higher recall.
+This is expected since a higher recall is a direct consequence of a more lenient threshold; as we let the threshold approach $1$, we lose the benefits of thresholding on the \emph{uniqueness ratio}, and all methods start approximating the results of a simple nearest neighbor match.
+For all but \emph{Ratio-Match} at high recall where the other algorithms no longer have results.
+As we demonstrated in \cite{arnfred2013mirror}, the removal of within-image matches improves performance on image pairs with partial or no overlap.
+For no overlap we would expect a matching algorithm to reject matches within regions that have no matching counterparts in the other image.
+
+The performance gap between methods increases gradually with angle, reaching its maximum between $25$ and $40$ degrees, where \emph{Mirror-Match} exhibits about 20 percentage-points higher precision than \emph{Ratio-Match}.
+At larger viewpoint differences above $45$ degrees, the performance gain decreases.
+We suspect this is partly because assumption \#2 stops being valid when the images are transformed beyond a certain level of recognizability.
+
+To summarize, the methods perform as predicted on the 3D Objects dataset with \emph{Mirror-Match} in general performing better than \emph{Ratio-Match-Ext}, which in turn outperforms \emph{Ratio-Match}.
+The experimental results also show that \emph{Self-Match} overall perform equal to or better than \emph{Ratio-Match}.
 
@@
 
-\begin{figure*}[t!]
-    \begin{subfigure}[t]{1\textwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/results_descriptors_imageset1}
-		\caption{Keypoint / Descriptor combinations evaluated on 15 
-		pairs of photos of 3D objects taken 25 degrees apart.}
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=2\columnwidth]{images/results_descriptors_imageset1}
+    \caption{Keypoint / Descriptor combinations measured on 15 pairs of 
+    photos of 3D objects taken 25 degrees apart.}
     \label{fig:descriptors}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{1\textwidth}
-        \centering
-        \includegraphics[width=1\columnwidth]{images/results_descriptors_easy}
-        \caption{Keypoint / Descriptor combinations evaluated on images 1 and 3 from the `Bikes' 
-        scene.}
-        \label{fig:descriptors_easy}
-    \end{subfigure}%
-    \caption{Evaluation of Keypoint / Descriptor combinations (K = Keypoint, D = 
-Descriptor).}
 \end{figure*}
 
-To evaluate whether the improvement gains with the SIFT descriptor 
-translate to other feature descriptors such as SURF \cite{bay2006surf} 
-or binary features such as BRIEF \cite{calonder2010brief}, BRISK 
-\cite{leutenegger2011brisk}, or FREAK \cite{alahi2012freak}, we evaluated 
-the different descriptors on the 3D objects data set.  The binary 
-features were each paired with the FAST feature detector for 
-consistency, while SIFT and SURF were tested with their respective 
-feature detectors.  For each keypoint detector and feature descriptor 
-pair we used the standard implementation from OpenCV 2.4.6.
-
-The descriptors were evaluated on 15 images of the 3D object dataset 
-with a fixed angle offset of 25 degrees (pictured in 
-Figure~\ref{fig:3d_objects}).  Otherwise the evaluation performed in the same manner as
-the general evaluation of 3D Objects in Section~ref{S:3dobjects}, and the data presented is 
-accumulated over the 15 objects, each set of results weighted by the 
-possible number of correspondences.
+To evaluate whether the improvement gains with the SIFT descriptor translate to other feature descriptors such as SURF \cite{bay2006surf} or binary features such as BRIEF \cite{calonder2010brief}, BRISK \cite{leutenegger2011brisk}, or FREAK \cite{alahi2012freak}, we evaluated the different descriptors on the 3D objects data set.
+The binary features were each paired with the FAST feature detector for consistency, while SIFT and SURF were tested with their respective feature detectors.
+For each keypoint detector and feature descriptor pair we used the standard implementation from OpenCV 2.4.6.
+
+The descriptors were evaluated on 15 images of the 3D object dataset with a fixed angle offset of 25 degrees (pictured in Figure~\ref{fig:3d_objects}).
+Otherwise the evaluation performed in the same manner as the general evaluation of 3D Objects in Section~ref{S:3dobjects}, and the data presented is accumulated over the 15 objects, each set of results weighted by the possible number of correspondences.
 
 The results in Figure~\ref{fig:descriptors} are again in line with the theoretical performance analysis of Section~\ref{S:Proofs} .
-They also show a clear difference in the variance of matching method 
-performance between SIFT and the rest of the descriptors. The 
-performance of \emph{Mirror-Match} using SIFT shows a clear increase in 
-precision over \emph{Ratio-Match} at equal recall levels. For other 
-descriptors the improvement is much less pronounced.  For SURF, BRISK, 
-and BRIEF we see a small improvement in precision using 
-\emph{Mirror-Match} over \emph{Ratio-Match} and \emph{Ratio-Match-ext}, 
-whereas FREAK yields similar results no matter what algorithm is used.  
-For all descriptors \emph{Self-Match} performs on par with 
-\emph{Ratio-Match}.
-
-Part of this difference between SIFT and the 
-other descriptors can be explained by looking at the recall rate 
-with for example SURF\@. Given the same amount of possible matches, 
-\emph{Ratio-Match} with SURF spans a larger range of recall.  
-Since all other methods filter out matches that are better matched 
-within the same image, but show no increase in precision, we can conclude 
-that correct matches are discarded because there are better matches 
-within the same image. This violates assumption \#2 stating that a 
-descriptor is well behaved and matches best with a descriptor of a true 
-correspondence. This means that for this particular evaluation case, SURF 
-and the binary features tested are not sufficiently discriminative to 
-provide a viable case for preferring \emph{Mirror-Match} over 
-\emph{Ratio-Match}.
-
-To test this hypothesis we looked at the results from matching an image 
-pair with very little inter image variation. We compare images 1 and 
-image 3 from the `bikes' scene in the image set released by Mikolajczyk 
-and Schmid \cite{mikolajczyk2005performance}. The results 
-in Figure~\ref{fig:descriptors_easy} show a market improvement for 
-\emph{Self-Match}, \emph{Mirror-Match}, and \emph{Ratio-Match-Ext} over 
-\emph{Ratio-Match} for the case of BRISK, BRIEF, and FREAK as expected.  
-For SURF however, the algorithms perform similarly at low recall while 
-\emph{Ratio-Match} shows better performance at more lenient thresholds.
+They also show a clear difference in the variance of matching method performance between SIFT and the rest of the descriptors.
+The performance of \emph{Mirror-Match} using SIFT shows a clear increase in precision over \emph{Ratio-Match} at equal recall levels.
+For other descriptors the improvement is much less pronounced.
+For SURF, BRISK, and BRIEF we see a small improvement in precision using \emph{Mirror-Match} over \emph{Ratio-Match} and \emph{Ratio-Match-ext}, whereas FREAK yields similar results no matter what algorithm is used.
+For all descriptors \emph{Self-Match} performs on par with \emph{Ratio-Match}.
+
+Part of this difference between SIFT and the other descriptors can be explained by looking at the recall rate with for example SURF\@.
+Given the same amount of possible matches, \emph{Ratio-Match} with SURF spans a larger range of recall.
+Since all other methods filter out matches that are better matched within the same image, but show no increase in precision, we can conclude that correct matches are discarded because there are better matches within the same image.
+This violates assumption \#2 stating that a descriptor is well behaved and matches best with a descriptor of a true correspondence.
+This means that for this particular evaluation case, SURF and the binary features tested are not sufficiently discriminative to provide a viable case for preferring \emph{Mirror-Match} over \emph{Ratio-Match}.
 
@@
 
-In terms of computational complexity, the algorithms can be implemented 
-in $O(n\log n)$, if we assume that both the \emph{query} and the 
-\emph{target} image have $n$ feature points. For a target image with $m$ 
-features where $m$ is significantly different from $n$, the complexities 
-are as noted in Table~\ref{table:running_times}. 
-In practice the constant factors 
-involved in the actual matching of two images with approximately the 
-same number of feature points are usually small enough that all the 
-algorithms run at very similar speeds. This is also shown in 
-Table~\ref{table:running_times}, which contains the running times as measured 
-while matching 15 3D objects under three different lighting conditions 
-($42$ image pairs were matched in total). The running times are averaged 
-over three separate runs of each algorithm implemented using the same 
-data structures and libraries in Python.
+In terms of computational complexity, the algorithms can be implemented in $O(n\log n)$, if we assume that both the \emph{query} and the \emph{target} image have $n$ feature points.
+For a target image with $m$ features where $m$ is significantly different from $n$, the complexities are as noted in Table~\ref{table:running_times}.
+In practice the constant factors involved in the actual matching of two images with approximately the same number of feature points are usually small enough that all the algorithms run at very similar speeds.
+This is also shown in Table~\ref{table:running_times}, which contains the running times as measured while matching 15 3D objects under three different lighting conditions ($42$ image pairs were matched in total).
+The running times are averaged over three separate runs of each algorithm implemented using the same data structures and libraries in Python.
 
 \begin{table}[htb]
-\caption{Complexity and running times tested on 15 image pairs on 3 
-lighting conditions with average $n = 236.7$ and average $m = 247.4$ feature points,
-as tested on an Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
+\caption{Complexity and running times tested on 45 image pairs with average $n = 237$ and average $m = 247$ feature points
+as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
 3.30~GHz with 8~GB memory.}
@@
     \emph{Self-Match} & $O(n\log(nm))$ & 118s  \\
-    \emph{Self-Match-Ext} & $O(n\log(n(n+m)))$ & 109s\\
+    %\emph{Self-Match-Ext} & $O(n\log(n(n+m)))$ & 109s\\
     \emph{Ratio-Match} & $O(n\log(m))$ & 114s\\
     \emph{Ratio-Match-Ext} & $O(n\log(n+m))$ & 112s\\
-    \emph{Mirror-Match} & $O(n\log(n(n+m)))$ & 116s\\
-    \emph{Mirror-Match-Ext} & $O(n\log(n+m))$ & 110s \\
+    %\emph{Both-Match} & $O(n\log(n(n+m)))$ & 116s\\
+    \emph{Mirror-Match} & $O(n\log(n+m))$ & 110s \\
     \hline
@@
 %
-When we match a query image against multiple target images, as 
-for example in image stitching, assumption \#1 that any feature in the 
-query image has at most one real correspondence in the set of target 
-features is no longer true. It might be the case that two target images 
-contain the same real object which yields two target features that are 
-both real correspondences. In this case calculating the \emph{uniqueness 
-ratio} by dividing the distance of one real correspondence with the 
-distance to another renders it entirely useless if the two features are 
-found in sets where there might be more than one correct 
-correspondence.
-
-Brown et al.\ \cite{brown2005multi} propose calculating the uniqueness 
-ratio by taking the average of the $n$ nearest neighbors in each of the 
-$n$ target images. Since their particular case deals with images that 
-are aligned horizontally one after the other, this approach is not 
-flawed per se. However for the more general case of $N$ target images 
-with an unknown amount of overlap in the target group, their approach 
-would not work since several features in the target group could possibly 
-be a correct correspondence.
-
-This leaves us with two alternatives. Either we match the query image to 
-every target image individually, or we use a matching strategy where the 
-\emph{baseline set} is guaranteed not to contain any real 
-correspondences. \emph{Self-Match} provides such a set, since the 
-\emph{baseline set} of \emph{Self-Match} only contains features in the 
-query image itself. In addition, matching a query image to $N$ target 
-images with \emph{Self-Match} is vastly faster than matching the query 
-image to every target image: If we assume 
-that every of the $N$ images has $n$ features, then matching the query 
-image to all $N$ images can be done in $O(Nn\log(n))$ using a metric 
-tree. However, matching with \emph{Self-Match} is done in $O(n\log(nN)) =
-O(n\log(N) + n\log(n))$.
+When we match a query image against multiple target images, as for example in image stitching, assumption \#1 that any feature in the query image has at most one real correspondence in the set of target features is no longer true.
+It might be the case that two target images contain the same real object which yields two target features that are both real correspondences.
+In this case calculating the \emph{uniqueness ratio} by dividing the distance of one real correspondence with the distance to another renders it entirely useless if the two features are found in sets where there might be more than one correct correspondence.
+
+Brown et al.\ \cite{brown2005multi} propose calculating the uniqueness ratio by taking the average of the $n$ nearest neighbors in each of the $n$ target images.
+Since their particular case deals with images that are aligned horizontally one after the other, this approach is not flawed per se.
+However for the more general case of $N$ target images with an unknown amount of overlap in the target group, their approach would not work since several features in the target group could possibly be a correct correspondence.
+
+This leaves us with two alternatives.
+Either we match the query image to every target image individually, or we use a matching strategy where the \emph{baseline set} is guaranteed not to contain any real correspondences.
+\emph{Self-Match} provides such a set, since the \emph{baseline set} of \emph{Self-Match} only contains features in the query image itself.
+In addition, matching a query image to $N$ target images with \emph{Self-Match} is vastly faster than matching the query image to every target image: If we assume that every of the $N$ images has $n$ features, then matching the query image to all $N$ images can be done in $O(Nn\log(n))$ using a metric tree.
+However, matching with \emph{Self-Match} is done in $O(n\log(nN)) = O(n\log(N) + n\log(n))$.
 
@@
 
-We have proposed a general framework of matching methods; building on the ideas 
-behind \emph{Ratio-Match} and \emph{Mirror-Match}, we also introduced the 
-variations \emph{Self-Match} and \emph{Ratio-Match-Ext}.
-
-We formally proved under three assumptions that \emph{Mirror-Match} 
-performs better than or equal to \emph{Ratio-Match-Ext} in terms of 
-precision and recall, which in turn performs better than or equal to 
-\emph{Ratio-Match}.
-
-From an evaluation using images of rotated 3D objects, we have shown that
-the theoretical conclusions are reflected in the experimental results with 
-\emph{Mirror-Match} often outperforming \emph{Ratio-Match}
-significantly over 3024 image pairs. We further confirmed this behavior 
-for the classical `graffiti' image set, although there is less variation 
-between the algorithms. Finally we show that the theoretical conclusions 
-hold across a variety of popular feature descriptors (SIFT, SURF, BRISK, 
-BRIEF, and FREAK).  These performance gains 
-come free in terms of both computational complexity as well as actual 
-computing time.
-
-With the framework we introduced three simple methods that are all 
-applicable in situations where \emph{Ratio-Match} is currently used.  
-\emph{Ratio-Match-Ext} and \emph{Mirror-Match} 
-can readily and easily replace \emph{Ratio-Match} without any performance penalty 
-and with an increase in precision.  However, both are limited to matching 
-image pairs like \emph{Ratio-Match}. \emph{Self-Match} on the other hand is on par with \emph{Ratio-Match} across all 
-evaluations, but can be applied when matching multiple overlapping images.
+We have proposed a framework of matching methods building on the ideas behind \emph{Ratio-Match} and \emph{Mirror-Match} introducing the variations \emph{Self-Match} and \emph{Ratio-Match-Ext}.
+We formally proved under three assumptions that \emph{Mirror-Match} performs better than or equal to \emph{Ratio-Match-Ext} in terms of precision and recall, which in turn performs better than or equal to \emph{Ratio-Match}.
+
+From an evaluation using images of rotated 3D objects, we have shown that the theoretical conclusions are reflected in the experimental results with \emph{Mirror-Match} often outperforming \emph{Ratio-Match} significantly over 3024 image pairs.
+Finally we show that the theoretical conclusions hold across a variety of popular feature descriptors (SIFT, SURF, BRISK, BRIEF, and FREAK).
+These performance gain come for free in terms of both computational complexity as well as actual computing time.
+
+With the framework we introduced three simple methods that are all applicable in situations where \emph{Ratio-Match} is currently used.
+\emph{Ratio-Match-Ext} and \emph{Mirror-Match} can readily and easily replace \emph{Ratio-Match} without any performance penalty and with an increase in precision.
+However, both are limited to matching image pairs like \emph{Ratio-Match}.
+\emph{Self-Match} on the other hand is on par with \emph{Ratio-Match} across all evaluations, but can be applied when matching multiple overlapping images.
+
+\appendix
+
+\subsection{Proof of equivalence of Self-Match and Self-Match-Ext}
+\label{A:self}
+
+In this appendix we prove the equivalence between \emph{Self-Match} and \emph{Self-Match-Ext}.
+To do this, we look at the nearest neighbor $f_{nn}$ of every query feature $f_{q}$ and consider the two cases of $f_{nn} \in F_{query}$ and $f_{nn} \in F_{target}$.
+For $f_{nn} \in F_{target}$ the uniqueness ratio of \emph{Self-Match-Ext} is:
+\begin{align*}
+    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
+        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
+        &= \text{r}(f_{q}, F_{target}, F_{baseline})
+\end{align*}
+
+Since $F_{proposed} = F_{target}$ for \emph{Self-Match} this shows that when the nearest neighbor is found in the target image, the two algorithms behave identically.
+For $f_{nn} \in F_{query}$ we know that the best match for the query feature is in the query image itself.
+Since neither algorithm returns a correspondence within the same image, they also behave identically for this case.
+This proves that for any set of \emph{query features} \emph{Self-Match} returns the same matches as \emph{Self-Match-Ext}.
+
+\subsection{Proof of equivalence of Both-Match and Mirror-Match}
+\label{A:mirror}
+
+In this appendix we prove the equivalence between \emph{Both-Match} and \emph{Mirror-Match}.
+This proof is almost identical to the equivalence proof between \emph{Self-Match} and \emph{Self-Match-Ext}.
+To prove the equivalence, we look at the nearest neighbor $f_{nn}$ of every query feature $f_{q}$ and consider the two cases of $f_{nn} \in F_{query}$ and $f_{nn} \in F_{target}$.
+For $f_{nn} \in F_{target}$ the uniqueness ratio of \emph{Mirror-Match} is:
+\begin{align*}
+    r &= \text{r}(f_{q}, F_{proposed}, F_{baseline}) \\
+        &= \text{r}(f_{q}, F_{query} \cup F_{target}, F_{baseline})\\
+        &= \text{r}(f_{q}, F_{target}, F_{baseline})
+\end{align*}
+
+Since $F_{proposed} = F_{target}$ for \emph{Both-Match} this shows that when the nearest neighbor is found in the target image, the two algorithms behave identically.
+For $f_{nn} \in F_{query}$ we know that the best match for the query feature is in the query image itself.
+Since neither algorithm returns a correspondence within the same image, they also behave identically for this case.
+This proves that for any set of \emph{query features} \emph{Both-Match} returns the same matches as \emph{Mirror-Match}.
 

### 2014-04-16 text/journal/paper.tex
Changed format to elsevier

@@
-%% bare_jrnl_compsoc.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE Computer
-%% Society journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
+\documentclass[]{elsarticle}
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
+%\usepackage[pdftex]{graphicx}
 
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
-% The Computer Society usually requires 10pt for submissions.
-%
-\documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[12pt,journal,compsoc]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
-  \usepackage{cite}
-\fi
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-%
-% Note that some packages require special options to format as the Computer
-% Society requires. In particular, Computer Society  papers do not use
-% compressed citation ranges as is done in typical IEEE papers
-% (e.g., [1]-[4]). Instead, they list every citation separately in order
-% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
-% package with the nocompress option which is supported by cite.sty v4.0
-% and later. Note also the use of a CLASSOPTION conditional provided by
-% IEEEtran.cls V1.7 and later.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
+\usepackage{natbib}
 \usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-\ifCLASSOPTIONcompsoc
-%\usepackage[tight,normalsize,sf,SF]{subfigure}
-\else
-%\usepackage[tight,footnotesize]{subfigure}
- \fi
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. Computer Society papers
-% use a larger font and \sffamily font for their captions, hence the
-% additional options needed under compsoc mode. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false]{caption}
-%  \usepackage[font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false]{caption}
-%  \usepackage[font=footnotesize]{subfig}
-%\fi
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
-% This package may be useful when used in conjunction with IEEEtran.cls'
-% captionsoff option. Some IEEE journals/societies require that submissions
-% have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.3.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% For subfigure.sty:
-% \let\MYorigsubfigure\subfigure
-% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat/subfig command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-%\documentclass{article}
 \usepackage{footnote}
 \usepackage{multirow} 
-%\usepackage[font={small}]{caption}
-%\usepackage{sidecap}
-\usepackage{cite}
+%\usepackage{cite}
 \usepackage[draft]{hyperref}
-%\usepackage[options]{nohyperref}
-%\usepackage{url}
-%\usepackage[stable]{footmisc}
-%\usepackage{adjustbox}
 \usepackage{balance}
@@
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-\title{Decade of Lost Precision:\\
+
+\title{Decade of Lost Precision:
 A General Framework For Image Feature Matching Without Geometric Constraints}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-%
-%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
-% lists the Computer Society journals use for "first footnote" author
-% affiliations. Use \IEEEcompsocthanksitem which works much like \item
-% for each affiliation group. When not in compsoc mode,
-% \IEEEcompsocitemizethanks becomes like \thanks and
-% \IEEEcompsocthanksitem becomes a line break with idention. This
-% facilitates dual compilation, although admittedly the differences in the
-% desired content of \author between the different types of papers makes a
-% one-size-fits-all approach a daunting prospect. For instance, compsoc 
-% journal papers have the author affiliations above the "Manuscript
-% received ..."  text while in non-compsoc journals this is reversed. Sigh.
 
-\author{Jonas~Toft~Arnfred,
-        Stefan~Winkler,
-        Sabine~S\"usstrunk% <-this % stops a space
-\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem J.~T.~Arnfred and S.~Winkler are with the Advanced Digital Sciences Center (ADSC), University of Illinois at Urbana-Champaign (UIUC), Singapore.\protect\\
-% note need leading \protect in front of \\ to get a newline within \thanks as
-% \\ is fragile and will error, could use \hfil\break instead.
-% E-mail: 
-\IEEEcompsocthanksitem S.~S\"usstrunk is with the \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland.}% <-this % stops a space
-\thanks{}}
+\author[adsc]{Jonas~Toft~Arnfred}
+\author[adsc]{Stefan~Winkler}
+\author[epfl]{Sabine~S\"usstrunk}
 
-%\IEEEauthorblockN{%
-%Jonas Toft Arnfred,\IEEEauthorrefmark{1} Stefan Winkler,\IEEEauthorrefmark{1} Sabine S\"usstrunk\IEEEauthorrefmark{2}}\\
-%\vspace{1mm}
-%\IEEEauthorblockA{%
-%\IEEEauthorrefmark{1}~Advanced Digital Sciences Center (ADSC), University of Illinois at Urbana-Champaign (UIUC), Singapore\\
-%\IEEEauthorrefmark{2}~\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland}
+\address[adsc]{Advanced Digital Sciences Center (ADSC), University of Illinois at Urbana-Champaign (UIUC), Singapore}
+\address[epfl]{\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland}
 
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-%\markboth{IEEE Trans. PAMI}%
-%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% The publisher's ID mark at the bottom of the page is less important with
-% Computer Society journal papers as those publications place the marks
-% outside of the main text columns and, therefore, unlike regular IEEE
-% journals, the available text space is not reduced by their presence.
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}
-% or like this to get the Computer Society new two part style.
-%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2007 IEEE}%
-%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark (Computer Society jorunal
-% papers don't need this extra clearance.)
-
-% for Computer Society papers, we must declare the abstract and index terms
-% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
-% command as these need to go into the title area created by \maketitle.
-\IEEEcompsoctitleabstractindextext{%
 \begin{abstract}
@@
 \end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the journal you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals frown on math
-% in the abstract anyway. In particular, the Computer Society does
-% not want either math or citations to appear in the abstract.
 
-% Note that keywords are not normally used for peer review papers.
-\begin{keywords}
+\begin{keyword}
 Feature matching, ratio match, mirror match, self match
-\end{keywords}}
+\end{keyword}
 
-% make the title area
 \maketitle
-
-% To allow for easy dual compilation without having to reenter the
-% abstract/keywords data, the \IEEEcompsoctitleabstractindextext text will
-% not be used in maketitle, but will appear (i.e., to be "transported")
-% here as \IEEEdisplaynotcompsoctitleabstractindextext when compsoc mode
-% is not selected <OR> if conference mode is selected - because compsoc
-% conference papers position the abstract like regular (non-compsoc)
-% papers do!
-\IEEEdisplaynotcompsoctitleabstractindextext
-% \IEEEdisplaynotcompsoctitleabstractindextext has no effect when using
-% compsoc under a non-conference mode.
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
 
@@
 \centering
-\includegraphics[width=0.85\columnwidth]{images/overview}
+\includegraphics[width=0.95\columnwidth]{images/overview-wide}
 \caption{Graphical representation of the \emph{Baseline} and 
@@
 In turn \emph{Mirror-Match} as introduced by the authors in \cite{arnfred2013mirror}, works by constructing the \emph{proposal set} and \emph{baseline set} by combining features from both the \emph{query} and \emph{target image}.
-By similar variations of the \emph{proposal} and \emph{baseline set} we derive four more algorithms as illustrated in Figure~\ref{fig:overview}, however we will not discuss \emph{Self-Match-Ext} and \emph{Both-Match} further in this paper since we show them to be equivalent with \emph{Self-Match} and \emph{Mirror-Match} respectively in Appendix~\ref{A:self} and \ref{A:mirror}.
+By similar variations of the \emph{proposal} and \emph{baseline set} we derive four more algorithms as illustrated in Figure~\ref{fig:overview}, however we will not discuss \emph{Self-Match-Ext} and \emph{Both-Match} further in this paper since we show them to be equivalent with \emph{Self-Match} and \emph{Mirror-Match} respectively in \ref{A:self} and \ref{A:mirror}.
 
@@
 \centering
-\includegraphics[width=0.9\columnwidth]{images/matching}
+\includegraphics[width=\columnwidth]{images/matching-wide}
 \caption{Feature matching flow chart. $\tau$ 
@@
 
-Using a similar procedure we prove that \emph{Self-Match} is equal to \emph{Self-Match-Ext} and \emph{Both-Match} is equal to \emph{Mirror Match} in Appendix~\ref{A:self} and \ref{A:mirror} respectively.
+Using a similar procedure we prove that \emph{Self-Match} is equal to \emph{Self-Match-Ext} and \emph{Both-Match} is equal to \emph{Mirror Match} in \ref{A:self} and \ref{A:mirror} respectively.
 
@@
 \centering
-\includegraphics[width=0.99\columnwidth]{images/results_ratio_hist}
+\includegraphics[width=0.7\columnwidth]{images/results_ratio_hist}
 \caption{Normalized histogram of the \emph{uniqueness ratios} of true 
@@
 	\centering
-    \includegraphics[width=2\columnwidth]{images/results_all_objects}
+    \includegraphics[width=\columnwidth]{images/results_all_objects}
     \caption{Results for the 3D objects dataset. Each plot 
@@
 \begin{figure}[htb]
-    \begin{subfigure}[t]{0.19\columnwidth}
+    \centering
+    \begin{subfigure}[t]{0.15\columnwidth}
         \centering
@@
     ~ %
-    \begin{subfigure}[t]{0.19\columnwidth}
+    \begin{subfigure}[t]{0.15\columnwidth}
         \centering
@@
 
-    \begin{subfigure}[t]{0.19\columnwidth}
+    \begin{subfigure}[t]{0.15\columnwidth}
         \centering
@@
 \begin{figure}[htb]
-    \begin{subfigure}[t]{0.48\columnwidth}
+    \centering
+    \begin{subfigure}[t]{0.22\columnwidth}
         \centering
@@
     %blank line to force the subfigure onto a new line)
-    \begin{subfigure}[t]{0.48\columnwidth}
+    \begin{subfigure}[t]{0.22\columnwidth}
         \centering
@@
     \end{subfigure}%
-    \\ %add desired spacing between images, e. g. ~, \quad, \qquad 
+    \quad %add desired spacing between images, e. g. ~, \quad, \qquad 
     %a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[t]{0.48\columnwidth}
+    \begin{subfigure}[t]{0.22\columnwidth}
         \centering
@@
     \centering
-    \includegraphics[width=2\columnwidth]{images/results_descriptors_imageset1}
+    \includegraphics[width=\columnwidth]{images/results_descriptors_imageset1}
     \caption{Keypoint / Descriptor combinations measured on 15 pairs of 
@@
 
-\subsection{Proof of equivalence of Self-Match and Self-Match-Ext}
+\section{Proof of equivalence of Self-Match and Self-Match-Ext}
 \label{A:self}
@@
 
-\subsection{Proof of equivalence of Both-Match and Mirror-Match}
+\section{Proof of equivalence of Both-Match and Mirror-Match}
 \label{A:mirror}
@@
 \balance
-\bibliographystyle{IEEEtran}
+\bibliographystyle{elsarticle-num}
 \bibliography{bibliography}
